### 2019-04-19 documents/draft.tex
Remove pdf files and include tex files

\documentclass[12pt,a4paper]{extarticle}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{booktabs} % for toprule, midrule and bottomrule
\usepackage{adjustbox}
\usepackage{amsmath}
\usepackage{bbold}
\usepackage{etoolbox}
\usepackage{setspace} % for \onehalfspacing and \singlespacing macros
\usepackage[hidelinks]{hyperref}
\usepackage{array}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{caption}
\usepackage{pdflscape}
\usepackage{caption}
\usepackage{tabularx}
\usepackage{authblk}
\usepackage{float}
\usepackage{siunitx}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage[authoryear]{natbib}
\usepackage{scrextend}
\usepackage{nicefrac}
\usepackage{enumitem}
\usepackage{multirow}
%\usepackage{showframe}
%\usepackage{lipsum}

% set space
%\doublespacing

% section headings
\renewcommand{\thesection}{\Roman{section}.\hspace{-0.5em}}
\renewcommand\thesubsection{\Alph{subsection}.\hspace{-0.5em}}
\renewcommand\thesubsubsection{\hspace{-1em}}
\newcommand{\subsubsubsection}[1]{\begin{center}{\textit{#1}}\end{center}}

\titleformat{\section}
{\bf\centering\large}{\thesection}{1em}{}

\titleformat{\subsection}
{\itshape\centering}{\thesubsection}{1em}{}

\titleformat{\subsubsection}
{\bf}{\thesubsubsection}{1em}{}

% unicode chars for plots
\DeclareUnicodeCharacter{2212}{$-$}

% booktabs
\setlength\heavyrulewidth{0.06em} % 0.01em> midrule

% images
\graphicspath{ {D:/Users/saketh/Documents/GitHub/BECCS-Case-Study/documents/exhibits/} }

% array
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

% caption set up
\captionsetup[table]{
	font = {sc},
	labelfont = {bf}
}

% sig stars
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}

% hyperlinks
\hypersetup{
	colorlinks=true,
	linkcolor = blue,
	urlcolor  = blue,
	citecolor = blue,
	anchorcolor = blue
}

% bibliography
\makeatletter
\renewenvironment{thebibliography}[1]
{\section*{References}%
	\@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}%
	\list{}%
	{\setlength{\labelwidth}{0pt}%
		\setlength{\labelsep}{0pt}%
		\setlength{\leftmargin}{\parindent}%
		\setlength{\itemindent}{-\parindent}%
		\@openbib@code
		\usecounter{enumiv}}%
	\sloppy
	\clubpenalty4000
	\@clubpenalty \clubpenalty
	\widowpenalty4000%
	\sfcode`\.\@m}
{\def\@noitemerr
	{\@latex@warning{Empty `thebibliography' environment}}%
	\endlist}
\makeatother

% etoolbox
\AtBeginEnvironment{quote}{\singlespacing}

% proofs
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1:} }{\ \rule{0.5em}{0.5em}}

\begin{document}

\title{\singlespacing{\textbf{Efficient pollution abatement in electricity markets with intermittent renewable energy}}}

\author[]{Saketh Aleti}

\affil[]{\small{}}

\date{\vspace{-1em}\small{\today}}

\maketitle

\section{Extended Abstract}

Renewable energy technologies have seen considerable adoption over the last few decades (EIA 2019). Unlike the alternatives, wind and solar power are particularly unique in that the amount of energy they supply is intermittent. Consequently, designing economically efficient policy to promote their adoption is not straightforward given that they cannot easily substitute for traditional technologies such as coal power which handles base load demand. Some of the literature has approached the problem by constructing numerical models that find the cheapest renewable technology set while accounting for intermittent supply. Müsgens and Neuhoff (2006) model uncertain renewable output with intertemporal generation constraints, while Neuhoff, Cust, and Keats (2007) model temporal and spatial characteristics of wind output to optimize its deployment in the UK. On the other hand, other literature focuses on the effect of intermittent technologies on the market itself; Ambec and Crampes (2010) study the interaction between intermittent renewables and traditional reliable sources of energy in decentralized markets, and Chao (2011) models alternative pricing mechanisms for intermittent renewable energy sources. Additionally, Borenstein (2010) reviews the effects of present public policies used to promote renewables and the challenges posed by intermittency.

In this paper, we present a theoretical model of electricity markets with intermittent renewable energy and derive the optimal public policy to handle pollution externalities. In contrast with other theoretical models of intermittency which optimize a pubic electricity sector, our model assumes utility and profit maximization. Additionally, it represents the energy sector over multiple periods with electricity output for each technology varying over time for intermittent technologies. This approach is better suited for studying the dynamics of present US electricity markets which are primarily funded by private sector investment and have prices that vary over time. We first consider a simpler version of our model with two periods and two energy generation technologies, derive the comparative statics for this model, and detail the policy implications. Then, we produce numerical results for optimal policy prescriptions with a multi-period, multi-technology version of our model using electricity generation data on the PGM region.

Present models of the energy sector concerned with the adoption of renewable energy often discuss the elasticity of substitution between clean and dirty energy; this elasticity is meant to capture factors such as intermittency and reliability that impede perfect substitution between energy sources. Additionally, this elasticity is often estimated empirically or modelled in a CGE using a CES production function with capital inputs for each energy technology. However, this top down approach may be missing the actual source of the substitution effects while also being unrealistic. For instance, consider a simple case where energy output is a Cobb-Douglas function (a special case of CES) of two energy inputs: solar and coal. According to this function, increasing the amount of coal input causes the marginal product of solar input to rise; this makes little sense in practical terms, since the output of additional solar panels should not be related to the amount of coal input. Moreover, this approach, while possibly relevant for other sectors' goods, weakens the accuracy of theoretical and CGE models focused on the energy sector.

However, it is still possible to produce a more accurate model of the electricity sector that can capture trade-offs between the energy output of different technologies from both cost and intermittency. To start, rather than energy production following a general CES function, we first assume that energy follows a linear production function where total energy is instead the sum of the energy output of each source. The purpose of using a linear production function is that increasing the input of one energy source does not change the marginal product of another source as it does in a CES function. Additionally, we split this production function up across periods; that is, in each period, the electricity generation is equal to the energy output of each source in that period. For intermittent technologies, energy output varies in each period, so total output would as well. Next, we assume that firms pick a profit-maximizing level of investment in each energy technology. This investment stays fixed in all periods, but the total energy output can vary over time due to intermittency; for instance, a solar plant provides a variable output by time of day, while nuclear plant cannot easily vary its output within 24 hours. Moreover, we assume that firms face linear costs and electricity prices are set equal to their marginal cost; the former assumption is temporarily made for mathematical tractability while the latter is realistic given the competitiveness of electricity markets.

While the production function described so far is linear, we may still find a non-zero elasticity of substitution between energy sources. That is, consider a representative agent with a CES utility function that captures intertemporal variation in the utility gained from energy consumption. Specifically, the utility function is composed of energy consumption differentiated by period; so, for example, in a two-period model, we may have off-peak consumption and on-peak consumption as our two goods. Because people prefer to consume energy at different proportions based on the time of day, this variation can be modeled through the share parameters in the CES function. Moreover, since people may substitute energy consumption across time by availability and prices, the CES elasticity parameter captures the intertemporal elasticity of substitution. Thus, in this model, the intermittency of an energy generation technology plays a key role in determining its substitutability with other technologies. For instance, solar power may be a good substitute for coal power during the day, but obviously not at night; consequently, this pair complements each other, since coal handles the base load while solar handles the peak load. Alternatively, wind and solar are a poor combination, since both produce intermittently; this pair is closer to being substitutes. All in all, the result of using CES preferences with temporally differentiated energy consumption is that we can capture substitutability/complementarity between energy sources in an accurate way.

The first significant result in this model is that the optimal quantity of investment in intermittent renewable technology is concave with respect to both cost efficiency (cost per unit) and output efficiency (energy output per unit). So, for example, suppose some location has a coal-fired plant and is considering investing in a solar power plant. A 10\% increase in the output per solar panel may increase the optimal quantity of solar panels by x\%, while a 20\% increase in solar efficiency will increase the optimal quantity of solar by y\% where y < 2x. Because of this concavity, exponential increases in efficiency of intermittent renewable sources over time, as Moore’s Law may predict, is not enough to fully substitute out reliable energy technology. Hence, we argue that a full transition to renewable energy requires more emphasis on technologies such as nuclear, biomass, hydro, and geothermal energy sources; although these sources compete with intermittent energy technology, they are able fully substitute out for fossil fuel energy. Additionally, the reliable output of these technologies can handle base loads; this allows them to complement the intermittency of renewables such as wind and solar.

Secondly, suppose that we would like to promote clean energy adoption and replace dirty energy to reduce the pollution emissions. Because we have diminishing returns from both forms of efficiency, it is optimal to subsidize both research and the cost of intermittent renewable technology. This is because we expect research subsidies to increase both output efficiency and cost efficiency, while subsidies would increase the cost efficiency of renewables for a market participant. A mix of both instruments leads to improving both forms of efficiency at once, thus replacing dirty energy technology in the most cost-efficient way. Alternatively, since we would see symmetrical effects from taxing dirty energy sources rather than subsidizing clean ones, taxing dirty energy sources can substitute for renewable cost subsidies. Consequently, a carbon tax plus a research subsidy for renewables is another optimal choice for pollution abatement.

Finally, our model implies that the optimal level of subsidies/taxes on energy generation should vary by the state of the local energy market. That is, the change in optimal quantity of intermittent energy technology with respect to both types of efficiency is also a function of the efficiencies of the other technologies available. Consequently, the marginal benefit of a subsidy or tax varies spatially, since different geographies have access to different energy sources. For instance, one community may be relying on hydropower while another may be using coal power; the effect of a 1\% cost subsidy on solar installments in these two communities would vary because of the differences in the communities’ pre-existing energy generation technologies. Hence, local communities that aim to promote clean energy and reduce pollution should optimize their policy instruments to suit their local energy markets.

\subsection{References}

\begin{itemize}
	\item Literature
	\item Description of model
	\item 
\end{itemize}

\section{Introduction}
\dots

Things I'd like to say:
\begin{itemize}
	\item Because the marginal product of renewable energy inputs may be time-dependent, renewable energy may complement traditional, constant-output energy sources rather than fully substitute for it. Obvious arugment follows from base load output required at all times. 
	\item How the conversion parameters for energy inputs affect their elasticity of substitution
	\item How variability in energy output decreases the value of particular energy sources. Obvious argument from concavity of utility implying risk aversion. 
\end{itemize}

\pagebreak

\section{Introduction}

By intermittency, we mean variation in output over time due to technical constraints; on the other hand, we define reliability as stochastic variation in output. For instance, solar power is intermittent while coal power is not. We focus on modeling intermittency but ignore reliability to keep our model tractable and its implications clear.

\section{Model}

We model electricity as a heterogenous good which is differentiated by its delivery time. Then, we consider a representative consumers who purchases varying quantities of electricity over time in order to maximize utility. Obviously, consumers would prefer to spread their electricity consumption out over time; the convexity of the indifference surfaces of a standard CES function can model this preference quite simply. Next, we model the electricity sector using a representative firm that chooses a set of electricity-generating inputs to maximize profit; some of these inputs are intermittent - they generate a non-constant amount of energy over time. These two sides of the market reach an equilibrium through adjustments in prices of electricity in each period.

\subsection{General Model}

Consumers purchase variable amounts of electricity $Z_t$ over each period $t$. Assuming the price of electricity in each period is held constant, they prefer that a fixed proportion of their energy arrive in period $t$ while some other fixed proportion arrive at $s \neq t$. Finally, we suppose that consumers would be willing to shift their consumption from one period to another in response to a shift in prices. In total, these assumptions can be captured using a representative consumer with the standard CES utility function
\begin{equation}
U = \left( \sum_t \alpha_t Z_t^\phi  \right)^{1/\phi}
\end{equation}
where $\sigma = 1/(1-\phi)$ is the intertemporal elasticity of substitution for electricity consumption. We define $\sum_t \alpha_t = 1$, so that $\alpha_t$ is the fraction of electricity consumption in period $t$ when all prices are equal; naturally, $\alpha_t > 0$ for all $t$. The budget constraint is given by
\begin{equation}
I = \sum_t p_t Z_t
\end{equation}
where $p_t$ is the price of electricity in period $t$ and $I$ is the income. Consequently, the first order conditions when maximizing utility given this budget constraint imply:
\begin{align}
Z_t &= \left(\frac{\alpha_t}{p_t} \right)^\sigma \frac{I}{P} \\
P &= \sum_t \alpha_t^\sigma p_t^{1-\sigma}
\end{align}
where $P$ is the price index.

Secondly, we have firms maximizing profit by picking an optimal set of energy inputs. In reality, electricity markets are fairly competitive, so we assume perfect competition. Hence, we can model the set of firms using a representative firm that sets marginal revenue equal to marginal cost. We define the quantity of deployed energy technology $i$ as $X_i$, and we define its output per unit in period $t$ as $\xi_{1,t}$. So, for example, if $i$ is solar power, $X_i$ would be the number of solar panels and $\xi_{i,t}$ may be kW generated per solar panel in period $t$. Consequently, the energy generated in period $t$, $Z_t$, is given by $\sum_i \xi_{i,t} X_i$. We define these variables in matrices to simplify notation:
\begin{align*}
X \equiv \begin{pmatrix}
X_1\\
\vdots\\
X_n
\end{pmatrix} ,\;
Z \equiv \begin{pmatrix}
Z_1\\
\vdots\\
Z_m
\end{pmatrix} ,\;
p \equiv \begin{pmatrix}
p_1\\
\vdots\\
p_m
\end{pmatrix} ,\;
\xi \equiv \begin{pmatrix}
\xi_{1,1} & \dots & \xi_{1,m}\\
\vdots & \ddots & \\
\xi_{n,1} &  & \xi_{n,m}
\end{pmatrix} 
\end{align*}
where we have $n$ technologies and  $m$ periods. Also, note that we have $Z \equiv \xi^T X$. Firms pick $X$ to maximize profit while facing the cost function $C(X_1, \dots, X_n)$ where $C$ is convex with respect to each input. Total profit is given by 
\begin{equation}
\Pi = p^T Z - C(X_1, \dots, X_n)
\end{equation}
To simplify the algebra, suppose we $n=m$. We further make the assumption that the output per unit of each technology is unique and non-negative in each period; in other words, the output per unit of one technology is not a linear combination of those of the other technology in our set. This then implies that $\xi$ is of full rank and therefore invertible. Lastly, suppose that we have a linear cost function $C = \sum_i c_i X_i = c^T X$ where $c_i$ is the cost per unit of $X_i$ Now, maximizing profit, we find the first order condition:
\begin{equation}
\frac{\partial \Pi}{\partial X} = 0 \implies p = \xi^{-1} c
\end{equation}
Combining both first order conditions allows us to find the equilibrium; however, in order to produce more comprehensible results, we consider a further simplification.

\subsection{Cobb-Douglas Case with Two Periods \& Two Technologies}

\subsubsection{Equilibrium Results}

Firstly, we restrict the utility function to its Cobb-Douglas form which is simply the case where the elasticity of substitution $\sigma = 1$. Secondly, we limit the number of periods and technologies to 2. Consequently, our demand equations simplify to:
\begin{align}
Z_t &= \alpha_t / p_t \\
Z_s &= \alpha_s / p_s
\end{align}
where $t$ and $s$ are our two periods. Next, solving for the FOC condition for profit maximizing (which remains the same), we have:
\begin{align*}
p &=  \xi^{-1} c \\
p &= \begin{pmatrix}
-\dfrac{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}  \\[2ex]
\dfrac{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}} 
\end{pmatrix} 
\end{align*}
And, substituting back into our demand equations, we have the equilibrium quantities for $Z$ and $X$. 
$$
Z = \begin{pmatrix}
\dfrac{\alpha _{t}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{c_{2}\,\xi _{\mathrm{1s}} - c_{1}\,\xi _{\mathrm{2s}}} \\[2ex]
\dfrac{\alpha _{s}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} 
\end{pmatrix}
\implies 
X = \begin{pmatrix}
\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}+\dfrac{\alpha _{s}\,\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} \\[2ex] 
-\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}-\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}
\end{pmatrix}
$$

Furthermore, we derive restrictions on the parameters $\xi$ and $c$ by assuming $Z, X > 0$. These restrictions are detailed in \hyperref[tab:paramrest]{Table 1}. There are two possible sets of symmetrical restrictions. The first set, Case 1, assumes that technology 2 is more cost effective in period $t$, while the second set, Case 2, assumes that technology 1 is more cost effective in period $t$. If a given set of parameters do not fall into either case, we are left with an edge case where one of the technologies is not used. Additionally, these inequalities compare two types of efficiency -- output efficiency and cost efficiency; we define output efficiency as electricity output per unit of input and cost efficiency in terms of electricity output per dollar of input. We refer to the last set of restrictions as mixed, because they relate both cost and output efficiency.

\begin{table}[h!]
	\caption{Parameter Restrictions for $Z, X > 0$} 
	\label{tab:paramrest}
	\small
	\centering
	\begin{tabular}{@{\extracolsep{2em}}l@{\hspace{-0.5 em}}cc}
		\\[-4ex]
		\toprule \\[-2.5ex]
		& \textbf{Case 1} & \textbf{Case 2 } \\
		\cmidrule(lr){2-2} \cmidrule(lr){3-3} \\[-1.5ex]
		\textbf{Cost Efficiency}& $\xi_{2t}/c_2 > \xi_{1t}/c_1$ & $\xi_{2t}/c_2 < \xi_{1t}/c_1 $\\
		\textbf{Restrictions} & $\xi_{1s}/c_1 > \xi_{2s}/c_2$  & $\xi_{1s}/c_1 < \xi_{2s}/c_2 $ 		\\ [3ex]
		\textbf{Output Efficiency}& $\xi_{2t}/\xi_{2s} > \xi_{1t}/\xi_{1s}$ & $\xi_{2t}/\xi_{2s} < \xi_{1t}/\xi_{1s}$\\
		\textbf{Restrictions} & $\xi_{1s}/\xi_{1t} > \xi_{2s}/\xi_{2t} $  & $\xi_{1s}/\xi_{1t} < \xi_{2s}/\xi_{2t}  $ 		\\ [3ex]
		\multirow{2}{10em}{\textbf{Mixed Efficiency Restrictions}}& $\dfrac{\alpha_s \left(\xi_{1s}/c_1 - \xi_{2s}/c_2\right)}{\alpha_t \left( \xi_{2t}/c_2 - \xi_{1t}/c_1 \right)} > \xi_{2s}/\xi_{2t}$ & $\dfrac{\alpha_s \left(\xi_{1s}/c_1 - \xi_{2s}/c_2\right)}{\alpha_t \left( \xi_{2t}/c_2 - \xi_{1t}/c_1 \right)} < \xi_{2s}/\xi_{2t}$\\
		& $\dfrac{\alpha_s \left(\xi_{1s}/c_1 - \xi_{2s}/c_2\right)}{\alpha_t \left( \xi_{2t}/c_2 - \xi_{1t}/c_1 \right)} < \xi_{1s}/\xi_{1t} $  & $\dfrac{\alpha_s \left(\xi_{1s}/c_1 - \xi_{2s}/c_2\right)}{\alpha_t \left( \xi_{2t}/c_2 - \xi_{1t}/c_1 \right)} > \xi_{1s}/\xi_{1t} $ 		\\[2ex] 
		\midrule
		\multicolumn{3}{@{}p{40em}@{}}{\footnotesize \textit{Note: } The inequalities in this table assume that all elements of $\xi$ are greater than $0$. The full proof given below provides equivalent restrictions for the zero cases.   }  \\ 
	\end{tabular} 
\end{table}

\begin{proof}
	We aim to derive conditions on $\xi$ and $c$ required to have positive $Z$ and $X$, so we begin by assuming $X, Z  > 0$. Second, since the equations so far are symmetrical, note that there be two symmetrical sets of potential restrictions we must impose on the parameters. Thus, we first assume the inequality $c_1 \xi_{2t} - c_2 \xi_{1t} > 0$ to restrict ourselves to one of the two cases. This assumption results in the denominator of $Z_s$ being positive. Hence, we must also have $\xi_{1s}\xi_{2t} - \xi_{2s}\xi_{1t} > 0 $ for $Z_s > 0$. This same term appears in the numerator for $Z_t$, hence its denominator must be positive: $c_2 \xi_{1s} - c_1 \xi_{2s} > 0$. Now, rewriting these inequalities, we have:
	\begin{align*}
	c_1 \xi_{2t} - c_2 \xi_{1t} > 0 &\implies \xi_{2t}/c_2 > \xi_{1t}/c_1 \\
	c_2 \xi_{1s} - c_1 \xi_{2s} > 0 &\implies \xi_{1s}/c_1 > \xi_{2s}/c_2 \\
	\xi_{1s}\xi_{2t} - \xi_{2s}\xi_{1t} > 0 &\implies \xi_{1s}/\xi_{1t} > \xi_{2s}/\xi_{2t} \\
	&\implies \xi_{1t}/\xi_{1s} < \xi_{2t}/\xi_{2s} 
	\end{align*}
	Note that the latter two restrictions can be derived from the former two. Additionally, we implicitly assume that we have $\xi > 0$. However, this is not necessary assumption, since $\xi$ invertible only requires $\xi_{1t} \xi_{2s} > 0$ or $\xi_{1s} \xi_{2t} > 0$. Instead, we may leave the latter two inequalities in the form $ \xi_{1s}\xi_{2t} > \xi_{2s}\xi_{1t}$ which remains valid when values of $\xi$ are equal to $0$. Lastly, the mixed efficiency restrictions come from $X > 0$. To start, for $X_1$, we have:
	\begin{align*}
	X_1 > 0 &\implies (\alpha_t \xi_{2s})(c_1 \xi_2t - c_2\xi_1t) + (\alpha_s \xi_{2t})(c_1 \xi_{2s} - c_2 \xi_{1s}) < 0\\
	&\implies (\alpha_t \xi_{2s})(c_1 \xi_2t - c_2\xi_1t) < (\alpha_s \xi_{2t})(c_2 \xi_{1s} - c_1 \xi_{2s}) \\
	&\implies (\xi_{2s}/\xi_{2t}) < (\alpha_s (c_2 \xi_{1s} - c_1 \xi_{2s}))/(\alpha_t(c_1 \xi_{2t} - c_2\xi_{1t})) \\
	&\implies (\xi_{2s}/\xi_{2t}) < (\alpha_s (\xi_{1s}/c_1 -  \xi_{2s}/c_2))/(\alpha_t(\xi_{2t}/c_2 - \xi_{1t}/c_1)) 
	\end{align*}
	Similarly, for $X_2$, note that only the numerators differ; $\xi_{2s}$ is replaced with $-\xi_{1s}$ and $\xi_{2t}$ is replaced with $-\xi_{1t}$. Hence, we have
	\begin{align*}
	X_2 > 0 &\implies (\alpha_t \xi_{1s})(c_1 \xi_2t - c_2\xi_1t) + (\alpha_s \xi_{1t})(c_1 \xi_{2s} - c_2 \xi_{1s}) > 0\\
	&\implies (\xi_{1s}/\xi_{1t}) > (\alpha_s (\xi_{1s}/c_1 -  \xi_{2s}/c_2))/(\alpha_t(\xi_{2t}/c_2 - \xi_{1t}/c_1)) 
	\end{align*}
	To double check, note that combining the inequalities from $X_1>0$ and $X_2 > 0$ leads to $\xi_{2s}/\xi_{2t} < \xi_{1s}/\xi_{1t}$. This is precisely the earlier result obtained from $Z > 0$. Again, it is  important to note that we assume $\xi > 0$ for to simplify the inequalities of $X_1 > 0$ and $X_2 > 0$ . Otherwise, we may leave the inequalities in their pre-simplified forms and they are still valid when  $\xi_{1t} \xi_{2s} > 0$ or $\xi_{1s} \xi_{2t} > 0$.   \\ \hfill
\end{proof}

Let us consider the set of restrictions belonging to Case 1. The first inequality, our initial assumption, states that technology 2 is relatively more cost effective in period $t$. The second inequality claims technology 1 is relatively more cost effective in period $s$. The implications are fairly straightforward; if a technology is to be used, it must have an absolute advantage in cost efficiency in at least one period. The third condition states that the relative output efficiency of technology 2 is greater than that of the first technology in period $t$. And, the fourth condition makes a symmetrical claim but for the technology 1 and period $s$. These latter two restrictions regarding output efficiency enter $Z$ and $X$ through $p$; they're simply a restatement of the invertibility of $\xi$ and can also be derived through the cost efficiency restrictions.

The mixed efficiency restrictions are less intuitive. Firstly, note that $\left(\xi_{1s}/c_1 - \xi_{2s}/c_2\right)$ is the difference in cost efficiency for the two technologies in period $s$; this is equivalent to the increase in $Z_s$ caused by shifting a marginal dollar towards technology 1. Similarly, the bottom term $\left( \xi_{2t}/c_2 - \xi_{1t}/c_1 \right)$ represents the change in $Z_t$ caused by shifting a marginal dollar towards technology 1. Both these terms are then multiplied by the share parameter of the utility function for their respective time periods. Furthermore, note that $\alpha_t$ $(\alpha_s)$ is the elasticity of utility with respect to $Z_t$ $(Z_t)$. Hence, in total, the mixed efficiency restrictions relate the relative cost efficiencies of each technology with their output efficiency and the demand for energy. So, for example, suppose that consumers prefer, \textit{ceteris paribus}, that nearly all their electricity arrive in period $t$. This would imply $\alpha_t$ is arbitrarily large which results in the left-hand side of the fraction becoming arbitrarily small. This violates the first mixed efficiency restriction but not the second; consequently, use of the first technology, which is less cost effective in period $t$, approaches $0$.

In more practical terms, suppose that our first technology was coal power and latter was solar power; additionally, assume period $t$ and $s$ are the peak and off-peak for a day. We know that the output efficiency of coal is constant through the day, while that of solar power is higher in period $t$ -- this ensures the output efficiency restriction: $\xi_{2t}/\xi_{2s} > \xi_{1t}/\xi_{1s}$. Additionally, we can reasonably assume that coal is more cost effective than solar in the off-peak period when there is less sun; hence, the second cost efficiency restriction is satisfied. Thirdly, the first condition must be true for there to be an incentive to use solar power; that is, solar needs be cost effective during peak hours otherwise we hit an edge case where no solar is employed. Finally, we face the mixed efficiency condition, which essentially implies that there must be sufficient demand for electricity during period $t$, when solar is more effective, for it to be a feasible technology. So, overall, for a technology to be feasible, we have three conditions: it must the most cost effective in a particular period, its output efficiency must be maximized in the same period, and there must be sufficient amount of demand in that period.

%\footnote{This same analysis can be further extended to any $n$ technologies. However, the number restrictions and different cases to ensure $X , Z > 0$ expands very quickly ($O(n!)$). For instance, if we had 3 technologies and 3 periods, we must first assume each technology is more cost effective than the other two in a unique period; this adds 3*2 restrictions. Then, we must make the output efficiency restrictions comparing each pair of technologies for each pair of periods.}

\subsubsection{Comparative Statics}

The comparative statics are similarly intuitive. The equilibrium quantity of a technology is increasing with its output efficiency and decreasing with its cost. Additionally, the equilibrium quantities for a particular technology move in the opposite direction with respect to the output efficiency and cost of the other technologies. So, for example, an increase in the output efficiency of solar or a decrease in solar's cost will reduce the optimal quantity of coal power. 
\hfill \\\\
\begin{proof}
We begin by deriving the comparative statics of the cost and efficiency parameters with respect to $X$.   Firstly, we take derivatives with respect to the cost vectors:
\begin{align*}
\frac{\partial X_1}{\partial c} &= 
\begin{pmatrix}
-\dfrac{\alpha _{t}\,{\xi _{\mathrm{2s}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}-\dfrac{\alpha _{s}\,{\xi _{\mathrm{2t}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} \\
\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}+\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}
\end{pmatrix}
=
\begin{pmatrix}
< 0 \\
> 0 
\end{pmatrix} \\
\frac{\partial X_2}{\partial c} &= 
\begin{pmatrix}
\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}+\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} \\
-\dfrac{\alpha _{t}\,{\xi _{\mathrm{1s}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}-\dfrac{\alpha _{s}\,{\xi _{\mathrm{1t}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}
\end{pmatrix}
=
\begin{pmatrix}
> 0 \\
< 0 
\end{pmatrix}
\end{align*}
The first and second terms of $\partial X_1 / \partial c_1$ are clearly both negative independent of the restrictions on the parameters. Similarly, all terms of  $\partial X_1 / \partial c_2$ are positive independent of any restrictions. Since the structure of this problem is symmetrical with respect to $X_1$ and $X_2$, the same comparative statics apply but in reverse for $X_1$. Next, we derive comparative statics for each element of $\xi$.
\begin{alignat*}{2}
\frac{\partial X_1}{\partial \xi} &= 
\begin{pmatrix}
\dfrac{\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} & \dfrac{\alpha _{t}\,c_{2}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} \\
\dfrac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} & \dfrac{-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} \\
\end{pmatrix}
&&=
\begin{pmatrix}
> 0 & > 0  \\
< 0 & < 0
\end{pmatrix} \\
\frac{\partial X_2}{\partial \xi} &= 
\begin{pmatrix}
\dfrac{-\alpha _{s}\,c_{1}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} & \dfrac{-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} \\
\dfrac{\alpha _{s}\,c_{1}\,\xi _{\mathrm{1t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}& \dfrac{\alpha _{t}\,c_{1}\,\xi _{\mathrm{1s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} \\
\end{pmatrix}
&&=
\begin{pmatrix}
< 0 & < 0 \\
> 0 & > 0  
\end{pmatrix}
\end{alignat*}
Again, the signs are fairly straightforward. The optimal quantity of $X_1$ increases with its output efficiency in both periods; however, it decreases with the output efficiency of $X_2$ in both periods. Similarly, symmetrical results are shown for $X_2$. Next, we study the effects of $\alpha$ on $X$; this requires us to place some restrictions on the parameters, so we use those belonging to Case 1 in \hyperref[tab:paramrest]{Table 1}. With $\alpha \equiv \left( \alpha_t \;\; \alpha_s \right)^T$, 
\begin{align*}
\frac{\partial X_1}{\partial \alpha} &= 
\begin{pmatrix}
\dfrac{\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} \\
\dfrac{\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}
\end{pmatrix}
=
\begin{pmatrix}
< 0 \\
> 0 
\end{pmatrix} \\
\frac{\partial X_2}{\partial \alpha} &= 
\begin{pmatrix}
\dfrac{-\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} \\
\dfrac{-\xi _{\mathrm{1t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}
\end{pmatrix}
=
\begin{pmatrix}
> 0 \\
< 0 
\end{pmatrix}
\end{align*}
Note that our restrictions imply that $c_1 \xi_{2t} - c_2 \xi_{1t} > 0$ and $c_2 \xi_{1s} - c_1 \xi_{2s} > 0$. From here, the intuition is clear; we assume that $X_2$ is more cost efficient in period $t$, so increases in demand during period $t$ (caused by increases in $\alpha_t$) will increase the optimal quantity of $X_2$. And, the same applies to $X_1$ with respect to period $s$ and $\alpha_s$. Again, due to symmetry, the statics are reversed when the technologies are flipped. Similarly, the signs would also be flipped if we used the restrictions given by Case 2 instead.

Next, we derive the comparative statics for $Z$. 
\begin{alignat*}{2}
\frac{\partial Z_t}{\partial c} &= 
\begin{pmatrix}
\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}\\
\dfrac{-\alpha _{t}\,\xi _{\mathrm{1s}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}
\end{pmatrix}
&=
\begin{pmatrix}
< 0 \\
> 0 
\end{pmatrix} \\
\frac{\partial Z_s}{\partial c} &= 
\begin{pmatrix}
\dfrac{-\alpha _{s}\,\xi _{\mathrm{2t}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} \\
\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}
\end{pmatrix}
&=
\begin{pmatrix}
> 0 \\
< 0 
\end{pmatrix}
\end{alignat*}
From our restrictions, we have

\hfill
\end{proof}

\clearpage

\subsubsection{Externalities}

Now, suppose that our first technology, which again may be coal power, produced negative externalities. Specifically, the social cost of pollution is given by $C(X) = \gamma X_1$ where $\gamma$ is the monetary damage per unit of $X_1$. A social planner is interested in balancing the damages caused by pollution with the surplus of the private sector. That is, they aim to solve
$$\max_{\tau} \; CS + PS - C(X)$$
where $\tau$ is the tax on $X_1$, so that its final price is $c_1 + \tau$. The traditional solution, a Pigouvian tax, simply sets the tax equal to the marginal social damage of pollution: $\tau = \gamma$. In our particular case, the producer faces a linear cost function resulting in $PS = 0$. Consequently, the solution in this case is to set the cost of the polluting technology directly equal to its social cost using $\tau = \gamma - c_1$.

But, the latter is not always the optimal solution in our model. In fact, it is a special case when each technology produces in one unique period. To see why, suppose, without loss of generality, that the first technology only produces in the first period and the second only produces in the second period. In other words, with periods $t$ and $s$, we have $\xi_{1s} = \xi_{2t} = 0$; this means $X_1$ is the only source of $Z_t$ while $X_2$  is the only source of $Z_s$. Since the demand functions of $Z_t$ and $Z_s$ are independent of $p_s$ and $p_t$ respectively, we can treat this case as two seperate markets for two seperate commodities. Consequently, since producer surplus is fixed, the optimal tax is given by $\tau = \gamma - c_1$.

However, now suppose that both technologies produce in both periods. We then solve the social planner's welfare maximization problem by finding a solution to the first-order condition:
$$\frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial C(X)}{\partial \tau} = 0$$
The optimal solution is characterized by the following first-order condition in terms of $p$.
$$
\gamma \left( \eta_{1,1}^2 \alpha_t / p_t^2 + \eta_{2,1}^2 \alpha_s / p_s^2 \right) = \left(\eta_{1,1} \alpha_t /p_t + \eta_{2,1} \alpha_s / p_s \right) $$
This itself does not provide a straightforward solution to $\tau$. Instead, let us consider a practical example to simplify the problem. Suppose that our first, pollution-creating technology is coal power while the second technology is solar power. Furthermore, assume that solar power produces during period $t$ but not during period $s$, so that we have $\xi_{2s} = 0$. This greatly simplifies the FOC and implies the following optimal tax:
$$\tau \, = \,  \gamma \, - \, c_1 \, +  \hspace{-1.5em} \underbrace{(c_2 \, \xi_{1t})/ \xi_{2t}}_\textrm{Intermittency Adjustment}$$

\hfill \\
\begin{proof}
Firstly, since our producer surplus is fixed due to linear costs, we have $\frac{\partial PS}{\partial \tau} = 0$. Now, we find the effect on consumer surplus. Letting $\eta = \xi^{-1}$, note that we have
$$\frac{\partial CS}{\partial p} = 
\begin{pmatrix}
-\alpha_t / p_t \\
-\alpha_s / p_s
\end{pmatrix}
\qquad
\frac{\partial p}{\partial \tau} =
\partial
\left( 
\eta
\begin{pmatrix}
c_1 + \tau \\
c_2
\end{pmatrix}
\right)
/ \partial \tau
=
\begin{pmatrix}
\eta_{1,1} \\
\eta_{2,1}
\end{pmatrix}
$$
Next, we find the partial derivatives for the equilibrium quantity of $X_1$. 
\begin{align*}
Z \equiv \xi^T X &\implies X = \eta^T Z \\
&\implies X_1 = \eta_{1,1} Z_t + \eta_{2,1} Z_s 
\end{align*}
$$\frac{\partial X_1}{\partial p} = 
\begin{pmatrix}
-\eta_{1,1} \alpha_t / p_t^2 \\
- \eta_{2,1} \alpha_s / p_s^2 
\end{pmatrix}
$$
Finally, we may solve for the first-order condition.
\begin{align*}
0 &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial C(X)}{\partial \tau}\\
\frac{\partial C(X)}{\partial \tau} &= \frac{\partial CS}{\partial \tau}\\
\frac{ \partial  C(X)}{\partial p} \frac{\partial p}{\partial \tau}  &= \frac{\partial CS}{\partial p} \frac{\partial p}{\partial \tau}\\
\gamma \left( \eta_{1,1}^2 \alpha_t / p_t^2 + \eta_{2,1}^2 \alpha_s / p_s^2 \right) &= \eta_{1,1} \alpha_t /p_t + \eta_{2,1} \alpha_s / p_s
\end{align*}
Plugging in for $p$ with $(c_1 + \tau, c_2)^T$ yields the following FOC with three roots for $\tau$.

$$-\frac{\alpha _{t}\,\mathrm{\gamma}\,{\xi _{\mathrm{1t}}}^2\,{\xi _{\mathrm{2s}}}^4}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2\,{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}+\tau \,\xi _{\mathrm{2s}}\right)}^2}-\frac{\alpha _{s}\,\mathrm{\gamma}\,{\xi _{\mathrm{2s}}}^2\,{\xi _{\mathrm{2t}}}^2}{{c_{2}}^2\,{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2} $$
$$ = 	
\frac{c_{2}\,\xi _{\mathrm{2s}}\,\left(\alpha _{s}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}+\alpha _{t}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)-\alpha _{s}\,{\xi _{\mathrm{2s}}}^2\,\xi _{\mathrm{2t}}\,\left(c_{1}+\tau \right)}{c_{2}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}+\tau \,\xi _{\mathrm{2s}}\right)}
$$
If we allow $\xi_{2s} = 0$, then this simplifies to
\begin{align*}
-\frac{\alpha _{s}\,\mathrm{\gamma}\,{\xi _{\mathrm{2t}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}+\tau \,\xi _{\mathrm{2t}}\right)}^2} &= -\frac{\alpha _{s}\,\xi _{\mathrm{2t}}}{\xi _{\mathrm{2t}}\,\left(c_{1}+\tau \right)-c_{2}\,\xi _{\mathrm{1t}}}\\
0 &= \frac{\alpha _{s}\,{\xi _{\mathrm{2t}}}^2\,\left(c_{1}-\mathrm{\gamma}+\tau \right)-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}+\tau \,\xi _{\mathrm{2t}}\right)}^2} \\
\alpha_s \xi_{2t}^2 (c_1 - \gamma + \tau) &= \alpha_s c_2 \xi_1t \xi_2t
 \\
\xi_{2t} (c_1 - \gamma + \tau) &=  c_2 \xi_{1t}\\
\tau &= 
\gamma - c_1 + (c_2\,\xi_{1t})/\xi_{2t}
\end{align*}
\end{proof}

\pagebreak

\pagebreak

\section{Notes}

\begin{itemize}
	\item The portfolio max with the heterogeneous time model is not always equivalent to the portfolio max in a one-period model. So, it does not min the variance of aggregate electricity output either.  Consequently, one-period optimization papers are problematic; if consumers prefer electricity more during certain points of the day, a one-period model will give suboptimal results.
	\item 
\end{itemize}

\pagebreak

%\subsection{MRS}
%
%Next, consider the marginal utility of $X_1$:
%\begin{equation}
%\frac{\partial U^\phi}{\partial X_1}  = \int_0^1 \alpha(t) \, \phi \, Y(t)^{\phi - 1} \xi_1(t) \, dt  = \frac{\partial U^\phi}{\partial U}  \frac{\partial U}{\partial X_1} 
%\end{equation}
%The marginal rate of substitution must then be:
%\begin{equation}
%MRS_{12} =  \frac{ \int_0^1 \alpha(t) \, Y(t)^{\phi - 1} \, \xi_1(t) \, dt }{ \int_0^1 \alpha(t) \, Y(t)^{\phi - 1} \, \xi_2(t) \, dt }
%\end{equation}
%Because $Y(t)$ is a function of $X_1$ and $X_2$, we have:
%\begin{equation}
%\phi = 1 \implies \frac{\partial MRS_{21}}{\partial X_1 / X_2} = 0 
%\end{equation}
%This further implies that the elasticity of substitution between $X_1$ and $X_2$ approaches infinity, hence the two inputs would become perfect substitutes. 
%
%% Now, suppose that we have $\xi_1(t) \neq \xi_2(t)$, so our inputs differ in their electricity generation.
%	
%

\pagebreak

\pagebreak

\section{Scratch}

\begin{align*}
\partial X / \partial \xi_{1,t} &= \left(\begin{array}{c} \frac{\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}\\ -\frac{\alpha _{s}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}-\frac{\alpha _{s}\,c_{2}\,\xi _{\mathrm{1t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} \end{array}\right) \\
\partial X / \partial \xi_{1,s} &= \left(\begin{array}{c} \frac{\alpha _{t}\,c_{2}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}\\ -\frac{\alpha _{t}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}-\frac{\alpha _{t}\,c_{2}\,\xi _{\mathrm{1s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} \end{array}\right)\\
\partial X / \partial \xi_{2,t} &= \left(\begin{array}{c} \frac{\alpha _{s}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}-\frac{\alpha _{s}\,c_{1}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}\\ \frac{\alpha _{s}\,c_{1}\,\xi _{\mathrm{1t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} \end{array}\right)\\
\partial X / \partial \xi_{2,s} &= \left(\begin{array}{c} \frac{\alpha _{t}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}-\frac{\alpha _{t}\,c_{1}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}\\ \frac{\alpha _{t}\,c_{1}\,\xi _{\mathrm{1s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} \end{array}\right)\\
\partial X / \partial c_{1} &= \left(\begin{array}{c} -\frac{\alpha _{t}\,{\xi _{\mathrm{2s}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}-\frac{\alpha _{s}\,{\xi _{\mathrm{2t}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}\\ \frac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}+\frac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} \end{array}\right) \\
\partial X / \partial c_2 &= \left(\begin{array}{c} \frac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}+\frac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}\\ -\frac{\alpha _{t}\,{\xi _{\mathrm{1s}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}-\frac{\alpha _{s}\,{\xi _{\mathrm{1t}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} \end{array}\right)
\end{align*}

\begin{align*}
\partial P / \partial \xi_{1,t} &= \left(\begin{array}{c} -\frac{\xi _{\mathrm{2s}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2}\\ \frac{\xi _{\mathrm{2s}}\,\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2}-\frac{c_{2}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}} \end{array}\right)\\
\partial P / \partial \xi_{1,s} &= \left(\begin{array}{c} \frac{c_{2}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}+\frac{\xi _{\mathrm{2t}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2}\\ -\frac{\xi _{\mathrm{2t}}\,\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2} \end{array}\right)\\
\partial P / \partial \xi_{2,t} &= \left(\begin{array}{c} \frac{\xi _{\mathrm{1s}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2}\\ \frac{c_{1}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}-\frac{\xi _{\mathrm{1s}}\,\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2} \end{array}\right) \\
\partial P / \partial \xi_{2,s} &= \left(\begin{array}{c} -\frac{c_{1}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}-\frac{\xi _{\mathrm{1t}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2}\\ \frac{\xi _{\mathrm{1t}}\,\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2} \end{array}\right) \\
\partial P / \partial c_1 &= \left(\begin{array}{c} -\frac{\xi _{\mathrm{2s}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}\\ \frac{\xi _{\mathrm{2t}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}} \end{array}\right)\\
\partial P / \partial c_2 &= \left(\begin{array}{c} \frac{\xi _{\mathrm{1s}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}\\ -\frac{\xi _{\mathrm{1t}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}} \end{array}\right)
\end{align*}

$$ \partial P_s / \partial \xi_{1,t} < 0 \iff  \frac{\xi _{\mathrm{2t}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2}<0$$

\pagebreak

\section{Literature}

\begin{itemize}
	\item \cite{Delarue} develop a model that distinguishes between power and energy in order to split up costs and risks into fixed and variable factors. 
	\item \cite{SB2018} look at interactions between different solar and wind installations (covar matrix), while many other energy models do not.
\end{itemize}

	\begin{thebibliography}{9}

		\bibitem[Delarue et al.(2010)]{Delarue}
		Delarue, E., De Jonghe, C., Belmans, R., \& D’Haeseleer, W. (2010). Applying portfolio theory to the electricity sector: Energy versus power. Energy Economics, 33(1), 12–23. https://doi.org/10.1016/j.eneco.2010.05.003

		\bibitem[Shahriari and Blumsack (2018)]{SB2018}
		Shahriari, M., \& Blumsack, S. (2018). The capacity value of optimal wind and solar portfolios. Energy, 148, 992–1005. https://doi.org/10.1016/j.energy.2017.12.121

		\bibitem[Ambec and Crampes (2012)]{AC2012}
		Ambec, S., \& Crampes, C. (2012). Electricity provision with intermittent sources of energy. Resource and Energy Economics, 34(3), 319–336. https://doi.org/10.1016/j.reseneeco.2012.01.001

		\bibitem[Borenstein (2012)]{Boren2012}
		Borenstein, S. (2012). The Private and Public Economics of Renewable Electricity Generation. Journal of Economic Perspectives, 26(1), 67–92. https://doi.org/10.1257/jep.26.1.67

		\bibitem[Chao (2011)]{Chao2011}
		Chao, H. (2011). Efficient pricing and investment in electricity markets with intermittent resources. Energy Policy, 39(7), 3945–3953. https://doi.org/10.1016/j.enpol.2011.01.010

		\bibitem[Electricity Information Administration (2019)]{EIA2019}
		Electricity Information Administration (2019). Net generation, United States, all sectors, annual. Electricity Data Browser. https://www.eia.gov/electricity/data/browser

		\bibitem[Joskow (2011)]{Joskow2011}
		Joskow, P. (2011). Comparing the Costs of Intermittent and Dispatchable Electricity Generating Technologies. American Economic Review, 101(3), 238–241. https://doi.org/10.1257/aer.101.3.238

		\bibitem[Musgens and Neuhoff (2006)]{MG2006}
		Musgens, F., \& Neuhoff, K. (2006). Modelling Dynamic Constraints in Electricity Markets and the Costs of Uncertain Wind Output. Faculty of Economics.

		\bibitem[Neuhoff et al. (2007)]{NCK2007}
		Neuhoff, K., Cust, J. \& Keats, K. (2007). Implications of intermittency and transmission constraints for renewables deployment. Cambridge Working Papers in Economics 0711, Faculty of Economics, University of Cambridge.

%		\bibitem[Angel, Harris, and Spatt(2011)]{Angel} 
%		Angel, J.J., Harris, L.E., \& Spatt, C. S. (2011). Equity Trading in the 21st Century. Quarterly Journal Of Finance, 1(1), 1-53.

%		\bibitem[Stern(2012)]{Stern} 
%		Stern, D. (2012). “Interfuel Substitution: A Meta-Analysis.” Journal of Economic Surveys 26 (2): 307–331. \href{https://doi.org/10.1111/j.1467-6419.2010.00646.x}{https://doi.org/10.1111/j.1467-6419.2010.00646.x}.

$-\alpha _{t}\,{c_{2}}^2\,{\xi _{1}}^2\,\xi _{\mathrm{2s}}\,\left(c_{2}\,\xi _{1}-c_{1}\,\xi _{\mathrm{2s}}+\mathrm{gamma}\,\xi _{\mathrm{2s}}-\xi _{\mathrm{2s}}\,z\right)$

	\end{thebibliography}

\end{document}

### 2019-04-19 documents/methodology_balance.tex
Remove pdf files and include tex files

\documentclass[12pt]{article}

\usepackage{amssymb,amsmath,amsfonts,eurosym,geometry,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,natbib,pdflscape,subfigure,array,hyperref,booktabs,float, multirow, pbox, rotating, adjustbox, caption}
\usepackage[colorinlistoftodos, textsize = footnotesize]{todonotes}

\normalem

%\onehalfspacing
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}{Proposition}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\newtheorem{hyp}{Hypothesis}
\newtheorem{subhyp}{Hypothesis}[hyp]
\renewcommand{\thesubhyp}{\thehyp\alph{subhyp}}

\newcommand{\red}[1]{{\color{red} #1}}
\newcommand{\blue}[1]{{\color{blue} #1}}
\definecolor{darkblue}{rgb}{0.0,0.0,0.5}

% hyperlinks
\hypersetup{
	colorlinks= true,
	linkcolor = darkblue,
	urlcolor  = darkblue,
	citecolor = darkblue,
	anchorcolor = blue
}

\newcolumntype{L}[1]{>{\raggedright\let\newline\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\arraybackslash\hspace{0pt}}m{#1}}

\geometry{left=1.0in,right=1.0in,top=1.0in,bottom=1.0in}

\begin{document}

	\section{Balancing Methodology}

	The primary goal of balancing the SAM is to bring the row and column totals to equivalent values. Additionally, we would also prefer that the entries of the balanced SAM remain similar to their original values in order to keep the values realistic. To do both, we must define an objective function that contains a penalty term for each.

	\subsection{Residual Penalty}

	We start by defining a penalty term for the difference in row and column totals. Firstly, our function should penalize negative differences by the same amount as positive differences. Additionally, we want larger differences to be penalized at an increasing rate. Defining our original SAM as $S_{(A)}$ and our balanced SAM as $S_{(B)}$, we may use the L2 norm of the row and column differences:
	$$\left\| S_{(B)} \textbf{1} - S_{(B)}^T \textbf{1} \right\|_2$$ 
	That is, we subtract the row totals,  $S_{(B)} \textbf{1}$, by the column totals, $S^T_{(B)} \textbf{1}$, and then sum the squares of each difference. However, we also want to penalize differences independently from the scale of the SAM; so, for instance, if all the entries were halved, this penalty term should not change. Defining $\mu_A$ as the average of the entries in the original SAM and $\mu_B$ as that of the balanced SAM, we modify this function to:
	$$(\mu_A / \mu_B)^2 \cdot \left\| S_{(B)} \textbf{1} - S_{(B)}^T \textbf{1} \right\|_2$$ 
	This prevents the optimization algorithm from behaving inappropriately by trying to scale down the SAM to reduce this penalty term. From here on, we refer to this function as the residual penalty.

	\subsection{Change Penalty}

	Next, we define a penalty term for the change in the entries. Firstly, we must define change in the SAM using ratios, since the relationships in the SAM are generally defined in percentage terms. For example, given some arbitrary industry, we may want to keep the capital-labor ratio close to their original ratio in the SAM. If we approached this problem by directly taking the sum of squares, we may not keep this ratio constrained appropriately. That is, suppose the original values in the SAM for this particular industry were \$7 for transfers to capital and \$3 for transfers to labor. Changing these values to (\$5, \$3) would produce the same sum of squares error as would the values (\$7, \$5). However, in the first case, the ratio would be 29\% lower than the original ratio, while, in the latter case, the ratio would be 40\% lower. Hence, we need to approach penalizing change in a different way.

	Alternatively, we could compute, for each element, the difference ratio between the new and old values, and then minimize the sum of squares of these terms. To motivate this, let us first define the vector $A \in R^{n^2}$ where $n$ is the number of rows in our SAM; $A$ is a vector of the stacked columns of our original SAM $S_{(A)}$. Likewise, let us refer to $B$ as a vector representation of the balanced SAM. Now, suppose that our unbalanced SAM $A$ is equal to the true balanced SAM $B$ multiplied an normally-distributed error term. That is, the ratio between any arbitrary elements of the two SAMS is equal to:
	$$\forall i, \; B_{i} /A_{i} - 1=   \varepsilon \qquad \varepsilon \sim N(0,\sigma^2)$$
	The maximum likelihood estimator for this equation is equivalent to minimizing the following term:
	$$ \left\| B_{i} /A_{i} - \textbf{1} \right\|_2$$
	which is simply the sum of squares of the difference of the ratios from 1. Note that, because this penalty term targets change in the entries, this function puts its minimal penalty on letting $B = A$. Additionally, to accommodate the capital-labor ratio problem mentioned earlier, we are directly minimizing the change in ratios through this function; moreover, this is penalization at an increasing rate.  Finally, since each change in ratio is squared, positive and negative changes are penalized equally. In short, this function -- the change penalty -- achieves all of our goals.

	\subsection{Constraints}

	Also, we must include some basic constraints in our model. To start, zero entries must be constrained at zero; additionally, we should exclude zero entries from our change penalty function, since such cases would be undefined in terms of change. Additionally, we must constrain the sign of our entries to their original signs. Positive entries should stay positive and likewise for negative entries. Lastly, we may want some terms to remain the same. For example, we may have a case where knew that certain elements of our original SAM were correct. Hence, we would constrain those elements from changing.

	\subsection{Objective Function}

	Finally, we define our objective function as a combination of the change penalty and the residual penalty. By defining these two terms separately, we can construct a weighting scheme for each one in our objective function:
	\begin{align*} \min_{S_{(B)}} Z &= w_1 \left( (\mu_A / \mu_B)^2 \cdot \left\| S_{(B)} \textbf{1} - S_{(B)}^T \textbf{1} \right\|_2 \right) + w_2 \left( \left\| B_{i} /A_{i} - \textbf{1} \right\|_2 \right) \\
	\text{s.t.} \quad \text{sgn} \left( B_i \right) &=  \text{sgn} \left( A_i \right)   \quad  \forall \, i 
	\end{align*}
	Then, by setting the weights $w_1$ and $w_2$, we can implicitly define a tolerance for the amount of acceptable residual penalty. That is, we can run this optimization algorithm on the original SAM and increase $w_1$ until the residual penalty falls below a desired tolerance. So, overall, this algorithm keeps the balanced SAM close to its original values while producing a feasible SAM for the CGE.

\end{document}

### 2019-04-19 documents/methodology_elcsector.tex
Remove pdf files and include tex files

\documentclass[12pt,a4paper]{extarticle}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{booktabs} % for toprule, midrule and bottomrule
\usepackage{adjustbox}
\usepackage{amsmath}
\usepackage{bbold}
\usepackage{etoolbox}
\usepackage{setspace} % for \onehalfspacing and \singlespacing macros
\usepackage[hidelinks]{hyperref}
\usepackage{array}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{caption}
\usepackage{pdflscape}
\usepackage{caption}
\usepackage{tabularx}
\usepackage{authblk}
\usepackage{float}
\usepackage{siunitx}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage[authoryear]{natbib}
\usepackage{scrextend}
\usepackage{nicefrac}
\usepackage{enumitem}
%\usepackage{showframe}
%\usepackage{lipsum}

% set space
%\doublespacing

%% section headings
%\renewcommand{\thesection}{\Roman{section}.\hspace{-0.5em}}
%\renewcommand\thesubsection{\Alph{subsection}.\hspace{-0.5em}}
%\renewcommand\thesubsubsection{\hspace{-1em}}
%\newcommand{\subsubsubsection}[1]{\begin{center}{\textit{#1}}\end{center}}
%
%\titleformat{\section}
%{\bf\centering\large}{\thesection}{1em}{}
%
%\titleformat{\subsection}
%{\itshape\centering}{\thesubsection}{1em}{}
%
%\titleformat{\subsubsection}
%{\bf}{\thesubsubsection}{1em}{}

% unicode chars for plots
\DeclareUnicodeCharacter{2212}{$-$}

% booktabs
\setlength\heavyrulewidth{0.06em} % 0.01em> midrule

% images
\graphicspath{ {D:/Users/saketh/Documents/GitHub/BECCS-Case-Study/documents/exhibits/} }

% array
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

% caption set up
\captionsetup[table]{
	font = {sc},
	labelfont = {bf}
}

% sig stars
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}

% hyperlinks
\hypersetup{
	colorlinks=true,
	linkcolor = blue,
	urlcolor  = blue,
	citecolor = blue,
	anchorcolor = blue
}

% bibliography
\makeatletter
\renewenvironment{thebibliography}[1]
{\section*{References}%
	\@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}%
	\list{}%
	{\setlength{\labelwidth}{0pt}%
		\setlength{\labelsep}{0pt}%
		\setlength{\leftmargin}{\parindent}%
		\setlength{\itemindent}{-\parindent}%
		\@openbib@code
		\usecounter{enumiv}}%
	\sloppy
	\clubpenalty4000
	\@clubpenalty \clubpenalty
	\widowpenalty4000%
	\sfcode`\.\@m}
{\def\@noitemerr
	{\@latex@warning{Empty `thebibliography' environment}}%
	\endlist}
\makeatother

% etoolbox
\AtBeginEnvironment{quote}{\singlespacing}

\begin{document}

%	\title{\singlespacing{\textbf{%%%}}}
%	
%   \author[]{Saketh Aleti}
%	
%	\affil[]{\small{%%%}}
%	
%	\date{\vspace{-1em}\small{%%%}}
%	
%	\maketitle

\section{Electricity Sector Construction}

\subsection{Producers}

Electricity production for technologies that handle base load demand generally consists of a fixed amount of capital with operating costs proportional to the amount of electricity being produced. On the other hand, renewable sources that produce intermittently only require fixed capital investments with little to no operating costs. In order to model both, we split up the traditional model of electricity production into two components: a fixed capacity investment and a variable production component. For example, suppose we are studying two technologies: coal and solar. The capacity of coal is represented by  $Z_{coal}$ while the capacity of solar is $Z_{solar}$. These values are proportional the amount of generating sources, such as coal factories and solar power plants, for each technology. Moreover, we let this capacity be determined by a CES function of intermediate inputs and factors:
$$ Z_{i} =  CES( X_{1,i}, \dots, X_{n,i}, F_{1,i}, \dots, F_{m,i})$$
where $X_{j,i}$ is the use of intermediate good $j$ and  $F_{k,i}$ which represents the use of factor input $k$; we assume here that there are $n$ total intermediate goods and $m$ factors. The capacity, $Z_{i}$, represents the maximum amount of electricity that we can produce in each period of our model.  Next, to model the actual production of electricity in each period $t$, we use two separate functions. One function is used to model production for technologies that can modify their output and another is used for intermittent technologies.

First, with respect to reliable energy, we can choose when and how much to produce, but we face costs such as labor and fuel. Hence, for technologies with modifiable generation, the total quantity of electricity produced at time $t$ is then given by:
$$ Z_{elc, i, t} = \min \left\{ Z_{i}, \; CES \left( X_{1,i^*,t}, \dots, X_{n,i^*,t}, F_{1,i^*,t}, \dots, F_{m,i^*,t} \right) \right\}$$
where $i^*$ is simply an index that denotes generation from technology $i$ rather than capacity; so, for instance, $i^*$ may be coal generation while $i$ would be coal capacity. Thus, $X_{j,i^*,t}$ represents the use of intermediate good $j$ for the generation of electricity through source $i$ in period $t$ and likewise for $F_{k,i^*,t}$. Now, as an example, consider the above function as modeling coal energy. The function implies that the maximum amount of coal-sourced electricity we can produce is equal to the capacity of coal factories; the amount that we actually produce is equal to a CES function of the inputs required to operate the factories. Thus, electricity generation in any period $t$ is constrained by our initial capacity investment, while generation in each period consumes resources proportional to the amount of electricity generated. A similar function is used for other technologies that can be turned on or off; these include BECCS, nuclear power, geothermal power, and hydro power. In each case, there exists a capacity constraint and the option to modify the quantity of electricity generation; the cost of this option varies by technology -- it may be inexpensive for hydro but far is more expensive for nuclear.

On the other hand, with respect to intermittent sources such as solar, we are unable to choose when these technologies generate energy. Hence, the production from these technologies must be modeled differently. We model electricity generation from intermittent source $i$ in period $t$ as:
\begin{align*}
Z_{elc, i, t} &= f_i(t) \cdot Z_{i} \\
f_i(t) &\in [0,1]
\end{align*} 
where $f_i(t)$ determines the percent of capacity used by technology $i$ in period $t$. So, for example, $f_{solar}$ would be closer to $1$ during the summer than the winter; similarly wind follows seasonal patterns that can be modeled through this function. Additionally, since total output still scales based on available capacity, firms continue to optimize the total amount of investment in intermittent renewable technology on a yearly basis. However, the drawback is that they cannot choose when and how much to produce at any particular time. So, while utilized capacity is a decision variable for reliable technologies, it is instead an exogenous parameter for intermittent sources of energy.

Finally, since electricity generation by different sources is completely substitutable within each period, we let total electricity generation at time $t$ be given by:
$$Z_{elc,t} = \sum_i Z_{elc,i,t}$$
where $i$ is each technology producing electricity. Consumers ultimately only interact with this value, since the utility they receive from electricity consumption is independent of that electricity's source.

\subsection{Consumers}

We model consumer welfare from electricity with two key factors in mind. Firstly, the utility people receive from consuming electricity varies over time due to seasonal effects. Secondly, people can choose to substitute between electricity consumption in one period for that in another. To account for this, we use a CES function composed of electricity consumption at different points in time; this function returns the total utility gained from electricity consumption while capturing seasonal variation in electricity consumption utility and substitution between electricity consumption over time. Then, we use another CES function to determine utility gained from the consumption of all goods; this is a standard approach in CGE models. And, lastly, we let total utility be the CES of utility from electricity consumption and that from the consumption of other goods.  
That is, our representative household's utility is given by:
$$U =   \left( \sum_{i \neq elc} \alpha_{i} Z_{i}^\eta +  \alpha_{elc} \left( \sum_{t=1}^T \alpha_{elc,t} Z_{elc, t}^\phi \right)^{\eta/\phi} \right)^{1/\eta}$$
where $U$ is total utility, , $\beta$ is a scale parameter, $\alpha_{elc,t}$ is a share parameter that models time-dependent differences in utility gained from electricity consumption, and $\sigma = 1 / (1-\phi)$ is the intertemporal elasticity of substitution. Similarly, $\alpha_i$ is a share parameter for all goods and $\xi = 1 / (1-\eta)$ is the elasticity of substitution for all consumption.

Because electricity consumption is differentiated by time, the elasticity parameter $\sigma$ captures our representative household's willingness to temporally shift electricity consumption in response to prices.  Since electricity consumption in one period is not a perfect substitute for that in another period, we have $\sigma < 1$ which implies that intermittent sources alone are not optimal for handling electricity demand. Hence, producers will maximize profit by balancing electricity generation through the day. This leads to different, implicit relationships between generation technologies. Firstly, reliable sources act as substitutes for one another, since one reliable source can easily generate electricity at the same time as another. On the other hand, intermittent sources may be either complements or substitutes with one another depending on the timing of their generation. Intermittent sources that produce at the same time will likely substitute for each other, while those that produce at different times may function as complements. Lastly, intermittent and reliable sources will generally be complements, since reliable sources can fill the gaps between intermittent generation. So, for example, wind and hydro will complement one another since gaps in the output of wind can be covered by modifying hydro generation. All in all, we are able model substitution/complementary relationships between different energy technologies by realistically modeling intermittency and reliability on the supply side and consumer welfare on the demand side.

\section{ Regression Methodology}

\subsection{Theoretical Derivation}

We aim to estimate $\sigma = 1/(1-\phi)$ which is the intertemporal elasticity of substitution for electricity consumption. We begin by considering the representative household described in the previous section; it maximizes utility given the budget constraint 
$$B = \sum_t P_{elc,t} + \sum_{i \neq elc} P_i $$
where $P_i$ is the price of good $i$ and $P_{elc,t}$ is the price of electricity at time $t$; the budget constraint is simply the cost of electricity consumption plus non-electricity consumption. Note that the derivative of logged utility is:
$$ \frac{\partial \log(U)}{\partial Z_{elc,t}} = \left( \alpha_{elc} \alpha_{elc,t} Z_{elc,t}^{\phi - 1}  \left( \sum_{t=1}^T \alpha_{elc,t} Z_{elc, t}^\phi \right)^{\eta/\phi -1} \right) / U^\eta$$
Now, solving the Lagrangian to maximize log utility while constrained by the budget, we find that the FOC for electricity consumption in particular is:
\begin{align*}\frac{Z_{elc, t}}{ Z_{elc, s}} &=  \left( \frac{\alpha_{elc,t} P_s}{\alpha_{elc,s} P_t}  \right)^{\sigma} 
\end{align*}
where $t$ refers to a particular month. Taking logs on both sides and letting $i$ represent different observations, we can estimate this function as 
\begin{align*}
\ln (Z_{elc, t, i} / Z_{elc, s, i}) &= -\sigma \ln (P_{t,i} / P_{s,i}) + \sigma \ln (\alpha_{t,i} / \alpha_{s,i}) 
\end{align*}
where $\alpha_{t,i}$ is equivalent to $\alpha_{elc,t}$ for a particular observation. Our data differentiates consumption for each state in the US, so we let $i$ refer to a particular state. Additionally, most consumers pay monthly fixed rates for electricity, so we can, at most, estimate this equation on a monthly basis; hence, $t$ and $s$ refer to different months. Lastly, note that the state $i$ is kept constant for each observation; this is because consumers within each state can substitute consumption across time, but consumers in different states do not substitute consumption with one another.

\subsection{Estimation and Identification}

In order to estimate this $\sigma$, we further modify the previous equation. 
Firstly, note that we cannot observe the demand shifter $\alpha_{t,i}$ directly, so we add a set of controls that may cause shifts in demand. Our regression is then
\begin{align*}
\ln (Z_{elc, t, i} / Z_{elc, s, i}) &= -\sigma \ln (P_{t,i} / P_{s,i}) +  \gamma_{t,i} A_{t,i} + \gamma_{s,i} A_{s,i} + u_i
\end{align*}
where $A$ represents set of controls for changes in demand while $u_i$ is a normal error term. Note that the control  $A_{t,i}$ replaces $\sigma \ln(\alpha_{t,i})$ and likewise for the period $s$ term; this substitution is valid because the $\ln(\alpha_{t,i}) \in \mathbb{R}$ and the $\sigma$ is simply absorbed into the estimated coefficient for $\gamma_{t,i}$. For the demand controls themselves, we choose to use heating (HDD) and cooling degree days (CDD) due to the aggregation of the data. That is, a more general control such as average temperature would not be able to directly capture intramonthly changes in demand, since variation in temperature would be lost when aggregated; on the other hand, CDDs and HDDs directly represent daily deviations in temperature even when totaled for each month. Additionally, demand for electricity may rise over time. Hence, we include, as a control, the difference in months between time $t$ and $s$; this is represented by $\Delta_{t,s}$. Finally, this panel requires us to consider fixed effects for each state, so we use a fixed effects panel regression. In total, the demand equation is:
\begin{align*}
\ln (Z_{elc, t, i} / Z_{elc, s, i}) &= -\sigma \ln (P_{t,i} / P_{s,i}) +  \gamma_{t,i} A_{t,i} + \gamma_{s,i} A_{s,i} + \eta \Delta_{t,s} + u_i \\
&= -\sigma \ln (P_{t,i} / P_{s,i}) +  \gamma_{t,i} \left( CDD_{t,i} + HDD{t,i} \right) \\
&\qquad + \gamma_{s,i} \left( CDD_{s,i} + HDD{s,i} \right)  + \eta \Delta_{t,s} + u_i
\end{align*}

Still, this equation may suffer from bias, since producers can also substitute production over time. For instance, it is possible to store fuel for electricity generation in the future when prices may rise. So, we define the following supply equation
\begin{align*}
\ln (Z_{elc, t, i} / Z_{elc, s, i}) &= \beta \ln (P_{t,i} / P_{s,i}) + \xi \ln (C_{t,i} / C_{s,i}) + v_{i}
\end{align*}
where $C_{t,i}$ is the average cost of coal used for electricity generation in state $i$ at time $t$ and $v_i$ is a normal error term. Coal prices are independent of the electricity demand error term $u_i$, since residential consumers do not generally use coal for electricity generation; on the other hand, shocks in the price of coal are linked with the supply of electricity. Hence, coal price is a theoretically valid instrument.  In total, the reduced form equation is given by:
$$ \ln (P_{t,i} / P_{s,i}) = \left( \beta + \sigma \right)^{-1} \left( \gamma_{t,i} A_{t,i} + \gamma_{s,i} A_{s,i} + \eta \Delta_{t,s} - \xi \ln (C_{t,i} / C_{s,i}) + u_{i} - v_i \right)  $$
where $A_{t,i}$ consists of CDDs and HDDs at time $t$.

Finally, we also consider a semiparametric specification. That is, we allow the error terms $u_i$ and $v_i$ to be non-normal and place the demand controls and instruments in unknown functions. So, overall, we have:
\begin{align*}
\ln (Z_{elc, t, i} / Z_{elc, s, i}) &= -\sigma \ln (P_{t,i} / P_{s,i}) +  f \left( A_{t,i}, A_{s,i}, \Delta_{t,s} \right) + u_i \\
\ln (Z_{elc, t, i} / Z_{elc, s, i}) &= \beta \ln (P_{t,i} / P_{s,i}) + g \left( \ln (C_{t,i} / C_{s,i})  \right) + v_{i}
\end{align*}
where $f$ and $g$ are unknown, bounded functions. We restrict $cov(u_i, v_i) = 0$ but allow for the controls and instruments to be correlated. The advantage of this specification is that we can account for the controls or instrument having any nonlinear effects on the regressands. \textbf{(More here on explaining the estimation)}

\subsection{Data}

We collect monthly data from the EIA on retail electricity prices and consumption for each state in the US from 2011 to 2018. Additionally, also from the EIA, we collect monthly data on the average cost of coal for electricity generation. The coal price data set contains a large number of missing values due to privacy reasons; however, we do not expect that these missing values are correlated with the data itself. Finally, we collect data on HDDs and CDDs from the NCEP for the same panel. Then, we merge these three data sets and trim 1\% of outliers for a total of $826$ observations. We use this preliminary data set to construct the data required for our regressions. That is, each observation in our estimation equation belongs to a set $(t,s,i)$ consisting of two time periods and a state. Hence, we construct each row in our regression data set using unique combinations of $t,s$ where $t \neq s$ for each state $i$. Due to the number of potential combinations and thus observations, we restrict our data set to a random sample of 9000 observations.\footnote{We reran our regressions with several different samples of 9000 and found that our estimated coefficients did not significantly change; hence we believe this sample size is sufficient.}

\subsection{Results}

Based on the OLS results reported in \hyperref[table:1]{Table 1}, we estimate the intertemporal elasticity of substitution for electricity consumption $\hat{\sigma}  = 0.609$ ($|t| > 24$) when accounting for all degree day covariates and state fixed effects. Interestingly, we find that the estimated coefficients for all three specifications do not differ when considering fixed effects. Additionally, as expected, the coefficients on the degree day covariates are symmetrical; that is, the coefficient on $CDD_{t}$ is approximately the same as the negative of that on $CDD_{s}$, and the same applies to $HDD_{t}$ and $HDD_{s}$. On the other hand, we found that electricity consumption seems to rise more in response to CDDs rather than HDDs. Lastly, we find that the sign on $\Delta_{t,s}$ is positive in all regressions; this implies that electricity consumption rises over time independent of price.

To account for endogeneity in the OLS results, we provide results for our IV specification in \hyperref[table:2]{Table 2}. Here, we find a much larger estimate $\hat{\sigma}  = 11.430$ ($|t| > 2.1$) when considering all covariates and fixed effects. F-Statistics on all three specifications are significantly larger than 10, which suggests that the instruments are not weak \citep{SS1997}. With respect to the demand controls, we find results similar to those of OLS. State fixed effects do not appear to affect the estimates, demand increases over time, and CDDs raise electricity consumption more than HDDs.

Finally, we control for nonlinear effects using a partially linear IV regression reported in \hyperref[table:3]{Table 3}. Here, we find results similar to that of OLS; $\hat{\sigma} = 0.413$ ($|t| > 48$) when considering all controls. The estimate of $\sigma$ without any controls is not significantly different from that in specifications with controls. However, all of these estimates are significantly different from the IV results; hence, the IV regressions do not appear to be robust. Consequently, we opt to use these estimates of $\sigma$ in our model. Since these estimates show $\hat{\sigma} \in (0,1)$, it appears that electricity consumption in different months complement one another.

\begin{table}[!htbp] \centering 
	\caption{OLS Regression Results}
	\label{table:1} 
	\small
	\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
		\\[-4ex]\hline  
		\hline \\[-1.8ex] 
		& \multicolumn{6}{c}{\textit{Dependent variable:} $\ln (Z_{elc, t, i} / Z_{elc, s, i})$} \\ [0.5ex]
		\cline{2-7} 
		\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ [0.5ex]
		\hline \\[-1.8ex] 
		$-\ln (P_{t,i} / P_{s,i})$ & 0.751$^{***}$ & 0.481$^{***}$ & 0.607$^{***}$ & 0.750$^{***}$ & 0.481$^{**}$ & 0.607$^{***}$ \\ 
		& (0.030) & (0.026) & (0.026) & (0.224) & (0.172) & (0.169) \\ 
		& & & & & & \\ 
		$\Delta_{t,s}$ &  &  & 0.001$^{***}$ &  &  & 0.001$^{***}$ \\ 
		&  &  & (0.0001) &  &  & (0.0002) \\ 
		& & & & & & \\ 
		CDD$_t$ &  & 0.990$^{***}$ & 1.003$^{***}$ &  & 0.990$^{***}$ & 1.002$^{***}$ \\ 
		$\quad(\times 1000^{-1})$&  & (0.016) & (0.016) &  & (0.087) & (0.086) \\ 
		& & & & & & \\ 
		CDD$_s$ &  & $-$0.999$^{***}$ & $-$1.011$^{***}$ &  & $-$0.999$^{***}$ & $-$1.012$^{***}$ \\ 
		$\quad(\times 1000^{-1})$&  & (0.016) & (0.016) &  & (0.087) & (0.085) \\ 
		& & & & & & \\ 
		HDD$_t$ &  & 0.306$^{***}$ & 0.294$^{***}$ &  & 0.307$^{***}$ & 0.295$^{***}$ \\ 
		$\quad(\times 1000^{-1})$&  & (0.005) & (0.005) &  & (0.030) & (0.030) \\ 
		& & & & & & \\ 
		HDD$_s$ &  & $-$0.309$^{***}$ & $-$0.296$^{***}$ &  & $-$0.308$^{***}$ & $-$0.295$^{***}$ \\ 
		$\quad(\times 1000^{-1})$&  & (0.005) & (0.005) &  & (0.029) & (0.029) \\ 
		& & & & & & \\ 
		Intercept & 0.001 & 0.002 & 0.002 &  &  &  \\ 
		& (0.003) & (0.006) & (0.006) &  &  &  \\ 
		& & & & & & \\  [0.9ex]
		\hline \\[-1.8ex] 
		State FEs &   &   &   & Yes & Yes & Yes \\ 
		Observations & 9,000 & 9,000 & 9,000 & 9,000 & 9,000 & 9,000 \\ 
		R$^{2}$ & 0.070 & 0.580 & 0.596 & 0.070 & 0.580 & 0.596 \\ 
		Adjusted R$^{2}$ & 0.070 & 0.579 & 0.596 & 0.065 & 0.577 & 0.594 \\ [0.5ex]
		\hline 
		\hline \\[-1.8ex] 
		\multicolumn{7}{@{}p{40em}@{}}{\textit{Note: } The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$. The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state; as discussed in the Data section, we take a random sample of 9000 observations from the data. The coefficient on $\ln (P_{t,i} / P_{s,i})$ is an estimate of $-\sigma$. The variable $\Delta_{t,s}$ is the difference in months between periods $t$ and $s$. CDD$_t$ and HDD$_t$ refer to the total number of heating and cooling degree days in month $t$. Robust standard errors are reported in parentheses. *p$\textless$0.05, **p$\textless$0.01, ***p$\textless$0.001}  \\ 
	\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
	\caption{IV (2SLS) Regression Results}
	\label{table:2} 
	\small
	\begin{tabular}{@{\extracolsep{4pt}}lcccccc} 
		\\[-4ex]\hline  
		\hline \\[-1.6ex] 
		& \multicolumn{3}{c}{First-Stage} & \multicolumn{3}{c}{Second-Stage} \\ [0.5ex]
		& \multicolumn{3}{c}{\textit{Dep. Variable:} $\ln (P_{t,i} / P_{s,i})$ } & \multicolumn{3}{c}{\textit{Dep. Variable:}  $\ln (Z_{elc, t, i} / Z_{elc, s, i})$}\\ [0.5ex]
		\cmidrule(lr){2-4} \cmidrule(lr){5-7}\\[-2.2ex] 
		& (A.1) & (B.1) & (C.1) & (A.2) & (B.2) & (C.2)\\ [0.5ex]
		\hline \\[-1.8ex] 
		$ \ln (C_{t,i} / C_{s,i})$ & $-$0.060$^{***}$ & 0.004$^{*}$ & 0.004$^{*}$ &  &  &  \\ 
		& (0.002) & (0.002) & (0.002) &  &  &  \\ 
		& & & & & & \\ 
		$-\ln (P_{t,i} / P_{s,i})$ &  &  &  & 0.711$^{***}$ & 13.987 & 11.430$^{*}$ \\ 
		&  &  &  & (0.106) & (8.384) & (5.330) \\ 
		& & & & & & \\ 
		$\Delta_{t,s}$  &  & 0.001$^{***}$ & 0.001$^{***}$ &  &  & 0.007$^{*}$ \\ 
		&  & (0.00002) & (0.00002) &  &  & (0.003) \\ 
		& & & & & & \\ 
		CDD$_t$  &  & 0.151$^{***}$ & 0.151$^{***}$ &  & 3.064$^{*}$ & 2.620$^{**}$ \\ 
		$\quad(\times 1000^{-1})$&  & (0.007) & (0.007) &  & (1.288) & (0.798) \\ 
		& & & & & & \\ 
		CDD$_s$  &  & $-$0.149$^{***}$ & $-$0.149$^{***}$ &  & $-$3.034$^{*}$ & $-$2.609$^{***}$ \\ 
		$\quad(\times 1000^{-1})$&  & (0.007) & (0.007) &  & (1.264) & (0.788) \\ 
		& & & & & & \\ 
		HDD$_t$  &  & $-$0.057$^{***}$ & $-$0.057$^{***}$ &  & $-$0.407 & $-$0.311 \\ 
		$\quad(\times 1000^{-1})$&  & (0.003) & (0.003) &  & (0.447) & (0.301) \\ 
		& & & & & & \\ 
		HDD$_s$  &  & 0.058$^{***}$ & 0.058$^{***}$ &  & 0.423 & 0.324 \\ 
		$\quad(\times 1000^{-1})$&  & (0.003) & (0.003) &  & (0.458) & (0.308) \\ [0.9ex]
		\hline \\[-1.8ex] 
		State FEs &  Yes & Yes  & Yes  & Yes & Yes & Yes \\ 
		Observations & 9,000 & 9,000 & 9,000 & 9,000 & 9,000 & 9,000 \\ 
		R$^{2}$          & 0.066 & 0.441 & 0.441 & & &  \\ 
		Adjusted R$^{2}$ & 0.066 & 0.441 & 0.441 & & &  \\ 
		F Statistic & 678$^{***}$ & 1,213$^{***}$ & 1,197$^{***}$  &  &  &  \\ 
		\hline 
		\hline \\[-1.8ex] 
		\multicolumn{7}{@{}p{39.2em}@{}}{\textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions. The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$. The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state; as discussed in the Data section, we take a random sample of 9000 observations from the data. The coefficient on $\ln (P_{t,i} / P_{s,i})$ is an estimate of $-\sigma$. The variable $\Delta_{t,s}$ is the difference in months between periods $t$ and $s$. CDD$_t$ and HDD$_t$ refer to the total number of heating and cooling degree days in month $t$. Robust standard errors are reported in parentheses. *p$\textless$0.05, **p$\textless$0.01, ***p$\textless$0.001}  \\ 
	\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
	\caption{Partially Linear IV Regression Results}
	\label{table:3} 
	\small
	\begin{tabular}{@{\extracolsep{4em}}lccc} 
		\\[-4ex]\hline  
		\hline \\[-1.8ex] 
		& \multicolumn{3}{c}{\textit{Instrument: $ \ln (C_{t,i} / C_{s,i})$}} \\ 
		\cline{2-4} 
		%\\[-1.8ex] & ln\_load\_rel \textasciitilde ln\_price\_rel & ln\_load\_rel \textasciitilde (CDD\_1) & ln\_load\_rel \textasciitilde time\_diff + (CDD\_1) \\ 
		\\[-1.8ex] & (1) & (2) & (3)\\ [0.5ex]
		\hline \\[-1.8ex] 
		$\hat{\sigma} $ & 0.5676$^{***}$ & 0.4511$^{***}$ & 0.4129$^{***}$ \\ 
		& (0.1036) & (0.0042) & (0.0085) \\ [0.9ex]
		\hline \\[-1.8ex] 
		Time Control &   &   & Yes  \\ 
		Degree Day Controls &   & Yes  & Yes  \\ 
		Observations & 9,000 & 9,000 & 9,000 \\
		\hline 
		\hline \\[-1.8ex] 
		\multicolumn{4}{@{}p{36em}@{}}{\textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions. The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$. The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state; as discussed in the Data section, we take a random sample of 9000 observations from the data. The estimation procedure is described in the appendix.  Robust standard errors are reported in parentheses. *p$\textless$0.05, **p$\textless$0.01, ***p$\textless$0.001}  \\ 
	\end{tabular} 
\end{table}

\pagebreak
\pagebreak
\pagebreak
\pagebreak
..

\section{Appendix}

\pagebreak

\begin{thebibliography}{9}

	%		\bibitem[Angel, Harris, and Spatt(2011)]{Angel} 
	%		Angel, J.J., Harris, L.E., \& Spatt, C. S. (2011). Equity Trading in the 21st Century. Quarterly Journal Of Finance, 1(1), 1-53.

	\bibitem[Staiger and Stock(1997)]{SS1997} 
	Staiger, D., \& Stock, J. (1997). Instrumental Variables Regression with Weak Instruments. Econometrica, 65(3), 557–586. https://doi.org/10.2307/2171753

\end{thebibliography}

\end{document}

### 2019-04-19 documents/notes.tex
Remove pdf files and include tex files

\documentclass[12pt,a4paper]{extarticle}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{booktabs} % for toprule, midrule and bottomrule
\usepackage{adjustbox}
\usepackage{amsmath}
\usepackage{bbold}
\usepackage{etoolbox}
\usepackage{setspace} % for \onehalfspacing and \singlespacing macros
\usepackage[hidelinks]{hyperref}
\usepackage{array}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{caption}
\usepackage{pdflscape}
\usepackage{caption}
\usepackage{tabularx}
\usepackage{authblk}
\usepackage{float}
\usepackage{siunitx}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage[authoryear]{natbib}
\usepackage{scrextend}
\usepackage{nicefrac}
\usepackage{enumitem}
%\usepackage{showframe}
%\usepackage{lipsum}

% set space
%\doublespacing

% section headings
\renewcommand{\thesection}{\Roman{section}.\hspace{-0.5em}}
\renewcommand\thesubsection{\Alph{subsection}.\hspace{-0.5em}}
\renewcommand\thesubsubsection{\hspace{-1em}}

\titleformat{\section}
{\bf\centering\large}{\thesection}{1em}{}

\titleformat{\subsection}
{\itshape\centering}{\thesubsection}{1em}{}

\titleformat{\subsubsection}
{\bf}{\thesubsubsection}{1em}{}

% unicode chars for plots
\DeclareUnicodeCharacter{2212}{$-$}

% booktabs
\setlength\heavyrulewidth{0.06em} % 0.01em> midrule

% images
\graphicspath{ {D:/Users/saketh/Documents/GitHub/BECCS-Case-Study/documents/exhibits/} }

% array
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

% caption set up
\captionsetup[table]{
	font = {sc},
	labelfont = {bf}
}

% sig stars
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}

% hyperlinks
\hypersetup{
	colorlinks=true,
	linkcolor = blue,
	urlcolor  = blue,
	citecolor = blue,
	anchorcolor = blue
}

% bibliography
\makeatletter
\renewenvironment{thebibliography}[1]
{\section*{References}%
	\@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}%
	\list{}%
	{\setlength{\labelwidth}{0pt}%
		\setlength{\labelsep}{0pt}%
		\setlength{\leftmargin}{\parindent}%
		\setlength{\itemindent}{-\parindent}%
		\@openbib@code
		\usecounter{enumiv}}%
	\sloppy
	\clubpenalty4000
	\@clubpenalty \clubpenalty
	\widowpenalty4000%
	\sfcode`\.\@m}
{\def\@noitemerr
	{\@latex@warning{Empty `thebibliography' environment}}%
	\endlist}
\makeatother

% etoolbox
\AtBeginEnvironment{quote}{\singlespacing}

\begin{document}

%	\title{\singlespacing{\textbf{%%%}}}
%	
%	\author[]{Saketh Aleti}
%	
%	\affil[]{\small{%%%}}
%	
%	\date{\vspace{-1em}\small{%%%}}
%	
%	\maketitle

\section{Literature Outline}

Two classifications for elasticities of substitution

\begin{itemize}
	\item \textbf{Gross/net elasticities}: 
	\begin{itemize}
		\item Net elasticities are computed holding output constant
		\item Gross elasticities are computed by letting output vary optimally (gross)
	\end{itemize}
	\item \textbf{Scalar, asymmetric ratio, or symmetric ratio elasticities}
	\begin{itemize}
		\item Scalar elasticities (Allen-Uzawa) measure the effect of a change in the price of another factor scaled by its cost share on the quantity of a factor demanded
		\item Asymmetric ratio elasticities (Morishima) measure the effect on the factor input ratio of a change in a ratio of prices
		\item Symmetric elasticities can be found by putting restrictions on asymmetric elasticities; holding cost constant on the Morishima elasticities produces the shadow elasticities of substitution
	\end{itemize} 
\end{itemize}

\subsection{Formulas}

\subsubsection{Translog}

Own price elasticities are given by:
$$\eta_{ii} = \frac{\partial \ln X_i(y, p)}{\partial \ln p_i} = \frac{\beta_{ii} + S_i^2 - S_i}{S_i}
\quad \implies \quad n_{ii}(1, \mathbb{1}) = \frac{\beta_{i,i} - \beta_i^2 - \beta_i}{\beta_i}$$
where $X_i$ is demand for input $i$, $p_i$ is its price, and $S_i$ is its predicted cost share. And, $B_{ij}$ is the second order parameter from the translog cost function, $y$ is the output, and $p$ is a vector of factor prices.

Cross price elasticities are given by:
$$\eta_{ij} = \frac{\partial \ln X_i(y, p)}{\partial \ln p_j} = \frac{B_{ij} + S_iS_j }{S_i}
\quad \implies \quad n_{ii}(1, \mathbb{1}) = \frac{\beta_{i,i} - \beta_{j}\beta_{i}}{\beta_i}$$
where $B_i$ is the first-order parameter of the translog cost function.

\subsubsection{Morishima}

The elasticity of substitution here is given by:
$$\mu_{ij} = \left. \frac{\partial \ln(X_j(y, p) / X_i(y,p))}{\partial \ln(p_i/p_j)} \right|_{p_j} = \eta_{ji} - \eta_{ii}$$

\subsubsection{Shadow}

The shadow elasticity of substitution is given by:
$$\sigma_{ij} = \left. \frac{\partial \ln(X_j(y, p) / X_i(y,p))}{\partial \ln(p_i/p_j)} \right|_{C} = \frac{S_i}{S_i + S_j} \mu_{ij} + \frac{S_j}{S_i + S_j} \mu_{ji}$$

\pagebreak

\section{Model of Electricity Production/Consumption}

\subsection{Formulation}

The model involves a consumer and producers reaching equilibrium in a two-period setting. The consumer maximizes a Cobb-Douglas utility function, and the producers allocate capital into two energy sources: one which provides a constant output and the other which generates an intermittent output. 
The producers' energy output, say kWh, at time $t$ is 
$$Y_t = \xi_{1,t} X_1 + \xi_{2,t} X_2$$
where $X_1$ is investment into the constant output source, $X_2$ is the investment into the intermittent output source, and $\xi_{i,t}$ is the conversion factor from input $X_i$ into kWh at time $t$. Referring to the next period as period $s$, we also have:
$$Y_s = \xi_{1,s} X_1 + \xi_{2,s} X_2$$
Since $X_1$ is a constant output source, $\xi_{1,t} = \xi_{1,s}$. And, since $X_2$ is an intermittent source, we may have $\xi_{2,t} > \xi_{2,s}$ without loss of generality. For example, $X_1$ may be coal and $X_2$ may be solar. Letting $\xi_{2,t} > \xi_{2,s}$  reflects the fact that the conversion rate from tons of coal to kWh is independent of the time of day, while the conversion rate for solar panels into kWh is higher during the day. 
Next, the cost of production for inputs $X_i$ is given by:
$$C(X_1, X_2) = p_1 (X_1 - c_1)^{\eta_1} + p_2 (X_2 - c_1)^{\eta_2}$$
where $p_i > 0$, $c_i > 0$, $\eta_i > 2$. When $\eta_i = 3$, this particular function has:
\begin{align*}
\partial C / \partial X_i &> 0 \\
\partial^2 C / \partial X_i^2 &< 0 \text{ when } X_i < c_i \\
\partial^2 C / \partial X_i^2 &> 0 \text{ when } X_i > c_i
\end{align*}
which shows concave costs followed by convex costs. That is, average cost initially decreases with production and then increases. This might be more realistic, but the following results can also be obtained with $c_i = 0$ and $\eta = 2$ which is a simpler model with linearly increasing average costs. 
Lastly, the producer has the following profit function:
$$\Pi = p_t Y_t + p_s Y_2 - C(X_1, X_2)$$
And, the consumer maximizes utility while constrained by their budget:
$$U = Y_t^\alpha \cdot Y_s^\beta$$
$$\text{s.t. }  p_t Y_t + p_s Y_2 \leq B$$

\subsection{Numerical Solution}

First, we assume that the social planner maximizes utility while keeping profit non-negative. Additionally, we keep all prices and quantities non-negative.

Optimizing a Cobb-Douglas function implies that the demand for energy is given by:
\begin{align*}
Q_{D, t} &= \alpha*B / p_t \\
Q_{D, s} &= \beta*B / p_s
\end{align*}
These demand functions maximize utility while ensuring the consumer budget constraint is satisfied.

The energy production functions remain the same:
\begin{align*}
Q_{S, t} &= \xi_{1,t} X_1 + \xi_{2,t} X_2 \\
Q_{S, s} &= \xi_{1,s} X_1 + \xi_{2,s} X_2
\end{align*}

But, the producer profit is now:
$$\Pi = p_t \min(Q_{D,t}, Q_{S,t}) + p_s \min(Q_{D,s}, Q_{S,s}) - C(X_1, X_2)$$

Running an optimization routine provides the following results:

\begin{center}
	\includegraphics[width=0.9\textwidth]{exhibits/model_v1_ex.png} 
\end{center}

Graphed above is $\ln(X_1/ X_2)$ versus $\ln(P_2/P_1)$. The blue line shows the results while the dashed orange line is an OLS fit. Similar to a CES function, this relationship is practically linear; error may be due to the optimization routine. The results were generated with $p_1 = 10, c_1 = 0.5, c_2 = 0.5, , \eta_1 = 3, \eta_2 = 3, \xi_{1,t} = 5, \xi_{1,s} = 5, \xi_{2,t} = 10, \xi_{2,s}  = 4, \alpha = 0.3, \beta = 0.7, B = 50$, and with $p_2$ allowed to vary over iterations from $7$ to $13$. That is, with:
\begin{align*}
U &= Y_t^{0.3} \cdot Y_s^{0.7} \\
p_t Y_t + p_s Y_2 &\leq 50 \\
Y_t &= 5 X_1 + 10 X_2 \\
Y_s &= 5 X_1 + 4 X_2 \\
C &= 10 (X_1 - 0.5)^{3} + p_2 (X_2 - 0.5)^{3}
\end{align*}

Running the routine again but with $\xi_{1,t} =  \xi_{1,s} = 6$, we get the following results:

\begin{center}
	\includegraphics[width=0.9\textwidth]{exhibits/model_v1_ex2.png} 
\end{center}

In the graph above, the yellow line is a second set of results obtained by modifiying $\xi$. We can see that the intercept has shifted without changing the slope very much ($<1\%$ change in the slope), which is similar to what would be seen with a CES model. That is, the optimization of a standard CES model would result in 
$$\ln(X_i/ X_j) = \sigma \ln(P_j / P_i) + \sigma \ln(\xi_i/ \xi_j)$$
where changes in $\xi$ would affect the intercept but not the slope (elasticity of substitution) $\sigma$ as seen in this two-period model. The estimated coefficient of the slope $\hat{\sigma}$ with these parameters is $0.3416$. This implies that the constant and intermittent energy sources are complements in energy production, which reflects reality since an intermittent source could not substitute well for a constant output source.

Part of the reason the model implies that they are complements may be due to the fact that the cost functions show increasing average cost, so it would be more expensive to completely substitute one for the other. However setting $\eta_1 = \eta_2 = 2$, results in $\hat{\sigma} = 0.6695$. The two are much weaker complements but still remain complements even if average cost is linearly increasing. Generally, as $\eta_i$ decreases, the elasticity of substitution rises and the two become increasingly better substitutes. On the other hand, when the output of the second source becomes more intermittent, when $\xi_{2_d} / \xi_{2_n}$ increases, the elasticity of substitution declines as expected.

Overall, this result - the near linear relationship between the log of inputs and prices - essentially implies that we could approximate a two-period model of electricity into a one-period model by using a CES production function. This is useful, because we do not have electricity output by source, hour, and state for 2016. Since modeling intermittency directly with a multi-period SAM would be impossible without data to estimate the parameters, a single period SAM with this theoretical approach would be more persuasive. Additionally, using a CES function without $\sigma \to \infty \iff \phi \to 1$ would always imply that 1 kWh from one source does not substitute for 1 kWh from another. When estimating the CES function: 
$$Y = \theta \cdot \left( \Pi_i \alpha_i X_i^\phi \right)^{1/\phi}$$
the estimates will always have $\hat{\theta} \to 1$, $\hat{\alpha_i}$ approaching the average conversion factors, and $\hat{\phi} \to 1$. When the electricity data comes from a single period, such as 2016 in our data, this must be the result; even theoretically this is true. For instance, this is true with the MATLAB simulation when aggregating the two-period model data into one period and fitting a CES function. We see $\theta \to 1$, $\phi \to 1$, and $\alpha_i \to (\xi_{i,t} + \xi_{i,s})/2$.  To get $\hat{\phi} \neq 1$ would be wrong in any single period model, but would make sense in a multi-period model. Implementing this in a CGE would still imply that 1 kWh of solar stops translating into 1 kWh of electricity when a shock occurs. But, this can make sense if we suppose reality follows a multi-period model and such a kWh of solar was just over-generated in one period as a result of optimal investment targeting all periods. So, starting from a multi-period theoretical foundation would better justify using $\phi \neq 1$ in the CGE.

\pagebreak	
%\section*{References}

\subsection{Centralized Approach}

\subsubsection{Cobb-Douglas Utility}

Firstly, the demand function for each commodity is derived from the Cobb-Douglas utility function. Hence, we have:
$$Y_t = (\alpha \cdot B)/p_t \qquad Y_s = (\beta \cdot B)/p_s$$
Therefore, the consumer surplus is given by:
$$\text{CS} = \int_{p_t}^{\infty} (\alpha \cdot B)/p \,dp \; + \; \int_{p_s}^{\infty} (\beta \cdot B)/p \,dp$$
Equivalently, using inverse demand, we have:
$$\text{CS} = \int_{0}^{Y_t} (\alpha \cdot B)/y \,dy \; + \; \int_{0}^{Y_s} (\beta \cdot B)/y \,dy$$
Producer surplus remains equivalent to profit; here I use a simple cost function. 
$$\text{PS} = \Pi = p_t Y_t + p_s Y_2 - ( p_1 X_1^2 + p_2 X_2^2)$$
Then, total welfare is $W = \text{PS} + \text{CS}$. So, we have:
$$\frac{\partial W}{\partial X_1} = \frac{\partial CS}{\partial X_1} + \frac{\partial PS}{\partial X_1} $$
Working with consumer surplus, we get:
\begin{align*}
CS &= (\alpha \cdot B) \cdot (\ln(Y_t) - \ln(0)) + (\beta \cdot B) \cdot (\ln(Y_s) - \ln(0)) \\
&\implies  \frac{\partial CS}{\partial X_1} = (\alpha \cdot B) \cdot (\xi_{1,t} / Y_t) + (\beta \cdot B) \cdot (\xi_{1,s} / Y_s)\\
&\implies  \frac{\partial CS}{\partial X_2} = (\alpha \cdot B) \cdot (\xi_{2,t} / Y_t) + (\beta \cdot B) \cdot (\xi_{2,s} / Y_s)
\end{align*}
And, for profit, we have:
$$ \frac{\partial PS}{\partial X_1} = p_t \cdot \xi_{1,t} + p_s \cdot \xi_{1,s} - 2\, p_1 X_1 $$
$$ \frac{\partial PS}{\partial X_2} = p_t \cdot \xi_{2,t} + p_s \cdot \xi_{2,s} - 2\, p_2 X_2 $$
Hence, the first-order conditions are:
\begin{align*}
\frac{\partial W}{\partial X_1} = 0 &\implies (\alpha \cdot B) \cdot (\xi_{1,t} / Y_t) + (\beta \cdot B) \cdot (\xi_{1,s} / Y_s) + p_t \cdot \xi_{1,t} + p_s \cdot \xi_{1,s} - 2\, p_1 X_1 = 0 \\
\frac{\partial W}{\partial X_2} = 0 &\implies (\alpha \cdot B) \cdot (\xi_{2,t} / Y_t) + (\beta \cdot B) \cdot (\xi_{2,s} / Y_s) + p_t \cdot \xi_{2,t} + p_s \cdot \xi_{2,s} - 2\, p_2 X_2 = 0
\end{align*}

\subsection{Decentralized Solution}

To restate the problem, we have production determined by:
$$Y_t = \xi_{1,t} X_1 + \xi_{2,t} X_2$$
$$Y_s = \xi_{1,s} X_1 + \xi_{2,s} X_2$$
with the cost function $C(X_1, X_2) = p_1 X_1^2 + p_2 X_2^2$. And, the consumer attempts to maximize their utility:
$$U = Y_t^\alpha \cdot Y_s^\beta$$  
subject to $p_t Y_t + p_s Y_s = B$.

\subsubsection{Cobb-Douglas Utility}

First, assume producers maximize profit. Then, we have:
\begin{align*}
\frac{\partial PS}{\partial X_1} &= p_t \cdot \xi_{1,t} + p_s \cdot \xi_{1,s} - 2\, p_1 X_1 = 0 \\
\frac{\partial PS}{\partial X_2} &= p_t \cdot \xi_{2,t} + p_s \cdot \xi_{2,s} - 2\, p_2 X_2 = 0 \\
\implies X_1 &= \left(p_t \cdot \xi_{1,t} + p_s \cdot \xi_{1,s}\right) / (2 p_1)    \\
\implies X_2 &= \left(p_t \cdot \xi_{2,t} + p_s \cdot \xi_{2,s}\right) / (2 p_2)
\end{align*}
Thus, given the demand curves,
$$Y_t = (\alpha \cdot B)/p_t \qquad Y_s = (\beta \cdot B)/p_s$$
we substitute in $X_1$ and $X_2$ to get:
\begin{align*}
p_t &= \frac{\alpha \cdot B}{\dfrac{\xi_{1,t}(p_s \cdot \xi_{1,s} + p_t \cdot \xi_{1,t})}{2p_1} + \dfrac{\xi_{2,t}(p_s \cdot \xi_{2,s} + p_t \cdot \xi_{2,t})}{2p_2}} \\
p_t &= \frac{\beta \cdot B}{\dfrac{\xi_{1,s}(p_s \cdot \xi_{1,s} + p_t \cdot \xi_{1,t})}{2p_1} + \dfrac{\xi_{2,s}(p_s \cdot \xi_{2,s} + p_t \cdot \xi_{2,t})}{2p_2}}
\end{align*}

Returning to the utility function, $U = Y_t^\alpha \cdot Y_s^\beta$, we expand it to get:
$$U = (\xi_{1,t} X_1 + \xi_{2,t} X_2)^\alpha (\cdot \xi_{1,s} X_1 + \xi_{2,s} X_2)^\beta$$
Furthermore, assuming profit-maximizing firms, we have:
\begin{align*}
U = \; & \left(\xi_{1,t} \left(p_t \cdot \xi_{1,t} + p_s \cdot \xi_{1,s}\right) / (2 p_1) + \xi_{2,t} \left(p_t \cdot \xi_{2,t} + p_s \cdot \xi_{2,s}\right) / (2 p_2) \right)^\alpha \\
&* \left( \xi_{1,s} \left(p_t \cdot \xi_{1,t} + p_s \cdot \xi_{1,s}\right) / (2 p_1) + \xi_{2,s} \left(p_t \cdot \xi_{2,t} + p_s \cdot \xi_{2,s}\right) / (2 p_2) \right)^\beta
\end{align*}

\subsubsection{CES Utility}

Suppose instead that we have a utility function of the form:
$$U = (\alpha Y_t^\phi \, + \, \beta Y_s^\phi)^{1/\phi}$$
The demand functions are then:
\begin{align*}
Y_t &= \left(\frac{\alpha}{p_t}\right)^\sigma \cdot \frac{B}{\alpha^\sigma p_t^{1-\sigma} \, + \, \beta^\sigma p_s^{1-\sigma}} \\
Y_s &= \left(\frac{\beta}{p_s}\right)^\sigma \cdot \frac{B}{\alpha^\sigma p_t^{1-\sigma} \, + \, \beta^\sigma p_s^{1-\sigma}}
\end{align*}
where $\sigma = 1 / (1 - \phi)$ is the elasticity of substitution. And, same as before, we have the following supply curve:
\begin{align*}
X_1^* &= \left( p_t \cdot \xi_{1,t} + p_2 \cdot \xi_{1,s} \right) / (2 p_1) \\
X_2^* &= \left( p_t \cdot \xi_{2,t} + p_2 \cdot \xi_{2,s} \right) / (2 p_2) 
\end{align*}

\subsubsection{Simpler Model}

Suppose that we have the same production function but our first input is equally productive at time $t$ or $s$, so we have:
$$Y_t = \xi_{1} X_1 + \xi_{2,t} X_2$$
$$Y_s = \xi_{1} X_1 + \xi_{2,s} X_2$$
Using matrix notation, we have:
$$M = 
\begin{pmatrix}
\xi_1 & \xi_{2,t} \\
\xi_1 & \xi_{2,s}
\end{pmatrix}
\quad \implies \quad 
Y = M \, X \quad \implies \quad X = M^{-1} \, Y$$

Additionally, suppose that we have the cost function $C = (X_1^2  + X_2^2) / 2$. Then, we have:
\begin{align*}
\frac{\partial C}{\partial Y_t} &= M^{-1}_{11} \cdot X_1 +  M^{-1}_{21} \cdot X_2 \\
\frac{\partial C}{\partial Y_s} &= M^{-1}_{12} \cdot X_1 +  M^{-1}_{22} \cdot X_2 
\end{align*}
Then, with our original profit function, we get the following first order conditions
\begin{align*}
\Pi &= p_t Y_t + p_s Y_s - C(X_1, X_2) \\
\implies p_t &= M^{-1}_{11} \cdot X_1 +  M^{-1}_{21} \cdot X_2 \\
\implies p_y &= M^{-1}_{12} \cdot X_1 +  M^{-1}_{22} \cdot X_2 \\
\implies P &= (M^{-1})^{T} X \\
\implies X &= M^{T} P
\end{align*}
Therefore, our supply curve is $Y = M \, M^{T} P$. 
And, assuming Cobb-Douglas utility, we have:
$$Y_t = (\alpha \cdot B)/p_t \qquad Y_s = (\beta \cdot B)/p_s $$
Hence, setting supply equal to demand, we get:
\begin{align*}
M \, M^{T} P &= 
\begin{pmatrix}
\alpha \cdot B / p_t \\
\beta \cdot B / p_s
\end{pmatrix} \\
\iff 
\left(\begin{array}{cc} {\xi _{1}}^2+{\xi _{2,t}}^2 & {\xi _{1}}^2+\xi _{2,s}\,\xi _{2,t}\\ {\xi _{1}}^2+\xi _{2,s}\,\xi _{2,t} & {\xi _{1}}^2+{\xi _{2,s}}^2 \end{array}\right) 
\begin{pmatrix}
p_t \\
p_s
\end{pmatrix}  
&= \begin{pmatrix}
\alpha \cdot B / p_t \\
\beta \cdot B / p_s
\end{pmatrix} \\
\implies
Y_{supply} &= 
\begin{pmatrix}
(\xi _{1}^2+\xi _{2,t}^2)p_t +  (\xi _{1}^2+\xi _{2,s}\,\xi _{2,t})p_s \\[2ex]
(\xi _{1}^2+\xi _{2,s}\,\xi _{2,t}) p_t  + ({\xi _{1}}^2+\xi _{2,s}^2 ) p_s
\end{pmatrix}\\
\implies
Y_{demand} &= 
\begin{pmatrix}
\alpha \cdot B / p_t \\
\beta \cdot B / p_s
\end{pmatrix} 
\end{align*}
Expanding and simplifying, we have:
\begin{align*}
({\xi _{1}}^2+\xi _{2,t}^2)p_t^2 +  (\xi _{1}^2+\xi _{2,s}\,\xi _{2,t})p_s p_t &= \alpha \cdot B \\
({\xi _{1}}^2+\xi _{2,s}\,\xi _{2,t}) p_t p_s + ({\xi _{1}}^2+\xi _{2,s}^2 ) p_s^2 &= \beta \cdot B \\
\implies ({\xi _{1}}^2+\xi _{2,t}^2)p_t^2 - ({\xi _{1}}^2+\xi _{2,s}^2 ) p_s^2 &= (\alpha - \beta) \cdot B
\end{align*}
Similarly, solving for the supply and demand of $X$, we get:
\begin{align*}
X_{demand} = 
\begin{pmatrix}
\dfrac{\mathrm{B}\,\left(\alpha \,p_{s}\,\xi _{2,s}-\beta\,p_{t}\,\xi _{2,t}\right)}{p_{s}\,p_{t}\,\xi _{1}\,\left(\xi _{2,s}-\xi _{2,t}\right)}\\[3ex] -\dfrac{\mathrm{B}\,\left(\alpha \,p_{s}-\beta\,p_{t}\right)}{p_{s}\,p_{t}\,\left(\xi _{2,s}-\xi _{2,t}\right)}
\end{pmatrix}  \qquad
X_{supply} = 
\begin{pmatrix}
p_{s}\,\xi _{1}+p_{t}\,\xi _{1}\\[1ex]
 p_{s}\,\xi _{2,s}+p_{t}\,\xi _{2,t}
\end{pmatrix}
\end{align*}

\subsubsection{Simplest Model}

Suppose that we have the same production function but our first input is equally productive at time $t$ or $s$, so we have:
$$Y_t = \xi_{1} X_1 + \xi_{2,t} X_2$$
$$Y_s = \xi_{1} X_1 + \xi_{2,s} X_2$$
Using matrix notation, we have:
$$M = 
\begin{pmatrix}
\xi_1 & \xi_{2,t} \\
\xi_1 & \xi_{2,s}
\end{pmatrix}
\quad \implies \quad 
Y = M \, X \quad \implies \quad X = M^{-1} \, Y$$
Additionally, suppose we have linear cost: $C = p_1 X_1 + p_2 X_2$. 
Then, our first-order conditions for profit maximization, assuming linear cost, are:
\begin{align*}
\frac{\partial PS}{\partial X_1} &= p_t \cdot \xi_1  + p_s \cdot \xi_1 - p_1 = 0 \\
\frac{\partial PS}{\partial X_2} &= p_t \cdot \xi_{2,t}  + p_s \cdot \xi_{2,s} - p_2 = 0 \\
\implies M^T p &= 
\begin{pmatrix}
p_1 \\
p_2
\end{pmatrix} \\
\implies p &= (M^{T})^{-1} \begin{pmatrix}
p_1 \\
p_2
\end{pmatrix}
\end{align*}
This essentially means that we have a supply curve that is perfectly horizontal at the optimal prices. Consequently, profit must be zero. 
$$
p^{opt} = 
\begin{pmatrix}
p_t^{opt} \\
p_s^{opt}
\end{pmatrix}
=
\begin{pmatrix}
\dfrac{p_{2}\,\xi _{1}-p_{1}\,\xi _{2,s}}{\xi _{1}\,\left(\xi _{2,t}-\xi _{2,s}\right)}\\[2ex]
-\dfrac{p_{2}\,\xi _{1}-p_{1}\,\xi _{2,t}}{\xi _{1}\,\left(\xi _{2,t}-\xi _{2,s}\right)}
\end{pmatrix}
$$
Then, assuming utility maximization, we have the following first-order conditions:
\begin{align*}
Y_t &= (\alpha \cdot B) / (p_t) \\
Y_s &= (\beta \cdot B) / (p_s)
\end{align*}
Therefore, the optimal quantities of $Y$ are given by:
\begin{align*}
Y^{opt} = 
\begin{pmatrix}
Y_t^{opt} \\
Y_s^{opt} 
\end{pmatrix}
=
\begin{pmatrix}
-\dfrac{\alpha \,\mathrm{B}\,\xi _{1}\,\left(\xi _{2,s}-\xi _{2,t}\right)}{p_{2}\,\xi _{1}-p_{1}\,\xi _{2,s}}\\[2.5ex]
\dfrac{\beta\,\mathrm{B}\,\xi _{1}\,\left(\xi _{2,s}-\xi _{2,t}\right)}{p_{2}\,\xi _{1}-p_{1}\,\xi _{2,t}}
\end{pmatrix}
\end{align*}
Lastly, since $Y = MX$,the optimal quantities of $X$ are given by:
\begin{align*}
X^{opt} = 
\begin{pmatrix}
X_1^{opt} \\
X_1^{opt} 
\end{pmatrix}
=
M^{-1} \, Y^{opt} = 
\begin{pmatrix}
-\dfrac{\mathrm{B}\,\left(\alpha \,p_{2}\,\xi _{1}\,\xi _{2,s}-\alpha \,p_{1}\,\xi _{2,s}\,\xi _{2,t}+\beta\,p_{2}\,\xi _{1}\,\xi _{2,t}-\beta\,p_{1}\,\xi _{2,s}\,\xi _{2,t}\right)}{\left(p_{2}\,\xi _{1}-p_{1}\,\xi _{2,s}\right)\,\left(p_{2}\,\xi _{1}-p_{1}\,\xi _{2,t}\right)}\\[3ex] 
\dfrac{\alpha \,\mathrm{B}\,\xi _{1}}{p_{2}\,\xi _{1}-p_{1}\,\xi _{2,s}}+\dfrac{\beta\,\mathrm{B}\,\xi _{1}}{p_{2}\,\xi _{1}-p_{1}\,\xi _{2,t}}
\end{pmatrix}
\end{align*}
Now, to find the comparative statics, we return to the first order conditions:
\begin{alignat*}{2}
&\frac{\partial PS}{\partial X_1} &&= p_t \cdot \xi_1  + p_s \cdot \xi_1 - p_1 = 0 \\
&\frac{\partial PS}{\partial X_2} &&= p_t \cdot \xi_{2,t}  + p_s \cdot \xi_{2,s} - p_2 = 0 \\ 
&\implies 
&&\begin{pmatrix}
\xi_1 & \xi_1 \\
\xi_{2,t} & \xi_{2,s} 
\end{pmatrix}
\begin{pmatrix}
p_t \\
p_s
\end{pmatrix}
=
\begin{pmatrix}
p_1 \\
p_2
\end{pmatrix} \\
&\implies 
&&
\begin{pmatrix}
p_t \\
p_s
\end{pmatrix}
=
\begin{pmatrix} 
\frac{\xi _{2,s}}{\xi _{1}\,\xi _{2,s}-\xi _{1}\,\xi _{2,t}} & -\frac{1}{\xi _{2,s}-\xi _{2,t}}\\ 
-\frac{\xi _{2,t}}{\xi _{1}\,\xi _{2,s}-\xi _{1}\,\xi _{2,t}} & \frac{1}{\xi _{2,s}-\xi _{2,t}} 
\end{pmatrix}
\begin{pmatrix}
p_1 \\
p_2
\end{pmatrix}
\end{alignat*}

Letting $N$ be the last matrix which provides the solutions to $p_t$ and $p_s$, we have the following derivatives and short-hand notations:
\begin{alignat*}{2}
\frac{\partial N}{\partial \xi_1} &= 
\left(\begin{array}{cc} \frac{\xi _{2,s}}{{\xi _{1}}^2\,\left(\xi _{2,t}-\xi _{2,s}\right)} & 0\\ -\frac{\xi _{2,t}}{{\xi _{1}}^2\,\left(\xi _{2,t}-\xi _{2,s}\right)} & 0 \end{array}\right)
&&\equiv N^{\xi_1} \\
\frac{\partial N}{\partial \xi_{2,t}} &=
\left(\begin{array}{cc} \frac{\xi _{2,s}}{\xi _{1}\,{\left(\xi _{2,s}-\xi _{2,t}\right)}^2} & -\frac{1}{{\left(\xi _{2,s}-\xi _{2,t}\right)}^2}\\ -\frac{\xi _{2,s}}{\xi _{1}\,{\left(\xi _{2,s}-\xi _{2,t}\right)}^2} & \frac{1}{{\left(\xi _{2,s}-\xi _{2,t}\right)}^2} \end{array}\right)
&&\equiv N^{\xi_{2,t}} \\
\frac{\partial N}{\partial \xi_{2,s}} &=
\left(\begin{array}{cc} -\frac{\xi _{2,t}}{\xi _{1}\,{\left(\xi _{2,s}-\xi _{2,t}\right)}^2} & \frac{1}{{\left(\xi _{2,s}-\xi _{2,t}\right)}^2}\\ \frac{\xi _{2,t}}{\xi _{1}\,{\left(\xi _{2,s}-\xi _{2,t}\right)}^2} & -\frac{1}{{\left(\xi _{2,s}-\xi _{2,t}\right)}^2} \end{array}\right)
&&\equiv N^{\xi_{2,s}} 
\end{alignat*}

By utility maximization, we have:
\begin{align*}
Y_t = (\alpha \cdot B)/p_t \qquad Y_s = (\beta \cdot B)/p_s 
\end{align*}
Therefore, we have:
\begin{align*}
\frac{\partial Y_t}{\partial \xi_1} = \frac{\partial Y_t}{\partial p_t}  \cdot \frac{\partial p_t}{\partial \xi_1} = (-(\alpha \cdot B)/p_t^2) \cdot (N^{\xi_1}_{1,1} p_1 + 0 \, p_2) < 0 \\
\frac{\partial Y_s}{\partial \xi_1} = \frac{\partial Y_s}{\partial p_s}  \cdot \frac{\partial p_s}{\partial \xi_1} = (-(\beta \cdot B)/p_s^2) \cdot (N^{\xi_1}_{2,1} p_1 + 0 \, p_2) > 0 
\end{align*}
because $N^{\xi_1}_{2,1} < 0 < N^{\xi_1}_{1,1}$ since we assumed earlier that $\xi_{2,t} > \xi_{2,s}$. If we have $X_1$ being coal and $X_2$ being solar, we have improvements in the conversion rate of coal to energy causing shifts in energy production to the night (period $s$) and away from the day (period $t$).

Now, we can do the same for $\xi_{2,t}$. 
\begin{align*}
\frac{\partial Y_t}{\partial \xi_{2,t}} = \frac{\partial Y_t}{\partial p_t}  \cdot \frac{\partial p_t}{\partial \xi_{2,t}} = (-(\alpha \cdot B)/p_t^2) \cdot (N^{\xi_{2,t}}_{1,1} p_1 + N^{\xi_{2,t}}_{1,2} \cdot p_2) \\
\frac{\partial Y_s}{\partial \xi_{2,t}} = \frac{\partial Y_s}{\partial p_s}  \cdot \frac{\partial p_s}{\partial \xi_{2,t}} = (-(\beta \cdot B)/p_s^2) \cdot (N^{\xi_{2,t}}_{2,1} p_1 + N^{\xi_{2,t}}_{2,2} \cdot p_2) 
\end{align*}
Firstly, note that $N^{\xi_{2,t}}_{1,1} \, p_1 + N^{\xi_{2,t}}_{1,2} \, p_2 < 0$ when $\xi_1 / p_1 > \xi_{2,s} / p_2$. And note that the second row of $N^{\xi_{2,t}}$ is simply the negative of the first row; hence, $N^{\xi_{2,t}}_{1,1} \, p_1 + N^{\xi_{2,t}}_{1,2} \, p_2 > 0$ when $\xi_1 / p_1 > \xi_{2,s} / p_2$. In practice, $\xi$ represents the conversion rate from units of input to units of output and $p$ is the price. So, the condition $\xi_1 / p_1 > \xi_{2,s} / p_2$ simply states that the cost efficiency of input $1$ is greater than the cost efficiency of input $2$ during period $s$. Therefore, we have:
$$\xi_1 / p_1 > \xi_{2,s} / p_2 \implies 
\frac{\partial Y_s}{\partial \xi_{2,t}} < 0 < \frac{\partial Y_t}{\partial \xi_{2,t}} $$
If $X_1$ were coal and $X_2$ were solar, we would obviously have coal being more cost efficient at night than solar. Therefore, improvements to solar's efficiency during the day would shift energy production to the day and away from the night.

Lastly, we have the derivatives for $\xi_{2,s}$. 
\begin{align*}
\frac{\partial Y_t}{\partial \xi_{2,s}} = \frac{\partial Y_t}{\partial p_t}  \cdot \frac{\partial p_t}{\partial \xi_{2,s}} = (-(\alpha \cdot B)/p_t^2) \cdot (N^{\xi_{2,s}}_{1,1} p_1 + N^{\xi_{2,s}}_{1,2} \cdot p_2) \\
\frac{\partial Y_s}{\partial \xi_{2,s}} = \frac{\partial Y_s}{\partial p_s}  \cdot \frac{\partial p_s}{\partial \xi_{2,s}} = (-(\beta \cdot B)/p_s^2) \cdot (N^{\xi_{2,s}}_{2,1} p_1 + N^{\xi_{2,s}}_{2,2} \cdot p_2) 
\end{align*}
Here, recall that we have  $\xi_{2,s} \, N^{\xi_{2,s}} = - \xi_{2,t} \, N^{\xi_{2,t}}$, which helps carry through the previous algebra. That is, replacing $\xi_{2,s}$ with $\xi_{2,t}$ and flipping the signs, we get:
$$\xi_1 / p_1 < \xi_{2,t} / p_2 \implies 
\frac{\partial Y_s}{\partial \xi_{2,s}} < 0 < \frac{\partial Y_t}{\partial \xi_{2,s}} $$
So, if solar is more cost efficient during the day than coal, then improvements in the night-time efficiency of solar will increase energy output during the day and decrease it during the night. This is because solar becoming more efficient will result in greater solar usage and so energy production will reflect the lop-sided output of solar.

It's important to note that the change in $Y_t$ and $Y_s$ in response to other parameters always gives away whether we consume more or less of $X_2$. This is because $X_1$ has a fixed conversion rate, so $Y_t$ and $Y_s$ will move in the same direction if $X_1$ changes. But, they can only move in opposite directions if $X_2$ changes. For example, if we have $\xi_{2,t} > \xi_{2,s}$, then an increase in $Y_t$ and a decrease in $Y_s$ must signal a greater use of $X_2$ and less of $X_1$.

Next, we have the comparative statics for the inputs $X_1$ and $X_2$. By definition, we have:
\begin{alignat*}{1}
Y &= MX \\
\implies X &= M^{-1} \, Y \\
&= \begin{pmatrix}
\dfrac{\xi _{2,t}\,Y_{s}-\xi _{2,s}\,Y_{t}}{\xi _{1}\,\left(\xi _{2,t}-\xi _{2,s}\right)}\\[2ex] 
\dfrac{Y_{t}-Y_{s}}{\xi _{2,t}-\xi _{2,s}} 
\end{pmatrix}
\end{alignat*}
Now, we differentiate with respect to the $\xi$ parameters. Using the previous derivations for the derivatives of $Y$ assumes utility and profit maximization.
\begin{alignat*}{2}
&\frac{\partial X_1}{\partial \xi_1} &&= - X_1 / \xi_1 + \left(\xi_{2,t} \, \frac{\partial Y_s}{\partial \xi_{1}} - \xi_{2,s} \, \frac{\partial Y_t}{\partial \xi_{1}} \right) \cdot \left(\xi_1 \, (\xi_{2,t} - \xi_{2,s}))^{-1} \right)  \\
&\frac{\partial X_1}{\partial \xi_{2,t}} &&= -X_1/(\xi_1 \, (\xi_{2,t} - \xi_{2,s})) + \left( - \xi_{2,s} \, \frac{\partial Y_t}{\partial \xi_{2,t}} + \xi_{2,t} \, \frac{\partial Y_s}{\partial \xi_{2,t}} + Y_s \right)\cdot(\xi_1 \, (\xi_{2,t} - \xi_{2,s}))^{-1} \\
&\frac{\partial X_1}{\partial \xi_{2,s}} &&= X_1/(\xi_1 \, (\xi_{2,t} - \xi_{2,s})) + \left( - \xi_{2,s} \, \frac{\partial Y_t}{\partial \xi_{2,s}} + \xi_{2,t} \, \frac{\partial Y_s}{\partial \xi_{2,s}} - Y_t \right)\cdot(\xi_1 \, (\xi_{2,t} - \xi_{2,s}))^{-1}  \\
\end{alignat*}
The above inequalities assume $Y_t \geq Y_s$, which must always be true given $\xi_{2,t} > \xi_{2,s}$, and the last inequality assumes $\xi_1 / p_1 < \xi_{2,t} / p_2$. The first inequality is negative since we proved earlier that $\frac{\partial Y_t}{\partial \xi_1} < 0 < \frac{\partial Y_s}{\partial \xi_1}$. Similarly, we get the result for the last inequality using the results for the derivatives of $Y_t$ and $Y_s$. The second inequality may be positive or negative. 
Next, for $X_2$, we have:
\begin{alignat*}{2}
&\frac{\partial X_2}{\partial \xi_1} &&= 
\left( \frac{\partial Y_t}{\partial \xi_{1}} -  \frac{\partial Y_s}{\partial \xi_{1}} \right) \cdot (\xi_{2,t} - \xi_{2,s}) < 0 \\
C_2 \implies &\frac{\partial X_1}{\partial \xi_{2,t}} &&= \left(\frac{\partial Y_t}{\partial \xi_{2,t}} - \frac{\partial Y_s}{\partial \xi_{2,t}}\right)/(\xi_{2,t} - \xi_{2,s}) - (Y_t - Y_s)/(\xi_{2,t} - \xi_{2,s})^2 > 0 \\
&\frac{\partial X_2}{\partial \xi_{2,s}} &&= \left(\frac{\partial Y_t}{\partial \xi_{2,s}} - \frac{\partial Y_s}{\partial \xi_{2,s}}\right)/(\xi_{2,t} + \xi_{2,s}) - (Y_t - Y_s)/(\xi_{2,t} - \xi_{2,s})^2 
\end{alignat*}
$$\text{where} \quad C_2 \iff \left(\frac{\partial (Y_t - Y_s)}{\partial \xi_{2,t}} \cdot \frac{\xi_{2,t} - \xi_{2,s}}{(Y_t - Y_s)} > 1\right) \; \wedge \; \left(\xi_1 / p_1 > \xi_{2,s} / p_2 \right)$$
Note that $C_2$ may or may not be true.

\subsection{Example Two Period Case with CD Utility and Two Technologies}

Suppose our utility function is instead given by $Y_t^{\alpha_t} \, Y_s^{\alpha_s}$ where our two periods are $t$ and $s$. Optimizing utility given the budget constraint $Y_t p_t + Y_s p_s = I$, our demand curves are $Y_t = \alpha_t / p_t$ and $Y_s = \alpha_s / p_s$.

Next, we introduce the following matrices to simplify the notation: 
$$
Y = \begin{pmatrix}
Y_t \\
Y_s 
\end{pmatrix}
\quad 
P = \begin{pmatrix}
p_t \\
p_s 
\end{pmatrix}
\quad 
X = \begin{pmatrix}
X_1 \\
X_2 
\end{pmatrix}
\quad 
\xi = \begin{pmatrix}
\xi _{\mathrm{1t}} & \xi _{\mathrm{2t}}\\ \xi _{\mathrm{1s}} & \xi _{\mathrm{2s}}
\end{pmatrix}$$
where $X_i$ is the quantity of input technologies and $\xi_{it}$ is the output of technology $i$ at time $t$. This implies that our output $Y = \xi \,X$. Next, we have profit maximizing firms with linear cost. Suppose $c_i$ is the cost of each unit of technology $i$, and let $C$ be a vector of $c_i$. Then, our profit function is:
$$\Pi = P^T \, Y - C^T \, X = \left(P^T \, \xi - C^T   \right)\, X$$
Now, assuming that $\xi$ is invertible, we have the first order condition:
\begin{align*}
P^T\, \xi &= C^T \\
P &= (\xi^{-1})^T \, C  \\
P^{opt} &= \begin{pmatrix}
-\dfrac{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}  \\[2ex]
\dfrac{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}} 
\end{pmatrix}
\end{align*}
Substituting back into the FOC for consumer demand, we have:
$$
Y^{opt} = \begin{pmatrix}
\dfrac{\alpha _{t}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{c_{2}\,\xi _{\mathrm{1s}} - c_{1}\,\xi _{\mathrm{2s}}} \\[2ex]
\dfrac{\alpha _{s}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} 
\end{pmatrix}
\implies 
X^{opt} = \begin{pmatrix}
\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}+\dfrac{\alpha _{s}\,\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} \\[2ex] 
-\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}-\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}
\end{pmatrix}
$$
If we assume that $Y$ is positive in both periods, then, without loss of generality, we have:
\begin{align*}
\text{$X_1$ has a comparative advantage in producing in period $s$: } \quad 
{\xi_{1s}}/{\xi_{1t}} &> {\xi_{2s}}/{\xi_{2t}} \\
\text{$X_1$ is more cost effective at producing in period $s$: } \quad \xi_{1s}/c_1 &> \xi_{2s}/c_2  \\
\text{$X_2$ is more cost effective at producing in period $t$:} \quad \xi_{1t}/c_t &< \xi_{2t}/c_2
\end{align*}
Similarly, if we assume $X$ is positive for both technologies, then, without loss of generality, we have:
\begin{align*}
\alpha_t \xi_{2s} \left( c_1 \xi_{2t} - c_2 \xi_{1t} \right) &> \alpha_s \xi_{2t} \left( c_2 \xi_1s - c_1 \xi_2s \right) \\
\alpha_t \xi_{1s} \left( c_1 \xi_{2t} - c_2 \xi_{1t} \right) &< \alpha_s \xi_{1t} \left( c_2 \xi_1s - c_1 \xi_2s \right) \\
\implies \xi_{2s} / \xi_{1s} &> \xi_{2t}/ \xi_{1t}
\end{align*}

\subsection{Two Period Two Technology Case with Risk}

The intermittency of electricity technologies not only concerns when they produce but how consistently they can produce. 
Consider the same simplified, two-period model as before with technologies that produce according to a stochastic process. Specifically, suppose that $X_1$ produces at the rate $N(\xi_{1t}, \sigma_{1t}^2)$ in period $t$ and at the rate $N(\xi_{1s}, \sigma_{1s}^2)$ in period $s$; also, consider equivalent definitions for $X_2$. We use the following matrices to simplify notation:
$$
\xi = 
\begin{pmatrix}
\xi _{\mathrm{1t}} & \xi _{\mathrm{2t}}\\ \xi _{\mathrm{1s}} & \xi _{\mathrm{2s}}
\end{pmatrix}
\quad 
\Sigma_t = \begin{pmatrix}
\sigma_{1t}^2 & \sigma_{1t, 2t} \\ 
\sigma_{1t, 2t} & \sigma_{2t}^2
\end{pmatrix}
\quad 
\Sigma_s = \begin{pmatrix}
\sigma_{1s}^2 & \sigma_{1s, 2s} \\ 
\sigma_{1s, 2s} & \sigma_{2s}^2
\end{pmatrix}
\quad 
$$
where $\Sigma_t$ is the covariance of electricity production in period $t$ and likewise for $\Sigma_s$ at period $s$; we the generation processes in both periods are independent for simplicity. This essentially reduces to a portfolio maximization problem in each period; however, there is a significant difference: electricity demand varies by period and the production technologies' output and variance of output vary by period as well. The optimization problem can be defined as:
\begin{align*}
\max \quad E \left[ U \right] \\
\text{s.t. \quad} I \cdot  w_i / c_i &= X_i \,\, \forall i \\
\textbf{1}^T w_i &= 1 \\
w_i &\in [0,1] \,\, \forall i
\end{align*}
where $w_i$ is the percent of our budget that is spent on $X_1$ and $X_2$, $I$ is the budget, and $c_i$ is the price of $X_i$.  Since the technologies generate electricity according to a normal process, we have:
\begin{equation*}
\mu \equiv
\begin{pmatrix}
\mu_t \\
\mu_s
\end{pmatrix}
=
\xi \, \textbf{w}
\qquad
\sigma_t^2 
=
\textbf{w}^T \,  \Sigma_t \, \textbf{w} \\
\qquad
\sigma_s^2
=
\textbf{w}^T \,  \Sigma_s \, \textbf{w}
\end{equation*}
\vspace{-2em}
\begin{align*}
Y_t &\sim  N \left( \mu_t, \sigma_t^2 \right) \\
Y_s &\sim  N \left( \mu_s, \sigma_s^2 \right)
\end{align*}
where $\textbf{w}$ is a column vector of weights, $\mu$ represents the electricity generation rate in each period, and $\Sigma$ is the covariance matrix for this rate. 
To solve, we take the second-order Taylor series around $(\overline{Y}_t, \overline{Y}_s) \equiv E \left[ Y_t, Y_s \right]$ which represents our average electricity generation. This is given by:
\begin{align*}
U(Y_t, Y_s) &\approx \overline{U} + \overline{U}_t(Y_t - \overline{Y_t}) + \overline{U}_s(Y_s - \overline{Y_s}) \\
&\phantom{\approx} \, + (1/2) \left[ \overline{U}_{tt}(Y_t - \overline{Y_t})^2 + 2 \overline{U}_{ts}(Y_t - \overline{Y_t})(Y_s - \overline{Y_s})  + \overline{U}_{ss}(Y_s - \overline{Y_s})^2 \right]
\end{align*}
where $\overline{U} \equiv U(\overline{Y}_t, \overline{Y}_s)$, and $\overline{U}_t$ is the derivative of $U$ with respect to $Y_t$ evaluated at $\overline{Y}_t$. Taking the expectation, the $U_t$ and $U_s$ drop out since $E(Y_s - \overline{Y_s}) = 0$, and the $U_{ts}$ drops out since $Y_t$ and $Y_s$ are independent so $E\left[(Y_t - \overline{Y_t})(Y_s - \overline{Y_s})\right] = 0 $. Thus, we are left with:
\begin{align*}
E \left[ U(Y_t, Y_s) \right] &\approx \overline{U} + (1/2) \left[\overline{U}_{tt}\,\sigma_t^2 + \overline{U}_{ss}\, \sigma_s^2 \right]
\end{align*}

%In practice, suppose we have $X_1$ as coal and $X_2$ as solar, and lienar costs. Then, we will see the following effects:
%
%\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
%	\item Improvements in the conversion rate of coal to electricity
%	\begin{enumerate}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
%		\item Decreases the use of solar
%		\item 
%	\end{enumerate}
%	\item Improvements in the conversion rate of solar to electricity during time $t$
%	\begin{enumerate}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
%		\item %
%		\item %
%	\end{enumerate}
%	\item Improvements in the conversion rate of solar to electricity during time $s$
%	\begin{enumerate}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
%		\item %
%		\item %
%	\end{enumerate}
%\end{enumerate}

\pagebreak

\pagebreak

	\begin{thebibliography}{9}

%		\bibitem[Angel, Harris, and Spatt(2011)]{Angel} 
%		Angel, J.J., Harris, L.E., \& Spatt, C. S. (2011). Equity Trading in the 21st Century. Quarterly Journal Of Finance, 1(1), 1-53.

		\bibitem[Stern(2012)]{Stern} 
		Stern, D. (2012). “Interfuel Substitution: A Meta-Analysis.” Journal of Economic Surveys 26 (2): 307–331. \href{https://doi.org/10.1111/j.1467-6419.2010.00646.x}{https://doi.org/10.1111/j.1467-6419.2010.00646.x}.

	\end{thebibliography}

\end{document}

### 2019-04-19 documents/presentation_june.tex
Remove pdf files and include tex files

\documentclass[11pt,aspectratio=169]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{booktabs}
\usepackage{color}
\usetheme{metropolis}

% images
\graphicspath{ {D:/Users/saketh/Documents/GitHub/BECCS-Case-Study/} }

% sig stars
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}

\author{Saketh Aleti}
\title{Estimation of CGE Parameters}
%\subtitle{}
%\logo{}
%\institute{}
\date{\today}
%\subject{}
%\setbeamercovered{transparent}
%\setbeamertemplate{navigation symbols}{}

\begin{document}

\maketitle

\begin{frame}{Outline}

\begin{itemize}
	\setlength\itemsep{1.5em}
	\item CES vs. CET Theory

	\item Fossil Fuel Results

	\item Renewables Results

\end{itemize}

\end{frame}

\begin{frame}{Theory}

	\metroset{block=fill}

	\begin{block}{\centering{CES/CET Problem}}
	\large \begin{align*}
	 \\[-3em] \text{\textbf{Prod./Trans. Function}: } &Q = \theta \cdot \left( \sum_i \; \alpha_i \cdot X_i^\phi \right)^{1/\phi} \\[1em]
	\text{\textbf{Budget Constraint}: } &B = \sum_i \;p_i \cdot  X_i \\[-2.5em]
	\end{align*}
	\end{block}

	\begin{itemize}
		\item $p_i$ are prices, $\theta$ is the scaling coefficient, $\alpha_i$ is the share coefficient, $B$ is the budget
		\item The elasticity of substitution is $\sigma = 1 / (1-\phi)$
		\item The elasticity of transformation is $\psi = 1 / (\phi - 1)$
	\end{itemize}
\end{frame}

\begin{frame}{CES versus CET - CES Example}

\begin{columns}[T,onlytextwidth]
	\column{0.5\textwidth}

	\begin{figure}
		\hspace{-2em}
		\vspace{1em}
		\includegraphics[width=1\textwidth]{exhibits/CES_example.PNG} 
	\end{figure}

	\column{0.5\textwidth}

	\begin{itemize}

		\setlength\itemsep{2em}

		\item Isoquant of imported good $M_i$ and domestic good $D_i$ shows combination needed to produce a fixed quantity $\tilde{Q_i}$

		\item Consumer wants to satisfy a utility function including the composite $Q_i$

		\item Convexity shows diminishing returns to consuming only $M_i$ or $D_i$

	\end{itemize}

\end{columns}

\end{frame}

\begin{frame}{CES versus CET - CET Example}

\begin{columns}[T,onlytextwidth]
	\column{0.5\textwidth}

	\begin{figure}
		\hspace{-2em}
		\vspace{1em}
		\includegraphics[width=1\textwidth]{exhibits/CET_example.PNG} 
	\end{figure}

	\column{0.5\textwidth}

	\begin{itemize}

		\setlength\itemsep{1.5em}

		\item Isoquant of exports $E_i$ and domestic supply $D_i$ of some good $i$

		\item Shows combination needed to reach a GDP of $\tilde{Z_i}$

		\item Firms maximize profit by selling goods where they are most valued

		\item Concavity shows diminishing returns to selling everything domestically versus exporting everything

	\end{itemize}

\end{columns}

\end{frame}

\begin{frame}{CES/CET Solution}

	\metroset{block=fill}

	\vspace{0.5em}

	\begin{block}{\centering{CES/CET Problem}}
		\large \begin{align*}
		\\[-3em] \text{\textbf{Prod./Trans. Function}: } &Q = \theta \cdot \left( \sum_i \; \alpha_i \cdot X_i^\phi \right)^{1/\phi} \\[1em]
		\text{\textbf{Budget Constraint}: } &B = \sum_i \;p_i \cdot  X_i \\[-2.5em]
		\end{align*}
	\end{block}

	\vspace{-1em}
\
	$$\text{Profit Maximization} \implies \frac{X_i}{X_j} = \left(\frac{\alpha_i \cdot p_j}{\alpha_j \cdot p_i}\right)^{1/(1-\phi)}$$

	$$\implies \ln\left(\frac{X_i}{X_j}\right) = \sigma \cdot \ln\left(\frac{\alpha_i \cdot p_j}{\alpha_j \cdot p_i}\right) = \psi \cdot \ln\left(\frac{\alpha_j \cdot p_i}{\alpha_i \cdot p_j}\right) $$

\end{frame}

\begin{frame}{Methodology}

	\metroset{block=fill}

	\vspace{0.5em}

	\begin{block}{\centering{CES $\implies$ Functional Form}}
	$$\ln\left(\frac{X_{i,s,t}}{X_{j,s,t}}\right) = \sigma \cdot \ln\left(\frac{ p_{j,s,t}}{ p_{i,s,t}}\right) + c_{s,t} + \varepsilon_{s,t}$$
	\end{block}

	\vspace{-0em}

		\begin{itemize}

			%\setlength\itemsep{1.5em}

			\item Inputs $i$ and $j$ in state $s$ at time $t$

			\item $X_i$ and $X_j$ are the input quantities, $p_i$ and $p_j$ are the input prices

			\item Share parameters from previous equation are absorbed into the constant term

			\item This approach avoids endogeneity problems since the input ratios are not dependent on any variables except for price $\implies$ demand is fixed, supply movements trace out demand curve

		\end{itemize}

\end{frame}

\begin{frame}{Methodology (cont.)}

\metroset{block=fill}

\vspace{0.5em}

\begin{block}{\centering{CES $\implies$ Functional Form}}
	$$\ln\left(\frac{X_{i,s,t}}{X_{j,s,t}}\right) = \sigma \cdot \ln\left(\frac{ p_{j,s,t}}{ p_{i,s,t}}\right) + c_{s,t} + \varepsilon_{s,t}$$
\end{block}

\vspace{-0em}

\begin{itemize}

	%\setlength\itemsep{1.5em}

	\item Elasticity of substitution/transformation is the same between all commodities in the production/transformation function

	\item Suppose coal ($i$), natural gas ($j$), and oil ($k$) are all part of the same production function for electricity
	\begin{align*}
	\implies &\ln(X_i/X_j) = \, \sigma \ln(p_j / p_i) + c_{1,s,t} + \varepsilon_{1,s,t} \\
	= &\ln(X_j/X_k) = \sigma \ln(p_k / p_j) + c_{2,s,t} + \varepsilon_{2,s,t} \\
	= &\ln(X_i/X_k) = \sigma \ln(p_k / p_i) + c_{3,s,t} + \varepsilon_{3,s,t}
	\end{align*}

\end{itemize}

\end{frame}

\begin{frame}{Methodology (cont.)}

\metroset{block=fill}

\vspace{0.5em}

\begin{block}{\centering{CES $\implies$ Functional Form}}
	$$\ln\left(\frac{X_{i,s,t}}{X_{j,s,t}}\right) = \sigma \cdot \ln\left(\frac{ p_{j,s,t}}{ p_{i,s,t}}\right) + c_{s,t} + \varepsilon_{s,t}$$
\end{block}

\vspace{-0em}

\begin{itemize}

	%\setlength\itemsep{1.5em}

	\item Elasticity of substitution/transformation is the same between all commodities in the production/transformation function 
	\begin{align*}
	\implies &corr(\ln(X_i/X_j), \,\ln(p_j / p_i)) \\
	= &corr(\ln(X_j/X_k), \ln(p_k / p_j)) \\
	= &corr(\ln(X_i/X_k), \ln(p_k / p_i))
	\end{align*}

	\item So, regressions are done by regressing all unique pairs with coefficients constrained to be equal

\end{itemize}

\end{frame}

\begin{frame}{Methodology (cont.)}

\metroset{block=fill}

\begin{itemize}

	\setlength\itemsep{1em}

	\item Constrained regressions on $n*(n-1)/2 -1$ sets of equations

	\item EG: (Coal/NatGas + Oil/NatGas), (Coal/NatGas + Oil/Coal), (Oil/Coal + Oil/NatGas)

	\item Theoretically, any set of equations in parenthesis should give the same results as another set of equations in parenthesis

	\item Data comes from the EIA for each state in 2016

	\begin{itemize}
		\item Factor input quantities are set to the amount of each used to generate electricity

		\item Factor prices are set to the be the average cost of the each input

		\item Coal given thousand tons, Natural gas in thousand McF, and oil in thousand barrels
	\end{itemize}

\end{itemize}

\end{frame}

\begin{frame}{Fossil Fuel Results}

\fontsize{6pt}{7}\selectfont
\begin{center}
\begin{table}
	\caption{Elasticity of Substitution for Fossil Fuels } 
	\begin{tabular}{@{\extracolsep{0.5em}}lcc|cc|cc} 
		\\[-8ex]\hline  
		\hline \\[-1.2ex]  
		& \multicolumn{6}{c}{\textit{\scriptsize Dependent variable: Difference in Log Inputs}} \\ [0.5em] 
		\cline{2-7}  \\[-0.5em] 
		& ln(Coal/NatGas) & ln(Coal/Oil) & ln(Coal/NatGas) & ln(Oil/NatGas)  & ln(Coal/Oil) & ln(Oil/NatGas) \\ \\ [-0.7em]
		\hline \\[-1.2ex] 
		ln($p_{natgas}/p_{coal}$)&   \colorbox{yellow}{$1.002^{***}$} &  & \colorbox{yellow}{$1.013^{***}$} &  &  &  \\ 
		& $(0.209)$ &  & $(0.210)$ &  &  &  \\ [0.5em]
		ln($p_{oil}/p_{coal}$)&  & $1.002^{***}$  &  &  & \colorbox{yellow}{$1.004^{***}$} &  \\ 
		&  & (0.209) &  &  & $(0.209)$ &  \\ [0.5em]
		ln($p_{natgas}/p_{oil}$)&  &  &  & $1.013^{***}$  &  & $1.004^{***}$ \\ 
		&  &  &  & $(0.210)$ &  & $(0.209)$ \\ [0.5em]
		Constant & $-2.429^{***}$ &  $-1.782^{***}$ & $-2.411^{***}$ & $-0.623$ & $-1.783^{***}$ & $-0.643$  \\ 
		&  $(0.398)$ & $(0.190)$ & $(0.399)$ & $(0.519)$ & $(0.190)$ & $(0.517)$ \\ [0.5em]
		State Dummies & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\ \\ [-0.5em]
		\hline \\ [-0.5em] 
		Observations & 109 & 109 & 109 & 109  & 109    & 109  \\ [0.25em]
		R$^2$ & 0.9284  & 0.9399 &  0.9284 &  0.8643 &  0.9399 & 0.8642  \\  [0.25em]
		Chi$^2$ & $1414^{***}$ & $1732^{***}$ & $1427^{***}$ & $706^{***}$ & $1725^{***}$ &  $701^{***}$ \\
		\\ [-0.75em] 
		\hline \hline
	\end{tabular} 
\end{table}

\end{center}

\end{frame}

\begin{frame}{Fossil Fuel Results}

\begin{center}
	\includegraphics[width=0.9\textwidth]{exhibits/coal_natgas_scatter.pdf} 
\end{center}

\end{frame}

\begin{frame}{Fossil Fuel Results}

\begin{center}
	\includegraphics[width=0.9\textwidth]{exhibits/coal_oil_scatter.pdf} 
\end{center}

\end{frame}

\begin{frame}{Fossil Fuel Results}

\begin{center}
	\includegraphics[width=0.9\textwidth]{exhibits/oil_natgas_scatter.pdf} 
\end{center}

\end{frame}

\begin{frame}{Methodology - A Different Approach}

\metroset{block=fill}

\vspace{0.5em}

\begin{block}{\centering{CES Parameter Optimization}}
	$$\min_{\theta, \phi, \alpha, \beta} \; || - \ln \left( Q_{elec} \right) + \ln(\theta) + \frac{1}{\phi} \cdot \ln \left( \alpha_{coal} X_{coal}^\phi + \alpha_{natgas} X_{natgas}^\phi + \alpha_{oil} X_{oil}^\phi\right) + \beta \cdot D_{state} ||_2^2$$
\end{block}

\vspace{-1em}

\begin{itemize}

	\setlength\itemsep{1em}

	\item Can estimate all parameters at once using non-linear least squares

	\item $D_{state}$ represents indicator variables for each state

	\item Can also check fit statistics to see if CES functional form matches the data

\end{itemize}

\end{frame}

\begin{frame}{Results}

\fontsize{6pt}{7}\selectfont
\begin{center}
	\begin{table}
		\caption{CES Parameter Estimation for Fossil Fuels - NLS} 
		\begin{tabular}{l@{\extracolsep{5em}}cc@{\extracolsep{5em}}c}
			\\[-7ex]\hline  
			\hline \\[-1.2ex]  
			& \multicolumn{3}{c}{\textit{\scriptsize \textit{Dependent Variable}: Electricity Output from Fossil Fuels}} \\ [0.25em] 
			\cline{2-4}  \\[-0.5em] 
			& \multicolumn{3}{c}{$\ln(\theta) + \frac{1}{\phi} \cdot \ln \left( \alpha_{coal} X_{coal}^\phi + \alpha_{natgas} X_{natgas}^\phi + \alpha_{oil} X_{oil}^\phi\right) + \beta \cdot D_{state}$} \\ \\ [-0.7em]
			\hline \\[-1.2ex] 
			$\theta$     &  &       1.144         &       0.676\sym{***}\\
			&&     (0.609)         &    (0.0941)         \\
			[0.5em]
			$\phi$ &   &    \colorbox{yellow}{0.917\sym{***}}&       \colorbox{yellow}{0.900\sym{***}}\\
			&&    (0.0916)         &    (0.0658)         \\
			[0.5em]
			 $\ln(\alpha_{coal})$ &  &     0.533         &       1.147         \\
			&&     (0.433)         &         (.)         \\
			[0.5em]
			$\ln(\alpha_{natgas})$ &&      -1.323\sym{*}  &      -0.925\sym{***}\\
			&&     (0.536)         &     (0.165)         \\
			[0.5em]
			$\ln(\alpha_{oil})$ &   &    1.308         &      -25.94         \\
			&&         (.)         &         (.)         \\ [0.5em]
			State Dummies && \checkmark &   \\ \\ [-0.5em]
			\hline \\ [-0.5em] 
			Observations && 518 & 518  \\ [0.25em]
			R$^2$ & & 0.934   & 0.796    \\  [0.25em]
			Adj. R$^2$ &&  0.928   &  0.795   \\
			\\ [-0.75em] 
			\hline \hline
		\end{tabular} 
	\end{table}
\end{center}

\end{frame}

\begin{frame}{Fossil Fuel Results}

\metroset{block=fill}

\vspace{0.5em}

\begin{block}{\centering{CES $\to$ Cobb-Douglas}}
	$$ \lim_{\phi \to \, 0} \; \theta \cdot \left( \sum_i \; \alpha_i \cdot X_i^\phi \right)^{1/\phi} = \theta \cdot  \prod_i \;  X_i^{\alpha_i} $$
\end{block}

\vspace{-0em}

\begin{itemize}

	%\setlength\itemsep{1.5em}

	\item Elasticity of substitution ($\sigma = \frac{1}{1-\phi}$) varied by approach

	\begin{itemize}
		\item Ratios between commodities led to $\sigma$ around 1 (Cobb-Douglas)
		\item Non-linear least squares led to estimates around 10 (strong substitutes)
	\end{itemize}

	\item Could try estimating the Translog Function

	\begin{itemize}
		\item Second Order Taylor Polynomial of CES around $\phi = 0$
		\item Works best when $\phi \approx 0$ $\implies$ true function is almost Cobb-Douglas
	\end{itemize}

\end{itemize}

\end{frame}

\begin{frame}{Methodology - Renewables}

	\begin{itemize}
		\setlength\itemsep{1.5em}
		\item Still working on getting production costs for solar and wind

		\item Currently have solar and wind elasticities are estimated using 3SLS

		\item Structural Equation Model:

		\begin{itemize}
			\item Solar Supply%: Average Solar Radiation, Land Area
			\item Solar Demand%: Population, Cooling/Heating Degree Days
			\item Wind Supply%: Average Wind Speed, Land Area
			\item Wind Demand%: Population, Cooling/Heating Degree Days
		\end{itemize}

	\end{itemize}

\end{frame}

\begin{frame}{Methodology - Renewables}

\begin{itemize}
	\item Instrumental Variables Approach

	\begin{itemize}
		\item Are price and quantity changes caused by shifts in demand or shifts in supply?
		\item $Q_s = \beta_1 \cdot P + \gamma \cdot Z + \varepsilon_1$
		\item $Q_d = \beta_2 \cdot P + \varepsilon_2$
		\item Z is an instrument in the supply equation $\implies$ identifies the demand curve
		\item Must have $Z$ has independent of demand and good at explaining supply
	\end{itemize}

	\item Instruments for each equation

	\begin{itemize}
		\item Solar Supply: Average Solar Radiation, Land Area
		\item Solar Demand: Population, Cooling/Heating Degree Days
		\item Wind Supply: Average Wind Speed, Land Area
		\item Wind Demand: Population, Cooling/Heating Degree Days
	\end{itemize}

\end{itemize}

\end{frame}

\begin{frame}{Methodology - Renewables}

\begin{itemize}
	\setlength\itemsep{1.5em}

	\item Solar Supply Instruments

	\begin{itemize}
		\item Solar energy generation $\approx$ Efficiency $\cdot$ Area $\cdot$ \textbf{Radiation}
		\item Taking logs $\implies$ $\ln(solar\,generation)$ is linear with $\ln(solar\,radiation)$ 
		\item \textbf{Land area} does not seem to have a log-log relationship with $\ln(solar\,generation)$
	\end{itemize}

	\item Solar Demand Instruments

	\begin{itemize}
		\item \textbf{Population} likely multiplicative with solar generation $\implies$ linear function with logs
		\item \textbf{Cooling/Heating Degree Days} - number of degrees that a day's average temperature is below/above room temperature
	\end{itemize}

\end{itemize}

\end{frame}

\begin{frame}{Methodology - Renewables}

\begin{itemize}
	\item Wind Supply Instruments

	\begin{itemize}
		\item \textbf{Land area} used again here
		\item Wind generation seems to increase exponentially with \textbf{wind speed} in theory
		\item Again, taking logs $\implies \ln(wind\,generation)$ is linear with $(average\,wind\,speed)$
	\end{itemize}

	\begin{center}
		\includegraphics[width=0.4\textwidth]{exhibits/windpowercurve.png} 
	\end{center}

	\item Wind Demand Instruments are the same as those for solar

\end{itemize}

\end{frame}

\begin{frame}

\fontsize{6pt}{7}\selectfont
\begin{center}
	\begin{table}
		\caption{Elasticities for Solar and Wind - 3SLS Estimation} 
		\begin{tabular}{l*{4}{c}}
			\\[-7ex]\hline  
			\hline \\[-1.2ex]  
			& \multicolumn{4}{c}{\textit{\scriptsize Dependent Variable}} \\ [0.25em] 
			\cline{2-5}  \\[-.5em] 
			& ln(Solar Net Gen) & ln(Solar Net Gen) & ln(Wind Net Gen) & ln(Wind Net Gen) \\ \\ [-0.7em]
			\hline \\[-1.5ex] 
			log(Electricity Price)       &       \colorbox{yellow}{14.46\sym{***}}&     \colorbox{yellow}{ -4.619\sym{*}}  &       \colorbox{yellow}{4.997\sym{***}}&      \colorbox{yellow}{-16.98\sym{***}}\\
			$(cents/kWh)$&     (1.597)         &     (1.911)         &     (1.487)         &     (4.086)         \\
			[0.5em]
			log(Average Solar Radiation)     &       101.5\sym{*}  &                     &                       &                     \\
			$(kWh/m^2)$&     (51.33)         &                     &                     &                     \\
			[0.5em]
			Log(Average Wind Speed)&                     &                     &       0.678\sym{***}&                     \\
			$(m/s)$&                     &                     &    (0.0811)         &                     \\
			[0.5em]
			Land Area    &    1.14e-11\sym{***}&                     &    1.41e-11\sym{***}&                     \\
			$(m^2)$&  (1.16e-12)         &                     &  (9.79e-13)         &                     \\
			[0.5em]
			Log(Population)      &                     &       1.085\sym{***}&                     &       1.166\sym{***}\\
			&                     &     (0.136)         &                     &     (0.286)         \\
			[0.5em]
			Log(Cooling Degree Days)      &                     &      -0.164         &                     &      -0.322         \\
			&                     &     (0.102)         &                     &     (0.191)         \\
			[0.5em]
			Log(Heating Degree Days)      &                     &      -0.169         &                     &     -0.0660         \\
			&                     &     (0.101)         &                     &     (0.182)         \\
			[0.5em]
			Constant      &      -66.97\sym{***}&       7.541         &      -24.11\sym{***}&       65.21\sym{***}\\
			&     (7.367)         &     (7.963)         &     (6.961)         &     (16.81)         \\ \\ [-0.5em] 
			State Dummies &     \checkmark       &    \checkmark     &    \checkmark     &   \checkmark       \\ \\ [-0.5em] 
			\hline \\ [-0.5em] 
			Obs       &         504         &   504                  &            504         &              504       \\
			Chi$^2$        &       109.3$^{***}$         &       81.32$^{***}$         &       76.64$^{***}$         &       41.26$^{***}$         \\\\ [-0.75em] 
			\hline \hline
		\end{tabular}
	\end{table}
\end{center}

]\end{frame}

\begin{frame}{Future Work}

\begin{itemize}
	\setlength\itemsep{1.5em}
	\item Working on non-linear least squares approach for renewables

	\item Adding biomass, hydroelectric, nuclear, and geothermal elasticities

	\item Elasticity of substitution between clean and dirty energy

	\item Can verify final results with price elasticity estimates

\end{itemize}

\end{frame}

\section{Questions?}

\end{document}

### 2019-04-20 documents/draft.tex
Update draft
- more on comparative statics
- proof for tax in producer surplus case

@@
 So, for example, an increase in the output efficiency of solar or a decrease in solar's cost will reduce the optimal quantity of coal power.
-\hfill \\\\
+To find the effects of $\alpha$ on $X$, we must assume one of the cases of restrictions shown in \ref{tab:paramrest}{Table 1}.
+So, assume Case 1 is true; this implies that $X_2$ is optimal in period $t$ and $X_1$ is optimal in period $s$.
+Additionally, note that $\alpha$ determines demand for electricity in a period.
+Hence, when $\alpha_t$ rises, we see the optimal level of $X_2$ rise as well; likewise, $X_1$ rises with $\alpha_s$.
+So, essentially, the optimal quantity of a technology rises with the demand shifter $alpha$ of the period that the technology is optimal in.
+This concept carries through for the comparative statics of $Z$.
+When the output efficiency of technology 1 rises or its cost falls, we see output $Z_s$ rise and output $Z_t$ fall.
+This is because technology 1 is optimal in period $s$ given the Case 1 restrictions.
+Moreover, we would see symmetrical results for the output with respect to the cost and output efficiency of technology 2.
+In total, the comparative statics do not imply any surprising relationships.
+
+\hfill \\
 \begin{proof}
@@
 \begin{pmatrix}
-< 0 \\
-> 0 
+> 0 \\
+< 0 
 \end{pmatrix} \\
@@
 \begin{pmatrix}
-> 0 \\
-< 0 
+< 0 \\
+> 0 
 \end{pmatrix}
 \end{alignat*}
-From our restrictions, we have
-
+From our restrictions, we have $\xi_{1s}\xi_{2t} > \xi_{2s}\xi_{1t}$, and all the results above follow from this. 
+\begin{alignat*}{2}
+\frac{\partial Z_t}{\partial \xi} &= 
+\begin{pmatrix}
+\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} & \dfrac{-\alpha _{t}\,\xi _{\mathrm{2s}}\,\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} \\
+\dfrac{-\alpha _{t}\,\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} & \dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} \\
+\end{pmatrix}
+&&=
+\begin{pmatrix}
+< 0 & < 0  \\
+> 0 & > 0
+\end{pmatrix} \\
+\frac{\partial Z_s}{\partial \xi} &= 
+\begin{pmatrix}
+\dfrac{-\alpha _{s}\,\xi _{\mathrm{2t}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}& \dfrac{\alpha _{s}\,\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}\\
+\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} & \dfrac{-\alpha _{s}\,\xi _{\mathrm{1t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}\\
+\end{pmatrix}
+&&=
+\begin{pmatrix}
+> 0 & > 0 \\
+< 0 & < 0  
+\end{pmatrix}
+\end{alignat*}
+Again, recall that we have $c_1 \xi_{2t} - c_2 \xi_{1t} > 0$ and $c_2 \xi_{1s} - c_1 \xi_{2s} > 0$; the rest follows. And finally, we have:
+\begin{align*}
+\frac{\partial Z_t}{\partial \alpha} &= 
+\begin{pmatrix}
+\dfrac{-\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} \\
+0
+\end{pmatrix}
+=
+\begin{pmatrix}
+> 0 \\
+0 
+\end{pmatrix} \\
+\frac{\partial Z_s}{\partial \alpha} &= 
+\begin{pmatrix}
+0 \\
+\dfrac{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}
+\end{pmatrix}
+=
+\begin{pmatrix}
+0 \\
+> 0 
+\end{pmatrix}
+\end{align*}
+These are fairly trivial, since $Z_t = \alpha_t / p_t$ (and $Z_s = \alpha_s/ p_s$) and prices are positive. \\
 \hfill
 \end{proof}
-
-\clearpage
 
@@
 Instead, let us consider a practical example to simplify the problem.
-Suppose that our first, pollution-creating technology is coal power while the second technology is solar power.
-Furthermore, assume that solar power produces during period $t$ but not during period $s$, so that we have $\xi_{2s} = 0$.
-This greatly simplifies the FOC and implies the following optimal tax:
+Suppose again that our first, pollution-creating technology is coal power while the second technology is solar power.
+Furthermore, assume that solar power produces during period $t$ but not during period $s$ so that we have $\xi_{2s} = 0$.
+This greatly simplifies the FOC which then implies the following optimal tax:
 $$\tau \, = \,  \gamma \, - \, c_1 \, +  \hspace{-1.5em} \underbrace{(c_2 \, \xi_{1t})/ \xi_{2t}}_\textrm{Intermittency Adjustment}$$
+Interestingly, this tax is larger than the standard tax in the zero profit case: $\gamma - c_1$.
+Moreover, this tax scales with the cost and output efficiency of our second technology.
+That is, as solar becomes more cost efficient, the tax required to correct for the externalities of coal approaches the standard level.
+At the same time, the tax also must increase with the output efficiency of coal.
+This is far from
 
+%%% Consider case with producer surplus
 \hfill \\
@@
 \end{align*}
+Next, we may consider the case where $\partial PS / \partial \tau$ is non-zero. That is, we allow $C(X)$, the cost of the technologies, to be nonlinear. Our general FOC is then:
+\begin{align*}
+0 &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial C(X)}{\partial \tau}\\
+\frac{\partial C(X)}{\partial \tau} &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} \\
+\frac{ \partial  C(X)}{\partial p} \frac{\partial p}{\partial \tau}  &= \frac{\partial CS}{\partial p} \frac{\partial p}{\partial \tau} + \frac{\partial PS}{\partial \tau} \\
+\gamma \left( \eta_{1,1}^2 \alpha_t / p_t^2 + \eta_{2,1}^2 \alpha_s / p_s^2 \right) &= \eta_{1,1} \alpha_t /p_t + \eta_{2,1} \alpha_s / p_s - \frac{\partial PS}{\partial \tau} 
+\end{align*}
+When we allow $\xi_{2s} = 0$, this simplifies to 
+$$\frac{\alpha _{s}\pm\sqrt{{\alpha _{s}}^2-4\,\frac{\partial PS}{\partial \tau} \,\alpha _{s}\,\mathrm{\gamma}}}{2\,\frac{\partial PS}{\partial \tau} } - c_1 + (c_2\,\xi_{1t})/\xi_{2t}$$
+This suggests there are two solutions; however, we can reduce this to one.
+Since the limit  of this equation as $\frac{\partial PS}{\partial \tau} \to 0$ must be $\gamma - c_1 + (c_2\,\xi_{1t})/\xi_{2t}$, we have:
+\begin{align*}
+\gamma - c_1 + (c_2\,\xi_{1t})/\xi_{2t} &= \lim_{\frac{\partial PS}{\partial \tau} \to 0} \left( \frac{\alpha _{s}\pm\sqrt{{\alpha _{s}}^2-4\,\frac{\partial PS}{\partial \tau} \,\alpha _{s}\,\mathrm{\gamma}}}{2\,\frac{\partial PS}{\partial \tau} } - c_1 + (c_2\,\xi_{1t})/\xi_{2t} \right) \\
+&= \lim_{\frac{\partial PS}{\partial \tau} \to 0} \left( \frac{\alpha _{s}\pm\sqrt{{\alpha _{s}}^2-4\,\frac{\partial PS}{\partial \tau} \,\alpha _{s}\,\mathrm{\gamma}}}{2\,\frac{\partial PS}{\partial \tau} } \right) - c_1 + (c_2\,\xi_{1t})/\xi_{2t}  \\
+&= \lim_{\frac{\partial PS}{\partial \tau} \to 0} \left( \pm 
+\frac{\left( (0.5)(-4\alpha_s \gamma) \right) \left( \alpha_s^2 - 4 \frac{\partial PS}{\partial \tau} \alpha_s \gamma \right)^{-0.5} }{2}
+ \right) - c_1 + (c_2\,\xi_{1t})/\xi_{2t}  \\
+\implies \gamma &= \lim_{\frac{\partial PS}{\partial \tau} \to 0} \left( \pm 
+\left( (-\alpha_s \gamma) \right) \left( \alpha_s^2 - 4 \frac{\partial PS}{\partial \tau} \alpha_s \gamma \right)^{-0.5} 
+\right) \\
+&=  \pm 
+\left( -\alpha_s \gamma \right)\alpha_s^{-1} \\
+&=  \pm (- \gamma)
+\end{align*}
+where L'Hopitals was used in the third step. Hence, the correct solution is:
+$$\frac{\alpha _{s} - \sqrt{{\alpha _{s}}^2-4\,\frac{\partial PS}{\partial \tau} \,\alpha _{s}\,\mathrm{\gamma}}}{2\,\frac{\partial PS}{\partial \tau} } - c_1 + (c_2\,\xi_{1t})/\xi_{2t}$$
+
 \end{proof}
@@
 \section{Scratch}
-
-\begin{align*}
-\partial X / \partial \xi_{1,t} &= \left(\begin{array}{c} \frac{\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}\\ -\frac{\alpha _{s}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}-\frac{\alpha _{s}\,c_{2}\,\xi _{\mathrm{1t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} \end{array}\right) \\
-\partial X / \partial \xi_{1,s} &= \left(\begin{array}{c} \frac{\alpha _{t}\,c_{2}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}\\ -\frac{\alpha _{t}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}-\frac{\alpha _{t}\,c_{2}\,\xi _{\mathrm{1s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} \end{array}\right)\\
-\partial X / \partial \xi_{2,t} &= \left(\begin{array}{c} \frac{\alpha _{s}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}-\frac{\alpha _{s}\,c_{1}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}\\ \frac{\alpha _{s}\,c_{1}\,\xi _{\mathrm{1t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} \end{array}\right)\\
-\partial X / \partial \xi_{2,s} &= \left(\begin{array}{c} \frac{\alpha _{t}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}-\frac{\alpha _{t}\,c_{1}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}\\ \frac{\alpha _{t}\,c_{1}\,\xi _{\mathrm{1s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} \end{array}\right)\\
-\partial X / \partial c_{1} &= \left(\begin{array}{c} -\frac{\alpha _{t}\,{\xi _{\mathrm{2s}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}-\frac{\alpha _{s}\,{\xi _{\mathrm{2t}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}\\ \frac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}+\frac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} \end{array}\right) \\
-\partial X / \partial c_2 &= \left(\begin{array}{c} \frac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}+\frac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}\\ -\frac{\alpha _{t}\,{\xi _{\mathrm{1s}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}-\frac{\alpha _{s}\,{\xi _{\mathrm{1t}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} \end{array}\right)
-\end{align*}
-
-\begin{align*}
-\partial P / \partial \xi_{1,t} &= \left(\begin{array}{c} -\frac{\xi _{\mathrm{2s}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2}\\ \frac{\xi _{\mathrm{2s}}\,\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2}-\frac{c_{2}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}} \end{array}\right)\\
-\partial P / \partial \xi_{1,s} &= \left(\begin{array}{c} \frac{c_{2}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}+\frac{\xi _{\mathrm{2t}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2}\\ -\frac{\xi _{\mathrm{2t}}\,\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2} \end{array}\right)\\
-\partial P / \partial \xi_{2,t} &= \left(\begin{array}{c} \frac{\xi _{\mathrm{1s}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2}\\ \frac{c_{1}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}-\frac{\xi _{\mathrm{1s}}\,\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2} \end{array}\right) \\
-\partial P / \partial \xi_{2,s} &= \left(\begin{array}{c} -\frac{c_{1}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}-\frac{\xi _{\mathrm{1t}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2}\\ \frac{\xi _{\mathrm{1t}}\,\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2} \end{array}\right) \\
-\partial P / \partial c_1 &= \left(\begin{array}{c} -\frac{\xi _{\mathrm{2s}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}\\ \frac{\xi _{\mathrm{2t}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}} \end{array}\right)\\
-\partial P / \partial c_2 &= \left(\begin{array}{c} \frac{\xi _{\mathrm{1s}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}\\ -\frac{\xi _{\mathrm{1t}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}} \end{array}\right)
-\end{align*}
-
-$$ \partial P_s / \partial \xi_{1,t} < 0 \iff  \frac{\xi _{\mathrm{2t}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2}<0$$
 

### 2019-04-23 documents/draft.tex
Update draft and code
- added to introduction
- fixed proofs for taxes

@@
-\documentclass[12pt,a4paper]{extarticle}
+\documentclass[11pt,a4paper]{extarticle}
 \usepackage[margin=1in]{geometry}
@@
 \usepackage{multirow}
+\usepackage{xcolor}
 %\usepackage{showframe}
@@
 % hyperlinks
+\definecolor{darkblue}{RGB}{0,0,150}
 \hypersetup{
@@
 	urlcolor  = blue,
-	citecolor = blue,
+	citecolor = darkblue,
 	anchorcolor = blue
@@
 
-\section{Introduction}
+\section{Outline}
 \dots
@@
 
-By intermittency, we mean variation in output over time due to technical constraints; on the other hand, we define reliability as stochastic variation in output.
-For instance, solar power is intermittent while coal power is not.
-We focus on modeling intermittency but ignore reliability to keep our model tractable and its implications clear.
+Renewable energy technologies have seen considerable adoption over the last few decades (EIA 2019).
+Unlike the alternatives, wind and solar power are particularly unique in that the amount of energy they supply is intermittent.
+Consequently, designing economically efficient policy to promote their adoption is not straightforward given that they cannot easily substitute for traditional technologies such as coal power which handles base load demand.
+Moreover, simpler approaches, such as using the levelized cost of electricity (LCOE) to compare technologies is flawed in any setting with variable electricity prices.
+In particular, \citet{Joskow2011} argues that
+
+\begin{quote}
+	``Instead [of using metrics like LCOE], the economics of all generating technologies, both intermittent and dispatchable, can be evaluated based on the expected market value of the electricity that
+	they will supply, their total life-cycle costs, and their associated expected profitability. Such an
+	analysis would reflect the actual expected production profiles of dispatchable and intermittent
+	technologies, the value of electricity supplied at different times, and other costs of intermittency
+	associated with reliable network integration. This is exactly the way investors in merchant generating plants evaluate whether or not to invest."
+\end{quote}
+We structure our model with this critique in mind.
+Specifically, we develop a model where producers optimize the supply of each generation technology on the expected market value of the electricity produce.
+We do so by
+
+Some of the literature has approached the problem by constructing numerical models that find the cheapest renewable technology set while accounting for intermittent supply.
+\citet{MN2006} model uncertain renewable output with intertemporal generation constraints, while \citet{NCK2007} model temporal and spatial characteristics of wind output to optimize its deployment in the UK.
+On the other hand, other literature focuses on the effect of intermittent technologies on the market itself; \citet{AC2012} study the interaction between intermittent renewables and traditional reliable sources of energy in decentralized markets, and \citet{Chao2011} models alternative pricing mechanisms for intermittent renewable energy sources.
+Additionally, \citet{Boren2012} reviews the effects of present public policies used to promote renewables and the challenges posed by intermittency.
+
+Our model comes closest to that of \citet{HH} who build a peak-load pricing model where the availability of renewable capacity varies stochastically.
+This stochastic variability models the intermittency and affects the adoption of renewables in a market with dynamic pricing.
+Furthermore, they simplify their analysis by setting aside complications such as  outage costs and rationing rules.
+In total, their model finds an S-shaped adoption curve for renewables once their LCOE's reach those of fossil fuel energy.
+In addition, they find that a Pigouvian tax can properly internalize the costs of fossil fuels in a setting with perfect competition.
+Likewise, our model makes equivalent simplifications and finds similar results on an equilibrium in  amarket with dynamic prices.
+But, our representation of the intermittency of renewables differs in a significant way.
+
+To highlight this difference, we must first contrast the terms  \textit{intermittency} and \textit{reliability}.
+By intermittency, we mean uncontrollable variation in output over time due to physical constraints; by reliability, we mean variation in output that is wholly unpredictable\footnote{By unpredictible, we mean a notion similar to that of \textit{Knightian uncertainity} \citep{Knight}.
+} and may be the result of failures that cannot be modeled stochastically.
+Consider wind energy as an example.
+The energy provided by a wind turbine necessarily varies over time due to differences in wind speed and direction.
+Moreover, the relationship between the force created by the wind and the amount of wind power generated must necessarily be a fixed, functional relationship; that is, \textit{ceterius paribus}, two identical wind turbines under identical wind conditions should generate the same amount of energy.
+Consequently, the output of wind power can be forecasted\footnote{\citet{Foley2012} provide a review of the literature on the forecasting of wind power and advancements over time} up to an error term.
+Because no forecast of wind (or solar) power can be perfect, some level of weather-related intermittency may be left in the error term.
+At the same time, the error term also captures unreliability; for instance, failures in the circuitry of wind turbines cannot be forecasted as a time series.
+So, overall, we may think of the energy output of a renewable technology as consisting of three components: a knowable/forecastable component related to intermittency, a stochastic component related to intermittency, and an unpredictible component related to reliability.
+
+While \citet{HH} model the stochastic component of intermittency, we model the predictible component.
+More specifically, Helm and Mier model the capacity of renewable energy equal to a baseline capacity multiplied by a uniform random variable between 0 and 1.
+This is a valid approach given that their model consists of a single period of generation.
+On the other hand, we neglect stochastic intermittency for parsimony and develop a general, multi-period model where the output per unit of each technology follows a known function.
+We then narrow this to a two period, two technology model where our first technology represents fossil fuel energy with constant output in both periods while our second technology's output differs between each period.
+Additionally, while their model consists of two sets of consumers, one set which receives fixed price contracts and another paying real time prices, we consider one representative consumer.
+Specifically, this representative consumer's utility is given by CES function where each good is electricity consumption differentiated by time; this approach was first set forth by \citet{Moha2016}.
+Interestingly, this treatment of intermittency produces some key results similar to that of Helm and Mier.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%% Summary of results
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 We model electricity as a heterogenous good which is differentiated by its delivery time.
-Then, we consider a representative consumers who purchases varying quantities of electricity over time in order to maximize utility.
-Obviously, consumers would prefer to spread their electricity consumption out over time; the convexity of the indifference surfaces of a standard CES function can model this preference quite simply.
-Next, we model the electricity sector using a representative firm that chooses a set of electricity-generating inputs to maximize profit; some of these inputs are intermittent - they generate a non-constant amount of energy over time.
-These two sides of the market reach an equilibrium through adjustments in prices of electricity in each period.
+Then, we consider a representative consumer who purchases varying quantities of electricity in each period in order to maximize utility.
+Generally, people prefer to spread their electricity consumption out over time; the convexity of the indifference surfaces of a standard CES function can model this preference in a simple way.
+Next, we model the electricity sector using a representative firm that chooses a set of electricity-generating inputs to maximize profit; some of these inputs are intermittent - they generate a differing amounts of energy in each period.
+These two sides of the market reach an equilibrium through adjustments in prices of electricity in each period.\footnote{While, in reality, consumers generally pay fixed rates for electricity, \citeauthor{HH} provide a motivation for models incorporating dynamic pricing; they argue such approaches to pricing will become the norm with further technological advances and coming regulatory changes.
+} For simplicity, we do not allow for load rationing  or negative prices.
+And, again for simplicity, we assume that the output of all technologies in each period does not vary stochastically.
 
@@
 where $P$ is the price index.
+This model naturally does not allow for blackouts in equilibrium, since the price of electricity in any period gets arbitrarily large as the quantity of energy consumed in that period falls.
 
@@
 Secondly, we limit the number of periods and technologies to 2.
+And, thirdly, we normalize the prices such that the budget is $1$.
 Consequently, our demand equations simplify to:
@@
 Hence, when $\alpha_t$ rises, we see the optimal level of $X_2$ rise as well; likewise, $X_1$ rises with $\alpha_s$.
-So, essentially, the optimal quantity of a technology rises with the demand shifter $alpha$ of the period that the technology is optimal in.
+So, essentially, the optimal quantity of a technology rises with the demand shifter $\alpha$ of the period that the technology is optimal in.
 This concept carries through for the comparative statics of $Z$.
@@
 Moreover, we would see symmetrical results for the output with respect to the cost and output efficiency of technology 2.
-In total, the comparative statics do not imply any surprising relationships.
+In total, the comparative statics are fairly straightforward.
 
@@
 
+\subsubsection{Technical Change and Market Shares}
+
+Like \cite{HH} we find an S-shaped adoption curve for renewable energy driven by intermittency.\footnote{\citet{HH} reference \citet{Geroski2000} who provides a survey of the literature on adoption of new technologies.
+He finds that S-shaped adoption curves are often generated by information cascades.
+On the other hand, our model and that of Helm and Mier find S-shaped curves as a result of intermittency slowing down adoption.}
+
 \subsubsection{Externalities}
 
-Now, suppose that our first technology, which again may be coal power, produced negative externalities.
-Specifically, the social cost of pollution is given by $C(X) = \gamma X_1$ where $\gamma$ is the monetary damage per unit of $X_1$.
-A social planner is interested in balancing the damages caused by pollution with the surplus of the private sector.
+Often times, a social planner may also be interested in using other policy instruments such as research subsidies.
+In fact, \citet{Ace2012} find that both carbon taxes and research subsidies are necessary to promote long-run structural change in the energy production sector and avert a climate disaster.
+While our model focuses on production on a shorter time scale, we find a similar result -- a combination of both taxes and subsidies may be more effective in promoting a shift towards clean energy.
+
+Firstly, consider a case where a carbon tax is our only policy instrument.
+Additionally, suppose that our first technology produced negative externalities.
+Specifically, the social cost of pollution is given by $S(X) = \gamma X_1$ where $\gamma$ is the monetary damage per unit of $X_1$.
+A social planner is interested in balancing the damages caused by pollution with the surplus of the private sector and the revenue from the tax.
 That is, they aim to solve
-$$\max_{\tau} \; CS + PS - C(X)$$
-where $\tau$ is the tax on $X_1$, so that its final price is $c_1 + \tau$.
-The traditional solution, a Pigouvian tax, simply sets the tax equal to the marginal social damage of pollution: $\tau = \gamma$.
-In our particular case, the producer faces a linear cost function resulting in $PS = 0$.
-Consequently, the solution in this case is to set the cost of the polluting technology directly equal to its social cost using $\tau = \gamma - c_1$.
+$$\max_{\tau} \; CS + PS - S(X) + \tau X_1$$
+where $\tau$ is the tax on $X_1$, so that its final price is $c_1 + \tau$ and the tax revenue is given by $\tau X_1$.
+The optimal tax is a Pigouvian tax; $\tau$ should be set equal to the marginal social cost of pollution $\gamma$.
+This is an expected, standard solution in most models.
 
-But, the latter is not always the optimal solution in our model.
-In fact, it is a special case when each technology produces in one unique period.
-To see why, suppose, without loss of generality, that the first technology only produces in the first period and the second only produces in the second period.
-In other words, with periods $t$ and $s$, we have $\xi_{1s} = \xi_{2t} = 0$; this means $X_1$ is the only source of $Z_t$ while $X_2$  is the only source of $Z_s$.
-Since the demand functions of $Z_t$ and $Z_s$ are independent of $p_s$ and $p_t$ respectively, we can treat this case as two seperate markets for two seperate commodities.
-Consequently, since producer surplus is fixed, the optimal tax is given by $\tau = \gamma - c_1$.
+%%% Pigouvian tax proof
+\hfill \\
+\begin{proof} We aim to maximize welfare with respect to the tax $\tau$, hence our first order condition is:
+\begin{align*}
+0 &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial S(X)}{\partial \tau} + \frac{\partial \tau X_1}{\partial \tau} \\
+&=  \left( \underbrace{\frac{\partial CS}{\partial p}  + \frac{\partial PS}{\partial p}}_{= 0} - \frac{ \partial  S(X)}{\partial p} + \frac{\partial \tau X_1}{\partial p} \right) \frac{\partial p}{\partial \tau} \\
+&=  - \gamma \frac{\partial  X_1}{\partial p} + \tau \frac{\partial  X_1}{\partial p}
+\end{align*}
+where the derivatives of producer and consumer surplus are eliminated by the envelope theorem. Therefore, we must have $\tau = \gamma$. \\
+\hfill
+\end{proof}
 
-However, now suppose that both technologies produce in both periods. We then solve the social planner's welfare maximization problem by finding a solution to the first-order condition:
-$$\frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial C(X)}{\partial \tau} = 0$$
-The optimal solution is characterized by the following first-order condition in terms of $p$.
-$$
-\gamma \left( \eta_{1,1}^2 \alpha_t / p_t^2 + \eta_{2,1}^2 \alpha_s / p_s^2 \right) = \left(\eta_{1,1} \alpha_t /p_t + \eta_{2,1} \alpha_s / p_s \right) $$
-This itself does not provide a straightforward solution to $\tau$.
-Instead, let us consider a practical example to simplify the problem.
-Suppose again that our first, pollution-creating technology is coal power while the second technology is solar power.
-Furthermore, assume that solar power produces during period $t$ but not during period $s$ so that we have $\xi_{2s} = 0$.
-This greatly simplifies the FOC which then implies the following optimal tax:
-$$\tau \, = \,  \gamma \, - \, c_1 \, +  \hspace{-1.5em} \underbrace{(c_2 \, \xi_{1t})/ \xi_{2t}}_\textrm{Intermittency Adjustment}$$
-Interestingly, this tax is larger than the standard tax in the zero profit case: $\gamma - c_1$.
-Moreover, this tax scales with the cost and output efficiency of our second technology.
-That is, as solar becomes more cost efficient, the tax required to correct for the externalities of coal approaches the standard level.
-At the same time, the tax also must increase with the output efficiency of coal.
-This is far from
+Now, suppose that we may also subsidize research which improves the output efficiency of a technology.
+In particular, we let the output efficiency of technology 2 be $(\xi_{2t}, \, \xi_{2s})(1 + \beta)$ where $\beta$ is the percent improvement created by research.
+And, we let the cost of research be given by a convex, differentiable function $G(\beta)$.
 
-%%% Consider case with producer surplus
 \hfill \\
-\begin{proof}
-Firstly, since our producer surplus is fixed due to linear costs, we have $\frac{\partial PS}{\partial \tau} = 0$.
-Now, we find the effect on consumer surplus.
-Letting $\eta = \xi^{-1}$, note that we have
-$$\frac{\partial CS}{\partial p} = 
-\begin{pmatrix}
--\alpha_t / p_t \\
--\alpha_s / p_s
-\end{pmatrix}
-\qquad
-\frac{\partial p}{\partial \tau} =
-\partial
-\left( 
-\eta
-\begin{pmatrix}
-c_1 + \tau \\
-c_2
-\end{pmatrix}
-\right)
-/ \partial \tau
-=
-\begin{pmatrix}
-\eta_{1,1} \\
-\eta_{2,1}
-\end{pmatrix}
-$$
-Next, we find the partial derivatives for the equilibrium quantity of $X_1$. 
+\begin{proof} First, note that we have:
+$$X_1 = \dfrac{\alpha _{t}\,(1+\beta) \, \xi_{\mathrm{2s}}}{(c_{1}+ \tau)\,(1+\beta)\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}+\dfrac{\alpha _{s}\,(1+\beta)\,\xi _{\mathrm{2t}}}{(c_{1}+ \tau)\,(1+\beta)\,\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}$$
+
+We aim to maximize welfare with respect to the tax $\tau$ and the research efficiency modifier $\beta$, hence our first order condition is:
 \begin{align*}
-Z \equiv \xi^T X &\implies X = \eta^T Z \\
-&\implies X_1 = \eta_{1,1} Z_t + \eta_{2,1} Z_s 
+0 	 &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial S(X)}{\partial \tau} + \frac{\partial \tau X_1}{\partial \tau}  - \frac{\partial G(\beta)}{\partial \beta}\\
+	 &=  \left( \underbrace{\frac{\partial CS}{\partial p}  + \frac{\partial PS}{\partial p}}_{= 0} - \frac{ \partial  S(X)}{\partial p} + \frac{\partial \tau X_1}{\partial p} - \frac{\partial G(\beta)}{\partial p} \right) \frac{\partial p}{\partial \tau} \\
+	 &=  - \gamma \frac{\partial  X_1}{\partial p} + \tau \frac{\partial  X_1}{\partial p} - \frac{\partial G(\beta)}{\partial p} \\
+\tau &= \gamma + \frac{\partial G(\beta)}{\partial X_1}
 \end{align*}
-$$\frac{\partial X_1}{\partial p} = 
-\begin{pmatrix}
--\eta_{1,1} \alpha_t / p_t^2 \\
-- \eta_{2,1} \alpha_s / p_s^2 
-\end{pmatrix}
-$$
-Finally, we may solve for the first-order condition.
-\begin{align*}
-0 &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial C(X)}{\partial \tau}\\
-\frac{\partial C(X)}{\partial \tau} &= \frac{\partial CS}{\partial \tau}\\
-\frac{ \partial  C(X)}{\partial p} \frac{\partial p}{\partial \tau}  &= \frac{\partial CS}{\partial p} \frac{\partial p}{\partial \tau}\\
-\gamma \left( \eta_{1,1}^2 \alpha_t / p_t^2 + \eta_{2,1}^2 \alpha_s / p_s^2 \right) &= \eta_{1,1} \alpha_t /p_t + \eta_{2,1} \alpha_s / p_s
-\end{align*}
-Plugging in for $p$ with $(c_1 + \tau, c_2)^T$ yields the following FOC with three roots for $\tau$.
+where the derivatives of producer and consumer surplus are eliminated by the envelope theorem. Equivalently, if we take the derivative of the welfare function with respect to $\beta$, we find that:
+$$G(\beta) = -\gamma + \frac{\partial \tau}{\partial X_1}$$
+\hfill
+\end{proof}
 
-$$-\frac{\alpha _{t}\,\mathrm{\gamma}\,{\xi _{\mathrm{1t}}}^2\,{\xi _{\mathrm{2s}}}^4}{{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2\,{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}+\tau \,\xi _{\mathrm{2s}}\right)}^2}-\frac{\alpha _{s}\,\mathrm{\gamma}\,{\xi _{\mathrm{2s}}}^2\,{\xi _{\mathrm{2t}}}^2}{{c_{2}}^2\,{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2} $$
-$$ = 	
-\frac{c_{2}\,\xi _{\mathrm{2s}}\,\left(\alpha _{s}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}+\alpha _{t}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)-\alpha _{s}\,{\xi _{\mathrm{2s}}}^2\,\xi _{\mathrm{2t}}\,\left(c_{1}+\tau \right)}{c_{2}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}+\tau \,\xi _{\mathrm{2s}}\right)}
-$$
-If we allow $\xi_{2s} = 0$, then this simplifies to
-\begin{align*}
--\frac{\alpha _{s}\,\mathrm{\gamma}\,{\xi _{\mathrm{2t}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}+\tau \,\xi _{\mathrm{2t}}\right)}^2} &= -\frac{\alpha _{s}\,\xi _{\mathrm{2t}}}{\xi _{\mathrm{2t}}\,\left(c_{1}+\tau \right)-c_{2}\,\xi _{\mathrm{1t}}}\\
-0 &= \frac{\alpha _{s}\,{\xi _{\mathrm{2t}}}^2\,\left(c_{1}-\mathrm{\gamma}+\tau \right)-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}+\tau \,\xi _{\mathrm{2t}}\right)}^2} \\
-\alpha_s \xi_{2t}^2 (c_1 - \gamma + \tau) &= \alpha_s c_2 \xi_1t \xi_2t
- \\
-\xi_{2t} (c_1 - \gamma + \tau) &=  c_2 \xi_{1t}\\
-\tau &= 
-\gamma - c_1 + (c_2\,\xi_{1t})/\xi_{2t}
-\end{align*}
-Next, we may consider the case where $\partial PS / \partial \tau$ is non-zero. That is, we allow $C(X)$, the cost of the technologies, to be nonlinear. Our general FOC is then:
-\begin{align*}
-0 &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial C(X)}{\partial \tau}\\
-\frac{\partial C(X)}{\partial \tau} &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} \\
-\frac{ \partial  C(X)}{\partial p} \frac{\partial p}{\partial \tau}  &= \frac{\partial CS}{\partial p} \frac{\partial p}{\partial \tau} + \frac{\partial PS}{\partial \tau} \\
-\gamma \left( \eta_{1,1}^2 \alpha_t / p_t^2 + \eta_{2,1}^2 \alpha_s / p_s^2 \right) &= \eta_{1,1} \alpha_t /p_t + \eta_{2,1} \alpha_s / p_s - \frac{\partial PS}{\partial \tau} 
-\end{align*}
-When we allow $\xi_{2s} = 0$, this simplifies to 
-$$\frac{\alpha _{s}\pm\sqrt{{\alpha _{s}}^2-4\,\frac{\partial PS}{\partial \tau} \,\alpha _{s}\,\mathrm{\gamma}}}{2\,\frac{\partial PS}{\partial \tau} } - c_1 + (c_2\,\xi_{1t})/\xi_{2t}$$
-This suggests there are two solutions; however, we can reduce this to one.
-Since the limit  of this equation as $\frac{\partial PS}{\partial \tau} \to 0$ must be $\gamma - c_1 + (c_2\,\xi_{1t})/\xi_{2t}$, we have:
-\begin{align*}
-\gamma - c_1 + (c_2\,\xi_{1t})/\xi_{2t} &= \lim_{\frac{\partial PS}{\partial \tau} \to 0} \left( \frac{\alpha _{s}\pm\sqrt{{\alpha _{s}}^2-4\,\frac{\partial PS}{\partial \tau} \,\alpha _{s}\,\mathrm{\gamma}}}{2\,\frac{\partial PS}{\partial \tau} } - c_1 + (c_2\,\xi_{1t})/\xi_{2t} \right) \\
-&= \lim_{\frac{\partial PS}{\partial \tau} \to 0} \left( \frac{\alpha _{s}\pm\sqrt{{\alpha _{s}}^2-4\,\frac{\partial PS}{\partial \tau} \,\alpha _{s}\,\mathrm{\gamma}}}{2\,\frac{\partial PS}{\partial \tau} } \right) - c_1 + (c_2\,\xi_{1t})/\xi_{2t}  \\
-&= \lim_{\frac{\partial PS}{\partial \tau} \to 0} \left( \pm 
-\frac{\left( (0.5)(-4\alpha_s \gamma) \right) \left( \alpha_s^2 - 4 \frac{\partial PS}{\partial \tau} \alpha_s \gamma \right)^{-0.5} }{2}
- \right) - c_1 + (c_2\,\xi_{1t})/\xi_{2t}  \\
-\implies \gamma &= \lim_{\frac{\partial PS}{\partial \tau} \to 0} \left( \pm 
-\left( (-\alpha_s \gamma) \right) \left( \alpha_s^2 - 4 \frac{\partial PS}{\partial \tau} \alpha_s \gamma \right)^{-0.5} 
-\right) \\
-&=  \pm 
-\left( -\alpha_s \gamma \right)\alpha_s^{-1} \\
-&=  \pm (- \gamma)
-\end{align*}
-where L'Hopitals was used in the third step. Hence, the correct solution is:
-$$\frac{\alpha _{s} - \sqrt{{\alpha _{s}}^2-4\,\frac{\partial PS}{\partial \tau} \,\alpha _{s}\,\mathrm{\gamma}}}{2\,\frac{\partial PS}{\partial \tau} } - c_1 + (c_2\,\xi_{1t})/\xi_{2t}$$
+\section{Conclusion}
 
-\end{proof}
+An aim for future research may be to develop a model of clean and dirty energy that incorporates both predictable and stochastic intermittency in a multi-period setting.
 
@@
 \begin{itemize}
-	\item The portfolio max with the heterogeneous time model is not always equivalent to the portfolio max in a one-period model.
-So, it does not min the variance of aggregate electricity output either.
-Consequently, one-period optimization papers are problematic; if consumers prefer electricity more during certain points of the day, a one-period model will give suboptimal results.
+	\item 
 	\item 
@@
 
+		\bibitem[Acemoglu et al.(2012)]{Ace2012}
+		Acemoglu, D., Aghion, P., Bursztyn, L., \& Hemous, D. (2012). The Environment and Directed Technical Change. American Economic Review, 102(1), 131–166. https://doi.org/10.1257/aer.102.1.131
+		\bibitem[Ambec and Crampes (2012)]{AC2012}
+		Ambec, S., \& Crampes, C. (2012). Electricity provision with intermittent sources of energy. Resource and Energy Economics, 34(3), 319–336. https://doi.org/10.1016/j.reseneeco.2012.01.001
+
+		\bibitem[Borenstein(2012)]{Boren2012}
+		Borenstein, S. (2012). The Private and Public Economics of Renewable Electricity Generation. Journal of Economic Perspectives, 26(1), 67–92. https://doi.org/10.1257/jep.26.1.67
+
+		\bibitem[Chao(2011)]{Chao2011}
+		Chao, H. (2011). Efficient pricing and investment in electricity markets with intermittent resources. Energy Policy, 39(7), 3945–3953. https://doi.org/10.1016/j.enpol.2011.01.010
+
 		\bibitem[Delarue et al.(2010)]{Delarue}
@@
 
-		\bibitem[Shahriari and Blumsack (2018)]{SB2018}
-		Shahriari, M., \& Blumsack, S. (2018). The capacity value of optimal wind and solar portfolios. Energy, 148, 992–1005. https://doi.org/10.1016/j.energy.2017.12.121
-
-		\bibitem[Ambec and Crampes (2012)]{AC2012}
-		Ambec, S., \& Crampes, C. (2012). Electricity provision with intermittent sources of energy. Resource and Energy Economics, 34(3), 319–336. https://doi.org/10.1016/j.reseneeco.2012.01.001
-
-		\bibitem[Borenstein (2012)]{Boren2012}
-		Borenstein, S. (2012). The Private and Public Economics of Renewable Electricity Generation. Journal of Economic Perspectives, 26(1), 67–92. https://doi.org/10.1257/jep.26.1.67
-
-		\bibitem[Chao (2011)]{Chao2011}
-		Chao, H. (2011). Efficient pricing and investment in electricity markets with intermittent resources. Energy Policy, 39(7), 3945–3953. https://doi.org/10.1016/j.enpol.2011.01.010
-
-		\bibitem[Electricity Information Administration (2019)]{EIA2019}
+		\bibitem[Electricity Information Administration(2019)]{EIA2019}
 		Electricity Information Administration (2019). Net generation, United States, all sectors, annual. Electricity Data Browser. https://www.eia.gov/electricity/data/browser
 
-		\bibitem[Joskow (2011)]{Joskow2011}
+		\bibitem[Foley et al.(2012)]{Foley2012}
+		Foley, A., Leahy, P., Marvuglia, A., \& Mckeogh, E.
+(2012).
+Current methods and advances in forecasting of wind power generation.
+Renewable Energy, 37(1), 1–8.
+https://doi.org/10.1016/j.renene.2011.05.033
+
+		\bibitem[Geroski(1957)]{Geroski2000}
+		Geroski, P. (2000). Models of technology diffusion. Research Policy. Elsevier B.V. https://doi.org/10.1016/S0048-7333(99)00092-X
+
+		\bibitem[Helm and Mier(2019)]{HH}
+		Helm, C., \& Mier, M. (2019). On the efficient market diffusion of intermittent renewable energies. Energy Economics, 80, 812–830. https://doi.org/10.1016/j.eneco.2019.01.017
+
+		\bibitem[Joskow(2011)]{Joskow2011}
 		Joskow, P. (2011). Comparing the Costs of Intermittent and Dispatchable Electricity Generating Technologies. American Economic Review, 101(3), 238–241. https://doi.org/10.1257/aer.101.3.238
 
-		\bibitem[Musgens and Neuhoff (2006)]{MG2006}
+		\bibitem[Mohajeryami et al.(2016)]{Moha2016}
+		Mohajeryami, S., Moghaddam, I., Doostan, M., Vatani, B., \& Schwarz, P.
+(2016).
+A novel economic model for price-based demand response.
+Electric Power Systems Research, 135, 1–9.
+https://doi.org/10.1016/j.epsr.2016.03.026
+
+		\bibitem[Musgens and Neuhoff(2006)]{MN2006}
 		Musgens, F., \& Neuhoff, K. (2006). Modelling Dynamic Constraints in Electricity Markets and the Costs of Uncertain Wind Output. Faculty of Economics.
 
-		\bibitem[Neuhoff et al. (2007)]{NCK2007}
+		\bibitem[Neuhoff et al.(2007)]{NCK2007}
 		Neuhoff, K., Cust, J.
@@
 Cambridge Working Papers in Economics 0711, Faculty of Economics, University of Cambridge.
+
+		\bibitem[Shahriari and Blumsack(2018)]{SB2018}
+		Shahriari, M., \& Blumsack, S. (2018). The capacity value of optimal wind and solar portfolios. Energy, 148, 992–1005. https://doi.org/10.1016/j.energy.2017.12.121
+
+		\bibitem[Warkins and Knight(1922)]{Knight}
+		Watkins, G., \& Knight, F. (1922). Knight’s Risk, Uncertainty and Profit. The Quarterly Journal of Economics, 36(4), 682–690. https://doi.org/10.2307/1884757
 
@@
 
-$-\alpha _{t}\,{c_{2}}^2\,{\xi _{1}}^2\,\xi _{\mathrm{2s}}\,\left(c_{2}\,\xi _{1}-c_{1}\,\xi _{\mathrm{2s}}+\mathrm{gamma}\,\xi _{\mathrm{2s}}-\xi _{\mathrm{2s}}\,z\right)$
-
 	\end{thebibliography}

### 2019-04-23 code/matlab/simulation_april/main.m

@@ -4,20 +4,18 @@
 % Two Periods
 
 
-%% Parameters
+%% CES Numerical Sim
 
 alpha = [0.3, 0.7];
 xi_1  = [1, 1];
-xi_2  = [0.1, 1];
+xi_2  = [0, 1];
 
-sigma = 0.5;
+sigma = 2;
 phi   = (sigma - 1)/sigma;
-budget = 1;
+budget = 1e4;
 
-x_1_cost_param = 95*0.5;
+x_1_cost_param = 95*0.9;
 x_2_cost_param = 50;
-
-%% Solution
 
 % Prices
 xi_mat   = [xi_1; xi_2];
@@ -29,14 +27,35 @@ P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
 
 % Quantities
 Y = ((alpha'./prices).^(sigma)) * (budget/P);
-X = (xi_mat')\Y;
+X = (xi_mat')\Y
+
+
+%% CD Numerical Sim
+
+alpha = [0.3, 0.7];
+xi_1  = [1, 1];
+xi_2  = [0, 1];
+
+budget = 1;
+
+x_1_cost_param = 95*0.9;
+x_2_cost_param = 50;
+
+% Prices
+xi_mat   = [xi_1; xi_2];
+cost_mat = [x_1_cost_param; x_2_cost_param];
+prices   = xi_mat\cost_mat;
+
+% Quantities
+Y = ((alpha'./prices).^(1))*budget;
+X = (xi_mat')\Y
 
 
 %% Price (Cost) Elasticity Sim
 
-n = 100;
+n = 500;
 results = zeros(n,2); 
-cost_multiplier = linspace(0.5,1.5,n);
+cost_multiplier = linspace(0.5,2.5,n);
 
 for i = 1:n
     
@@ -44,7 +63,7 @@ for i = 1:n
     xi_1  = [1,   1];
     xi_2  = [0.1, 1];
 
-    sigma = 0.5;
+    sigma = 5;
     phi   = (sigma - 1)/sigma;
     budget = 1;
 
@@ -95,14 +114,14 @@ for i = 1:n
    
     alpha = [0.3, 0.7];
     xi_1  = [1, 1];
-    xi_2  = [0.5, 1.5];
+    xi_2  = [0, 1];
 
     sigma = sigma_range(i);
     phi   = (sigma - 1)/sigma;
     budget = 1;
 
[…]

### 2019-04-23 code/matlab/simulation_april/tax_subsidy_sim.m

@@ -1,0 +1,84 @@
+%% Simulation to find the optimal tax + research combination
+% Cobb-Douglas, 2 Periods
+% Cost of research given by c_beta*beta
+
+beta   = 1;
+c_beta = 0.00001;
+gamma  =  0.00116*100;
+tau    = gamma;
+
+n = 100;
+results = zeros(n,3); 
+tau_range  = linspace(0,2.5,n);
+beta_range = linspace(0.5,2.5,n);
+
+for i = 1:n
+
+    % Variable params
+    tau = tau_range(i);
+    
+    % Parameters
+    alpha = [0.3, 0.7];
+    xi_1  = [1, 1];
+    xi_2  = [0, 1];
+    sigma = 1;
+    phi   = (sigma - 1)/sigma;
+    budget = 1;
+    c_1 = 95*0.9;
+    c_2 = 50;
+
+    % Prices
+    xi_mat   = [xi_1; xi_2*(1+beta)];
+    cost_mat = [c_1*(1+tau); c_2];
+    prices   = xi_mat\cost_mat;
+
+    % Price Index
+    P = 1;
+    
+    % Quantities
+    Y = ((alpha'./prices).^(sigma)) * (budget/P);
+    X = (xi_mat')\Y;
+    
+    % Expand parameters
+    alpha_t = alpha(1);
+    alpha_s = alpha(2);
+    xi_1t = xi_1(1);
+    xi_1s = xi_1(2);
+    xi_2t = xi_2(1);
+    xi_2s = xi_2(2);
+    
+    % Partial G(B) / Partial X_1
+    diff_X1_beta = - (alpha_t*c_2*xi_1s*xi_2s)/(- c_2*xi_1s +    ...
+        tau*xi_2s + c_1*(xi_2s + beta*xi_2s) + beta*tau*xi_2s)^2 ...
+        - (alpha_s*c_2*xi_1t*xi_2t)/(c_1*xi_2t - c_2*xi_1t +     ...
+        tau*xi_2t + beta*c_1*xi_2t + beta*tau*xi_2t)^2;
+    diff_GB_X1 = c_beta*(1/diff_X1_beta);
+    
+    results(i,1) = X(1);
+    results(i,2) = X(2);
+    results(i,3) = gamma + diff_GB_X1;
+
+end
+
+
+%% Plots
+
+figure;
+hold on;
+plot(tau_range, tau_range)
+plot(tau_range, results(:,3))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2019-04-23 documents/draft.tex
Update draft and simulation
- Add numerical example of varying elasticity of substition
- Updates to draft

@@
 Specifically, we develop a model where producers optimize the supply of each generation technology on the expected market value of the electricity produce.
-We do so by
+We do so by ....
 
@@
 Moreover, the relationship between the force created by the wind and the amount of wind power generated must necessarily be a fixed, functional relationship; that is, \textit{ceterius paribus}, two identical wind turbines under identical wind conditions should generate the same amount of energy.
-Consequently, the output of wind power can be forecasted\footnote{\citet{Foley2012} provide a review of the literature on the forecasting of wind power and advancements over time} up to an error term.
-Because no forecast of wind (or solar) power can be perfect, some level of weather-related intermittency may be left in the error term.
-At the same time, the error term also captures unreliability; for instance, failures in the circuitry of wind turbines cannot be forecasted as a time series.
+Consequently, the output of wind power can be forecasted up to an error term.\footnote{\citet{Foley2012} provide a review of the literature on the forecasting of wind power.} Because no forecast of wind (or solar) power can be perfect, some level of stochastic intermittency may be left in the error term.
+At the same time, the error term also captures unreliability; for instance, failures in the circuitry of wind turbines cannot simply be forecasted with a time series.
 So, overall, we may think of the energy output of a renewable technology as consisting of three components: a knowable/forecastable component related to intermittency, a stochastic component related to intermittency, and an unpredictible component related to reliability.
@@
 Additionally, while their model consists of two sets of consumers, one set which receives fixed price contracts and another paying real time prices, we consider one representative consumer.
-Specifically, this representative consumer's utility is given by CES function where each good is electricity consumption differentiated by time; this approach was first set forth by \citet{Moha2016}.
+Specifically, this representative consumer's utility is given by CES function where each good is electricity consumption differentiated by time.
 Interestingly, this treatment of intermittency produces some key results similar to that of Helm and Mier.
+
+% What we have in common
+% What's new, what adds to the literature
 
@@
 Generally, people prefer to spread their electricity consumption out over time; the convexity of the indifference surfaces of a standard CES function can model this preference in a simple way.
+The use of a CES function for modeling consumer utility with electricity consumption differentiated by time has been explored earlier by \citet{Moha2016}.
+Their paper calibrates the share parameters of the CES function with actual electricity consumption data for peak and off-peak hours; they further provide a sensitivity analysis with respect to the elasticity of substitution parameter.
+Similarly, \citet{Schwarz} provides an empirical study of this CES function and estimate its parameters for industrial customers in a real-time pricing program; their estimates of the intertemporal elasticity of substitution for electricity consumption fall around 0.03.
+
 Next, we model the electricity sector using a representative firm that chooses a set of electricity-generating inputs to maximize profit; some of these inputs are intermittent - they generate a differing amounts of energy in each period.
@@
 Secondly, we have firms maximizing profit by picking an optimal set of energy inputs.
-In reality, electricity markets are fairly competitive, so we assume perfect competition.
-Hence, we can model the set of firms using a representative firm that sets marginal revenue equal to marginal cost.
+In reality, electricity markets are fairly competitive, so we can model the set of firms by using a single representative firm that sets marginal revenue equal to marginal cost.
 We define the quantity of deployed energy technology $i$ as $X_i$, and we define its output per unit in period $t$ as $\xi_{1,t}$.
@@
 \end{align*}
-where we have $n$ technologies and  $m$ periods.
-Also, note that we have $Z \equiv \xi^T X$.
-Firms pick $X$ to maximize profit while facing the cost function $C(X_1, \dots, X_n)$ where $C$ is convex with respect to each input.
+where we have $n$ technologies, $m$ periods, and $Z \equiv \xi^T X$.
+A key element of this model is that $X$ does not vary by time.
+This is important, because the time scale of our model must be fairly granular to study the effects of intermittency.
+So, for instance, we may have $t \in \{ 1, \dots, 24\}$ representing each hour of the day.
+In such short time scales, we can safely assume that producers do not modify the quantity of the technology they employ.
+Moreover, this keeps the model parsimonious by preventing more complicated dynamics from entering the producers optimization problem.
+
+Instead, our representative firm sets $X$ once to maximize profit in all periods while facing the cost function $C(X_1, \dots, X_n)$.
+\citet{HH} note that past literature has argued for concave cost functions in the energy market due to effects such as economics of scale and learning by doing; on the other hand, standard cost functions are generally convex.
+So, like Helm and Meir, we take an intermediate approach by using a linear cost function.
+Specifically, we have $C(X) \equiv \sum_i c_i X_i \equiv c^T X$ where $c_i$ is the cost per unit of $X_i$.
 Total profit is given by
 \begin{equation}
-\Pi = p^T Z - C(X_1, \dots, X_n)
+\Pi = p^T Z - c^T X
 \end{equation}
-To simplify the algebra, suppose we $n=m$.
-We further make the assumption that the output per unit of each technology is unique and non-negative in each period; in other words, the output per unit of one technology is not a linear combination of those of the other technology in our set.
+To simplify the algebra, we set the number of technologies equal to the number of periods $(n=m)$.
+Additionally, we further require that the output per unit of each technology is unique and non-negative in each period; in other words, the output per unit of one technology is not a linear combination of those of the other technologies in our set.
 This then implies that $\xi$ is of full rank and therefore invertible.
-Lastly, suppose that we have a linear cost function $C = \sum_i c_i X_i = c^T X$ where $c_i$ is the cost per unit of $X_i$ Now, maximizing profit, we find the first order condition:
+Now, maximizing profit, we find the first order condition:
 \begin{equation}
@@
 \end{equation}
-Combining both first order conditions allows us to find the equilibrium; however, in order to produce more comprehensible results, we consider a further simplification.
+Combining both first order conditions allows us to find the equilibrium.
+The equilibrium results any number of technologies ($n$) are analytic, but they are difficult to interpret due to the number of parameters involved.
+Hence, in order to produce more comprehensible results, we proceed with a special case of our general model.
 
@@
 Secondly, we limit the number of periods and technologies to 2.
-And, thirdly, we normalize the prices such that the budget is $1$.
+And, thirdly, we normalize the prices such that the budget $I$ is $1$.
 Consequently, our demand equations simplify to:
@@
 \end{align}
-where $t$ and $s$ are our two periods. Next, solving for the FOC condition for profit maximizing (which remains the same), we have:
+where $t$ and $s$ are our two periods. Next, solving for the FOC condition for profit maximization, we have:
 \begin{align*}
@@
 \end{align*}
-And, substituting back into our demand equations, we have the equilibrium quantities for $Z$ and $X$. 
+And, substituting back into our demand equations, we find the equilibrium quantities for $Z$ and $X$. 
 $$
@@
 The full proof given below provides equivalent restrictions for the zero cases.
-}  \\
+}
 	\end{tabular} 
@@
 
+\hfill\\
 \begin{proof}
@@
 
-In more practical terms, suppose that our first technology was coal power and latter was solar power; additionally, assume period $t$ and $s$ are the peak and off-peak for a day.
-We know that the output efficiency of coal is constant through the day, while that of solar power is higher in period $t$ -- this ensures the output efficiency restriction: $\xi_{2t}/\xi_{2s} > \xi_{1t}/\xi_{1s}$.
-Additionally, we can reasonably assume that coal is more cost effective than solar in the off-peak period when there is less sun; hence, the second cost efficiency restriction is satisfied.
-Thirdly, the first condition must be true for there to be an incentive to use solar power; that is, solar needs be cost effective during peak hours otherwise we hit an edge case where no solar is employed.
-Finally, we face the mixed efficiency condition, which essentially implies that there must be sufficient demand for electricity during period $t$, when solar is more effective, for it to be a feasible technology.
-So, overall, for a technology to be feasible, we have three conditions: it must the most cost effective in a particular period, its output efficiency must be maximized in the same period, and there must be sufficient amount of demand in that period.
+In more practical terms, suppose that our first technology is coal power and the latter is solar power.
+Although coal power is dispatchable, it does not easily ramp up or down within a day; hence, it is reasonable to apply our model where capacities are fixed over time so long as our time frame is sufficiently short.
+Hence, we now assume periods $t$ and $s$ represent the peak and off-peak for a day.
+And, we expect that there is more available solar radiation during peak hours than off-peak hours, since peak hours are usually during the middle of the day.
+This implies that the the output efficiency of solar power is higher in period $t$ due to more available solar radiation.
+Additionally, since the energy output of a unit of coal is independent of time, we know that the output efficiency of coal is constant.
+In total, this implies that we have met the output efficiency restrictions, since we have $\xi_{2t}/\xi_{2s} > \xi_{1t}/\xi_{1s}$.
+Next, we can reasonably assume that coal is more cost effective than solar in the off-peak period when there is less sun; hence, the second cost efficiency restriction is satisfied.
+Then, for there to be an incentive to use solar power, we must satisfy the first cost-efficiency condition; that is, solar needs be cost effective during peak hours otherwise we hit an edge case where no solar is employed.
+And, finally, solar must also satisfy the mixed efficiency condition, which essentially implies that there must be sufficient demand for electricity during period $t$, when solar is more effective, for it to be a feasible technology.
+So, overall, for a technology to be economical, it must meet three conditions: it must the most cost effective technology for a particular period, its output efficiency must be maximized in the same period, and there must be sufficient amount of demand in that period.
 
@@
 The comparative statics are similarly intuitive.
-The equilibrium quantity of a technology is increasing with its output efficiency and decreasing with its cost.
+The equilibrium quantity of a technology is increasing with its output efficiency and decreasing with its cost per unit.
 Additionally, the equilibrium quantities for a particular technology move in the opposite direction with respect to the output efficiency and cost of the other technologies.
-So, for example, an increase in the output efficiency of solar or a decrease in solar's cost will reduce the optimal quantity of coal power.
-To find the effects of $\alpha$ on $X$, we must assume one of the cases of restrictions shown in \ref{tab:paramrest}{Table 1}.
-So, assume Case 1 is true; this implies that $X_2$ is optimal in period $t$ and $X_1$ is optimal in period $s$.
-Additionally, note that $\alpha$ determines demand for electricity in a period.
+For a practical example, consider again coal and solar power from before.
+An increase in the output efficiency of solar or a decrease in solar power's cost will reduce the optimal quantity of coal power.
+Likewise, as coal power's efficiency improves, it's adoption rises.
+To find the effects of $\alpha$ on $X$, we must assume one of the cases of restrictions shown in \hyperref[tab:paramrest]{Table 1}.
+So, again, let us assume Case 1 is true; this implies that $X_2$ is the most cost effective technology in period $t$ and likewise for $X_1$ in period $s$.
+Firstly, note that $\alpha$ determines demand for electricity in a period.
 Hence, when $\alpha_t$ rises, we see the optimal level of $X_2$ rise as well; likewise, $X_1$ rises with $\alpha_s$.
-So, essentially, the optimal quantity of a technology rises with the demand shifter $\alpha$ of the period that the technology is optimal in.
+In short, the optimal quantity of a technology rises linearly with the demand for electricity in the period it specializes in.
+Moreover, these relationships are reversed with respect to demand in each technology's suboptimal period.
+So, for example, we would expect the use of solar energy to rise when demand for electricity during peak hours rises, and it would fall when demand for energy in the off-peak rises.
+On the other hand, use coal power would rise with off-peak demand and fall with peak demand.
 This concept carries through for the comparative statics of $Z$.
@@
 This is because technology 1 is optimal in period $s$ given the Case 1 restrictions.
-Moreover, we would see symmetrical results for the output with respect to the cost and output efficiency of technology 2.
-In total, the comparative statics are fairly straightforward.
+Likewise, we see symmetrical results for the output with respect to the cost and output efficiency of technology 2; improvements in the efficiency of $X_2$ result in greater output in $Z_t$ and smaller output in $Z_s$.
 
@@
 
-\subsubsection{Technical Change and Market Shares}
+\subsubsection{The Effects of Technical Change}
+
+While our model sets the intertemporal elasticity of substitution for  electricity consumption $\sigma$ to a fixed value, we make no direct assumptions about the elasticity of substitution between different energy technologies.
+Rather, an interesting relationship regarding the substitutability/complementarity between technologies emerges indirectly as a result of intermittency.
+To illustrate this, we provide a numerical example that models the relationship between the use of solar and coal energy.
+But, to start, we must initialize our model with a set of parameter values.
+
+Firstly, we let technology 1 be coal power and technology 2 be solar power; again, period $t$ represents peak hours and period $s$ represents off-peak hours.
+We assume that, holding prices equal, consumers prefer that 60\% of their energy arrive in period $t$ and the remaining 40\% arrive in period $s$.
+Additionally, we normalize the units of the quantities to a MWh basis.
+Hence, $\xi$ represents the percent of capacity utilized in each period; we assume coal can access 100\% of its capacity in both periods, while solar can access 100\% during peak hours and only 10\% during off-peak hours.
+Finally, we set cost parameters, given in  \$ per MWh, equal to LCOE estimates for 2023 from the \citet{EIALCOE}; specifically, we use estimates for "Solar PV" and "Coal with 30\% CCS." In total, we have the following parameters.
+
+\begin{center}
+\noindent \textbf{Example  1:} $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$. 
+\end{center}
+
+\noindent We begin by exploring the implied elasticity of substitution between these two technologies; for any two commodities $i$ and $j$,  the elasticity of substitution $e_{i,j}$ is given by:
+$$e_{i,j} = \frac{\partial \ln (X_1/ X_2)}{\partial \ln (c_2/c_1)}$$
+where $c$ is their prices.
+This relationship is of particular interest, because many applied and theoretical models studying renewable and fossil energy impose a CES relationship between the two.
+That is, they assume that $e$ is a fixed constant.
+In our model, this is not the case; while we cannot directly derive a clean solution for the value of $e_{i,j}$, we can obtain the numerical results for the difference in log prices and quantities and study its slope.
+Moreover, we extend our analysis beyond the Cobb-Douglas case and allow $\sigma$ to vary.\footnote{In the general CES case, we still have $p = \xi^{-1} c$.
+However, for the amount of electricity produced in each period, we instead have $Z^T = \left( \alpha_t/p_t \; \alpha_s /p_s \right) \cdot (1/P)$ where $P$ is the price index defined earlier.
+And, of course, we again have $(\xi^T)^{-1} Z = X$.}
 
@@
 
-		\bibitem[Electricity Information Administration(2019)]{EIA2019}
+		\bibitem[EIA(2019a)]{EIANetgen}
 		Electricity Information Administration (2019). Net generation, United States, all sectors, annual. Electricity Data Browser. https://www.eia.gov/electricity/data/browser
+
+		\bibitem[EIA(2019b)]{EIALCOE}
+		Electricity Information Administration (2019).
+Levelized Cost and Levelized Avoided Cost of New Generation.
+Annual Energy Outlook 2019.
+https://www.eia.gov/outlooks/aeo/pdf/electricity\_generation.pdf
 
@@
 
+		\bibitem[Schwarz et al.(2002)]{Schwarz}
+		Schwarz, P., Taylor, T., Birmingham, M., \& Dardan, S.
+(2002).
+INDUSTRIAL RESPONSE TO ELECTRICITY REAL‐TIME PRICES: SHORT RUN AND LONG RUN.
+Economic Inquiry, 40(4), 597–610.
+https://doi.org/10.1093/ei/40.4.597
+
 		\bibitem[Shahriari and Blumsack(2018)]{SB2018}

### 2019-04-23 code/matlab/simulation_april/sim_technical_change.m

@@ -1,0 +1,87 @@
+%% Price (Cost) Elasticity Sim
+
+n = 500;
+results = zeros(n,2); 
+cost_multiplier = linspace(0.5,2,n);
+sigma_range = [0.1, 0.5, 1.0, 1.5, 2];
+m = length(sigma_range);
+
+
+figure;
+hold on;
+
+for j = 1:m
+    
+    sigma = sigma_range(j);
+
+    for i = 1:n
+
+        alpha = [0.6, 0.4];
+        xi_1  = [1,   1];
+        xi_2  = [1, 0.1];
+        
+        phi   = (sigma - 1)/sigma;
+        budget = 1;
+
+        x_1_cost_param = 104.3*cost_multiplier(i);
+        x_2_cost_param = 50;
+
+        % Prices
+        xi_mat   = [xi_1; xi_2];
+        cost_mat = [x_1_cost_param; x_2_cost_param];
+        prices   = xi_mat\cost_mat;
+
+        if any(prices<0)
+            continue
+        end
+
+        % Price Index
+        P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
+
+        % Quantities
+        if sigma ~= 1
+            Y = ((alpha'./prices).^(sigma)) * (budget/P);
+        else 
+            Y = (alpha'./prices);
+        end 
+           
+        X = (xi_mat')\Y;
+
+        results(i,:) = X';
+
+    end    
+
+    output = [];
+    output(1,:) = 95*cost_multiplier'./50;
+    output(2,:) = results(:,1)./results(:,2);
+
+    % subset to positive quantities
+    ind = ~any(output <= 0);
+    output = output(:,ind);
+
+    % relationship between log prices and quantities
+    subplot(2,1,1);
+    hold on;
+    plot(-log(output(1,:)), log(output(2,:)))
+    
+    
+    % relationship between log prices and quantities
+    subplot(2,1,2);
+    hold on;
+    plot(-log(output(1,2:end)), diff(log(output(2,:)))./diff(-log(output(1,:))))
+    
+end
+
+subplot(2,1,1);
+legend('0.1', '0.5', '1.0', '1.5', '2.0')
+xlabel('Negative Log Difference in Prices')
+ylabel('Log Difference in Quantities')
+
+[hleg,att] = legend('show');
+title(hleg, '\sigma')
+
+subplot(2,1,2);
[…]

### 2019-04-23 documents/draft.tex
Update draft and simulation
- fix simulation code and graphs
- add more on simulation results to paper

@@
 Consumers purchase variable amounts of electricity $Z_t$ over each period $t$.
-Assuming the price of electricity in each period is held constant, they prefer that a fixed proportion of their energy arrive in period $t$ while some other fixed proportion arrive at $s \neq t$.
-Finally, we suppose that consumers would be willing to shift their consumption from one period to another in response to a shift in prices.
-In total, these assumptions can be captured using a representative consumer with the standard CES utility function
+Additionally, assuming that the price of electricity in each period is held constant, they prefer to ration their electricity usage across each period in fixed proportions.
+And, lastly, we presume that consumers would be willing to shift their consumption from one period to another in response to a shift in prices.
+Overall, these assumptions can be captured using a a standard CES utility function
 \begin{equation}
@@
 We define $\sum_t \alpha_t = 1$, so that $\alpha_t$ is the fraction of electricity consumption in period $t$ when all prices are equal; naturally, $\alpha_t > 0$ for all $t$.
-The budget constraint is given by
+We assume that any discounting over time is absorbed into $\alpha$ for parsimony.The budget constraint is given by
 \begin{equation}
@@
 \end{equation}
-where $p_t$ is the price of electricity in period $t$ and $I$ is the income. Consequently, the first order conditions when maximizing utility given this budget constraint imply:
+where $p_t$ is the price of electricity in period $t$ and $I$ is the income.
+Furthermore, since CES preferences are homothetic, we may aggregate the consumers into a single representative consumer.
+Consequently, the first order conditions four our representative consumer when maximizing utility given this budget constraint imply:
 \begin{align}
@@
 where $P$ is the price index.
-This model naturally does not allow for blackouts in equilibrium, since the price of electricity in any period gets arbitrarily large as the quantity of energy consumed in that period falls.
+Note that this model naturally does not allow for blackouts in equilibrium, since the price of electricity in any period gets arbitrarily large as the quantity of energy consumed in that period approaches 0.
+Furthermore, note that prices must be positive; although this is sometimes violated in reality, we do not believe that this assumption significantly affects our analysis.
 
@@
 where $c$ is their prices.
-This relationship is of particular interest, because many applied and theoretical models studying renewable and fossil energy impose a CES relationship between the two.
-That is, they assume that $e$ is a fixed constant.
-In our model, this is not the case; while we cannot directly derive a clean solution for the value of $e_{i,j}$, we can obtain the numerical results for the difference in log prices and quantities and study its slope.
+This relationship is of particular interest, because many applied and theoretical models studying renewable and fossil energy impose a CES production structure between the two.
+That is, they assume that $e_{renew, fossil}$ is a fixed constant.
+In our model, this is not the case; while directly deriving the value the elasticity of substition $e$ is analytically intractable, we are able to run a numerical simulation to estimate it.
 Moreover, we extend our analysis beyond the Cobb-Douglas case and allow $\sigma$ to vary.\footnote{In the general CES case, we still have $p = \xi^{-1} c$.
@@
 
-Like \cite{HH} we find an S-shaped adoption curve for renewable energy driven by intermittency.\footnote{\citet{HH} reference \citet{Geroski2000} who provides a survey of the literature on adoption of new technologies.
+\begin{table}[t]
+	\caption*{\textbf{Figure 1:} Elasticity of Substition Between Solar and Coal} 
+	\label{fig:eosnum}
+	\footnotesize
+	\begin{tabular}{@{\extracolsep{0em}}c}
+		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/example_1_fig_1} \\
+		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } The y-axis of the first plot is equivalent to $\log(X_1/X_2)$ and the x-axis of both plots is equivalent to  $\log(c_2/c_1)$.
+The legend in the upper subplot also applies to the lower subplot.
+These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
+We plot results for various values of the intertemporal elasticity of substition for electricity consumption $\sigma$, which is used in the consumer's CES utility function.
+In order to numerically estimate these relationships, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.5\, c_1, 2 \,c_1)$.
+Then, we obtained estimates of the elasticity of substition by numerically differentiating $\log(X_1/X_2)$ with respect to $-log(c_1, c_2)$.
+That is, the elasticity of substitution between technology 1 and 2 is given by the slope of the upper subplot, and it is graphed in the lower subplot.
+}     \\
+	\end{tabular}
+\end{table}
+
+We plot our numerical estimates of the elasticity of substitution between solar and coal power in \hyperref[fig:eosnum]{Figure 1}.
+These results were generated by computing the optimal quantities of each technology given a range of prices.
+Specifically, we held the price of solar constant and varied the price of coal from 50\% to 200\% of its original parametrized price.
+Then, we numerical differentiated $\log(X_1/X_2)$ with respect to $\log(c_2/c_1)$ to estimate the elasticity of substitution between solar and coal.
+This numerically computed elasticity of substitution $e$ on the production side is shown in the lower subplot.
+We repeat this process with different values of $\sigma$, the elasticity of substitution in the consumer's utility function.
+Recall that $\sigma < 1$ implies that  electricity consumption in different periods are complements, $\sigma = 1$ implies to a Cobb-Douglas relationship, and $\sigma > 1$ implies that electricity consumption in different periods are substitutes.
+Our results strongly suggest that a CES production structure does not accurately model intermittency.
+
+Firstly, note that the elasticity of substitution becomes increasingly non-linear as $\sigma$ rises.
+This is somewhat intuitive; when energy consumption can be substituted across periods, the market is more sensitive to the cost efficiency of technologies and less sensitive to when they produce.
+For instance, suppose we had two technologies that each produced in a different period; if consumers are less willing to substitute consumption across periods, both technologies are likely to be  employed, On the other hand, when consumers are open to substitution (implying large $\sigma$), they will simply consume the majority of their electricity in whichever period it is most cost effective to do so.
+Consequently, price plays bigger role than intermittency as $\sigma$ rises.
+This is further evident in the lower subplots; note that the numerical estimates of  $e$ rise as $\sigma$ rises.
+When consumers are less concerned about when they receive their energy, they are far more open to substituting between coal and solar power.
+
+Second, we find that $e$ approaches a "U" shape as $\sigma$ rises....
+
+...Like \cite{HH} we find an S-shaped adoption curve for renewable energy driven by intermittency.\footnote{\citet{HH} reference \citet{Geroski2000} who provides a survey of the literature on adoption of new technologies.
 He finds that S-shaped adoption curves are often generated by information cascades.
@@
 
+\pagebreak
+
+\section{Empirical Methodology}
+
+We aim to empirically estimate the intertemporal elasticity of substition for electricity consumption $\sigma$........
+
+Recall our original first order condition (Equation 3) in the general model:
+\begin{align*}
+Z_t &= \left(\frac{\alpha_t}{p_t} \right)^\sigma \frac{I}{P} \\
+P &= \sum_t \alpha_t^\sigma p_t^{1-\sigma}
+\end{align*}
+For any pair of electricity ouputs $Z_t$ and $Z_s$, we have:
+$$\frac{Z_t}{Z_s} = \left(\frac{\alpha_t \, p_s}{\alpha_s \, p_t} \right)^\sigma \\$$
+Taking logs on both sides and letting $i$ represent different observations, we may rewrite this in a form more suitable for estimation. 
+\begin{align*}
+\ln (Z_{t, i} / Z_{ s, i}) &= -\sigma \ln (P_{t,i} / P_{s,i}) + \sigma \ln (\alpha_{t,i} / \alpha_{s,i}) 
+\end{align*}
+Our data differentiates consumption for each state in the US, so we let $i$ refer to a particular state.
+Additionally, most consumers pay monthly fixed rates for electricity, so we can, at most, estimate this equation on a monthly basis; hence, $t$ and $s$ refer to different months.
+Lastly, note that the state $i$ is kept constant for each observation; this is because consumers within each state can substitute consumption across time, but consumers in different states do not substitute consumption with one another.
+
+In order to estimate this $\sigma$, we further modify the previous equation. 
+Firstly, note that we cannot observe the demand shifter $\alpha_{t,i}$ directly, so we add a set of controls that may be responsible for shifts in demand. Our regression is then
+\begin{align*}
+\ln (Z_{t, i} / Z_{ s, i}) &= -\sigma \ln (P_{t,i} / P_{s,i}) +  \gamma_{t,i} A_{t,i} + \gamma_{s,i} A_{s,i} + u_i
+\end{align*}
+where $A$ represents set of controls for changes in demand while $u_i$ is a normal error term.
+Note that the control  $A_{t,i}$ replaces $\sigma \ln(\alpha_{t,i})$ and likewise for the period $s$ term; this substitution is valid because the $\ln(\alpha_{t,i}) \in \mathbb{R}$ and the $\sigma$ is simply absorbed into the estimated coefficient for $\gamma_{t,i}$.
+For the demand controls themselves, we choose to use heating (HDD) and cooling degree days (CDD) due to the aggregation of the data.
+That is, a more general control such as average temperature would not be able to directly capture intramonthly changes in demand, since variation in temperature would be lost when aggregated; on the other hand, CDDs and HDDs directly represent daily deviations in temperature even when totaled for each month.
+Additionally, demand for electricity may rise over time.
+Hence, we include, as a control, the difference in months between time $t$ and $s$; this is represented by $\Delta_{t,s}$.
+Finally, this panel requires us to consider fixed effects for each state, so we use a fixed effects panel regression.
+In total, the demand equation is:
+\begin{align*}
+\ln (Z_{ t, i} / Z_{ s, i}) &= -\sigma \ln (P_{t,i} / P_{s,i}) +  \gamma_{t,i} A_{t,i} + \gamma_{s,i} A_{s,i} + \eta \Delta_{t,s} + u_i \\
+&= -\sigma \ln (P_{t,i} / P_{s,i}) +  \gamma_{t,i} \left( CDD_{t,i} + HDD{t,i} \right) \\
+&\qquad + \gamma_{s,i} \left( CDD_{s,i} + HDD{s,i} \right)  + \eta \Delta_{t,s} + u_i
+\end{align*}
+
+Still, this equation may suffer from bias, since producers can also substitute production over time.
+For instance, it is possible to store fuel for electricity generation in the future when prices may rise.
+So, we define the following supply equation
+\begin{align*}
+\ln (Z_{ t, i} / Z_{ s, i}) &= \beta \ln (P_{t,i} / P_{s,i}) + \xi \ln (C_{t,i} / C_{s,i}) + v_{i}
+\end{align*}
+where $C_{t,i}$ is the average cost of coal used for electricity generation in state $i$ at time $t$ and $v_i$ is a normal error term.
+Coal prices are independent of the electricity demand error term $u_i$, since residential consumers do not generally use coal for electricity generation; on the other hand, shocks in the price of coal are linked with the supply of electricity.
+Hence, coal price is a theoretically valid instrument.
+In total, the reduced form equation is given by:
+$$ \ln (P_{t,i} / P_{s,i}) = \left( \beta + \sigma \right)^{-1} \left( \gamma_{t,i} A_{t,i} + \gamma_{s,i} A_{s,i} + \eta \Delta_{t,s} - \xi \ln (C_{t,i} / C_{s,i}) + u_{i} - v_i \right)  $$
+where $A_{t,i}$ consists of CDDs and HDDs at time $t$.
+
+Finally, we also consider a semiparametric specification.
+That is, we allow the error terms $u_i$ and $v_i$ to be non-normal and place the demand controls and instruments in unknown functions.
+So, overall, we have:
+\begin{align*}
+\ln (Z_{ t, i} / Z_{ s, i}) &= -\sigma \ln (P_{t,i} / P_{s,i}) +  f \left( A_{t,i}, A_{s,i}, \Delta_{t,s} \right) + u_i \\
+\ln (Z_{ t, i} / Z_{ s, i}) &= \beta \ln (P_{t,i} / P_{s,i}) + g \left( \ln (C_{t,i} / C_{s,i})  \right) + v_{i}
+\end{align*}
+where $f$ and $g$ are unknown, bounded functions.
+We restrict $cov(u_i, v_i) = 0$ but allow for the controls and instruments to be correlated.
+The advantage of this specification is that we can account for the controls or instrument having any nonlinear effects on the regressands.
+\textbf{(More here on explaining the estimation)}
+
+\section{Data}
+
+We collect monthly data from the EIA on retail electricity prices and consumption for each state in the US from 2011 to 2018.
+Additionally, also from the EIA, we collect monthly data on the average cost of coal for electricity generation.
+The coal price data set contains a large number of missing values due to privacy reasons; however, we do not expect that these missing values are correlated with the data itself.
+Finally, we collect data on HDDs and CDDs from the NCEP for the same panel.
+Then, we merge these three data sets and trim 1\% of outliers for a total of $826$ observations.
+We use this preliminary data set to construct the data required for our regressions.
+That is, each observation in our estimation equation belongs to a set $(t,s,i)$ consisting of two time periods and a state.
+Hence, we construct each row in our regression data set using unique combinations of $t,s$ where $t \neq s$ for each state $i$.
+Due to the number of potential combinations and thus observations, we restrict our data set to a random sample of 9000 observations.\footnote{We reran our regressions with several different samples of 9000 and found that our estimated coefficients did not significantly change; hence we believe this sample size is sufficient.}
+
+\section{Results}
+
+Based on the OLS results reported in \hyperref[table:1]{Table 1}, we estimate the intertemporal elasticity of substitution for electricity consumption $\hat{\sigma}  = 0.609$ ($|t| > 24$) when accounting for all degree day covariates and state fixed effects.
+Interestingly, we find that the estimated coefficients for all three specifications do not differ when considering fixed effects.
+Additionally, as expected, the coefficients on the degree day covariates are symmetrical; that is, the coefficient on $CDD_{t}$ is approximately the same as the negative of that on $CDD_{s}$, and the same applies to $HDD_{t}$ and $HDD_{s}$.
+On the other hand, we found that electricity consumption seems to rise more in response to CDDs rather than HDDs.
+Lastly, we find that the sign on $\Delta_{t,s}$ is positive in all regressions; this implies that electricity consumption rises over time independent of price.
+
+To account for endogeneity in the OLS results, we provide results for our IV specification in \hyperref[table:2]{Table 2}.
+Here, we find a much larger estimate $\hat{\sigma}  = 11.430$ ($|t| > 2.1$) when considering all covariates and fixed effects.
+F-Statistics on all three specifications are significantly larger than 10, which suggests that the instruments are not weak \citep{SS1997}.
+With respect to the demand controls, we find results similar to those of OLS.
+State fixed effects do not appear to affect the estimates, demand increases over time, and CDDs raise electricity consumption more than HDDs.
+
+Finally, we control for nonlinear effects using a partially linear IV regression reported in \hyperref[table:3]{Table 3}.
+Here, we find results similar to that of OLS; $\hat{\sigma} = 0.413$ ($|t| > 48$) when considering all controls.
+The estimate of $\sigma$ without any controls is not significantly different from that in specifications with controls.
+However, all of these estimates are significantly different from the IV results; hence, the IV regressions do not appear to be robust.
+Consequently, we opt to use these estimates of $\sigma$ in our model.
+Since these estimates show $\hat{\sigma} \in (0,1)$, it appears that electricity consumption in different months complement one another.
+
+\begin{table}[!htbp] \centering 
+	\caption{OLS Regression Results}
+	\label{table:1} 
+	\small
+	\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
+		\\[-4ex]\hline  
+		\hline \\[-1.8ex] 
+		& \multicolumn{6}{c}{\textit{Dependent variable:} $\ln (Z_{ t, i} / Z_{ s, i})$} \\ [0.5ex]
+		\cline{2-7} 
+		\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ [0.5ex]
+		\hline \\[-1.8ex] 
+		$-\ln (P_{t,i} / P_{s,i})$ & 0.751$^{***}$ & 0.481$^{***}$ & 0.607$^{***}$ & 0.750$^{***}$ & 0.481$^{**}$ & 0.607$^{***}$ \\ 
+		& (0.030) & (0.026) & (0.026) & (0.224) & (0.172) & (0.169) \\ 
+		& & & & & & \\ 
+		$\Delta_{t,s}$ &  &  & 0.001$^{***}$ &  &  & 0.001$^{***}$ \\ 
+		&  &  & (0.0001) &  &  & (0.0002) \\ 
+		& & & & & & \\ 
+		CDD$_t$ &  & 0.990$^{***}$ & 1.003$^{***}$ &  & 0.990$^{***}$ & 1.002$^{***}$ \\ 
+		$\quad(\times 1000^{-1})$&  & (0.016) & (0.016) &  & (0.087) & (0.086) \\ 
+		& & & & & & \\ 
+		CDD$_s$ &  & $-$0.999$^{***}$ & $-$1.011$^{***}$ &  & $-$0.999$^{***}$ & $-$1.012$^{***}$ \\ 
+		$\quad(\times 1000^{-1})$&  & (0.016) & (0.016) &  & (0.087) & (0.085) \\ 
+		& & & & & & \\ 
+		HDD$_t$ &  & 0.306$^{***}$ & 0.294$^{***}$ &  & 0.307$^{***}$ & 0.295$^{***}$ \\ 
+		$\quad(\times 1000^{-1})$&  & (0.005) & (0.005) &  & (0.030) & (0.030) \\ 
+		& & & & & & \\ 
+		HDD$_s$ &  & $-$0.309$^{***}$ & $-$0.296$^{***}$ &  & $-$0.308$^{***}$ & $-$0.295$^{***}$ \\ 
+		$\quad(\times 1000^{-1})$&  & (0.005) & (0.005) &  & (0.029) & (0.029) \\ 
+		& & & & & & \\ 
+		Intercept & 0.001 & 0.002 & 0.002 &  &  &  \\ 
+		& (0.003) & (0.006) & (0.006) &  &  &  \\ 
+		& & & & & & \\  [0.9ex]
+		\hline \\[-1.8ex] 
+		State FEs &   &   &   & Yes & Yes & Yes \\ 
+		Observations & 9,000 & 9,000 & 9,000 & 9,000 & 9,000 & 9,000 \\ 
+		R$^{2}$ & 0.070 & 0.580 & 0.596 & 0.070 & 0.580 & 0.596 \\ 
+		Adjusted R$^{2}$ & 0.070 & 0.579 & 0.596 & 0.065 & 0.577 & 0.594 \\ [0.5ex]
+		\hline 
+		\hline \\[-1.8ex] 
+		\multicolumn{7}{@{}p{40em}@{}}{\textit{Note: } The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
+The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state; as discussed in the Data section, we take a random sample of 9000 observations from the data.
+The coefficient on $\ln (P_{t,i} / P_{s,i})$ is an estimate of $-\sigma$.
+The variable $\Delta_{t,s}$ is the difference in months between periods $t$ and $s$.
+CDD$_t$ and HDD$_t$ refer to the total number of heating and cooling degree days in month $t$.
+Robust standard errors are reported in parentheses.
+*p$\textless$0.05, **p$\textless$0.01, ***p$\textless$0.001}  \\
+	\end{tabular} 
+\end{table}
+
+\begin{table}[!htbp] \centering 
+	\caption{IV (2SLS) Regression Results}
+	\label{table:2} 
+	\small
+	\begin{tabular}{@{\extracolsep{4pt}}lcccccc} 
+		\\[-4ex]\hline  
+		\hline \\[-1.6ex] 
+		& \multicolumn{3}{c}{First-Stage} & \multicolumn{3}{c}{Second-Stage} \\ [0.5ex]
+		& \multicolumn{3}{c}{\textit{Dep. Variable:} $\ln (P_{t,i} / P_{s,i})$ } & \multicolumn{3}{c}{\textit{Dep. Variable:}  $\ln (Z_{ t, i} / Z_{ s, i})$}\\ [0.5ex]
+		\cmidrule(lr){2-4} \cmidrule(lr){5-7}\\[-2.2ex] 
+		& (A.1) & (B.1) & (C.1) & (A.2) & (B.2) & (C.2)\\ [0.5ex]
+		\hline \\[-1.8ex] 
+		$ \ln (C_{t,i} / C_{s,i})$ & $-$0.060$^{***}$ & 0.004$^{*}$ & 0.004$^{*}$ &  &  &  \\ 
+		& (0.002) & (0.002) & (0.002) &  &  &  \\ 
+		& & & & & & \\ 
+		$-\ln (P_{t,i} / P_{s,i})$ &  &  &  & 0.711$^{***}$ & 13.987 & 11.430$^{*}$ \\ 
+		&  &  &  & (0.106) & (8.384) & (5.330) \\ 
+		& & & & & & \\ 
+		$\Delta_{t,s}$  &  & 0.001$^{***}$ & 0.001$^{***}$ &  &  & 0.007$^{*}$ \\ 
+		&  & (0.00002) & (0.00002) &  &  & (0.003) \\ 
+		& & & & & & \\ 
+		CDD$_t$  &  & 0.151$^{***}$ & 0.151$^{***}$ &  & 3.064$^{*}$ & 2.620$^{**}$ \\ 
+		$\quad(\times 1000^{-1})$&  & (0.007) & (0.007) &  & (1.288) & (0.798) \\ 
+		& & & & & & \\ 
+		CDD$_s$  &  & $-$0.149$^{***}$ & $-$0.149$^{***}$ &  & $-$3.034$^{*}$ & $-$2.609$^{***}$ \\ 
+		$\quad(\times 1000^{-1})$&  & (0.007) & (0.007) &  & (1.264) & (0.788) \\ 
+		& & & & & & \\ 
+		HDD$_t$  &  & $-$0.057$^{***}$ & $-$0.057$^{***}$ &  & $-$0.407 & $-$0.311 \\ 
+		$\quad(\times 1000^{-1})$&  & (0.003) & (0.003) &  & (0.447) & (0.301) \\ 
+		& & & & & & \\ 
+		HDD$_s$  &  & 0.058$^{***}$ & 0.058$^{***}$ &  & 0.423 & 0.324 \\ 
+		$\quad(\times 1000^{-1})$&  & (0.003) & (0.003) &  & (0.458) & (0.308) \\ [0.9ex]
+		\hline \\[-1.8ex] 
+		State FEs &  Yes & Yes  & Yes  & Yes & Yes & Yes \\ 
+		Observations & 9,000 & 9,000 & 9,000 & 9,000 & 9,000 & 9,000 \\ 
+		R$^{2}$          & 0.066 & 0.441 & 0.441 & & &  \\ 
+		Adjusted R$^{2}$ & 0.066 & 0.441 & 0.441 & & &  \\ 
+		F Statistic & 678$^{***}$ & 1,213$^{***}$ & 1,197$^{***}$  &  &  &  \\ 
+		\hline 
+		\hline \\[-1.8ex] 
+		\multicolumn{7}{@{}p{39.2em}@{}}{\textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions.
+The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
+The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state; as discussed in the Data section, we take a random sample of 9000 observations from the data.
+The coefficient on $\ln (P_{t,i} / P_{s,i})$ is an estimate of $-\sigma$.
+The variable $\Delta_{t,s}$ is the difference in months between periods $t$ and $s$.
+CDD$_t$ and HDD$_t$ refer to the total number of heating and cooling degree days in month $t$.
+Robust standard errors are reported in parentheses.
+*p$\textless$0.05, **p$\textless$0.01, ***p$\textless$0.001}  \\
+	\end{tabular} 
+\end{table}
+
+\begin{table}[!htbp] \centering 
+	\caption{Partially Linear IV Regression Results}
+	\label{table:3} 
+	\small
+	\begin{tabular}{@{\extracolsep{4em}}lccc} 
+		\\[-4ex]\hline  
+		\hline \\[-1.8ex] 
+		& \multicolumn{3}{c}{\textit{Instrument: $ \ln (C_{t,i} / C_{s,i})$}} \\ 
+		\cline{2-4} 
+		%\\[-1.8ex] & ln\_load\_rel \textasciitilde ln\_price\_rel & ln\_load\_rel \textasciitilde (CDD\_1) & ln\_load\_rel \textasciitilde time\_diff + (CDD\_1) \\ 
+		\\[-1.8ex] & (1) & (2) & (3)\\ [0.5ex]
+		\hline \\[-1.8ex] 
+		$\hat{\sigma} $ & 0.5676$^{***}$ & 0.4511$^{***}$ & 0.4129$^{***}$ \\ 
+		& (0.1036) & (0.0042) & (0.0085) \\ [0.9ex]
+		\hline \\[-1.8ex] 
+		Time Control &   &   & Yes  \\ 
+		Degree Day Controls &   & Yes  & Yes  \\ 
+		Observations & 9,000 & 9,000 & 9,000 \\
+		\hline 
+		\hline \\[-1.8ex] 
+		\multicolumn{4}{@{}p{36em}@{}}{\textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions.
+The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
+The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state; as discussed in the Data section, we take a random sample of 9000 observations from the data.
+The estimation procedure is described in the appendix.
+Robust standard errors are reported in parentheses.
+*p$\textless$0.05, **p$\textless$0.01, ***p$\textless$0.001}  \\
+	\end{tabular} 
+\end{table}
+
+\pagebreak
+
 \section{Conclusion}
@@
 An aim for future research may be to develop a model of clean and dirty energy that incorporates both predictable and stochastic intermittency in a multi-period setting.
-
-\pagebreak
-
-\pagebreak
-
-\section{Notes}
-
-\begin{itemize}
-	\item 
-	\item 
-\end{itemize}
-
-\pagebreak
-
-%\subsection{MRS}
-%
-%Next, consider the marginal utility of $X_1$:
-%\begin{equation}
-%\frac{\partial U^\phi}{\partial X_1}  = \int_0^1 \alpha(t) \, \phi \, Y(t)^{\phi - 1} \xi_1(t) \, dt  = \frac{\partial U^\phi}{\partial U}  \frac{\partial U}{\partial X_1} 
-%\end{equation}
-%The marginal rate of substitution must then be:
-%\begin{equation}
-%MRS_{12} =  \frac{ \int_0^1 \alpha(t) \, Y(t)^{\phi - 1} \, \xi_1(t) \, dt }{ \int_0^1 \alpha(t) \, Y(t)^{\phi - 1} \, \xi_2(t) \, dt }
-%\end{equation}
-%Because $Y(t)$ is a function of $X_1$ and $X_2$, we have:
-%\begin{equation}
-%\phi = 1 \implies \frac{\partial MRS_{21}}{\partial X_1 / X_2} = 0 
-%\end{equation}
-%This further implies that the elasticity of substitution between $X_1$ and $X_2$ approaches infinity, hence the two inputs would become perfect substitutes. 
-%
-%% Now, suppose that we have $\xi_1(t) \neq \xi_2(t)$, so our inputs differ in their electricity generation.
-%	
-%
-
-\pagebreak
-
-\pagebreak
-
-\section{Scratch}
 
@@
 
+	\bibitem[Staiger and Stock(1997)]{SS1997} 
+	Staiger, D., \& Stock, J. (1997). Instrumental Variables Regression with Weak Instruments. Econometrica, 65(3), 557–586. https://doi.org/10.2307/2171753
+
 	\bibitem[Warkins and Knight(1922)]{Knight}

### 2019-04-23 code/matlab/simulation_april/sim_technical_change.m

@@ -1,30 +1,36 @@
 %% Price (Cost) Elasticity Sim
 
+close all; clear; clc;
+
+% Simulation params
 n = 500;
-results = zeros(n,2); 
 cost_multiplier = linspace(0.5,2,n);
 sigma_range = [0.1, 0.5, 1.0, 1.5, 2];
 m = length(sigma_range);
 
+% Exogenous params
+c_1 = 104.3;
+c_2 = 50;
+alpha = [0.6, 0.4];
+xi_1  = [1,   1];
+xi_2  = [1, 0.1];
+budget = 1;
 
-figure;
+
+figure('Renderer', 'painters', 'Position', [100 100 900 600])
 hold on;
 
 for j = 1:m
     
     sigma = sigma_range(j);
+    results = zeros(n,2); 
 
     for i = 1:n
 
-        alpha = [0.6, 0.4];
-        xi_1  = [1,   1];
-        xi_2  = [1, 0.1];
-        
-        phi   = (sigma - 1)/sigma;
-        budget = 1;
 
-        x_1_cost_param = 104.3*cost_multiplier(i);
-        x_2_cost_param = 50;
+        phi   = (sigma - 1)/sigma;
+        x_1_cost_param = c_1*cost_multiplier(i);
+        x_2_cost_param = c_2;
 
         % Prices
         xi_mat   = [xi_1; xi_2];
@@ -52,7 +58,7 @@ for j = 1:m
     end    
 
     output = [];
-    output(1,:) = 95*cost_multiplier'./50;
+    output(1,:) = c_1*cost_multiplier'./c_2;
     output(2,:) = results(:,1)./results(:,2);
 
     % subset to positive quantities
@@ -62,26 +68,45 @@ for j = 1:m
     % relationship between log prices and quantities
     subplot(2,1,1);
     hold on;
-    plot(-log(output(1,:)), log(output(2,:)))
+    plot(-log(output(1,:)), log(output(2,:)), 'LineWidth', 1)
     
     
     % relationship between log prices and quantities
     subplot(2,1,2);
     hold on;
-    plot(-log(output(1,2:end)), diff(log(output(2,:)))./diff(-log(output(1,:))))
+    
+    plot(-log(output(1,2:end)), ...
+        diff(log(output(2,:)))./diff(-log(output(1,:))), ...
+        'LineWidth', 1);
     
 end
 
+%% Plot formatting
+
[…]

### 2019-04-26 documents/draft.tex
Update draft
- revise definition of intermittency/reliability
- update last paragraph of intro

@@
 
-\author[]{Saketh Aleti}
-
-\affil[]{\small{}}
+\author[]{Saketh Aleti\thanks{I would like to thank Gal Hochman for helpful comments and the Sun Grant for funding this project. }}
+
+\affil[]{\small{Rutgers University}}
 
@@
 To highlight this difference, we must first contrast the terms  \textit{intermittency} and \textit{reliability}.
-By intermittency, we mean uncontrollable variation in output over time due to physical constraints; by reliability, we mean variation in output that is wholly unpredictable\footnote{By unpredictible, we mean a notion similar to that of \textit{Knightian uncertainity} \citep{Knight}.
-} and may be the result of failures that cannot be modeled stochastically.
-Consider wind energy as an example.
-The energy provided by a wind turbine necessarily varies over time due to differences in wind speed and direction.
-Moreover, the relationship between the force created by the wind and the amount of wind power generated must necessarily be a fixed, functional relationship; that is, \textit{ceterius paribus}, two identical wind turbines under identical wind conditions should generate the same amount of energy.
-Consequently, the output of wind power can be forecasted up to an error term.\footnote{\citet{Foley2012} provide a review of the literature on the forecasting of wind power.} Because no forecast of wind (or solar) power can be perfect, some level of stochastic intermittency may be left in the error term.
-At the same time, the error term also captures unreliability; for instance, failures in the circuitry of wind turbines cannot simply be forecasted with a time series.
-So, overall, we may think of the energy output of a renewable technology as consisting of three components: a knowable/forecastable component related to intermittency, a stochastic component related to intermittency, and an unpredictible component related to reliability.
-
-While \citet{HH} model the stochastic component of intermittency, we model the predictible component.
-More specifically, Helm and Mier model the capacity of renewable energy equal to a baseline capacity multiplied by a uniform random variable between 0 and 1.
-This is a valid approach given that their model consists of a single period of generation.
-On the other hand, we neglect stochastic intermittency for parsimony and develop a general, multi-period model where the output per unit of each technology follows a known function.
-We then narrow this to a two period, two technology model where our first technology represents fossil fuel energy with constant output in both periods while our second technology's output differs between each period.
-Additionally, while their model consists of two sets of consumers, one set which receives fixed price contracts and another paying real time prices, we consider one representative consumer.
-Specifically, this representative consumer's utility is given by CES function where each good is electricity consumption differentiated by time.
-Interestingly, this treatment of intermittency produces some key results similar to that of Helm and Mier.
+By intermittency, we predictable changes in output related to physical constraints.
+For instance, while wind energy output varies over time, if  we know the angle and speed of wind, we may precisely derive the quantity of energy that a wind farm generates.\footnote{\citet{Foley2012} provide a review of the literature on the forecasting of wind power.
+Over time, forecasts have gotten much more accurate allowing electricity grids to manage wind power intermittency ahead of time.}  At the same time, these forecasts may not be perfect and, as a result, we see unexpected variation in the output of a technology.
+This unpredictability may be better captured by the notion of reliability; specifically,  we refer to definition provided by the US Department of Energy's \citep{ORNL} -- ``Power reliability can be defined as the degree to which the performance of the elements in a bulk system results in electricity being delivered to customers within accepted standards and in the amount desired." This is more so related to the stochastic or unpredictable variation in the output of a technology.
+Unlike intermittency, this cannot be planned around with 100\% certainty.
+A practical example may be a wind turbine's systems failing.
+While we may know the chances of this occurring, it's not possible to know when it will occur ahead of time; consequently, this may result in a temporary reduction in the quantity and quality of the electricity delivered --  a loss of reliability.
+In short, when \citeauthor{HH} define renewable output as equal to a baseline capacity multiplied by a uniform random variable, their model is closer to one of reliability rather than intermittency.
+
+On the other hand, we neglect reliability for parsimony and develop a two-technology, two-period model consisting of fossil and renewable energy.
+Then, we model intermittency as defined above by allowing the output of renewable energy to differ between periods according to known function.
+At the same time, we consider a representative consumer whose utility is given by CES function where each good is electricity consumption differentiated by time.
+This captures consumers' preferences for electricity consumption throughout the day as well as their willingness to substitute consumption across time.
+We then fit the parameters of this CES utility function using electricity consumption and price data for each US state.
+At the same time, we set parameters of our technologies (their cost and output) to those of coal and solar.
+Overall, this treatment of intermittency produces some key results similar to that of Helm and Mier.
+That is, we also find a Pigovian tax to be a solution to externalities along with an S-shaped adoption curve for renewables.
+But, moreover, we find the elasticity of substitution between fossils and renewables to be highly non-linear; this directly challenges the CES production structure assumption made by standard models of fossil and renewable energy.
+Finally, we discuss how a combination of carbon taxes and research subsidies may be more optimal than carbon taxes alone in the presence of intermittency.
 
@@
 In order to estimate this $\sigma$, we further modify the previous equation. 
-Firstly, note that we cannot observe the demand shifter $\alpha_{t,i}$ directly, so we add a set of controls that may be responsible for shifts in demand. Our regression is then
+Firstly, note that we cannot observe the demand shifter $\alpha_{t,i}$ directly, so we must replace the $\alpha$ terms with a set of controls that may be responsible for shifts in demand.
+So, still in general terms, our regression equation is now
 \begin{align*}
@@
 
+	\bibitem[ORNL(2004)]{ORNL}
+	ORNL (2004).
+Measurement practices for reliability and power quality.
+A toolkit of reliability measurement practices.
+U.S.
+Department of Energy.
+https://info.ornl.gov/sites/publications/Files/Pub57467.pdf
+
 	\bibitem[Schwarz et al.(2002)]{Schwarz}

### 2019-04-27 documents/draft.tex
Update draft
- Clean up equilibrium results
- Move cobb-douglas example to appendix
- Add intro to empirical methodology
- Add more literature

@@
 
+% math claims
+\newtheorem{theorem}{Theorem}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{proposition}{Proposition}
+\newenvironment{proof}[1][Proof]{\noindent\textbf{#1:} }{\ \rule{0.5em}{0.5em}}
+
 % sig stars
@@
 
-% proofs
-\newenvironment{proof}[1][Proof]{\noindent\textbf{#1:} }{\ \rule{0.5em}{0.5em}}
-
 \begin{document}
@@
 
-\author[]{Saketh Aleti\thanks{I would like to thank Gal Hochman for helpful comments and the Sun Grant for funding this project. }}
+\author[]{Saketh Aleti\thanks{I would like to thank Gal Hochman and Roger Klein for helpful comments and the Sun Grant for funding this project. }}
 
@@
 
-\subsection{General Model}
+\subsection{Consumers}
 
@@
 
+\subsection{Firms}
+
 Secondly, we have firms maximizing profit by picking an optimal set of energy inputs.
@@
 \end{equation}
-Combining both first order conditions allows us to find the equilibrium.
-The equilibrium results any number of technologies ($n$) are analytic, but they are difficult to interpret due to the number of parameters involved.
-Hence, in order to produce more comprehensible results, we proceed with a special case of our general model.
-
-\subsection{Cobb-Douglas Case with Two Periods \& Two Technologies}
-
-\subsubsection{Equilibrium Results}
-
-Firstly, we restrict the utility function to its Cobb-Douglas form which is simply the case where the elasticity of substitution $\sigma = 1$.
-Secondly, we limit the number of periods and technologies to 2.
-And, thirdly, we normalize the prices such that the budget $I$ is $1$.
-Consequently, our demand equations simplify to:
-\begin{align}
-Z_t &= \alpha_t / p_t \\
-Z_s &= \alpha_s / p_s
-\end{align}
-where $t$ and $s$ are our two periods. Next, solving for the FOC condition for profit maximization, we have:
-\begin{align*}
-p &=  \xi^{-1} c \\
-p &= \begin{pmatrix}
--\dfrac{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}  \\[2ex]
-\dfrac{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}} 
-\end{pmatrix} 
-\end{align*}
-And, substituting back into our demand equations, we find the equilibrium quantities for $Z$ and $X$. 
-$$
-Z = \begin{pmatrix}
-\dfrac{\alpha _{t}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{c_{2}\,\xi _{\mathrm{1s}} - c_{1}\,\xi _{\mathrm{2s}}} \\[2ex]
-\dfrac{\alpha _{s}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} 
-\end{pmatrix}
-\implies 
-X = \begin{pmatrix}
-\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}+\dfrac{\alpha _{s}\,\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} \\[2ex] 
--\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}-\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}
-\end{pmatrix}
-$$
-
-Furthermore, we derive restrictions on the parameters $\xi$ and $c$ by assuming $Z, X > 0$.
-These restrictions are detailed in \hyperref[tab:paramrest]{Table 1}.
-There are two possible sets of symmetrical restrictions.
-The first set, Case 1, assumes that technology 2 is more cost effective in period $t$, while the second set, Case 2, assumes that technology 1 is more cost effective in period $t$.
-If a given set of parameters do not fall into either case, we are left with an edge case where one of the technologies is not used.
-Additionally, these inequalities compare two types of efficiency -- output efficiency and cost efficiency; we define output efficiency as electricity output per unit of input and cost efficiency in terms of electricity output per dollar of input.
-We refer to the last set of restrictions as mixed, because they relate both cost and output efficiency.
-
-\begin{table}[h!]
-	\caption{Parameter Restrictions for $Z, X > 0$} 
-	\label{tab:paramrest}
-	\small
-	\centering
-	\begin{tabular}{@{\extracolsep{2em}}l@{\hspace{-0.5 em}}cc}
-		\\[-4ex]
-		\toprule \\[-2.5ex]
-		& \textbf{Case 1} & \textbf{Case 2 } \\
-		\cmidrule(lr){2-2} \cmidrule(lr){3-3} \\[-1.5ex]
-		\textbf{Cost Efficiency}& $\xi_{2t}/c_2 > \xi_{1t}/c_1$ & $\xi_{2t}/c_2 < \xi_{1t}/c_1 $\\
-		\textbf{Restrictions} & $\xi_{1s}/c_1 > \xi_{2s}/c_2$  & $\xi_{1s}/c_1 < \xi_{2s}/c_2 $ 		\\ [3ex]
-		\textbf{Output Efficiency}& $\xi_{2t}/\xi_{2s} > \xi_{1t}/\xi_{1s}$ & $\xi_{2t}/\xi_{2s} < \xi_{1t}/\xi_{1s}$\\
-		\textbf{Restrictions} & $\xi_{1s}/\xi_{1t} > \xi_{2s}/\xi_{2t} $  & $\xi_{1s}/\xi_{1t} < \xi_{2s}/\xi_{2t}  $ 		\\ [3ex]
-		\multirow{2}{10em}{\textbf{Mixed Efficiency Restrictions}}& $\dfrac{\alpha_s \left(\xi_{1s}/c_1 - \xi_{2s}/c_2\right)}{\alpha_t \left( \xi_{2t}/c_2 - \xi_{1t}/c_1 \right)} > \xi_{2s}/\xi_{2t}$ & $\dfrac{\alpha_s \left(\xi_{1s}/c_1 - \xi_{2s}/c_2\right)}{\alpha_t \left( \xi_{2t}/c_2 - \xi_{1t}/c_1 \right)} < \xi_{2s}/\xi_{2t}$\\
-		& $\dfrac{\alpha_s \left(\xi_{1s}/c_1 - \xi_{2s}/c_2\right)}{\alpha_t \left( \xi_{2t}/c_2 - \xi_{1t}/c_1 \right)} < \xi_{1s}/\xi_{1t} $  & $\dfrac{\alpha_s \left(\xi_{1s}/c_1 - \xi_{2s}/c_2\right)}{\alpha_t \left( \xi_{2t}/c_2 - \xi_{1t}/c_1 \right)} > \xi_{1s}/\xi_{1t} $ 		\\[2ex]
-		\midrule
-		\multicolumn{3}{@{}p{40em}@{}}{\footnotesize \textit{Note: } The inequalities in this table assume that all elements of $\xi$ are greater than $0$.
-The full proof given below provides equivalent restrictions for the zero cases.
+Combining this FOC with the demand equation (Equation (3)) allows us to find the equilibrium.
+Generally, the equilibrium results for any number of technologies ($n$) are analytic, but they are difficult to interpret due to the number of parameters involved.
+
+\subsection{Equilibrium}
+
+For more tractable results, we consider a simpler scenario where $n = m = 2$ and $\sigma = 1$ (Cobb-Douglas) which is described in detail in the appendix.
+To start, this scenario allows us to determine which sets of parameters lead to edge cases where one of the technologies is not used.
+We may define these conditions in terms of cost efficiency and output efficiency; to clarify, for some arbitrary period $t$ and technology $i$, we use cost efficiency to refer to $\xi_{i,t}/c_i$ and output efficiency to refer to $\xi_{i,t}$.
+The conditions to avoid an edge case are then given by the following proposition.
+\begin{proposition}
+	For technology $i$ to be economical, it must meet three conditions with respect to same arbitrary period $t$.
+Firstly, it must the most cost effective technology for some particular period $t$.
+Secondly, it must have have a comparative advantage in output efficiency in the same period $t$.
+And, thirdly, there must be sufficient amount of demand for energy in this period $t$.
+\end{proposition}
+The condition on cost efficacy is fairly intuitive; one case of the contrapositive is that if a technology is not cost effective in any period, it will not be used.
+Similarly, the other is that if a technology is the most cost effective in every period, it will be the only technology used.
+The second condition regarding output efficiency actually stems from the invertibility of $\xi$.
+If we did not have $\xi$ invertible, we either have at least one technology that does not produce in any period or we have at least one technology being a linear combination of the other technologies.
+In the latter case, some technologies are not economical because their output can be replicated the other technologies in a more cost effective way.
+As an example, suppose $\xi$ consisted of 3 technologies but was of rank $2$.
+In this case, we may represent any of these technologies as a linear combination of the other two; call this combination the synthetic version of technology $i$.
+It is not possible for every synthetic technology $i$ to be more expensive than its original; for at least one $i$, we must have a synthetic technology being cheaper or equal in price to the actual technology.
+In the first case, synthetic technology $i$ is cheaper so we do not use the actual technology $i$.
+In the later case, we may still eliminate technology $i$ or not use the other two technologies depending on the demand.
+Overall, in any case, $\xi$ not invertible means at least one technology is not used.
+Finally, the demand condition is straightforward; even if a technology is optimal in a certain period, if consumers do not sufficiently demand electricity during that period, then there is little reason to use that technology.
+
+We may also derive the comparative statics for this simplified scenario.  
+\begin{proposition}
+	The equilibrium quantity of a technology is increasing with its output efficiency and decreasing with its cost; at the same time, it is decreasing with the output efficiency of the other technologies and increasing with their cost.
+Also, suppose that some technology $i$ is the most cost effective in period $t$.
+Then, its equilibrium quantity is increasing with respect to the demand share parameter $\alpha_t$ and decreasing with respect to the demand share parameters of the other periods.
+Furthermore, with the same conditions on $i$ and $t$, the comparative statics of $Z_t$ and $X_i$ are equivalent.
+\end{proposition}	
+The comparative statics with respect to $X$ and its output efficiency and cost are not surprising.
+On the other hand, the statics for $Z$ may not be immediately obvious.
+However, they are still intuitive given that we have $Z = \xi_T X$.
+That is, suppose that the optimal quantity of $X_1$ rises by 1\% while that of $X_2$ falls by the same amount.
+Then, we expect output to increase whichever period $\xi_1$ is largest, while it should fall in whichever period $\xi_2$ is smallest; this essentially describes the signs for $\partial Z / \partial X$.
+Now, since we have already derived the signs of the comparative statics for $X$ with respect to each of the parameters, we can intuit, by the chain rule, the comparative statics for $Z$.\footnote{This intuition would not be correct if the derivative in $X_1$ with respect to an arbitrary parameter was significantly different in magnitude from the derivative in $X_2$ with respect to the same parameter.
+However, in this particular scenario, such a case does not occur.} Similarly, the comparative statics for the share parameters of the utility function, $\alpha$, follow in the opposite direction.
+A rise in $\alpha_t$ would directly raise the optimal quantity of $Z_t$; hence, whichever technology is more cost effective at producing in period $t$ would be used more.
+We provide a more detailed and quantitative discussion of the comparative statics and edge cases in the appendix.
+
+\section{Empirical Methodology}
+
+In order to better understand the practical implications of our model, we empirically estimate its parameters and study its implications numerically.
+We are particularly interested in estimating $\sigma$, the intertemporal elasticity of substitution for electricity consumption.
+In our  \hyperref[sec:Discussion]{discussion}, we explain in detail why $\sigma$ is of interest; but, to summarize, $\sigma$ implicitly determines how well renewables can substitute for fossil energy.
+Specifically, if $\sigma \geq 1$, then electricity consumption in different periods are substitutes; consequently, fossil energy and renewable energy are highly substitutable.
+On the other hand, if $\sigma$ is around $0.5$, electricity consumption in different periods are complements; so, fossil and renewable energy are far less substitutable due to the effects of intermittency.
+
+The other parameters in our model, $c$,  $\xi$, and $\alpha$, are of secondary interest, since they are easier to obtain directly.
+To start, $c$ is the cost per unit for each technology; estimates of this value for different technologies can be obtained directly from the literature.
+Similarly, $\xi$, the output per unit of technology, can be directly obtained from the literature.
+And, finally, $\alpha$ may be approximated directly from the data.
+That is, note that the demand equation from earlier (Equation 3) is:
+$$Z_t = \left(\frac{\alpha_t}{p_t} \right)^\sigma \frac{I}{P}$$
+where $P$ is the price index and $I$ is income.
+Retail customers pay fixed rates each month for electricity, hence $p_t$ is constant within each month; and, we expect that income $I$ does not vary significantly on a daily basis.
+Consequently, all variation in intramonthly demand is due to the share parameter $\alpha$ and the elasticity $\sigma$.
+Hence, after estimating $\sigma$, we can approximate $\alpha$.
+However, this raises another problem, because, without prices varying each hour, we cannot estimate  $\sigma$ on an hourly basis.
+
+A number of other papers have approached this problem using data from real-time pricing experiments.
+These include \citet{Schwarz}, \citet{Herriges}, and \citet{KS1994}.\footnote{There has also been a large literature that directly estimates the price elasticity of electricity demand without imposing a CES functional form.
+These papers include \citet{Wolak}, \citet{Zarnikau}, \citet{Woo}, \citet{Zhou}, \citet{Reiss}, \citet{Fan}, and \citet{Deryugina}.
+These papers estimate own-price elasticities, while some also estimate cross-price elasticities for electricity consumption at different times.
+Because they do not impose a CES structure, we cannot obtain estimates of $\sigma$ from this literature.
 }
-	\end{tabular} 
-\end{table}
-
-\hfill\\
-\begin{proof}
-	We aim to derive conditions on $\xi$ and $c$ required to have positive $Z$ and $X$, so we begin by assuming $X, Z  > 0$.
-Second, since the equations so far are symmetrical, note that there be two symmetrical sets of potential restrictions we must impose on the parameters.
-Thus, we first assume the inequality $c_1 \xi_{2t} - c_2 \xi_{1t} > 0$ to restrict ourselves to one of the two cases.
-This assumption results in the denominator of $Z_s$ being positive.
-Hence, we must also have $\xi_{1s}\xi_{2t} - \xi_{2s}\xi_{1t} > 0 $ for $Z_s > 0$.
-This same term appears in the numerator for $Z_t$, hence its denominator must be positive: $c_2 \xi_{1s} - c_1 \xi_{2s} > 0$.
-Now, rewriting these inequalities, we have:
-	\begin{align*}
-	c_1 \xi_{2t} - c_2 \xi_{1t} > 0 &\implies \xi_{2t}/c_2 > \xi_{1t}/c_1 \\
-	c_2 \xi_{1s} - c_1 \xi_{2s} > 0 &\implies \xi_{1s}/c_1 > \xi_{2s}/c_2 \\
-	\xi_{1s}\xi_{2t} - \xi_{2s}\xi_{1t} > 0 &\implies \xi_{1s}/\xi_{1t} > \xi_{2s}/\xi_{2t} \\
-	&\implies \xi_{1t}/\xi_{1s} < \xi_{2t}/\xi_{2s} 
-	\end{align*}
-	Note that the latter two restrictions can be derived from the former two.
-Additionally, we implicitly assume that we have $\xi > 0$.
-However, this is not necessary assumption, since $\xi$ invertible only requires $\xi_{1t} \xi_{2s} > 0$ or $\xi_{1s} \xi_{2t} > 0$.
-Instead, we may leave the latter two inequalities in the form $ \xi_{1s}\xi_{2t} > \xi_{2s}\xi_{1t}$ which remains valid when values of $\xi$ are equal to $0$.
-Lastly, the mixed efficiency restrictions come from $X > 0$.
-To start, for $X_1$, we have:
-	\begin{align*}
-	X_1 > 0 &\implies (\alpha_t \xi_{2s})(c_1 \xi_2t - c_2\xi_1t) + (\alpha_s \xi_{2t})(c_1 \xi_{2s} - c_2 \xi_{1s}) < 0\\
-	&\implies (\alpha_t \xi_{2s})(c_1 \xi_2t - c_2\xi_1t) < (\alpha_s \xi_{2t})(c_2 \xi_{1s} - c_1 \xi_{2s}) \\
-	&\implies (\xi_{2s}/\xi_{2t}) < (\alpha_s (c_2 \xi_{1s} - c_1 \xi_{2s}))/(\alpha_t(c_1 \xi_{2t} - c_2\xi_{1t})) \\
-	&\implies (\xi_{2s}/\xi_{2t}) < (\alpha_s (\xi_{1s}/c_1 -  \xi_{2s}/c_2))/(\alpha_t(\xi_{2t}/c_2 - \xi_{1t}/c_1)) 
-	\end{align*}
-	Similarly, for $X_2$, note that only the numerators differ; $\xi_{2s}$ is replaced with $-\xi_{1s}$ and $\xi_{2t}$ is replaced with $-\xi_{1t}$. Hence, we have
-	\begin{align*}
-	X_2 > 0 &\implies (\alpha_t \xi_{1s})(c_1 \xi_2t - c_2\xi_1t) + (\alpha_s \xi_{1t})(c_1 \xi_{2s} - c_2 \xi_{1s}) > 0\\
-	&\implies (\xi_{1s}/\xi_{1t}) > (\alpha_s (\xi_{1s}/c_1 -  \xi_{2s}/c_2))/(\alpha_t(\xi_{2t}/c_2 - \xi_{1t}/c_1)) 
-	\end{align*}
-	To double check, note that combining the inequalities from $X_1>0$ and $X_2 > 0$ leads to $\xi_{2s}/\xi_{2t} < \xi_{1s}/\xi_{1t}$.
-This is precisely the earlier result obtained from $Z > 0$.
-Again, it is  important to note that we assume $\xi > 0$ for to simplify the inequalities of $X_1 > 0$ and $X_2 > 0$ .
-Otherwise, we may leave the inequalities in their pre-simplified forms and they are still valid when  $\xi_{1t} \xi_{2s} > 0$ or $\xi_{1s} \xi_{2t} > 0$.
-\\ \hfill
-\end{proof}
-
-Let us consider the set of restrictions belonging to Case 1.
-The first inequality, our initial assumption, states that technology 2 is relatively more cost effective in period $t$.
-The second inequality claims technology 1 is relatively more cost effective in period $s$.
-The implications are fairly straightforward; if a technology is to be used, it must have an absolute advantage in cost efficiency in at least one period.
-The third condition states that the relative output efficiency of technology 2 is greater than that of the first technology in period $t$.
-And, the fourth condition makes a symmetrical claim but for the technology 1 and period $s$.
-These latter two restrictions regarding output efficiency enter $Z$ and $X$ through $p$; they're simply a restatement of the invertibility of $\xi$ and can also be derived through the cost efficiency restrictions.
-
-The mixed efficiency restrictions are less intuitive.
-Firstly, note that $\left(\xi_{1s}/c_1 - \xi_{2s}/c_2\right)$ is the difference in cost efficiency for the two technologies in period $s$; this is equivalent to the increase in $Z_s$ caused by shifting a marginal dollar towards technology 1.
-Similarly, the bottom term $\left( \xi_{2t}/c_2 - \xi_{1t}/c_1 \right)$ represents the change in $Z_t$ caused by shifting a marginal dollar towards technology 1.
-Both these terms are then multiplied by the share parameter of the utility function for their respective time periods.
-Furthermore, note that $\alpha_t$ $(\alpha_s)$ is the elasticity of utility with respect to $Z_t$ $(Z_t)$.
-Hence, in total, the mixed efficiency restrictions relate the relative cost efficiencies of each technology with their output efficiency and the demand for energy.
-So, for example, suppose that consumers prefer, \textit{ceteris paribus}, that nearly all their electricity arrive in period $t$.
-This would imply $\alpha_t$ is arbitrarily large which results in the left-hand side of the fraction becoming arbitrarily small.
-This violates the first mixed efficiency restriction but not the second; consequently, use of the first technology, which is less cost effective in period $t$, approaches $0$.
-
-In more practical terms, suppose that our first technology is coal power and the latter is solar power.
-Although coal power is dispatchable, it does not easily ramp up or down within a day; hence, it is reasonable to apply our model where capacities are fixed over time so long as our time frame is sufficiently short.
-Hence, we now assume periods $t$ and $s$ represent the peak and off-peak for a day.
-And, we expect that there is more available solar radiation during peak hours than off-peak hours, since peak hours are usually during the middle of the day.
-This implies that the the output efficiency of solar power is higher in period $t$ due to more available solar radiation.
-Additionally, since the energy output of a unit of coal is independent of time, we know that the output efficiency of coal is constant.
-In total, this implies that we have met the output efficiency restrictions, since we have $\xi_{2t}/\xi_{2s} > \xi_{1t}/\xi_{1s}$.
-Next, we can reasonably assume that coal is more cost effective than solar in the off-peak period when there is less sun; hence, the second cost efficiency restriction is satisfied.
-Then, for there to be an incentive to use solar power, we must satisfy the first cost-efficiency condition; that is, solar needs be cost effective during peak hours otherwise we hit an edge case where no solar is employed.
-And, finally, solar must also satisfy the mixed efficiency condition, which essentially implies that there must be sufficient demand for electricity during period $t$, when solar is more effective, for it to be a feasible technology.
-So, overall, for a technology to be economical, it must meet three conditions: it must the most cost effective technology for a particular period, its output efficiency must be maximized in the same period, and there must be sufficient amount of demand in that period.
-
-%\footnote{This same analysis can be further extended to any $n$ technologies.
-However, the number restrictions and different cases to ensure $X , Z > 0$ expands very quickly ($O(n!)$).
-For instance, if we had 3 technologies and 3 periods, we must first assume each technology is more cost effective than the other two in a unique period; this adds 3*2 restrictions.
-Then, we must make the output efficiency restrictions comparing each pair of technologies for each pair of periods.}
-
-\subsubsection{Comparative Statics}
-
-The comparative statics are similarly intuitive.
-The equilibrium quantity of a technology is increasing with its output efficiency and decreasing with its cost per unit.
-Additionally, the equilibrium quantities for a particular technology move in the opposite direction with respect to the output efficiency and cost of the other technologies.
-For a practical example, consider again coal and solar power from before.
-An increase in the output efficiency of solar or a decrease in solar power's cost will reduce the optimal quantity of coal power.
-Likewise, as coal power's efficiency improves, it's adoption rises.
-To find the effects of $\alpha$ on $X$, we must assume one of the cases of restrictions shown in \hyperref[tab:paramrest]{Table 1}.
-So, again, let us assume Case 1 is true; this implies that $X_2$ is the most cost effective technology in period $t$ and likewise for $X_1$ in period $s$.
-Firstly, note that $\alpha$ determines demand for electricity in a period.
-Hence, when $\alpha_t$ rises, we see the optimal level of $X_2$ rise as well; likewise, $X_1$ rises with $\alpha_s$.
-In short, the optimal quantity of a technology rises linearly with the demand for electricity in the period it specializes in.
-Moreover, these relationships are reversed with respect to demand in each technology's suboptimal period.
-So, for example, we would expect the use of solar energy to rise when demand for electricity during peak hours rises, and it would fall when demand for energy in the off-peak rises.
-On the other hand, use coal power would rise with off-peak demand and fall with peak demand.
-This concept carries through for the comparative statics of $Z$.
-When the output efficiency of technology 1 rises or its cost falls, we see output $Z_s$ rise and output $Z_t$ fall.
-This is because technology 1 is optimal in period $s$ given the Case 1 restrictions.
-Likewise, we see symmetrical results for the output with respect to the cost and output efficiency of technology 2; improvements in the efficiency of $X_2$ result in greater output in $Z_t$ and smaller output in $Z_s$.
-
-\hfill \\
-\begin{proof}
-	We begin by deriving the comparative statics of the cost and efficiency parameters with respect to $X$.   Firstly, we take derivatives with respect to the cost vectors:
-	\begin{align*}
-	\frac{\partial X_1}{\partial c} &= 
-	\begin{pmatrix}
-	-\dfrac{\alpha _{t}\,{\xi _{\mathrm{2s}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}-\dfrac{\alpha _{s}\,{\xi _{\mathrm{2t}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} \\
-	\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}+\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}
-	\end{pmatrix}
-	=
-	\begin{pmatrix}
-	< 0 \\
-	> 0 
-	\end{pmatrix} \\
-	\frac{\partial X_2}{\partial c} &= 
-	\begin{pmatrix}
-	\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}+\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} \\
-	-\dfrac{\alpha _{t}\,{\xi _{\mathrm{1s}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}-\dfrac{\alpha _{s}\,{\xi _{\mathrm{1t}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}
-	\end{pmatrix}
-	=
-	\begin{pmatrix}
-	> 0 \\
-	< 0 
-	\end{pmatrix}
-	\end{align*}
-	The first and second terms of $\partial X_1 / \partial c_1$ are clearly both negative independent of the restrictions on the parameters.
-Similarly, all terms of  $\partial X_1 / \partial c_2$ are positive independent of any restrictions.
-Since the structure of this problem is symmetrical with respect to $X_1$ and $X_2$, the same comparative statics apply but in reverse for $X_1$.
-Next, we derive comparative statics for each element of $\xi$.
-	\begin{alignat*}{2}
-	\frac{\partial X_1}{\partial \xi} &= 
-	\begin{pmatrix}
-	\dfrac{\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} & \dfrac{\alpha _{t}\,c_{2}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} \\
-	\dfrac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} & \dfrac{-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} \\
-	\end{pmatrix}
-	&&=
-	\begin{pmatrix}
-	> 0 & > 0  \\
-	< 0 & < 0
-	\end{pmatrix} \\
-	\frac{\partial X_2}{\partial \xi} &= 
-	\begin{pmatrix}
-	\dfrac{-\alpha _{s}\,c_{1}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} & \dfrac{-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} \\
-	\dfrac{\alpha _{s}\,c_{1}\,\xi _{\mathrm{1t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}& \dfrac{\alpha _{t}\,c_{1}\,\xi _{\mathrm{1s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} \\
-	\end{pmatrix}
-	&&=
-	\begin{pmatrix}
-	< 0 & < 0 \\
-	> 0 & > 0  
-	\end{pmatrix}
-	\end{alignat*}
-	Again, the signs are fairly straightforward.
-The optimal quantity of $X_1$ increases with its output efficiency in both periods; however, it decreases with the output efficiency of $X_2$ in both periods.
-Similarly, symmetrical results are shown for $X_2$.
-Next, we study the effects of $\alpha$ on $X$; this requires us to place some restrictions on the parameters, so we use those belonging to Case 1 in \hyperref[tab:paramrest]{Table 1}.
-With $\alpha \equiv \left( \alpha_t \;\; \alpha_s \right)^T$,
-	\begin{align*}
-	\frac{\partial X_1}{\partial \alpha} &= 
-	\begin{pmatrix}
-	\dfrac{\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} \\
-	\dfrac{\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}
-	\end{pmatrix}
-	=
-	\begin{pmatrix}
-	< 0 \\
-	> 0 
-	\end{pmatrix} \\
-	\frac{\partial X_2}{\partial \alpha} &= 
-	\begin{pmatrix}
-	\dfrac{-\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} \\
-	\dfrac{-\xi _{\mathrm{1t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}
-	\end{pmatrix}
-	=
-	\begin{pmatrix}
-	> 0 \\
-	< 0 
-	\end{pmatrix}
-	\end{align*}
-	Note that our restrictions imply that $c_1 \xi_{2t} - c_2 \xi_{1t} > 0$ and $c_2 \xi_{1s} - c_1 \xi_{2s} > 0$.
-From here, the intuition is clear; we assume that $X_2$ is more cost efficient in period $t$, so increases in demand during period $t$ (caused by increases in $\alpha_t$) will increase the optimal quantity of $X_2$.
-And, the same applies to $X_1$ with respect to period $s$ and $\alpha_s$.
-Again, due to symmetry, the statics are reversed when the technologies are flipped.
-Similarly, the signs would also be flipped if we used the restrictions given by Case 2 instead.
-
-	Next, we derive the comparative statics for $Z$. 
-	\begin{alignat*}{2}
-	\frac{\partial Z_t}{\partial c} &= 
-	\begin{pmatrix}
-	\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}\\
-	\dfrac{-\alpha _{t}\,\xi _{\mathrm{1s}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}
-	\end{pmatrix}
-	&=
-	\begin{pmatrix}
-	> 0 \\
-	< 0 
-	\end{pmatrix} \\
-	\frac{\partial Z_s}{\partial c} &= 
-	\begin{pmatrix}
-	\dfrac{-\alpha _{s}\,\xi _{\mathrm{2t}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} \\
-	\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}
-	\end{pmatrix}
-	&=
-	\begin{pmatrix}
-	< 0 \\
-	> 0 
-	\end{pmatrix}
-	\end{alignat*}
-	From our restrictions, we have $\xi_{1s}\xi_{2t} > \xi_{2s}\xi_{1t}$, and all the results above follow from this. 
-	\begin{alignat*}{2}
-	\frac{\partial Z_t}{\partial \xi} &= 
-	\begin{pmatrix}
-	\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} & \dfrac{-\alpha _{t}\,\xi _{\mathrm{2s}}\,\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} \\
-	\dfrac{-\alpha _{t}\,\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} & \dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} \\
-	\end{pmatrix}
-	&&=
-	\begin{pmatrix}
-	< 0 & < 0  \\
-	> 0 & > 0
-	\end{pmatrix} \\
-	\frac{\partial Z_s}{\partial \xi} &= 
-	\begin{pmatrix}
-	\dfrac{-\alpha _{s}\,\xi _{\mathrm{2t}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}& \dfrac{\alpha _{s}\,\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}\\
-	\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} & \dfrac{-\alpha _{s}\,\xi _{\mathrm{1t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}\\
-	\end{pmatrix}
-	&&=
-	\begin{pmatrix}
-	> 0 & > 0 \\
-	< 0 & < 0  
-	\end{pmatrix}
-	\end{alignat*}
-	Again, recall that we have $c_1 \xi_{2t} - c_2 \xi_{1t} > 0$ and $c_2 \xi_{1s} - c_1 \xi_{2s} > 0$; the rest follows. And finally, we have:
-	\begin{align*}
-	\frac{\partial Z_t}{\partial \alpha} &= 
-	\begin{pmatrix}
-	\dfrac{-\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} \\
-	0
-	\end{pmatrix}
-	=
-	\begin{pmatrix}
-	> 0 \\
-	0 
-	\end{pmatrix} \\
-	\frac{\partial Z_s}{\partial \alpha} &= 
-	\begin{pmatrix}
-	0 \\
-	\dfrac{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}
-	\end{pmatrix}
-	=
-	\begin{pmatrix}
-	0 \\
-	> 0 
-	\end{pmatrix}
-	\end{align*}
-	These are fairly trivial, since $Z_t = \alpha_t / p_t$ (and $Z_s = \alpha_s/ p_s$) and prices are positive. \\
-	\hfill
-\end{proof}
-
-\subsubsection{The Effects of Technical Change}
-
-While our model sets the intertemporal elasticity of substitution for  electricity consumption $\sigma$ to a fixed value, we make no direct assumptions about the elasticity of substitution between different energy technologies.
-Rather, an interesting relationship regarding the substitutability/complementarity between technologies emerges indirectly as a result of intermittency.
-To illustrate this, we provide a numerical example that models the relationship between the use of solar and coal energy.
-But, to start, we must initialize our model with a set of parameter values.
-
-Firstly, we let technology 1 be coal power and technology 2 be solar power; again, period $t$ represents peak hours and period $s$ represents off-peak hours.
-We assume that, holding prices equal, consumers prefer that 60\% of their energy arrive in period $t$ and the remaining 40\% arrive in period $s$.
-Additionally, we normalize the units of the quantities to a MWh basis.
-Hence, $\xi$ represents the percent of capacity utilized in each period; we assume coal can access 100\% of its capacity in both periods, while solar can access 100\% during peak hours and only 10\% during off-peak hours.
-Finally, we set cost parameters, given in  \$ per MWh, equal to LCOE estimates for 2023 from the \citet{EIALCOE}; specifically, we use estimates for "Solar PV" and "Coal with 30\% CCS." In total, we have the following parameters.
-
-\begin{center}
-	\noindent \textbf{Example  1:} $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$. 
-\end{center}
-
-\noindent We begin by exploring the implied elasticity of substitution between these two technologies; for any two commodities $i$ and $j$,  the elasticity of substitution $e_{i,j}$ is given by:
-$$e_{i,j} = \frac{\partial \ln (X_1/ X_2)}{\partial \ln (c_2/c_1)}$$
-where $c$ is their prices.
-This relationship is of particular interest, because many applied and theoretical models studying renewable and fossil energy impose a CES production structure between the two.
-That is, they assume that $e_{renew, fossil}$ is a fixed constant.
-In our model, this is not the case; while directly deriving the value the elasticity of substition $e$ is analytically intractable, we are able to run a numerical simulation to estimate it.
-Moreover, we extend our analysis beyond the Cobb-Douglas case and allow $\sigma$ to vary.\footnote{In the general CES case, we still have $p = \xi^{-1} c$.
-However, for the amount of electricity produced in each period, we instead have $Z^T = \left( \alpha_t/p_t \; \alpha_s /p_s \right) \cdot (1/P)$ where $P$ is the price index defined earlier.
-And, of course, we again have $(\xi^T)^{-1} Z = X$.}
-
-\begin{table}[t]
-	\caption*{\textbf{Figure 1:} Elasticity of Substition Between Solar and Coal} 
-	\label{fig:eosnum}
-	\footnotesize
-	\begin{tabular}{@{\extracolsep{0em}}c}
-		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/example_1_fig_1} \\
-		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } The y-axis of the first plot is equivalent to $\log(X_1/X_2)$ and the x-axis of both plots is equivalent to  $\log(c_2/c_1)$.
-The legend in the upper subplot also applies to the lower subplot.
-These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
-We plot results for various values of the intertemporal elasticity of substition for electricity consumption $\sigma$, which is used in the consumer's CES utility function.
-In order to numerically estimate these relationships, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.5\, c_1, 2 \,c_1)$.
-Then, we obtained estimates of the elasticity of substition by numerically differentiating $\log(X_1/X_2)$ with respect to $-log(c_1, c_2)$.
-That is, the elasticity of substitution between technology 1 and 2 is given by the slope of the upper subplot, and it is graphed in the lower subplot.
-}     \\
-	\end{tabular}
-\end{table}
-
-We plot our numerical estimates of the elasticity of substitution between solar and coal power in \hyperref[fig:eosnum]{Figure 1}.
-These results were generated by computing the optimal quantities of each technology given a range of prices.
-Specifically, we held the price of solar constant and varied the price of coal from 50\% to 200\% of its original parametrized price.
-Then, we numerical differentiated $\log(X_1/X_2)$ with respect to $\log(c_2/c_1)$ to estimate the elasticity of substitution between solar and coal.
-This numerically computed elasticity of substitution $e$ on the production side is shown in the lower subplot.
-We repeat this process with different values of $\sigma$, the elasticity of substitution in the consumer's utility function.
-Recall that $\sigma < 1$ implies that  electricity consumption in different periods are complements, $\sigma = 1$ implies to a Cobb-Douglas relationship, and $\sigma > 1$ implies that electricity consumption in different periods are substitutes.
-Our results strongly suggest that a CES production structure does not accurately model intermittency.
-
-Firstly, note that the elasticity of substitution becomes increasingly non-linear as $\sigma$ rises.
-This is somewhat intuitive; when energy consumption can be substituted across periods, the market is more sensitive to the cost efficiency of technologies and less sensitive to when they produce.
-For instance, suppose we had two technologies that each produced in a different period; if consumers are less willing to substitute consumption across periods, both technologies are likely to be  employed, On the other hand, when consumers are open to substitution (implying large $\sigma$), they will simply consume the majority of their electricity in whichever period it is most cost effective to do so.
-Consequently, price plays bigger role than intermittency as $\sigma$ rises.
-This is further evident in the lower subplots; note that the numerical estimates of  $e$ rise as $\sigma$ rises.
-When consumers are less concerned about when they receive their energy, they are far more open to substituting between coal and solar power.
-
-Second, we find that $e$ approaches a "U" shape as $\sigma$ rises....
-
-...Like \cite{HH} we find an S-shaped adoption curve for renewable energy driven by intermittency.\footnote{\citet{HH} reference \citet{Geroski2000} who provides a survey of the literature on adoption of new technologies.
-He finds that S-shaped adoption curves are often generated by information cascades.
-On the other hand, our model and that of Helm and Mier find S-shaped curves as a result of intermittency slowing down adoption.}
-
-\subsubsection{Externalities}
-
-Often times, a social planner may also be interested in using other policy instruments such as research subsidies.
-In fact, \citet{Ace2012} find that both carbon taxes and research subsidies are necessary to promote long-run structural change in the energy production sector and avert a climate disaster.
-While our model focuses on production on a shorter time scale, we find a similar result -- a combination of both taxes and subsidies may be more effective in promoting a shift towards clean energy.
-
-Firstly, consider a case where a carbon tax is our only policy instrument.
-Additionally, suppose that our first technology produced negative externalities.
-Specifically, the social cost of pollution is given by $S(X) = \gamma X_1$ where $\gamma$ is the monetary damage per unit of $X_1$.
-A social planner is interested in balancing the damages caused by pollution with the surplus of the private sector and the revenue from the tax.
-That is, they aim to solve
-$$\max_{\tau} \; CS + PS - S(X) + \tau X_1$$
-where $\tau$ is the tax on $X_1$, so that its final price is $c_1 + \tau$ and the tax revenue is given by $\tau X_1$.
-The optimal tax is a Pigouvian tax; $\tau$ should be set equal to the marginal social cost of pollution $\gamma$.
-This is an expected, standard solution in most models.
-
-%%% Pigouvian tax proof
-\hfill \\
-\begin{proof} We aim to maximize welfare with respect to the tax $\tau$, hence our first order condition is:
-	\begin{align*}
-	0 &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial S(X)}{\partial \tau} + \frac{\partial \tau X_1}{\partial \tau} \\
-	&=  \left( \underbrace{\frac{\partial CS}{\partial p}  + \frac{\partial PS}{\partial p}}_{= 0} - \frac{ \partial  S(X)}{\partial p} + \frac{\partial \tau X_1}{\partial p} \right) \frac{\partial p}{\partial \tau} \\
-	&=  - \gamma \frac{\partial  X_1}{\partial p} + \tau \frac{\partial  X_1}{\partial p}
-	\end{align*}
-	where the derivatives of producer and consumer surplus are eliminated by the envelope theorem. Therefore, we must have $\tau = \gamma$. \\
-	\hfill
-\end{proof}
-
-Now, suppose that we may also subsidize research which improves the output efficiency of a technology.
-In particular, we let the output efficiency of technology 2 be $(\xi_{2t}, \, \xi_{2s})(1 + \beta)$ where $\beta$ is the percent improvement created by research.
-And, we let the cost of research be given by a convex, differentiable function $G(\beta)$.
-
-\hfill \\
-\begin{proof} First, note that we have:
-	$$X_1 = \dfrac{\alpha _{t}\,(1+\beta) \, \xi_{\mathrm{2s}}}{(c_{1}+ \tau)\,(1+\beta)\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}+\dfrac{\alpha _{s}\,(1+\beta)\,\xi _{\mathrm{2t}}}{(c_{1}+ \tau)\,(1+\beta)\,\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}$$
-
-	We aim to maximize welfare with respect to the tax $\tau$ and the research efficiency modifier $\beta$, hence our first order condition is:
-	\begin{align*}
-	0 	 &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial S(X)}{\partial \tau} + \frac{\partial \tau X_1}{\partial \tau}  - \frac{\partial G(\beta)}{\partial \beta}\\
-	&=  \left( \underbrace{\frac{\partial CS}{\partial p}  + \frac{\partial PS}{\partial p}}_{= 0} - \frac{ \partial  S(X)}{\partial p} + \frac{\partial \tau X_1}{\partial p} - \frac{\partial G(\beta)}{\partial p} \right) \frac{\partial p}{\partial \tau} \\
-	&=  - \gamma \frac{\partial  X_1}{\partial p} + \tau \frac{\partial  X_1}{\partial p} - \frac{\partial G(\beta)}{\partial p} \\
-	\tau &= \gamma + \frac{\partial G(\beta)}{\partial X_1}
-	\end{align*}
-	where the derivatives of producer and consumer surplus are eliminated by the envelope theorem. Equivalently, if we take the derivative of the welfare function with respect to $\beta$, we find that:
-	$$G(\beta) = -\gamma + \frac{\partial \tau}{\partial X_1}$$
-	\hfill
-\end{proof}
-
-\pagebreak
-
-\section{Empirical Methodology}
-
-We aim to empirically estimate the intertemporal elasticity of substition for electricity consumption $\sigma$........
-
-Recall our original first order condition (Equation 3) in the general model:
+The latter two papers estimate $\sigma$ to be around $0.1$ while the paper by \citeauthor{Schwarz}  obtain estimates around $0.04$.
+All three papers study real-time electricity pricing programs for industrial consumers using similar methodologies.
+\citet{Aubin} also provide estimates of the $\sigma$ but using a different methodology; their results find $\sigma < 0$ which is impossible since it would imply upward-sloping demand curves under a CES structure.
+A common flaw in these papers is that they do not account for endogeneity caused by a supply-side response to prices.
+For instance, coal plants are able to modify their generation between days; so, they might respond to an increase in future prices by storing coal until prices rise.
+That is, there may exist intertemporal substitution for electricity generation which would bias $\sigma$ downward unless controlled for.
+This is particularly important, because whether $\sigma$ is closer to 0.1 or 1 can make a significant difference with respect to the practical implications of our model.
+
+Consequently, we provide our own estimates of $\sigma$ estimated on a monthly basis.
+Regarding the time scale, this decision is primarily due to data limitations, since we do  not have access to the proprietary data on real-time pricing experiments which the past literature has used.
+Although we are interested in understanding intertemporal substitution over a shorter time scale (since intermittency plays a larger role in shorter periods), estimates of $\sigma$ on a monthly basis may still be applicable on a smaller time frame.
+For instance, \citet{Schwarz} estimate $\sigma$ on a daily and hourly basis and find fairly close results; similarly, \citet{Herriges} also find no significant difference in their estimates of $\sigma$ for these two intervals.
+That is, while a daily basis is 24 times larger than an hourly basis, the estimates for $\sigma$, suprisingly, do not appear to change.
+Hence, we expect our estimates of $\sigma$ on a monthly basis to not be far from estimates on shorter time scales.
+We now define our econometric methodology in detail.
+
+\subsection{Theory}
+
+Firstly, recall the demand equation (Equation 3) from our general model:
 \begin{align*}
@@
 \ln (Z_{ t, i} / Z_{ s, i}) &= -\sigma \ln (P_{t,i} / P_{s,i}) +  \gamma_{t,i} A_{t,i} + \gamma_{s,i} A_{s,i} + \eta \Delta_{t,s} + u_i \\
-&= -\sigma \ln (P_{t,i} / P_{s,i}) +  \gamma_{t,i} \left( CDD_{t,i} + HDD{t,i} \right) \\
+&= -\sigma \ln (P_{t,i} / P_{s,i}) +  \gamma_{t,i} \left( CDD_{t,i} + HDD_{t,i} \right) \\
 &\qquad + \gamma_{s,i} \left( CDD_{s,i} + HDD{s,i} \right)  + \eta \Delta_{t,s} + u_i
@@
 
-We collect monthly data from the EIA on retail electricity prices and consumption for each state in the US from 2011 to 2018.
-Additionally, also from the EIA, we collect monthly data on the average cost of coal for electricity generation.
-The coal price data set contains a large number of missing values due to privacy reasons; however, we do not expect that these missing values are correlated with the data itself.
-Finally, we collect data on HDDs and CDDs from the NCEP for the same panel.
-Then, we merge these three data sets and trim 1\% of outliers for a total of $826$ observations.
+We collect monthly data from the \cite{EIANetgen} on retail electricity prices and consumption for each state in the US from 2011 to 2018.
+Additionally, also from the EIA, we obtain data on the average cost of coal for electricity generation for each state and month.\footnote{The coal price data set contains a large number of missing values due to privacy concerns; however, we do not expect that these missing values are correlated with the data itself.}
+Finally, we collect data on HDDs and CDDs from the NOAA's \citet{CPC} for the same panel.
+Then, we merge these three data sets and trim 1\% of outliers for a total of $826$ observations for each month and state.
 We use this preliminary data set to construct the data required for our regressions.
@@
 Due to the number of potential combinations and thus observations, we restrict our data set to a random sample of 9000 observations.\footnote{We reran our regressions with several different samples of 9000 and found that our estimated coefficients did not significantly change; hence we believe this sample size is sufficient.}
+All in all, each observation in our regression data set consists the following variables: state ($i$), date 1 ($t$), date 2 ($s$), the log difference in electricity consumption between month 1 and month 2, the log difference in the price of electricity, the log difference in the price of coal, the number of CDDs for each date, the number of HDDs for each date, and the difference (in months) between dates 1 and 2.
 
@@
 
+\section{Discussion}
+\label{sec:Discussion}
+
+\subsubsection{The Relationship between Renewable and Fossil Energy}
+
+To understand the economic implications of these estimates for $\sigma$, we parametrize and numerically evaluate our model in a two-period, two-technology setting.
+In particular, we are concerned with how $\sigma$ affects the substitutability of fossil and renewable energy.
+This is particularly important, because sufficient substitutability between these two technologies is required to transition to greener economy in the future.
+For instance, \citet{Ace2012} argues that, ``When the two
+sectors [clean and dirty energy] are substitutable but not sufficiently so, preventing an environmental disaster requires a permanent policy intervention.
+Finally, when the two sectors are complementary, the only way to stave off a disaster is to stop long-run growth." However, note that, while our model sets the intertemporal elasticity of substitution for  electricity consumption $\sigma$ to a fixed value, we make no direct assumptions about the elasticity of substitution between different energy technologies.
+Rather, an interesting relationship regarding the substitutability/complementarity between technologies emerges indirectly as a result of intermittency.
+To illustrate this, we now proceed with the numerical model.
+
+Firstly, we let technology 1 be coal power and technology 2 be solar power; again, period $t$ represents peak hours and period $s$ represents off-peak hours.
+We assume that, holding prices equal, consumers prefer that 60\% of their energy arrive in period $t$ and the remaining 40\% arrive in period $s$; that is, we have $\alpha_t = 0.6$ and $\alpha_s = 0.4$.
+Additionally, we normalize the units of the quantities to a MWh basis.
+Hence, $\xi$ represents the percent of capacity utilized in each period; we assume coal uses 100\% of its capacity in both periods, while solar can access 100\% during peak hours and only 10\% during the off-peak.
+Finally, we set cost parameters (given in  \$ per MWh)  equal to LCOE estimates for 2023 from the \citet{EIALCOE}; specifically, we use estimates for "Solar PV" and "Coal with 30\% CCS." In total, we have the following parameters.
+
+\begin{center}
+	\noindent \textbf{Example  1:} $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$. 
+\end{center}
+
+\noindent We begin by exploring the implied elasticity of substitution between these two technologies.
+Recall, for any two commodities $i$ and $j$,  the elasticity of substitution $e_{i,j}$ is given by:
+$$e_{i,j} = \frac{\partial \ln (X_1/ X_2)}{\partial \ln (c_2/c_1)}$$
+where $c$ is their prices.
+This relationship is of particular interest, because many applied and theoretical models studying renewable and fossil energy impose a CES production structure between the two.
+That is, they assume that $e$ is a fixed constant different pairs of generation technologies.
+In our model, this is not the case; while directly deriving the equation for $e$ in our model is analytically intractable, we numerically estimate it for varying costs and $\sigma$.
+
+\begin{table}[t]
+	\caption*{\textbf{Figure 1:} Elasticity of Substition Between Solar and Coal} 
+	\label{fig:eosnum}
+	\footnotesize
+	\begin{tabular}{@{\extracolsep{0em}}c}
+		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/example_1_fig_1} \\
+		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } The y-axis of the first plot is equivalent to $\log(X_1/X_2)$ and the x-axis of both plots is equivalent to  $\log(c_2/c_1)$.
+The legend in the upper subplot also applies to the lower subplot.
+These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
+We plot results for various values of the intertemporal elasticity of substition for electricity consumption $\sigma$, which is used in the consumer's CES utility function.
+In order to numerically estimate these relationships, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.5\, c_1, 2 \,c_1)$.
+Then, we obtained estimates of the elasticity of substition by numerically differentiating $\log(X_1/X_2)$ with respect to $-log(c_1, c_2)$.
+That is, the elasticity of substitution between technology 1 and 2 is given by the slope of the upper subplot, and it is graphed in the lower subplot.
+}     \\
+	\end{tabular}
+\end{table}
+
+We plot our numerical estimates of $e_{solar, coal}$, the elasticity of substitution between solar and coal power, in \hyperref[fig:eosnum]{Figure 1}.
+These results were generated by computing the optimal quantities of each technology given a range of prices.
+Specifically, we held the price of solar constant and varied the price of coal from 50\% to 200\% of its original parametrized price.
+Then, we numerical differentiated $\log(X_1/X_2)$ with respect to $\log(c_2/c_1)$ to estimate the elasticity of substitution between solar and coal.
+This numerically computed elasticity of substitution $e$ on the production side is shown in the lower subplot.
+We repeat this process with different values of $\sigma$, the elasticity of substitution in the consumer's utility function.
+Recall that $\sigma < 1$ implies that  electricity consumption in different periods are complements, $\sigma = 1$ implies to a Cobb-Douglas relationship, and $\sigma > 1$ implies that electricity consumption in different periods are substitutes.
+Our results strongly suggest that a CES production structure does not accurately model intermittency.
+
+Firstly, note that the elasticity of substitution becomes increasingly non-linear as $\sigma$ rises.
+This is somewhat intuitive; when energy consumption can be substituted across periods, the market is more sensitive to the cost efficiency of technologies and less sensitive to when they produce.
+For instance, suppose we had two technologies that each produced in a different period; if consumers are less willing to substitute consumption across periods, both technologies are likely to be  employed, On the other hand, when consumers are open to substitution (implying large $\sigma$), they will simply consume the majority of their electricity in whichever period it is most cost effective to do so.
+Consequently, price plays bigger role than intermittency as $\sigma$ rises.
+This is further evident in the lower subplots; note that the numerical estimates of  $e$ rise as $\sigma$ rises.
+When consumers are less concerned about when they receive their energy, they are far more open to substituting between coal and solar power.
+
+Second, we find that $e$ approaches a "U" shape as $\sigma$ rises....
+
+...Like \cite{HH} we find an S-shaped adoption curve for renewable energy driven by intermittency.\footnote{\citet{HH} reference \citet{Geroski2000} who provides a survey of the literature on adoption of new technologies.
+He finds that S-shaped adoption curves are often generated by information cascades.
+On the other hand, our model and that of Helm and Mier find S-shaped curves as a result of intermittency slowing down adoption.}
+
+\subsubsection{Externalities}
+
+Often times, a social planner may also be interested in using other policy instruments such as research subsidies.
+In fact, \citet{Ace2012} find that both carbon taxes and research subsidies are necessary to promote long-run structural change in the energy production sector and avert a climate disaster.
+While our model focuses on production on a shorter time scale, we find a similar result -- a combination of both taxes and subsidies may be more effective in promoting a shift towards clean energy.
+
+Firstly, consider a case where a carbon tax is our only policy instrument.
+Additionally, suppose that our first technology produced negative externalities.
+Specifically, the social cost of pollution is given by $S(X) = \gamma X_1$ where $\gamma$ is the monetary damage per unit of $X_1$.
+A social planner is interested in balancing the damages caused by pollution with the surplus of the private sector and the revenue from the tax.
+That is, they aim to solve
+$$\max_{\tau} \; CS + PS - S(X) + \tau X_1$$
+where $\tau$ is the tax on $X_1$, so that its final price is $c_1 + \tau$ and the tax revenue is given by $\tau X_1$.
+The optimal tax is a Pigouvian tax; $\tau$ should be set equal to the marginal social cost of pollution $\gamma$.
+This is an expected, standard solution in most models.
+
+%%% Pigouvian tax proof
+\hfill \\
+\begin{proof} We aim to maximize welfare with respect to the tax $\tau$, hence our first order condition is:
+	\begin{align*}
+	0 &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial S(X)}{\partial \tau} + \frac{\partial \tau X_1}{\partial \tau} \\
+	&=  \left( \underbrace{\frac{\partial CS}{\partial p}  + \frac{\partial PS}{\partial p}}_{= 0} - \frac{ \partial  S(X)}{\partial p} + \frac{\partial \tau X_1}{\partial p} \right) \frac{\partial p}{\partial \tau} \\
+	&=  - \gamma \frac{\partial  X_1}{\partial p} + \tau \frac{\partial  X_1}{\partial p}
+	\end{align*}
+	where the derivatives of producer and consumer surplus are eliminated by the envelope theorem. Therefore, we must have $\tau = \gamma$. \\
+	\hfill
+\end{proof}
+
+Now, suppose that we may also subsidize research which improves the output efficiency of a technology.
+In particular, we let the output efficiency of technology 2 be $(\xi_{2t}, \, \xi_{2s})(1 + \beta)$ where $\beta$ is the percent improvement created by research.
+And, we let the cost of research be given by a convex, differentiable function $G(\beta)$.
+
+\hfill \\
+\begin{proof} First, note that we have:
+	$$X_1 = \dfrac{\alpha _{t}\,(1+\beta) \, \xi_{\mathrm{2s}}}{(c_{1}+ \tau)\,(1+\beta)\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}+\dfrac{\alpha _{s}\,(1+\beta)\,\xi _{\mathrm{2t}}}{(c_{1}+ \tau)\,(1+\beta)\,\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}$$
+
+	We aim to maximize welfare with respect to the tax $\tau$ and the research efficiency modifier $\beta$, hence our first order condition is:
+	\begin{align*}
+	0 	 &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial S(X)}{\partial \tau} + \frac{\partial \tau X_1}{\partial \tau}  - \frac{\partial G(\beta)}{\partial \beta}\\
+	&=  \left( \underbrace{\frac{\partial CS}{\partial p}  + \frac{\partial PS}{\partial p}}_{= 0} - \frac{ \partial  S(X)}{\partial p} + \frac{\partial \tau X_1}{\partial p} - \frac{\partial G(\beta)}{\partial p} \right) \frac{\partial p}{\partial \tau} \\
+	&=  - \gamma \frac{\partial  X_1}{\partial p} + \tau \frac{\partial  X_1}{\partial p} - \frac{\partial G(\beta)}{\partial p} \\
+	\tau &= \gamma + \frac{\partial G(\beta)}{\partial X_1}
+	\end{align*}
+	where the derivatives of producer and consumer surplus are eliminated by the envelope theorem. Equivalently, if we take the derivative of the welfare function with respect to $\beta$, we find that:
+	$$G(\beta) = -\gamma + \frac{\partial \tau}{\partial X_1}$$
+	\\ \hfill
+\end{proof}
+
+\pagebreak
+
 \section{Conclusion}
@@
 An aim for future research may be to develop a model of clean and dirty energy that incorporates both predictable and stochastic intermittency in a multi-period setting.
+
+\pagebreak
+
+\section{Appendix}
+
+\subsection{Cobb-Douglas Case with Two Periods \& Two Technologies}
+
+In this section, we consider a simpler case of our general model to better understand its implications.
+Firstly, we restrict the utility function to its Cobb-Douglas form which is simply the case where the elasticity of substitution $\sigma = 1$.
+Secondly, we limit the number of periods and technologies to 2.
+And, thirdly, we normalize the prices such that our repesentative consumer's income $I$ is $1$.
+
+\subsubsection{Equilibrium Results}
+
+Firstly, our demand equations simplify to:
+\begin{align}
+Z_t &= \alpha_t / p_t \\
+Z_s &= \alpha_s / p_s
+\end{align}
+where $t$ and $s$ are our two periods. Next, solving for the FOC condition for profit maximization, we have:
+\begin{align*}
+p &=  \xi^{-1} c \\
+p &= \begin{pmatrix}
+-\dfrac{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}  \\[2ex]
+\dfrac{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}} 
+\end{pmatrix} 
+\end{align*}
+And, substituting back into our demand equations, we find the equilibrium quantities for $Z$ and $X$. 
+$$
+Z = \begin{pmatrix}
+\dfrac{\alpha _{t}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{c_{2}\,\xi _{\mathrm{1s}} - c_{1}\,\xi _{\mathrm{2s}}} \\[2ex]
+\dfrac{\alpha _{s}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} 
+\end{pmatrix}
+\implies 
+X = \begin{pmatrix}
+\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}+\dfrac{\alpha _{s}\,\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} \\[2ex] 
+-\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}-\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}
+\end{pmatrix}
+$$
+
+Furthermore, we derive restrictions on the parameters $\xi$ and $c$ by assuming $Z, X > 0$.
+These restrictions are detailed in \hyperref[tab:paramrest]{Table 1}.
+There are two possible sets of symmetrical restrictions.
+The first set, Case 1, assumes that technology 2 is more cost effective in period $t$, while the second set, Case 2, assumes that technology 1 is more cost effective in period $t$.
+If a given set of parameters do not fall into either case, we are left with an edge case where one of the technologies is not used.
+Additionally, these inequalities compare two types of efficiency -- output efficiency and cost efficiency; we define output efficiency as electricity output per unit of input and cost efficiency in terms of electricity output per dollar of input.
+We refer to the last set of restrictions as mixed, because they relate both cost and output efficiency.
+
+\begin{table}[h!]
+	\caption{Parameter Restrictions for $Z, X > 0$} 
+	\label{tab:paramrest}
+	\small
+	\centering
+	\begin{tabular}{@{\extracolsep{2em}}l@{\hspace{-0.5 em}}cc}
+		\\[-4ex]
+		\toprule \\[-2.5ex]
+		& \textbf{Case 1} & \textbf{Case 2 } \\
+		\cmidrule(lr){2-2} \cmidrule(lr){3-3} \\[-1.5ex]
+		\textbf{Cost Efficiency}& $\xi_{2t}/c_2 > \xi_{1t}/c_1$ & $\xi_{2t}/c_2 < \xi_{1t}/c_1 $\\
+		\textbf{Restrictions} & $\xi_{1s}/c_1 > \xi_{2s}/c_2$  & $\xi_{1s}/c_1 < \xi_{2s}/c_2 $ 		\\ [3ex]
+		\textbf{Output Efficiency}& $\xi_{2t}/\xi_{2s} > \xi_{1t}/\xi_{1s}$ & $\xi_{2t}/\xi_{2s} < \xi_{1t}/\xi_{1s}$\\
+		\textbf{Restrictions} & $\xi_{1s}/\xi_{1t} > \xi_{2s}/\xi_{2t} $  & $\xi_{1s}/\xi_{1t} < \xi_{2s}/\xi_{2t}  $ 		\\ [3ex]
+		\multirow{2}{10em}{\textbf{Mixed Efficiency Restrictions}}& $\dfrac{\alpha_s \left(\xi_{1s}/c_1 - \xi_{2s}/c_2\right)}{\alpha_t \left( \xi_{2t}/c_2 - \xi_{1t}/c_1 \right)} > \xi_{2s}/\xi_{2t}$ & $\dfrac{\alpha_s \left(\xi_{1s}/c_1 - \xi_{2s}/c_2\right)}{\alpha_t \left( \xi_{2t}/c_2 - \xi_{1t}/c_1 \right)} < \xi_{2s}/\xi_{2t}$\\
+		& $\dfrac{\alpha_s \left(\xi_{1s}/c_1 - \xi_{2s}/c_2\right)}{\alpha_t \left( \xi_{2t}/c_2 - \xi_{1t}/c_1 \right)} < \xi_{1s}/\xi_{1t} $  & $\dfrac{\alpha_s \left(\xi_{1s}/c_1 - \xi_{2s}/c_2\right)}{\alpha_t \left( \xi_{2t}/c_2 - \xi_{1t}/c_1 \right)} > \xi_{1s}/\xi_{1t} $ 		\\[2ex]
+		\midrule
+		\multicolumn{3}{@{}p{40em}@{}}{\footnotesize \textit{Note: } The inequalities in this table assume that all elements of $\xi$ are greater than $0$.
+The full proof given below provides equivalent restrictions for the zero cases.
+}
+	\end{tabular} 
+\end{table}
+
+\hfill\\
+\begin{proof}
+	We aim to derive conditions on $\xi$ and $c$ required to have positive $Z$ and $X$, so we begin by assuming $X, Z  > 0$.
+Second, since the equations so far are symmetrical, note that there be two symmetrical sets of potential restrictions we must impose on the parameters.
+Thus, we first assume the inequality $c_1 \xi_{2t} - c_2 \xi_{1t} > 0$ to restrict ourselves to one of the two cases.
+This assumption results in the denominator of $Z_s$ being positive.
+Hence, we must also have $\xi_{1s}\xi_{2t} - \xi_{2s}\xi_{1t} > 0 $ for $Z_s > 0$.
+This same term appears in the numerator for $Z_t$, hence its denominator must be positive: $c_2 \xi_{1s} - c_1 \xi_{2s} > 0$.
+Now, rewriting these inequalities, we have:
+	\begin{align*}
+	c_1 \xi_{2t} - c_2 \xi_{1t} > 0 &\implies \xi_{2t}/c_2 > \xi_{1t}/c_1 \\
+	c_2 \xi_{1s} - c_1 \xi_{2s} > 0 &\implies \xi_{1s}/c_1 > \xi_{2s}/c_2 \\
+	\xi_{1s}\xi_{2t} - \xi_{2s}\xi_{1t} > 0 &\implies \xi_{1s}/\xi_{1t} > \xi_{2s}/\xi_{2t} \\
+	&\implies \xi_{1t}/\xi_{1s} < \xi_{2t}/\xi_{2s} 
+	\end{align*}
+	Note that the latter two restrictions can be derived from the former two.
+Additionally, we implicitly assume that we have $\xi > 0$.
+However, this is not necessary assumption, since $\xi$ invertible only requires $\xi_{1t} \xi_{2s} > 0$ or $\xi_{1s} \xi_{2t} > 0$.
+Instead, we may leave the latter two inequalities in the form $ \xi_{1s}\xi_{2t} > \xi_{2s}\xi_{1t}$ which remains valid when values of $\xi$ are equal to $0$.
+Lastly, the mixed efficiency restrictions come from $X > 0$.
+To start, for $X_1$, we have:
+	\begin{align*}
+	X_1 > 0 &\implies (\alpha_t \xi_{2s})(c_1 \xi_2t - c_2\xi_1t) + (\alpha_s \xi_{2t})(c_1 \xi_{2s} - c_2 \xi_{1s}) < 0\\
+	&\implies (\alpha_t \xi_{2s})(c_1 \xi_2t - c_2\xi_1t) < (\alpha_s \xi_{2t})(c_2 \xi_{1s} - c_1 \xi_{2s}) \\
+	&\implies (\xi_{2s}/\xi_{2t}) < (\alpha_s (c_2 \xi_{1s} - c_1 \xi_{2s}))/(\alpha_t(c_1 \xi_{2t} - c_2\xi_{1t})) \\
+	&\implies (\xi_{2s}/\xi_{2t}) < (\alpha_s (\xi_{1s}/c_1 -  \xi_{2s}/c_2))/(\alpha_t(\xi_{2t}/c_2 - \xi_{1t}/c_1)) 
+	\end{align*}
+	Similarly, for $X_2$, note that only the numerators differ; $\xi_{2s}$ is replaced with $-\xi_{1s}$ and $\xi_{2t}$ is replaced with $-\xi_{1t}$. Hence, we have
+	\begin{align*}
+	X_2 > 0 &\implies (\alpha_t \xi_{1s})(c_1 \xi_2t - c_2\xi_1t) + (\alpha_s \xi_{1t})(c_1 \xi_{2s} - c_2 \xi_{1s}) > 0\\
+	&\implies (\xi_{1s}/\xi_{1t}) > (\alpha_s (\xi_{1s}/c_1 -  \xi_{2s}/c_2))/(\alpha_t(\xi_{2t}/c_2 - \xi_{1t}/c_1)) 
+	\end{align*}
+	To double check, note that combining the inequalities from $X_1>0$ and $X_2 > 0$ leads to $\xi_{2s}/\xi_{2t} < \xi_{1s}/\xi_{1t}$.
+This is precisely the earlier result obtained from $Z > 0$.
+Again, it is  important to note that we assume $\xi > 0$ for to simplify the inequalities of $X_1 > 0$ and $X_2 > 0$ .
+Otherwise, we may leave the inequalities in their pre-simplified forms and they are still valid when  $\xi_{1t} \xi_{2s} > 0$ or $\xi_{1s} \xi_{2t} > 0$.
+\\ \hfill
+
+\end{proof}
+
+Let us consider the set of restrictions belonging to Case 1.
+The first inequality, our initial assumption, states that technology 2 is relatively more cost effective in period $t$.
+The second inequality claims technology 1 is relatively more cost effective in period $s$.
+The implications are fairly straightforward; if a technology is to be used, it must have an absolute advantage in cost efficiency in at least one period.
+The third condition states that the relative output efficiency of technology 2 is greater than that of the first technology in period $t$.
+And, the fourth condition makes a symmetrical claim but for the technology 1 and period $s$.
+These latter two restrictions regarding output efficiency enter $Z$ and $X$ through $p$; they're simply a restatement of the invertibility of $\xi$ and can also be derived through the cost efficiency restrictions.
+
+The mixed efficiency restrictions are less intuitive.
+Firstly, note that $\left(\xi_{1s}/c_1 - \xi_{2s}/c_2\right)$ is the difference in cost efficiency for the two technologies in period $s$; this is equivalent to the increase in $Z_s$ caused by shifting a marginal dollar towards technology 1.
+Similarly, the bottom term $\left( \xi_{2t}/c_2 - \xi_{1t}/c_1 \right)$ represents the change in $Z_t$ caused by shifting a marginal dollar towards technology 1.
+Both these terms are then multiplied by the share parameter of the utility function for their respective time periods.
+Furthermore, note that $\alpha_t$ $(\alpha_s)$ is the elasticity of utility with respect to $Z_t$ $(Z_t)$.
+Hence, in total, the mixed efficiency restrictions relate the relative cost efficiencies of each technology with their output efficiency and the demand for energy.
+So, for example, suppose that consumers prefer, \textit{ceteris paribus}, that nearly all their electricity arrive in period $t$.
+This would imply $\alpha_t$ is arbitrarily large which results in the left-hand side of the fraction becoming arbitrarily small.
+This violates the first mixed efficiency restriction but not the second; consequently, use of the first technology, which is less cost effective in period $t$, approaches $0$.
+
+In more practical terms, suppose that our first technology is coal power and the latter is solar power.
+Although coal power is dispatchable, it does not easily ramp up or down within a day; hence, it is reasonable to apply our model where capacities are fixed over time so long as our time frame is sufficiently short.
+Hence, we now assume periods $t$ and $s$ represent the peak and off-peak for a day.
+And, we expect that there is more available solar radiation during peak hours than off-peak hours, since peak hours are usually during the middle of the day.
+This implies that the the output efficiency of solar power is higher in period $t$ due to more available solar radiation.
+Additionally, since the energy output of a unit of coal is independent of time, we know that the output efficiency of coal is constant.
+In total, this implies that we have met the output efficiency restrictions, since we have $\xi_{2t}/\xi_{2s} > \xi_{1t}/\xi_{1s}$.
+Next, we can reasonably assume that coal is more cost effective than solar in the off-peak period when there is less sun; hence, the second cost efficiency restriction is satisfied.
+Then, for there to be an incentive to use solar power, we must satisfy the first cost-efficiency condition; that is, solar needs be cost effective during peak hours otherwise we hit an edge case where no solar is employed.
+And, finally, solar must also satisfy the mixed efficiency condition, which essentially implies that there must be sufficient demand for electricity during period $t$, when solar is more effective, for it to be a feasible technology.
+So, overall, for a technology to be economical, it must meet three conditions: it must the most cost effective technology for a particular period, it must have a comparative advantage in output efficiency in the same period, and there must be sufficient amount of demand in that period.
+
+%\footnote{This same analysis can be further extended to any $n$ technologies.
+However, the number restrictions and different cases to ensure $X , Z > 0$ expands very quickly ($O(n!)$).
+For instance, if we had 3 technologies and 3 periods, we must first assume each technology is more cost effective than the other two in a unique period; this adds 3*2 restrictions.
+Then, we must make the output efficiency restrictions comparing each pair of technologies for each pair of periods.}
+
+\subsubsection{Comparative Statics}
+
+The comparative statics are similarly intuitive.
+The equilibrium quantity of a technology is increasing with its output efficiency and decreasing with its cost per unit.
+Additionally, the equilibrium quantities for a particular technology move in the opposite direction with respect to the output efficiency and cost of the other technologies.
+For a practical example, consider again coal and solar power from before.
+An increase in the output efficiency of solar or a decrease in solar power's cost will reduce the optimal quantity of coal power.
+Likewise, as coal power's efficiency improves, it's adoption rises.
+To find the effects of $\alpha$ on $X$, we must assume one of the cases of restrictions shown in \hyperref[tab:paramrest]{Table 1}.
+So, again, let us assume Case 1 is true; this implies that $X_2$ is the most cost effective technology in period $t$ and likewise for $X_1$ in period $s$.
+Firstly, note that $\alpha$ determines demand for electricity in a period.
+Hence, when $\alpha_t$ rises, we see the optimal level of $X_2$ rise as well; likewise, $X_1$ rises with $\alpha_s$.
+In short, the optimal quantity of a technology rises linearly with the demand for electricity in the period it specializes in.
+Moreover, these relationships are reversed with respect to demand in each technology's suboptimal period.
+So, for example, we would expect the use of solar energy to rise when demand for electricity during peak hours rises, and it would fall when demand for energy in the off-peak rises.
+On the other hand, use coal power would rise with off-peak demand and fall with peak demand.
+This concept carries through for the comparative statics of $Z$.
+When the output efficiency of technology 1 rises or its cost falls, we see output $Z_s$ rise and output $Z_t$ fall.
+This is because technology 1 is optimal in period $s$ given the Case 1 restrictions.
+Likewise, we see symmetrical results for the output with respect to the cost and output efficiency of technology 2; improvements in the efficiency of $X_2$ result in greater output in $Z_t$ and smaller output in $Z_s$.
+
+\hfill \\
+\begin{proof}
+	We begin by deriving the comparative statics of the cost and efficiency parameters with respect to $X$.   Firstly, we take derivatives with respect to the cost vectors:
+	\begin{align*}
+	\frac{\partial X_1}{\partial c} &= 
+	\begin{pmatrix}
+	\dfrac{-\alpha _{t}\,{\xi _{\mathrm{2s}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}-\dfrac{\alpha _{s}\,{\xi _{\mathrm{2t}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}<0 \\
+	\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}+\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}>0
+	\end{pmatrix}
+	=
+	\begin{pmatrix}
+	< 0 \\
+	> 0 
+	\end{pmatrix} \\
+	\frac{\partial X_2}{\partial c} &= 
+	\begin{pmatrix}
+	\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}+\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}>0 \\
+	\dfrac{-\alpha _{t}\,{\xi _{\mathrm{1s}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}-\dfrac{\alpha _{s}\,{\xi _{\mathrm{1t}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}<0
+	\end{pmatrix}
+	=
+	\begin{pmatrix}
+	> 0 \\
+	< 0 
+	\end{pmatrix}
+	\end{align*}
+	The first and second terms of $\partial X_1 / \partial c_1$ are clearly both negative independent of the restrictions on the parameters.
+Similarly, all terms of  $\partial X_1 / \partial c_2$ are positive independent of any restrictions.
+Since the structure of this problem is symmetrical with respect to $X_1$ and $X_2$, the same comparative statics apply but in reverse for $X_1$.
+Next, we derive comparative statics for each element of $\xi$.
+	\begin{alignat*}{2}
+	\frac{\partial X_1}{\partial \xi} &= 
+	\begin{pmatrix}
+	\dfrac{\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}>0 & \dfrac{\alpha _{t}\,c_{2}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}>0 \\
+	\dfrac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}<0 & \dfrac{-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}<0 \\
+	\end{pmatrix}
+	&&=
+	\begin{pmatrix}
+	> 0 & > 0  \\
+	< 0 & < 0
+	\end{pmatrix} \\
+	\frac{\partial X_2}{\partial \xi} &= 
+	\begin{pmatrix}
+	\dfrac{-\alpha _{s}\,c_{1}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} <0& \dfrac{-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} <0\\
+	\dfrac{\alpha _{s}\,c_{1}\,\xi _{\mathrm{1t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}>0& \dfrac{\alpha _{t}\,c_{1}\,\xi _{\mathrm{1s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} >0\\
+	\end{pmatrix}
+	&&=
+	\begin{pmatrix}
+	< 0 & < 0 \\
+	> 0 & > 0  
+	\end{pmatrix}
+	\end{alignat*}
+	Again, the signs are fairly straightforward.
+The optimal quantity of $X_1$ increases with its output efficiency in both periods; however, it decreases with the output efficiency of $X_2$ in both periods.
+Similarly, symmetrical results are shown for $X_2$.
+Next, we study the effects of $\alpha$ on $X$; this requires us to place some restrictions on the parameters, so we use those belonging to Case 1 in \hyperref[tab:paramrest]{Table 1}.
+With $\alpha \equiv \left( \alpha_t \;\; \alpha_s \right)^T$,
+	\begin{align*}
+	\frac{\partial X_1}{\partial \alpha} &= 
+	\begin{pmatrix}
+	\dfrac{\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}<0 \\
+	\dfrac{\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}>0
+	\end{pmatrix}
+	=
+	\begin{pmatrix}
+	< 0 \\
+	> 0 
+	\end{pmatrix} \\
+	\frac{\partial X_2}{\partial \alpha} &= 
+	\begin{pmatrix}
+	\dfrac{-\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}>0 \\
+	\dfrac{-\xi _{\mathrm{1t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}<0
+	\end{pmatrix}
+	=
+	\begin{pmatrix}
+	> 0 \\
+	< 0 
+	\end{pmatrix}
+	\end{align*}
+	Note that our restrictions imply that $c_1 \xi_{2t} - c_2 \xi_{1t} > 0$ and $c_2 \xi_{1s} - c_1 \xi_{2s} > 0$.
+From here, the intuition is clear; we assume that $X_2$ is more cost efficient in period $t$, so increases in demand during period $t$ (caused by increases in $\alpha_t$) will increase the optimal quantity of $X_2$.
+And, the same applies to $X_1$ with respect to period $s$ and $\alpha_s$.
+Again, due to symmetry, the statics are reversed when the technologies are flipped.
+Similarly, the signs would also be flipped if we used the restrictions given by Case 2 instead.
+
+	Next, we derive the comparative statics for $Z$. 
+	\begin{alignat*}{2}
+	\frac{\partial Z_t}{\partial c} &= 
+	\begin{pmatrix}
+	\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}>0\\
+	\dfrac{-\alpha _{t}\,\xi _{\mathrm{1s}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}<0
+	\end{pmatrix}
+	&=
+	\begin{pmatrix}
+	> 0 \\
+	< 0 
+	\end{pmatrix} \\
+	\frac{\partial Z_s}{\partial c} &= 
+	\begin{pmatrix}
+	\dfrac{-\alpha _{s}\,\xi _{\mathrm{2t}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} <0\\
+	\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} >0
+	\end{pmatrix}
+	&=
+	\begin{pmatrix}
+	< 0 \\
+	> 0 
+	\end{pmatrix}
+	\end{alignat*}
+	From our restrictions, we have $\xi_{1s}\xi_{2t} > \xi_{2s}\xi_{1t}$, and all the results above follow from this. 
+	\begin{alignat*}{2}
+	\frac{\partial Z_t}{\partial \xi} &= 
+	\begin{pmatrix}
+	\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} < 0& \dfrac{-\alpha _{t}\,\xi _{\mathrm{2s}}\,\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} <0 \\
+	\dfrac{-\alpha _{t}\,\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} >0& \dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} >0\\
+	\end{pmatrix}
+	&&=
+	\begin{pmatrix}
+	< 0 & < 0  \\
+	> 0 & > 0
+	\end{pmatrix} \\
+	\frac{\partial Z_s}{\partial \xi} &= 
+	\begin{pmatrix}
+	\dfrac{-\alpha _{s}\,\xi _{\mathrm{2t}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}> 0& \dfrac{\alpha _{s}\,\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} > 0\\
+	\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} < 0& \dfrac{-\alpha _{s}\,\xi _{\mathrm{1t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} <0\\
+	\end{pmatrix}
+	&&=
+	\begin{pmatrix}
+	> 0 & > 0 \\
+	< 0 & < 0  
+	\end{pmatrix}
+	\end{alignat*}
+	Again, recall that we have $c_1 \xi_{2t} - c_2 \xi_{1t} > 0$ and $c_2 \xi_{1s} - c_1 \xi_{2s} > 0$; the rest follows. And finally, we have:
+	\begin{align*}
+	\frac{\partial Z_t}{\partial \alpha} &= 
+	\begin{pmatrix}
+	\dfrac{-\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} \\
+	0
+	\end{pmatrix}
+	=
+	\begin{pmatrix}
+	> 0 \\
+	0 
+	\end{pmatrix} \\
+	\frac{\partial Z_s}{\partial \alpha}> 0 &= 
+	\begin{pmatrix}
+	0 \\
+	\dfrac{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} > 0
+	\end{pmatrix}
+	=
+	\begin{pmatrix}
+	0 \\
+	> 0 
+	\end{pmatrix}
+	\end{align*}
+	These are fairly trivial, since $Z_t = \alpha_t / p_t$ (and $Z_s = \alpha_s/ p_s$) and prices are positive. \\
+	\hfill
+\end{proof}
 
@@
 	Acemoglu, D., Aghion, P., Bursztyn, L., \& Hemous, D. (2012). The Environment and Directed Technical Change. American Economic Review, 102(1), 131–166. https://doi.org/10.1257/aer.102.1.131
+
 	\bibitem[Ambec and Crampes (2012)]{AC2012}
 	Ambec, S., \& Crampes, C. (2012). Electricity provision with intermittent sources of energy. Resource and Energy Economics, 34(3), 319–336. https://doi.org/10.1016/j.reseneeco.2012.01.001
+
+	\bibitem[Aubin et al.(1995)]{Aubin}
+	Aubin, C., Fougere, D., Husson, E., \& Ivaldi, M.
+(1995).
+Real-time pricing of electricity for residential customers: Econometric analysis of an experiment.
+Journal Of Applied Econometrics, 10, S171–S191.
 
@@
 
+	\bibitem[Deryugina and Mackay(2017)]{Deryugina}
+	Deryugina, T., Mackay, A., \& Reif, J. (2017). The Long-Run Dynamics of Electricity Demand: Evidence from Municipal Aggregation. NBER Working Paper Series. https://doi.org/10.3386/w23483
+
 	\bibitem[EIA(2019a)]{EIANetgen}
@@
 https://www.eia.gov/outlooks/aeo/pdf/electricity\_generation.pdf
+
+	\bibitem[Fan and Hyndman(2011)]{Fan}
+	Fan, S., \& Hyndman, R. (2011). The price elasticity of electricity demand in South Australia. Energy Policy, 39(6), 3709–3719. https://doi.org/10.1016/j.enpol.2011.03.080
 
@@
 
+	\bibitem[Herriges et al.(1993)]{Herriges}
+	Herriges, J., Baladi, S., Caves, D., \& Neenan, B.
+(1993).
+The Response of Industrial Customers to Electric Rates Based Upon Dynamic Marginal Costs.
+The Review of Economics and Statistics, 75(3), 446.
+https://doi.org/10.2307/2109458
+
 	\bibitem[Joskow(2011)]{Joskow2011}
 	Joskow, P. (2011). Comparing the Costs of Intermittent and Dispatchable Electricity Generating Technologies. American Economic Review, 101(3), 238–241. https://doi.org/10.1257/aer.101.3.238
+
+	\bibitem[King and Shatrawka(2011)]{KS1994}
+	King, Kathleen, and Peter Shatrawka (1994). "Customer Response to a Permanent Time- Varying
+	Pricing Program in the United Kingdom." Laurits R. Christensen Associates, Madison,
+	Wisconsin.
 
@@
 	Musgens, F., \& Neuhoff, K. (2006). Modelling Dynamic Constraints in Electricity Markets and the Costs of Uncertain Wind Output. Faculty of Economics.
+
+	\bibitem[Climate Prediction Center(2019)]{CPC}
+	Climate Prediction Center (2019). Degree Days Statistics. National Oceanic and Atmospheric Administration. https://www.cpc.ncep.noaa.gov/products/analysis\_monitoring/cdus/degree\_days/
 
@@
 
+	\bibitem[Reiss and White(2005)]{Reiss}
+	Reiss, P., \& White, M. (2005). Household Electricity Demand, Revisited. The Review of Economic Studies, 72(252), 853. Retrieved from http://search.proquest.com/docview/204335314/
+
 	\bibitem[Schwarz et al.(2002)]{Schwarz}
@@
 (2002).
-INDUSTRIAL RESPONSE TO ELECTRICITY REAL‐TIME PRICES: SHORT RUN AND LONG RUN.
+Industrial response to electricity real-time prices: short run and long run.
 Economic Inquiry, 40(4), 597–610.
@@
 
+	\bibitem[Zhou and Teng(2013)]{Zhou}
+	Zhou, S. \& Teng, F., (2013). Estimation of urban residential electricity demand in China using household survey data.(Statistical data). Energy Policy, 61, 394–402.
+
 	\bibitem[Staiger and Stock(1997)]{SS1997} 
@@
 
-	\bibitem[Warkins and Knight(1922)]{Knight}
-	Watkins, G., \& Knight, F. (1922). Knight’s Risk, Uncertainty and Profit. The Quarterly Journal of Economics, 36(4), 682–690. https://doi.org/10.2307/1884757
+	\bibitem[Wolak and Patrick(2001)]{Wolak}
+	Wolak, F., \& Patrick, R.
+(2001).
+The Impact of Market Rules and Market Structure on the Price Determination Process in the England and Wales Electricity Market.
+NBER Working Paper Series.
+https://doi.org/10.3386/w8248
+
+	\bibitem[Woo et al.(1996)]{Woo}
+	Woo, C., Chow, P., \& Horowitz, I. (1996). Optional real-time pricing of electricity for industrial firms. Pacific Economic Review, 1(1), 79–92. https://doi.org/10.1111/j.1468-0106.1996.tb00175.x
+
+	\bibitem[Zarnikau(1990)]{Zarnikau}
+	Zarnikau, J. (1990). Customer Responsiveness to Real-Time Pricing of Electricity. The Energy Journal, 11(4), 99. https://doi.org/10.5547/ISSN0195-6574-EJ-Vol11-No4-6
+
+%	\bibitem[Warkins and Knight(1922)]{Knight}
+%	Watkins, G., \& Knight, F. (1922). Knight’s Risk, Uncertainty and Profit. The Quarterly Journal of Economics, 36(4), 682–690. https://doi.org/10.2307/1884757
 

### 2019-04-28 code/matlab/simulation_april/sim_adoption_curve.m
Update matlab simulation code
- add script for adoption surfaces (not used)
- add script for adoption curves
- add figures for adoption curves
- rename figure for elasticity effects
- update elasticity simulation script

@@ -1,0 +1,195 @@
+%% Adoption with Respect to Price of Solar Sim
+
+close all; clear; clc;
+
+% Simulation params
+n = 5000;
+cost_multiplier = linspace(0.01,2,n);
+sigma_range = [0.05, 0.25, 0.5, 1, 1.5];
+m = length(sigma_range);
+
+% Exogenous params
+c_1 = 104.3;
+c_2 = 50;
+alpha = [0.6, 0.4];
+xi_1  = [1,   1];
+xi_2  = [1, 0.1];
+budget = 1;
+
+
+figure('Renderer', 'painters', 'Position', [100 100 900 600])
+hold on;
+
+for j = 1:m
+    
+    sigma = sigma_range(j);
+    results = zeros(n,2); 
+
+    for i = 1:n
+
+
+        phi   = (sigma - 1)/sigma;
+        x_1_cost_param = c_1;
+        x_2_cost_param = c_2*cost_multiplier(i);
+
+        % Prices
+        xi_mat   = [xi_1; xi_2];
+        cost_mat = [x_1_cost_param; x_2_cost_param];
+        prices   = xi_mat\cost_mat;
+
+        if any(prices<0)
+            continue
+        end
+
+        % Price Index
+        P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
+
+        % Quantities
+        if sigma ~= 1
+            Y = ((alpha'./prices).^(sigma)) * (budget/P);
+        else 
+            Y = (alpha'./prices);
+        end 
+           
+        X = (xi_mat')\Y;
+
+        results(i,:) = X';
+
+    end    
+
+    output = [];
+    output(1,:) = results(:,1);
+    output(2,:) = results(:,2);
+    output(3,:) = 1-cost_multiplier;
+    
+    % subset to positive quantities
+    ind = ~any(output(1:2,:) <= 0);
+    output = output(:,ind);
+
+    % adoption curve for solar
+    hold on;
+    plot(output(3,:)*100, ...
+         100*output(2,:)./(output(1,:) + output(2,:)), ...
+        'LineWidth', 1);
+    
+end
+
+%% Plot formatting
+
+% Add horizontal line at 1
+
+% Format subplot 1
+legend('0.05', '0.25', '0.5', '1', '1.5')
+xlabel('Percent Decrease in the Cost of Solar')
[…]

### 2019-04-28 code/matlab/simulation_april/sim_adoption_surface.m

@@ -1,0 +1,67 @@
+%% Adoption Curve with Respect to Both Prices Sim
+
+close all; clear; clc;
+
+% Simulation params
+[c_1_range, c_2_range] = meshgrid(0.5:0.05:2, 0.5:0.05:2);
+
+% Exogenous params
+c_1 = 104.3;
+c_2 = 50;
+alpha = [0.6, 0.4];
+xi_1  = [1,   1];
+xi_2  = [1, 0.1];
+budget = 1;
+sigma = 0.5;
+
+
+figure('Renderer', 'painters', 'Position', [100 100 900 600])
+hold on;
+
+results = ones(length(c_1_range), length(c_1_range)); 
+
+for i = 1:length(results)
+    for j = 1:length(results)
+
+        phi   = (sigma - 1)/sigma;
+        x_1_cost_param = c_1*c_1_range(i,j);
+        x_2_cost_param = c_2*c_2_range(i,j);
+
+        % Prices
+        xi_mat   = [xi_1; xi_2];
+        cost_mat = [x_1_cost_param; x_2_cost_param];
+        prices   = xi_mat\cost_mat;
+
+        % Price Index
+        P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
+
+        % Quantities
+        if sigma ~= 1
+            Y = ((alpha'./prices).^(sigma)) * (budget/P);
+        else 
+            Y = (alpha'./prices);
+        end 
+
+        X = (xi_mat')\Y;
+
+        if all(X > 0)
+            results(i,j) = X(2)/(X(1) + X(2));
+        else
+            results(i,j) = nan;
+        end
+
+    end    
+end
+
+surf(100*(c_1_range-1), 100*(c_2_range-1), results)
+
+%% Plot formatting
+
+xlabel('Percent Change in the Cost of Coal')
+ylabel('Percent Change in the Cost of Solar')
+zlabel('Solar Capacity as a Fraction of All Capacity')
+xtickformat('percentage')
+ytickformat('percentage')
+
+
+

### 2019-04-28 code/matlab/simulation_april/sim_elasticity.m

@@ -1,11 +1,11 @@
-%% Price (Cost) Elasticity Sim
+%% Elasticity of Substitution Sim
 
 close all; clear; clc;
 
 % Simulation params
 n = 500;
 cost_multiplier = linspace(0.5,2,n);
-sigma_range = [0.01, 0.25, 0.5, 1, 1.5];
+sigma_range = [0.05, 0.25, 0.5, 1, 1.5];
 m = length(sigma_range);
 
 % Exogenous params
@@ -85,7 +85,7 @@ end
 
 % Format subplot 1
 subplot(2,1,1);
-legend('0.01', '0.25', '0.5', '1', '1.5')
+legend('0.05', '0.25', '0.5', '1', '1.5')
 xlabel('Negative Log Difference in Prices')
 ylabel('Log Difference in Quantities')
 xlim([-1.5, -0.2])
@@ -108,5 +108,5 @@ e_1_line = plot([-1.4, -0.2], [1,1], 'LineStyle', '--', 'Color', 'k');
 legend([e_1_line], ' e = 1');
 
 % Save figure
-print(gcf,'example_1_fig_1.png','-dpng','-r300')
+print(gcf,'fig_elasticity.png','-dpng','-r300')
 

### 2019-04-28 documents/draft.tex
Update draft
- add further discussion of results
- update data section, mentioning deflation
- add figures for discussion

@@
 
-\section{Data}
+\subsection{Data}
 
 We collect monthly data from the \cite{EIANetgen} on retail electricity prices and consumption for each state in the US from 2011 to 2018.
-Additionally, also from the EIA, we obtain data on the average cost of coal for electricity generation for each state and month.\footnote{The coal price data set contains a large number of missing values due to privacy concerns; however, we do not expect that these missing values are correlated with the data itself.}
+Additionally, also from the EIA, we obtain data on the average cost of coal for electricity generation for each state and month.\footnote{The coal price data set contains a large number of missing values due to privacy concerns; however, we do not expect that these missing values are correlated with the data itself.} We deflated both electricity and coal prices over time using the PCECP Index provided by the  \cite{USBEA}.
 Finally, we collect data on HDDs and CDDs from the NOAA's \citet{CPC} for the same panel.
@@
 
-\begin{table}[!htbp] \centering 
+\begin{table}[!t] \centering 
 	\caption{OLS Regression Results}
@@
 
-\begin{table}[!htbp] \centering 
+\begin{table}[!t] \centering 
 	\caption{IV (2SLS) Regression Results}
@@
 
-\begin{table}[!htbp] \centering 
+\begin{table}[!t] \centering 
 	\caption{Partially Linear IV Regression Results}
@@
 \pagebreak
+\clearpage
 
@@
 
-\subsubsection{The Relationship between Renewable and Fossil Energy}
+\subsubsection{The Elasticity of Substitution between Renewable and Fossil Energy}
 
@@
 Hence, $\xi$ represents the percent of capacity utilized in each period; we assume coal uses 100\% of its capacity in both periods, while solar can access 100\% during peak hours and only 10\% during the off-peak.
-Finally, we set cost parameters (given in  \$ per MWh)  equal to LCOE estimates for 2023 from the \citet{EIALCOE}; specifically, we use estimates for "Solar PV" and "Coal with 30\% CCS." In total, we have the following parameters.
+Finally, we set cost parameters (given in  \$ per MWh)  equal to LCOE estimates for 2023 from the \citet{EIALCOE}; specifically, we use estimates for "Solar PV" and "Coal with 30\% CCS" from Table 1b.
+In total, we have the following parameters.
 
@@
 \begin{table}[t]
-	\caption*{\textbf{Figure 1:} Elasticity of Substition Between Solar and Coal} 
+	\caption*{\textbf{Figure 1:} The Elasticity of Substition Between Solar and Coal} 
 	\label{fig:eosnum}
 	\footnotesize
+	\vspace{-1em}
 	\begin{tabular}{@{\extracolsep{0em}}c}
-		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/example_1_fig_1} \\
+		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_elasticity} \\
 		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } The y-axis of the first plot is equivalent to $\log(X_1/X_2)$ and the x-axis of both plots is equivalent to  $\log(c_2/c_1)$.
@@
 These results were generated by computing the optimal quantities of each technology given a range of prices.
-Specifically, we held the price of solar constant and varied the price of coal from 50\% to 200\% of its original parametrized price.
-Then, we numerical differentiated $\log(X_1/X_2)$ with respect to $\log(c_2/c_1)$ to estimate the elasticity of substitution between solar and coal.
-This numerically computed elasticity of substitution $e$ on the production side is shown in the lower subplot.
+Specifically, we held the price of solar capacity constant and varied the price of coal capacity from 50\% to 200\% of its original parametrized price.
+Then, we numerical differentiated $\log(X_1/X_2)$ with respect to $\log(c_2/c_1)$ to estimate the elasticity of substitution between solar and coal.\footnote{Instead, we could have generated variation in $\log(c_2/c_1)$ data by holding solar at a constant price and varying the price of coal capacity.
+However, this does not change the results.} This numerically computed elasticity of substitution between solar and coal power, $e_{solar,coal}$, is shown in the lower subplot.
 We repeat this process with different values of $\sigma$, the elasticity of substitution in the consumer's utility function.
-Recall that $\sigma < 1$ implies that  electricity consumption in different periods are complements, $\sigma = 1$ implies to a Cobb-Douglas relationship, and $\sigma > 1$ implies that electricity consumption in different periods are substitutes.
-Our results strongly suggest that a CES production structure does not accurately model intermittency.
-
-Firstly, note that the elasticity of substitution becomes increasingly non-linear as $\sigma$ rises.
+Finally, we drop all observations of our numerical simulation that correspond to edge cases.
+
+Our results show that $e$ is clearly non-linear, hence assuming a CES production structure between clean and dirty energy is not an accurate assumption.
+Furthermore, the relationship between log quantities and log prices becomes increasingly non-linear as $\sigma$ rises.
 This is somewhat intuitive; when energy consumption can be substituted across periods, the market is more sensitive to the cost efficiency of technologies and less sensitive to when they produce.
-For instance, suppose we had two technologies that each produced in a different period; if consumers are less willing to substitute consumption across periods, both technologies are likely to be  employed, On the other hand, when consumers are open to substitution (implying large $\sigma$), they will simply consume the majority of their electricity in whichever period it is most cost effective to do so.
+For instance, suppose we had two technologies that each produced in a different period; if consumers are less willing to substitute consumption across periods, both technologies are likely to be  employed, On the other hand, when consumers are open to substitution,they will simply consume the majority of their electricity in whichever period it is most cost effective to do so.
 Consequently, price plays bigger role than intermittency as $\sigma$ rises.
-This is further evident in the lower subplots; note that the numerical estimates of  $e$ rise as $\sigma$ rises.
-When consumers are less concerned about when they receive their energy, they are far more open to substituting between coal and solar power.
-
-Second, we find that $e$ approaches a "U" shape as $\sigma$ rises....
-
-...Like \cite{HH} we find an S-shaped adoption curve for renewable energy driven by intermittency.\footnote{\citet{HH} reference \citet{Geroski2000} who provides a survey of the literature on adoption of new technologies.
-He finds that S-shaped adoption curves are often generated by information cascades.
-On the other hand, our model and that of Helm and Mier find S-shaped curves as a result of intermittency slowing down adoption.}
+This is further evident in the lower subplots; note that the numerical estimates of  $e$ rise and become more u-shaped as $\sigma$ rises.\footnote{Recall that $\sigma < 1$ implies that  electricity consumption in different periods are complements, $\sigma = 1$ implies to a Cobb-Douglas relationship, and $\sigma > 1$ implies that electricity consumption in different periods are substitutes.}  When consumers are less concerned about when they receive their energy, they are far more open to substituting between coal and solar power.
+On the other hand, for lower values of $\sigma$, we find that the substitutability of coal and solar power diminishes as solar becomes progressively cheaper.
+To clarify, note that the x-axis of the lower subplot is $\log(c_2/c_1)$; since $c_2$ is the price of solar, cheaper solar energy implies lower values of $\log(c_2/c_1)$ which corresponds to lower values of $e$.
+This can be explained by $\sigma < 1$ implying a complementary relationship between electricity consumption over time.
+Consumers with such preferences will be relatively less sensitive to prices and more interested in spreading their electricity consumption across each period.
+Thus, solar is less substitutable for coal in this case, because its intermittency conflicts with consumers wanting to smooth their electricity consumption over time.
+
+Additionally, note that we assumed earlier that the estimates of $\sigma$ on a monthly basis would be fairly close to those on a daily or hourly basis.
+But, our results showed estimates of $\hat{\sigma} \approx 0.5$ which differs from the literatures' estimates which fall between $0.01$ and $0.25$.
+Does this impact our numerical results?
+Alternatively, if our estimates were closer to past estimates, would there be significantly different economic implications?
+Based on our numerical model, the answer seems to be no.
+That is, the relationship between $e$ and $\log(c_2/c_1)$ in \hyperref[fig:eosnum]{Figure 1} does not significantly differ when varying $\sigma$ in $\{0.05, 0.25, 0.5\}$.
+Hence, even if our assumption is incorrect or past estimates are biased, our model's results do not significantly differ within this range of estimates for $\sigma$.
+
+\subsubsection{Technical Change and the Adoption of Renewable Energy}
+
+ \begin{table}[!t]
+ 	\caption*{\textbf{Figure 2:} The Market Share of Solar Energy versus Own Price} 
+ 	\label{fig:adoptc2}
+ 	\footnotesize
+ 	\vspace{-1em}
+ 	\begin{tabular}{@{\extracolsep{0em}}c}
+ 		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_adoption_c2} \\
+ 		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
+To generate these values, we first vary the price of solar relative to its original parametrized cost $c_2$.
+Then, we find the optimal capacity of solar as a fraction of the total optimal capacity of all technologies (solar and coal) for each set of prices.
+And, finally, we repeat this process and plot the results for different values of $\sigma$, the consumer's intertemporal elasticity of electricity consumption.
+}     \\
+ 	\end{tabular}
+ \end{table}
+
+ \begin{table}[!t]
+ 	\caption*{\textbf{Figure 3:} The Market Share of Solar Energy versus the Price of Coal} 
+ 	\label{fig:adoptc1}
+ 	\footnotesize
+ 	\vspace{-1em}
+ 	\begin{tabular}{@{\extracolsep{0em}}c}
+ 		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_adoption_c1} \\
+ 		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
+To generate these values, we first vary the price of coal relative to its original parametrized cost $c_1$.
+Then, we find the optimal capacity of solar as a fraction of the total optimal capacity of all technologies (solar and coal) for each set of prices.
+And, finally, we repeat this process and plot the results for different values of $\sigma$, the consumer's intertemporal elasticity of electricity consumption.
+}     \\
+ 	\end{tabular}
+ \end{table}
+
+We now do a similar exercise but instead study the adoption (or market share/diffusion) of renewables.
+Specifically, using the same technologies, solar and coal, along with the same parameters, we study how the cost of each technology affects the market share of solar.
+First, we study the market share of solar with respect to its own price.
+Our results are shown in \hyperref[fig:adoptc2]{Figure 2}.
+We find that, for values of $\sigma \geq 1$, the market share of solar energy appears to be convex with respect to increases in cost efficiency.
+This relationship somewhat persists through to $\sigma = 0.5$; here, the market share appears to follow an inverted S-shape that starts concave and becomes convex.
+But, overall, the curve for $\sigma = 0.5$ seems almost linear.
+On the other hand, when $\sigma$ is sufficiently low, this relationship is more consistently convex.
+Interestingly, these dynamics with respect to $\sigma$ seem to be a product of intermittency.
+That is, as we discussed earlier, when consumers have high $\sigma$, they are more willing to shift their electricity consumption and are thus relatively more sensitive to chances in price.
+Consequently, the rate of adoption (the slope of the market share curve) is larger for higher $\sigma$ around moderate changes in price; however, this relationship between adoption and $\sigma$ changes as price falls more drastically.
+To understand why, see \hyperref[fig:adoptc1]{Figure 3}, where we compare the market share of solar with respect to the price of coal.
+We find that solar market share is concave for all values of $\sigma$; consequently, the market share of coal must be convex with respect to its own price.
+Hence, it seems that market share with respect to own price is convex for non-intermittent technologies, but may be concave for intermittent ones.
+Furthermore, the importance of intermittency in this context is driven by $\sigma$; that is, intermittency plays a bigger role in determining market share when consumers prefer, on the margin, smoother electricity consumption than electricity cost savings.
+This result directly contrasts with \cite{HH} who find S-shaped market diffusion for renewable energy; this shape is a result of their representation of intermittency as unpredictable, stochastic variability in the output of renewable energy.
+On the other hand, because we represent intermittency in a different way, our market share curves differ significantly.
+In any case, these market share curves have important implications in the context of promoting renewable energy adoption.
 
 \subsubsection{Externalities}
+
+That is, suppose we are interested in
+
+One way to interpret this is in the context of a tax and subsidy.
+Taxing coal at increasing rates has diminishing returns on promoting the market share of solar energy.
+However, for $\sigma \leq 0.5$, subsidizing solar energy can have linear or increasing returns with respect to its market share.
+Also,
 
@@
 
+	\bibitem[Climate Prediction Center(2019)]{CPC}
+	Climate Prediction Center (2019). Degree Days Statistics. National Oceanic and Atmospheric Administration. https://www.cpc.ncep.noaa.gov/products/analysis\_monitoring/cdus/degree\_days/
+
 	\bibitem[Delarue et al.(2010)]{Delarue}
@@
 	Musgens, F., \& Neuhoff, K. (2006). Modelling Dynamic Constraints in Electricity Markets and the Costs of Uncertain Wind Output. Faculty of Economics.
-
-	\bibitem[Climate Prediction Center(2019)]{CPC}
-	Climate Prediction Center (2019). Degree Days Statistics. National Oceanic and Atmospheric Administration. https://www.cpc.ncep.noaa.gov/products/analysis\_monitoring/cdus/degree\_days/
 
@@
 
+	\bibitem[US BEA(2019)]{USBEA}
+	U.S. Bureau of Economic Analysis (2019). Personal consumption expenditures: chain-type price index. FRED, Federal Reserve Bank of St. Louis. https://fred.stlouisfed.org/series/PCEPI, April 27, 2019.
+
 	\bibitem[Wolak and Patrick(2001)]{Wolak}

### 2019-04-29 code/matlab/simulation_april/sim_adoption_curve.m
Update simulation code
- regenerate graphs
- rename elasticity simulation
- fix sigma = 1 case
- remove old code

@@ -45,12 +45,8 @@ for j = 1:m
         P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
 
         % Quantities
-        if sigma ~= 1
-            Y = ((alpha'./prices).^(sigma)) * (budget/P);
-        else 
-            Y = (alpha'./prices);
-        end 
-           
+        Y = ((alpha'./prices).^(sigma)) * (budget/P);
+          
         X = (xi_mat')\Y;
 
         results(i,:) = X';
@@ -142,12 +138,8 @@ for j = 1:m
         P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
 
         % Quantities
-        if sigma ~= 1
-            Y = ((alpha'./prices).^(sigma)) * (budget/P);
-        else 
-            Y = (alpha'./prices);
-        end 
-           
+        Y = ((alpha'./prices).^(sigma)) * (budget/P);
+
         X = (xi_mat')\Y;
 
         results(i,:) = X';

### 2019-04-29 code/matlab/simulation_april/sim_adoption_surface.m

@@ -36,11 +36,7 @@ for i = 1:length(results)
         P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
 
         % Quantities
-        if sigma ~= 1
-            Y = ((alpha'./prices).^(sigma)) * (budget/P);
-        else 
-            Y = (alpha'./prices);
-        end 
+        Y = ((alpha'./prices).^(sigma)) * (budget/P);
 
         X = (xi_mat')\Y;
 

### 2019-04-29 code/matlab/simulation_april/sim_eos.m

@@ -45,11 +45,7 @@ for j = 1:m
         P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
 
         % Quantities
-        if sigma ~= 1
-            Y = ((alpha'./prices).^(sigma)) * (budget/P);
-        else 
-            Y = (alpha'./prices);
-        end 
+        Y = ((alpha'./prices).^(sigma)) * (budget/P);
            
         X = (xi_mat')\Y;
 

### 2019-04-29 code/matlab/simulation_april/tax_subsidy_sim.m

@@ -1,84 +1,0 @@
-%% Simulation to find the optimal tax + research combination
-% Cobb-Douglas, 2 Periods
-% Cost of research given by c_beta*beta
-
-beta   = 1;
-c_beta = 0.00001;
-gamma  =  0.00116*100;
-tau    = gamma;
-
-n = 100;
-results = zeros(n,3); 
-tau_range  = linspace(0,2.5,n);
-beta_range = linspace(0.5,2.5,n);
-
-for i = 1:n
-
-    % Variable params
-    tau = tau_range(i);
-    
-    % Parameters
-    alpha = [0.3, 0.7];
-    xi_1  = [1, 1];
-    xi_2  = [0, 1];
-    sigma = 1;
-    phi   = (sigma - 1)/sigma;
-    budget = 1;
-    c_1 = 95*0.9;
-    c_2 = 50;
-
-    % Prices
-    xi_mat   = [xi_1; xi_2*(1+beta)];
-    cost_mat = [c_1*(1+tau); c_2];
-    prices   = xi_mat\cost_mat;
-
-    % Price Index
-    P = 1;
-    
-    % Quantities
-    Y = ((alpha'./prices).^(sigma)) * (budget/P);
-    X = (xi_mat')\Y;
-    
-    % Expand parameters
-    alpha_t = alpha(1);
-    alpha_s = alpha(2);
-    xi_1t = xi_1(1);
-    xi_1s = xi_1(2);
-    xi_2t = xi_2(1);
-    xi_2s = xi_2(2);
-    
-    % Partial G(B) / Partial X_1
-    diff_X1_beta = - (alpha_t*c_2*xi_1s*xi_2s)/(- c_2*xi_1s +    ...
-        tau*xi_2s + c_1*(xi_2s + beta*xi_2s) + beta*tau*xi_2s)^2 ...
-        - (alpha_s*c_2*xi_1t*xi_2t)/(c_1*xi_2t - c_2*xi_1t +     ...
-        tau*xi_2t + beta*c_1*xi_2t + beta*tau*xi_2t)^2;
-    diff_GB_X1 = c_beta*(1/diff_X1_beta);
-    
-    results(i,1) = X(1);
-    results(i,2) = X(2);
-    results(i,3) = gamma + diff_GB_X1;
-
-end
-
-
-%% Plots
-
-figure;
-hold on;
-plot(tau_range, tau_range)
-plot(tau_range, results(:,3))
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-

### 2019-04-29 code/matlab/simulation_april/sim_tax_subsidy.m
Add simulation for tax/subsidies
- add script to simulate effect of technical change on coal quantity
- generate plots from script

@@ -1,0 +1,166 @@
+%% Optimal capacity of Coal with respect to solar price
+
+close all; clear; clc;
+
+% Simulation params
+n = 5000;
+research_multiplier = linspace(1,2,n);
+sigma_range = [0.5];
+m = length(sigma_range);
+
+% Exogenous params
+c_1 = 104.3;
+c_2 = 50;
+alpha = [0.6, 0.4];
+xi_1  = [1,   1];
+xi_2  = [1, 0.1];
+budget = 1;
+
+
+figure('Renderer', 'painters', 'Position', [100 100 900 600])
+hold on;
+
+for j = 1:m
+    
+    sigma = sigma_range(j);
+    results = zeros(n,2); 
+
+    for i = 1:n
+
+        phi   = (sigma - 1)/sigma;
+        x_1_cost_param = c_1;
+        x_2_cost_param = c_2;
+
+        % Prices
+        xi_mat   = [xi_1; xi_2*(research_multiplier(i))];
+        cost_mat = [x_1_cost_param; x_2_cost_param];
+        prices   = xi_mat\cost_mat;
+
+        if any(prices<0)
+            continue
+        end
+
+        % Price Index
+        P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
+
+        % Quantities
+        Y = ((alpha'./prices).^(sigma)) * (budget/P);
+           
+        X = (xi_mat')\Y;
+
+        results(i,:) = X';
+
+    end    
+
+    output = [];
+    output(1,:) = results(:,1);
+    output(2,:) = results(:,2);
+    output(3,:) = research_multiplier-1;
+    
+    % subset to positive quantities
+    ind = ~any(output(1:2,:) <= 0);
+    output = output(:,ind);
+
+    % quantity of solar
+    subplot(2,1,1);
+    hold on;
+    plot(output(3,:)*100, ...
+         output(1,:), ...
+        'LineWidth', 1);
+    
+end
+
+%% Plot formatting
+
+% Add horizontal line at 1
+
+% Format subplot 1
+xlabel('Percent Change in the Efficiency of Solar (MWh)')
+ylabel('Coal Capacity (MWh)')
+xtickformat('percentage')
+xlim([0, 100])
+grid('on')
+
+
+%% Optimal capacity of Coal with respect to own price
+
+% Simulation params
+n = 5000;
[…]

### 2019-04-29 documents/draft.tex
Update draft
- add to externality section
- remove/move proofs

@@
 \usepackage{xcolor}
+\usepackage{cleveref}
 %\usepackage{showframe}
@@
 \newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+
+% section referencing
+\crefformat{section}{\S#2#1#3}
+\crefformat{subsection}{\S#2#1#3}
+\crefformat{subsubsection}{\S#2#1#3}
+\crefrangeformat{section}{\S\S#3#1#4 to~#5#2#6}
+\crefmultiformat{section}{\S\S#2#1#3}{ and~#2#1#3}{, #2#1#3}{ and~#2#1#3}
 
@@
 
-That is, suppose we are interested in
-
-One way to interpret this is in the context of a tax and subsidy.
-Taxing coal at increasing rates has diminishing returns on promoting the market share of solar energy.
-However, for $\sigma \leq 0.5$, subsidizing solar energy can have linear or increasing returns with respect to its market share.
-Also,
-
-Often times, a social planner may also be interested in using other policy instruments such as research subsidies.
-In fact, \citet{Ace2012} find that both carbon taxes and research subsidies are necessary to promote long-run structural change in the energy production sector and avert a climate disaster.
-While our model focuses on production on a shorter time scale, we find a similar result -- a combination of both taxes and subsidies may be more effective in promoting a shift towards clean energy.
-
-Firstly, consider a case where a carbon tax is our only policy instrument.
-Additionally, suppose that our first technology produced negative externalities.
-Specifically, the social cost of pollution is given by $S(X) = \gamma X_1$ where $\gamma$ is the monetary damage per unit of $X_1$.
-A social planner is interested in balancing the damages caused by pollution with the surplus of the private sector and the revenue from the tax.
-That is, they aim to solve
+Suppose we are interested in handling externalities.
+We may assume that our first technology produces pollution according to the function $S(X) = \gamma X_1$ where $\gamma$ is the monetary damage per unit of $X_1$.
+A social planner then aims to balance the damages caused by pollution with the surplus of the private sector and the revenue from the tax.
+Hence, their objective function is given by
 $$\max_{\tau} \; CS + PS - S(X) + \tau X_1$$
-where $\tau$ is the tax on $X_1$, so that its final price is $c_1 + \tau$ and the tax revenue is given by $\tau X_1$.
-The optimal tax is a Pigouvian tax; $\tau$ should be set equal to the marginal social cost of pollution $\gamma$.
-This is an expected, standard solution in most models.
-
-%%% Pigouvian tax proof
-\hfill \\
-\begin{proof} We aim to maximize welfare with respect to the tax $\tau$, hence our first order condition is:
-	\begin{align*}
-	0 &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial S(X)}{\partial \tau} + \frac{\partial \tau X_1}{\partial \tau} \\
-	&=  \left( \underbrace{\frac{\partial CS}{\partial p}  + \frac{\partial PS}{\partial p}}_{= 0} - \frac{ \partial  S(X)}{\partial p} + \frac{\partial \tau X_1}{\partial p} \right) \frac{\partial p}{\partial \tau} \\
-	&=  - \gamma \frac{\partial  X_1}{\partial p} + \tau \frac{\partial  X_1}{\partial p}
-	\end{align*}
-	where the derivatives of producer and consumer surplus are eliminated by the envelope theorem. Therefore, we must have $\tau = \gamma$. \\
-	\hfill
-\end{proof}
-
-Now, suppose that we may also subsidize research which improves the output efficiency of a technology.
-In particular, we let the output efficiency of technology 2 be $(\xi_{2t}, \, \xi_{2s})(1 + \beta)$ where $\beta$ is the percent improvement created by research.
-And, we let the cost of research be given by a convex, differentiable function $G(\beta)$.
-
-\hfill \\
-\begin{proof} First, note that we have:
-	$$X_1 = \dfrac{\alpha _{t}\,(1+\beta) \, \xi_{\mathrm{2s}}}{(c_{1}+ \tau)\,(1+\beta)\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}+\dfrac{\alpha _{s}\,(1+\beta)\,\xi _{\mathrm{2t}}}{(c_{1}+ \tau)\,(1+\beta)\,\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}$$
-
-	We aim to maximize welfare with respect to the tax $\tau$ and the research efficiency modifier $\beta$, hence our first order condition is:
-	\begin{align*}
-	0 	 &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial S(X)}{\partial \tau} + \frac{\partial \tau X_1}{\partial \tau}  - \frac{\partial G(\beta)}{\partial \beta}\\
-	&=  \left( \underbrace{\frac{\partial CS}{\partial p}  + \frac{\partial PS}{\partial p}}_{= 0} - \frac{ \partial  S(X)}{\partial p} + \frac{\partial \tau X_1}{\partial p} - \frac{\partial G(\beta)}{\partial p} \right) \frac{\partial p}{\partial \tau} \\
-	&=  - \gamma \frac{\partial  X_1}{\partial p} + \tau \frac{\partial  X_1}{\partial p} - \frac{\partial G(\beta)}{\partial p} \\
-	\tau &= \gamma + \frac{\partial G(\beta)}{\partial X_1}
-	\end{align*}
-	where the derivatives of producer and consumer surplus are eliminated by the envelope theorem. Equivalently, if we take the derivative of the welfare function with respect to $\beta$, we find that:
-	$$G(\beta) = -\gamma + \frac{\partial \tau}{\partial X_1}$$
-	\\ \hfill
-\end{proof}
+where $CS$ is consumer surplus, $PS$ is producer surplus, $S(X)$ is the cost of pollution, $\tau$ is the tax on $X_1$, and $\tau X_1$ is the tax revenue.
+As usual, the optimal tax is a Pigouvian tax; $\tau$ should be set equal to the marginal social cost of pollution $\gamma$.
+
+However, given the presence of intermittency, is there a better way to handle pollution?
+For example, \citet{Ace2012} model intermittency using a CES production function between clean and dirty energy.
+They find that both carbon taxes and research subsidies are necessary to promote long-run structural change in the energy production sector and avert a climate disaster.
+The necessity of both instruments is a consequence of their model spanning multiple periods; that is, assuming we have CES production structure between clean and dirty energy in a one-period model, a single instrument is enough to optimally handle externalities.
+\footnote{ Recall that, with a CES production structure, the optimal quantity of technology $i$ is given by $X_i = \left( \frac{\xi_i}{c_i} \right)^\sigma  \frac{B}{P}$ where $\xi_i$ is its output per unit, $B$ is the budget, and $P$ is the price index.
+Neglecting effects on the price index, the own-price elasticity of any good is $-\sigma$.
+Furthermore, for the same structure,  we have the FOC: $X_i/X_j =  \left( \frac{\xi_i c_j}{\xi_j c_i} \right)^\sigma$.
+This implies that the cross elasticity of $X_i$ with respect to the output efficiency of technology $j$, $\xi_j$, is also $-\sigma$.
+Hence, a tax on the cost of $X_i$ or a subsidy that increases the efficiency $X_j$ can be used to deal with externalities; but, both are not necessary to do so.} However, while our model focuses on production on a shorter time scale, we find a similar result -- a combination of both taxes and subsidies may be more effective in promoting a shift towards clean energy.
+Moreover, the optimality of combining both instruments is a result of intermittency.
+
+For clarity, let us first consider the cases in our framework where only one instrument is necessary.
+The first case is when no two technologies produce in the same period.
+That is, we can say that the output efficiency matrix, $\xi$, is diagonal without loss of generality; this further implies that we have a CES structure between technologies where the elasticity of substitution is same as that for consumers, $\sigma$.\footnote{A proof is provided in \hyperref[sec:CESspecialcase]{Appendix A.C}} Consequently, if one of these technologies creates negative externalities, the optimal solution is simply use a single instrument such as a Pigouvian tax.
+On the other hand, the second case occurs when all technologies produce in every period but with time-invariant output.
+This results in an edge case where we only employ whichever technology has the highest cost efficiency (output per dollar).
+Consequently, we only need one or no instruments depending on whether the technology employed creates negative externalities.
+Essentially this case describes a situation where we have no intermittency at all.
+On the other hand, the first case describes a situation where we have, in a sense, maximized relative intermittency.
+
+\begin{table}[!t]
+	\caption*{\textbf{Figure 4:} Technical Change and the Optimal Quantity of Coal} 
+	\label{fig:coaltech}
+	\footnotesize
+	\vspace{-1em}
+	\begin{tabular}{@{\extracolsep{0em}}c}
+		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_tax_subsidy} \\
+		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$, $\sigma = 0.5$.
+For the first subplot, we plot the optimal quantity of coal while varying $\xi_2$, the output efficiency of solar, by different factors; so, for instance, at 100\% on the x-axis, we have $\xi_2 = (2, \, 0.2))$.
+Similarly, in the second subplot, we do the same but with the cost of coal, $c_1$.
+}     \\
+	\end{tabular}
+\end{table}
+
+In all other situations, where we have a mix of intermittent and constant-output technologies, two instruments can be more optimal than one.
 
@@
 
-\section{Appendix}
+\section{Appendix A: Supplementary Proofs}
 
@@
 \\ \hfill
-
 \end{proof}
@@
 
-\pagebreak
+\subsection{Optimal Taxation}
+
+The following proof is a derivation of the optimal tax $\tau$ on $X_1$ in the case where it produces externalities. 
+\hfill \\
+\begin{proof} We aim to maximize welfare with respect to the tax $\tau$, hence our first order condition is:
+	\begin{align*}
+	0 &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial S(X)}{\partial \tau} + \frac{\partial \tau X_1}{\partial \tau} \\
+	&=  \left( \underbrace{\frac{\partial CS}{\partial p}  + \frac{\partial PS}{\partial p}}_{= 0} - \frac{ \partial  S(X)}{\partial p} + \frac{\partial \tau X_1}{\partial p} \right) \frac{\partial p}{\partial \tau} \\
+	&=  - \gamma \frac{\partial  X_1}{\partial p} + \tau \frac{\partial  X_1}{\partial p}
+	\end{align*}
+	where the derivatives of producer and consumer surplus are eliminated by the envelope theorem. Therefore, we must have $\tau = \gamma$. \\
+	\hfill
+\end{proof}
+
+\subsection{CES Production as a Special Case}
+
+\label{sec:CESspecialcase}
+
+Our framework nests the case where there exists a CES production structure between each technology.
+This happens when no two technologies produce in the same period and we have the same number of periods as technologies.
+Additionally, the CES production function's elasticity parameter in this case will be equivalent to the consumer's CES utility elasticity parameter (the intertemporal elasticity of substitution for electricity consumption).
+
+\begin{proof}
+	Firstly, note that we can reindex our technologies such that $\xi$ is diagonal, since each technology only produces in one period.
+Hence, without loss of generality, we have diagonal $\xi$.
+Next, we may say that the electricity output in period $i$ is given by $Z_i = \xi_{i,i} X_i$.
+Now, recall that the FOC for profit-maximization is given by $p = \xi^{-1} c$, hence we have $p_i = c_i / \xi_{i,i}$.
+And, finally, with the FOC for utility maximization, we have:
+	\begin{align*}
+	\frac{Z_i}{Z_j} &= \left( \frac{\alpha_i p_j}{\alpha_j p_i} \right)^\sigma \\
+	\frac{ X_i }{X_j} &= \left( \frac{ \alpha_i p_j \xi_{j,j}^{1/\sigma} }{ \alpha_j p_i \xi_{i,i}^{1/\sigma} } \right)^\sigma \\
+	\frac{ X_i }{X_j} &= \left( \frac{ \alpha_i c_j \xi_{j,j}^{1/\sigma - 1} }{ \alpha_j c_i \xi_{i,i}^{1/\sigma - 1} } \right)^\sigma
+	\end{align*}
+	By definition, the elasticity of substitution between any two, arbitrary technologies $i$ and $j$ is constant.
+Moreover, it can be shown that this FOC can be rearranged to give the following demand equation for each technology $i$
+	\begin{align}
+	X_i &= \left(\frac{\beta_i}{c_i} \right)^\sigma \frac{I}{P} \\
+	P &= \sum_t \beta_i^\sigma p_i^{1-\sigma}
+	\end{align}
+	where $\beta_i = \alpha_i \xi_{i,i}^{-\phi}$, $\sigma = 1 / (1-\phi)$, and $I$ is the consumers income.	So, in total, accounting for both the producer and consumer's objectives, we are essentially solving for:
+	\begin{align*} 
+	V &= \left( \sum_i \beta_i X_i^\phi \right)^{(1/\phi)}  \\
+	\text{such that\quad} I &= \sum_i c_i X_i 
+	\end{align*}
+	This is a standard CES function.
+	\\ \hfill
+\end{proof}
 

### 2019-04-30 documents/draft.tex
Update draft and code
- add script to estimate hessian for x1
- add to discussion on pollution policy

@@
 	colorlinks=true,
-	linkcolor = blue,
-	urlcolor  = blue,
+	linkcolor = darkblue,
+	urlcolor  = darkblue,
 	citecolor = darkblue,
-	anchorcolor = blue
+	anchorcolor = darkblue
 }
@@
 	\noindent \textbf{Example  1:} $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$. 
+	\label{Params: Example 1}
 \end{center}
@@
 Consequently, we only need one or no instruments depending on whether the technology employed creates negative externalities.
-Essentially this case describes a situation where we have no intermittency at all.
-On the other hand, the first case describes a situation where we have, in a sense, maximized relative intermittency.
+Essentially this latter case describes a situation where we have no intermittency at all.
+On the other hand, the former case describes a situation where we have, in a sense, maximized relative intermittency.
+But, with respect to both cases, we only need one instrument to handle externalities.
 
@@
 		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$, $\sigma = 0.5$.
-For the first subplot, we plot the optimal quantity of coal while varying $\xi_2$, the output efficiency of solar, by different factors; so, for instance, at 100\% on the x-axis, we have $\xi_2 = (2, \, 0.2))$.
-Similarly, in the second subplot, we do the same but with the cost of coal, $c_1$.
-}     \\
+For the first subplot, we graph the optimal quantity of coal while varying $\xi_2$, the output efficiency of solar, by different factors; so, for instance, at 100\% on the x-axis, we have $\xi_2 = (2, \, 0.2)$.
+Similarly, in the second subplot, we do the same but with the cost of coal, $c_1$.}     \\
 	\end{tabular}
@@
 
-In all other situations, where we have a mix of intermittent and constant-output technologies, two instruments can be more optimal than one.
+In all other situations, where we have a mix of intermittent and constant-output technologies, using multiple instruments can be more effective than just one.
+That is,  first suppose that research subsidies increase the output efficiency $\xi_i$ of some technology $i$.
+So, output efficiency is then given by $\xi_i \left( 1 + \beta_i \right)$ where $\beta_i$ is the percent increase in the output efficiency of technology $i$ as a result of research.
+Now, consider again a two-period setting with coal and solar with the same parameters as those given in \hyperref[Params: Example 1]{Example 1}.
+As discussed earlier, one solution to externalities is to set a Pigouvian tax on coal equal to its marginal social damage.
+However, we may be able to reduce our reliance on coal in a more effective (welfare-maximizing) way by subsidizing research in solar as well.
+We can intuit this to be a potential solution based on \hyperref[fig:coaltech]{Figure 4}; in the first subplot, we show the effects of research into solar on the use of coal, while, in the second subplot, we show the effect of taxes on the use of coal.
+Essentially, with respect to reducing the use of coal power, there are diminishing returns to both pollution taxes and solar research subsidies.
+Hence, the pollution-reduction benefits of both instruments are convex.\footnote{To be more precise, we numerically compute the Hessian for $X_1$ with respect to $\beta_2$, the percent change in the output efficiency of solar from research, and the tax rate, $\tau$.
+We find that the Hessian is negative definite.
+Consequently, since reducing $X_1$ creates welfare by reducing the social cost of pollution $\gamma X_1$, the Hessian of the benefits, $-\gamma X_1$ is positive definite and thus convex.} On the other hand, the deadweight loss created by taxation is generally convex; since research subsidies must be funded by tax revenue, its costs must necessarily be convex as well.
+In short, both instruments have convex benefits and costs, which implies that optimal policy is likely a combination of both.
+
+In total, besides for edge cases, this suggests that optimal policy may be to incorporate both
 
@@
 \section{Conclusion}
+
+Throughout the paper, we considered coal and solar power as examples of fossil and renewable energy. Moreover, 
+For instance, we discussed how to handle pollution when energy sources are intermittent; we found that, rather than a standard Pigouvian tax, we would be better off using a combination of research subsidies and carbon taxes.
+One implicit but important point here is that optimal policy must be tuned for differences in local electricity markets.
+That is, even if externalities are global and research spills over, optimal policy differs on a local scale since generation technologies differ on a local scale.
 

### 2019-04-30 code/matlab/simulation_april/main.m

@@ -6,15 +6,15 @@
 
 %% CES Numerical Sim
 
-alpha = [0.3, 0.7];
+alpha = [0.6, 0.4];
 xi_1  = [1, 1];
-xi_2  = [0, 1];
+xi_2  = [1, 0.1]*1.00;
 
-sigma = 2;
+sigma = 0.5;
 phi   = (sigma - 1)/sigma;
-budget = 1e4;
+budget = 1;
 
-x_1_cost_param = 95*0.9;
+x_1_cost_param = 104.3*1.00;
 x_2_cost_param = 50;
 
 % Prices
@@ -30,213 +30,26 @@ Y = ((alpha'./prices).^(sigma)) * (budget/P);
 X = (xi_mat')\Y
 
 
-%% CD Numerical Sim
+%% Hessian
 
-alpha = [0.3, 0.7];
-xi_1  = [1, 1];
-xi_2  = [0, 1];
+f_ab = (sim_function([1.01,1.01]) - sim_function([1.01, 0.99])        ...
+    - sim_function([0.99, 1.01]) + sim_function([0.99, 0.99])) ...
+    / (4*0.02*0.02);
 
-budget = 1;
-
-x_1_cost_param = 95*0.9;
-x_2_cost_param = 50;
-
-% Prices
-xi_mat   = [xi_1; xi_2];
-cost_mat = [x_1_cost_param; x_2_cost_param];
-prices   = xi_mat\cost_mat;
-
-% Quantities
-Y = ((alpha'./prices).^(1))*budget;
-X = (xi_mat')\Y
+f_aa = (-sim_function([0.99, 1.0]) + 2*sim_function([1, 1]) ...
+    - sim_function([1.01, 1]))/(0.01^2);
 
 
-%% Price (Cost) Elasticity Sim
-
-n = 500;
-results = zeros(n,2); 
-cost_multiplier = linspace(0.5,2.5,n);
-
-for i = 1:n
-    
-    alpha = [0.3, 0.7];
-    xi_1  = [1,   1];
-    xi_2  = [0.1, 1];
-
-    sigma = 5;
-    phi   = (sigma - 1)/sigma;
-    budget = 1;
-
-    x_1_cost_param = 95*cost_multiplier(i);
-    x_2_cost_param = 50;
-
-    % Prices
-    xi_mat   = [xi_1; xi_2];
-    cost_mat = [x_1_cost_param; x_2_cost_param];
-    prices   = xi_mat\cost_mat;
-    
[…]

### 2019-04-30 code/matlab/simulation_april/sim_function.m

@@ -1,0 +1,36 @@
+function [ X ] = sim_function(v)
+% ========================================================================
+% SIM_FUNCTION finds the optimal quantity of X_1 given a multiplier for 
+% the output efficiency of solar and a tax rate on coal
+% ========================================================================
+% INPUT ARGUMENTS:
+%   v             (matrx)  the first entry is the multiplier on the output
+%                          efficiency of solar and the second entry is the 
+%                          tax rate
+% ========================================================================
+
+alpha = [0.6, 0.4];
+xi_1  = [1, 1];
+xi_2  = [1, 0.1]*v(1);
+
+sigma = 0.5;
+phi   = (sigma - 1)/sigma;
+budget = 1;
+
+x_1_cost_param = 104.3*v(2);
+x_2_cost_param = 50;
+
+% Prices
+xi_mat   = [xi_1; xi_2];
+cost_mat = [x_1_cost_param; x_2_cost_param];
+prices   = xi_mat\cost_mat;
+
+% Price Index
+P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
+
+% Quantities
+Y = ((alpha'./prices).^(sigma)) * (budget/P);
+X = (xi_mat')\Y;
+
+
+end

### 2019-05-01 documents/draft.tex
Update draft
- clean up introduction
- clarify methodology
- fix results formatting

@@
 
-\section{Extended Abstract}
+\section{Introduction}
 
@@
 Unlike the alternatives, wind and solar power are particularly unique in that the amount of energy they supply is intermittent.
-Consequently, designing economically efficient policy to promote their adoption is not straightforward given that they cannot easily substitute for traditional technologies such as coal power which handles base load demand.
-Some of the literature has approached the problem by constructing numerical models that find the cheapest renewable technology set while accounting for intermittent supply.
-Müsgens and Neuhoff (2006) model uncertain renewable output with intertemporal generation constraints, while Neuhoff, Cust, and Keats (2007) model temporal and spatial characteristics of wind output to optimize its deployment in the UK.
-On the other hand, other literature focuses on the effect of intermittent technologies on the market itself; Ambec and Crampes (2010) study the interaction between intermittent renewables and traditional reliable sources of energy in decentralized markets, and Chao (2011) models alternative pricing mechanisms for intermittent renewable energy sources.
-Additionally, Borenstein (2010) reviews the effects of present public policies used to promote renewables and the challenges posed by intermittency.
-
-In this paper, we present a theoretical model of electricity markets with intermittent renewable energy and derive the optimal public policy to handle pollution externalities.
-In contrast with other theoretical models of intermittency which optimize a pubic electricity sector, our model assumes utility and profit maximization.
-Additionally, it represents the energy sector over multiple periods with electricity output for each technology varying over time for intermittent technologies.
-This approach is better suited for studying the dynamics of present US electricity markets which are primarily funded by private sector investment and have prices that vary over time.
-We first consider a simpler version of our model with two periods and two energy generation technologies, derive the comparative statics for this model, and detail the policy implications.
-Then, we produce numerical results for optimal policy prescriptions with a multi-period, multi-technology version of our model using electricity generation data on the PGM region.
-
-Present models of the energy sector concerned with the adoption of renewable energy often discuss the elasticity of substitution between clean and dirty energy; this elasticity is meant to capture factors such as intermittency and reliability that impede perfect substitution between energy sources.
-Additionally, this elasticity is often estimated empirically or modelled in a CGE using a CES production function with capital inputs for each energy technology.
-However, this top down approach may be missing the actual source of the substitution effects while also being unrealistic.
-For instance, consider a simple case where energy output is a Cobb-Douglas function (a special case of CES) of two energy inputs: solar and coal.
-According to this function, increasing the amount of coal input causes the marginal product of solar input to rise; this makes little sense in practical terms, since the output of additional solar panels should not be related to the amount of coal input.
-Moreover, this approach, while possibly relevant for other sectors' goods, weakens the accuracy of theoretical and CGE models focused on the energy sector.
-
-However, it is still possible to produce a more accurate model of the electricity sector that can capture trade-offs between the energy output of different technologies from both cost and intermittency.
-To start, rather than energy production following a general CES function, we first assume that energy follows a linear production function where total energy is instead the sum of the energy output of each source.
-The purpose of using a linear production function is that increasing the input of one energy source does not change the marginal product of another source as it does in a CES function.
-Additionally, we split this production function up across periods; that is, in each period, the electricity generation is equal to the energy output of each source in that period.
-For intermittent technologies, energy output varies in each period, so total output would as well.
-Next, we assume that firms pick a profit-maximizing level of investment in each energy technology.
-This investment stays fixed in all periods, but the total energy output can vary over time due to intermittency; for instance, a solar plant provides a variable output by time of day, while nuclear plant cannot easily vary its output within 24 hours.
-Moreover, we assume that firms face linear costs and electricity prices are set equal to their marginal cost; the former assumption is temporarily made for mathematical tractability while the latter is realistic given the competitiveness of electricity markets.
-
-While the production function described so far is linear, we may still find a non-zero elasticity of substitution between energy sources.
-That is, consider a representative agent with a CES utility function that captures intertemporal variation in the utility gained from energy consumption.
-Specifically, the utility function is composed of energy consumption differentiated by period; so, for example, in a two-period model, we may have off-peak consumption and on-peak consumption as our two goods.
-Because people prefer to consume energy at different proportions based on the time of day, this variation can be modeled through the share parameters in the CES function.
-Moreover, since people may substitute energy consumption across time by availability and prices, the CES elasticity parameter captures the intertemporal elasticity of substitution.
-Thus, in this model, the intermittency of an energy generation technology plays a key role in determining its substitutability with other technologies.
-For instance, solar power may be a good substitute for coal power during the day, but obviously not at night; consequently, this pair complements each other, since coal handles the base load while solar handles the peak load.
-Alternatively, wind and solar are a poor combination, since both produce intermittently; this pair is closer to being substitutes.
-All in all, the result of using CES preferences with temporally differentiated energy consumption is that we can capture substitutability/complementarity between energy sources in an accurate way.
-
-The first significant result in this model is that the optimal quantity of investment in intermittent renewable technology is concave with respect to both cost efficiency (cost per unit) and output efficiency (energy output per unit).
-So, for example, suppose some location has a coal-fired plant and is considering investing in a solar power plant.
-A 10\% increase in the output per solar panel may increase the optimal quantity of solar panels by x\%, while a 20\% increase in solar efficiency will increase the optimal quantity of solar by y\% where y < 2x.
-Because of this concavity, exponential increases in efficiency of intermittent renewable sources over time, as Moore’s Law may predict, is not enough to fully substitute out reliable energy technology.
-Hence, we argue that a full transition to renewable energy requires more emphasis on technologies such as nuclear, biomass, hydro, and geothermal energy sources; although these sources compete with intermittent energy technology, they are able fully substitute out for fossil fuel energy.
-Additionally, the reliable output of these technologies can handle base loads; this allows them to complement the intermittency of renewables such as wind and solar.
-
-Secondly, suppose that we would like to promote clean energy adoption and replace dirty energy to reduce the pollution emissions.
-Because we have diminishing returns from both forms of efficiency, it is optimal to subsidize both research and the cost of intermittent renewable technology.
-This is because we expect research subsidies to increase both output efficiency and cost efficiency, while subsidies would increase the cost efficiency of renewables for a market participant.
-A mix of both instruments leads to improving both forms of efficiency at once, thus replacing dirty energy technology in the most cost-efficient way.
-Alternatively, since we would see symmetrical effects from taxing dirty energy sources rather than subsidizing clean ones, taxing dirty energy sources can substitute for renewable cost subsidies.
-Consequently, a carbon tax plus a research subsidy for renewables is another optimal choice for pollution abatement.
-
-Finally, our model implies that the optimal level of subsidies/taxes on energy generation should vary by the state of the local energy market.
-That is, the change in optimal quantity of intermittent energy technology with respect to both types of efficiency is also a function of the efficiencies of the other technologies available.
-Consequently, the marginal benefit of a subsidy or tax varies spatially, since different geographies have access to different energy sources.
-For instance, one community may be relying on hydropower while another may be using coal power; the effect of a 1\% cost subsidy on solar installments in these two communities would vary because of the differences in the communities’ pre-existing energy generation technologies.
-Hence, local communities that aim to promote clean energy and reduce pollution should optimize their policy instruments to suit their local energy markets.
-
-\subsection{References}
-
-\begin{itemize}
-	\item Literature
-	\item Description of model
-	\item 
-\end{itemize}
-
-\section{Outline}
-\dots
-
-Things I'd like to say:
-\begin{itemize}
-	\item Because the marginal product of renewable energy inputs may be time-dependent, renewable energy may complement traditional, constant-output energy sources rather than fully substitute for it.
-Obvious arugment follows from base load output required at all times.
-	\item How the conversion parameters for energy inputs affect their elasticity of substitution
-	\item How variability in energy output decreases the value of particular energy sources. Obvious argument from concavity of utility implying risk aversion. 
-\end{itemize}
-
-\pagebreak
-
-\section{Introduction}
-
-Renewable energy technologies have seen considerable adoption over the last few decades (EIA 2019).
-Unlike the alternatives, wind and solar power are particularly unique in that the amount of energy they supply is intermittent.
-Consequently, designing economically efficient policy to promote their adoption is not straightforward given that they cannot easily substitute for traditional technologies such as coal power which handles base load demand.
-Moreover, simpler approaches, such as using the levelized cost of electricity (LCOE) to compare technologies is flawed in any setting with variable electricity prices.
-In particular, \citet{Joskow2011} argues that
-
-\begin{quote}
-	``Instead [of using metrics like LCOE], the economics of all generating technologies, both intermittent and dispatchable, can be evaluated based on the expected market value of the electricity that
-	they will supply, their total life-cycle costs, and their associated expected profitability. Such an
-	analysis would reflect the actual expected production profiles of dispatchable and intermittent
-	technologies, the value of electricity supplied at different times, and other costs of intermittency
-	associated with reliable network integration. This is exactly the way investors in merchant generating plants evaluate whether or not to invest."
-\end{quote}
-We structure our model with this critique in mind.
-Specifically, we develop a model where producers optimize the supply of each generation technology on the expected market value of the electricity produce.
-We do so by ....
-
-Some of the literature has approached the problem by constructing numerical models that find the cheapest renewable technology set while accounting for intermittent supply.
-\citet{MN2006} model uncertain renewable output with intertemporal generation constraints, while \citet{NCK2007} model temporal and spatial characteristics of wind output to optimize its deployment in the UK.
+Consequently, designing economically efficient policy to promote their adoption is not straightforward given that they cannot easily substitute for fossil fuel technologies such as coal power.
+Moreover, traditional economic measures such as the levelized cost of electricity (LCOE) fail to capture the true economic value of intermittent technologies, because they neglect to account for variation in output and prices over time \citep{Joskow2011}.
+
+Some of the literature has overcome this critique by constructing numerical models that find the cheapest renewable technology set while accounting for intermittent supply.
+For instance, \citet{MN2006} model uncertain renewable output with intertemporal generation constraints, while \citet{NCK2007} model temporal and spatial characteristics of wind output to optimize its deployment in the UK.
 On the other hand, other literature focuses on the effect of intermittent technologies on the market itself; \citet{AC2012} study the interaction between intermittent renewables and traditional reliable sources of energy in decentralized markets, and \citet{Chao2011} models alternative pricing mechanisms for intermittent renewable energy sources.
@@
 Our model comes closest to that of \citet{HH} who build a peak-load pricing model where the availability of renewable capacity varies stochastically.
-This stochastic variability models the intermittency and affects the adoption of renewables in a market with dynamic pricing.
+This stochastic variability models intermittency and negatively affects the adoption of renewables.
 Furthermore, they simplify their analysis by setting aside complications such as  outage costs and rationing rules.
-In total, their model finds an S-shaped adoption curve for renewables once their LCOE's reach those of fossil fuel energy.
+In total, their model finds an S-shaped adoption curve for renewables as they get cheaper.
 In addition, they find that a Pigouvian tax can properly internalize the costs of fossil fuels in a setting with perfect competition.
-Likewise, our model makes equivalent simplifications and finds similar results on an equilibrium in  amarket with dynamic prices.
-But, our representation of the intermittency of renewables differs in a significant way.
+Likewise, we model the  equilibrium of a market with dynamic prices and access to both renewable and fossil energy.
+However, our results differ in key ways, because we take a different approach to modeling intermittency.
 
@@
 By intermittency, we predictable changes in output related to physical constraints.
-For instance, while wind energy output varies over time, if  we know the angle and speed of wind, we may precisely derive the quantity of energy that a wind farm generates.\footnote{\citet{Foley2012} provide a review of the literature on the forecasting of wind power.
+For instance, while wind energy output varies over time, if  we know the angle and speed of wind, we may precisely derive the quantity of energy that a wind farm generates.\footnote{ \citet{Foley2012} provide a review of the literature on the forecasting of wind power.
 Over time, forecasts have gotten much more accurate allowing electricity grids to manage wind power intermittency ahead of time.}  At the same time, these forecasts may not be perfect and, as a result, we see unexpected variation in the output of a technology.
-This unpredictability may be better captured by the notion of reliability; specifically,  we refer to definition provided by the US Department of Energy's \citep{ORNL} -- ``Power reliability can be defined as the degree to which the performance of the elements in a bulk system results in electricity being delivered to customers within accepted standards and in the amount desired." This is more so related to the stochastic or unpredictable variation in the output of a technology.
+This unpredictability may be better captured by the notion of reliability; specifically,  we refer to definition provided by the US Department of Energy's \citet{ORNL} -- ``Power reliability can be defined as the degree to which the performance of the elements in a bulk system results in electricity being delivered to customers within accepted standards and in the amount desired." This is more so related to the stochastic or unpredictable variation in the output of a technology.
 Unlike intermittency, this cannot be planned around with 100\% certainty.
@@
 
-On the other hand, we neglect reliability for parsimony and develop a two-technology, two-period model consisting of fossil and renewable energy.
-Then, we model intermittency as defined above by allowing the output of renewable energy to differ between periods according to known function.
-At the same time, we consider a representative consumer whose utility is given by CES function where each good is electricity consumption differentiated by time.
-This captures consumers' preferences for electricity consumption throughout the day as well as their willingness to substitute consumption across time.
-We then fit the parameters of this CES utility function using electricity consumption and price data for each US state.
-At the same time, we set parameters of our technologies (their cost and output) to those of coal and solar.
-Overall, this treatment of intermittency produces some key results similar to that of Helm and Mier.
-That is, we also find a Pigovian tax to be a solution to externalities along with an S-shaped adoption curve for renewables.
-But, moreover, we find the elasticity of substitution between fossils and renewables to be highly non-linear; this directly challenges the CES production structure assumption made by standard models of fossil and renewable energy.
-Finally, we discuss how a combination of carbon taxes and research subsidies may be more optimal than carbon taxes alone in the presence of intermittency.
-
-% What we have in common
-% What's new, what adds to the literature
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%% Summary of results
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+On the other hand,  we model intermittency as defined above by allowing the output of renewable energy to differ between periods according to known function.
+But, for parsimony, we assume that the output of all technologies in each period does not vary stochastically; that is, we focus on intermittency rather than reliability.
+We then model the electricity sector using a representative firm that chooses and builds capacity from a set of electricity-generating technologies to maximize profit; some of these technologies are intermittent while others have constant output.
+Then, we consider a representative consumer who purchases varying quantities of electricity in each period in order to maximize utility.
+Generally, people prefer to spread their electricity consumption out over time; a standard CES function can capture this preference in a simple way.
+That is, we treat electricity as a heterogenous good which is differentiated by its delivery time; consumer utility is given by a CES function of electricity consumption in each period.\footnote{ The use of a CES function as such has been explored earlier by \citet{Schwarz}, \citet{Schwarz}, \citet{Herriges}, and \citet{KS1994}, \citet{Aubin}, and \citet{Moha2016}.
+Their papers empirically estimate the parameters for this function; we provide a more detailed discussion of the empirical literature in our \hyperref[sec:methodology]{Methodology}.} These two sides of the market reach an equilibrium through adjustments in prices of electricity in each period.
+All in all, we make many of the same assumptions that \citet{HH} do.
+We assume dynamic pricing,\footnote{ \citeauthor{HH} provide a motivation for models incorporating the dynamic pricing of electricity.
+They argue such approaches to pricing will become the norm with further technological advances and coming regulatory changes.} no load rationing, and positive prices.
+
+Then, we parametrize our model empirically.
+To start, we fit the parameters of the consumer's CES utility function using electricity consumption and price data for each US state.
+Specifically, we estimate the intertemporal elasticity of substitution for electricity consumption; this parameter plays a particularly important role in our model, since it captures the effects of intermittency on demand.
+Then, to model the supply side, we narrow our model to a two-period, two-technology setting with renewables and fossil energy.
+We proxy for renewable energy using solar and proxy for fossil energy using coal; then, we parametrize each accordingly.
+Finally, we implement our model numerically and solve for the equilibrium.
+We study the effects of technical change on the energy market and derive policy implications.
+
+Overall, this treatment of intermittency produces some key results that contrast with those of Helm and Mier.
+First, while we also find that externalities can be handled through a Pigouvian tax, we further find that a combining both taxes on pollution and research subsidies for renewables is more optimal than either policy instrument alone.
+Second, we find that, as renewables get cheaper, their adoption is not necessarily S-shaped but can be concave or convex depending the elasticity of substitution in the consumer's utility function; with our estimated parameters, we find this relationship to be almost linear.
+Third, a significant amount of literature has assumed a CES structure between renewable and fossil energy (see \citet{Pap}); this assumption has been motivated, in part, by the need to capture imperfect substitutability between these two generation technologies as a result of intermittency.
+However, our direct model of intermittency disconfirms this assumption; the elasticity of substitution between these two energy technologies is far from linear as a \textit{consequence} of intermittency.
+In short, optimal taxes and subsidies along with the substitutability of renewable and fossil energy all vary with the state of the local energy market.
+Hence, we believe that optimal environmental policy must take into account local conditions far more than has previously been assumed.
 
 \section{Model}
-
-We model electricity as a heterogenous good which is differentiated by its delivery time.
-Then, we consider a representative consumer who purchases varying quantities of electricity in each period in order to maximize utility.
-Generally, people prefer to spread their electricity consumption out over time; the convexity of the indifference surfaces of a standard CES function can model this preference in a simple way.
-The use of a CES function for modeling consumer utility with electricity consumption differentiated by time has been explored earlier by \citet{Moha2016}.
-Their paper calibrates the share parameters of the CES function with actual electricity consumption data for peak and off-peak hours; they further provide a sensitivity analysis with respect to the elasticity of substitution parameter.
-Similarly, \citet{Schwarz} provides an empirical study of this CES function and estimate its parameters for industrial customers in a real-time pricing program; their estimates of the intertemporal elasticity of substitution for electricity consumption fall around 0.03.
-
-Next, we model the electricity sector using a representative firm that chooses a set of electricity-generating inputs to maximize profit; some of these inputs are intermittent - they generate a differing amounts of energy in each period.
-These two sides of the market reach an equilibrium through adjustments in prices of electricity in each period.\footnote{While, in reality, consumers generally pay fixed rates for electricity, \citeauthor{HH} provide a motivation for models incorporating dynamic pricing; they argue such approaches to pricing will become the norm with further technological advances and coming regulatory changes.
-} For simplicity, we do not allow for load rationing  or negative prices.
-And, again for simplicity, we assume that the output of all technologies in each period does not vary stochastically.
 
@@
 
-For more tractable results, we consider a simpler scenario where $n = m = 2$ and $\sigma = 1$ (Cobb-Douglas) which is described in detail in the appendix.
-To start, this scenario allows us to determine which sets of parameters lead to edge cases where one of the technologies is not used.
-We may define these conditions in terms of cost efficiency and output efficiency; to clarify, for some arbitrary period $t$ and technology $i$, we use cost efficiency to refer to $\xi_{i,t}/c_i$ and output efficiency to refer to $\xi_{i,t}$.
-The conditions to avoid an edge case are then given by the following proposition.
+For more tractable results, we consider a simpler scenario where $n = m = 2$ and $\sigma = 1$ (Cobb-Douglas); this particular case is described in greater  detail with proofs in \hyperref[sec:cobbdoug]{Appendix A.A}.
+Moreover, these parameters are of particular interest, because they simplify the model enough to allow us to derive comparative statics and determine which sets of parameters lead to edge cases.
+
+To start, we discuss the conditions on the exogenous parameters required to avoid edge-cases.
+Alternatively, these are the conditions required for a technology to be economical.
+But, first, we define two recurring terms in our analysis: cost efficiency and output efficiency.
+For some arbitrary period $t$ and technology $i$, we use cost efficiency to refer to $\xi_{i,t}/c_i$ and output efficiency to refer to $\xi_{i,t}$.
+So, for example, A technology is more cost efficient than another in a particular period when its output in that period per ``dollar" spent is larger than that of the other technology in the same period.
 \begin{proposition}
-	For technology $i$ to be economical, it must meet three conditions with respect to same arbitrary period $t$.
-Firstly, it must the most cost effective technology for some particular period $t$.
+	Assume that, for all $i$ and $t$, we have $\xi_{i,t}, \alpha_t, c_i > 0$.
+Furthermore, suppose that $\xi$ is invertible.
+For technology $i$ to be economical, it must meet three conditions with respect to some arbitrary period $t$.
+Firstly, it must the more cost effective than any of the other technologies in period $t$.
 Secondly, it must have have a comparative advantage in output efficiency in the same period $t$.
@@
 \end{proposition}
-The condition on cost efficacy is fairly intuitive; one case of the contrapositive is that if a technology is not cost effective in any period, it will not be used.
-Similarly, the other is that if a technology is the most cost effective in every period, it will be the only technology used.
+The condition on cost efficacy is fairly intuitive; one case of the contrapositive is that if a technology is not the most cost effective in any period, it will not be used.
+Alternatively, if a technology is the most cost effective in every single period, it will be the only technology used.
 The second condition regarding output efficiency actually stems from the invertibility of $\xi$.
-If we did not have $\xi$ invertible, we either have at least one technology that does not produce in any period or we have at least one technology being a linear combination of the other technologies.
+If we did not have $\xi$ invertible, we either have at least one technology that does not produce in any period or we have at least one technology being a linear combination of the other technologies in terms of output.
 In the latter case, some technologies are not economical because their output can be replicated the other technologies in a more cost effective way.
@@
 In the later case, we may still eliminate technology $i$ or not use the other two technologies depending on the demand.
-Overall, in any case, $\xi$ not invertible means at least one technology is not used.
+Overall, in any case, $\xi$ not invertible means that at least one technology is not used.
 Finally, the demand condition is straightforward; even if a technology is optimal in a certain period, if consumers do not sufficiently demand electricity during that period, then there is little reason to use that technology.
@@
 \begin{proposition}
+	Suppose we are not in an edge case, so that the conditions of Proposition 1 hold for each technology.
 The equilibrium quantity of a technology is increasing with its output efficiency and decreasing with its cost; at the same time, it is decreasing with the output efficiency of the other technologies and increasing with their cost.
@@
 Then, its equilibrium quantity is increasing with respect to the demand share parameter $\alpha_t$ and decreasing with respect to the demand share parameters of the other periods.
-Furthermore, with the same conditions on $i$ and $t$, the comparative statics of $Z_t$ and $X_i$ are equivalent.
+Furthermore, again assuming technology $i$ is the most cost effective in period $t$, the comparative statics of $Z_t$ and $X_i$ are equivalent.
 \end{proposition}	
@@
 On the other hand, the statics for $Z$ may not be immediately obvious.
-However, they are still intuitive given that we have $Z = \xi_T X$.
-That is, suppose that the optimal quantity of $X_1$ rises by 1\% while that of $X_2$ falls by the same amount.
-Then, we expect output to increase whichever period $\xi_1$ is largest, while it should fall in whichever period $\xi_2$ is smallest; this essentially describes the signs for $\partial Z / \partial X$.
-Now, since we have already derived the signs of the comparative statics for $X$ with respect to each of the parameters, we can intuit, by the chain rule, the comparative statics for $Z$.\footnote{This intuition would not be correct if the derivative in $X_1$ with respect to an arbitrary parameter was significantly different in magnitude from the derivative in $X_2$ with respect to the same parameter.
-However, in this particular scenario, such a case does not occur.} Similarly, the comparative statics for the share parameters of the utility function, $\alpha$, follow in the opposite direction.
-A rise in $\alpha_t$ would directly raise the optimal quantity of $Z_t$; hence, whichever technology is more cost effective at producing in period $t$ would be used more.
+Instead, they follow from the fact that we have $Z \equiv \xi_T X$.
+That is, suppose we have an arbitary technology $i$ that is the most cost effective source of electricity on period $t$.
+If consumers demanded that 100\% of their energy arrive in period $t$, then relying solely on technology $i$ for energy would be the most economical solution.
+Consequently, it seems intuitive that the comparative statics of $X_i$ follow through to $Z_t$.
+This intuition just happens to follow through even when other technologies are employed and there is demand in multiple periods.
+Similarly, the comparative statics for the share parameters of the utility function, $\alpha$, travel in the opposite direction.
+A rise in $\alpha_t$ would directly raise the optimal quantity of $Z_t$; hence, whichever technology is most cost effective at producing in period $t$ would be used more.
 We provide a more detailed and quantitative discussion of the comparative statics and edge cases in the appendix.
@@
 \section{Empirical Methodology}
+\label{sec:methodology}
 
@@
 A number of other papers have approached this problem using data from real-time pricing experiments.
-These include \citet{Schwarz}, \citet{Herriges}, and \citet{KS1994}.\footnote{There has also been a large literature that directly estimates the price elasticity of electricity demand without imposing a CES functional form.
+These include \citet{Schwarz}, \citet{Herriges}, and \citet{KS1994}.\footnote{ There has also been a large literature that directly estimates the price elasticity of electricity demand without imposing a CES functional form.
 These papers include \citet{Wolak}, \citet{Zarnikau}, \citet{Woo}, \citet{Zhou}, \citet{Reiss}, \citet{Fan}, and \citet{Deryugina}.
@@
 All three papers study real-time electricity pricing programs for industrial consumers using similar methodologies.
-\citet{Aubin} also provide estimates of the $\sigma$ but using a different methodology; their results find $\sigma < 0$ which is impossible since it would imply upward-sloping demand curves under a CES structure.
+Additionally, \citet{Aubin} also provide estimates of the $\sigma$ but using a different methodology; their results find $\sigma < 0$ which is impossible since it would imply upward-sloping demand curves under a CES structure.
+Finally, \citet{Moha2016} also empirically estimates the share parameters for a CES function of this form, but do not estimate the elasticity of substitution.
+
 A common flaw in these papers is that they do not account for endogeneity caused by a supply-side response to prices.
@@
 We collect monthly data from the \cite{EIANetgen} on retail electricity prices and consumption for each state in the US from 2011 to 2018.
-Additionally, also from the EIA, we obtain data on the average cost of coal for electricity generation for each state and month.\footnote{The coal price data set contains a large number of missing values due to privacy concerns; however, we do not expect that these missing values are correlated with the data itself.} We deflated both electricity and coal prices over time using the PCECP Index provided by the  \cite{USBEA}.
+Additionally, also from the EIA, we obtain data on the average cost of coal for electricity generation for each state and month.\footnote{ The coal price data set contains a large number of missing values due to privacy concerns; however, we do not expect that these missing values are correlated with the data itself.} We deflated both electricity and coal prices over time using the PCECP Index provided by the  \cite{USBEA}.
 Finally, we collect data on HDDs and CDDs from the NOAA's \citet{CPC} for the same panel.
@@
 Hence, we construct each row in our regression data set using unique combinations of $t,s$ where $t \neq s$ for each state $i$.
-Due to the number of potential combinations and thus observations, we restrict our data set to a random sample of 9000 observations.\footnote{We reran our regressions with several different samples of 9000 and found that our estimated coefficients did not significantly change; hence we believe this sample size is sufficient.}
+Due to the number of potential combinations and thus observations, we restrict our data set to a random sample of 9000 observations.\footnote{ We reran our regressions with several different samples of 9000 and found that our estimated coefficients did not significantly change; hence we believe this sample size is sufficient.}
 All in all, each observation in our regression data set consists the following variables: state ($i$), date 1 ($t$), date 2 ($s$), the log difference in electricity consumption between month 1 and month 2, the log difference in the price of electricity, the log difference in the price of coal, the number of CDDs for each date, the number of HDDs for each date, and the difference (in months) between dates 1 and 2.
@@
 
-Based on the OLS results reported in \hyperref[table:1]{Table 1}, we estimate the intertemporal elasticity of substitution for electricity consumption $\hat{\sigma}  = 0.609$ ($|t| > 24$) when accounting for all degree day covariates and state fixed effects.
-Interestingly, we find that the estimated coefficients for all three specifications do not differ when considering fixed effects.
-Additionally, as expected, the coefficients on the degree day covariates are symmetrical; that is, the coefficient on $CDD_{t}$ is approximately the same as the negative of that on $CDD_{s}$, and the same applies to $HDD_{t}$ and $HDD_{s}$.
-On the other hand, we found that electricity consumption seems to rise more in response to CDDs rather than HDDs.
-Lastly, we find that the sign on $\Delta_{t,s}$ is positive in all regressions; this implies that electricity consumption rises over time independent of price.
-
-To account for endogeneity in the OLS results, we provide results for our IV specification in \hyperref[table:2]{Table 2}.
-Here, we find a much larger estimate $\hat{\sigma}  = 11.430$ ($|t| > 2.1$) when considering all covariates and fixed effects.
-F-Statistics on all three specifications are significantly larger than 10, which suggests that the instruments are not weak \citep{SS1997}.
-With respect to the demand controls, we find results similar to those of OLS.
-State fixed effects do not appear to affect the estimates, demand increases over time, and CDDs raise electricity consumption more than HDDs.
-
-Finally, we control for nonlinear effects using a partially linear IV regression reported in \hyperref[table:3]{Table 3}.
-Here, we find results similar to that of OLS; $\hat{\sigma} = 0.413$ ($|t| > 48$) when considering all controls.
-The estimate of $\sigma$ without any controls is not significantly different from that in specifications with controls.
-However, all of these estimates are significantly different from the IV results; hence, the IV regressions do not appear to be robust.
-Consequently, we opt to use these estimates of $\sigma$ in our model.
-Since these estimates show $\hat{\sigma} \in (0,1)$, it appears that electricity consumption in different months complement one another.
-
-\begin{table}[!t] \centering 
+\begin{table}[t] \centering 
 	\caption{OLS Regression Results}
@@
 CDD$_t$ and HDD$_t$ refer to the total number of heating and cooling degree days in month $t$.
+We scale the coefficients on degree days for clarity.
 Robust standard errors are reported in parentheses.
@@
 
+Based on the OLS results reported in \hyperref[table:1]{Table 1}, we estimate the intertemporal elasticity of substitution for electricity consumption $\hat{\sigma}  = 0.609$ ($|t| > 24$) when accounting for all degree day covariates and state fixed effects.
+Interestingly, we find that the estimated coefficients for all three specifications do not differ when considering fixed effects.
+Additionally, as expected, the coefficients on the degree day covariates are symmetrical; that is, the coefficient on $CDD_{t}$ is approximately the same as the negative of that on $CDD_{s}$, and the same applies to $HDD_{t}$ and $HDD_{s}$.
+On the other hand, we found that electricity consumption seems to rise more in response to CDDs rather than HDDs.
+Lastly, we find that the sign on $\Delta_{t,s}$ is positive in all regressions; this implies that electricity consumption rises over time independent of price.
+
+To account for endogeneity in the OLS results, we provide results for our IV specification in \hyperref[table:2]{Table 2}.
+Here, we find a much larger estimate $\hat{\sigma}  = 11.430$ ($|t| > 2.1$) when considering all covariates and fixed effects.
+F-Statistics on all three specifications are significantly larger than 10, which suggests that the instruments are not weak \citep{SS1997}.
+With respect to the demand controls, we find results similar to those of OLS.
+State fixed effects do not appear to affect the estimates, demand increases over time, and CDDs raise electricity consumption more than HDDs.
+
+Finally, we control for nonlinear effects using a partially linear IV regression reported in \hyperref[table:3]{Table 3}.
+Here, we find results similar to that of OLS; $\hat{\sigma} = 0.413$ ($|t| > 48$) when considering all controls.
+The estimate of $\sigma$ without any controls is not significantly different from that in specifications with controls.
+However, all of these estimates are significantly different from the IV results; hence, the IV regressions do not appear to be robust.
+Consequently, we opt to use these estimates of $\sigma$ in our model.
+Since these estimates show $\hat{\sigma} \in (0,1)$, it appears that electricity consumption in different months complement one another.
+
 \pagebreak
-\clearpage
-
+\vspace{1em}
 \section{Discussion}
@@
 Hence, $\xi$ represents the percent of capacity utilized in each period; we assume coal uses 100\% of its capacity in both periods, while solar can access 100\% during peak hours and only 10\% during the off-peak.
-Finally, we set cost parameters (given in  \$ per MWh)  equal to LCOE estimates for 2023 from the \citet{EIALCOE}; specifically, we use estimates for "Solar PV" and "Coal with 30\% CCS" from Table 1b.
-In total, we have the following parameters.
+Finally, we set cost parameters (given in  \$ per MWh)  equal to LCOE estimates for 2023 from the \citet{EIALCOE}; specifically, we use estimates for "Solar PV" and "Coal with 30\% CCS" from Table 1b.\footnote{ The LCOE for a technology is equal to the sum of its lifetime costs divided by its lifetime energy output.
+While \citet{Joskow2011} explains the flaws of comparing generation technologies solely on the basis of LCOE, our use of this measure is unrelated to his critique.
+That is, he argues that the economic value an intermittent technology should account for when it produces electricity and the prices of electricity in those periods (see Table 2 of his paper).
+Our model does exactly this.}  In total, we have the following parameters.
 
@@
 Specifically, we held the price of solar capacity constant and varied the price of coal capacity from 50\% to 200\% of its original parametrized price.
-Then, we numerical differentiated $\log(X_1/X_2)$ with respect to $\log(c_2/c_1)$ to estimate the elasticity of substitution between solar and coal.\footnote{Instead, we could have generated variation in $\log(c_2/c_1)$ data by holding solar at a constant price and varying the price of coal capacity.
+Then, we numerical differentiated $\log(X_1/X_2)$ with respect to $\log(c_2/c_1)$ to estimate the elasticity of substitution between solar and coal.\footnote{ Instead, we could have generated variation in $\log(c_2/c_1)$ data by holding solar at a constant price and varying the price of coal capacity.
 However, this does not change the results.} This numerically computed elasticity of substitution between solar and coal power, $e_{solar,coal}$, is shown in the lower subplot.
@@
 Consequently, price plays bigger role than intermittency as $\sigma$ rises.
-This is further evident in the lower subplots; note that the numerical estimates of  $e$ rise and become more u-shaped as $\sigma$ rises.\footnote{Recall that $\sigma < 1$ implies that  electricity consumption in different periods are complements, $\sigma = 1$ implies to a Cobb-Douglas relationship, and $\sigma > 1$ implies that electricity consumption in different periods are substitutes.}  When consumers are less concerned about when they receive their energy, they are far more open to substituting between coal and solar power.
+This is further evident in the lower subplots; note that the numerical estimates of  $e$ rise and become more u-shaped as $\sigma$ rises.\footnote{ Recall that $\sigma < 1$ implies that  electricity consumption in different periods are complements, $\sigma = 1$ implies to a Cobb-Douglas relationship, and $\sigma > 1$ implies that electricity consumption in different periods are substitutes.}  When consumers are less concerned about when they receive their energy, they are far more open to substituting between coal and solar power.
 On the other hand, for lower values of $\sigma$, we find that the substitutability of coal and solar power diminishes as solar becomes progressively cheaper.
@@
 The first case is when no two technologies produce in the same period.
-That is, we can say that the output efficiency matrix, $\xi$, is diagonal without loss of generality; this further implies that we have a CES structure between technologies where the elasticity of substitution is same as that for consumers, $\sigma$.\footnote{A proof is provided in \hyperref[sec:CESspecialcase]{Appendix A.C}} Consequently, if one of these technologies creates negative externalities, the optimal solution is simply use a single instrument such as a Pigouvian tax.
+That is, we can say that the output efficiency matrix, $\xi$, is diagonal without loss of generality; this further implies that we have a CES structure between technologies where the elasticity of substitution is same as that for consumers, $\sigma$.\footnote{ A proof is provided in \hyperref[sec:CESspecialcase]{Appendix A.C}} Consequently, if one of these technologies creates negative externalities, the optimal solution is simply use a single instrument such as a Pigouvian tax.
 On the other hand, the second case occurs when all technologies produce in every period but with time-invariant output.
@@
 Essentially, with respect to reducing the use of coal power, there are diminishing returns to both pollution taxes and solar research subsidies.
-Hence, the pollution-reduction benefits of both instruments are convex.\footnote{To be more precise, we numerically compute the Hessian for $X_1$ with respect to $\beta_2$, the percent change in the output efficiency of solar from research, and the tax rate, $\tau$.
+Hence, the pollution-reduction benefits of both instruments are convex.\footnote{ To be more precise, we numerically compute the Hessian for $X_1$ with respect to $\beta_2$, the percent change in the output efficiency of solar from research, and the tax rate, $\tau$.
 We find that the Hessian is negative definite.
@@
 \subsection{Cobb-Douglas Case with Two Periods \& Two Technologies}
+\label{sec:cobbdoug}
 
@@
 
+	\bibitem[Papageorgiou et al.(2017)]{Pap}
+	Papageorgiou, C., Saarn, M., \& Schulte, P.
+(2017).
+Substitution between clean and dirty energy inputs: a macroeconomic perspective.(Author abstract).
+Review of Economics and Statistics, 99(2), 201–212.
+https://doi.org/10.1162/REST\_a\_00623
+
 	\bibitem[Reiss and White(2005)]{Reiss}
@@
 
-%	\bibitem[Warkins and Knight(1922)]{Knight}
-%	Watkins, G., \& Knight, F. (1922). Knight’s Risk, Uncertainty and Profit. The Quarterly Journal of Economics, 36(4), 682–690. https://doi.org/10.2307/1884757
-
-	%		\bibitem[Angel, Harris, and Spatt(2011)]{Angel} 
-	%		Angel, J.J., Harris, L.E., \& Spatt, C. S. (2011). Equity Trading in the 21st Century. Quarterly Journal Of Finance, 1(1), 1-53.
-
-	%		\bibitem[Stern(2012)]{Stern} 
-	%		Stern, D.
-(2012).
-“Interfuel Substitution: A Meta-Analysis.” Journal of Economic Surveys 26 (2): 307–331.
-\href{https://doi.org/10.1111/j.1467-6419.2010.00646.x}{https://doi.org/10.1111/j.1467-6419.2010.00646.x}.
-
 \end{thebibliography}

### 2019-05-01 code/matlab/simulation_april/sim_function.m

@@ -28,6 +28,11 @@ prices   = xi_mat\cost_mat;
 % Price Index
 P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
 
+if sigma == 1
+    P = 1;
+end
+        
+
 % Quantities
 Y = ((alpha'./prices).^(sigma)) * (budget/P);
 X = (xi_mat')\Y;

### 2019-05-03 code/matlab/simulation_april/main.m
Update simulation code
- fix sigma case
- regenerate plots

@@ -43,13 +43,13 @@ f_aa = (-sim_function([0.99, 1.0]) + 2*sim_function([1, 1]) ...
 f_bb = (-sim_function([1.0, 0.99]) + 2*sim_function([1, 1]) ...
     - sim_function([1.0, 0.99]))/(0.01^2);
 
+% g = tax X1
+g_ab = f_ab(1);
+g_aa = f_aa(1);
+g_bb = f_bb(1);
 
-X1_ab = f_ab(1);
-X1_aa = f_aa(1);
-X1_bb = f_bb(1);
+g_Hes = [g_aa, g_ab; g_ab, g_bb];
 
-X1_Hes = [X1_aa, X1_ab; X1_ab, X1_bb];
-
-
+eig(-g_Hes)
 
 

### 2019-05-03 code/matlab/simulation_april/sim_adoption_curve.m

@@ -43,7 +43,10 @@ for j = 1:m
 
         % Price Index
         P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
-
+        if sigma == 1
+            P = 1;
+        end
+        
         % Quantities
         Y = ((alpha'./prices).^(sigma)) * (budget/P);
           
@@ -136,6 +139,9 @@ for j = 1:m
 
         % Price Index
         P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
+        if sigma == 1
+            P = 1;
+        end
 
         % Quantities
         Y = ((alpha'./prices).^(sigma)) * (budget/P);

### 2019-05-03 code/matlab/simulation_april/sim_eos.m

@@ -43,7 +43,10 @@ for j = 1:m
 
         % Price Index
         P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
-
+        if sigma == 1
+            P = 1;
+        end
+        
         % Quantities
         Y = ((alpha'./prices).^(sigma)) * (budget/P);
            
@@ -100,7 +103,7 @@ ylim([0 15])
 grid('on')
 
 % Add horizontal line at 1
-e_1_line = plot([-1.4, -0.2], [1,1], 'LineStyle', '--', 'Color', 'k');
+e_1_line = plot([-1.5, -0.2], [1,1], 'LineStyle', '--', 'Color', 'k');
 legend([e_1_line], ' e = 1');
 
 % Save figure

### 2019-05-03 code/matlab/simulation_april/sim_opt_policy.m

@@ -1,0 +1,88 @@
+%% Optimal policy with just tax
+
+beta = 0;
+n = 10000;
+tau_range = linspace(0,140,n);
+results = zeros(n,1);
+
+
+for i = 1:n
+
+    tau = tau_range(i);
+    output = sim_function([1+beta, tau]);
+    welfare = output(3) + output(4) + output(5);
+    results(i) = welfare;
+
+end
+
+plot(tau_range, results)
+[M, I] = max(results);
+tau_range(I)
+
+
+%% Optimal policy with just subsidy
+
+tau = 0;
+n = 1000;
+beta_range = linspace(0,4,n);
+results = zeros(n,1);
+
+
+for j = 1:n
+
+    beta = beta_range(j);
+    output = sim_function([1+beta, tau]);
+    welfare = output(3) + output(4) + output(5);
+    results(j) = welfare;
+
+    if (output(1) < 0) || (output(2) < 0)
+        results(j) = nan;
+    end
+    
+end
+
+plot(beta_range, results)
+[M, I] = max(results);
+beta_range(I)
+
+
+%% Optimal policy with both
+
+n = 500;
+[tau_range, beta_range] = meshgrid(linspace(60,80,n), linspace(0,1,n));
+results = zeros(n,n);
+
+
+for i = 1:n      % tau
+    for j = 1:n  % beta
+           
+        tau = tau_range(i,j);
+        beta = beta_range(i,j);
+        output = sim_function([1+beta, tau]);
+        welfare = output(3) + output(4) + output(5);
+        results(i,j) = welfare;
+
+        if ((output(1) < 0) || (output(2) < 0) ||  ~isreal(welfare))
+            results(i,j) = nan;
+        end
+
+    end
+end
+
+disp('Done')
+
+mesh(tau_range, beta_range, results)
+
+%%
+
+% beta = 0 case
+[M, I] = max(results(1,:));
+tau_range(I)
+
+% general case
+[M, I] = max(results(:));
+[beta_range(I) tau_range(I)]
+
+
+
+

### 2019-05-03 code/matlab/simulation_april/sim_tax_subsidy.m

@@ -4,7 +4,7 @@ close all; clear; clc;
 
 % Simulation params
 n = 5000;
-research_multiplier = linspace(1,2,n);
+research_multiplier = linspace(1,5,n);
 sigma_range = [0.5];
 m = length(sigma_range);
 
@@ -42,7 +42,10 @@ for j = 1:m
 
         % Price Index
         P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
-
+        if sigma == 1
+            P = 1;
+        end
+        
         % Quantities
         Y = ((alpha'./prices).^(sigma)) * (budget/P);
            
@@ -78,7 +81,7 @@ end
 xlabel('Percent Change in the Efficiency of Solar (MWh)')
 ylabel('Coal Capacity (MWh)')
 xtickformat('percentage')
-xlim([0, 100])
+xlim([0, 350])
 grid('on')
 
 
@@ -86,7 +89,7 @@ grid('on')
 
 % Simulation params
 n = 5000;
-cost_multiplier = linspace(1,2,n);
+cost_multiplier = linspace(1,5,n);
 sigma_range = [0.5];
 m = length(sigma_range);
 
@@ -122,7 +125,10 @@ for j = 1:m
 
         % Price Index
         P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
-
+        if sigma == 1
+            P = 1;
+        end
+        
         % Quantities
         Y = ((alpha'./prices).^(sigma)) * (budget/P);
            
@@ -157,7 +163,7 @@ subplot(2,1,2)
 xlabel('Percent Increase in the Cost of Coal')
 ylabel('Coal Capacity (MWh)')
 xtickformat('percentage')
-xlim([0, 100])
+xlim([0, 350])
 grid('on')
 
 % Save figure

### 2019-05-03 documents/draft.tex
Update draft
- clean up results
- remove old discussion of externalities
- clean  up comparative statics
- formatting

@@
 
-\title{\singlespacing{\textbf{Efficient pollution abatement in electricity markets with intermittent renewable energy}}}
+\title{\singlespacing{\textbf{Optimal environmental policy for electricity markets with intermittent renewable energy}}}
 
@@
 
-\affil[]{\small{Rutgers University}}
-
-\date{\vspace{-1em}\small{\today}}
+\affil[]{Rutgers University}
+
+\date{\vspace{-1em}\today}
 
@@
 \begin{proposition}
-	Assume that, for all $i$ and $t$, we have $\xi_{i,t}, \alpha_t, c_i > 0$.
+	Assume that, for all  $i$ (technologies) and  $t$ (periods), we have $\xi_{i,t} > 0 \, , \alpha_t > 0 \, ,$ and $ c_i > 0$.
 Furthermore, suppose that $\xi$ is invertible.
@@
 Consequently, it seems intuitive that the comparative statics of $X_i$ follow through to $Z_t$.
-This intuition just happens to follow through even when other technologies are employed and there is demand in multiple periods.
+This intuition just happens to apply even when other technologies are employed and there is demand in multiple periods.
 Similarly, the comparative statics for the share parameters of the utility function, $\alpha$, travel in the opposite direction.
@@
 In our  \hyperref[sec:Discussion]{discussion}, we explain in detail why $\sigma$ is of interest; but, to summarize, $\sigma$ implicitly determines how well renewables can substitute for fossil energy.
-Specifically, if $\sigma \geq 1$, then electricity consumption in different periods are substitutes; consequently, fossil energy and renewable energy are highly substitutable.
+Specifically, if $\sigma > 1$, then electricity consumption in different periods are substitutes; consequently, fossil energy and renewable energy are highly substitutable.
 On the other hand, if $\sigma$ is around $0.5$, electricity consumption in different periods are complements; so, fossil and renewable energy are far less substitutable due to the effects of intermittency.
@@
 Interestingly, we find that the estimated coefficients for all three specifications do not differ when considering fixed effects.
+Moreover, these results slightly differ from the literature which finds estimates of $\hat{\sigma}$ to be between 0.1 and 0.25.
+However, this may be because their data focuses on industrial customers while our data concerns retail customers.
 Additionally, as expected, the coefficients on the degree day covariates are symmetrical; that is, the coefficient on $CDD_{t}$ is approximately the same as the negative of that on $CDD_{s}$, and the same applies to $HDD_{t}$ and $HDD_{s}$.
 On the other hand, we found that electricity consumption seems to rise more in response to CDDs rather than HDDs.
-Lastly, we find that the sign on $\Delta_{t,s}$ is positive in all regressions; this implies that electricity consumption rises over time independent of price.
+Lastly, we find that the sign on $\Delta_{t,s}$ is positive in all regressions, so electricity consumption rises over time independent of price.
+Specifically, fit (3) finds a coefficient of 0.001021 which implies that electricity consumption rises, on average, by 1.2\% per year.
 
@@
 F-Statistics on all three specifications are significantly larger than 10, which suggests that the instruments are not weak \citep{SS1997}.
+These results greatly differ from the literature's estimates; this difference may be the result of controlling for endogeneity.
 With respect to the demand controls, we find results similar to those of OLS.
-State fixed effects do not appear to affect the estimates, demand increases over time, and CDDs raise electricity consumption more than HDDs.
+State fixed effects do not appear to affect the estimates.
+Also, we find that electricity consumption seems to rise by about 1\% per year.
+However, with respect to CDDs, we find that the coefficients that are about 10 times larger than those in the OLS results.
+But, overall, we again find that demand increases over time, and CDDs raise electricity consumption more than HDDs.
 
@@
 Since these estimates show $\hat{\sigma} \in (0,1)$, it appears that electricity consumption in different months complement one another.
+We now discuss what this means for renewable energy policy in greater detail.
 
@@
 sectors [clean and dirty energy] are substitutable but not sufficiently so, preventing an environmental disaster requires a permanent policy intervention.
-Finally, when the two sectors are complementary, the only way to stave off a disaster is to stop long-run growth." However, note that, while our model sets the intertemporal elasticity of substitution for  electricity consumption $\sigma$ to a fixed value, we make no direct assumptions about the elasticity of substitution between different energy technologies.
+Finally, when the two sectors are complementary, the only way to stave off a disaster is to stop long-run growth." However, note that while our model sets the intertemporal elasticity of substitution for  electricity consumption $\sigma$ to a fixed value, we make no direct assumptions about the elasticity of substitution between different energy technologies.
 Rather, an interesting relationship regarding the substitutability/complementarity between technologies emerges indirectly as a result of intermittency.
@@
 
-Firstly, we let technology 1 be coal power and technology 2 be solar power; again, period $t$ represents peak hours and period $s$ represents off-peak hours.
+Firstly, we let technology 1 be coal power and technology 2 be solar power; let period $t$ represent peak hours and period $s$ represent off-peak hours.
 We assume that, holding prices equal, consumers prefer that 60\% of their energy arrive in period $t$ and the remaining 40\% arrive in period $s$; that is, we have $\alpha_t = 0.6$ and $\alpha_s = 0.4$.
-Additionally, we normalize the units of the quantities to a MWh basis.
+Next, we normalize all quantity units to a MWh basis.
 Hence, $\xi$ represents the percent of capacity utilized in each period; we assume coal uses 100\% of its capacity in both periods, while solar can access 100\% during peak hours and only 10\% during the off-peak.
-Finally, we set cost parameters (given in  \$ per MWh)  equal to LCOE estimates for 2023 from the \citet{EIALCOE}; specifically, we use estimates for "Solar PV" and "Coal with 30\% CCS" from Table 1b.\footnote{ The LCOE for a technology is equal to the sum of its lifetime costs divided by its lifetime energy output.
+Finally, we set cost parameters, given in  \$ per MWh, equal to LCOE estimates for 2023 from the \citet{EIALCOE}; specifically, we use estimates for "Solar PV" and "Coal with 30\% CCS" from Table 1b.\footnote{ The LCOE for a technology is equal to the sum of its lifetime costs divided by its lifetime energy output.
 While \citet{Joskow2011} explains the flaws of comparing generation technologies solely on the basis of LCOE, our use of this measure is unrelated to his critique.
-That is, he argues that the economic value an intermittent technology should account for when it produces electricity and the prices of electricity in those periods (see Table 2 of his paper).
-Our model does exactly this.}  In total, we have the following parameters.
+That is, he argues that the economic value an intermittent technology should also account for when it produces electricity and the prices of electricity in those periods (see Table 2 of his paper).
+Our model does exactly this; but, we still need to  use LCOE to parametrize the cost of developing capacity.
+}  In total, we have the following parameters.
 
 \begin{center}
-	\noindent \textbf{Example  1:} $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$. 
-	\label{Params: Example 1}
+	\noindent \textbf{Example  A:} $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$. 
+	\label{Params: Example A}
 \end{center}
 
-\noindent We begin by exploring the implied elasticity of substitution between these two technologies.
-Recall, for any two commodities $i$ and $j$,  the elasticity of substitution $e_{i,j}$ is given by:
+We begin by exploring the implied elasticity of substitution between these two technologies. Recall, for any two commodities $i$ and $j$,  the elasticity of substitution $e_{i,j}$ is given by:
 $$e_{i,j} = \frac{\partial \ln (X_1/ X_2)}{\partial \ln (c_2/c_1)}$$
 where $c$ is their prices.
-This relationship is of particular interest, because many applied and theoretical models studying renewable and fossil energy impose a CES production structure between the two.
-That is, they assume that $e$ is a fixed constant different pairs of generation technologies.
-In our model, this is not the case; while directly deriving the equation for $e$ in our model is analytically intractable, we numerically estimate it for varying costs and $\sigma$.
+This relationship is of particular interest, because many applied and theoretical models studying renewable and fossil energy impose a CES production structure between the two (see \citet{Pap}).
+That is, they assume that $e$ is a fixed constant between renewable and fossil energy.
+In our model, this is not the case; while directly deriving the equation for $e$ in our model is analytically intractable, we numerically estimate how it varies with $\ln (c_2/c_1)$ and $\sigma$.
 
@@
 These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
-We plot results for various values of the intertemporal elasticity of substition for electricity consumption $\sigma$, which is used in the consumer's CES utility function.
+We plot results for various values of the intertemporal elasticity of substition for electricity consumption $\sigma$ which is used in the consumer's CES utility function.
 In order to numerically estimate these relationships, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.5\, c_1, 2 \,c_1)$.
-Then, we obtained estimates of the elasticity of substition by numerically differentiating $\log(X_1/X_2)$ with respect to $-log(c_1, c_2)$.
+Then, we obtained estimates of the elasticity of substition by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1, c_2)$.
 That is, the elasticity of substitution between technology 1 and 2 is given by the slope of the upper subplot, and it is graphed in the lower subplot.
+For reference, we include a dashed line at $e = 1$ which is the elasticity of substitution that corresponds to a Cobb-Douglas structure.
 }     \\
@@
 We repeat this process with different values of $\sigma$, the elasticity of substitution in the consumer's utility function.
-Finally, we drop all observations of our numerical simulation that correspond to edge cases.
+Finally, we filter all observations of our numerical simulation that correspond to edge cases.
 
@@
 
-However, given the presence of intermittency, is there a better way to handle pollution?
+\textbf{More Here}
+
+%However, given the presence of intermittency, is there a better way to handle pollution?
 For example, \citet{Ace2012} model intermittency using a CES production function between clean and dirty energy.
 They find that both carbon taxes and research subsidies are necessary to promote long-run structural change in the energy production sector and avert a climate disaster.
-The necessity of both instruments is a consequence of their model spanning multiple periods; that is, assuming we have CES production structure between clean and dirty energy in a one-period model, a single instrument is enough to optimally handle externalities.
+
+%The necessity of both instruments is a consequence of their model spanning multiple periods; that is, assuming we have CES production structure between clean and dirty energy in a one-period model, a single instrument is enough to optimally handle externalities.
 \footnote{ Recall that, with a CES production structure, the optimal quantity of technology $i$ is given by $X_i = \left( \frac{\xi_i}{c_i} \right)^\sigma  \frac{B}{P}$ where $\xi_i$ is its output per unit, $B$ is the budget, and $P$ is the price index.
@@
 
-For clarity, let us first consider the cases in our framework where only one instrument is necessary.
+%For clarity, let us first consider the cases in our framework where only one instrument is necessary.
 The first case is when no two technologies produce in the same period.
@@
 
-In all other situations, where we have a mix of intermittent and constant-output technologies, using multiple instruments can be more effective than just one.
+%In all other situations, where we have a mix of intermittent and constant-output technologies, using multiple instruments can be more effective than just one.
 That is,  first suppose that research subsidies increase the output efficiency $\xi_i$ of some technology $i$.
 So, output efficiency is then given by $\xi_i \left( 1 + \beta_i \right)$ where $\beta_i$ is the percent increase in the output efficiency of technology $i$ as a result of research.
-Now, consider again a two-period setting with coal and solar with the same parameters as those given in \hyperref[Params: Example 1]{Example 1}.
+Now, consider again a two-period setting with coal and solar with the same parameters as those given in \hyperref[Params: Example A]{Example A}.
 As discussed earlier, one solution to externalities is to set a Pigouvian tax on coal equal to its marginal social damage.
 However, we may be able to reduce our reliance on coal in a more effective (welfare-maximizing) way by subsidizing research in solar as well.
-We can intuit this to be a potential solution based on \hyperref[fig:coaltech]{Figure 4}; in the first subplot, we show the effects of research into solar on the use of coal, while, in the second subplot, we show the effect of taxes on the use of coal.
-Essentially, with respect to reducing the use of coal power, there are diminishing returns to both pollution taxes and solar research subsidies.
-Hence, the pollution-reduction benefits of both instruments are convex.\footnote{ To be more precise, we numerically compute the Hessian for $X_1$ with respect to $\beta_2$, the percent change in the output efficiency of solar from research, and the tax rate, $\tau$.
+
+%We can intuit this to be a potential solution based on \hyperref[fig:coaltech]{Figure 4}.
+In the first subplot, we show the effects of improving solar output efficiency on the use of coal; in the second subplot, we show how the use of coal varies with its own price.
+Essentially, with respect to reducing the use of coal power, there are diminishing returns to both carbon taxes and solar research subsidies.
+Consequently, there must the be diminishing returns to the pollution-reduction benefits of each, since pollution scales with the amount of coal power employed.
+But, we should also consider a secondary benefit of carbon taxes -- the revenue they generate.
+
+%It is also important to note that carbon taxes have an added benefit -- they generate revenue.
+
+%Hence, the pollution-reduction benefits of both instruments are convex.
+Additionally, even when \footnote{ To be more precise, we numerically compute the Hessian for $X_1$ with respect to $\beta_2$, the percent change in the output efficiency of solar from research, and the tax rate, $\tau$.
 We find that the Hessian is negative definite.
-Consequently, since reducing $X_1$ creates welfare by reducing the social cost of pollution $\gamma X_1$, the Hessian of the benefits, $-\gamma X_1$ is positive definite and thus convex.} On the other hand, the deadweight loss created by taxation is generally convex; since research subsidies must be funded by tax revenue, its costs must necessarily be convex as well.
-In short, both instruments have convex benefits and costs, which implies that optimal policy is likely a combination of both.
-
-In total, besides for edge cases, this suggests that optimal policy may be to incorporate both
+Consequently, since reducing $X_1$ creates welfare by reducing the social cost of pollution $\gamma X_1$, the Hessian of the benefits, $-\gamma X_1$ is positive definite and thus convex.}
+
+%Additionally, the deadweight loss created by taxation is generally convex; since research subsidies must be funded by tax revenue, its costs must necessarily be convex as well.
+The remaining factors to consider are the secondary benefits to each instrument.
+Research subsidies increase consumer surplus by making energy cheaper; since producers have linear costs in our model, we can neglect the effect on producer surplus.
+Additionally,
+
+% CO2 emits 204 pounds of co2 per million btu
+% million btu = 0.29307107 mwh
+% ~700 pounds per Mwh
+
+% On the other hand, the deadweight loss created by taxation is generally convex; since research subsidies must be funded by tax revenue, its costs must necessarily be convex as well.
+In short, both instruments have convex benefits and costs.
+If we are not at an edge case, this implies that optimal policy is likely a combination of both.
+%\footnote{ To be more precise, we numerically compute the Hessian for $X_1$ with respect to $\beta_2$, the percent change in the output efficiency of solar from research, and the tax rate, $\tau$.
+We find that the Hessian is negative definite.
+Consequently, since reducing $X_1$ creates welfare by reducing the social cost of pollution $\gamma X_1$, the Hessian of the benefits, $-\gamma X_1$ is positive definite and thus convex.
+Note that we neglect here the change in surplus from the technological improvement $beta$ and the tax revenue from $\tau$.
+}
 
@@
 
-Throughout the paper, we considered coal and solar power as examples of fossil and renewable energy. Moreover, 
+\dots Throughout the paper, we considered coal and solar power as examples of fossil and renewable energy. Moreover, 
 For instance, we discussed how to handle pollution when energy sources are intermittent; we found that, rather than a standard Pigouvian tax, we would be better off using a combination of research subsidies and carbon taxes.
@@
 That is, even if externalities are global and research spills over, optimal policy differs on a local scale since generation technologies differ on a local scale.
-
-An aim for future research may be to develop a model of clean and dirty energy that incorporates both predictable and stochastic intermittency in a multi-period setting.
+\dots
+
+\dots An aim for future research may be to develop a model of clean and dirty energy that incorporates both predictable and stochastic intermittency in a multi-period setting.
 
@@
 	\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}+\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}>0
-	\end{pmatrix}
-	=
-	\begin{pmatrix}
-	< 0 \\
-	> 0 
-	\end{pmatrix} \\
+	\end{pmatrix}\\
 	\frac{\partial X_2}{\partial c} &= 
@@
 	\end{pmatrix}
-	=
-	\begin{pmatrix}
-	> 0 \\
-	< 0 
-	\end{pmatrix}
 	\end{align*}
@@
 Next, we derive comparative statics for each element of $\xi$.
-	\begin{alignat*}{2}
+	\begin{alignat*}{1}
 	\frac{\partial X_1}{\partial \xi} &= 
@@
 	\dfrac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}<0 & \dfrac{-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}<0 \\
-	\end{pmatrix}
-	&&=
-	\begin{pmatrix}
-	> 0 & > 0  \\
-	< 0 & < 0
-	\end{pmatrix} \\
+	\end{pmatrix}\\
 	\frac{\partial X_2}{\partial \xi} &= 
@@
 	\dfrac{\alpha _{s}\,c_{1}\,\xi _{\mathrm{1t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}>0& \dfrac{\alpha _{t}\,c_{1}\,\xi _{\mathrm{1s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} >0\\
-	\end{pmatrix}
-	&&=
-	\begin{pmatrix}
-	< 0 & < 0 \\
-	> 0 & > 0  
 	\end{pmatrix}
@@
 	\dfrac{\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}>0
-	\end{pmatrix}
-	=
-	\begin{pmatrix}
-	< 0 \\
-	> 0 
-	\end{pmatrix} \\
+	\end{pmatrix}\\
 	\frac{\partial X_2}{\partial \alpha} &= 
@@
 	Next, we derive the comparative statics for $Z$.
-	\begin{alignat*}{2}
+From our restrictions, we have $\xi_{1s}\xi_{2t} > \xi_{2s}\xi_{1t}$.
+All the results above follow from this inequality and the cost efficiency restrictions.
+	\begin{align*}
 	\frac{\partial Z_t}{\partial c} &= 
@@
 	\dfrac{-\alpha _{t}\,\xi _{\mathrm{1s}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}<0
-	\end{pmatrix}
-	&=
-	\begin{pmatrix}
-	> 0 \\
-	< 0 
-	\end{pmatrix} \\
+	\end{pmatrix}\\
 	\frac{\partial Z_s}{\partial c} &= 
@@
 	\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} >0
-	\end{pmatrix}
-	&=
-	\begin{pmatrix}
-	< 0 \\
-	> 0 
-	\end{pmatrix}
-	\end{alignat*}
-	From our restrictions, we have $\xi_{1s}\xi_{2t} > \xi_{2s}\xi_{1t}$, and all the results above follow from this. 
-	\begin{alignat*}{2}
+	\end{pmatrix}\\
 	\frac{\partial Z_t}{\partial \xi} &= 
@@
 	\dfrac{-\alpha _{t}\,\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} >0& \dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} >0\\
-	\end{pmatrix}
-	&&=
-	\begin{pmatrix}
-	< 0 & < 0  \\
-	> 0 & > 0
-	\end{pmatrix} \\
+	\end{pmatrix}\\
 	\frac{\partial Z_s}{\partial \xi} &= 
@@
 	\end{pmatrix}
-	&&=
-	\begin{pmatrix}
-	> 0 & > 0 \\
-	< 0 & < 0  
-	\end{pmatrix}
-	\end{alignat*}
+	\end{align*}
 	Again, recall that we have $c_1 \xi_{2t} - c_2 \xi_{1t} > 0$ and $c_2 \xi_{1s} - c_1 \xi_{2s} > 0$; the rest follows. And finally, we have:
@@
 	\begin{pmatrix}
-	\dfrac{-\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} \\
-	0
-	\end{pmatrix}
-	=
-	\begin{pmatrix}
-	> 0 \\
+	\dfrac{-\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} > 0  \\
 	0
 	\end{pmatrix} \\
-	\frac{\partial Z_s}{\partial \alpha}> 0 &= 
+	\frac{\partial Z_s}{\partial \alpha} &= 
 	\begin{pmatrix}
@@
 	\end{pmatrix}
-	=
-	\begin{pmatrix}
-	0 \\
-	> 0 
-	\end{pmatrix}
 	\end{align*}
@@
 This happens when no two technologies produce in the same period and we have the same number of periods as technologies.
-Additionally, the CES production function's elasticity parameter in this case will be equivalent to the consumer's CES utility elasticity parameter (the intertemporal elasticity of substitution for electricity consumption).
+Additionally, in this case, the CES production function's elasticity parameter  will be equivalent to the that of the consumer's CES utility function -- the intertemporal elasticity of substitution for electricity consumption.
 
@@
 Now, recall that the FOC for profit-maximization is given by $p = \xi^{-1} c$, hence we have $p_i = c_i / \xi_{i,i}$.
-And, finally, with the FOC for utility maximization, we have:
+Combining this equations with the FOC for utility maximization, we have:
 	\begin{align*}
 	\frac{Z_i}{Z_j} &= \left( \frac{\alpha_i p_j}{\alpha_j p_i} \right)^\sigma \\
-	\frac{ X_i }{X_j} &= \left( \frac{ \alpha_i p_j \xi_{j,j}^{1/\sigma} }{ \alpha_j p_i \xi_{i,i}^{1/\sigma} } \right)^\sigma \\
-	\frac{ X_i }{X_j} &= \left( \frac{ \alpha_i c_j \xi_{j,j}^{1/\sigma - 1} }{ \alpha_j c_i \xi_{i,i}^{1/\sigma - 1} } \right)^\sigma
+	\implies \frac{ X_i }{X_j} &= \left( \frac{ \alpha_i p_j \xi_{j,j}^{1/\sigma} }{ \alpha_j p_i \xi_{i,i}^{1/\sigma} } \right)^\sigma \\
+	\implies \frac{ X_i }{X_j} &= \left( \frac{ \alpha_i c_j \xi_{j,j}^{1/\sigma - 1} }{ \alpha_j c_i \xi_{i,i}^{1/\sigma - 1} } \right)^\sigma
 	\end{align*}
@@
 
-\section{Literature}
-
-\begin{itemize}
-	\item \cite{Delarue} develop a model that distinguishes between power and energy in order to split up costs and risks into fixed and variable factors. 
-	\item \cite{SB2018} look at interactions between different solar and wind installations (covar matrix), while many other energy models do not.
-\end{itemize}
+\pagebreak
 

### 2019-05-06 code/matlab/simulation_april/sim_batteries.m
Update matlab code and figures
- add sigma estimates with confidence intervals
- add code for batteries and elasticity simulation
- update all figures

@@ -1,0 +1,112 @@
+%% Elasticity of Substitution Sim with error bars on sigma estimate
+
+close all; clear; clc;
+
+% Simulation params
+n = 500;
+cost_multiplier = linspace(0.5,2,n);
+xi_2_values = [1, 0.1; 0.95, 0.15; 0.9, 0.2];
+m = 3;
+
+% Exogenous params
+c_1 = 104.3;
+c_2 = 50;
+alpha = [0.6, 0.4];
+xi_1  = [1,   1];
+xi_2  = [1, 0.1];
+budget = 1;
+sigma = 0.8847;
+
+figure('Renderer', 'painters', 'Position', [100 100 900 600])
+hold on;
+
+for j = 1:m
+    
+    xi_2 = xi_2_values(j,:);
+    results = zeros(n,2); 
+
+    for i = 1:n
+
+
+        phi   = (sigma - 1)/sigma;
+        x_1_cost_param = c_1*cost_multiplier(i);
+        x_2_cost_param = c_2;
+
+        % Prices
+        xi_mat   = [xi_1; xi_2];
+        cost_mat = [x_1_cost_param; x_2_cost_param];
+        prices   = xi_mat\cost_mat;
+
+        if any(prices<0)
+            continue
+        end
+
+        % Price Index
+        P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
+        if sigma == 1
+            P = 1;
+        end
+        
+        % Quantities
+        Y = ((alpha'./prices).^(sigma)) * (budget/P);
+           
+        X = (xi_mat')\Y;
+
+        results(i,:) = X';
+
+    end    
+
+    output = [];
+    output(1,:) = c_1*cost_multiplier'./c_2;
+    output(2,:) = results(:,1)./results(:,2);
+
+    % subset to positive quantities
+    ind = ~any(output <= 0);
+    output = output(:,ind);
+
+    % relationship between log prices and quantities
+    subplot(2,1,1);
+    hold on;
+    
+    plot(-log(output(1,:)), log(output(2,:)), ...
+        'LineWidth', 1.2);
+    
+    
+    % relationship between log prices and quantities
+    subplot(2,1,2);
+    hold on;
+    plot(-log(output(1,2:end)), ...
+        diff(log(output(2,:)))./diff(-log(output(1,:))), ...
[…]

### 2019-05-06 code/matlab/simulation_april/sim_elasticity.m

@@ -1,0 +1,108 @@
+%% Adoption with Respect to Price of Solar Sim
+
+close all; clear; clc;
+
+% Simulation params
+n = 500;
+cost_multiplier = linspace(1, 2, n);
+sigma_range = [0.8847 + 2*0.044, 0.8847, 0.8847 - 2*0.044];
+m = length(sigma_range);
+
+% Exogenous params
+c_1 = 104.3;
+c_2 = 50;
+alpha = [0.6, 0.4];
+xi_1  = [1,   1];
+xi_2  = [1, 0.1];
+budget = 1;
+
+
+figure('Renderer', 'painters', 'Position', [100 100 900 400])
+hold on;
+
+for j = 1:m
+    
+    sigma = sigma_range(j);
+    results = zeros(n,2); 
+
+    for i = 1:n
+
+
+        phi   = (sigma - 1)/sigma;
+        x_1_cost_param = c_1*cost_multiplier(i);
+        x_2_cost_param = c_2;
+
+        % Prices
+        xi_mat   = [xi_1; xi_2];
+        cost_mat = [x_1_cost_param; x_2_cost_param];
+        prices   = xi_mat\cost_mat;
+
+        if any(prices<0)
+            continue
+        end
+
+        % Price Index
+        P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
+        if sigma == 1
+            P = 1;
+        end
+        
+        % Quantities
+        Y = ((alpha'./prices).^(sigma)) * (budget/P);
+          
+        X = (xi_mat')\Y;
+
+        results(i,:) = X';
+
+    end    
+
+    output = [];
+    output(1,:) = results(:,1);
+    output(2,:) = results(:,2);
+    output(3,:) = cost_multiplier-1;
+    output(4,:) = c_1*cost_multiplier;
+    
+    % subset to positive quantities
+    ind = ~any(output(1:2,:) <= 0);
+    output = output(:,ind);
+
+    % elasticity of coal versus price
+    hold on;
+    
+    if sigma == 0.8847
+        plot(output(3,2:end)*100, ...
+            diff(log(output(1,:)))./diff(log(output(4,:))), ...
+            'LineWidth', 1, 'Color', 'k');
+    elseif sigma < 0.8846
+        plot(output(3,2:end)*100, ...
+            diff(log(output(1,:)))./diff(log(output(4,:))), ...
[…]

### 2019-05-06 code/matlab/simulation_april/sim_function.m

@@ -1,7 +1,7 @@
-function [ X ] = sim_function(v)
+function [ output ] = sim_function(v)
 % ========================================================================
-% SIM_FUNCTION finds the optimal quantity of X_1 given a multiplier for 
-% the output efficiency of solar and a tax rate on coal
+% SIM_FUNCTION finds the optimal X_1 given a multiplier 
+% for the output efficiency of solar and a tax rate on coal
 % ========================================================================
 % INPUT ARGUMENTS:
 %   v             (matrx)  the first entry is the multiplier on the output
@@ -13,12 +13,17 @@ alpha = [0.6, 0.4];
 xi_1  = [1, 1];
 xi_2  = [1, 0.1]*v(1);
 
-sigma = 0.5;
+sigma = 1;
 phi   = (sigma - 1)/sigma;
 budget = 1;
+gamma = 70;
 
-x_1_cost_param = 104.3*v(2);
-x_2_cost_param = 50;
+c_1 = 104.3;
+c_2 = 50;
+c_b = 0.75;
+
+x_1_cost_param = c_1+v(2);
+x_2_cost_param = c_2;
 
 % Prices
 xi_mat   = [xi_1; xi_2];
@@ -37,5 +42,18 @@ end
 Y = ((alpha'./prices).^(sigma)) * (budget/P);
 X = (xi_mat')\Y;
 
+% Tax revenue + Pollution costs 
+tax_revenue    = v(2) * X(1);
+pollution_dmg  = gamma*X(1);
+
+% Beta costs
+beta_cost = c_b*v(1);
+
+% Consumer surplus trim
+cons_surplus_trim = -alpha(1)*budget*log(prices(1)) + ...
+                    -alpha(2)*budget*log(prices(2));
+
+output = [X(1), X(2), ...
+    tax_revenue - pollution_dmg, cons_surplus_trim, -beta_cost];
 
 end

### 2019-05-06 code/matlab/simulation_april/sim_tax_subsidy.m

@@ -3,9 +3,9 @@
 close all; clear; clc;
 
 % Simulation params
-n = 5000;
-research_multiplier = linspace(1,5,n);
-sigma_range = [0.5];
+n = 10000;
+research_multiplier = linspace(1,3,n);
+sigma_range = [0.8847 + 2*0.044, 0.8847, 0.8847 - 2*0.044];
 m = length(sigma_range);
 
 % Exogenous params
@@ -68,29 +68,34 @@ for j = 1:m
     subplot(2,1,1);
     hold on;
     plot(output(3,:)*100, ...
-         output(1,:), ...
+        100*output(2,:)./(output(1,:) + output(2,:)), ...
         'LineWidth', 1);
     
 end
 
 %% Plot formatting
 
-% Add horizontal line at 1
-
 % Format subplot 1
-xlabel('Percent Change in the Efficiency of Solar (MWh)')
-ylabel('Coal Capacity (MWh)')
+legend('0.9727 (Upper 95% Confidence Limit)', '0.8847', ...
+    '0.7967 (Lower 95% Confidence Limit)')
+xlabel('Percent Change in the Output Efficiency of Solar')
+ylabel({'Solar Capacity', 'as a Fraction of All Capacity'})
 xtickformat('percentage')
-xlim([0, 350])
+xlim([0 200])
 grid('on')
+
+% Format legend
+[hleg,att] = legend('show');
+legend('Location', 'southeast')
+title(hleg, '\sigma')
 
 
 %% Optimal capacity of Coal with respect to own price
 
 % Simulation params
-n = 5000;
+n = 10000;
 cost_multiplier = linspace(1,5,n);
-sigma_range = [0.5];
+sigma_range = [0.8847 + 2*0.044, 0.8847, 0.8847 - 2*0.044];
 m = length(sigma_range);
 
 % Exogenous params
@@ -151,7 +156,7 @@ for j = 1:m
     subplot(2,1,2);
     hold on;
     plot(output(3,:)*100, ...
-         output(1,:), ...
+        100*output(2,:)./(output(1,:) + output(2,:)), ...
         'LineWidth', 1);
     
 end
@@ -160,10 +165,10 @@ end
 
 % Format subplot 2
 subplot(2,1,2)
-xlabel('Percent Increase in the Cost of Coal')
-ylabel('Coal Capacity (MWh)')
+xlabel('Percent Change in the Cost of Coal')
[…]

### 2019-05-06 documents/draft.tex
Update draft
- start abstract
- clean up intro
- fix empirical methodology explaination
- update data description
- update regression results
- update results discussion
- add discussion of externalities
- clean up discussion of substitution elasticities
- add proof of elasticity e special case

@@
 
-\title{\singlespacing{\textbf{Optimal environmental policy for electricity markets with intermittent renewable energy}}}
-
-\author[]{Saketh Aleti\thanks{I would like to thank Gal Hochman and Roger Klein for helpful comments and the Sun Grant for funding this project. }}
+\title{\singlespacing{\textbf{Efficient pollution abatement in electricity markets with intermittent renewable energy}}}
+
+\author[]{Saketh Aleti\thanks{I would like to thank Prof. Roger Klein for helpful comments and the Sun Grant for funding this project.} \, and Gal Hochman}
 
@@
 \maketitle
+
+% Syntax: \begin{addmargin}[<left indentation>]{<indentation>}
+\begin{addmargin}[0.5in]{0.5in}
+	\textit{ Use of renewable energy has increased greatly ... 
+		We evaluate renewable energy technologies in a partial equilibrium setting that integrates their production profiles with variation in the market price of electricity. 
+		In order to discount the ..., we use a representative agent that prefers to smooth their electricity consumption over time. 
+		Our results find a highly non-linear elasticity of substitution between intermittent and fossil energy. 
+		Furthermore, we find that standard environmental policy such as carbon taxes and renewable subsidies can have important distributional consequences as a result of intermittency.
+Subsidizing research that improves battery technologies can complement present policy and greatly increase the substitutability of renewable and fossil energy.
+	 }
+\end{addmargin}
 
@@
 On the other hand,  we model intermittency as defined above by allowing the output of renewable energy to differ between periods according to known function.
-But, for parsimony, we assume that the output of all technologies in each period does not vary stochastically; that is, we focus on intermittency rather than reliability.
-We then model the electricity sector using a representative firm that chooses and builds capacity from a set of electricity-generating technologies to maximize profit; some of these technologies are intermittent while others have constant output.
+For parsimony, we assume that the output of all technologies in each period does not vary stochastically; that is, we focus on intermittency rather than reliability.
+Next, we model the electricity sector using a representative firm that chooses and builds capacity from a set of electricity-generating technologies to maximize profit; some of these technologies are intermittent while others have constant output.
 Then, we consider a representative consumer who purchases varying quantities of electricity in each period in order to maximize utility.
-Generally, people prefer to spread their electricity consumption out over time; a standard CES function can capture this preference in a simple way.
-That is, we treat electricity as a heterogenous good which is differentiated by its delivery time; consumer utility is given by a CES function of electricity consumption in each period.\footnote{ The use of a CES function as such has been explored earlier by \citet{Schwarz}, \citet{Schwarz}, \citet{Herriges}, and \citet{KS1994}, \citet{Aubin}, and \citet{Moha2016}.
+Generally, people prefer to spread their electricity consumption out over time.
+We model this preference by using a CES function of electricity consumption differentiated by period.\footnote{ The use of a CES function in this way has been explored earlier by \citet{Schwarz}, \citet{Schwarz}, \citet{Herriges}, and \citet{KS1994}, \citet{Aubin}, and \citet{Moha2016}.
 Their papers empirically estimate the parameters for this function; we provide a more detailed discussion of the empirical literature in our \hyperref[sec:methodology]{Methodology}.} These two sides of the market reach an equilibrium through adjustments in prices of electricity in each period.
-All in all, we make many of the same assumptions that \citet{HH} do.
-We assume dynamic pricing,\footnote{ \citeauthor{HH} provide a motivation for models incorporating the dynamic pricing of electricity.
+All in all, we make many of the same assumptions that \citet{HH} do; we assume dynamic pricing,\footnote{ \citeauthor{HH} provide a motivation for models incorporating the dynamic pricing of electricity.
 They argue such approaches to pricing will become the norm with further technological advances and coming regulatory changes.} no load rationing, and positive prices.
@@
 Third, a significant amount of literature has assumed a CES structure between renewable and fossil energy (see \citet{Pap}); this assumption has been motivated, in part, by the need to capture imperfect substitutability between these two generation technologies as a result of intermittency.
-However, our direct model of intermittency disconfirms this assumption; the elasticity of substitution between these two energy technologies is far from linear as a \textit{consequence} of intermittency.
-In short, optimal taxes and subsidies along with the substitutability of renewable and fossil energy all vary with the state of the local energy market.
-Hence, we believe that optimal environmental policy must take into account local conditions far more than has previously been assumed.
+However, our direct model of intermittency disconfirms this assumption; the elasticity of substitution between these two energy technologies is far from constant as a \textit{consequence} of intermittency.
+Moreover, it varies with the prices and quantities of energy generation technologies employed.
+Hence, we believe that optimal environmental policy, such as pollution taxes and research subsidies, should take into account the technologies powering local energy markets in order to effectively handle externalities.
 
@@
 All three papers study real-time electricity pricing programs for industrial consumers using similar methodologies.
-Additionally, \citet{Aubin} also provide estimates of the $\sigma$ but using a different methodology; their results find $\sigma < 0$ which is impossible since it would imply upward-sloping demand curves under a CES structure.
+Additionally, \citet{Aubin} also provide estimates of the $\sigma$ but using a different methodology; their results find elasticity of substitution below 0.
+Under a CES structure, this is problematic, because it would imply upward-sloping demand curves.
 Finally, \citet{Moha2016} also empirically estimates the share parameters for a CES function of this form, but do not estimate the elasticity of substitution.
 
-A common flaw in these papers is that they do not account for endogeneity caused by a supply-side response to prices.
-For instance, coal plants are able to modify their generation between days; so, they might respond to an increase in future prices by storing coal until prices rise.
-That is, there may exist intertemporal substitution for electricity generation which would bias $\sigma$ downward unless controlled for.
-This is particularly important, because whether $\sigma$ is closer to 0.1 or 1 can make a significant difference with respect to the practical implications of our model.
-
-Consequently, we provide our own estimates of $\sigma$ estimated on a monthly basis.
-Regarding the time scale, this decision is primarily due to data limitations, since we do  not have access to the proprietary data on real-time pricing experiments which the past literature has used.
+Overall, the past literature has approached the estimation of $\sigma$ by running regressions with variants of the CES demand equation.
+We are concerned about endogeneity, because producers may intertemporally substitute electricity generation.
+For instance, during the oil crisis of 1973, refineries increased gasoline stocks expecting future prices to be higher \citep{genie}.
+The existence of such behavior implies that estimates of $\sigma$ would be biased downwards unless we properly control for endogeneity.
+This is particularly important because whether $\sigma$ is closer to 0.1 or 1 significantly change the practical implications of our model.
+
+So, we take a different approach by using a supply instrument to identify the CES demand parameters.
+Specifically, we use coal prices which affect the supply of electricity but not the demand.
+Furthermore, we estimate $\sigma$ on a monthly basis.
+This decision is primarily due to data limitations, since we do  not have access to the proprietary data on real-time pricing experiments which the past literature has used.
 Although we are interested in understanding intertemporal substitution over a shorter time scale (since intermittency plays a larger role in shorter periods), estimates of $\sigma$ on a monthly basis may still be applicable on a smaller time frame.
@@
 Hence, we expect our estimates of $\sigma$ on a monthly basis to not be far from estimates on shorter time scales.
+At the same time, our estimates of $\sigma$ will likely be larger than that of the literature, because we are controlling for endogeneity.
 We now define our econometric methodology in detail.
@@
 Finally, we collect data on HDDs and CDDs from the NOAA's \citet{CPC} for the same panel.
-Then, we merge these three data sets and trim 1\% of outliers for a total of $826$ observations for each month and state.
+Then, we merge these three data sets and trim 1\% of outliers for a total of $818$ observations for each month and state.
 We use this preliminary data set to construct the data required for our regressions.
@@
 Hence, we construct each row in our regression data set using unique combinations of $t,s$ where $t \neq s$ for each state $i$.
-Due to the number of potential combinations and thus observations, we restrict our data set to a random sample of 9000 observations.\footnote{ We reran our regressions with several different samples of 9000 and found that our estimated coefficients did not significantly change; hence we believe this sample size is sufficient.}
-All in all, each observation in our regression data set consists the following variables: state ($i$), date 1 ($t$), date 2 ($s$), the log difference in electricity consumption between month 1 and month 2, the log difference in the price of electricity, the log difference in the price of coal, the number of CDDs for each date, the number of HDDs for each date, and the difference (in months) between dates 1 and 2.
+This gives us a total of 6817 observations.
+All in all, each observation in our regression data set consists the following variables: state ($i$), date 1 ($t$), date 2 ($s$), the log difference in electricity consumption between month 1 and month 2, the log difference in the price of electricity, the log difference in the price of coal, the number of CDDs for each date, the number of HDDs for each date, and the difference in months between dates 1 and 2.
 
@@
 		\hline \\[-1.8ex] 
-		$-\ln (P_{t,i} / P_{s,i})$ & 0.751$^{***}$ & 0.481$^{***}$ & 0.607$^{***}$ & 0.750$^{***}$ & 0.481$^{**}$ & 0.607$^{***}$ \\ 
+		$-\ln (P_{t,i} / P_{s,i})$ & 0.937$^{***}$ & 1.075$^{***}$ & 1.098$^{***}$ & 1.074$^{***}$ & 1.263$^{***}$ & 1.305$^{***}$ \\ 
 		& (0.030) & (0.026) & (0.026) & (0.224) & (0.172) & (0.169) \\ 
 		& & & & & & \\ 
-		$\Delta_{t,s}$ &  &  & 0.001$^{***}$ &  &  & 0.001$^{***}$ \\ 
-		&  &  & (0.0001) &  &  & (0.0002) \\ 
+		$\Delta_{t,s}$ &  &  & 0.0005$^{***}$ &  &  & 0.0065$^{*}$ \\ 
+		&  &  & (0.0001) &  &  & (0.0003) \\ 
 		& & & & & & \\ 
-		CDD$_t$ &  & 0.990$^{***}$ & 1.003$^{***}$ &  & 0.990$^{***}$ & 1.002$^{***}$ \\ 
-		$\quad(\times 1000^{-1})$&  & (0.016) & (0.016) &  & (0.087) & (0.086) \\ 
+		CDD$_t$ &  & 1.156$^{***}$ & 1.163$^{***}$ &  & 1.164$^{***}$ & 1.174$^{***}$ \\
+
+		$\quad(\times 1000^{-1})$ &  & (0.017) & (0.017) &  & (0.072) & (0.075) \\ 
 		& & & & & & \\ 
-		CDD$_s$ &  & $-$0.999$^{***}$ & $-$1.011$^{***}$ &  & $-$0.999$^{***}$ & $-$1.012$^{***}$ \\ 
-		$\quad(\times 1000^{-1})$&  & (0.016) & (0.016) &  & (0.087) & (0.085) \\ 
+		CDD$_s$ &  & $-$1.143$^{***}$ & $-$1.158$^{***}$ &  & $-$1.200$^{***}$ & $-$1.224$^{***}$ \\ 
+		$\quad(\times 1000^{-1})$&  & (0.025) & (0.026) &  & (0.096) & (0.098) \\ 
 		& & & & & & \\ 
-		HDD$_t$ &  & 0.306$^{***}$ & 0.294$^{***}$ &  & 0.307$^{***}$ & 0.295$^{***}$ \\ 
-		$\quad(\times 1000^{-1})$&  & (0.005) & (0.005) &  & (0.030) & (0.030) \\ 
+		HDD$_t$  &  & 0.246$^{***}$ & 0.245$^{***}$ &  & 0.237$^{***}$ & 0.236$^{***}$ \\ 
+		$\quad(\times 1000^{-1})$ &  & (0.007) & (0.007) &  & (0.031) & (0.031) \\ 
 		& & & & & & \\ 
-		HDD$_s$ &  & $-$0.309$^{***}$ & $-$0.296$^{***}$ &  & $-$0.308$^{***}$ & $-$0.295$^{***}$ \\ 
-		$\quad(\times 1000^{-1})$&  & (0.005) & (0.005) &  & (0.029) & (0.029) \\ 
+		HDD$_s$ &  & $-$0.267$^{***}$ & $-$0.265$^{***}$ &  & $-$0.268$^{***}$ & $-$0.263$^{***}$ \\ 
+		$\quad(\times 1000^{-1})$ &  & (0.008) & (0.008) &  & (0.038) & (0.038) \\ 
 		& & & & & & \\ 
-		Intercept & 0.001 & 0.002 & 0.002 &  &  &  \\ 
-		& (0.003) & (0.006) & (0.006) &  &  &  \\ 
-		& & & & & & \\  [0.9ex]
+		Intercept & 0.028$^{***}$ & 0.012$^{*}$ & 0.026$^{***}$ &  &  &  \\ 
+		& (0.004) & (0.006) & (0.007) &  &  &  \\  [0.9ex]
 		\hline \\[-1.8ex] 
 		State FEs &   &   &   & Yes & Yes & Yes \\ 
-		Observations & 9,000 & 9,000 & 9,000 & 9,000 & 9,000 & 9,000 \\ 
-		R$^{2}$ & 0.070 & 0.580 & 0.596 & 0.070 & 0.580 & 0.596 \\ 
-		Adjusted R$^{2}$ & 0.070 & 0.579 & 0.596 & 0.065 & 0.577 & 0.594 \\ [0.5ex]
+		Observations & 6,817 & 6,817 & 6,817 & 6,817 & 6,817 & 6,817 \\ 
+		R$^{2}$ & 0.079 & 0.507 & 0.508 & 0.092 & 0.521 & 0.524 \\ 
+		Adjusted R$^{2}$ & 0.079 & 0.506 & 0.508 & 0.085 & 0.518 & 0.520 \\  
+		F Statistic & 582$^{***}$  & 1399$^{***}$  & 1172$^{***}$ & 685$^{***}$  & 1474$^{***}$  & 1241$^{***}$  \\ [0.5ex]
 		\hline 
 		\hline \\[-1.8ex] 
-		\multicolumn{7}{@{}p{40em}@{}}{\textit{Note: } The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
+		\multicolumn{7}{@{}p{41.4em}@{}}{\textit{Note: } The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
 The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state; as discussed in the Data section, we take a random sample of 9000 observations from the data.
-The coefficient on $\ln (P_{t,i} / P_{s,i})$ is an estimate of $-\sigma$.
+The coefficient on $-\ln (P_{t,i} / P_{s,i})$ is the estimate of $\sigma$.
 The variable $\Delta_{t,s}$ is the difference in months between periods $t$ and $s$.
@@
 		\hline \\[-1.8ex] 
-		$ \ln (C_{t,i} / C_{s,i})$ & $-$0.060$^{***}$ & 0.004$^{*}$ & 0.004$^{*}$ &  &  &  \\ 
+		$ \ln (C_{t,i} / C_{s,i})$ & $-$0.042$^{***}$ & $-$0.018$^{***}$ & $-$0.018$^{***}$ &  &  &  \\ 
 		& (0.002) & (0.002) & (0.002) &  &  &  \\ 
 		& & & & & & \\ 
-		$-\ln (P_{t,i} / P_{s,i})$ &  &  &  & 0.711$^{***}$ & 13.987 & 11.430$^{*}$ \\ 
-		&  &  &  & (0.106) & (8.384) & (5.330) \\ 
+		$-\ln (P_{t,i} / P_{s,i})$ &  &  &  & 2.978$^{***}$ & 5.896$^{***}$ & 5.818$^{***}$ \\ 
+		 &  &  &  & (0.180) & (0.548) & (0.524) \\ 
 		& & & & & & \\ 
-		$\Delta_{t,s}$  &  & 0.001$^{***}$ & 0.001$^{***}$ &  &  & 0.007$^{*}$ \\ 
-		&  & (0.00002) & (0.00002) &  &  & (0.003) \\ 
+		$\Delta_{t,s}$  &  &  & 0.001$^{***}$ &  &  & 0.003$^{***}$ \\ 
+		 &  &  & (0.00004) &  &  & (0.0004) \\ 
 		& & & & & & \\ 
-		CDD$_t$  &  & 0.151$^{***}$ & 0.151$^{***}$ &  & 3.064$^{*}$ & 2.620$^{**}$ \\ 
-		$\quad(\times 1000^{-1})$&  & (0.007) & (0.007) &  & (1.288) & (0.798) \\ 
+		CDD$_t$  &  & 0.100$^{***}$ & 0.105$^{***}$ &  & 1.637$^{***}$ & 1.657$^{***}$ \\ 
+		$\quad(\times 1000^{-1})$ &  & (0.006) & (0.006) &  & (0.068) & (0.067) \\ 
 		& & & & & & \\ 
-		CDD$_s$  &  & $-$0.149$^{***}$ & $-$0.149$^{***}$ &  & $-$3.034$^{*}$ & $-$2.609$^{***}$ \\ 
-		$\quad(\times 1000^{-1})$&  & (0.007) & (0.007) &  & (1.264) & (0.788) \\ 
+		CDD$_s$ &  & $-$0.096$^{***}$ & $-$0.114$^{***}$ &  & $-$1.688$^{***}$ & $-$1.783$^{***}$ \\ 
+		$\quad(\times 1000^{-1})$  &  & (0.009) & (0.009) &  & (0.079) & (0.084) \\ 
 		& & & & & & \\ 
-		HDD$_t$  &  & $-$0.057$^{***}$ & $-$0.057$^{***}$ &  & $-$0.407 & $-$0.311 \\ 
-		$\quad(\times 1000^{-1})$&  & (0.003) & (0.003) &  & (0.447) & (0.301) \\ 
+		HDD$_t$  &  & $-$0.048$^{***}$ & $-$0.048$^{***}$ &  & 0.001 & 0.007 \\ 
+		$\quad(\times 1000^{-1})$ &  & (0.003) & (0.003) &  & (0.031) & (0.030) \\ 
 		& & & & & & \\ 
-		HDD$_s$  &  & 0.058$^{***}$ & 0.058$^{***}$ &  & 0.423 & 0.324 \\ 
-		$\quad(\times 1000^{-1})$&  & (0.003) & (0.003) &  & (0.458) & (0.308) \\ [0.9ex]
+		HDD$_s$  &  & 0.053$^{***}$ & 0.055$^{***}$ &  & 0.0001 & 0.007 \\ 
+		$\quad(\times 1000^{-1})$  &  & (0.003) & (0.003) &  & (0.035) & (0.034) \\   [0.9ex]
 		\hline \\[-1.8ex] 
 		State FEs &  Yes & Yes  & Yes  & Yes & Yes & Yes \\ 
-		Observations & 9,000 & 9,000 & 9,000 & 9,000 & 9,000 & 9,000 \\ 
-		R$^{2}$          & 0.066 & 0.441 & 0.441 & & &  \\ 
-		Adjusted R$^{2}$ & 0.066 & 0.441 & 0.441 & & &  \\ 
-		F Statistic & 678$^{***}$ & 1,213$^{***}$ & 1,197$^{***}$  &  &  &  \\ 
+		Observations & 6817 & 6817 & 6817 & 6817 & 6817 & 6817 \\ 
+		R$^{2}$ & 0.061 & 0.264 & 0.294 &  &  & \\ 
+		Adjusted R$^{2}$ & 0.061 & 0.264 & 0.293 & &  &  \\ 
+		F Statistic & 443$^{***}$  & 489$^{***}$ & 472$^{***}$  &  &  &  \\ 
 		\hline 
 		\hline \\[-1.8ex] 
-		\multicolumn{7}{@{}p{39.2em}@{}}{\textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions.
+		\multicolumn{7}{@{}p{41.5em}@{}}{\textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions.
 The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
@@
 		\hline \\[-1.8ex] 
-		$\hat{\sigma} $ & 0.5676$^{***}$ & 0.4511$^{***}$ & 0.4129$^{***}$ \\ 
-		& (0.1036) & (0.0042) & (0.0085) \\ [0.9ex]
+		$\hat{\sigma} $ & 2.9976$^{***}$ & 1.2123$^{***}$ & 0.8847$^{***}$ \\ 
+		& (0.169) & (0.052) & (0.044) \\ [0.9ex]
 		\hline \\[-1.8ex] 
@@
 		Degree Day Controls &   & Yes  & Yes  \\ 
-		Observations & 9,000 & 9,000 & 9,000 \\
+		Observations & 6817 & 6817 & 6817 \\
 		\hline 
 		\hline \\[-1.8ex] 
-		\multicolumn{4}{@{}p{36em}@{}}{\textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions.
+		\multicolumn{4}{@{}p{37em}@{}}{\textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions.
 The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
@@
 
-Based on the OLS results reported in \hyperref[table:1]{Table 1}, we estimate the intertemporal elasticity of substitution for electricity consumption $\hat{\sigma}  = 0.609$ ($|t| > 24$) when accounting for all degree day covariates and state fixed effects.
-Interestingly, we find that the estimated coefficients for all three specifications do not differ when considering fixed effects.
-Moreover, these results slightly differ from the literature which finds estimates of $\hat{\sigma}$ to be between 0.1 and 0.25.
-However, this may be because their data focuses on industrial customers while our data concerns retail customers.
-Additionally, as expected, the coefficients on the degree day covariates are symmetrical; that is, the coefficient on $CDD_{t}$ is approximately the same as the negative of that on $CDD_{s}$, and the same applies to $HDD_{t}$ and $HDD_{s}$.
-On the other hand, we found that electricity consumption seems to rise more in response to CDDs rather than HDDs.
-Lastly, we find that the sign on $\Delta_{t,s}$ is positive in all regressions, so electricity consumption rises over time independent of price.
-Specifically, fit (3) finds a coefficient of 0.001021 which implies that electricity consumption rises, on average, by 1.2\% per year.
+Based on the OLS results reported in \hyperref[table:1]{Table 1}, we estimate the intertemporal elasticity of substitution for electricity consumption $\hat{\sigma}  = 1.305$ ($|t| > 24$) when accounting for all degree day covariates and state fixed effects.
+Additionally, we find that accounting for cooling and heating degree days captures a large amount of variation in demand for electricity; in the fixed effects regressions, adding these controls raises adjusted $R^2$ from 8.5\% to 51.8\%.
+Also, as expected, the coefficients on the degree day covariates are symmetrical; that is, the coefficient on $CDD_{t}$ is approximately the same as the negative of that on $CDD_{s}$, and the same applies to $HDD_{t}$ and $HDD_{s}$.
+\footnote{It is important to note that the reason they are not perfectly equal is because our regression data consists of each unique \textit{combination} of $(t,s)$ for each $i$; that is, if we have an arbitrary observation $(t,s,i)$ in our data, then $(s,t,i)$ does not also appear.
+Including these observations would not affect $\sigma$ and they also don't add any further information to our regression.
+However, they would make the magnitude of the estimated coefficients for  CDD$_t$ and CDD$_s$ equivalent (and likewise for HDDs).
+}  Furthermore, we found that electricity consumption seems to rise more in response to CDDs rather than HDDs.
+Next, we find that the sign on $\Delta_{t,s}$ is positive in all regressions, so electricity consumption rises over time independent of price.
+Specifically, fit (6) finds a coefficient of $0.000655$ which implies that electricity consumption rises, on average, by $\approx 0.7\%$ per year.
+Finally, adding state fixed effects seems to raise the estimates of $\sigma$ for all fits.
 
 To account for endogeneity in the OLS results, we provide results for our IV specification in \hyperref[table:2]{Table 2}.
-Here, we find a much larger estimate $\hat{\sigma}  = 11.430$ ($|t| > 2.1$) when considering all covariates and fixed effects.
+Here, we find a much larger estimate of $\hat{\sigma}  = 5.818$ ($|t| > 11.1$) when considering all covariates and fixed effects.
 F-Statistics on all three specifications are significantly larger than 10, which suggests that the instruments are not weak \citep{SS1997}.
-These results greatly differ from the literature's estimates; this difference may be the result of controlling for endogeneity.
-With respect to the demand controls, we find results similar to those of OLS.
-State fixed effects do not appear to affect the estimates.
-Also, we find that electricity consumption seems to rise by about 1\% per year.
-However, with respect to CDDs, we find that the coefficients that are about 10 times larger than those in the OLS results.
-But, overall, we again find that demand increases over time, and CDDs raise electricity consumption more than HDDs.
+These results greatly differ from the literature's estimates probably as a consequence of controlling for endogeneity.
+That is, ignoring variation on the supply side would bias OLS estimates for the effect of price on demand downwards; by controlling for this, we find larger estimates of $\sigma$ which is expected.
+Next, with respect to the demand controls, we find results similar to those of OLS.
+The magnitudes of the coefficients on DDs do not appear to be significantly different.
+Furthermore, we again find that CDDs affect electricity consumption more than HDDs.
+But, this time, the coefficients on heating degree days do not appear to be significant.
+Additionally, in contrast with the OLS results, we find a much larger estimate for the coefficient on $\Delta_{t,s}$ of $0.003$; this implies that electricity consumption seems to rise by about 3.65\% per year.
+So, overall, our IV results suggest much higher estimates of $\sigma$.
 
 Finally, we control for nonlinear effects using a partially linear IV regression reported in \hyperref[table:3]{Table 3}.
-Here, we find results similar to that of OLS; $\hat{\sigma} = 0.413$ ($|t| > 48$) when considering all controls.
-The estimate of $\sigma$ without any controls is not significantly different from that in specifications with controls.
-However, all of these estimates are significantly different from the IV results; hence, the IV regressions do not appear to be robust.
-Consequently, we opt to use these estimates of $\sigma$ in our model.
-Since these estimates show $\hat{\sigma} \in (0,1)$, it appears that electricity consumption in different months complement one another.
+Here, we find much smaller results than 2SLS when controlling for all possible covariates.
+Specifically, in fit (3), we have $\hat{\sigma} = 0.8847$ ($|t| > 20$).
+The estimates of $\sigma$ with less controls are much larger.
+However, based on the OLS and IV results, it seems that both the time control and degree day controls are significant.
+Hence, fit (3) is likely the most appropriate specification.
+Additionally, all of these estimates are significantly different from the 2SLS results which suggests that the 2SLS results are not robust.
+To be precise, our controls and instrument likely have non-linear effects on price and quantity which cannot be captured by linear models; this may explain why the 2SLS results differ significantly from these semiparametric results.
+Alternatively, this difference may also be because the errors in our regressions are not Gaussian.
+In any case, we  believe that our third semiparametric fit, $\hat{\sigma} = 0.8847$, is the most robust estimate of $\sigma$.
 We now discuss what this means for renewable energy policy in greater detail.
@@
 
-\subsubsection{The Elasticity of Substitution between Renewable and Fossil Energy}
+\subsection{The Elasticity of Substitution between Renewable and Fossil Energy}
 
@@
 In particular, we are concerned with how $\sigma$ affects the substitutability of fossil and renewable energy.
-This is particularly important, because sufficient substitutability between these two technologies is required to transition to greener economy in the future.
-For instance, \citet{Ace2012} argues that, ``When the two
+This is important, because sufficient substitutability between these two technologies is required to transition into greener economy in the future.
+For instance, \citet{Ace2012} provide a model where they argue that, ``When the two
 sectors [clean and dirty energy] are substitutable but not sufficiently so, preventing an environmental disaster requires a permanent policy intervention.
 Finally, when the two sectors are complementary, the only way to stave off a disaster is to stop long-run growth." However, note that while our model sets the intertemporal elasticity of substitution for  electricity consumption $\sigma$ to a fixed value, we make no direct assumptions about the elasticity of substitution between different energy technologies.
-Rather, an interesting relationship regarding the substitutability/complementarity between technologies emerges indirectly as a result of intermittency.
-To illustrate this, we now proceed with the numerical model.
+Instead, this latter elasticity emerges as an indirect result of substitution between electricity consumption in periods.
+To illustrate this, we parametrize and estimate our model numerically.
 
 Firstly, we let technology 1 be coal power and technology 2 be solar power; let period $t$ represent peak hours and period $s$ represent off-peak hours.
-We assume that, holding prices equal, consumers prefer that 60\% of their energy arrive in period $t$ and the remaining 40\% arrive in period $s$; that is, we have $\alpha_t = 0.6$ and $\alpha_s = 0.4$.
+We assume that, holding prices equal, consumers prefer that approximately 60\% of their energy arrive in period $t$ and the remaining 40\% arrive in period $s$; that is, we have $\alpha_t = 0.6$ and $\alpha_s = 0.4$.
 Next, we normalize all quantity units to a MWh basis.
@@
 We begin by exploring the implied elasticity of substitution between these two technologies. Recall, for any two commodities $i$ and $j$,  the elasticity of substitution $e_{i,j}$ is given by:
-$$e_{i,j} = \frac{\partial \ln (X_1/ X_2)}{\partial \ln (c_2/c_1)}$$
+$$e_{i,j} = \frac{\partial \ln (X_i/ X_j)}{\partial \ln (c_j/c_i)}$$
 where $c$ is their prices.
@@
 That is, they assume that $e$ is a fixed constant between renewable and fossil energy.
-In our model, this is not the case; while directly deriving the equation for $e$ in our model is analytically intractable, we numerically estimate how it varies with $\ln (c_2/c_1)$ and $\sigma$.
+In our model, this is not the case; while directly deriving the equation for $e_{1,2}$ in our model is analytically intractable, we numerically estimate how it varies with $\ln (c_2/c_1)$ and $\sigma$.
 
 \begin{table}[t]
-	\caption*{\textbf{Figure 1:} The Elasticity of Substition Between Solar and Coal} 
+	\caption*{\textbf{Figure 1:} The Elasticity of Substition between Solar and Coal} 
 	\label{fig:eosnum}
@@
 		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_elasticity} \\
-		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } The y-axis of the first plot is equivalent to $\log(X_1/X_2)$ and the x-axis of both plots is equivalent to  $\log(c_2/c_1)$.
+		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } Technology 1 is coal and technology 2 is solar.
 The legend in the upper subplot also applies to the lower subplot.
 These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
-We plot results for various values of the intertemporal elasticity of substition for electricity consumption $\sigma$ which is used in the consumer's CES utility function.
-In order to numerically estimate these relationships, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.5\, c_1, 2 \,c_1)$.
+Furthermore, we set the parameter for the intertemporal elasticity of substition for electricity consumption equal to our estimate $\hat{\sigma} = 0.8847$.
+In order to generate these numerical, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.5\, c_1, 2 \,c_1)$.
 Then, we obtained estimates of the elasticity of substition by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1, c_2)$.
 That is, the elasticity of substitution  between technology 1 and 2 is given by the slope of the upper subplot, and it is graphed in the lower subplot.
-For reference, we include a dashed line at $e = 1$ which is the elasticity of substitution that corresponds to a Cobb-Douglas structure.
+Finally, we repeat this procedure with $\sigma$ equal to two standard deviations above and below its estimated value; that is, the dashed lines represent  $\sigma = 0.8847 \pm 2(0.044)$.
 }     \\
@@
 
-We plot our numerical estimates of $e_{solar, coal}$, the elasticity of substitution between solar and coal power, in \hyperref[fig:eosnum]{Figure 1}.
+We plot our numerical estimates of $e_{1, 2}$, the elasticity of substitution between solar and coal power, in \hyperref[fig:eosnum]{Figure 1}.
 These results were generated by computing the optimal quantities of each technology given a range of prices.
@@
 We repeat this process with different values of $\sigma$, the elasticity of substitution in the consumer's utility function.
-Finally, we filter all observations of our numerical simulation that correspond to edge cases.
-
-Our results show that $e$ is clearly non-linear, hence assuming a CES production structure between clean and dirty energy is not an accurate assumption.
-Furthermore, the relationship between log quantities and log prices becomes increasingly non-linear as $\sigma$ rises.
-This is somewhat intuitive; when energy consumption can be substituted across periods, the market is more sensitive to the cost efficiency of technologies and less sensitive to when they produce.
-For instance, suppose we had two technologies that each produced in a different period; if consumers are less willing to substitute consumption across periods, both technologies are likely to be  employed, On the other hand, when consumers are open to substitution,they will simply consume the majority of their electricity in whichever period it is most cost effective to do so.
-Consequently, price plays bigger role than intermittency as $\sigma$ rises.
-This is further evident in the lower subplots; note that the numerical estimates of  $e$ rise and become more u-shaped as $\sigma$ rises.\footnote{ Recall that $\sigma < 1$ implies that  electricity consumption in different periods are complements, $\sigma = 1$ implies to a Cobb-Douglas relationship, and $\sigma > 1$ implies that electricity consumption in different periods are substitutes.}  When consumers are less concerned about when they receive their energy, they are far more open to substituting between coal and solar power.
-On the other hand, for lower values of $\sigma$, we find that the substitutability of coal and solar power diminishes as solar becomes progressively cheaper.
-To clarify, note that the x-axis of the lower subplot is $\log(c_2/c_1)$; since $c_2$ is the price of solar, cheaper solar energy implies lower values of $\log(c_2/c_1)$ which corresponds to lower values of $e$.
-This can be explained by $\sigma < 1$ implying a complementary relationship between electricity consumption over time.
-Consumers with such preferences will be relatively less sensitive to prices and more interested in spreading their electricity consumption across each period.
-Thus, solar is less substitutable for coal in this case, because its intermittency conflicts with consumers wanting to smooth their electricity consumption over time.
-
-Additionally, note that we assumed earlier that the estimates of $\sigma$ on a monthly basis would be fairly close to those on a daily or hourly basis.
+Specifically, we use our estimate of $\hat{\sigma} = 0.8847\, (0.044)$ and its 95\%  confidence interval $(0.7967, 0.9727)$.
+Finally, after finding the optimal values of our quantities $X$, we filter all observations of our numerical simulation that correspond to edge cases -- solutions where $X, Z \leq  0$.
+
+The first relationship we see in \hyperref[fig:eosnum]{Figure 1} is that $e_{1,2}$ varies non-linearly with the relative costs of each technology; in particular, it appears to take on a hook shape.
+This shape is a result of both intermittency and costs.
+Intermittency reduces substitutability as overall energy generation becomes more intermittent.
+In other words, intermittency is bigger issue for consumers when their energy supply is not consistent.
+This causes $e_{1,2}$ to fall when the majority of energy generated comes from solar; naturally, the latter occurs when $\log(c_2/c_1)$ is small (solar is relatively cheap).
+At the same time, quantities become more sensitive to costs when costs greatly differ.\footnote{We explore this point further in Appendix B in which we consider a numerical example where technologies are minimally intermittent.
+That is, we again consider a two-period, two-technology example, but assume that $\xi_1$ and $\xi_2$ are nearly constant over time.
+We plot our results in \hyperref[fig:eosrange]{Figure B.1} and find that the elasticity of substitution takes on a u-shape.
+} That is, $e_{1,2}$ rises when the relative prices of solar and coal are very different.
+When these two effects interact, we see the elasticity of substitution between solar and coal take on a hook shape.
+
+% Middle of paragraph (hard to understand?)
+% To understand why, let us consider three cases.
+For the first case, suppose coal is relatively far cheaper than solar ($\log(c_2/c_1)$ is large).
+This suggests producers will primarily employ coal for electricity.
+Because the output of coal does not vary with time, we will have a constant amount of electricity through the day.
+Consequently, the intermittency will not matter much on the margin since generation is already quite consistent.
+Instead, the cost of a competing generation technology will play a much bigger role.
+Consequently, solar and coal will be strong substitutes; this explains why $e_{1,2}$ is much larger when $\log(c_2/c_1)$ is large.
+On the other hand, for the second case, suppose that the price of solar and coal are such that we use about an equal amount of both.
+This corresponds to the point where $\log(c_2/c_1)  = -0.7$ in the \hyperref[fig:eosnum]{Figure 1}.
+In this case, output will not be constant through the day, since a large portion of electricity is coming from solar.
+As a result, consumers will care about intermittency on the margin; so, the  intermittency effect will matters in this case and will impede the adoption of solar.
+As a result, coal and solar will be relatively weaker substitutes; thus, we see $e_{1,2}$ is relatively lower when relative prices are not at extrema.
+Finally, consider the third case where solar is relatively much cheaper than coal.
+In this case, the quantity of solar is much larger than that of coal; this causes overall electricity output to be very intermittent.
+So, again, the intermittency effect matters.
+However, since the cost of each technology differs greatly, small changes in price could cause large changes in quantity.
+Accounting for both these factors, we see a moderately large elasticity of substitution $e_{1,2}$ when $\log(c_2/c_1)$ is small.
+
+Additionally, note that the elasticity of substitution $e_{1,2}$ between solar and coal becomes larger and more non-linear as $\sigma$ rises.
+Firstly, the reason why  it becomes larger is fairly intuitive.
+When a consumer's intertemporal elasticity of substitution for electricity consumption $\sigma$ is large, they will be more sensitive to changes in the price of electricity and more willing to substitute their electricity consumption across periods.
+As a result, the intermittency of solar becomes less of an  issue for consumers, but its relative price with respect to coal will play a bigger role.
+Consequently, this implies that the elasticity of substitution $e_{1, 2}$ will be larger.
+Hence, in the lower subplot of \hyperref[fig:eosnum]{Figure 1}, we see that $e_{1, 2}$ rises with $\sigma$ when holding relative prices of each technology constant.
+Secondly, we find that $e_{1,2}$ becomes more u-shaped as $\sigma$ rises.
+This is because larger values of $\sigma$ weaken the disincentive created by intermittency.
+Consequently, the shape of the elasticity of substitution $e_{1,2}$ becomes more dependent on the relative costs.
+As argued earlier, when costs differ greatly between technologies, the elasticity of substitution $e_{1,2}$ is higher; this effect causes $e_{1,2}$ to take on a u-shape.
+So, in total, as $\sigma$ rises, we expect $e_{1,2}$ to become increasingly u-shaped.
+
+%Additionally, note that we assumed earlier that the estimates of $\sigma$ on a monthly basis would be fairly close to those on a daily or hourly basis.
 But, our results showed estimates of $\hat{\sigma} \approx 0.5$ which differs from the literatures' estimates which fall between $0.01$ and $0.25$.
@@
 
-\subsubsection{Technical Change and the Adoption of Renewable Energy}
+%\footnote{ Recall that $\sigma < 1$ implies that  electricity consumption in different periods are complements, $\sigma = 1$ implies to a Cobb-Douglas relationship, and $\sigma > 1$ implies that electricity consumption in different periods are substitutes.}
+
+\subsection{Implications for Pollution Abatement}
+
+Overall, our results have shown that the traditional assumption of a CES relationship between renewable and fossil energy is inappropriate.
+However, since $e$ takes on a fairly simple shape, we can still adjust the findings of past models to account for variation in the elasticity of substitution.
+For example, consider again the results of \citet{Ace2012}.
+
+Firstly, they find that the short-run cost of policy intervention is increasing with the elasticity of substitution between clean and dirty technologies.\footnote{See Corollary 1 of their paper for a proof and intuitive explanation.} We find that the elasticity of substitution between renewable and fossil energy is decreasing with intermittency.
+Consequently, this implies that regions with access to clean, reliable energy (such as hydro and geothermal energy) will require the most expensive interventions.
+Additionally, their paper states that the cost of delaying intervention is increasing with the elasticity of substitution $e$.
+Similarly, this implies delaying policy intervention is the most costly in regions with access to non-intermittent, clean energy.
+
+Secondly, \citeauthor{Ace2012} argue that, when the discount rate and elasticity of substitution between clean and dirty energy ($e$) is sufficiently low, a disaster cannot be avoided under laissez-faire.\footnote{See Proposition 9 of their paper.} In our model, it is possible for $e$ to start at a large value and transition to much smaller values as clean energy becomes cheaper; this occurs when the source of clean energy is highly intermittent.
+On the other hand, if clean energy is not intermittent, it will be highly substitutable with dirty energy no matter their relative prices.
+This latter case would likely not lead to disaster but the former case (with high intermittency) would.
+Hence, we offer an alternative interpretation of this proposition: when the discount rate is sufficiently low and the intermittency of clean energy is sufficiently high, a disaster cannot be avoided under laissez-faire.
+
+Finally, \citeauthor{Ace2012} find that, ``when the elasticity
+of substitution is high, since in this case a relatively small carbon tax is sufficient to
+redirect R\&D towards clean technologies." Recall that, in our model, we see that $e$ changes with relative prices; when fossil fuels are relatively cheap, $e$ is large.
+Hence, this implies we need a relatively small carbon tax early on to spur research.
+As technological change makes renewables cheaper, $e$ will fall and thus the carbon tax needs to rise.
+On the other hand, \citeauthor{Ace2012} show numerically that an optimal carbon tax should decreases over time when $e$ is sufficiently large.
+Hence, an intermediate solution may be to maintain a constant carbon tax over time.
 
 \begin{table}[!t]
- 	\caption*{\textbf{Figure 2:} The Market Share of Solar Energy versus Own Price} 
- 	\label{fig:adoptc2}
+	\caption*{\textbf{Figure 2:} The Price Elasticity of Demand for Coal Power} 
+	\label{fig:coalelas}
 	\footnotesize
@@
 	\begin{tabular}{@{\extracolsep{0em}}c}
- 		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_adoption_c2} \\
- 		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
+		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_coal_elas} \\
+		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$, $\sigma = 0.5$.
+We generate these results by finding the optimal quantity of coal, $X_1$, over a range of percent changes in its price $c_1$.
+Then, on the y-axis, we plot the log difference in $X_1$ divided by the log difference in its price.
+This is equivalent to the price elasticity of demand for $X_1$.
+}     \\
+	\end{tabular}
+\end{table}
+
+Carbon taxes can have important distributional consequences.
+Earlier, we showed that the elasticity of substitution between renewable and fossil fuels $(e)$ is non-constant and falls with intermittency of present generation.
+This further implies that the elasticity of demand for generation technologies is non-constant as well.
+Specifically, we find that the elasticity of demand for a reliable source of energy increases in magnitude with respect to its own price.
+Using the earlier numerical example of solar and coal power, we show this explicitly in \hyperref[fig:coalelas]{Figure 2}.
+As the price of coal power rises significantly beyond its current price, demand gets more elastic as its price becomes the primary factor disincentivizing its use.
+But, initially, demand for coal power is inelastic since it is needed to fill the gaps in solar power's intermittent output.
+This should be of concern for policy makers considering a pollution tax.
+Consumers in regions without access to clean and reliable energy will have an inelastic demand for fossil fuels; hence, they will bear significant welfare losses from a tax on fossil fuels.
+On the other hand, consumers in regions that have access to dispatchable, renewable energy such as hydropower will have a relatively elastic demand for fossil fuels, because they can easily manage added intermittency; hence, they will lose relatively less welfare from a carbon tax.
+All in all, if a carbon tax were implemented federally and its revenue were distributed equally, it may nevertheless function as an inequitable, between-state welfare transfer due to differences in the availability of renewable energy technology.
+This same argument applies to renewable subsidies and carbon quotas.
+
+\begin{table}[t]
+	\captionsetup{justification=centering}
+	\caption*{\textbf{Figure 3:} The Effect of Battery Storage on the Elasticity\newline of Substition between Solar and Coal} 
+	\label{fig:battery}
+	\footnotesize
+	\vspace{-1em}
+	\begin{tabular}{@{\extracolsep{0em}}c}
+		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_batteries} \\
+		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } Technology 1 is coal and technology 2 is solar.
+The legend in the upper subplot also applies to the lower subplot.
+These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
+Furthermore, we set the parameter for the intertemporal elasticity of substition for electricity consumption equal to our estimate $\hat{\sigma} = 0.8847$.
+In order to generate these numerical, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.5\, c_1, 2 \,c_1)$.
+Then, we obtained estimates of the elasticity of substition by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1, c_2)$.
+That is, the elasticity of substitution  between technology 1 and 2 is given by the slope of the upper subplot, and it is graphed in the lower subplot.
+Finally, we repeat this procedure with $\xi_2 = (0.95, 0.15)$ and $\xi_2 = (0.90, 0.20)$ to simulate the effects of shifting solar power output using batteries.
+}     \\
+	\end{tabular}
+\end{table}
+
+However, there alternative policies that can mitigate this distributional side effect.
+One such policy is a research subsidy for improving battery technologies.
+Reducing battery costs, improving their storage capacity, and reducing their  energy loss can allow intermittent renewables to far more easily substitute for traditional, fossil energy.
+To understand the magnitude of this effect, we again provide a numerical example using solar and coal.
+We model solar energy with batteries by shifting a portion of the original solar energy output across periods.
+That is, we initially parametrized solar with $\xi_{2} = (1, 0.1)$ implying that it functions at 100\% of its potential capacity during the peak and at 10\% of its potential capacity during the off-peak.
+We shift a fraction of its peak capacity to the off-peak, thereby modeling battery storage and deployment, by considering $\xi_2 = (0.95, 0.15)$ and $\xi_2 = (0.90, 0.20)$; this is equivalent to transferring 5\% and 10\% of peak solar output to off-peak hours.
+We ignore the energy losses and costs of battery storage for simplicity.
+We plot our results in \hyperref[fig:battery]{Figure 3}.
+It is immediately clear that making solar output more consistent through the day results in it being far more substitutable with coal.
+Moreover, we can see that intermittency no longer causes $e_{1,2}$ to taper off around 5 as solar becomes the dominant source of electricity.
+Rather, with batteries, cost plays a much larger role in determining the optimal quantity of each technology even when solar is relatively cheap.
+Overall, shifting even a small fraction of solar output using batteries can significantly improve solar power's substitutability with coal.
+
+Consequently, batteries can complement reductions in the cost of intermittent renewables and mitigate the distributional effects of a carbon tax.
+As shown in \hyperref[fig:battery]{Figure 3}, the elasticity of substitution between solar and coal rises significantly as solar becomes less intermittent; this implies that a change in price of solar would have a far greater effect when combined with batteries for solar output.
+Hence, if policy makers aim to promote the use of renewables, they should subsidize research that reduces the cost of renewables as well as research that improves battery technology.
+Using both policy instruments can be more effective than either alone.
+Additionally, the second benefit of batteries is that they mitigate the distributional problems of a carbon tax.
+This is because, by reducing the intermittency of renewables, they make demand for fossil fuels less inelastic.
+In other words, regions without clean, consistent-output renewables can instead employ intermittent technologies with batteries to transition away from fossil fuel energy; this reduces welfare losses that they would have otherwise experienced from intermittency.
+
+%\subsubsection{Technical Change and the Adoption of Renewable Energy}
+% 
+% \begin{table}[!t]
+% 	\caption*{\textbf{Figure 2:} The Market Share of Solar Energy versus Own Price} 
+% 	\label{fig:adoptc2}
+% 	\footnotesize
+% 	\vspace{-1em}
+% 	\begin{tabular}{@{\extracolsep{0em}}c}
+% 		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_adoption_c2} \\
+% 		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
 To generate these values, we first vary the price of solar relative to its original parametrized cost $c_2$.
@@
 }     \\
- 	\end{tabular}
- \end{table}
-
- \begin{table}[!t]
- 	\caption*{\textbf{Figure 3:} The Market Share of Solar Energy versus the Price of Coal} 
- 	\label{fig:adoptc1}
- 	\footnotesize
- 	\vspace{-1em}
- 	\begin{tabular}{@{\extracolsep{0em}}c}
- 		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_adoption_c1} \\
- 		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
+% 	\end{tabular}
+% \end{table}
+% 
+% \begin{table}[!t]
+% 	\caption*{\textbf{Figure 3:} The Market Share of Solar Energy versus the Price of Coal} 
+% 	\label{fig:adoptc1}
+% 	\footnotesize
+% 	\vspace{-1em}
+% 	\begin{tabular}{@{\extracolsep{0em}}c}
+% 		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_adoption_c1} \\
+% 		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
 To generate these values, we first vary the price of coal relative to its original parametrized cost $c_1$.
@@
 }     \\
- 	\end{tabular}
- \end{table}
-
-We now do a similar exercise but instead study the adoption (or market share/diffusion) of renewables.
+% 	\end{tabular}
+% \end{table}
+%
+%
+% 
+%We now do a similar exercise but instead study the adoption (or market share/diffusion) of renewables.
 Specifically, using the same technologies, solar and coal, along with the same parameters, we study how the cost of each technology affects the market share of solar.
@@
 
-\subsubsection{Externalities}
-
-Suppose we are interested in handling externalities.
+%
+%\subsubsection{Externalities}
+%
+%
+%
+%Suppose we are interested in handling externalities.
 We may assume that our first technology produces pollution according to the function $S(X) = \gamma X_1$ where $\gamma$ is the monetary damage per unit of $X_1$.
@@
 Hence, their objective function is given by
-$$\max_{\tau} \; CS + PS - S(X) + \tau X_1$$
-where $CS$ is consumer surplus, $PS$ is producer surplus, $S(X)$ is the cost of pollution, $\tau$ is the tax on $X_1$, and $\tau X_1$ is the tax revenue.
+%$$\max_{\tau} \; CS + PS - \gamma X_1 + \tau X_1$$
+%where $CS$ is consumer surplus, $PS$ is producer surplus, $\gamma$ is the marginal cost of pollution generated by $X_1$, $\gamma X_1$ is the cost of pollution, $\tau$ is the tax on $X_1$, and $\tau X_1$ is the tax revenue.
 As usual, the optimal tax is a Pigouvian tax; $\tau$ should be set equal to the marginal social cost of pollution $\gamma$.
-
-\textbf{More Here}
+%
+%\textbf{More Here}
 
@@
 But, with respect to both cases, we only need one instrument to handle externalities.
-
-\begin{table}[!t]
-	\caption*{\textbf{Figure 4:} Technical Change and the Optimal Quantity of Coal} 
-	\label{fig:coaltech}
-	\footnotesize
-	\vspace{-1em}
-	\begin{tabular}{@{\extracolsep{0em}}c}
-		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_tax_subsidy} \\
-		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$, $\sigma = 0.5$.
-For the first subplot, we graph the optimal quantity of coal while varying $\xi_2$, the output efficiency of solar, by different factors; so, for instance, at 100\% on the x-axis, we have $\xi_2 = (2, \, 0.2)$.
-Similarly, in the second subplot, we do the same but with the cost of coal, $c_1$.}     \\
-	\end{tabular}
-\end{table}
 
@@
 
-\subsection{Optimal Taxation}
-
-The following proof is a derivation of the optimal tax $\tau$ on $X_1$ in the case where it produces externalities. 
-\hfill \\
-\begin{proof} We aim to maximize welfare with respect to the tax $\tau$, hence our first order condition is:
-	\begin{align*}
-	0 &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial S(X)}{\partial \tau} + \frac{\partial \tau X_1}{\partial \tau} \\
-	&=  \left( \underbrace{\frac{\partial CS}{\partial p}  + \frac{\partial PS}{\partial p}}_{= 0} - \frac{ \partial  S(X)}{\partial p} + \frac{\partial \tau X_1}{\partial p} \right) \frac{\partial p}{\partial \tau} \\
-	&=  - \gamma \frac{\partial  X_1}{\partial p} + \tau \frac{\partial  X_1}{\partial p}
-	\end{align*}
-	where the derivatives of producer and consumer surplus are eliminated by the envelope theorem. Therefore, we must have $\tau = \gamma$. \\
-	\hfill
-\end{proof}
+%\subsection{Optimal Taxation}
+%
+%The following proof is a derivation of the optimal tax $\tau$ on $X_1$ in the case where it produces externalities. The marginal cost of pollution is given by $\gamma$. 
+%\hfill \\
+%\begin{proof} We aim to maximize welfare with respect to the tax $\tau$, hence our first order condition is:
+%	\begin{align*}
+%	0 &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial \gamma X_1}{\partial \tau} + \frac{\partial \tau X_1}{\partial \tau} \\
+%	&=  \left( \underbrace{\frac{\partial CS}{\partial p}  + \frac{\partial PS}{\partial p}}_{= 0} - \frac{ \partial  \gamma X_1}{\partial p} + \frac{\partial \tau X_1}{\partial p} \right) \frac{\partial p}{\partial \tau} \\
+%	&=  \left( 0 - \frac{ \partial  \gamma X_1}{\partial p} + \frac{\partial \tau X_1}{\partial p} \right) \frac{\partial p}{\partial \tau} \\
+%	&=  - \gamma \frac{\partial  X_1}{\partial \tau} + \tau \frac{\partial  X_1}{\partial \tau}
+%	\end{align*}
+%	where the derivatives of producer and consumer surplus are eliminated by the envelope theorem. Therefore, we must have $\tau = \gamma$. \\
+%	\hfill
+%\end{proof}
 
@@
 Our framework nests the case where there exists a CES production structure between each technology.
-This happens when no two technologies produce in the same period and we have the same number of periods as technologies.
-Additionally, in this case, the CES production function's elasticity parameter  will be equivalent to the that of the consumer's CES utility function -- the intertemporal elasticity of substitution for electricity consumption.
+This occurs when each technology can only produce in a single, unique period; note that this is not a realistic scenario.
+For instance, this would occur if we had one technology that can only output electricity during the day and another that only outputs electricity at night.
+Anyways, in this case, the CES production function's elasticity parameter  will be equivalent to the that of the consumer's CES utility function -- the intertemporal elasticity of substitution for electricity consumption.
 
@@
 
+\subsection{Asymptotic Elasticity of Substitution}
+
+\label{sec:asympeos}
+
+Suppose we are in a two-period, two-technology setting with $\sigma = 1$.
+Furthermore, suppose that the output of our first technology is constant in both periods, $\xi_{1t} = \xi_{2t}$, but the output of our second technology is zero in the second period $\xi_{2s} = 0$.
+And, assume we have the parameter restrictions mentioned in earlier in \hyperref[sec:cobbdoug]{Section A} that ensure $X, Z > 0$.
+This is a simple case where we have (1) a constant output reliable technology and (2) a completely intermittent technology.
+We now show that, in this case, the elasticity of substitution approaches $1$ as the relative cost of our second technology $c_2/c_1$ approaches $0$.
+
+\begin{proof}
+	Firstly, note that from earlier we have:
+	$$
+	X = \begin{pmatrix}
+		\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}+\dfrac{\alpha _{s}\,\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} \\[2ex] 
+		-\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}-\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}
+	\end{pmatrix}
+	$$
+	Let $\xi_1 = \xi_{1t} = \xi_{2t}$ and note that $\xi_{2s} = 0$. Hence, we have:
+	$$
+	X = \begin{pmatrix}
+	\dfrac{\alpha _{s}\,\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1}}} \\
+	\dfrac{\alpha _{t}}{c_{2}}-\dfrac{\alpha _{s}\,\xi _{\mathrm{1}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1}}}
+	\end{pmatrix}
+	$$
+	Now, note that $X_1/X_2$ is given by:
+	\begin{align*}
+	\frac{X_1}{X_2} &= \frac{\alpha_s \xi_{2t} \left( c_2 ( c_1 \xi_{2t} - c_2 \xi_{1} ) \right)}{ \left( \alpha_t (c_1 \xi_{2t} - c_2 \xi_{1}) -  c_2 \alpha_s \xi_1 \right) (c_1 \xi_{2t} - c_2 \xi_{1t})}  \\
+	&= \frac{\alpha_s c_2 \xi_{2t}}{ \alpha_t (c_1 \xi_{2t} - c_2 \xi_{1}) -  c_2 \alpha_s \xi_1 }\\
+	&= \frac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{\xi _{1}\,\left(\alpha _{s}\,c_{2}+\alpha _{t}\,c_{2}\right)-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}
+	\end{align*}
+	 Next, we can see that:
+	$$
+	\frac{\partial \log(X_1/X_2)}{c_1} = \frac{\alpha _{t}\,\xi _{\mathrm{2t}}}{\xi _{1}\,\left(\alpha _{s}\,c_{2}+\alpha _{t}\,c_{2}\right)-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}
+	$$
+	The elasticity of substitution is given by:
+	\begin{align*}
+	\frac{\partial \log(X_1/X_2)}{\partial \log(c_2/c_1)} &= \frac{\partial \log(X_1/X_2)}{\partial c_1}\frac{\partial c_1}{\partial \log(c_2/c_1)} \\
+	&= \frac{\alpha _{t}\,\xi _{\mathrm{2t}}}{\xi _{1}\,\left(\alpha _{s}\,c_{2}+\alpha _{t}\,c_{2}\right)-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}\frac{\partial c_1}{\partial \log(c_2/c_1)} \\
+	&= \frac{-c_1 \alpha _{t}\,\xi _{\mathrm{2t}}}{\xi _{1}\,\left(\alpha _{s}\,c_{2}+\alpha _{t}\,c_{2}\right)-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}\\
+	&= \left( \frac{c_2 \xi_1 }{-c_1 \alpha_t \xi_{2t}} + 1 \right)^{-1} \\
+	\end{align*}
+	where $\alpha_t + \alpha_s = 1$ by definition (Equation (1)). Finally, it is simple to see that:
+	$$ \lim_{c_2/c_1 \to 0} \frac{\partial \log(X_1/X_2)}{\partial \log(c_2/c_1)} = 1$$
+	\\ \hfill
+\end{proof}
+
+\pagebreak
+
+\section{Appendix B: Supplementary Figures}
+\label{sec:AppendixB}
+
+\hyperref[fig:eosrange]{Figure B.1} below models the elasticity of substitution for two technologies that are close to being non-intermittent.
+That is, for technology 1, we have $\xi_1 = (0.95,\, 1)$, and, for technology 2, we have $\xi_2 = (1, \,0.95)$.
+We further set their costs, $c_1$ and $c_2$, to equal values and allow $\alpha_t = \alpha_s$.
+This example illustrates how the elasticity of substitution between technologies $e_{1,2}$ would appear with minimal intermittency.
+We can see that the $e_{1,2}$ takes on a u-shape.
+
+\begin{table}[h!]
+	\captionsetup{justification=centering}
+	\caption*{\textbf{Figure B.1:} The Elasticity of Substition Between Two \newline  Minimally Intermittent Technologies} 
+	\label{fig:eosrange}
+	\footnotesize
+	\vspace{-1em}
+	\begin{tabular}{@{\extracolsep{0em}}c}
+		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_elasticity_range} \\
+		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } The y-axis of the first plot is equivalent to $\log(X_1/X_2)$ and the x-axis of both plots is equivalent to  $\log(c_2/c_1)$.
+Technology 1 and 2 represent two arbitrary technologies that are practically non-intermittent.
+The legend in the upper subplot also applies to the lower subplot.
+These results were obtained using the following parameters: $\alpha_t = 0.5$, $\alpha_s = 0.5$, $\xi_1 = (0.95, \, 1)$, $\xi_2 = (1, \, 0.95)$, $c_1 = 100$, $c_2 = 100$.
+In order to generate these numerical, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.5\, c_1, 1.5 \,c_1)$.
+Then, we obtained estimates of the elasticity of substition by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1, c_2)$.
+That is, the elasticity of substitution  between technology 1 and 2 is given by the slope of the upper subplot, and it is graphed in the lower subplot.
+Finally, we repeat this procedure for various values of $\sigma$.
+}     \\
+	\end{tabular}
+\end{table}
+
+\pagebreak
+
+\pagebreak
 \pagebreak
@@
 
-	\bibitem[Ambec and Crampes (2012)]{AC2012}
+	\bibitem[Adelman(1995)]{genie}
+	Adelman, M. A. (1995). The genie out of the bottle: World oil since 1970. MIT Press.
+
+	\bibitem[Ambec and Crampes(2012)]{AC2012}
 	Ambec, S., \& Crampes, C. (2012). Electricity provision with intermittent sources of energy. Resource and Energy Economics, 34(3), 319–336. https://doi.org/10.1016/j.reseneeco.2012.01.001

### 2019-05-07 code/matlab/simulation_april/sim_adoption_curve.m
Update simulation code
- fix prices in simulations
- add code for eos with batteries
- add code for ves approx with high intermittency
- regenerate plots

@@ -5,7 +5,7 @@ close all; clear; clc;
 % Simulation params
 n = 5000;
 cost_multiplier = linspace(0.01,2,n);
-sigma_range = [0.05, 0.25, 0.5, 1, 1.5];
+sigma_range = [0.8847 + 2*0.044, 0.8847, 0.8847 - 2*0.044];
 m = length(sigma_range);
 
 % Exogenous params
@@ -59,7 +59,7 @@ for j = 1:m
     output = [];
     output(1,:) = results(:,1);
     output(2,:) = results(:,2);
-    output(3,:) = 1-cost_multiplier;
+    output(3,:) = cost_multiplier-1;
     
     % subset to positive quantities
     ind = ~any(output(1:2,:) <= 0);
@@ -67,6 +67,7 @@ for j = 1:m
 
     % adoption curve for solar
     hold on;
+    subplot(2,1,1);
     plot(output(3,:)*100, ...
          100*output(2,:)./(output(1,:) + output(2,:)), ...
         'LineWidth', 1);
@@ -75,33 +76,32 @@ end
 
 %% Plot formatting
 
-% Add horizontal line at 1
-
-% Format subplot 1
-legend('0.05', '0.25', '0.5', '1', '1.5')
-xlabel('Percent Decrease in the Cost of Solar')
-ylabel('Solar Capacity as a Fraction of All Capacity')
+% Format plot 1
+legend('0.9727 (Upper 95% Confidence Limit)', '0.8847', ...
+    '0.7967 (Lower 95% Confidence Limit)')
+xlabel('Percent Change in the Cost of Solar')
+ylabel({'Solar Capacity', 'as a Fraction of All Capacity'})
 xtickformat('percentage')
 ytickformat('percentage')
-xlim([-40, 80])
+xlim([-80, 40])
 ylim([0 100])
 grid('on')
 
 % Format legend
 [hleg,att] = legend('show');
-legend('Location', 'northwest')
+legend('Location', 'southwest')
 title(hleg, '\sigma')
 
 % Save figure
-print(gcf,'fig_adoption_c2.png','-dpng','-r300')
+%print(gcf,'fig_adoption_c2.png','-dpng','-r300')
 
 
 %% Adoption with Respect to Price of Solar Sim
 
 % Simulation params
 n = 5000;
-cost_multiplier = linspace(0.50,2,n);
-sigma_range = [0.05, 0.25, 0.5, 1, 1.5];
[…]

### 2019-05-07 code/matlab/simulation_april/sim_batteries.m

@@ -10,7 +10,7 @@ m = 3;
 
 % Exogenous params
 c_1 = 104.3;
-c_2 = 50;
+c_2 = 60;
 alpha = [0.6, 0.4];
 xi_1  = [1,   1];
 xi_2  = [1, 0.1];
@@ -69,7 +69,7 @@ for j = 1:m
     hold on;
     
     plot(-log(output(1,:)), log(output(2,:)), ...
-        'LineWidth', 1.2);
+        'LineWidth', 1.5);
     
     
     % relationship between log prices and quantities
@@ -77,7 +77,7 @@ for j = 1:m
     hold on;
     plot(-log(output(1,2:end)), ...
         diff(log(output(2,:)))./diff(-log(output(1,:))), ...
-        'LineWidth', 1.2);
+        'LineWidth', 1.5);
     
     
 end
@@ -89,7 +89,7 @@ subplot(2,1,1);
 legend('(100%, 10%)', '(  95%, 15%)', '(  90%, 20%)')
 xlabel({'Negative Log Difference in Costs', 'log(c_2/c_1)'})
 ylabel({'Log Difference in Quantities', 'log(X_1/X_2)'})
-xlim([-1.5, -0.4])
+xlim([-1.3, -0.4])
 ylim([-10, 15])
 grid('on')
 
@@ -103,7 +103,7 @@ subplot(2,1,2);
 xlabel({'Negative Log Difference in Costs', 'log(c_2/c_1)'})
 ylabel({'Elasticity of Substitution', ...
     'between Technologies', 'e_{1, 2}',})
-xlim([-1.5, -0.4])
+xlim([-1.3, -0.4])
 ylim([0 25])
 grid('on')
 

### 2019-05-07 code/matlab/simulation_april/sim_battery_elas.m

@@ -1,0 +1,83 @@
+%% Adoption with Respect to Price of Solar Sim
+
+close all; clear; clc;
+
+% Simulation params
+n = 500;
+cost_multiplier = linspace(0.99, 1.01, n);
+xi_2_values = [1, 0.1; 0.95, 0.15; 0.9, 0.2; 0.85, 0.25; 0.8, 0.30];
+m = length(xi_2_values);
+sigma = 0.8847;
+ 
+% Exogenous params
+c_1    = 104.3;
+c_2    = 60;
+alpha  = [0.6, 0.4];
+xi_1   = [1,   1];
+xi_2   = [1, 0.1];
+budget = 1;
+
+% Elasticities at each level of battery shift
+elas_array = zeros(m, 2);
+
+for j = 1:m
+    
+    xi_2 = xi_2_values(j,:);
+    results = zeros(n,2); 
+    
+    for i = 1:n
+
+
+        phi   = (sigma - 1)/sigma;
+        x_1_cost_param = c_1*cost_multiplier(i);
+        x_2_cost_param = c_2;
+
+        % Prices
+        xi_mat   = [xi_1; xi_2];
+        cost_mat = [x_1_cost_param; x_2_cost_param];
+        prices   = xi_mat\cost_mat;
+
+        if any(prices<0)
+            continue
+        end
+
+        % Price Index
+        P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
+        if sigma == 1
+            P = 1;
+        end
+        
+        % Quantities
+        Y = ((alpha'./prices).^(sigma)) * (budget/P);
+          
+        X = (xi_mat')\Y;
+
+        results(i,:) = X';
+
+    end    
+
+    output = [];
+    output(1,:) = results(:,1);
+    output(2,:) = results(:,2);
+    output(3,:) = cost_multiplier-1;
+    output(4,:) = c_1*cost_multiplier;
+    
+    % subset to positive quantities
+    ind = ~any(output(1:2,:) <= 0);
+    output = output(:,ind);
+
+    % elasticity of coal versus price
+    elas_coal_p = diff(log(output(1,:)))./diff(log(output(4,:)));
+    
+    % save elasticity around initial price
+    elas_coal_p0  = elas_coal_p(round(n/2));
+    
+    % add to results
+    elas_array(j, 1) = 1-xi_2(1);
+    elas_array(j, 2) = elas_coal_p0;
+    
+end
+
+%% Results
+elas_array
+

### 2019-05-07 code/matlab/simulation_april/sim_elasticity.m

@@ -10,7 +10,7 @@ m = length(sigma_range);
 
 % Exogenous params
 c_1 = 104.3;
-c_2 = 50;
+c_2 = 60;
 alpha = [0.6, 0.4];
 xi_1  = [1,   1];
 xi_2  = [1, 0.1];

### 2019-05-07 code/matlab/simulation_april/sim_ves_int.m

@@ -4,8 +4,8 @@ close all; clear; clc;
 
 % Simulation params
 n = 5000;
-cost_multiplier = linspace(0.5,2,n);
-sigma_range = [0.8847 + 2*0.044, 0.8847, 0.8847 - 2*0.044];
+cost_multiplier = linspace(0.9,2,n);
+sigma_range = [0.8847];
 m = length(sigma_range);
 
 % Exogenous params
@@ -16,8 +16,7 @@ xi_1  = [1,   1];
 xi_2  = [1, 0.1];
 budget = 1;
 
-
-figure('Renderer', 'painters', 'Position', [100 100 900 600])
+figure('Renderer', 'painters', 'Position', [100 100 900 400])
 hold on;
 
 for j = 1:m
@@ -63,69 +62,79 @@ for j = 1:m
     % subset to positive quantities
     ind = ~any(output <= 0);
     output = output(:,ind);
-
-    % relationship between log prices and quantities
-    subplot(2,1,1);
+    
+    % relationship between e and the ratio of quantities
     hold on;
     
     if sigma == 0.8847
-        plot(-log(output(1,:)), log(output(2,:)), ...
-            'LineWidth', 1, 'Color', 'k');
+        plot(output(2,2:end), ...
+            diff(log(output(2,:)))./diff(-log(output(1,:))), ...
+            'LineWidth', 1.5, 'Color', 'k');
     elseif sigma < 0.8846
-        plot(-log(output(1,:)), log(output(2,:)), ...
+        plot(output(2,2:end), ...
+            diff(log(output(2,:)))./diff(-log(output(1,:))), ...
             'LineWidth', 1, 'LineStyle', '--', 'Color', [0 0 1]*0.8);
     else
-        plot(-log(output(1,:)), log(output(2,:)), ...
+        plot(output(2,2:end), ...
+            diff(log(output(2,:)))./diff(-log(output(1,:))), ...
             'LineWidth', 1, 'LineStyle', '--', 'Color', [1 0 0]*0.8);
     end
     
-    
-    % relationship between e and log prices
-    subplot(2,1,2);
-    hold on;
-    
+    % store data for average sigma assumption
     if sigma == 0.8847
-        plot(-log(output(1,2:end)), ...
-            diff(log(output(2,:)))./diff(-log(output(1,:))), ...
[…]

### 2019-05-07 documents/draft.tex
Update draft
- add some more to abstract
- update discussion
- add table for battery implications
- add section on implementing our results (ves and cge examples)

@@
 \usepackage{cleveref}
+\usepackage{varwidth}
 %\usepackage{showframe}
@@
 \graphicspath{ {D:/Users/saketh/Documents/GitHub/BECCS-Case-Study/documents/exhibits/} }
+
+% multiline cells
+\newcommand{\specialcell}[2][c]{%
+	\begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
+
+% proper caption centering
+\DeclareCaptionFormat{centerproper}{%
+	% #1: label (e.g. "Table 1")
+	% #2: separator (e.g. ": ")
+	% #3: caption text
+	\begin{varwidth}{\linewidth}%
+		\centering
+		#1#2#3%
+	\end{varwidth}%
+}
 
@@
 		In order to discount the ..., we use a representative agent that prefers to smooth their electricity consumption over time. 
-		Our results find a highly non-linear elasticity of substitution between intermittent and fossil energy. 
-		Furthermore, we find that standard environmental policy such as carbon taxes and renewable subsidies can have important distributional consequences as a result of intermittency.
-Subsidizing research that improves battery technologies can complement present policy and greatly increase the substitutability of renewable and fossil energy.
+		We find a non-linear elasticity of substitution between intermittent and non-intermittent generation technologies.
+Hence, a CES production function fails to accurately model substitutability between renewables and fossil fuels.
+Alternatively, we find that a VES production function can reasonably approximate the effect of intermittency on the elasticity of substitution between between intermittent and non-intermittent energy.
+		Furthermore, our results suggest that the welfare burden of carbon taxes on consumers will vary geographically based on the availability of consistent, renewable technology.
+This distributional side effect can be counteracted by subsidizing research into battery technologies; improvements in batteries can also complement present policy to promote renewables by greatly increasing the substitutability of intermittent  and non-intermittent energy technologies.
 	 }
@@
 \subsection{Consumers}
+\label{sec:consumers}
 
@@
 Finally, when the two sectors are complementary, the only way to stave off a disaster is to stop long-run growth." However, note that while our model sets the intertemporal elasticity of substitution for  electricity consumption $\sigma$ to a fixed value, we make no direct assumptions about the elasticity of substitution between different energy technologies.
-Instead, this latter elasticity emerges as an indirect result of substitution between electricity consumption in periods.
+Instead, this latter elasticity is indirectly defined by the substitutability of electricity consumption between periods.
 To illustrate this, we parametrize and estimate our model numerically.
 
-Firstly, we let technology 1 be coal power and technology 2 be solar power; let period $t$ represent peak hours and period $s$ represent off-peak hours.
+Firstly, let technology 1 be coal power and technology 2 be solar power.
+These two technologies exemplify consistent fossil energy and intermittent renewable energy.
+Furthermore,  let period $t$ represent peak hours and period $s$ represent off-peak hours.
 We assume that, holding prices equal, consumers prefer that approximately 60\% of their energy arrive in period $t$ and the remaining 40\% arrive in period $s$; that is, we have $\alpha_t = 0.6$ and $\alpha_s = 0.4$.
 Next, we normalize all quantity units to a MWh basis.
-Hence, $\xi$ represents the percent of capacity utilized in each period; we assume coal uses 100\% of its capacity in both periods, while solar can access 100\% during peak hours and only 10\% during the off-peak.
-Finally, we set cost parameters, given in  \$ per MWh, equal to LCOE estimates for 2023 from the \citet{EIALCOE}; specifically, we use estimates for "Solar PV" and "Coal with 30\% CCS" from Table 1b.\footnote{ The LCOE for a technology is equal to the sum of its lifetime costs divided by its lifetime energy output.
-While \citet{Joskow2011} explains the flaws of comparing generation technologies solely on the basis of LCOE, our use of this measure is unrelated to his critique.
+Hence, we let $\xi$ represent the percent of capacity utilized in each period; we assume coal uses 100\% of its capacity in both periods, while solar can access 100\% during peak hours and only 10\% during the off-peak.
+Finally, we set the cost parameters, given in  \$ per MWh, equal to LCOE\footnote{ The LCOE for a technology is equal to the sum of its lifetime costs divided by its lifetime energy output.
+\citet{Joskow2011} explains the flaws of comparing generation technologies solely on the basis of LCOE; but,  our use of this measure is unrelated to his critique.
 That is, he argues that the economic value an intermittent technology should also account for when it produces electricity and the prices of electricity in those periods (see Table 2 of his paper).
 Our model does exactly this; but, we still need to  use LCOE to parametrize the cost of developing capacity.
-}  In total, we have the following parameters.
+} estimates for 2023 from the \citet{EIALCOE}; specifically, we use estimates for "Solar PV" and "Coal with 30\% CCS" from Table 1b.
+In total, we have the following parameters.
 
@@
 We begin by exploring the implied elasticity of substitution between these two technologies. Recall, for any two commodities $i$ and $j$,  the elasticity of substitution $e_{i,j}$ is given by:
-$$e_{i,j} = \frac{\partial \ln (X_i/ X_j)}{\partial \ln (c_j/c_i)}$$
+$$e_{i,j} = \frac{\partial \log (X_i/ X_j)}{\partial \log (c_j/c_i)}$$
 where $c$ is their prices.
@@
 That is, they assume that $e$ is a fixed constant between renewable and fossil energy.
-In our model, this is not the case; while directly deriving the equation for $e_{1,2}$ in our model is analytically intractable, we numerically estimate how it varies with $\ln (c_2/c_1)$ and $\sigma$.
+In our model, this is not the case; while directly deriving the equation for $e_{1,2}$ in our model is analytically intractable, we numerically estimate how it varies with $\log (c_2/c_1)$ and $\sigma$.
 
@@
 These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
-Furthermore, we set the parameter for the intertemporal elasticity of substition for electricity consumption equal to our estimate $\hat{\sigma} = 0.8847$.
-In order to generate these numerical, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.5\, c_1, 2 \,c_1)$.
-Then, we obtained estimates of the elasticity of substition by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1, c_2)$.
+Furthermore, we set the parameter for the intertemporal elasticity of substitution for electricity consumption equal to our estimate $\hat{\sigma} = 0.8847$.
+In order to generate these numerical results, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.5\, c_1, 2 \,c_1)$.
+Then, we obtained estimates of the elasticity of substitution by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1/ c_2)$.
 That is, the elasticity of substitution  between technology 1 and 2 is given by the slope of the upper subplot, and it is graphed in the lower subplot.
-Finally, we repeat this procedure with $\sigma$ equal to two standard deviations above and below its estimated value; that is, the dashed lines represent  $\sigma = 0.8847 \pm 2(0.044)$.
+Finally, we repeat this procedure with $\sigma$ equal to two standard deviations above and below its estimated value $\hat{\sigma}$; that is, the dashed lines represent  $\sigma = 0.8847 \pm 2(0.044)$.
 }     \\
@@
 We plot our numerical estimates of $e_{1, 2}$, the elasticity of substitution between solar and coal power, in \hyperref[fig:eosnum]{Figure 1}.
-These results were generated by computing the optimal quantities of each technology given a range of prices.
-Specifically, we held the price of solar capacity constant and varied the price of coal capacity from 50\% to 200\% of its original parametrized price.
-Then, we numerical differentiated $\log(X_1/X_2)$ with respect to $\log(c_2/c_1)$ to estimate the elasticity of substitution between solar and coal.\footnote{ Instead, we could have generated variation in $\log(c_2/c_1)$ data by holding solar at a constant price and varying the price of coal capacity.
-However, this does not change the results.} This numerically computed elasticity of substitution between solar and coal power, $e_{solar,coal}$, is shown in the lower subplot.
+We generated these results by computing the optimal quantities of each technology given a range of relative prices $c_2/c_1$.
+Then, we numerically differentiated $\log(X_1/X_2)$ with respect to $\log(c_2/c_1)$ to estimate the elasticity of substitution between solar and coal.
+This numerically computed elasticity of substitution between solar and coal power, $e_{solar,coal}$, is shown in the lower subplot.
 We repeat this process with different values of $\sigma$, the elasticity of substitution in the consumer's utility function.
@@
 
-Firstly, they find that the short-run cost of policy intervention is increasing with the elasticity of substitution between clean and dirty technologies.\footnote{See Corollary 1 of their paper for a proof and intuitive explanation.} We find that the elasticity of substitution between renewable and fossil energy is decreasing with intermittency.
-Consequently, this implies that regions with access to clean, reliable energy (such as hydro and geothermal energy) will require the most expensive interventions.
-Additionally, their paper states that the cost of delaying intervention is increasing with the elasticity of substitution $e$.
-Similarly, this implies delaying policy intervention is the most costly in regions with access to non-intermittent, clean energy.
-
-Secondly, \citeauthor{Ace2012} argue that, when the discount rate and elasticity of substitution between clean and dirty energy ($e$) is sufficiently low, a disaster cannot be avoided under laissez-faire.\footnote{See Proposition 9 of their paper.} In our model, it is possible for $e$ to start at a large value and transition to much smaller values as clean energy becomes cheaper; this occurs when the source of clean energy is highly intermittent.
+Firstly, they find that the short-run cost of policy intervention is increasing with the elasticity of substitution between clean and dirty technologies.\footnote{ See Corollary 1 of their paper for a proof and intuitive explanation.} We find that the elasticity of substitution between renewable and fossil energy is decreasing with intermittency.
+Consequently, this implies that regions with access to clean, non-intermittent energy (such as hydro and geothermal energy) will require the most expensive interventions.
+Additionally, their paper states that the cost of delaying intervention is increasing with the elasticity of substitution $e$ as well.
+So, this implies that delaying policy intervention is also the most costly in regions with access to non-intermittent, clean energy.
+
+Secondly, \citeauthor{Ace2012} argue that, when the discount rate and elasticity of substitution between clean and dirty energy ($e$) is sufficiently low, a disaster cannot be avoided under laissez-faire.\footnote{ See Proposition 9 of their paper.} In our model, it is possible for $e$ to start at a large value and transition to much smaller values as clean energy becomes cheaper; this occurs when the source of clean energy is highly intermittent.
 On the other hand, if clean energy is not intermittent, it will be highly substitutable with dirty energy no matter their relative prices.
@@
 Hence, we offer an alternative interpretation of this proposition: when the discount rate is sufficiently low and the intermittency of clean energy is sufficiently high, a disaster cannot be avoided under laissez-faire.
+The intuition here is that, even if clean energy became relatively cheap, it would fail to properly substitute  for fossil energy as a result of intermittency.
+Hence, the laissez-faire equilibrium would require policy intervention to avoid a climate disaster.
 
 Finally, \citeauthor{Ace2012} find that, ``when the elasticity
-of substitution is high, since in this case a relatively small carbon tax is sufficient to
+of substitution is high\dots\, a relatively small carbon tax is sufficient to
 redirect R\&D towards clean technologies." Recall that, in our model, we see that $e$ changes with relative prices; when fossil fuels are relatively cheap, $e$ is large.
 Hence, this implies we need a relatively small carbon tax early on to spur research.
-As technological change makes renewables cheaper, $e$ will fall and thus the carbon tax needs to rise.
-On the other hand, \citeauthor{Ace2012} show numerically that an optimal carbon tax should decreases over time when $e$ is sufficiently large.
-Hence, an intermediate solution may be to maintain a constant carbon tax over time.
+As technological change makes renewables cheaper, fossil fuels will become relatively more expensive and $e$ will fall; thus, the carbon tax will need to increase over time.
+These dynamics (a rising carbon tax) contrast with the results of \citeauthor{Ace2012} who numerically show that an optimal carbon tax should decrease over time when $e$ is sufficiently large.
+A potential resolution to these contradictory solutions may be to take an intermediate route and maintain a constant carbon tax over time.
 
@@
 
-Carbon taxes can have important distributional consequences.
+Our results also suggest that carbon taxes can have important distributional consequences.
 Earlier, we showed that the elasticity of substitution between renewable and fossil fuels $(e)$ is non-constant and falls with intermittency of present generation.
 This further implies that the elasticity of demand for generation technologies is non-constant as well.
-Specifically, we find that the elasticity of demand for a reliable source of energy increases in magnitude with respect to its own price.
+Specifically, the elasticity of demand for non-intermittent energy increases then decreases with respect to its own price.
 Using the earlier numerical example of solar and coal power, we show this explicitly in \hyperref[fig:coalelas]{Figure 2}.
-As the price of coal power rises significantly beyond its current price, demand gets more elastic as its price becomes the primary factor disincentivizing its use.
-But, initially, demand for coal power is inelastic since it is needed to fill the gaps in solar power's intermittent output.
-This should be of concern for policy makers considering a pollution tax.
-Consumers in regions without access to clean and reliable energy will have an inelastic demand for fossil fuels; hence, they will bear significant welfare losses from a tax on fossil fuels.
-On the other hand, consumers in regions that have access to dispatchable, renewable energy such as hydropower will have a relatively elastic demand for fossil fuels, because they can easily manage added intermittency; hence, they will lose relatively less welfare from a carbon tax.
+As the price of coal power rises significantly beyond its current price, demand gets more elastic because its price becomes the primary factor disincentivizing its use.
+But, initially, a rise in the cost of coal power causes its demand to become inelastic.
+This is because a rise in the price of coal shifts generation towards solar;  consequently, generation becomes more intermittent and demand for coal becomes less price sensitive since it is needed to help smooth electricity generation.
+This relationship should be of concern for policy makers considering a pollution tax.
+Consumers in regions without access to clean, non-intermittent energy will have the most inelastic demand for fossil fuels; hence, they will bear the greatest welfare losses from a tax on pollution/carbon.
+On the other hand, consumers in regions that have access to dispatchable, renewable energy such as hydropower will see smaller welfare losses; demand for fossil fuels in these regions will not be as inelastic, because dirty generation can be replaced with non-intermittent, clean generation.
 All in all, if a carbon tax were implemented federally and its revenue were distributed equally, it may nevertheless function as an inequitable, between-state welfare transfer due to differences in the availability of renewable energy technology.
-This same argument applies to renewable subsidies and carbon quotas.
+This same argument would apply  to renewable subsidies and carbon quotas.
 
 \begin{table}[t]
-	\captionsetup{justification=centering}
-	\caption*{\textbf{Figure 3:} The Effect of Battery Storage on the Elasticity\newline of Substition between Solar and Coal} 
+	\captionsetup{format=centerproper}
+	\caption*{\textbf{Figure 3:} The Effect of Battery Storage on the Elasticity\newline of Substitution between Solar and Coal} 
 	\label{fig:battery}
@@
 The legend in the upper subplot also applies to the lower subplot.
+The elasticity of substitution  between technology 1 and 2 is given by the slope of the upper subplot, and it is graphed in the lower subplot.
 These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
-Furthermore, we set the parameter for the intertemporal elasticity of substition for electricity consumption equal to our estimate $\hat{\sigma} = 0.8847$.
-In order to generate these numerical, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.5\, c_1, 2 \,c_1)$.
-Then, we obtained estimates of the elasticity of substition by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1, c_2)$.
-That is, the elasticity of substitution  between technology 1 and 2 is given by the slope of the upper subplot, and it is graphed in the lower subplot.
-Finally, we repeat this procedure with $\xi_2 = (0.95, 0.15)$ and $\xi_2 = (0.90, 0.20)$ to simulate the effects of shifting solar power output using batteries.
+Furthermore, we set the parameter for the intertemporal elasticity of substitution for electricity consumption equal to our estimate $\hat{\sigma} = 0.8847$.
+We generated these numerical results with the same procedure used for \hyperref[fig:eosnum]{Figure 1}.
+We repeated this procedure with $\xi_2 = (0.95, 0.15)$ and $\xi_2 = (0.90, 0.20)$ to simulate the effects of shifting solar power output using batteries.
 }     \\
@@
 
-However, there alternative policies that can mitigate this distributional side effect.
+However, there are alternative policies that can mitigate this distributional side effect.
 One such policy is a research subsidy for improving battery technologies.
@@
 To understand the magnitude of this effect, we again provide a numerical example using solar and coal.
-We model solar energy with batteries by shifting a portion of the original solar energy output across periods.
-That is, we initially parametrized solar with $\xi_{2} = (1, 0.1)$ implying that it functions at 100\% of its potential capacity during the peak and at 10\% of its potential capacity during the off-peak.
-We shift a fraction of its peak capacity to the off-peak, thereby modeling battery storage and deployment, by considering $\xi_2 = (0.95, 0.15)$ and $\xi_2 = (0.90, 0.20)$; this is equivalent to transferring 5\% and 10\% of peak solar output to off-peak hours.
-We ignore the energy losses and costs of battery storage for simplicity.
+We model solar energy with batteries by shifting a portion of the original solar energy output across periods; we also ignore the energy losses and costs of battery storage for simplicity.
+In reality, batteries would be more accurately modeled by rewriting our model as a dynamic optimization problem and solving using optimal control theory.
+However, we set aside these complications and consider a second-best solution where batteries are used to shift a fraction of solar output during peak hours to the off-peak period.
+When we can only shift a marginal fraction of output, this is likely equivalent to the first-best solution, because solar power generates relatively too little electricity during off-peak hours than relatively too much during peak hours.
+Specifically, we initially parametrized solar with $\xi_{2} = (1, 0.1)$ implying that it functions at 100\% of its potential capacity during the peak and at 10\% of its potential capacity during the off-peak; this is far from matching consumer demand.
+So, we represent solar output with batteries using $\xi_2 = (0.95, 0.15)$ and $\xi_2 = (0.90, 0.20)$; this is equivalent to transferring 5\% and 10\% of peak solar output to off-peak hours.
 We plot our results in \hyperref[fig:battery]{Figure 3}.
-It is immediately clear that making solar output more consistent through the day results in it being far more substitutable with coal.
-Moreover, we can see that intermittency no longer causes $e_{1,2}$ to taper off around 5 as solar becomes the dominant source of electricity.
+It is immediately clear that making solar output more consistent through the day results in a large increase in the elasticity of substitution $e_{1,2}$.
+Moreover, we can see that intermittency no longer causes $e_{1,2}$ to taper off around 4 as solar becomes the dominant source of electricity.
 Rather, with batteries, cost plays a much larger role in determining the optimal quantity of each technology even when solar is relatively cheap.
@@
 
-Consequently, batteries can complement reductions in the cost of intermittent renewables and mitigate the distributional effects of a carbon tax.
-As shown in \hyperref[fig:battery]{Figure 3}, the elasticity of substitution between solar and coal rises significantly as solar becomes less intermittent; this implies that a change in price of solar would have a far greater effect when combined with batteries for solar output.
+\begin{table}[!t] \centering 
+	\captionsetup{format=centerproper}
+	\caption*{\textbf{Table 4:} The Effect of Battery Storage on the   \newline Elasticity of Demand for Coal Power} 
+	\label{table:4} 
+	\small
+	\begin{tabular}{@{\extracolsep{2em}}ccc} 
+		\\[-4ex]\hline  
+		\hline \\[-1.8ex] 
+		\\[-1.8ex] \specialcell{Solar Output during \\ Peak Hours ($\xi_{2t}$)} &  \specialcell{Solar Output during \\ Off-Peak Hours ($\xi_{2s}$)}  & \specialcell{Elasticity of Demand \\ for Coal Power}\\ [0.5ex]
+		\hline \\[-1.8ex] 
+		           100\% &  \phantom{1}5\%  &  -3.25 \\
+		 \phantom{1}95\% &            10\%  &  -3.71 \\
+		 \phantom{1}90\% &            15\%  &  -4.40 \\
+		 \phantom{1}85\% &            20\%  &  -5.48 \\
+		 \phantom{1}80\% &            25\%  &  -7.29 \\
+		\hline 
+		\hline \\[-1.8ex] 
+		\multicolumn{3}{@{}p{34.2em}@{}}{\textit{Note: } These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $c_1 = 104.3$, $c_2 = 60$, $\sigma = 0.8847$.
+We generated these results by numerically differentiating the optimal quantity of coal power, $X_1$, with respect to its own price, $c_1$, around its initial price $104.3$.
+We repeated this process for various values of the output parameter for solar power, $\xi_{2}$.
+Specifically, we considered 5\% to 20\% shifts in the output of solar power from peak to  off-peak hours to simulate the effects of implementing battery storage.
+}  \\
+	\end{tabular} 
+\end{table}
+
+Consequently, batteries can complement reductions in the cost of intermittent renewables and mitigate the distributional side effects of a carbon tax.
+As shown in \hyperref[fig:battery]{Figure 3}, the elasticity of substitution between solar and coal rises significantly as solar becomes less intermittent; this implies that a change in relative price of solar would have a far greater effect on solar adoption if batteries were employed with solar.
 Hence, if policy makers aim to promote the use of renewables, they should subsidize research that reduces the cost of renewables as well as research that improves battery technology.
@@
 Additionally, the second benefit of batteries is that they mitigate the distributional problems of a carbon tax.
-This is because, by reducing the intermittency of renewables, they make demand for fossil fuels less inelastic.
-In other words, regions without clean, consistent-output renewables can instead employ intermittent technologies with batteries to transition away from fossil fuel energy; this reduces welfare losses that they would have otherwise experienced from intermittency.
+This is because, by reducing the intermittency of renewables, batteries make demand for fossil fuels less inelastic.
+We specifically show this elasticity would change with another numerical example in \hyperref[table:4]{Table 4}; like  \hyperref[fig:battery]{Figure 3}, we model batteries that shift solar output towards the off-peak.
+We then estimate the elasticity of demand for coal power around its initial price; this elasticity is decreasing at an increasing rate with the percent shift in solar output.
+The practical implications of this are straightforward.
+Researching and implementing battery technology can reduce the welfare losses from a carbon tax.
+Moreover, regions without clean, consistent renewables would benefit in particular, because they will be able to combine intermittent technologies with better energy storage to help transition away from fossil fuel energy.
+In short, subsidizing battery research can reduce some of the distributional side effects of carbon taxes while mitigating environmental damage.
+
+\subsection{Adjusting Future Models}
+
+Given that traditional assumption of a CES relationship between renewable and fossil energy appears to be inaccurate, we offer two alternative approaches for future models.
+The first approach is to directly integrate our model within a given framework.
+The second approach is to assume a variable elasticity of substitution (VES) structure\footnote{ The VES function was originally introduced by \citet{VES}.} between clean and dirty energy.
+These two approaches have their own advantages/disadvantages and serve different purposes.
+
+\subsubsection{Direct Integration}
+
+The first approach is better suited for numerical models.
+For example, our model of the energy sector can be embedded within a Computational General Equilibrium (CGE) model.
+CGEs, specifically ones designed to study energy and environmental policy, tend to assume a CES relationship between generation technologies and treat electricity as a homogeneous good.
+On the other hand, our representation of the energy sector makes more realistic assumptions and directly models the source of imperfect substitutability between generation technologies -- intermittency.
+Consequently, embedding our model within a CGE offers more realistic microfoundations and predictive accuracy.
+Moreover, even though our model is analytically intractable with $\sigma \neq 1$, this is not a problem for CGEs which are evaluated numerically.
+
+Furthermore, implementation can be done with relatively few modifications to standard CGE.
+To start, CGEs already use CES utility to model consumer preferences.
+In order to integrate our method of modeling electricity consumption, a CGE practitioner need only to rewrite preferences as:
+\begin{equation}
+U =   \left( \sum_{i \neq elc} \alpha_{i} Z_{i}^\eta +  \alpha_{elc} \left( \sum_{t=1}^T \alpha_{elc,t} Z_{elc, t}^\phi \right)^{\eta/\phi} \right)^{1/\eta}
+\end{equation}
+where the intertemporal elasticity of substitution for electricity consumption is given by $\sigma = 1/(1-\phi)$,  the elasticity of substitution between all consumer goods is given by $1/(1-\eta)$, the consumption of each good is given by $Z_{i}$, and the consumption of electricity in each period $t$ is given by $Z_{elc, t}$.
+This can be simplified to:
+\begin{align}
+U &= \left(  \left( \sum_{i \neq elc} \alpha_{i} Z_{i}^\eta \right) + \alpha_{elc} Z_{elc}^\eta \right)^{1/\eta} \\
+Z_{elc} &= \left(  \sum_{t=1}^T \alpha_{elc,t} Z_{elc, t}^\phi \right)^{1/\phi}
+\end{align}
+where $Z_{elc}$ is an aggregate electricity good.
+Next, we consider the production functions for electricity production in each period.
+These are simply linear, since the total  electricity produced in a period is equal to the sum of electricity produced by each technology in that period.
+That is, we have
+\begin{equation}
+Z_{elc,t} = \sum_i \xi_{i,t} X_i 
+\end{equation}
+where $X_i$ is a generation technology and $\xi_{i,t}$ is its output in period $t$.
+The parameters for $\xi_{1,t}$ must be estimated using additional data.
+For fossil fuels, $\xi_i$ can remain constant over time.
+For intermittent renewables, $\xi_{i,t}$ may be set to empirical estimates of the average output per unit of $X_i$ in period $t$.\footnote{It is important to note that each period $t$ should describe a short time frame.
+For instance, each period may represent an hour of a day, or, as in our examples, we may have two periods that represent peak and off-peak.
+If larger periods are chosen, the underlying assumptions behind our model are no longer relevant.
+That is, technologies like coal and nuclear can change their output over longer periods of time to respond to changes in price; on the other hand, as discussed earlier, we assume here that output in each period is exogenous.}  Additionally, the supply-side equations for building capacity in each technology can be modeled using the usual  CGE approach; total cost is given by the sum of costs for each input factor and total quantity is given by a CES of the input factors used to build capacity $(X_i)$.
+Finally, since these functional forms equivalent\footnote{Linear production functions simply a special case of CES production functions where the elasticity of substitution is arbitrarily high.} to those used in standard CGEs, they can be calibrated using the usual procedures and a social accounting matrix.
+So, overall, implementing our model within a CGE can be done in a fairly simple way.
+
+\subsubsection{VES Approximation}
+
+The second approach is to use a variable elasticity of substitution function to model the relationship between clean and dirty energy.
+A VES function would approximately capture the dynamics of $e$, the elasticity of substitution between clean and dirty technology,  while keeping a theoretical model relatively simple.
+The latter is because assuming a VES structure between clean and dirty energy only requires considering one more parameter than a traditional CES function.
+To be more precise, the VES function is defined in \citet{VES} as
+\begin{align}
+Z &= \gamma X_1^{\omega(1-\delta \rho)} \left( X_2 + (\rho - 1) X_1 \right)^{\omega \delta \rho} \\
+e &= 1 + \beta (X_1 / X_2) \\
+\beta &= (\rho - 1) / ( 1- \delta \rho ) 
+\end{align}
+\vspace{-4ex}
+$$\gamma > 0, \quad \omega > 0, \quad0 < \delta < 1, \quad 0 \leq \delta \rho \leq 1 , \quad (X_2/X_1) >  -\beta $$
+where $\omega, \delta, \rho$, and $\gamma$ are parameters.
+Additionally, $Z$ is the output, $X_1$ and $X_2$ are the inputs, and $e$ is the elasticity of substitution between $X_1$ and $X_2$.
+In our case, we can think of $Z$ as electricity output while $X_1$ and $X_2$ represent dirty and clean technology.
+Note that $e$ is a linear function of $X_1/X_2$; this relationship allows a VES function to approximate the effects of intermittency.
+To show why, we plot $e$ against its VES approximation $\hat{e}$ for solar and coal in \hyperref[fig:ves]{Figure 4}.
+This approximation was fit by running OLS against the numerical results for $e$ while holding the intercept fixed at 1.\footnote{ There also exists a VES function described by \citet{VES} with the form $e = \beta_0 + \beta (X_1/X_2)$.
+This function may provide a better approximation of $e$, but there is no tractable production function that underlies it for $\beta_0 \neq 1$.
+Hence, we only consider the case where $\beta_0 = 1$, since the entire point of taking a VES approximation, in this case, is for analytical tractability.
+} We can see that, as either the capacity of solar or coal dominates the market, the approximation becomes weaker.
+But, overall, it seems to mimic the shape of the true elasticity of substitution $e$ implied by our model of intermittency.
+Hence, a  VES function is a reasonable alternative to a CES function -- it better models intermittency while also maintaining parsimony.
+
+\begin{table}[t]
+	\captionsetup{format=centerproper}
+	\caption*{\textbf{Figure 4:} The VES Approximation of the Elasticity of Substitution \\ between Solar and Coal } 
+	\label{fig:ves}
+	\footnotesize
+	\vspace{-1em}
+	\begin{tabular}{@{\extracolsep{0em}}c}
+		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_ves_approx} \\
+		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } Technology 1 is coal and technology 2 is solar.
+The purple, dash-dots line represents a linear approximation of $e_{1,2}$ for $\sigma = 0.8847$ with a fixed intercept of 1.
+These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
+Furthermore, we set the parameter for the intertemporal elasticity of substitution for electricity consumption equal to our estimate $\hat{\sigma} = 0.8847$.
+In order to generate these numerical results, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.9\, c_1, 2 \,c_1)$.
+Then, we obtained estimates of the elasticity of substitution by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1, c_2)$.
+}     \\
+	\end{tabular}
+\end{table}
+
+One potential objection to using the VES function is that it assumes the elasticity of substitution $e$ approaches 1 when the majority of generation comes from renewables ($X_1/X_2 \to 0$).
+This actually happens to be a fairly reasonable assumption in our model.
+That is, suppose renewable energy was arbitrarily cheap but highly intermittent.
+Furthermore, suppose that the consumer's elasticity of substitution $\sigma = 1$.
+We show in \hyperref[sec:asympeos]{Appendix A.C} that this results in renewable  and fossil energy entering Cobb-Douglas relationship ($e = 1$).
+And, more generally, whenever the renewable technology is highly intermittent, $e$ becomes almost perfectly linear with respect to the quantity ratio $X_1/X_2$.
+Hence, in these cases, the VES approximation $\hat{e}$ almost perfectly matches $e$; this is shown in \hyperref[fig:ves_int]{Figure B.2}.
+Thus, the VES assumption that $e = 1$ when $X_1/X_2$ is arbitrarily small is not necessarily a drawback.
+Moreover, even if these assumptions were not true, our model implies that VES function would only underestimate the substitutability of clean and dirty energy in these edge cases.
+While \textit{overestimating} $e$ may result in policy failing to mitigate a preventable climate disaster, \textit{underestimating} $e$ would simply cause a policy overreaction.
+The former would likely  result in far more economic damage than the latter, hence a risk averse policymaker need not be too concerned with the error of a VES assumption for $e$.
+
+Overall, using a VES function is a reasonable alternative to directly modeling intermittency.
+It allows theorists derive policy implications from intermittency without relying too heavily on numerical models.
+Furthermore, it keeps theory simple by assuming a linear elasticity of substitution that depends on a single parameter $\beta$.
+And, this parameter can be estimated econometrically, so theoretical models assuming a VES structure can offer empirically-based results.
+Finally, it may even be of use for CGE modelers.
+Its structure is simple enough to be calibrated with a given set of data, while its implementation can produce simple but reasonably accurate models of energy sectors with intermittency.
 
@@
 
-\pagebreak
-
 \section{Conclusion}
@@
 Secondly, we limit the number of periods and technologies to 2.
-And, thirdly, we normalize the prices such that our repesentative consumer's income $I$ is $1$.
+And, thirdly, we normalize the prices such that our representative consumer's income $I$ is $1$.
 
@@
 Again, it is  important to note that we assume $\xi > 0$ for to simplify the inequalities of $X_1 > 0$ and $X_2 > 0$ .
-Otherwise, we may leave the inequalities in their pre-simplified forms and they are still valid when  $\xi_{1t} \xi_{2s} > 0$ or $\xi_{1s} \xi_{2t} > 0$.
+Otherwise, we may leave the inequalities in their original forms and they are still valid when  $\xi_{1t} \xi_{2s} > 0$ or $\xi_{1s} \xi_{2t} > 0$.
 \\ \hfill
@@
 And, assume we have the parameter restrictions mentioned in earlier in \hyperref[sec:cobbdoug]{Section A} that ensure $X, Z > 0$.
-This is a simple case where we have (1) a constant output reliable technology and (2) a completely intermittent technology.
+This is a simple case where we have (1) a constant output technology and (2) a highly intermittent technology.
 We now show that, in this case, the elasticity of substitution approaches $1$ as the relative cost of our second technology $c_2/c_1$ approaches $0$.
@@
 	\end{align*}
-	where $\alpha_t + \alpha_s = 1$ by definition (Equation (1)). Finally, it is simple to see that:
+	where $\alpha_t + \alpha_s = 1$ by definition (see \hyperref[sec:consumers]{Section II.A}). Finally, it is simple to see that:
 	$$ \lim_{c_2/c_1 \to 0} \frac{\partial \log(X_1/X_2)}{\partial \log(c_2/c_1)} = 1$$
@@
 \begin{table}[h!]
-	\captionsetup{justification=centering}
-	\caption*{\textbf{Figure B.1:} The Elasticity of Substition Between Two \newline  Minimally Intermittent Technologies} 
+	\captionsetup{format=centerproper}
+	\caption*{\textbf{Figure B.1:} The Elasticity of Substitution Between Two \newline  Minimally Intermittent Technologies} 
 	\label{fig:eosrange}
@@
 These results were obtained using the following parameters: $\alpha_t = 0.5$, $\alpha_s = 0.5$, $\xi_1 = (0.95, \, 1)$, $\xi_2 = (1, \, 0.95)$, $c_1 = 100$, $c_2 = 100$.
-In order to generate these numerical, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.5\, c_1, 1.5 \,c_1)$.
-Then, we obtained estimates of the elasticity of substition by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1, c_2)$.
+In order to generate these numerical results, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.5\, c_1, 1.5 \,c_1)$.
+Then, we obtained estimates of the elasticity of substitution by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1, c_2)$.
 That is, the elasticity of substitution  between technology 1 and 2 is given by the slope of the upper subplot, and it is graphed in the lower subplot.
@@
 \pagebreak
+
+We repeat the exercise done to produce \hyperref[fig:ves]{Figure 4} but with $\xi_2 = (1, 0.01)$.
+That is, we assume here that solar is far more intermittent.
+We plot our results below in \hyperref[fig:ves_int]{Figure B.2}.
+
+\begin{table}[t]
+	\captionsetup{format=centerproper}
+	\caption*{\textbf{Figure B.2:} The VES Approximation of the Elasticity of Substitution \\ between Highly Intermittent Solar and Coal} 
+	\label{fig:ves_int}
+	\footnotesize
+	\vspace{-1em}
+	\begin{tabular}{@{\extracolsep{0em}}c}
+		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_ves_approx_int} \\
+		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } Technology 1 is coal and technology 2 is solar.
+The purple, dash-dots line represents a linear approximation of $e_{1,2}$ for $\sigma = 0.8847$ with a fixed intercept of 1.
+These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.01)$, $c_1 = 104.3$, $c_2 = 60$.
+Furthermore, we set the parameter for the intertemporal elasticity of substitution for electricity consumption equal to our estimate $\hat{\sigma} = 0.8847$.
+In order to generate these numerical results, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.95\, c_1, 2 \,c_1)$.
+Then, we obtained estimates of the elasticity of substitution by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1, c_2)$.
+}     \\
+	\end{tabular}
+\end{table}
 
@@
 
+	\bibitem[Revankar(1971)]{VES}
+	Revankar, N. (1971). A Class of Variable Elasticity of Substitution Production Functions. Econometrica, 39(1), 61–71. https://doi.org/10.2307/1909140
+
 	\bibitem[Schwarz et al.(2002)]{Schwarz}

### 2019-05-10 documents/draft.tex
Update draft
- abstract clean up
- updates to method
- rewrite beginning of discussion
- label subsubsections
- add VES approx proof
- add econometric methodology explanation

@@
 \usepackage{varwidth}
+\usepackage{gensymb}
 %\usepackage{showframe}
@@
 \begin{addmargin}[0.5in]{0.5in}
-	\textit{ Use of renewable energy has increased greatly ... 
-		We evaluate renewable energy technologies in a partial equilibrium setting that integrates their production profiles with variation in the market price of electricity. 
-		In order to discount the ..., we use a representative agent that prefers to smooth their electricity consumption over time. 
-		We find a non-linear elasticity of substitution between intermittent and non-intermittent generation technologies.
-Hence, a CES production function fails to accurately model substitutability between renewables and fossil fuels.
-Alternatively, we find that a VES production function can reasonably approximate the effect of intermittency on the elasticity of substitution between between intermittent and non-intermittent energy.
-		Furthermore, our results suggest that the welfare burden of carbon taxes on consumers will vary geographically based on the availability of consistent, renewable technology.
-This distributional side effect can be counteracted by subsidizing research into battery technologies; improvements in batteries can also complement present policy to promote renewables by greatly increasing the substitutability of intermittent  and non-intermittent energy technologies.
+	\textit{In this paper, we present a model of the electricity sector where generation technologies are intermittent.
+The economic value of a electricity generation technology is given by integrating its production profile with the market price of electricity.
+We parametrize this model empirically and generate numerical results.
+The introduction of intermittency results in a non-constant elasticity of substitution between renewable and fossil energy.
+Consequently, this suggests that the efficacy and welfare effects of carbon taxes and renewable subsidies vary geographically.
+Subsidizing research into battery technology can mitigate this distributional side effect while complementing traditional policies used to promote renewable energy.
 	 }
@@
 
-Renewable energy technologies have seen considerable adoption over the last few decades (EIA 2019).
+Renewable energy technologies have seen considerable adoption over the last few decades \citep{EIArenew}.
 Unlike the alternatives, wind and solar power are particularly unique in that the amount of energy they supply is intermittent.
-Consequently, designing economically efficient policy to promote their adoption is not straightforward given that they cannot easily substitute for fossil fuel technologies such as coal power.
+Consequently, designing economically efficient policies to promote their adoption is not straightforward given that they cannot easily substitute for fossil fuel technologies such as coal power.
 Moreover, traditional economic measures such as the levelized cost of electricity (LCOE) fail to capture the true economic value of intermittent technologies, because they neglect to account for variation in output and prices over time \citep{Joskow2011}.
 
-Some of the literature has overcome this critique by constructing numerical models that find the cheapest renewable technology set while accounting for intermittent supply.
-For instance, \citet{MN2006} model uncertain renewable output with intertemporal generation constraints, while \citet{NCK2007} model temporal and spatial characteristics of wind output to optimize its deployment in the UK.
-On the other hand, other literature focuses on the effect of intermittent technologies on the market itself; \citet{AC2012} study the interaction between intermittent renewables and traditional reliable sources of energy in decentralized markets, and \citet{Chao2011} models alternative pricing mechanisms for intermittent renewable energy sources.
+Some of the literature has approached this problem by constructing numerical models that find the cheapest renewable technology set while accounting for intermittent supply.
+For instance, \citet{MN2006} model uncertain renewable output with intertemporal generation constraints, while \citet{NCK2007} model the temporal and spatial characteristics of wind output to optimize its deployment in the UK.
+Other papers study how intermittent technologies affect the market itself; \citet{AC2012} study the interaction between intermittent renewables and traditional reliable sources of energy in decentralized markets, and \citet{Chao2011} models alternative pricing mechanisms for intermittent renewable energy sources.
 Additionally, \citet{Boren2012} reviews the effects of present public policies used to promote renewables and the challenges posed by intermittency.
@@
 Furthermore, they simplify their analysis by setting aside complications such as  outage costs and rationing rules.
-In total, their model finds an S-shaped adoption curve for renewables as they get cheaper.
+Their model finds an S-shaped adoption curve for renewables as they get cheaper.
 In addition, they find that a Pigouvian tax can properly internalize the costs of fossil fuels in a setting with perfect competition.
-Likewise, we model the  equilibrium of a market with dynamic prices and access to both renewable and fossil energy.
+Like \citeauthor{HH}, we model the  equilibrium of a market with dynamic prices and access to both renewable and fossil energy.
 However, our results differ in key ways, because we take a different approach to modeling intermittency.
@@
 To highlight this difference, we must first contrast the terms  \textit{intermittency} and \textit{reliability}.
-By intermittency, we predictable changes in output related to physical constraints.
-For instance, while wind energy output varies over time, if  we know the angle and speed of wind, we may precisely derive the quantity of energy that a wind farm generates.\footnote{ \citet{Foley2012} provide a review of the literature on the forecasting of wind power.
-Over time, forecasts have gotten much more accurate allowing electricity grids to manage wind power intermittency ahead of time.}  At the same time, these forecasts may not be perfect and, as a result, we see unexpected variation in the output of a technology.
-This unpredictability may be better captured by the notion of reliability; specifically,  we refer to definition provided by the US Department of Energy's \citet{ORNL} -- ``Power reliability can be defined as the degree to which the performance of the elements in a bulk system results in electricity being delivered to customers within accepted standards and in the amount desired." This is more so related to the stochastic or unpredictable variation in the output of a technology.
+By intermittency, we mean predictable changes in output related to physical constraints.
+For instance, while wind energy output varies over time, if  we know the wind speed and angle, we may precisely derive the quantity of energy that a wind farm generates.\footnote{ \citet{Foley2012} provide a review of the literature on the forecasting of wind power.
+Over time, forecasts have gotten much more accurate allowing electricity grids to manage wind power intermittency ahead of time.}  At the same time, wind forecasts are not be perfect, so we may see unexpected variation in the electricity output of a wind farm.
+This unpredictability is better captured by the notion of reliability; specifically,  we refer to definition provided by the US Department of Energy's \citet{ORNL} -- ``Power reliability can be defined as the degree to which the performance of the elements in a bulk system results in electricity being delivered to customers within accepted standards and in the amount desired." This is more so related to the stochastic or unpredictable variation in the output of a technology.
 Unlike intermittency, this cannot be planned around with 100\% certainty.
@@
 While we may know the chances of this occurring, it's not possible to know when it will occur ahead of time; consequently, this may result in a temporary reduction in the quantity and quality of the electricity delivered --  a loss of reliability.
-In short, when \citeauthor{HH} define renewable output as equal to a baseline capacity multiplied by a uniform random variable, their model is closer to one of reliability rather than intermittency.
+In short, when \citeauthor{HH} model renewable output as equal to a base capacity multiplied by a uniform random variable, their treatment is closer to one of reliability rather than intermittency.
 
 On the other hand,  we model intermittency as defined above by allowing the output of renewable energy to differ between periods according to known function.
-For parsimony, we assume that the output of all technologies in each period does not vary stochastically; that is, we focus on intermittency rather than reliability.
+For parsimony, we assume that the output of each technology  does not vary stochastically; that is, we do not study reliability.
 Next, we model the electricity sector using a representative firm that chooses and builds capacity from a set of electricity-generating technologies to maximize profit; some of these technologies are intermittent while others have constant output.
 Then, we consider a representative consumer who purchases varying quantities of electricity in each period in order to maximize utility.
-Generally, people prefer to spread their electricity consumption out over time.
-We model this preference by using a CES function of electricity consumption differentiated by period.\footnote{ The use of a CES function in this way has been explored earlier by \citet{Schwarz}, \citet{Schwarz}, \citet{Herriges}, and \citet{KS1994}, \citet{Aubin}, and \citet{Moha2016}.
+People prefer to smooth their electricity consumption over time, so we model our consumer's preferences using a CES function of electricity consumption differentiated by period.\footnote{ The use of a CES function in this way has been explored earlier by \citet{Schwarz}, \citet{Schwarz}, \citet{Herriges}, and \citet{KS1994}, \citet{Aubin}, and \citet{Moha2016}.
 Their papers empirically estimate the parameters for this function; we provide a more detailed discussion of the empirical literature in our \hyperref[sec:methodology]{Methodology}.} These two sides of the market reach an equilibrium through adjustments in prices of electricity in each period.
-All in all, we make many of the same assumptions that \citet{HH} do; we assume dynamic pricing,\footnote{ \citeauthor{HH} provide a motivation for models incorporating the dynamic pricing of electricity.
-They argue such approaches to pricing will become the norm with further technological advances and coming regulatory changes.} no load rationing, and positive prices.
+Overall, we make many of the same assumptions that \citet{HH} do; we assume dynamic pricing,\footnote{ \citeauthor{HH} motivate models incorporating the dynamic pricing of electricity.
+They argue that such approaches to pricing will become the norm with further technological advances and coming regulatory changes.} no load rationing, and positive prices.
 
 Then, we parametrize our model empirically.
-To start, we fit the parameters of the consumer's CES utility function using electricity consumption and price data for each US state.
-Specifically, we estimate the intertemporal elasticity of substitution for electricity consumption; this parameter plays a particularly important role in our model, since it captures the effects of intermittency on demand.
-Then, to model the supply side, we narrow our model to a two-period, two-technology setting with renewables and fossil energy.
-We proxy for renewable energy using solar and proxy for fossil energy using coal; then, we parametrize each accordingly.
-Finally, we implement our model numerically and solve for the equilibrium.
-We study the effects of technical change on the energy market and derive policy implications.
-
-Overall, this treatment of intermittency produces some key results that contrast with those of Helm and Mier.
-First, while we also find that externalities can be handled through a Pigouvian tax, we further find that a combining both taxes on pollution and research subsidies for renewables is more optimal than either policy instrument alone.
-Second, we find that, as renewables get cheaper, their adoption is not necessarily S-shaped but can be concave or convex depending the elasticity of substitution in the consumer's utility function; with our estimated parameters, we find this relationship to be almost linear.
-Third, a significant amount of literature has assumed a CES structure between renewable and fossil energy (see \citet{Pap}); this assumption has been motivated, in part, by the need to capture imperfect substitutability between these two generation technologies as a result of intermittency.
-However, our direct model of intermittency disconfirms this assumption; the elasticity of substitution between these two energy technologies is far from constant as a \textit{consequence} of intermittency.
-Moreover, it varies with the prices and quantities of energy generation technologies employed.
-Hence, we believe that optimal environmental policy, such as pollution taxes and research subsidies, should take into account the technologies powering local energy markets in order to effectively handle externalities.
+We fit the parameters of the consumer's CES utility function using electricity consumption and price data for each US state.
+That is, we estimate the intertemporal elasticity of substitution for electricity consumption; this parameter plays a particularly important role in our model, since it captures the effects of intermittency on demand.
+Next, to model the supply side, we narrow our framework to a two-period, two-technology setting to focus on the substitutability between renewable and fossil energy.
+We proxy for renewable and fossil energy using solar and coal; we parametrize each accordingly.
+Finally, we implement our model numerically and provide suggestions for policy and future models.
+
+Our results show that the elasticity of substitution between renewable and fossil energy is not constant.
+This is important because a significant amount of literature has assumed a CES structure between renewable and fossil energy (see \citet{Pap}); this assumption has been motivated, in part, by the need to capture imperfect substitutability between these two generation technologies as a result of intermittency.
+But, our model finds that the elasticity of substitution between renewable and fossil energy is far from constant as a \textit{consequence} of intermittency.
+Specifically, this elasticity appears to vary with the quantity of each energy technology.
+Hence, we argue against assuming a CES structure.
+Alternatively, we find that a VES production function can be used to approximate the relationship that our model finds between the elasticity of substitution and the quantities of each technology.
+That is, this relationship is roughly linear which is exactly what a VES function assumes.
+Moreover, a VES function is analytically tractable, so it can be implemented in other frameworks without making them overly complicated.
+
+Additionally, our results have multiple important implications for environmental/energy policy.
+Firstly, we find that the welfare burden of a carbon tax  and the effect of subsidies on renewable adoption both vary geographically.
+This variation is a consequence of differences in the intermittency and availability of renewable energy by location.
+Moreover, this can create a trade-off between equitably and efficiently mitigating climate change.
+Hence, policymakers should account for geographic variation in energy markets to ensure they handle this equity-efficiency trade-off appropriately.
+Secondly, we find strong motivation for research subsidies aimed at improving battery technology.
+That is, better energy storage can greatly increase the elasticity of substitution between renewable and fossil energy.
+Also, batteries can  lessen the distributional side effects of carbon taxes and renewable subsidies by  reducing intermittency.
+Hence, research into improving batteries can complement other policies by making them more equitable and by increasing their impact on the adoption of renewables.
+Finally, we revisit the results of \citet{Ace2012} and qualitatively discuss the implications of our model in their setting.
+We now discuss our model in greater detail.
 
@@
 
-Consumers purchase variable amounts of electricity $Z_t$ over each period $t$.
-Additionally, assuming that the price of electricity in each period is held constant, they prefer to ration their electricity usage across each period in fixed proportions.
-And, lastly, we presume that consumers would be willing to shift their consumption from one period to another in response to a shift in prices.
-Overall, these assumptions can be captured using a a standard CES utility function
+Consumers purchase a quantity of electricity $Z_t$ in each period $t$.
+Furthermore, they demand a greater quantity of electricity in certain periods; for instance, consumers need more electricity during the middle of the day more than at night.
+At the same time, consumers are willing to shift their consumption from one period to another in response to a shift in prices.
+Overall, these characteristics can be captured using a standard CES utility function.
+Furthermore, since CES preferences are homothetic, we may aggregate the consumers into a single representative consumer.
+This consumer has the utility function
 \begin{equation}
@@
 where $\sigma = 1/(1-\phi)$ is the intertemporal elasticity of substitution for electricity consumption.
-We define $\sum_t \alpha_t = 1$, so that $\alpha_t$ is the fraction of electricity consumption in period $t$ when all prices are equal; naturally, $\alpha_t > 0$ for all $t$.
-We assume that any discounting over time is absorbed into $\alpha$ for parsimony.The budget constraint is given by
+To ensure that indifferences surfaces are convex, we have $\phi \in (0,1)$ or, equivalently,  $\sigma > 0$; additionally, since electricity consumption increases utility, we must have $\alpha_t > 0$ for all $t$.
+For simplicity, we also define $\sum_t \alpha_t = 1$, so that a 1\% increase in electricity consumption in all periods increases utility by 1\%; consequently, we then have $\alpha_t \in (0,1)$.
+The budget constraint is given by
 \begin{equation}
@@
 where $p_t$ is the price of electricity in period $t$ and $I$ is the income.
-Furthermore, since CES preferences are homothetic, we may aggregate the consumers into a single representative consumer.
-Consequently, the first order conditions four our representative consumer when maximizing utility given this budget constraint imply:
+Our representative consumer maximizes utility against this budget constraint; the first order conditions of this problem imply:
 \begin{align}
@@
 In reality, electricity markets are fairly competitive, so we can model the set of firms by using a single representative firm that sets marginal revenue equal to marginal cost.
-We define the quantity of deployed energy technology $i$ as $X_i$, and we define its output per unit in period $t$ as $\xi_{1,t}$.
-So, for example, if $i$ is solar power, $X_i$ would be the number of solar panels and $\xi_{i,t}$ may be kW generated per solar panel in period $t$.
+
+We let $X_i$  represent the quantity of energy technology $i$ , and we define its output per unit in period $t$ as $\xi_{1,t}$.
+So, for example, if $i$ is solar power, $X_i$ would be the number of solar panels and $\xi_{i,t}$ may be kWh generated per solar panel in period $t$.
 Consequently, the energy generated in period $t$, $Z_t$, is given by $\sum_i \xi_{i,t} X_i$.
-We define these variables in matrices to simplify notation:
+To simplify notation, we have
 \begin{align*}
@@
 A key element of this model is that $X$ does not vary by time.
-This is important, because the time scale of our model must be fairly granular to study the effects of intermittency.
+This is important because the time scale of our model must be fairly granular to study the effects of intermittency.
 So, for instance, we may have $t \in \{ 1, \dots, 24\}$ representing each hour of the day.
-In such short time scales, we can safely assume that producers do not modify the quantity of the technology they employ.
-Moreover, this keeps the model parsimonious by preventing more complicated dynamics from entering the producers optimization problem.
-
-Instead, our representative firm sets $X$ once to maximize profit in all periods while facing the cost function $C(X_1, \dots, X_n)$.
-\citet{HH} note that past literature has argued for concave cost functions in the energy market due to effects such as economics of scale and learning by doing; on the other hand, standard cost functions are generally convex.
+Over such short time scales, the intermittency of renewables like solar and wind can significantly affect their economic value.
+Additionally, this allows us to assume that producers cannot modify the quantity of the technologies they deploy.
+And, thirdly, for certain technologies, this time frame is short enough to assume that $\xi$ is exogenous; that is, technologies like coal power cannot significantly modify their output within a day, so $\xi$ can be treated as a given set of constants.
+These latter two assumptions, that $X$ cannot change over time and that $\xi$ is exogenous, are important for parsimony, because they prevent more complicated dynamics for entering our model.
+So, by assuming a sufficiently short time frame, we can continue our study of intermittency in a relatively simpler setting.
+
+Next, our representative firm sets $X$ once to maximize total profit while facing the cost function $C(X_1, \dots, X_n)$.
+\citet{HH} note that past literature has argued for concave cost functions in the energy market due to effects such as economies of scale and learning-by-doing; on the other hand, standard cost functions are generally convex.
 So, like Helm and Meir, we take an intermediate approach by using a linear cost function.
@@
 
-For more tractable results, we consider a simpler scenario where $n = m = 2$ and $\sigma = 1$ (Cobb-Douglas); this particular case is described in greater  detail with proofs in \hyperref[sec:cobbdoug]{Appendix A.A}.
-Moreover, these parameters are of particular interest, because they simplify the model enough to allow us to derive comparative statics and determine which sets of parameters lead to edge cases.
-
-To start, we discuss the conditions on the exogenous parameters required to avoid edge-cases.
-Alternatively, these are the conditions required for a technology to be economical.
-But, first, we define two recurring terms in our analysis: cost efficiency and output efficiency.
+For more tractable results, we consider a simpler scenario where $n = m = 2$ and $\sigma = 1$ (Cobb-Douglas); this particular case is described in greater  detail  in \hyperref[sec:cobbdoug]{Appendix A.A}.
+These parameters simplify the model enough to allow us to derive comparative statics and determine which sets of parameters lead to edge cases.
+Furthermore, as we will discuss in our \hyperref[sec:results]{results}, assuming $\sigma=1$ is not far from its empirical estimate.
+
+To start, we discuss the conditions required on the exogenous parameters  to avoid edge-cases.
+But  first, we define two recurring terms in our analysis: cost efficiency and output efficiency.
 For some arbitrary period $t$ and technology $i$, we use cost efficiency to refer to $\xi_{i,t}/c_i$ and output efficiency to refer to $\xi_{i,t}$.
-So, for example, A technology is more cost efficient than another in a particular period when its output in that period per ``dollar" spent is larger than that of the other technology in the same period.
+So, for example, with two technologies $i$ and $j$ and an arbitrary period $t$, technology $i$ is more cost efficient than technology $j$ in period $t$ when $\xi_{i,t}/c_i > \xi_{j,t}/c_j$.
+Additionally, we say a technology is economical if its equilibrium quantity is above 0.
+In order to avoid an edge-case, we require both technologies to be economical; we give the conditions to ensure this for each technology in Proposition 1.
 \begin{proposition}
-	Assume that, for all  $i$ (technologies) and  $t$ (periods), we have $\xi_{i,t} > 0 \, , \alpha_t > 0 \, ,$ and $ c_i > 0$.
-Furthermore, suppose that $\xi$ is invertible.
-For technology $i$ to be economical, it must meet three conditions with respect to some arbitrary period $t$.
-Firstly, it must the more cost effective than any of the other technologies in period $t$.
-Secondly, it must have have a comparative advantage in output efficiency in the same period $t$.
-And, thirdly, there must be sufficient amount of demand for energy in this period $t$.
+	Assume that, for all technologies $i$ and  periods $t$, we have $\xi_{i,t} > 0 \, , \alpha_t > 0 \, ,$ and $ c_i > 0$.
+For technology $j$ to be economical, it must meet three conditions with respect to some arbitrary period $s$.
+Firstly, it must be more cost effective than any of the other technologies in period $s$.
+Secondly, it must have  a relative advantage in output efficiency in the same period $s$.
+And, thirdly, there must be sufficient amount of demand for energy in this period $s$.
 \end{proposition}
-The condition on cost efficacy is fairly intuitive; one case of the contrapositive is that if a technology is not the most cost effective in any period, it will not be used.
+The first condition is on cost efficacy and is fairly intuitive.
+Consider its contrapositive: if a technology does not have an advantage is cost efficiency in any period, it will not be used; this is fairly obvious.
 Alternatively, if a technology is the most cost effective in every single period, it will be the only technology used.
@@
 If we did not have $\xi$ invertible, we either have at least one technology that does not produce in any period or we have at least one technology being a linear combination of the other technologies in terms of output.
-In the latter case, some technologies are not economical because their output can be replicated the other technologies in a more cost effective way.
-As an example, suppose $\xi$ consisted of 3 technologies but was of rank $2$.
+In the latter case, some technologies are not economical because their output can be replicated by the other technologies in a more cost effective way.
+That is, suppose $\xi$ consisted of 3 technologies but was of rank $2$.
 In this case, we may represent any of these technologies as a linear combination of the other two; call this combination the synthetic version of technology $i$.
@@
 In the first case, synthetic technology $i$ is cheaper so we do not use the actual technology $i$.
-In the later case, we may still eliminate technology $i$ or not use the other two technologies depending on the demand.
+In the latter case, we may still eliminate technology $i$ or not use the other two technologies depending on the demand.
 Overall, in any case, $\xi$ not invertible means that at least one technology is not used.
@@
 Also, suppose that some technology $i$ is the most cost effective in period $t$.
-Then, its equilibrium quantity is increasing with respect to the demand share parameter $\alpha_t$ and decreasing with respect to the demand share parameters of the other periods.
+Then, its equilibrium quantity is increasing with respect to the demand parameter $\alpha_t$ and decreasing with respect to the demand parameters of the other periods.
 Furthermore, again assuming technology $i$ is the most cost effective in period $t$, the comparative statics of $Z_t$ and $X_i$ are equivalent.
@@
 Instead, they follow from the fact that we have $Z \equiv \xi_T X$.
-That is, suppose we have an arbitary technology $i$ that is the most cost effective source of electricity on period $t$.
+That is, suppose we have an arbitrary technology $i$ that is the most cost effective source of electricity in period $t$.
 If consumers demanded that 100\% of their energy arrive in period $t$, then relying solely on technology $i$ for energy would be the most economical solution.
@@
 A rise in $\alpha_t$ would directly raise the optimal quantity of $Z_t$; hence, whichever technology is most cost effective at producing in period $t$ would be used more.
-We provide a more detailed and quantitative discussion of the comparative statics and edge cases in the appendix.
+We provide a more detailed and formal discussion of the comparative statics and edge cases in the appendix.
 
@@
 We are particularly interested in estimating $\sigma$, the intertemporal elasticity of substitution for electricity consumption.
-In our  \hyperref[sec:Discussion]{discussion}, we explain in detail why $\sigma$ is of interest; but, to summarize, $\sigma$ implicitly determines how well renewables can substitute for fossil energy.
+In our  \hyperref[sec:Discussion]{discussion}, we explain in detail why $\sigma$ is of interest; to summarize, $\sigma$ implicitly determines how well renewables can substitute for fossil energy.
 Specifically, if $\sigma > 1$, then electricity consumption in different periods are substitutes; consequently, fossil energy and renewable energy are highly substitutable.
-On the other hand, if $\sigma$ is around $0.5$, electricity consumption in different periods are complements; so, fossil and renewable energy are far less substitutable due to the effects of intermittency.
-
+On the other hand, if $\sigma< 1$, electricity consumption in different periods are complements; so, fossil and renewable energy are far less substitutable due to the effects of intermittency.
 The other parameters in our model, $c$,  $\xi$, and $\alpha$, are of secondary interest, since they are easier to obtain directly.
-To start, $c$ is the cost per unit for each technology; estimates of this value for different technologies can be obtained directly from the literature.
-Similarly, $\xi$, the output per unit of technology, can be directly obtained from the literature.
-And, finally, $\alpha$ may be approximated directly from the data.
-That is, note that the demand equation from earlier (Equation 3) is:
+
+Now, recalle that the demand equation from earlier (Equation 3) is:
 $$Z_t = \left(\frac{\alpha_t}{p_t} \right)^\sigma \frac{I}{P}$$
@@
 Consequently, all variation in intramonthly demand is due to the share parameter $\alpha$ and the elasticity $\sigma$.
-Hence, after estimating $\sigma$, we can approximate $\alpha$.
-However, this raises another problem, because, without prices varying each hour, we cannot estimate  $\sigma$ on an hourly basis.
+But, this creates a problem; since retail consumers do not face prices that vary each hour, we cannot estimate  $\sigma$ on an hourly basis.
 
 A number of other papers have approached this problem using data from real-time pricing experiments.
-These include \citet{Schwarz}, \citet{Herriges}, and \citet{KS1994}.\footnote{ There has also been a large literature that directly estimates the price elasticity of electricity demand without imposing a CES functional form.
+\footnote{ There has also been a large literature that directly estimates the price elasticity of electricity demand without imposing a CES functional form.
 These papers include \citet{Wolak}, \citet{Zarnikau}, \citet{Woo}, \citet{Zhou}, \citet{Reiss}, \citet{Fan}, and \citet{Deryugina}.
@@
 Because they do not impose a CES structure, we cannot obtain estimates of $\sigma$ from this literature.
-}
-The latter two papers estimate $\sigma$ to be around $0.1$ while the paper by \citeauthor{Schwarz}  obtain estimates around $0.04$.
+} In such experiments, consumers of electricity face prices that vary on an hourly basis; this makes it possible to estimate $\sigma$.
+Papers that use these experiments include \citet{Schwarz}, \citet{Herriges}, and \citet{KS1994}.
+The latter two papers estimate $\sigma$ to be around $0.1$ while the paper by \citeauthor{Schwarz}  obtains estimates around $0.04$.
 All three papers study real-time electricity pricing programs for industrial consumers using similar methodologies.
-Additionally, \citet{Aubin} also provide estimates of the $\sigma$ but using a different methodology; their results find elasticity of substitution below 0.
+Additionally, \citet{Aubin} also provide estimates of the $\sigma$ but using a different methodology; their results find an elasticity of substitution below 0.
 Under a CES structure, this is problematic, because it would imply upward-sloping demand curves.
-Finally, \citet{Moha2016} also empirically estimates the share parameters for a CES function of this form, but do not estimate the elasticity of substitution.
-
-Overall, the past literature has approached the estimation of $\sigma$ by running regressions with variants of the CES demand equation.
-We are concerned about endogeneity, because producers may intertemporally substitute electricity generation.
+Finally, \citet{Moha2016} also empirically estimates the share parameters for a CES function of this form, but they do not estimate the elasticity of substitution.
+
+Overall, the past literature has estimated $\sigma$ by running regressions on the CES demand equation, however we are concerned that this approach suffers from endogeneity.
+That is, producers may intertemporally substitute electricity generation which essentially means that there is a supply equation affecting prices.
 For instance, during the oil crisis of 1973, refineries increased gasoline stocks expecting future prices to be higher \citep{genie}.
 The existence of such behavior implies that estimates of $\sigma$ would be biased downwards unless we properly control for endogeneity.
-This is particularly important because whether $\sigma$ is closer to 0.1 or 1 significantly change the practical implications of our model.
+This is particularly important because whether $\sigma$ is closer to 0.1 or 1 significantly changes the practical implications of our model.
 
@@
 For instance, \citet{Schwarz} estimate $\sigma$ on a daily and hourly basis and find fairly close results; similarly, \citet{Herriges} also find no significant difference in their estimates of $\sigma$ for these two intervals.
-That is, while a daily basis is 24 times larger than an hourly basis, the estimates for $\sigma$, suprisingly, do not appear to change.
+That is, while a daily basis is 24 times larger than an hourly basis, the estimates for $\sigma$, surprisingly, do not appear to change.
 Hence, we expect our estimates of $\sigma$ on a monthly basis to not be far from estimates on shorter time scales.
@@
 \end{align*}
-For any pair of electricity ouputs $Z_t$ and $Z_s$, we have:
+For any pair of electricity outputs $Z_t$ and $Z_s$, we have:
 $$\frac{Z_t}{Z_s} = \left(\frac{\alpha_t \, p_s}{\alpha_s \, p_t} \right)^\sigma \\$$
@@
 Additionally, most consumers pay monthly fixed rates for electricity, so we can, at most, estimate this equation on a monthly basis; hence, $t$ and $s$ refer to different months.
-Lastly, note that the state $i$ is kept constant for each observation; this is because consumers within each state can substitute consumption across time, but consumers in different states do not substitute consumption with one another.
-
-In order to estimate this $\sigma$, we further modify the previous equation. 
+Also, note that each observation only corresponds to a single state $i$; this is because consumers within each state can substitute consumption across time, but consumers in different states do not substitute consumption with one another.
+
+In order to estimate this $\sigma$, we further modify this equation. 
 Firstly, note that we cannot observe the demand shifter $\alpha_{t,i}$ directly, so we must replace the $\alpha$ terms with a set of controls that may be responsible for shifts in demand.
@@
 where $A$ represents set of controls for changes in demand while $u_i$ is a normal error term.
-Note that the control  $A_{t,i}$ replaces $\sigma \ln(\alpha_{t,i})$ and likewise for the period $s$ term; this substitution is valid because the $\ln(\alpha_{t,i}) \in \mathbb{R}$ and the $\sigma$ is simply absorbed into the estimated coefficient for $\gamma_{t,i}$.
-For the demand controls themselves, we choose to use heating (HDD) and cooling degree days (CDD) due to the aggregation of the data.
-That is, a more general control such as average temperature would not be able to directly capture intramonthly changes in demand, since variation in temperature would be lost when aggregated; on the other hand, CDDs and HDDs directly represent daily deviations in temperature even when totaled for each month.
-Additionally, demand for electricity may rise over time.
+Note that the control  $A_{t,i}$ replaces $\sigma \ln(\alpha_{t,i})$ and likewise for the period $s$ term; this substitution is valid because the $\ln(\alpha_{t,i}) \in \mathbb{R}$ and the $\sigma$ term is simply absorbed into the estimated coefficient $\gamma_{t,i}$.
+For the demand controls themselves, we consider degree days and the difference in months between periods $t$ and $s$.
+Firstly, we use degree days rather than temperature due to the aggregation of the data.
+A degree day is defined as the difference between the average temperature for a day and a base temperature -- our data uses 65 \degree F (18 \degree C).
+Cooling degree days (CDDs) and heating degree days (HDDs) further split this measure into deviations above and below the base temperature.
+That is, if the average temperature of a day is $x$ \degree F, its CDD is $\max \{0, x-65\}$ and its HDD is $\max \{0, 65-x\}$ .
+Since these measures are linear, CDDs and HDDs can be aggregated without losing information.
+This does not hold true for temperature; averaging temperature over a month causes daily variation to be lost.
+Secondly, the demand for electricity may rise over time.
 Hence, we include, as a control, the difference in months between time $t$ and $s$; this is represented by $\Delta_{t,s}$.
@@
 
-Still, this equation may suffer from bias, since producers can also substitute production over time.
-For instance, it is possible to store fuel for electricity generation in the future when prices may rise.
-So, we define the following supply equation
+Still, this equation may suffer from bias, since producers can also substitute production over time. To address endogeneity concerns, we define the following supply equation
 \begin{align*}
@@
 where $C_{t,i}$ is the average cost of coal used for electricity generation in state $i$ at time $t$ and $v_i$ is a normal error term.
-Coal prices are independent of the electricity demand error term $u_i$, since residential consumers do not generally use coal for electricity generation; on the other hand, shocks in the price of coal are linked with the supply of electricity.
+Coal prices are independent of the electricity demand error term $u_i$, since residential consumers generally do not  use coal for electricity generation; on the other hand, shocks in the price of coal are linked with the supply of electricity.
 Hence, coal price is a theoretically valid instrument.
 In total, the reduced form equation is given by:
-$$ \ln (P_{t,i} / P_{s,i}) = \left( \beta + \sigma \right)^{-1} \left( \gamma_{t,i} A_{t,i} + \gamma_{s,i} A_{s,i} + \eta \Delta_{t,s} - \xi \ln (C_{t,i} / C_{s,i}) + u_{i} - v_i \right)  $$
+\begin{equation}
+ \ln (P_{t,i} / P_{s,i}) = \left( \beta + \sigma \right)^{-1} \left( \gamma_{t,i} A_{t,i} + \gamma_{s,i} A_{s,i} + \eta \Delta_{t,s} - \xi \ln (C_{t,i} / C_{s,i}) + u_{i} - v_i \right)  
+ \end{equation}
 where $A_{t,i}$ consists of CDDs and HDDs at time $t$.
@@
 So, overall, we have:
-\begin{align*}
+\begin{align}
 \ln (Z_{ t, i} / Z_{ s, i}) &= -\sigma \ln (P_{t,i} / P_{s,i}) +  f \left( A_{t,i}, A_{s,i}, \Delta_{t,s} \right) + u_i \\
 \ln (Z_{ t, i} / Z_{ s, i}) &= \beta \ln (P_{t,i} / P_{s,i}) + g \left( \ln (C_{t,i} / C_{s,i})  \right) + v_{i}
-\end{align*}
+\end{align}
 where $f$ and $g$ are unknown, bounded functions.
@@
 The advantage of this specification is that we can account for the controls or instrument having any nonlinear effects on the regressands.
-\textbf{(More here on explaining the estimation)}
-
+In order to estimate these equations, we use a procedure based on \citet{Newey} that we describe in further detail in \hyperref[sec:AppendixC]{Appendix C}.
+\noindent
+
+\noindent
 \subsection{Data}
@@
 \section{Results}
+\label{sec:results}
 
@@
 Specifically, in fit (3), we have $\hat{\sigma} = 0.8847$ ($|t| > 20$).
-The estimates of $\sigma$ with less controls are much larger.
+The estimates of $\sigma$ with fewer controls are much larger.
 However, based on the OLS and IV results, it seems that both the time control and degree day controls are significant.
@@
 
-\pagebreak
-\vspace{1em}
+\clearpage
 \section{Discussion}
@@
 
-To understand the economic implications of these estimates for $\sigma$, we parametrize and numerically evaluate our model in a two-period, two-technology setting.
-In particular, we are concerned with how $\sigma$ affects the substitutability of fossil and renewable energy.
+We are concerned with how $\sigma$ affects the substitutability of fossil and renewable energy.
 This is important, because sufficient substitutability between these two technologies is required to transition into greener economy in the future.
@@
 Hence, we let $\xi$ represent the percent of capacity utilized in each period; we assume coal uses 100\% of its capacity in both periods, while solar can access 100\% during peak hours and only 10\% during the off-peak.
-Finally, we set the cost parameters, given in  \$ per MWh, equal to LCOE\footnote{ The LCOE for a technology is equal to the sum of its lifetime costs divided by its lifetime energy output.
+Finally, we set the cost parameters, given in  \$ per MWh, equal to LCOE\footnote{ The LCOE for a generation technology is equal to the sum of its lifetime costs divided by its lifetime energy output.
 \citet{Joskow2011} explains the flaws of comparing generation technologies solely on the basis of LCOE; but,  our use of this measure is unrelated to his critique.
@@
 
-The first relationship we see in \hyperref[fig:eosnum]{Figure 1} is that $e_{1,2}$ varies non-linearly with the relative costs of each technology; in particular, it appears to take on a hook shape.
+The first relationship we see in \hyperref[fig:eosnum]{Figure 1} is that $e_{1,2}$ varies non-linearly with the relative costs of each technology; in particular, it appears to take on a hockey stick shape.
 This shape is a result of both intermittency and costs.
 Intermittency reduces substitutability as overall energy generation becomes more intermittent.
-In other words, intermittency is bigger issue for consumers when their energy supply is not consistent.
+In other words, intermittency is a bigger issue for consumers when their energy supply is not consistent.
 This causes $e_{1,2}$ to fall when the majority of energy generated comes from solar; naturally, the latter occurs when $\log(c_2/c_1)$ is small (solar is relatively cheap).
@@
 } That is, $e_{1,2}$ rises when the relative prices of solar and coal are very different.
-When these two effects interact, we see the elasticity of substitution between solar and coal take on a hook shape.
+When these two effects interact, we see the elasticity of substitution between solar and coal takes on a hockey stick shape.
 
@@
 Consequently, this implies that the elasticity of substitution $e_{1, 2}$ will be larger.
-Hence, in the lower subplot of \hyperref[fig:eosnum]{Figure 1}, we see that $e_{1, 2}$ rises with $\sigma$ when holding relative prices of each technology constant.
+Hence, in the lower subplot of \hyperref[fig:eosnum]{Figure 1}, we see that $e_{1, 2}$ rises with $\sigma$ when holding the  relative prices of each technology constant.
 Secondly, we find that $e_{1,2}$ becomes more u-shaped as $\sigma$ rises.
@@
 Consequently, the shape of the elasticity of substitution $e_{1,2}$ becomes more dependent on the relative costs.
-As argued earlier, when costs differ greatly between technologies, the elasticity of substitution $e_{1,2}$ is higher; this effect causes $e_{1,2}$ to take on a u-shape.
-So, in total, as $\sigma$ rises, we expect $e_{1,2}$ to become increasingly u-shaped.
+As argued earlier, when costs differ greatly between technologies, the elasticity of substitution $e_{1,2}$ is higher.
 
@@
 
-\subsection{Implications for Pollution Abatement}
-
-Overall, our results have shown that the traditional assumption of a CES relationship between renewable and fossil energy is inappropriate.
-However, since $e$ takes on a fairly simple shape, we can still adjust the findings of past models to account for variation in the elasticity of substitution.
-For example, consider again the results of \citet{Ace2012}.
-
-Firstly, they find that the short-run cost of policy intervention is increasing with the elasticity of substitution between clean and dirty technologies.\footnote{ See Corollary 1 of their paper for a proof and intuitive explanation.} We find that the elasticity of substitution between renewable and fossil energy is decreasing with intermittency.
-Consequently, this implies that regions with access to clean, non-intermittent energy (such as hydro and geothermal energy) will require the most expensive interventions.
-Additionally, their paper states that the cost of delaying intervention is increasing with the elasticity of substitution $e$ as well.
-So, this implies that delaying policy intervention is also the most costly in regions with access to non-intermittent, clean energy.
-
-Secondly, \citeauthor{Ace2012} argue that, when the discount rate and elasticity of substitution between clean and dirty energy ($e$) is sufficiently low, a disaster cannot be avoided under laissez-faire.\footnote{ See Proposition 9 of their paper.} In our model, it is possible for $e$ to start at a large value and transition to much smaller values as clean energy becomes cheaper; this occurs when the source of clean energy is highly intermittent.
-On the other hand, if clean energy is not intermittent, it will be highly substitutable with dirty energy no matter their relative prices.
-This latter case would likely not lead to disaster but the former case (with high intermittency) would.
-Hence, we offer an alternative interpretation of this proposition: when the discount rate is sufficiently low and the intermittency of clean energy is sufficiently high, a disaster cannot be avoided under laissez-faire.
-The intuition here is that, even if clean energy became relatively cheap, it would fail to properly substitute  for fossil energy as a result of intermittency.
-Hence, the laissez-faire equilibrium would require policy intervention to avoid a climate disaster.
-
-Finally, \citeauthor{Ace2012} find that, ``when the elasticity
-of substitution is high\dots\, a relatively small carbon tax is sufficient to
-redirect R\&D towards clean technologies." Recall that, in our model, we see that $e$ changes with relative prices; when fossil fuels are relatively cheap, $e$ is large.
+\subsection{Implications for Environmental Policy}
+
+Overall, our results suggest that the elasticity of substitution between  renewable and fossil energy is not constant.
+Furthermore, it appears to fall with the level of intermittency.
+What implications does this result have?
+
+\subsubsection{Revisiting Past Models}
+
+To start, we consider how  a variable elasticity of substitution affects past models of the energy sector.
+As an example, consider the results of \citet{Ace2012}.
+Firstly, they find that the short-run cost of policy intervention is increasing with the elasticity of substitution between clean and dirty technologies.\footnote{ See Corollary 1 of their paper for a proof and intuitive explanation.} Additionally, their paper states that the cost of delaying intervention is increasing with the elasticity of substitution.
+Secondly, \citeauthor{Ace2012} argue that, when the discount rate and elasticity of substitution between clean and dirty energy ($e$) is sufficiently low, a disaster cannot be avoided under laissez-faire.\footnote{ See Proposition 9 of their paper.} And, finally, \citeauthor{Ace2012} find that, ``when the elasticity of substitution is high\dots\, a relatively small carbon tax is sufficient to redirect R\&D towards clean technologies."
+
+Based on our results, each of these statements has a complementary interpretation in terms of intermittency.
+For instance, the first statements suggests that the cost of policy intervention is decreasing with the intermittency of clean technologies.
+To clarify, recall that the elasticity of substitution between renewables and fossil fuels becomes small when renewables are more intermittent.
+Likewise, the cost of delaying intervention is decreasing with intermittency as well.
+In other words, delaying policy intervention will be the most costly in regions with access to clean, non-intermittent energy (such as hydro and geothermal energy).
+Secondly,  when the discount rate is sufficiently low and the intermittency of clean energy is sufficiently high, a disaster cannot be avoided under laissez-faire.
+The intuition here is that, even if clean energy became relatively cheap, its intermittency would prevent it from adequately substituting for fossil energy.
+Finally, \citeauthor{Ace2012} argue that the size of a carbon tax should be inversely proportional to the elasticity of substitution and should decrease over time.
+Recall that, in our model, the elasticity of substitution $e$ changes with relative prices; when fossil fuels are relatively cheap, $e$ is large.
 Hence, this implies we need a relatively small carbon tax early on to spur research.
-As technological change makes renewables cheaper, fossil fuels will become relatively more expensive and $e$ will fall; thus, the carbon tax will need to increase over time.
+As technological change makes renewables cheaper, fossil fuels will become relatively more expensive so $e$ will fall; thus, the carbon tax will need to increase over time.
 These dynamics (a rising carbon tax) contrast with the results of \citeauthor{Ace2012} who numerically show that an optimal carbon tax should decrease over time when $e$ is sufficiently large.
@@
 
+\subsubsection{Carbon Taxes and their Distributive Consequences}
+
 Our results also suggest that carbon taxes can have important distributional consequences.
-Earlier, we showed that the elasticity of substitution between renewable and fossil fuels $(e)$ is non-constant and falls with intermittency of present generation.
+Earlier, we showed that the elasticity of substitution between renewable and fossil fuels $(e)$ is non-constant and falls with the intermittency of present generation.
 This further implies that the elasticity of demand for generation technologies is non-constant as well.
@@
 Consumers in regions without access to clean, non-intermittent energy will have the most inelastic demand for fossil fuels; hence, they will bear the greatest welfare losses from a tax on pollution/carbon.
-On the other hand, consumers in regions that have access to dispatchable, renewable energy such as hydropower will see smaller welfare losses; demand for fossil fuels in these regions will not be as inelastic, because dirty generation can be replaced with non-intermittent, clean generation.
+On the other hand, consumers in regions that have access to dispatchable, renewable energy such as hydropower will see smaller welfare losses; the demand for fossil fuels in these regions will not be as inelastic, because dirty generation can be replaced with non-intermittent, clean generation.
 All in all, if a carbon tax were implemented federally and its revenue were distributed equally, it may nevertheless function as an inequitable, between-state welfare transfer due to differences in the availability of renewable energy technology.
-This same argument would apply  to renewable subsidies and carbon quotas.
+This same argument would apply  to carbon quotas.
 
@@
 
+\subsubsection{The Case for Subsidizing Battery Research}
+
 However, there are alternative policies that can mitigate this distributional side effect.
@@
 To understand the magnitude of this effect, we again provide a numerical example using solar and coal.
-We model solar energy with batteries by shifting a portion of the original solar energy output across periods; we also ignore the energy losses and costs of battery storage for simplicity.
-In reality, batteries would be more accurately modeled by rewriting our model as a dynamic optimization problem and solving using optimal control theory.
-However, we set aside these complications and consider a second-best solution where batteries are used to shift a fraction of solar output during peak hours to the off-peak period.
-When we can only shift a marginal fraction of output, this is likely equivalent to the first-best solution, because solar power generates relatively too little electricity during off-peak hours than relatively too much during peak hours.
-Specifically, we initially parametrized solar with $\xi_{2} = (1, 0.1)$ implying that it functions at 100\% of its potential capacity during the peak and at 10\% of its potential capacity during the off-peak; this is far from matching consumer demand.
-So, we represent solar output with batteries using $\xi_2 = (0.95, 0.15)$ and $\xi_2 = (0.90, 0.20)$; this is equivalent to transferring 5\% and 10\% of peak solar output to off-peak hours.
+We aim to understand how batteries effect substitutability, so consider a parsimonious model where batteries are used to shift a portion of solar energy output from its high-output period to its low-output period.\footnote{Because we are only interested in the effects of batteries on $e$, we ignore the energy losses and costs of battery storage.
+Furthermore, if our goal instead was to economically optimize battery storage and deployment, we would have to   rewrite our model as a dynamic optimization problem and solve using optimal control theory.
+However, we set aside these complications and consider a second-best solution where batteries are used to shift a fraction of solar output from its low-output period to its high-output period.
+But, since we are shifting relatively marginal fractions of energy output, this is likely equivalent to the first-best solution.
+} Specifically, we initially parametrized solar with $\xi_{2} = (1, 0.1)$ implying that it functions at 100\% of its potential capacity during the peak and at 10\% of its potential capacity during the off-peak; this is far from matching consumer demand.
+So, we represent solar output with batteries using $\xi_2 = (0.95, 0.15)$ and $\xi_2 = (0.90, 0.20)$; this is equivalent to transferring 5\% and 10\% of solar output.
 We plot our results in \hyperref[fig:battery]{Figure 3}.
 It is immediately clear that making solar output more consistent through the day results in a large increase in the elasticity of substitution $e_{1,2}$.
-Moreover, we can see that intermittency no longer causes $e_{1,2}$ to taper off around 4 as solar becomes the dominant source of electricity.
+Moreover,  $e_{1,2}$ no longer tapers off around 4 as solar becomes the dominant source of electricity.
 Rather, with batteries, cost plays a much larger role in determining the optimal quantity of each technology even when solar is relatively cheap.
@@
 Consequently, batteries can complement reductions in the cost of intermittent renewables and mitigate the distributional side effects of a carbon tax.
-As shown in \hyperref[fig:battery]{Figure 3}, the elasticity of substitution between solar and coal rises significantly as solar becomes less intermittent; this implies that a change in relative price of solar would have a far greater effect on solar adoption if batteries were employed with solar.
+As shown in \hyperref[fig:battery]{Figure 3}, the elasticity of substitution between solar and coal rises significantly as solar becomes less intermittent; this implies that a change in the relative price of solar would have a far greater effect on solar adoption if batteries were employed with solar.
 Hence, if policy makers aim to promote the use of renewables, they should subsidize research that reduces the cost of renewables as well as research that improves battery technology.
@@
 Moreover, regions without clean, consistent renewables would benefit in particular, because they will be able to combine intermittent technologies with better energy storage to help transition away from fossil fuel energy.
-In short, subsidizing battery research can reduce some of the distributional side effects of carbon taxes while mitigating environmental damage.
+In short, subsidizing battery research can reduce some of the unintended distributional consequences of carbon taxes while mitigating environmental damage.
+
+\subsubsection{Learning-by-Doing and Intermittency}
+
+Lastly, our results suggest that renewable subsidies aimed at correcting the positive externalities of ``learning-by-doing" should also vary geographically.
+This is because the adoption rate of a renewable technology depends on its intermittency and the pre-existing technologies used for generation.
+For instance, hydropower plants can easily substitute for fossil fuel technologies, because hydropower is non-intermittent.
+Consequently, developing a larger initial capacity of hydropower to promote learning-by-doing can be done with a relatively small subsidy.
+On the other hand, suppose a region's only source of renewable energy is wind power.
+In this case, the intermittency of wind power reduces its elasticity of substitution with fossil fuel technologies.
+Thus, relatively larger subsidies are required to raise the capacity of wind power.
+Furthermore, the intermittency of renewable technologies (especially wind and solar) is linked to the weather which varies geographically.
+Hence, two regions with access to the same intermittent renewables at the same cost may still experience differing levels of intermittency based on their location.
+So, optimal renewable subsidies may also vary geographically simply due to differences in the weather.
+Thirdly, as discussed earlier, the elasticity of substitution between clean and dirty energy rises when prices differ greatly.
+This implies that regions with relatively expensive renewables (relatively cheap fossil energy) can benefit more from subsidies; again, this can vary geographically since the costs of both fossil fuels and renewables vary geographically.
+So, in total, correcting the externality from learning-by-doing should take into account the geographic differences in the availability of renewable technologies, weather conditions that may influence renewable output, and the relative prices of renewable and fossil energy.
+
+This implies that optimal renewable subsidies should differ geographically but only to the extent that the spillovers of learning-by-doing balance out differences in welfare gains.
+That is, recall that subsidies for renewables have two benefits: promoting learning-by-doing and raising consumer and producer surplus.
+The first effect  can spur innovation that affects technology in all regions while the latter effect is mostly local.
+Now, consider two edge-case policy solutions targeting one benefit but ignoring the other.
+The first extreme solution may be to maximize learning by doing while ignoring the effects of subsidies on welfare.
+This solution would suggest that we subsidize renewables wherever they can best substitute for fossil fuels.
+The other extreme solution would be to distribute subsidies almost equally to ensure welfare gains are equitable; this assumes policymakers do not want to concentrate welfare gains for some regions but not others.
+Since we know the effect of subsidies on renewable adoption varies geographically, these two extreme solutions must differ; in other words, there's likely a trade-off between efficiently and equitably promoting renewables.
+Consequently, ignoring an edge case, an intermediate choice between these two approaches is a valid second-best solution for policymakers looking to balance efficiency and equity.
+Alternatively, a first-best solution would simply maximize efficiency with the first approach and then make welfare outcomes more equitable with direct monetary transfers.
+And finally, like before with carbon taxes, improving battery technology can also help mitigate the distributional side effects of efficient renewable subsidies.
 
@@
 For fossil fuels, $\xi_i$ can remain constant over time.
-For intermittent renewables, $\xi_{i,t}$ may be set to empirical estimates of the average output per unit of $X_i$ in period $t$.\footnote{It is important to note that each period $t$ should describe a short time frame.
+For intermittent renewables, $\xi_{i,t}$ may be set to empirical estimates of the average output per unit of $X_i$ in period $t$.\footnote{ It is important to note that each period $t$ should describe a short time frame.
 For instance, each period may represent an hour of a day, or, as in our examples, we may have two periods that represent peak and off-peak.
@@
 That is, technologies like coal and nuclear can change their output over longer periods of time to respond to changes in price; on the other hand, as discussed earlier, we assume here that output in each period is exogenous.}  Additionally, the supply-side equations for building capacity in each technology can be modeled using the usual  CGE approach; total cost is given by the sum of costs for each input factor and total quantity is given by a CES of the input factors used to build capacity $(X_i)$.
-Finally, since these functional forms equivalent\footnote{Linear production functions simply a special case of CES production functions where the elasticity of substitution is arbitrarily high.} to those used in standard CGEs, they can be calibrated using the usual procedures and a social accounting matrix.
+Finally, since these functional forms equivalent\footnote{ Linear production functions simply a special case of CES production functions where the elasticity of substitution is arbitrarily high.} to those used in standard CGEs, they can be calibrated using the usual procedures and a social accounting matrix.
 So, overall, implementing our model within a CGE can be done in a fairly simple way.
@@
 \subsubsection{VES Approximation}
+
+\begin{table}[t]
+	\captionsetup{format=centerproper}
+	\caption*{\textbf{Figure 4:} The VES Approximation of the Elasticity of Substitution \\ between Solar and Coal } 
+	\label{fig:ves}
+	\footnotesize
+	\vspace{-1em}
+	\begin{tabular}{@{\extracolsep{0em}}c}
+		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_ves_approx} \\
+		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } Technology 1 is coal and technology 2 is solar.
+The purple, dash-dots line represents a linear approximation of $e_{1,2}$ for $\sigma = 0.8847$ with a fixed intercept of 1.
+These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
+Furthermore, we set the parameter for the intertemporal elasticity of substitution for electricity consumption equal to our estimate $\hat{\sigma} = 0.8847$.
+In order to generate these numerical results, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.9\, c_1, 2 \,c_1)$.
+Then, we obtained estimates of the elasticity of substitution by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1, c_2)$.
+}     \\
+	\end{tabular}
+\end{table}
 
@@
 
-\begin{table}[t]
-	\captionsetup{format=centerproper}
-	\caption*{\textbf{Figure 4:} The VES Approximation of the Elasticity of Substitution \\ between Solar and Coal } 
-	\label{fig:ves}
-	\footnotesize
-	\vspace{-1em}
-	\begin{tabular}{@{\extracolsep{0em}}c}
-		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_ves_approx} \\
-		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } Technology 1 is coal and technology 2 is solar.
-The purple, dash-dots line represents a linear approximation of $e_{1,2}$ for $\sigma = 0.8847$ with a fixed intercept of 1.
-These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
-Furthermore, we set the parameter for the intertemporal elasticity of substitution for electricity consumption equal to our estimate $\hat{\sigma} = 0.8847$.
-In order to generate these numerical results, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.9\, c_1, 2 \,c_1)$.
-Then, we obtained estimates of the elasticity of substitution by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1, c_2)$.
-}     \\
-	\end{tabular}
-\end{table}
-
 One potential objection to using the VES function is that it assumes the elasticity of substitution $e$ approaches 1 when the majority of generation comes from renewables ($X_1/X_2 \to 0$).
-This actually happens to be a fairly reasonable assumption in our model.
-That is, suppose renewable energy was arbitrarily cheap but highly intermittent.
-Furthermore, suppose that the consumer's elasticity of substitution $\sigma = 1$.
-We show in \hyperref[sec:asympeos]{Appendix A.C} that this results in renewable  and fossil energy entering Cobb-Douglas relationship ($e = 1$).
-And, more generally, whenever the renewable technology is highly intermittent, $e$ becomes almost perfectly linear with respect to the quantity ratio $X_1/X_2$.
-Hence, in these cases, the VES approximation $\hat{e}$ almost perfectly matches $e$; this is shown in \hyperref[fig:ves_int]{Figure B.2}.
-Thus, the VES assumption that $e = 1$ when $X_1/X_2$ is arbitrarily small is not necessarily a drawback.
-Moreover, even if these assumptions were not true, our model implies that VES function would only underestimate the substitutability of clean and dirty energy in these edge cases.
+And, a VES structure assumes linear $e$ which does not seem to be the case in \hyperref[fig:ves]{Figure 4}.
+However, both these assumptions may still be fairly reasonable in the right context.
+That is, suppose renewable energy was highly intermittent and that the consumer's elasticity of substitution $\sigma = 1$.
+Firstly, this results in renewable  and fossil energy entering a Cobb-Douglas relationship ($e = 1$) as $X_1/X_2 \to 0$ which supports the VES assumption of an intercept of 1.
+Secondly, no matter the relative prices, whenever the renewable technology is highly intermittent, $e$ becomes perfectly linear with respect to $X_1/X_2$; this supports the VES assumption of linearity.
+The proofs for both are given in \hyperref[sec:asympeos]{Appendix A.C}.
+Hence, in these cases, a VES approximation  can perfectly match $e$.
+Additionally, even when consumer's elasticity of substitution is not $1$, $e$ may still be approximately linear; this is shown in \hyperref[fig:ves_int]{Figure B.2} where we consider our estimated $\hat{sigma} = 0.8847$.
+In short, the assumptions made by a VES structure may nevertheless be accurate in certain cases.
+
+%Moreover, even if these assumptions were not true, our model implies that VES function would only underestimate the substitutability of clean and dirty energy in these edge cases.
 While \textit{overestimating} $e$ may result in policy failing to mitigate a preventable climate disaster, \textit{underestimating} $e$ would simply cause a policy overreaction.
@@
 Overall, using a VES function is a reasonable alternative to directly modeling intermittency.
-It allows theorists derive policy implications from intermittency without relying too heavily on numerical models.
+It allows theorists to derive policy implications from intermittency without relying too heavily on numerical models.
 Furthermore, it keeps theory simple by assuming a linear elasticity of substitution that depends on a single parameter $\beta$.
@@
 
-\dots Throughout the paper, we considered coal and solar power as examples of fossil and renewable energy. Moreover, 
-For instance, we discussed how to handle pollution when energy sources are intermittent; we found that, rather than a standard Pigouvian tax, we would be better off using a combination of research subsidies and carbon taxes.
-One implicit but important point here is that optimal policy must be tuned for differences in local electricity markets.
-That is, even if externalities are global and research spills over, optimal policy differs on a local scale since generation technologies differ on a local scale.
-\dots
-
-\dots An aim for future research may be to develop a model of clean and dirty energy that incorporates both predictable and stochastic intermittency in a multi-period setting.
+In this paper, we have offered a framework for understanding the economics of intermittent renewable energy that bears in mind the critique offered by \citet{Joskow2011}.
+That is, our model evaluates the economic feasibility of a technology by integrating its production profile with the market value of electricity in equilibrium.
+Moreover, this equilibrium is reached using a fairly realistic model of consumer behavior.
+The empirical parameterization of our model and its numerical results suggest that the elasticity of substitution between renewable and fossil energy is non-constant.
+We have shown that this has important implications for policy and future models.
+
+With respect to policy, we have shown (i) the welfare effects of carbon taxes and renewable subsidies depend on the intermittency of renewables and thus vary geographically; (ii) the effect that renewable subsidies have on promoting the adoption of renewables varies geographically; (iii) the combination of (i) and (ii) can create a trade-off between efficiently and equitably preventing climate change; (iv) subsidizing battery research can complement other policies by increasing the substitutability of renewable and fossil energy; (v) improving batteries can mitigate the distributional side effects of carbon taxes and research subsidies.
+Additionally, we have qualitatively evaluated the results of \citet{Ace2012} in a setting where renewables and fossil fuels have a non-linear elasticity of substitution.
+Based on their framework, we have further argued that: (vi) the short-run cost of policy intervention is decreasing with intermittency;  (vii) the cost of delaying intervention is decreasing with intermittency; (viii) when the discount rate is sufficiently low and the intermittency of renewables is sufficiently high, a laissez-faire equilibrium would require policy intervention to prevent disaster; (ix) when renewables are moderately intermittent, an optimal carbon tax should remain approximately constant over time.
+
+Given how strongly the elasticity of substitution between renewable and fossil energy varies with relative price, future models of intermittency should not assume a CES structure.
+So, we show how to integrate our framework within a numerical model, such as a CGE; this may improve predictive accuracy by providing more realistic microfoundations.
+On the other hand, theoretical models would be better served by more a analytically tractable alternative.
+Therefore, we suggest theoretical models use a VES production function to approximate the effect of intermittency on the elasticity of substitution between renewable and fossil energy.
+We show that, under certain conditions, our own model simplifies to a VES case; hence, this production function can reasonably approximate for our full model.
+
+While constructing our model, we made several simplifications for tractability.
+For instance, we set aside modeling reliability -- stochastic or otherwise unpredictable variation in output.
+An aim for future research may be to develop a model of clean and dirty energy that incorporates both intermittency and reliability in a multi-period setting.
+This could involve integrating our framework with that of \citet{HH}.
+Additionally, another avenue for future research may be to explicitly model the effects of battery technology and how storage interacts with intermittency and reliability.
+Such models can offer more accurate predictions/suggestions for policymakers and bring theory closer to reality.
 
@@
 Hence, in total, the mixed efficiency restrictions relate the relative cost efficiencies of each technology with their output efficiency and the demand for energy.
-So, for example, suppose that consumers prefer, \textit{ceteris paribus}, that nearly all their electricity arrive in period $t$.
+So, for example, suppose that consumers prefer, \textit{ceteris paribus}, that nearly all their electricity arrives in period $t$.
 This would imply $\alpha_t$ is arbitrarily large which results in the left-hand side of the fraction becoming arbitrarily small.
@@
 And, we expect that there is more available solar radiation during peak hours than off-peak hours, since peak hours are usually during the middle of the day.
-This implies that the the output efficiency of solar power is higher in period $t$ due to more available solar radiation.
+This implies that the output efficiency of solar power is higher in period $t$ due to more available solar radiation.
 Additionally, since the energy output of a unit of coal is independent of time, we know that the output efficiency of coal is constant.
@@
 And, finally, solar must also satisfy the mixed efficiency condition, which essentially implies that there must be sufficient demand for electricity during period $t$, when solar is more effective, for it to be a feasible technology.
-So, overall, for a technology to be economical, it must meet three conditions: it must the most cost effective technology for a particular period, it must have a comparative advantage in output efficiency in the same period, and there must be sufficient amount of demand in that period.
+So, overall, for a technology to be economical, it must meet three conditions: it must the most cost effective technology for a particular period, it must have a comparative advantage in output efficiency in the same period, and there must be a sufficient amount of demand in that period.
 
@@
 So, again, let us assume Case 1 is true; this implies that $X_2$ is the most cost effective technology in period $t$ and likewise for $X_1$ in period $s$.
-Firstly, note that $\alpha$ determines demand for electricity in a period.
+Firstly, note that $\alpha$ determines the demand for electricity in a period.
 Hence, when $\alpha_t$ rises, we see the optimal level of $X_2$ rise as well; likewise, $X_1$ rises with $\alpha_s$.
@@
 Moreover, these relationships are reversed with respect to demand in each technology's suboptimal period.
-So, for example, we would expect the use of solar energy to rise when demand for electricity during peak hours rises, and it would fall when demand for energy in the off-peak rises.
+So, for example, we would expect the use of solar energy to rise when the demand for electricity during peak hours rises, and it would fall when demand for energy in the off-peak rises.
 On the other hand, use coal power would rise with off-peak demand and fall with peak demand.
@@
 For instance, this would occur if we had one technology that can only output electricity during the day and another that only outputs electricity at night.
-Anyways, in this case, the CES production function's elasticity parameter  will be equivalent to the that of the consumer's CES utility function -- the intertemporal elasticity of substitution for electricity consumption.
+Anyways, in this case, the CES production function's elasticity parameter  will be equivalent to that of the consumer's CES utility function -- the intertemporal elasticity of substitution for electricity consumption.
 
@@
 Now, recall that the FOC for profit-maximization is given by $p = \xi^{-1} c$, hence we have $p_i = c_i / \xi_{i,i}$.
-Combining this equations with the FOC for utility maximization, we have:
+Combining these equations with the FOC for utility maximization, we have:
 	\begin{align*}
@@
 We now show that, in this case, the elasticity of substitution approaches $1$ as the relative cost of our second technology $c_2/c_1$ approaches $0$.
+Furthermore, we show that the elasticity of substitution between $X_1$ and $X_2$ is a linear function of $X_1/X_2$.
 
@@
 	&= \frac{\alpha_s c_2 \xi_{2t}}{ \alpha_t (c_1 \xi_{2t} - c_2 \xi_{1}) -  c_2 \alpha_s \xi_1 }\\
-	&= \frac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{\xi _{1}\,\left(\alpha _{s}\,c_{2}+\alpha _{t}\,c_{2}\right)-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}
-	\end{align*}
-	 Next, we can see that:
+	&= \frac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{\xi _{1}\,\left(\alpha _{s}\,c_{2}+\alpha _{t}\,c_{2}\right)-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}} \\
+	&= \frac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}
+	\end{align*}
+	where $\alpha_t + \alpha_s = 1$ by definition (see \hyperref[sec:consumers]{Section II.A}).  Next, we can see that:
 	$$
-	\frac{\partial \log(X_1/X_2)}{c_1} = \frac{\alpha _{t}\,\xi _{\mathrm{2t}}}{\xi _{1}\,\left(\alpha _{s}\,c_{2}+\alpha _{t}\,c_{2}\right)-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}
+	\frac{\partial \log(X_1/X_2)}{c_1} = \frac{\alpha _{t}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}
 	$$
-	The elasticity of substitution is given by:
+	The elasticity of substitution $e_{1,2}$ is given by:
 	\begin{align*}
 	\frac{\partial \log(X_1/X_2)}{\partial \log(c_2/c_1)} &= \frac{\partial \log(X_1/X_2)}{\partial c_1}\frac{\partial c_1}{\partial \log(c_2/c_1)} \\
-	&= \frac{\alpha _{t}\,\xi _{\mathrm{2t}}}{\xi _{1}\,\left(\alpha _{s}\,c_{2}+\alpha _{t}\,c_{2}\right)-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}\frac{\partial c_1}{\partial \log(c_2/c_1)} \\
-	&= \frac{-c_1 \alpha _{t}\,\xi _{\mathrm{2t}}}{\xi _{1}\,\left(\alpha _{s}\,c_{2}+\alpha _{t}\,c_{2}\right)-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}\\
-	&= \left( \frac{c_2 \xi_1 }{-c_1 \alpha_t \xi_{2t}} + 1 \right)^{-1} \\
-	\end{align*}
-	where $\alpha_t + \alpha_s = 1$ by definition (see \hyperref[sec:consumers]{Section II.A}). Finally, it is simple to see that:
+	&= \left( \frac{\alpha _{t}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}} \right) \left( -c_1 \right)  \\
+	&= \frac{-c_1 \alpha _{t}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}\\
+	&= \left( \frac{c_2 \xi_1 }{-c_1 \alpha_t \xi_{2t}} + 1 \right)^{-1}
+	\end{align*}
+	Finally, it is simple to see that:
 	$$ \lim_{c_2/c_1 \to 0} \frac{\partial \log(X_1/X_2)}{\partial \log(c_2/c_1)} = 1$$
+	Additionally, we can see that the elasticity of substition between $X_1$ and $X_2$ is linear with respect to $X_1/X_2$. That is, note that we may rewrite the elasticity above as:
+	\begin{align*}
+	\frac{\partial \log(X_1/X_2)}{\partial \log(c_2/c_1)} &= \frac{-c_1 \alpha _{t}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}} \\
+	&= \left( \frac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}} \right) \left( \frac{- \alpha_t c_1 \xi_{2t} }{- \alpha_s c_2 \xi_{2t}} \right)\\
+	&= \left( \frac{X_1}{X_2} \right) \left( \frac{ \alpha_t c_1  }{\alpha_s c_2 } \right)
+	\end{align*}
+	Since the parameters $\alpha$ and $c$ are exogenous constants, we have shown that $e$ can be written as a linear function of $X_1/X_2$. 
 	\\ \hfill
@@
 
-\begin{table}[t]
+\begin{table}[h!]
 	\captionsetup{format=centerproper}
@@
 Furthermore, we set the parameter for the intertemporal elasticity of substitution for electricity consumption equal to our estimate $\hat{\sigma} = 0.8847$.
-In order to generate these numerical results, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.95\, c_1, 2 \,c_1)$.
+In order to generate these numerical results, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (c_1, 2 \,c_1)$.
 Then, we obtained estimates of the elasticity of substitution by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1, c_2)$.
@@
 \end{table}
+
+\pagebreak
+
+\section{Appendix C: Econometric Methodology}
+\label{sec:AppendixC}
+
+We aim to estimate $\sigma$ in the following set of equations:
+\begin{align*}
+\ln (Z_{ t, i} / Z_{ s, i}) &= -\sigma \ln (P_{t,i} / P_{s,i}) +  f \left( A_{t,i}, A_{s,i}, \Delta_{t,s} \right) + u_i \\
+\ln (Z_{ t, i} / Z_{ s, i}) &= \beta \ln (P_{t,i} / P_{s,i}) + g \left( \ln (C_{t,i} / C_{s,i})  \right) + v_{i}
+\end{align*}
+We base our estimation procedure on \citet{Newey}. To start, for simplicity, let us rewrite the above set of equations as:
+\begin{align*}
+Q &= P \beta_d + f(T) + u \\
+Q &= P \beta_s + g(W) + v 
+\end{align*}
+where $\beta_d$ is the parameter of interest. Furthermore, we assume that 
+\begin{align*}
+E(u \, | \, T, W) &= 0 \\
+E(v \, | \, T, W) &= 0 
+\end{align*}
+Next, with $\alpha \equiv (\beta_d - \beta_s)^{-1}$ and assuming $\beta_d \neq \beta_s$, note that:
+\begin{align*}
+P &= (\beta_d - \beta_s)^{-1} \, \left(  g(W) - f(T) + u_s - u_d \right)  \\
+E(P\,|\,T)   &= \alpha \left( E(g(W)|T) - f(T)  \right)\\
+E(P\,|\,W)   &= \alpha \left( g(W) - E(f(T)|W)  \right) \\
+E(P\,|\,T,W) &= \alpha \left( g(W) - f(T)     \right) 
+\end{align*}
+Now, differencing $Q$ with its conditional expectation, we have:
+\begin{align*}
+Q - E(Q \,|\,T) &= (P - E(P\,|\,T))\beta_d + (f(T) - E(f(T) \,|\,T)) + (u - E(u|T))\\
+&= (\alpha(g(W) - E(g(W)|T)))\beta_d + 0 + u_d 
+\end{align*}
+Furthermore, it can be shown that:
+$$E(P\,|\,T,W) - E(P\,|\,T) = \alpha (g(W) - E(g(W)|T))$$
+Hence, we can regress 
+$$(Q - E(Q \,|\,T)) = (E(P\,|\,T,W) - E(P\,|\,T)) \beta_d + u_d $$
+to estimate $\beta_d$.
+But, we cannot know the true values of these expectations.
+Hence, we estimate each conditional expectation in this regression by using Nadaraya–Watson kernel regressions.
+This requires us to trim the data, so we drop 1\% of outliers of $Q, P, T$, and $W$.
+Additionally, we use the \citet{Silverman} rule-of-thumb to select bandwidths.
 
@@
 	\bibitem[EIA(2019a)]{EIANetgen}
-	Electricity Information Administration (2019). Net generation, United States, all sectors, annual. Electricity Data Browser. https://www.eia.gov/electricity/data/browser
+	Electricity Information Administration (2019a). Net generation, United States, all sectors, annual. Electricity Data Browser. https://www.eia.gov/electricity/data/browser
 
 	\bibitem[EIA(2019b)]{EIALCOE}
-	Electricity Information Administration (2019).
+	Electricity Information Administration (2019b).
 Levelized Cost and Levelized Avoided Cost of New Generation.
@@
 https://www.eia.gov/outlooks/aeo/pdf/electricity\_generation.pdf
+
+	\bibitem[EIA(2019c)]{EIArenew}
+	Electricity Information Administration (2019c). U.S. renewable electricity generation has doubled since 2008. Today in Energy. https://www.eia.gov/todayinenergy/detail.php?id=38752
 
@@
 Cambridge Working Papers in Economics 0711, Faculty of Economics, University of Cambridge.
+
+	\bibitem[Newey(2007)]{Newey}
+	Newey, W. (1990). Efficient Instrumental Variables Estimation of Non-linear Models. Econometrica, 58(4), 809–837. https://doi.org/10.2307/2938351
 
@@
 
+	\bibitem[Silverman(1986)]{Silverman}
+	Silverman, B. (1986). Density estimation for statistics and data analysis. London; Chapman and Hall.
+
 	\bibitem[Zhou and Teng(2013)]{Zhou}

### 2019-05-15 documents/draft.tex
FInalize draft

@@
 
-\title{\singlespacing{\textbf{Efficient pollution abatement in electricity markets with intermittent renewable energy}}}
-
-\author[]{Saketh Aleti\thanks{I would like to thank Prof. Roger Klein for helpful comments and the Sun Grant for funding this project.} \, and Gal Hochman}
+\title{\singlespacing{\textbf{Efficient Pollution Abatement in Electricity Markets with Intermittent Renewable Energy}}\thanks{We would like to thank Prof.
+Roger Klein for helpful comments and the Sun Grant (award number 122682) for funding this project.}}
+
+\author[]{Saketh Aleti \, and Gal Hochman}
 
@@
 
-\date{\vspace{-1em}\today}
+\date{\vspace{-1em}}
 
@@
 Subsidizing research into battery technology can mitigate this distributional side effect while complementing traditional policies used to promote renewable energy.
+(JEL Q28, Q41, Q48, Q52, Q55, Q58)
 	 }
@@
 Consequently, designing economically efficient policies to promote their adoption is not straightforward given that they cannot easily substitute for fossil fuel technologies such as coal power.
-Moreover, traditional economic measures such as the levelized cost of electricity (LCOE) fail to capture the true economic value of intermittent technologies, because they neglect to account for variation in output and prices over time \citep{Joskow2011}.
+Moreover, traditional approaches such as the levelized cost of electricity (LCOE) fail to capture the true economic value of intermittent technologies, because they neglect to account for variation in output and prices over time \citep{Joskow2011}.
 
@@
 For instance, while wind energy output varies over time, if  we know the wind speed and angle, we may precisely derive the quantity of energy that a wind farm generates.\footnote{ \citet{Foley2012} provide a review of the literature on the forecasting of wind power.
-Over time, forecasts have gotten much more accurate allowing electricity grids to manage wind power intermittency ahead of time.}  At the same time, wind forecasts are not be perfect, so we may see unexpected variation in the electricity output of a wind farm.
+Over time, forecasts have gotten much more accurate allowing electricity grids to manage wind power intermittency ahead of time.}  At the same time, forecasts can never be perfectly accurate, so we may see still unexpected variation in  electricity output.
 This unpredictability is better captured by the notion of reliability; specifically,  we refer to definition provided by the US Department of Energy's \citet{ORNL} -- ``Power reliability can be defined as the degree to which the performance of the elements in a bulk system results in electricity being delivered to customers within accepted standards and in the amount desired." This is more so related to the stochastic or unpredictable variation in the output of a technology.
@@
 A practical example may be a wind turbine's systems failing.
-While we may know the chances of this occurring, it's not possible to know when it will occur ahead of time; consequently, this may result in a temporary reduction in the quantity and quality of the electricity delivered --  a loss of reliability.
+While we may know the chances of this occurring, it's not always possible to know when it will occur ahead of time; consequently, this may result in a temporary reduction in the quantity and quality of the electricity delivered --  a loss of reliability.
 In short, when \citeauthor{HH} model renewable output as equal to a base capacity multiplied by a uniform random variable, their treatment is closer to one of reliability rather than intermittency.
@@
 
-Now, recalle that the demand equation from earlier (Equation 3) is:
+Now, recall the demand equation from earlier (Equation 3)
 $$Z_t = \left(\frac{\alpha_t}{p_t} \right)^\sigma \frac{I}{P}$$
@@
 
-\begin{table}[!t] \centering 
+Based on the OLS results reported in \hyperref[table:1]{Table 1}, we estimate the intertemporal elasticity of substitution for electricity consumption $\hat{\sigma}  = 1.305$ ($|t| > 24$) when accounting for all degree day covariates and state fixed effects.
+Additionally, we find that accounting for cooling and heating degree days captures a large amount of variation in demand for electricity; in the fixed effects regressions, adding these controls raises adjusted $R^2$ from 8.5\% to 51.8\%.
+Also, as expected, the coefficients on the degree day covariates are symmetrical; that is, the coefficient on $CDD_{t}$ is approximately the same as the negative of that on $CDD_{s}$, and the same applies to $HDD_{t}$ and $HDD_{s}$.
+\footnote{It is important to note that the reason they are not perfectly equal is because our regression data consists of each unique \textit{combination} of $(t,s)$ for each $i$; that is, if we have an arbitrary observation $(t,s,i)$ in our data, then $(s,t,i)$ does not also appear.
+Including these observations would not affect $\sigma$ and they also don't add any further information to our regression.
+However, they would make the magnitude of the estimated coefficients for  CDD$_t$ and CDD$_s$ equivalent (and likewise for HDDs).
+}  Furthermore, we found that electricity consumption seems to rise more in response to CDDs rather than HDDs.
+Next, we find that the sign on $\Delta_{t,s}$ is positive in all regressions, so electricity consumption rises over time independent of price.
+Specifically, fit (6) finds a coefficient of $0.000655$ which implies that electricity consumption rises, on average, by $\approx 0.7\%$ per year.
+Finally, adding state fixed effects seems to raise the estimates of $\sigma$ for all fits.
+
+To account for endogeneity in the OLS results, we provide results for our IV specification in \hyperref[table:2]{Table 2}.
+Here, we find a much larger estimate of $\hat{\sigma}  = 5.818$ ($|t| > 11.1$) when considering all covariates and fixed effects.
+F-Statistics on all three specifications are significantly larger than 10, which suggests that the instruments are not weak \citep{SS1997}.
+These results greatly differ from the literature's estimates probably as a consequence of controlling for endogeneity.
+That is, ignoring variation on the supply side would bias OLS estimates for the effect of price on demand downwards; by controlling for this, we find larger estimates of $\sigma$ which is expected.
+Next, with respect to the demand controls, we find results similar to those of OLS.
+The magnitudes of the coefficients on DDs do not appear to be significantly different.
+Furthermore, we again find that CDDs affect electricity consumption more than HDDs.
+But, this time, the coefficients on heating degree days do not appear to be significant.
+Additionally, in contrast with the OLS results, we find a much larger estimate for the coefficient on $\Delta_{t,s}$ of $0.003$; this implies that electricity consumption seems to rise by about 3.65\% per year.
+So, overall, our IV results suggest much higher estimates of $\sigma$.
+
+Finally, we control for nonlinear effects using a partially linear IV regression reported in \hyperref[table:3]{Table 3}.
+Here, we find much smaller results than 2SLS when controlling for all possible covariates.
+Specifically, in fit (3), we have $\hat{\sigma} = 0.8847$ ($|t| > 20$).
+The estimates of $\sigma$ with fewer controls are much larger.
+However, based on the OLS and IV results, it seems that both the time control and degree day controls are significant.
+Hence, fit (3) is likely the most appropriate specification.
+Additionally, all of these estimates are significantly different from the 2SLS results which suggests that the 2SLS results are not robust.
+To be precise, our controls and instrument likely have non-linear effects on price and quantity which cannot be captured by linear models; this may explain why the 2SLS results differ significantly from these semiparametric results.
+Alternatively, this difference may also be because the errors in our regressions are not Gaussian.
+In any case, we  believe that our third semiparametric fit, $\hat{\sigma} = 0.8847$, is the most robust estimate of $\sigma$.
+We now discuss what this means for renewable energy policy in greater detail.
+
+\begin{table}[h] \centering 
+	\vspace{-2em}
 	\caption{IV (2SLS) Regression Results}
@@
 	\end{tabular} 
-\end{table}
-
-\begin{table}[!t] \centering 
+	%\end{table}
+	\\[4ex]
+
+	%\begin{table}[!t] \centering 
 	\caption{Partially Linear IV Regression Results}
@@
 	\small
-	\begin{tabular}{@{\extracolsep{4em}}lccc} 
+	\begin{tabular}{@{\extracolsep{5.3em}}lccc} 
 		\\[-4ex]\hline  
@@
 		\hline \\[-1.8ex] 
-		\multicolumn{4}{@{}p{37em}@{}}{\textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions.
+		\multicolumn{4}{@{}p{41.5em}@{}}{\textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions.
 The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
@@
 \end{table}
-
-Based on the OLS results reported in \hyperref[table:1]{Table 1}, we estimate the intertemporal elasticity of substitution for electricity consumption $\hat{\sigma}  = 1.305$ ($|t| > 24$) when accounting for all degree day covariates and state fixed effects.
-Additionally, we find that accounting for cooling and heating degree days captures a large amount of variation in demand for electricity; in the fixed effects regressions, adding these controls raises adjusted $R^2$ from 8.5\% to 51.8\%.
-Also, as expected, the coefficients on the degree day covariates are symmetrical; that is, the coefficient on $CDD_{t}$ is approximately the same as the negative of that on $CDD_{s}$, and the same applies to $HDD_{t}$ and $HDD_{s}$.
-\footnote{It is important to note that the reason they are not perfectly equal is because our regression data consists of each unique \textit{combination} of $(t,s)$ for each $i$; that is, if we have an arbitrary observation $(t,s,i)$ in our data, then $(s,t,i)$ does not also appear.
-Including these observations would not affect $\sigma$ and they also don't add any further information to our regression.
-However, they would make the magnitude of the estimated coefficients for  CDD$_t$ and CDD$_s$ equivalent (and likewise for HDDs).
-}  Furthermore, we found that electricity consumption seems to rise more in response to CDDs rather than HDDs.
-Next, we find that the sign on $\Delta_{t,s}$ is positive in all regressions, so electricity consumption rises over time independent of price.
-Specifically, fit (6) finds a coefficient of $0.000655$ which implies that electricity consumption rises, on average, by $\approx 0.7\%$ per year.
-Finally, adding state fixed effects seems to raise the estimates of $\sigma$ for all fits.
-
-To account for endogeneity in the OLS results, we provide results for our IV specification in \hyperref[table:2]{Table 2}.
-Here, we find a much larger estimate of $\hat{\sigma}  = 5.818$ ($|t| > 11.1$) when considering all covariates and fixed effects.
-F-Statistics on all three specifications are significantly larger than 10, which suggests that the instruments are not weak \citep{SS1997}.
-These results greatly differ from the literature's estimates probably as a consequence of controlling for endogeneity.
-That is, ignoring variation on the supply side would bias OLS estimates for the effect of price on demand downwards; by controlling for this, we find larger estimates of $\sigma$ which is expected.
-Next, with respect to the demand controls, we find results similar to those of OLS.
-The magnitudes of the coefficients on DDs do not appear to be significantly different.
-Furthermore, we again find that CDDs affect electricity consumption more than HDDs.
-But, this time, the coefficients on heating degree days do not appear to be significant.
-Additionally, in contrast with the OLS results, we find a much larger estimate for the coefficient on $\Delta_{t,s}$ of $0.003$; this implies that electricity consumption seems to rise by about 3.65\% per year.
-So, overall, our IV results suggest much higher estimates of $\sigma$.
-
-Finally, we control for nonlinear effects using a partially linear IV regression reported in \hyperref[table:3]{Table 3}.
-Here, we find much smaller results than 2SLS when controlling for all possible covariates.
-Specifically, in fit (3), we have $\hat{\sigma} = 0.8847$ ($|t| > 20$).
-The estimates of $\sigma$ with fewer controls are much larger.
-However, based on the OLS and IV results, it seems that both the time control and degree day controls are significant.
-Hence, fit (3) is likely the most appropriate specification.
-Additionally, all of these estimates are significantly different from the 2SLS results which suggests that the 2SLS results are not robust.
-To be precise, our controls and instrument likely have non-linear effects on price and quantity which cannot be captured by linear models; this may explain why the 2SLS results differ significantly from these semiparametric results.
-Alternatively, this difference may also be because the errors in our regressions are not Gaussian.
-In any case, we  believe that our third semiparametric fit, $\hat{\sigma} = 0.8847$, is the most robust estimate of $\sigma$.
-We now discuss what this means for renewable energy policy in greater detail.
 
@@
 That is, the elasticity of substitution  between technology 1 and 2 is given by the slope of the upper subplot, and it is graphed in the lower subplot.
-Finally, we repeat this procedure with $\sigma$ equal to two standard deviations above and below its estimated value $\hat{\sigma}$; that is, the dashed lines represent  $\sigma = 0.8847 \pm 2(0.044)$.
+Finally, we repeat this procedure with $\sigma$ equal to two standard deviations above and below its estimated value $\hat{\sigma}$; that is, the dashed lines represent  $\sigma = 0.8847 \pm (1.96)(0.044)$.
 }     \\
@@
 We repeat this process with different values of $\sigma$, the elasticity of substitution in the consumer's utility function.
-Specifically, we use our estimate of $\hat{\sigma} = 0.8847\, (0.044)$ and its 95\%  confidence interval $(0.7967, 0.9727)$.
+Specifically, we use our estimate of $\hat{\sigma} = 0.8847\, (0.044)$ and its 95\%  confidence interval $(0.7985, 0.9709)$.
 Finally, after finding the optimal values of our quantities $X$, we filter all observations of our numerical simulation that correspond to edge cases -- solutions where $X, Z \leq  0$.
@@
 Firstly, they find that the short-run cost of policy intervention is increasing with the elasticity of substitution between clean and dirty technologies.\footnote{ See Corollary 1 of their paper for a proof and intuitive explanation.} Additionally, their paper states that the cost of delaying intervention is increasing with the elasticity of substitution.
-Secondly, \citeauthor{Ace2012} argue that, when the discount rate and elasticity of substitution between clean and dirty energy ($e$) is sufficiently low, a disaster cannot be avoided under laissez-faire.\footnote{ See Proposition 9 of their paper.} And, finally, \citeauthor{Ace2012} find that, ``when the elasticity of substitution is high\dots\, a relatively small carbon tax is sufficient to redirect R\&D towards clean technologies."
+Secondly, Acemoglu et al.
+argue that, when the discount rate and elasticity of substitution between clean and dirty energy ($e$) is sufficiently low, a disaster cannot be avoided under laissez-faire.\footnote{ See Proposition 9 of their paper.} And, finally, Acemoglu et al.
+find that, ``when the elasticity of substitution is high\dots\, a relatively small carbon tax is sufficient to redirect R\&D towards clean technologies."
 
 Based on our results, each of these statements has a complementary interpretation in terms of intermittency.
-For instance, the first statements suggests that the cost of policy intervention is decreasing with the intermittency of clean technologies.
-To clarify, recall that the elasticity of substitution between renewables and fossil fuels becomes small when renewables are more intermittent.
-Likewise, the cost of delaying intervention is decreasing with intermittency as well.
-In other words, delaying policy intervention will be the most costly in regions with access to clean, non-intermittent energy (such as hydro and geothermal energy).
+For instance, the first statement suggests that the cost of policy intervention is decreasing with the intermittency of clean technologies; the cost of delaying intervention is decreasing with intermittency as well.
+This is because the elasticity of substitution between renewables and fossil fuels becomes small when renewables are more intermittent.
+So, in other words, delaying policy intervention will be the most costly in regions with access to clean, non-intermittent energy (such as hydro and geothermal energy).
 Secondly,  when the discount rate is sufficiently low and the intermittency of clean energy is sufficiently high, a disaster cannot be avoided under laissez-faire.
 The intuition here is that, even if clean energy became relatively cheap, its intermittency would prevent it from adequately substituting for fossil energy.
-Finally, \citeauthor{Ace2012} argue that the size of a carbon tax should be inversely proportional to the elasticity of substitution and should decrease over time.
+Finally, Acemoglu et al.
+argue that the size of a carbon tax should be inversely proportional to the elasticity of substitution and should decrease over time.
 Recall that, in our model, the elasticity of substitution $e$ changes with relative prices; when fossil fuels are relatively cheap, $e$ is large.
@@
 As technological change makes renewables cheaper, fossil fuels will become relatively more expensive so $e$ will fall; thus, the carbon tax will need to increase over time.
-These dynamics (a rising carbon tax) contrast with the results of \citeauthor{Ace2012} who numerically show that an optimal carbon tax should decrease over time when $e$ is sufficiently large.
+These dynamics (a rising carbon tax) contrast with the results of Acemoglu et al.
+who numerically show that an optimal carbon tax should decrease over time when $e$ is sufficiently large.
 A potential resolution to these contradictory solutions may be to take an intermediate route and maintain a constant carbon tax over time.
@@
 		\hline \\[-1.8ex] 
-		\\[-1.8ex] \specialcell{Solar Output during \\ Peak Hours ($\xi_{2t}$)} &  \specialcell{Solar Output during \\ Off-Peak Hours ($\xi_{2s}$)}  & \specialcell{Elasticity of Demand \\ for Coal Power}\\ [0.5ex]
+		\\[-2.6ex] \specialcell{Solar Output during \\ Peak Hours ($\xi_{2t}$)} &  \specialcell{Solar Output during \\ Off-Peak Hours ($\xi_{2s}$)}  & \specialcell{The Elasticity of  \\ Demand for Coal Power}\\ [0.5ex]
 		\hline \\[-1.8ex] 
@@
 On the other hand, our representation of the energy sector makes more realistic assumptions and directly models the source of imperfect substitutability between generation technologies -- intermittency.
-Consequently, embedding our model within a CGE offers more realistic microfoundations and predictive accuracy.
-Moreover, even though our model is analytically intractable with $\sigma \neq 1$, this is not a problem for CGEs which are evaluated numerically.
+Consequently, embedding our model within a CGE would improve its predictive accuracy by giving it more realistic microfoundations.
 
@@
 Hence, in these cases, a VES approximation  can perfectly match $e$.
-Additionally, even when consumer's elasticity of substitution is not $1$, $e$ may still be approximately linear; this is shown in \hyperref[fig:ves_int]{Figure B.2} where we consider our estimated $\hat{sigma} = 0.8847$.
+Additionally, even when consumer's elasticity of substitution is not $1$, $e$ may still be approximately linear; this is shown in \hyperref[fig:ves_int]{Figure B.2} where we consider our estimated $\hat{\sigma} = 0.8847$.
 In short, the assumptions made by a VES structure may nevertheless be accurate in certain cases.
@@
 It allows theorists to derive policy implications from intermittency without relying too heavily on numerical models.
-Furthermore, it keeps theory simple by assuming a linear elasticity of substitution that depends on a single parameter $\beta$.
+Furthermore, it keeps theory simple since the elasticity of substitution can be represented as a linear function of a single parameter $\beta$.
 And, this parameter can be estimated econometrically, so theoretical models assuming a VES structure can offer empirically-based results.
@@
 
-With respect to policy, we have shown (i) the welfare effects of carbon taxes and renewable subsidies depend on the intermittency of renewables and thus vary geographically; (ii) the effect that renewable subsidies have on promoting the adoption of renewables varies geographically; (iii) the combination of (i) and (ii) can create a trade-off between efficiently and equitably preventing climate change; (iv) subsidizing battery research can complement other policies by increasing the substitutability of renewable and fossil energy; (v) improving batteries can mitigate the distributional side effects of carbon taxes and research subsidies.
+With respect to policy, we have shown (i) the welfare effects of carbon taxes and renewable subsidies depend on the intermittency of renewables and thus vary geographically; (ii) the effect that renewable subsidies have on promoting the adoption of renewables varies geographically; (iii) the combination of (i) and (ii) can create a trade-off between efficiently and equitably preventing climate change; (iv) subsidizing battery research can complement other policies by increasing the substitutability of renewable and fossil energy; (v) improving batteries can mitigate the unintentional distributional consequences of carbon taxes and research subsidies.
 Additionally, we have qualitatively evaluated the results of \citet{Ace2012} in a setting where renewables and fossil fuels have a non-linear elasticity of substitution.
@@
 Given how strongly the elasticity of substitution between renewable and fossil energy varies with relative price, future models of intermittency should not assume a CES structure.
-So, we show how to integrate our framework within a numerical model, such as a CGE; this may improve predictive accuracy by providing more realistic microfoundations.
+So, we have shown to integrate our framework within a numerical model, such as a CGE; this may improve predictive accuracy by providing more realistic microfoundations.
 On the other hand, theoretical models would be better served by more a analytically tractable alternative.
 Therefore, we suggest theoretical models use a VES production function to approximate the effect of intermittency on the elasticity of substitution between renewable and fossil energy.
-We show that, under certain conditions, our own model simplifies to a VES case; hence, this production function can reasonably approximate for our full model.
+Under certain conditions, our own model simplifies to a VES case; hence, the VES production function can reasonably approximate for our full model in a more tractable way.
 
@@
 Furthermore, we derive restrictions on the parameters $\xi$ and $c$ by assuming $Z, X > 0$.
-These restrictions are detailed in \hyperref[tab:paramrest]{Table 1}.
+These restrictions are detailed in \hyperref[tab:paramrest]{Table A.1}.
 There are two possible sets of symmetrical restrictions.
@@
 \begin{table}[h!]
-	\caption{Parameter Restrictions for $Z, X > 0$} 
+	\caption*{\textbf{Table A.1:} Parameter Restrictions for $Z, X > 0$} 
 	\label{tab:paramrest}
@@
 Likewise, as coal power's efficiency improves, it's adoption rises.
-To find the effects of $\alpha$ on $X$, we must assume one of the cases of restrictions shown in \hyperref[tab:paramrest]{Table 1}.
+To find the effects of $\alpha$ on $X$, we must assume one of the cases of restrictions shown in \hyperref[tab:paramrest]{Table A.1}.
 So, again, let us assume Case 1 is true; this implies that $X_2$ is the most cost effective technology in period $t$ and likewise for $X_1$ in period $s$.
@@
 Similarly, symmetrical results are shown for $X_2$.
-Next, we study the effects of $\alpha$ on $X$; this requires us to place some restrictions on the parameters, so we use those belonging to Case 1 in \hyperref[tab:paramrest]{Table 1}.
+Next, we study the effects of $\alpha$ on $X$; this requires us to place some restrictions on the parameters, so we use those belonging to Case 1 in \hyperref[tab:paramrest]{Table A.1}.
 With $\alpha \equiv \left( \alpha_t \;\; \alpha_s \right)^T$,
@@
 	$$ \lim_{c_2/c_1 \to 0} \frac{\partial \log(X_1/X_2)}{\partial \log(c_2/c_1)} = 1$$
-	Additionally, we can see that the elasticity of substition between $X_1$ and $X_2$ is linear with respect to $X_1/X_2$. That is, note that we may rewrite the elasticity above as:
+	Additionally, we can see that the elasticity of substitution between $X_1$ and $X_2$ is linear with respect to $X_1/X_2$. That is, note that we may rewrite the elasticity above as:
 	\begin{align*}
@@
 	\end{align*}
-	Since the parameters $\alpha$ and $c$ are exogenous constants, we have shown that $e$ can be written as a linear function of $X_1/X_2$. 
+	Hence, we have shown that $e$ can be written as a linear function of $X_1/X_2$. 
 	\\ \hfill

### 2019-06-10 documents/workshop_presentation.tex
Update for workshop
- matlab code
- R script
- tex file

\documentclass[aspectratio=169]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{booktabs}
\usepackage{color}
\usepackage{multirow}
\usepackage[percent]{overpic}
\usetheme[
outer/progressbar=foot,
outer/numbering=none]{metropolis}

% theme settings
\metroset{titleformat=smallcaps}

% highlighting
\newcommand{\highlight}[2][yellow]{\mathchoice%
	{\colorbox{#1}{$\displaystyle#2$}}%
	{\colorbox{#1}{$\textstyle#2$}}%
	{\colorbox{#1}{$\scriptstyle#2$}}%
	{\colorbox{#1}{$\scriptscriptstyle#2$}}}%

% images
\graphicspath{ {D:/Users/saketh/Documents/GitHub/BECCS-Case-Study/code/matlab/simulation_april/}}

% sig stars
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}

\newcommand{\xoverbrace}[2][\vphantom{\dfrac{A}{A}}]{\overbrace{#1#2}}
\newcommand{\xunderbrace}[2][\vphantom{\dfrac{A}{A}}]{\underbrace{#1#2}}

\begin{document}
	\author{Saketh Aleti \& Gal Hochman}
	\title{Efficient Pollution Abatement in Electricity Markets with Intermittent Renewable Energy}
	%\subtitle{}
	%\logo{}
	\institute{Rutgers University}
	%\date{February 22}
	%\subject{}
	%\setbeamercovered{transparent}
	%\setbeamertemplate{navigation symbols}{}
\begin{frame}[plain]
	\maketitle
\end{frame}

%%%%% To do
%% Line up stuff between empirical methodology equations

\begin{frame}
\frametitle{Motivation}

\begin{block}{\centering Constructing a realistic model of intermittency}
\vspace{2em}
``\textit{\dots the economics of all generating technologies, both intermittent and dispatchable, can be evaluated based on the expected market value of the electricity that they will supply, their total life-cycle costs, and their associated expected profitability. Such an analysis would reflect the actual expected production profiles of dispatchable and intermittent technologies, the value of electricity supplied at different times, and other costs of intermittency associated with reliable network integration.}'' (Joskow, 2011)

\end{block}

\end{frame}

\begin{frame}
\frametitle{Motivation}
\vspace{1em}

\begin{block}{\centering Intermittency matters}

	\vspace{1em}
	\begin{overpic}[width=1\textwidth,tics=10]{../documents/exhibits/ercot_load.pdf} 
		\put (42,13) {\only<2>{$\Bigg\}$ Underproduction }}
		\put (71,37) {\only<2>{$\Big\}$ Overproduction }}
	\end{overpic}

\end{block}

\end{frame}

%%%%%%remove
\begin{frame}
\frametitle{Literature}

\begin{itemize}
	\setlength\itemsep{0.2em}
	\item Some literature approach the problem by numerically optimizing the capacity of intermittent renewables given reliability constraints\footnote{(Musgens \& Neuhoff, 2006), (Neuhoff et al., 2007)}
	\item Other papers study how intermittent technologies affect the market itself\footnote{(Ambec \& Crampes, 2012), (Chao, 2011), (Borenstein, 2012)}	
	\item A common top-down approach is to model intermittency through a CES function between different energy technologies\footnote{See Papageorgiou et al. (2017) for a survey of the literature taking this approach}
	%\item Consumers prefer to smooth their electricity consumption\footnote{(Schwarz et al., 2002), (Herriges et al., 1993), (King \& Shatrawka, 2011).}
	\item Our model is closest to Helm and Mier (2019)
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Model -- Overview}

\begin{figure}
	\includegraphics[width=0.8\textwidth]{../documents/exhibits/model_diagram.png} 
\end{figure}

\vspace{-1em}

\begin{itemize}
	\setlength\itemsep{0.2em}
	\item Multi-period model with electricity consumers and producers
	\item Consumers purchase electricity in each period to maximize utility
	\item Producers build up capacity in generation technologies to maximize profit
	\item Market reaches an equilibrium through variable electricity prices
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Model -- Overview}

\begin{figure}
	\includegraphics[width=0.8\textwidth]{../documents/exhibits/model_diagram.png} 
\end{figure}

\vspace{-0.8em}

\begin{itemize}
	\setlength\itemsep{0.2em}
	\item[$\implies$] Elasticity of substitution between renewables and fossil fuels is non-constant
	\item[$\implies$] The importance of intermittency (in terms of welfare) increases with the intermittency of present generation
	\item[$\implies$] Batteries can drastically increase the substitutability of renewables and fossil fuels
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Model -- Consumers}

%\begin{block}{Consumer assumptions}
%	\begin{itemize}
%		\setlength\itemsep{0.25em}
%		\item Representative consumer who purchases and uses electricity in each period
%		\item Consumers prefer to use different amounts of electricity at different times
%		\item Consumers will substitute electricity consumption across time periods based on relative prices\footnote{ This has been empirically studied by Schwarz et al. (2002), Herriges et al. (1993), King \& Shatrawka (2011).}
%	\end{itemize}
%\end{block}

\begin{columns}[T]%beamer

	\column{0.4\textwidth}
	\begin{figure}
		\includegraphics[width=1\textwidth]{../documents/exhibits/model_diagram_cons.png} 
	\end{figure}

	\column{0.6\textwidth}	
		\begin{block}{Consumer assumptions}
			\begin{itemize}
				\setlength\itemsep{0.25em}
				\item Representative consumer who purchases and uses electricity in each period
				\item Consumers prefer to use different amounts of electricity at different times
				\item Consumers will substitute electricity consumption across time periods based on relative prices%\footnote{ This has been empirically studied by Schwarz et al. (2002), Herriges et al. (1993), King \& Shatrawka (2011).}
			\end{itemize}
		\end{block}

\end{columns}

\end{frame}

\begin{frame}
\frametitle{Model -- Consumers}

\metroset{block=fill}

\vspace{1em}
\begin{block}{\centering{Consumer's Optimization Problem}}
	\small
	\begin{align*}
	\\[-3em] \text{\textbf{Utility}: } &U = \left( \sum_t \alpha_t Z_t^\phi  \right)^{1/\phi} \\[1em]
	\text{\textbf{Budget Constraint}: } &I = \sum_t p_t Z_t \\[-2.5em]
	\end{align*}
\end{block}

\begin{itemize}
	\setlength\itemsep{0.25em}
	\small
	\item $\alpha_t$ captures preference to use different amounts of electricity at different times
	\item $\phi$ captures preference to substitute electricity consumption across time periods based on relative prices
	\item  $\sigma = 1/(1-\phi)$ is the intertemporal elasticity of substitution for electricity consumption
	\item Total cost of electricity equals the cost of electricity consumed in each period
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Model -- Firms}

\begin{columns}[T]%beamer

	\column{0.4\textwidth}
	\begin{figure}
		\includegraphics[width=1\textwidth]{../documents/exhibits/model_diagram_prod.png} 
	\end{figure}

	\column{0.6\textwidth}	
	\begin{block}{Producer assumptions}
		\begin{itemize}
			\setlength\itemsep{0.25em}
			\item Representative firm that maximizes profit
			\item Firms build a fixed amount of capacity in different generation technologies
			\item Different technologies can access different fractions of their capacity in each period
			\item Output is not stochastic; we focus our model on intermittency rather than reliability
		\end{itemize}
	\end{block}

\end{columns}

\end{frame}

\begin{frame}
\frametitle{Model -- Firms}

\metroset{block=fill}

\vspace{1em}
\begin{block}{\centering{Firm's Optimization Problem}}
	\small
	\begin{align*}
	\\[-3em] \text{\textbf{Profit}: } &\Pi = p^T Z - c^T X \\[1em]
	&= p^T \xi X - c^T X \\[-2.5em]
	\end{align*}
\end{block}

\begin{itemize}
	\setlength\itemsep{0.25em}
	\item Firms choose fixed quantities $X_i$ of each generation technology $i$ 
	\item Technology $i$ produces $\xi_{i,t}$ electricity per unit in period $t$
	\item Cost of building  $X_i$ units of generation technology $i$ is  $c_i X_i$
	\item Reminiscent of Joskow (2011) $\implies$ $X$ is chosen  ``\textit{\dots based on the expected market value of the electricity that they will supply, their total life-cycle costs, and their associated expected profitability\dots}''
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Model -- Solution}

\metroset{block=fill}

\begin{block}{\centering Equilibrium}
	\begin{align*}
	\\[-3em] \text{\textbf{Utility Max}: } Z_t &= \left(\frac{\alpha_t}{p_t} \right)^\sigma \frac{I}{\sum_t \alpha_t^\sigma p_t^{1-\sigma}} \\[1em]
	 \text{\textbf{Profit Max}: \hspace{0.1em} }	p &= \xi^{-1} c \\[-2.5em]
	\end{align*}
\end{block}

\vspace{1em}

\begin{itemize}
	\setlength\itemsep{0.25em}
	\item Consumer's optimum is the standard CES solution
	\item Analytically tractable only when $\sigma = 1$ and number of generation technologies equals the number of periods
	\item Can study the solution numerically by parametrizing $\xi, c, \alpha$, and $\sigma$. 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Empirical Methodology}

\vspace{2em}
\begin{block}{\centering{Goal}}
	\centering \vspace{0.2em}
	Estimate the intertemporal elasticity of \\
	substitution for electricity consumption $\sigma$
\end{block}
\vspace{1em}

\begin{itemize}
	\setlength\itemsep{0.75em}
	\item <1->CES First order condition: $\dfrac{Z_t}{Z_s} = \left(\dfrac{\alpha_t \, p_s}{\alpha_s \, p_t} \right)^\sigma $
	\item <1->Cet par, an IES Of $\sigma$ implies a 1\% increase in the relative price of electricity $(P_{t}/P_{t+1})$  decreases relative electricity consumption $(Z_{t}/Z_{t+1})$  by $\sigma\%$
	\item <2->Directly affects the economic importance of intermittency
	\item <2->Literature has estimated $\sigma$ to be around 0.05 
\end{itemize}
\vspace{2.75em}

\end{frame}

\begin{frame}
\frametitle{Empirical Methodology -- Theory}

$$\xoverbrace{\ln (Z_{ t, i} / Z_{ s, i}) = -\sigma \ln (P_{t,i} / P_{s,i})}^{\text{CES First Order Condition}}$$
\vspace{-1.75em}
$$+  \sigma \ln (\alpha_{t,i} / \alpha_{s,i}) + u_i$$
\vspace{1em}
\begin{itemize}
	\setlength\itemsep{0.25em}
	\item $\sigma$ = Intertemporal elasticity of substitution for electricity consumption
	\item $\ln (Z_{t, i} / Z_{s, i})$ = Log Difference in electricity consumption
	\item $\ln (P_{t,i} / P_{s,i})$ = Log Difference in electricity prices
	\item $\alpha_{t,i},\, \alpha_{s,i}$ = Demand shifters
	\item Subscripts $t$ and $s$ refer to time periods while $i$ refers to observations
\end{itemize}
\vspace{2.75em}

\end{frame}

\begin{frame}
\frametitle{Empirical Methodology -- Theory}

	$$\xoverbrace{\ln (Z_{ t, i} / Z_{ s, i}) = -\sigma \ln (P_{t,i} / P_{s,i})}^{\text{CES First Order Condition}}$$
	\vspace{-1.5em}
	$$+  \xunderbrace{\,\gamma_{t,i}  CDD_{t,i} + \omega_{t,i} HDD_{t,i} + \gamma_{s,i} CDD_{s,i} +  \omega_{s,i} HDD_{s,i}  + \eta \Delta_{t,s}}_{\text{Demand Controls}} + u_i$$

	\begin{itemize}
		\setlength\itemsep{0.25em}
		\item $\sigma$ = Intertemporal elasticity of substitution for electricity consumption
		\item $\ln (Z_{t, i} / Z_{s, i})$ = Log Difference in electricity consumption
		\item $\ln (P_{t,i} / P_{s,i})$ = Log Difference in electricity prices
		\item $CDD_{t,i}$ = Cooling Degree Days
		\item $HDD_{t,i}$ = Heating Degree Days
		\item $\Delta_{t,s}$ = Difference in months between periods $t$ and $s$
	\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Empirical Methodology -- Theory}

\vspace{2em}
\begin{block}{\centering What if there was intertemporal substitution on the supply side?}

	\vspace{2em}
	\begin{itemize}
		\item During the 1973 oil crisis,  refineries increased gasoline stocks expecting higher future prices
		\item Previous literature has not accounted for endogeneity
		\item Might bias $\sigma$ downwards
	\end{itemize}

\end{block}

\end{frame}

\begin{frame}
\frametitle{Empirical Methodology -- Theory}

\vspace{1em}

\begin{table}
	\begin{tabular}{@{\extracolsep{2em}}lc}
		\multirow{2}{*}{\textbf{Demand:}}\quad & $\ln (Z_{ t, i} / Z_{ s, i}) = -\sigma \ln (P_{t,i} / P_{s,i}) + \,\gamma_{t,i}  CDD_{t,i} $\\
		& $+ \,\omega_{t,i} HDD_{t,i} + \gamma_{s,i} CDD_{s,i} +  \omega_{s,i} HDD_{s,i}  + \eta \Delta_{t,s} + u_i$ \\[1em]
		\multirow{2}{*}{\textbf{Supply:}}\quad & $\ln (Z_{ t, i} / Z_{ s, i}) = \beta \ln (P_{t,i} / P_{s,i})$\\
		& $+ \,\psi$  \hspace{-0.25em}\colorbox{yellow}{$\ln (C_{t,i} / C_{s,i})$}$  + v_{i}$
	\end{tabular}
\end{table}

\vspace{1em}

\begin{itemize}
	\item $\ln (C_{t,i} / C_{s,i})$ = Log Difference in coal prices
	\item Coal prices affect the supply of electricity but not its demand
	\item Can use IV to handle endogeneity
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Empirical Methodology -- Approach}

\begin{itemize}
	\setlength\itemsep{1em}
	\item Approach the problem using OLS, IV (2SLS), and a semiparametric regression
	\item \textbf{Semiparametric regression} - Partially Linear IV
	\begin{itemize}
		\item<1-> Places controls (degree days, time) and instrument (coal prices) in smooth, unknown functions estimated using Kernel regressions
		\item<2->  Error term assumed to be mean zero but may be non-Gaussian
		\item<3->  Will produce different results than 2SLS if these functions are \textit{actually} non-linear 
		\item<4->  I find semiparametric results are significantly different from 2SLS
	\end{itemize} 
\end{itemize}

\vspace{7.5em}

\end{frame}

\begin{frame}
\frametitle{Empirical Methodology -- Approach}

\vspace{0.1em}

\begin{itemize}
	\setlength\itemsep{1em}
	\item Approach the problem using OLS, IV (2SLS), and a semiparametric regression
	\item \textbf{Semiparametric regression} - Partially Linear IV
	\begin{itemize}
		\item Places controls (degree days, time) and instrument (coal prices) in smooth, unknown functions estimated using Kernel regressions
		\item Error term assumed to be mean zero but may be non-Gaussian
		\item Will produce different results than 2SLS if these functions are \textit{actually} non-linear 
		\item I find semiparametric results are significantly different from 2SLS
	\end{itemize} 
\end{itemize}

\begin{table}
	\begin{tabular}{@{\extracolsep{2em}}lc}
		\multirow{2}{*}{\textbf{Demand:}}\quad & $\ln (Z_{ t, i} / Z_{ s, i}) = -\sigma \ln (P_{t,i} / P_{s,i})   $ \\
		& $+ $ \colorbox{yellow}{$f(CDD_{t,i}, HDD_{t,i}, CDD_{s,i} , HDD_{s,i}, \Delta_{t,s} )$}$ + u_i$ \\[1em]
		\multirow{2}{*}{\textbf{Supply:}}\quad & $\ln (Z_{ t, i} / Z_{ s, i}) = \beta \ln (P_{t,i} / P_{s,i})$\\
		& $+ $\colorbox{yellow}{$g(\ln (C_{t,i} / C_{s,i}))$}$  + v_{i}$
	\end{tabular}
\end{table}

\end{frame}

\begin{frame}
\frametitle{Data}

\begin{itemize}
	\setlength\itemsep{1em}
	\item Panel consists of monthly data for each state in the US from 2011 to 2018
	\item Monthly retail electricity price and consumption data is obtained from the EIA
	\item Coal prices for the same period are also obtained from the EIA
	\item Degree day data is collected from the NOAA
	\item Each variable is trimmed by 1\%
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Results}

\begin{table}
\caption{Partially Linear IV Regression Results}
\label{table:3} 
\small
\begin{tabular}{@{\extracolsep{4em}}lccc} 
	\\[-5ex]\hline  
	\hline \\[-1.8ex] 
	& \multicolumn{3}{c}{\textit{Instrument: $ \ln (C_{t,i} / C_{s,i})$}} \\ 
	\cline{2-4} 
	%\\[-1.8ex] & ln\_load\_rel \textasciitilde ln\_price\_rel & ln\_load\_rel \textasciitilde (CDD\_1) & ln\_load\_rel \textasciitilde time\_diff + (CDD\_1) \\ 
	\\[-1.8ex] & (1) & (2) & (3)\\ [0.5ex]
	\hline \\[-1.8ex] 
	$\hat{\sigma} $ & 2.9976$^{***}$ & 1.2123$^{***}$ & \colorbox{yellow}{0.8847}$^{***}$ \\ 
	& (0.169) & (0.052) & (0.044) \\ [0.9ex]
	\hline \\[-1.8ex] 
	Time Control &   &   & Yes  \\ 
	Degree Day Controls &   & Yes  & Yes  \\ 
	Observations & 6817 & 6817 & 6817 \\
	\hline 
	\hline \\[-2.5ex] 
	\multicolumn{4}{@{}p{37em}@{}}{\scriptsize \textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions. The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$. The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state.  Robust standard errors are reported in parentheses. *p$\textless$0.05, **p$\textless$0.01, ***p$\textless$0.001}  \\ 
\end{tabular} 
\end{table}

\end{frame}

\begin{frame}
\frametitle{Discussion}

\vspace{2em}

\begin{block}{\centering What are the practical implications of IES $\boldsymbol{\sigma}$ = 0.88?}
\end{block}

\vspace{1em}

\begin{itemize}
	\setlength\itemsep{0.5em}
	\item<1-> Consider our model in a setting with two periods (peak and off-peak) and two technologies (solar and coal)
	\item<2-> We parametrize our  model using data on cost and efficiency from the EIA
	\item<3-> We numerically evaluate this model to understand the effects of intermittency
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Discussion}

\vspace{2em}

\begin{block}{Does intermittency motivate a CES relationship between renewables and fossil fuel technologies? }
	\begin{itemize}
		\setlength\itemsep{0.5em}
		\item<1-> Many papers assume electricity should be modeled as a CES function of renewable and fossil fuel capacity or capital
		\item<1-> Often something like: $Electricity = (\alpha \cdot {Renewables}^\phi + \beta \cdot {Fossils}^\phi)^{1/\phi}$
		\item<2-> Does this relationship arise in our model? Is the elasticity of substitution ($e$) between these technologies constant? 
		\item<2-> We numerically estimate the elasticity of substitution $e$ between solar and coal in our model
	\end{itemize}
\end{block}

\vspace{1em}

\end{frame}

\begin{frame}
\frametitle{Discussion}

\begin{block}{\centering The elasticity of substitution between technologies is not constant}
\end{block}

\hspace*{-1.5em}
\begin{overpic}[width=1.1\textwidth,tics=10]{../code/matlab/simulation_april/fig_elasticity_x.png} 
	\put (24,11.5) {\colorbox{yellow}{$\leftarrow$ More reliance on solar, lower $e$}}
	\put (46,36) {\colorbox{yellow}{More reliance on coal, higher $e$ $\rightarrow$ }}
\end{overpic}

\end{frame}

\begin{frame}
\frametitle{Discussion}

\begin{block}{\centering The elasticity of substitution between technologies is not constant}
\end{block}

\hspace*{-1.5em}
\begin{overpic}[width=1.1\textwidth,tics=10]{../code/matlab/simulation_april/fig_elasticity_x.png} 
	\put (20,33) {\colorbox{yellow}{\parbox{22em}{As the electricity supply becomes more intermittent, baseload technologies become more valuable}}}
\end{overpic}

\end{frame}

\begin{frame}
\frametitle{Discussion}

\begin{block}{\centering Demand for base load capacity becomes more inelastic with its price }
\end{block}

\hspace*{-1.5em}
\begin{overpic}[width=1.1\textwidth,tics=10]{../code/matlab/simulation_april/fig_coal_elas_x.png} 
	\put (35,22) {\colorbox{yellow}{\parbox{22em}{As the electricity supply becomes more intermittent, baseload technologies become more valuable}}}
\end{overpic}

\end{frame}

\begin{frame}
\frametitle{Discussion}

\begin{block}{Why does a non-linear elasticity of substitution between intermittent and base load technologies matter?}
	\begin{itemize}
		\setlength\itemsep{0.5em}
		\item Over time, we may expect the share of renewable energy to increase $\implies$ elasticity of substitution between renewables and fossil fuels will decrease over time
		\item Taxes/subsidies need to be increasingly larger to shift the same fraction of capacity towards renewables and away from fossil fuels 
		\item Models assuming a constant elasticity of substitution may not be realistic
	\end{itemize}
\end{block}
\end{frame}

\begin{frame}
\frametitle{Discussion}

\begin{block}{How should we handle pollution abatement when generation is intermittent?}
	\begin{itemize}
		\setlength\itemsep{0.5em}
		\item<1-> Carbon taxes still work
		\item<2-> Should also account for its distributional effects
		\item<3-> Greater welfare losses in regions without access to non-intermittent renewables
		\item<4-> Can turn into an equity--efficiency trade--off
	\end{itemize}
\end{block}
\end{frame}

\begin{frame}
\frametitle{Discussion}

\begin{block}{\centering Distribution of Hydrothermal and Geothermal Plants (EIA, 2019)}
\end{block}

\begin{figure}
	\vspace{-1em}
	\includegraphics[width=0.8\textwidth]{../documents/exhibits/rel_renew_map.pdf} 
\end{figure}

\end{frame}

\begin{frame}
\frametitle{Discussion -- Batteries}

\begin{block}{Improving battery technology can make a significant difference}
	\begin{itemize}
		\setlength\itemsep{0.5em}
		\item Reducing the intermittency of renewables greatly increases their substitutability
		\item Mitigates the distributional side effects of intermittency + carbon taxes
		\item Can roughly approximate the effects of batteries in our model by shifting solar output to the off-peak period when it under-produces
	\end{itemize}
\end{block}
\end{frame}

\begin{frame}
\frametitle{Discussion -- Batteries}

\begin{block}{\centering Using batteries to shift solar output greatly increases its substitutability}
\end{block}

\hspace*{-1.5em}
\begin{overpic}[width=1.1\textwidth,tics=10]{../code/matlab/simulation_april/fig_batteries_x.png} 
	\put (31,30) {\colorbox{yellow}{\parbox{15em}{Shifting 10\% of solar output doubles the elasticity when the majority of generation is intermittent}}}
	\linethickness{2pt}
	\put(31,27){\color{black}\vector(-1,-1){6.5}}
\end{overpic}

\end{frame}

\begin{frame}
\frametitle{Discussion -- Batteries}

\begin{block}{\centering Initially, increasing returns to batteries and substitutability}
\end{block}

\hspace*{-1.5em}
\begin{overpic}[width=1.1\textwidth,tics=10]{../code/matlab/simulation_april/fig_batteries_x.png} 
	\put (32,35) {\colorbox{yellow}{\parbox{16em}{Elasticity increases by $\approx 25\%$ for a 5\% shift but by $\approx 70\%$ for a 10\% shift}}}
	\linethickness{2pt}
	\put(70,31.5){\color{black}\vector(4,-3){8}}
	\put(73,31.5){\color{black}\vector(3,-2){3}}
\end{overpic}

\end{frame}

\begin{frame}
\frametitle{Discussion -- Improving Models}

\begin{block}{How can future models of energy generation substitutability be improved?}
	\begin{itemize}
		\setlength\itemsep{0.5em}
		\item <1-> Assuming a constant elasticity of substitution between renewables and fossil fuels does not accurately capture intermittency
		\item <1-> Empirical estimates of the elasticity of substitution may be incorrect since the functional form (CES) does not seem to be appropriate 
		\item <2-> Directly implementing our model may not allow for analytical tractability
		\item <2-> Can try the variable elasticity of substitution (VES) form instead\footnote{The VES function was first defined in Revankar (1971).}
	\end{itemize}
\end{block}
\end{frame}

\begin{frame}
\frametitle{Discussion -- Improving Models}

\begin{block}{\centering VES approximation of the relationship between solar and coal}
\end{block}

\hspace*{-1.5em}
\begin{overpic}[width=1.1\textwidth,tics=10]{../code/matlab/simulation_april/fig_ves_approx_x.png} 
\end{overpic}

\end{frame}

\begin{frame}
\frametitle{Discussion -- Improving Models}

\begin{block}{What exactly is the VES function?}
	\begin{itemize}
		\setlength\itemsep{0.5em}
		\item Assumes that the elasticity of substitution between factors varies as a linear function of their quantities
		\item Can be empirically estimated
		\item Simpler to implement in a theoretical or numerical framework than our model
	\end{itemize}
	\begin{align*}
	&Z = \gamma X_1^{\omega(1-\delta \rho)} \left( X_2 + (\rho - 1) X_1 \right)^{\omega \delta \rho} \\
	&\highlight{e = 1 + \beta (X_1 / X_2)} \\
	&\,\beta = (\rho - 1) / ( 1- \delta \rho ) 
	\end{align*}
	\vspace{-4ex}
	$$\gamma > 0, \quad \omega > 0, \quad0 < \delta < 1, \quad 0 \leq \delta \rho \leq 1 , \quad (X_2/X_1) >  -\beta $$
\end{block}

\end{frame}

\begin{frame}
\frametitle{Conclusion}

\begin{itemize}
	\setlength\itemsep{0.75em}
	\item Welfare effects of carbon taxes and renewable subsidies depend on the intermittency of renewables and thus vary geographically
	\item Intermittency can create a trade-off between efficiently and equitably preventing climate change
	\item Subsidizing battery research can complement other policies by increasing the substitutability of renewable and fossil energy while mitigating their unintentional distributional consequences 
	\item The VES function can do a reasonable job of approximating the substitutability between renewables and fossil fuels
\end{itemize}

\end{frame}

%%%%%%% References
\begin{frame}[allowframebreaks]
\frametitle{References}
\tiny

\begin{itemize}

\item Acemoglu, D., Aghion, P., Bursztyn, L., \& Hemous, D. (2012). The Environment and Directed Technical Change. American Economic Review, 102(1), 131–166. https://doi.org/10.1257/aer.102.1.131

\item Adelman, M. A. (1995). The genie out of the bottle: World oil since 1970. MIT Press.

\item Ambec, S., \& Crampes, C. (2012). Electricity provision with intermittent sources of energy. Resource and Energy Economics, 34(3), 319–336. https://doi.org/10.1016/j.reseneeco.2012.01.001

\item Aubin, C., Fougere, D., Husson, E., \& Ivaldi, M. (1995). Real-time pricing of electricity for residential customers: Econometric analysis of an experiment. Journal Of Applied Econometrics, 10, S171–S191.

\item Borenstein, S. (2012). The Private and Public Economics of Renewable Electricity Generation. Journal of Economic Perspectives, 26(1), 67–92. https://doi.org/10.1257/jep.26.1.67

\item Chao, H. (2011). Efficient pricing and investment in electricity markets with intermittent resources. Energy Policy, 39(7), 3945–3953. https://doi.org/10.1016/j.enpol.2011.01.010

\item Climate Prediction Center (2019). Degree Days Statistics. National Oceanic and Atmospheric Administration. https://www.cpc.ncep.noaa.gov/products/analysis\_monitoring/cdus/degree\_days/

\item Delarue, E., De Jonghe, C., Belmans, R., \& D’Haeseleer, W. (2010). Applying portfolio theory to the electricity sector: Energy versus power. Energy Economics, 33(1), 12–23. https://doi.org/10.1016/j.eneco.2010.05.003

\item Deryugina, T., Mackay, A., \& Reif, J. (2017). The Long-Run Dynamics of Electricity Demand: Evidence from Municipal Aggregation. NBER Working Paper Series. https://doi.org/10.3386/w23483

\item Electricity Information Administration (2019a). Net generation, United States, all sectors, annual. Electricity Data Browser. https://www.eia.gov/electricity/data/browser

\item Electricity Information Administration (2019b). Levelized Cost and Levelized Avoided Cost of New Generation. Annual Energy Outlook 2019. https://www.eia.gov/outlooks/aeo/pdf/electricity\_generation.pdf

\item Electricity Information Administration (2019c). U.S. renewable electricity generation has doubled since 2008. Today in Energy. https://www.eia.gov/todayinenergy/detail.php?id=38752

\item Fan, S., \& Hyndman, R. (2011). The price elasticity of electricity demand in South Australia. Energy Policy, 39(6), 3709–3719. https://doi.org/10.1016/j.enpol.2011.03.080

\item Foley, A., Leahy, P., Marvuglia, A., \& Mckeogh, E. (2012). Current methods and advances in forecasting of wind power generation. Renewable Energy, 37(1), 1–8. https://doi.org/10.1016/j.renene.2011.05.033

\item Geroski, P. (2000). Models of technology diffusion. Research Policy. Elsevier B.V. https://doi.org/10.1016/S0048-7333(99)00092-X

\item Helm, C., \& Mier, M. (2019). On the efficient market diffusion of intermittent renewable energies. Energy Economics, 80, 812–830. https://doi.org/10.1016/j.eneco.2019.01.017

\item Herriges, J., Baladi, S., Caves, D., \& Neenan, B. (1993). The Response of Industrial Customers to Electric Rates Based Upon Dynamic Marginal Costs. The Review of Economics and Statistics, 75(3), 446. https://doi.org/10.2307/2109458

\item Joskow, P. (2011). Comparing the Costs of Intermittent and Dispatchable Electricity Generating Technologies. American Economic Review, 101(3), 238–241. https://doi.org/10.1257/aer.101.3.238

\item King, Kathleen, and Peter Shatrawka (1994). "Customer Response to a Permanent Time- Varying
Pricing Program in the United Kingdom." Laurits R. Christensen Associates, Madison,
Wisconsin.

\item Mohajeryami, S., Moghaddam, I., Doostan, M., Vatani, B., \& Schwarz, P. (2016). A novel economic model for price-based demand response. Electric Power Systems Research, 135, 1–9. https://doi.org/10.1016/j.epsr.2016.03.026

\item Musgens, F., \& Neuhoff, K. (2006). Modelling Dynamic Constraints in Electricity Markets and the Costs of Uncertain Wind Output. Faculty of Economics.

\item Neuhoff, K., Cust, J. \& Keats, K. (2007). Implications of intermittency and transmission constraints for renewables deployment. Cambridge Working Papers in Economics 0711, Faculty of Economics, University of Cambridge.

\item Newey, W. (1990). Efficient Instrumental Variables Estimation of Non-linear Models. Econometrica, 58(4), 809–837. https://doi.org/10.2307/2938351

\item ORNL (2004). Measurement practices for reliability and power quality. A toolkit of reliability measurement practices. U.S. Department of Energy. https://info.ornl.gov/sites/publications/Files/Pub57467.pdf

\item Papageorgiou, C., Saarn, M., \& Schulte, P. (2017). Substitution between clean and dirty energy inputs: a macroeconomic perspective.(Author abstract). Review of Economics and Statistics, 99(2), 201–212. https://doi.org/10.1162/REST\_a\_00623

\item Reiss, P., \& White, M. (2005). Household Electricity Demand, Revisited. The Review of Economic Studies, 72(252), 853. Retrieved from http://search.proquest.com/docview/204335314/

\item Revankar, N. (1971). A Class of Variable Elasticity of Substitution Production Functions. Econometrica, 39(1), 61–71. https://doi.org/10.2307/1909140

\item Schwarz, P., Taylor, T., Birmingham, M., \& Dardan, S. (2002). Industrial response to electricity real-time prices: short run and long run. Economic Inquiry, 40(4), 597–610. https://doi.org/10.1093/ei/40.4.597

\item Shahriari, M., \& Blumsack, S. (2018). The capacity value of optimal wind and solar portfolios. Energy, 148, 992–1005. https://doi.org/10.1016/j.energy.2017.12.121

\item Silverman, B. (1986). Density estimation for statistics and data analysis. London; Chapman and Hall.

\item Zhou, S. \& Teng, F., (2013). Estimation of urban residential electricity demand in China using household survey data.(Statistical data). Energy Policy, 61, 394–402.

\item Staiger, D., \& Stock, J. (1997). Instrumental Variables Regression with Weak Instruments. Econometrica, 65(3), 557–586. https://doi.org/10.2307/2171753

\item U.S. Bureau of Economic Analysis (2019). Personal consumption expenditures: chain-type price index. FRED, Federal Reserve Bank of St. Louis. https://fred.stlouisfed.org/series/PCEPI, April 27, 2019.

\item Wolak, F., \& Patrick, R. (2001). The Impact of Market Rules and Market Structure on the Price Determination Process in the England and Wales Electricity Market. NBER Working Paper Series. https://doi.org/10.3386/w8248

\item Woo, C., Chow, P., \& Horowitz, I. (1996). Optional real-time pricing of electricity for industrial firms. Pacific Economic Review, 1(1), 79–92. https://doi.org/10.1111/j.1468-0106.1996.tb00175.x

\item Zarnikau, J. (1990). Customer Responsiveness to Real-Time Pricing of Electricity. The Energy Journal, 11(4), 99. https://doi.org/10.5547/ISSN0195-6574-EJ-Vol11-No4-6

\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Appendix -- OLS Results}

\begin{table}[t] \centering 
	\caption{OLS Regression Results}
	\label{table:1} 
	\footnotesize
	\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
		\\[-5ex]\hline  
		\hline \\[-1.8ex] 
		& \multicolumn{6}{c}{\textit{Dependent variable:} $\ln (Z_{ t, i} / Z_{ s, i})$} \\ [0.5ex]
		\cline{2-7} 
		\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ [0.5ex]
		\hline \\[-1.8ex] 
		$-\ln (P_{t,i} / P_{s,i})$ & 0.937$^{***}$ & 1.075$^{***}$ & 1.098$^{***}$ & 1.074$^{***}$ & 1.263$^{***}$ & 1.305$^{***}$ \\ 
		& (0.030) & (0.026) & (0.026) & (0.224) & (0.172) & (0.169) \\  [0.9ex]
		\hline \\[-1.8ex] 
		Time Control &   &   & Yes &   &   & Yes  \\ 
		Degree Day Controls &   & Yes  & Yes &   & Yes  & Yes \\ 
		State FEs &   &   &   & Yes & Yes & Yes \\ 
		Observations & 6,817 & 6,817 & 6,817 & 6,817 & 6,817 & 6,817 \\ 
		Adjusted R$^{2}$ & 0.079 & 0.506 & 0.508 & 0.085 & 0.518 & 0.520 \\  
		F Statistic & 582$^{***}$  & 1399$^{***}$  & 1172$^{***}$ & 685$^{***}$  & 1474$^{***}$  & 1241$^{***}$  \\ [0.5ex]
		\hline 
		\hline \\[-1.8ex] 
		%\multicolumn{7}{@{}p{41.4em}@{}}{\textit{Note: } The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$. The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state. The coefficient on $-\ln (P_{t,i} / P_{s,i})$ is the estimate of $\sigma$. The variable $\Delta_{t,s}$ is the difference in months between periods $t$ and $s$. CDD$_t$ and HDD$_t$ refer to the total number of heating and cooling degree days in month $t$. We scale the coefficients on degree days for clarity. Robust standard errors are reported in parentheses. *p$\textless$0.05, **p$\textless$0.01, ***p$\textless$0.001}  \\ 
	\end{tabular} 
\end{table}

\end{frame}

\begin{frame}
\frametitle{Appendix -- IV Results}

\begin{table}[h] \centering 
	\caption{IV (2SLS) Regression Results}
	\label{table:2} 
	\scriptsize
	\begin{tabular}{@{\extracolsep{4pt}}lcccccc} 
		\\[-6ex]\hline  
		\hline \\[-1.6ex] 
		& \multicolumn{3}{c}{First-Stage} & \multicolumn{3}{c}{Second-Stage} \\ [0.5ex]
		& \multicolumn{3}{c}{\textit{Dep. Variable:} $\ln (P_{t,i} / P_{s,i})$ } & \multicolumn{3}{c}{\textit{Dep. Variable:}  $\ln (Z_{ t, i} / Z_{ s, i})$}\\ [0.5ex]
		\cmidrule(lr){2-4} \cmidrule(lr){5-7}\\[-2.9ex] 
		& (A.1) & (B.1) & (C.1) & (A.2) & (B.2) & (C.2)\\ [0.5ex]
		\hline \\[-1.8ex] 
		$ \ln (C_{t,i} / C_{s,i})$ & $-$0.042$^{***}$ & $-$0.018$^{***}$ & $-$0.018$^{***}$ &  &  &  \\ 
		& (0.002) & (0.002) & (0.002) &  &  &  \\ 
		& & & & & & \\[-1ex]
		$-\ln (P_{t,i} / P_{s,i})$ &  &  &  & 2.978$^{***}$ & 5.896$^{***}$ & 5.818$^{***}$ \\ 
		&  &  &  & (0.180) & (0.548) & (0.524) \\   [0.9ex]
		\hline \\[-1.8ex] 
		Time Control &   &   & Yes &   &   & Yes  \\ 
		Degree Day Controls &   & Yes  & Yes &   & Yes  & Yes \\ 
		State FEs &  Yes & Yes  & Yes  & Yes & Yes & Yes \\ 
		Observations & 6817 & 6817 & 6817 & 6817 & 6817 & 6817 \\ 
		Adjusted R$^{2}$ & 0.061 & 0.264 & 0.293 & &  &  \\ 
		F Statistic & 443$^{***}$  & 489$^{***}$ & 472$^{***}$  &  &  &  \\ 
		\hline 
		\hline \\[-1.8ex] 
		%\multicolumn{7}{@{}p{41.5em}@{}}{\textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions. The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$. The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state. The coefficient on $\ln (P_{t,i} / P_{s,i})$ is an estimate of $-\sigma$. The variable $\Delta_{t,s}$ is the difference in months between periods $t$ and $s$. CDD$_t$ and HDD$_t$ refer to the total number of heating and cooling degree days in month $t$. We scale the coefficients on degree days for clarity. Robust standard errors are reported in parentheses. *p$\textless$0.05, **p$\textless$0.01, ***p$\textless$0.001}  \\ 
	\end{tabular} 
\end{table}

\end{frame}

\begin{frame}
\frametitle{Appendix -- Model Parameters}

$$\underbrace{\alpha_t = 0.6, \,\alpha_s = 0.4}_{Demand\,\,parameters}, \,\underbrace{\xi_1 = (1, \, 1), \,\xi_2 = (1, \, 0.1)}_{Output\,\,parameters}, \,\underbrace{c_1 = 104.3, \,c_2 = 60}_{Cost \,\, parameters}$$

\begin{itemize}
	\setlength\itemsep{0.5em}
	\item We normalize quantity units in terms of capacity, so cost is given in \$/MWh and output is given as the fraction of capacity available in each period
	\item EIA LCOE estimates for 2023 for ``Coal with 30\% CCS'' and ``Solar PV''  are 104.3\$/MWh and 60\$/MWh $\implies$ $c_1 = 104.3$, $c_2 = 60$
	\item Based on the graph of ERCOT loads from earlier, consumers prefer that $\approx$ 60\% of their energy arrive between 900-2400 $\implies$ $(\alpha_t, \alpha_s) = (0.6, 0.4)$
	\item For same periods, solar output seems to be $\approx 10:1 \implies \xi_2 = (1, \, 0.1)$
	\item Coal output is assumed to be constant over both periods $\implies \xi_1 = (1, \, 1)$
\end{itemize}

\end{frame}

\end{document}

### 2019-06-10 code/R/workshop_graphs.R

@@ -33,6 +33,7 @@ folder <- '../../data/'
 plant_data <- read_excel(paste0(folder, 'EIA/plantlocations_04_2019.xlsx'))
 map_data_state  <- map_data("state")
 map_data_county <- map_data("county")
+ercot_data <- read_csv(paste0(folder, 'processed/ercot_load_solar.csv'))
 
 ## Clean up data
 
@@ -43,7 +44,10 @@ plant_data <- filter(plant_data,
 # Rename col
 plant_data$Capacity <- plant_data$`Nameplate Capacity (MW)`
 
+
 ## Plot
+
+# Geo Hydro plants
 
 rel_renew_plot <- ggplot() +
     geom_polygon(data = map_data_state, color = 'grey70', fill = 'white',
@@ -65,3 +69,28 @@ rel_renew_plot <- ggplot() +
 print(rel_renew_plot)
 ggsave('../../documents/exhibits/rel_renew_map.pdf',
        width = plot_width, height = plot_height, dpi = 600)
+
+# Ercot data
+
+ggplot(data = ercot_data) +
+    geom_line(aes(x = Hour, y = Load, color = 'Load'), size = 1) +
+    geom_line(aes(x = Hour, y = SolarGen*50, color = 'SolarGen'), size = 1) +
+    scale_y_continuous(expand = c(0, 100),
+        sec.axis = sec_axis(~./50, name = "Solar Generation (MW)")) +
+    scale_colour_manual(values = c("blue", "orange")) +
+    expand_limits(x = 0, y = 0) +
+    theme(legend.box = "vertical", legend.key.size = unit(0.5, "cm"),
+          legend.key.width = unit(2, "cm"), legend.title = element_blank(),
+          legend.direction = "horizontal", legend.position = "bottom",
+          legend.margin = margin(-0.25,0,0,0, unit="cm"),
+          legend.background = element_rect(fill = '#FAFAFA', color = '#FAFAFA'),
+          panel.background = element_rect(fill = '#FAFAFA', color = '#FAFAFA'),
+          plot.background = element_rect(fill = '#FAFAFA', color = '#FAFAFA'),
+          axis.line.x.bottom = element_line(size = 0.5, colour = "grey50"),
+          axis.line.y.left = element_line(size = 0.5, colour = "grey50"),
+          panel.grid.major = element_line(color = 'grey90'))
+
+
+
+
+

### 2019-06-10 code/matlab/simulation_april/sim_batteries_x.m

@@ -40,7 +40,7 @@ for j = 1:m
         if any(prices<0)
             continue
         end
-0
+
         % Price Index
         P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
         if sigma == 1
@@ -85,7 +85,7 @@ end
 
 % Format subplot 1
 % subplot(2,1,1);
-lgnd = legend('(0%)', '(5%)', '(10%)')
+lgnd = legend('(0%)', '(5%)', '(10%)');
 % xlabel({'Negative Log Difference in Costs', 'log(c_2/c_1)'})
 % ylabel({'Log Difference in Quantities', 'log(X_1/X_2)'})
 % xlim([-1.3, -0.4])

### 2019-06-10 code/matlab/simulation_april/sim_ves_x.m

@@ -1,0 +1,142 @@
+%% Elasticity of Substitution Sim with error bars on sigma estimate
+
+close all; clear; clc;
+
+% Simulation params
+n = 5000;
+cost_multiplier = linspace(0.9,2,n);
+sigma_range = [0.8847];
+m = length(sigma_range);
+
+% Exogenous params
+c_1 = 104.3;
+c_2 = 60;
+alpha = [0.6, 0.4];
+xi_1  = [1,   1];
+xi_2  = [1, 0.1];
+budget = 1;
+
+figure('Renderer', 'painters', 'Position', [100 100 900 400])
+hold on;
+
+for j = 1:m
+    
+    sigma = sigma_range(j);
+    results = zeros(n,2); 
+
+    for i = 1:n
+
+
+        phi   = (sigma - 1)/sigma;
+        x_1_cost_param = c_1*cost_multiplier(i);
+        x_2_cost_param = c_2;
+
+        % Prices
+        xi_mat   = [xi_1; xi_2];
+        cost_mat = [x_1_cost_param; x_2_cost_param];
+        prices   = xi_mat\cost_mat;
+
+        if any(prices<0)
+            continue
+        end
+
+        % Price Index
+        P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
+        if sigma == 1
+            P = 1;
+        end
+        
+        % Quantities
+        Y = ((alpha'./prices).^(sigma)) * (budget/P);
+           
+        X = (xi_mat')\Y;
+
+        results(i,:) = X';
+
+    end    
+
+    output = [];
+    output(1,:) = c_1*cost_multiplier'./c_2;
+    output(2,:) = results(:,1)./results(:,2);
+
+    % subset to positive quantities
+    ind = ~any(output <= 0);
+    output = output(:,ind);
+    
+    % relationship between e and the ratio of quantities
+    hold on;
+    
+    if sigma == 0.8847
+        plot(output(2,2:end), ...
+            diff(log(output(2,:)))./diff(-log(output(1,:))), ...
+            'LineWidth', 1.5, 'Color', 'k');
+    elseif sigma < 0.8846
+        plot(output(2,2:end), ...
+            diff(log(output(2,:)))./diff(-log(output(1,:))), ...
[…]

### 2019-06-13 documents/workshop_presentation.tex
Finalize workshop presentation

@@
 
+\newcommand\blfootnote[1]{%
+	\begingroup
+	\renewcommand\thefootnote{}\footnote{#1}%
+	\addtocounter{footnote}{-1}%
+	\endgroup
+}
+
 \begin{document}
@@
 \frametitle{Motivation}
-
-\begin{block}{\centering Constructing a realistic model of intermittency}
-\vspace{2em}
-``\textit{\dots the economics of all generating technologies, both intermittent and dispatchable, can be evaluated based on the expected market value of the electricity that they will supply, their total life-cycle costs, and their associated expected profitability.
-Such an analysis would reflect the actual expected production profiles of dispatchable and intermittent technologies, the value of electricity supplied at different times, and other costs of intermittency associated with reliable network integration.}'' (Joskow, 2011)
-
-\end{block}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Motivation}
 \vspace{1em}
 
-\begin{block}{\centering Intermittency matters}
+\begin{block}{\centering What is intermittency?}
 
@@
 
-%%%%%%remove
 \begin{frame}
-\frametitle{Literature}
+\frametitle{Motivation}
 
-\begin{itemize}
-	\setlength\itemsep{0.2em}
-	\item Some literature approach the problem by numerically optimizing the capacity of intermittent renewables given reliability constraints\footnote{(Musgens \& Neuhoff, 2006), (Neuhoff et al., 2007)}
-	\item Other papers study how intermittent technologies affect the market itself\footnote{(Ambec \& Crampes, 2012), (Chao, 2011), (Borenstein, 2012)}	
-	\item A common top-down approach is to model intermittency through a CES function between different energy technologies\footnote{See Papageorgiou et al.
-(2017) for a survey of the literature taking this approach}
-	%\item Consumers prefer to smooth their electricity consumption\footnote{(Schwarz et al., 2002), (Herriges et al., 1993), (King \& Shatrawka, 2011).}
-	\item Our model is closest to Helm and Mier (2019)
-\end{itemize}
+\begin{block}{\centering How should we model intermittency?}
+	\vspace{2em}
+	``\textit{\dots the economics of all generating technologies, both intermittent and dispatchable, can be evaluated based on the expected market value of the electricity that they will supply, their total life-cycle costs, and their associated expected profitability.
+Such an analysis would reflect the actual expected production profiles of dispatchable and intermittent technologies, the value of electricity supplied at different times, and other costs of intermittency associated with reliable network integration.}'' (Joskow, 2011)
+
+\end{block}
 
@@
 	\item Multi-period model with electricity consumers and producers
-	\item Consumers purchase electricity in each period to maximize utility
-	\item Producers build up capacity in generation technologies to maximize profit
-	\item Market reaches an equilibrium through variable electricity prices
+	\item Parametrize the model empirically
+	\item Numerically evaluate the model to study its implications
 \end{itemize}
@@
 \begin{frame}
-\frametitle{Model -- Overview}
+\frametitle{Model -- Preview of the Results}
 
@@
 \begin{itemize}
-	\setlength\itemsep{0.25em}
+	\setlength\itemsep{0.5em}
 	\small
-	\item $\alpha_t$ captures preference to use different amounts of electricity at different times
-	\item $\phi$ captures preference to substitute electricity consumption across time periods based on relative prices
-	\item  $\sigma = 1/(1-\phi)$ is the intertemporal elasticity of substitution for electricity consumption
+	\item $\alpha_t$ captures ``time'' preference 
+	\item  $\sigma = 1/(1-\phi)$ is the intertemporal elasticity of substitution (IES) 
 	\item Total cost of electricity equals the cost of electricity consumed in each period
@@
 			\item Different technologies can access different fractions of their capacity in each period
-			\item Output is not stochastic; we focus our model on intermittency rather than reliability
+			\item Output is not stochastic
 		\end{itemize}
@@
 
-\begin{frame}
-\frametitle{Empirical Methodology}
+%\begin{frame}
+%\frametitle{Empirical Methodology}
+%
+%\vspace{2em}
+%\begin{block}{\centering{Goal}}
+%	\centering \vspace{0.2em}
+%	Estimate the intertemporal elasticity of \\
+%	substitution for electricity consumption $\sigma$
+%\end{block}
+%\vspace{1em}
+%
+%\begin{itemize}
+%	\setlength\itemsep{0.75em}
+%	\item <1->CES First order condition: $\dfrac{Z_t}{Z_s} = \left(\dfrac{\alpha_t \, p_s}{\alpha_s \, p_t} \right)^\sigma $
+%	\item <1->Cet par, an IES of $\sigma$ implies a 1\% increase in the relative price of electricity $(p_{t}/p_{t+1})$  decreases relative electricity consumption $(Z_{t}/Z_{t+1})$  by $\sigma\%$
+%	\item <1->Directly affects the economic importance of intermittency
+%\end{itemize}
+%\vspace{2.75em}
+%
+%\end{frame}
 
-\vspace{2em}
-\begin{block}{\centering{Goal}}
-	\centering \vspace{0.2em}
-	Estimate the intertemporal elasticity of \\
-	substitution for electricity consumption $\sigma$
-\end{block}
-\vspace{1em}
+%\begin{frame}
+%\frametitle{Empirical Methodology -- Theory}
+%
+%
+%
+%$$\xoverbrace{\ln (Z_{ t, i} / Z_{ s, i}) = -\sigma \ln (P_{t,i} / P_{s,i})}^{\text{CES First Order Condition}}$$
+%\vspace{-1.75em}
+%$$+  \sigma \ln (\alpha_{t,i} / \alpha_{s,i}) + u_i$$
+%\vspace{1em}
+%\begin{itemize}
+%	\setlength\itemsep{0.25em}
+%	\item $\sigma$ = Intertemporal elasticity of substitution for electricity consumption
+%	\item $\ln (Z_{t, i} / Z_{s, i})$ = Log Difference in electricity consumption
+%	\item $\ln (P_{t,i} / P_{s,i})$ = Log Difference in electricity prices
+%	\item $\alpha_{t,i},\, \alpha_{s,i}$ = Demand shifters
+%	\item Subscripts $t$ and $s$ refer to time periods while $i$ refers to observations
+%\end{itemize}
+%\vspace{2.75em}
+%
+%\end{frame}
+%
+%
+%
+%\begin{frame}
+%\frametitle{Empirical Methodology -- Theory}
+%
+%
+%	
+%	$$\xoverbrace{\ln (Z_{ t, i} / Z_{ s, i}) = -\sigma \ln (P_{t,i} / P_{s,i})}^{\text{CES First Order Condition}}$$
+%	\vspace{-1.5em}
+%	$$+  \xunderbrace{\,\gamma_{t,i}  CDD_{t,i} + \omega_{t,i} HDD_{t,i} + \gamma_{s,i} CDD_{s,i} +  \omega_{s,i} HDD_{s,i}  + \eta \Delta_{t,s}}_{\text{Demand Controls}} + u_i$$
+%	 
+%	\begin{itemize}
+%		\setlength\itemsep{0.25em}
+%		\item $\sigma$ = Intertemporal elasticity of substitution for electricity consumption
+%		\item $\ln (Z_{t, i} / Z_{s, i})$ = Log difference in electricity consumption
+%		\item $\ln (P_{t,i} / P_{s,i})$ = Log difference in electricity prices
+%		\item $CDD_{t,i}$ = Cooling Degree Days
+%		\item $HDD_{t,i}$ = Heating Degree Days
+%		\item $\Delta_{t,s}$ = Difference in months between periods $t$ and $s$
+%	\end{itemize}
+%
+%\end{frame}
+%
+%
+%\begin{frame}
+%\frametitle{Empirical Methodology -- Theory}
+%
+%\vspace{2em}
+%\begin{block}{\centering What if there was intertemporal substitution on the supply side?}
+%	
+%	\vspace{2em}
+%	\begin{itemize}
+%		\item During the 1973 oil crisis,  refineries increased gasoline stocks expecting higher future prices
+%		\item Previous literature has not accounted for endogeneity
+%		\item Might bias $\sigma$ downwards
+%	\end{itemize}
+%	
+%\end{block}
+%
+%
+%
+%\end{frame}
 
-\begin{itemize}
-	\setlength\itemsep{0.75em}
-	\item <1->CES First order condition: $\dfrac{Z_t}{Z_s} = \left(\dfrac{\alpha_t \, p_s}{\alpha_s \, p_t} \right)^\sigma $
-	\item <1->Cet par, an IES Of $\sigma$ implies a 1\% increase in the relative price of electricity $(P_{t}/P_{t+1})$  decreases relative electricity consumption $(Z_{t}/Z_{t+1})$  by $\sigma\%$
-	\item <2->Directly affects the economic importance of intermittency
-	\item <2->Literature has estimated $\sigma$ to be around 0.05 
-\end{itemize}
-\vspace{2.75em}
-
-\end{frame}
+%	$$\xoverbrace{\ln (Z_{ t, i} / Z_{ s, i}) = -\sigma \ln (P_{t,i} / P_{s,i})}^{\text{CES First Order Condition}}$$
+%	\vspace{-1.5em}
+%	$$+  \xunderbrace{\,\gamma_{t,i}  CDD_{t,i} + \omega_{t,i} HDD_{t,i} + \gamma_{s,i} CDD_{s,i} +  \omega_{s,i} HDD_{s,i}  + \eta \Delta_{t,s}}_{\text{Demand Controls}} + u_i$$
 
@@
 
-$$\xoverbrace{\ln (Z_{ t, i} / Z_{ s, i}) = -\sigma \ln (P_{t,i} / P_{s,i})}^{\text{CES First Order Condition}}$$
-\vspace{-1.75em}
-$$+  \sigma \ln (\alpha_{t,i} / \alpha_{s,i}) + u_i$$
 \vspace{1em}
-\begin{itemize}
-	\setlength\itemsep{0.25em}
-	\item $\sigma$ = Intertemporal elasticity of substitution for electricity consumption
-	\item $\ln (Z_{t, i} / Z_{s, i})$ = Log Difference in electricity consumption
-	\item $\ln (P_{t,i} / P_{s,i})$ = Log Difference in electricity prices
-	\item $\alpha_{t,i},\, \alpha_{s,i}$ = Demand shifters
-	\item Subscripts $t$ and $s$ refer to time periods while $i$ refers to observations
-\end{itemize}
-\vspace{2.75em}
 
-\end{frame}
+%\begin{table}
+%	\begin{tabular}{@{\extracolsep{2em}}lc}
+%		\multirow{2}{*}{\textbf{Demand:}}\quad & $\ln (Z_{ t, i} / Z_{ s, i}) = -\sigma \ln (P_{t,i} / P_{s,i}) + \,\gamma_{t,i}  CDD_{t,i} $\\
+%		& $+ \,\omega_{t,i} HDD_{t,i} + \gamma_{s,i} CDD_{s,i} +  \omega_{s,i} HDD_{s,i}  + \eta \Delta_{t,s} + u_i$ \\[1em]
+%	\end{tabular}
+%\end{table}
 
-\begin{frame}
-\frametitle{Empirical Methodology -- Theory}
+\begin{table}
+	\begin{tabular}{@{\extracolsep{2em}}lc}
+		\multirow{2}{*}{\textbf{Demand:}}\quad & $\xoverbrace{\ln (Z_{ t, i} / Z_{ s, i}) = -\sigma \ln (P_{t,i} / P_{s,i})}^{\text{CES First Order Condition}}$\\
+		& $+  \xunderbrace{\,\gamma_{t,i}  CDD_{t,i} + \omega_{t,i} HDD_{t,i} + \gamma_{s,i} CDD_{s,i} +  \omega_{s,i} HDD_{s,i}  + \eta \Delta_{t,s}}_{\text{Demand Controls}} + u_i$ \\[1em]
+	\end{tabular}
+\end{table}
 
-	$$\xoverbrace{\ln (Z_{ t, i} / Z_{ s, i}) = -\sigma \ln (P_{t,i} / P_{s,i})}^{\text{CES First Order Condition}}$$
-	\vspace{-1.5em}
-	$$+  \xunderbrace{\,\gamma_{t,i}  CDD_{t,i} + \omega_{t,i} HDD_{t,i} + \gamma_{s,i} CDD_{s,i} +  \omega_{s,i} HDD_{s,i}  + \eta \Delta_{t,s}}_{\text{Demand Controls}} + u_i$$
+\vspace{1em}
 
 \begin{itemize}
-		\setlength\itemsep{0.25em}
-		\item $\sigma$ = Intertemporal elasticity of substitution for electricity consumption
-		\item $\ln (Z_{t, i} / Z_{s, i})$ = Log Difference in electricity consumption
-		\item $\ln (P_{t,i} / P_{s,i})$ = Log Difference in electricity prices
 	\item $CDD_{t,i}$ = Cooling Degree Days
@@
 \end{itemize}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Empirical Methodology -- Theory}
-
-\vspace{2em}
-\begin{block}{\centering What if there was intertemporal substitution on the supply side?}
-
-	\vspace{2em}
-	\begin{itemize}
-		\item During the 1973 oil crisis,  refineries increased gasoline stocks expecting higher future prices
-		\item Previous literature has not accounted for endogeneity
-		\item Might bias $\sigma$ downwards
-	\end{itemize}
-
-\end{block}
 
@@
 \begin{itemize}
-	\item $\ln (C_{t,i} / C_{s,i})$ = Log Difference in coal prices
+	\item $\ln (C_{t,i} / C_{s,i})$ = Log difference in coal prices
 	\item Coal prices affect the supply of electricity but not its demand
@@
 	\begin{itemize}
-		\item<1-> Places controls (degree days, time) and instrument (coal prices) in smooth, unknown functions estimated using Kernel regressions
-		\item<2->  Error term assumed to be mean zero but may be non-Gaussian
-		\item<3->  Will produce different results than 2SLS if these functions are \textit{actually} non-linear 
-		\item<4->  I find semiparametric results are significantly different from 2SLS
-	\end{itemize} 
-\end{itemize}
-
-\vspace{7.5em}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Empirical Methodology -- Approach}
-
-\vspace{0.1em}
-
-\begin{itemize}
-	\setlength\itemsep{1em}
-	\item Approach the problem using OLS, IV (2SLS), and a semiparametric regression
-	\item \textbf{Semiparametric regression} - Partially Linear IV
-	\begin{itemize}
 		\item Places controls (degree days, time) and instrument (coal prices) in smooth, unknown functions estimated using Kernel regressions
 		\item Error term assumed to be mean zero but may be non-Gaussian
-		\item Will produce different results than 2SLS if these functions are \textit{actually} non-linear 
-		\item I find semiparametric results are significantly different from 2SLS
+		\item Robust to misspecified functional forms on controls and instrument
 	\end{itemize} 
@@
 		\multirow{2}{*}{\textbf{Supply:}}\quad & $\ln (Z_{ t, i} / Z_{ s, i}) = \beta \ln (P_{t,i} / P_{s,i})$\\
-		& $+ $\colorbox{yellow}{$g(\ln (C_{t,i} / C_{s,i}))$}$  + v_{i}$
+		& $+ $\colorbox{yellow}{$g( C_{t,i} / C_{s,i})$}$  + v_{i}$
 	\end{tabular}
@@
 	\setlength\itemsep{0.5em}
-	\item<1-> Consider our model in a setting with two periods (peak and off-peak) and two technologies (solar and coal)
-	\item<2-> We parametrize our  model using data on cost and efficiency from the EIA
-	\item<3-> We numerically evaluate this model to understand the effects of intermittency
+	\item Consider our model in a setting with two periods (peak and off-peak) and two technologies (solar and coal)
+	\item We parametrize our  model using data on cost and efficiency from the EIA
+	\item We then numerically evaluate the model
 \end{itemize}
@@
 
-\begin{frame}
-\frametitle{Discussion}
-
-\begin{block}{Why does a non-linear elasticity of substitution between intermittent and base load technologies matter?}
-	\begin{itemize}
-		\setlength\itemsep{0.5em}
-		\item Over time, we may expect the share of renewable energy to increase $\implies$ elasticity of substitution between renewables and fossil fuels will decrease over time
-		\item Taxes/subsidies need to be increasingly larger to shift the same fraction of capacity towards renewables and away from fossil fuels 
-		\item Models assuming a constant elasticity of substitution may not be realistic
-	\end{itemize}
-\end{block}
-\end{frame}
+%\begin{frame}
+%\frametitle{Discussion}
+%
+%\begin{block}{What does a non-constant elasticity of substitution between intermittent and base load technologies imply?}
+%	\begin{itemize}
+%		\setlength\itemsep{0.5em}
+%		\item Models assuming a constant elasticity of substitution may not be realistic
+%		\item Taxes/subsidies need to be increasingly larger to shift the same fraction of capacity towards renewables and away from fossil fuels 
+%		\item Over time, we may expect the share of renewable energy to increase $\implies$ elasticity of substitution between renewables and fossil fuels will decrease over time
+%	\end{itemize}
+%\end{block}
+%\end{frame}
 
@@
 		\setlength\itemsep{0.5em}
-		\item<1-> Carbon taxes still work
-		\item<2-> Should also account for its distributional effects
-		\item<3-> Greater welfare losses in regions without access to non-intermittent renewables
-		\item<4-> Can turn into an equity--efficiency trade--off
+		\item Carbon taxes and renewable subsidies still work
+		\item Should also account for its distributional effects
+		\item Welfare effects depend on access to non-intermittent renewables
+		\item Keep equity-efficiency trade-off in mind
 	\end{itemize}
@@
 
-\begin{block}{Improving battery technology can make a significant difference}
+\begin{block}{Researching battery technology can make a significant difference}
 	\begin{itemize}
@@
 		\item Reducing the intermittency of renewables greatly increases their substitutability
-		\item Mitigates the distributional side effects of intermittency + carbon taxes
+		\item Mitigates the distributional side effects of intermittency + policy
 		\item Can roughly approximate the effects of batteries in our model by shifting solar output to the off-peak period when it under-produces
@@
 \begin{frame}
-\frametitle{Discussion -- Improving Models}
+\frametitle{Conclusion}
 
-\begin{block}{How can future models of energy generation substitutability be improved?}
 \begin{itemize}
-		\setlength\itemsep{0.5em}
-		\item <1-> Assuming a constant elasticity of substitution between renewables and fossil fuels does not accurately capture intermittency
-		\item <1-> Empirical estimates of the elasticity of substitution may be incorrect since the functional form (CES) does not seem to be appropriate 
-		\item <2-> Directly implementing our model may not allow for analytical tractability
-		\item <2-> Can try the variable elasticity of substitution (VES) form instead\footnote{The VES function was first defined in Revankar (1971).}
+	\setlength\itemsep{1em}
+	\item Welfare effects of carbon taxes and renewable subsidies depend on the intermittency of renewables
+	\item Geographic heterogeneity in intermittency can create a trade-off between efficiently and equitably preventing climate change
+	\item Subsidizing battery research can complement other policies by increasing the substitutability of renewable and fossil energy while mitigating their unintentional distributional consequences 
+	%\item The VES function can do a reasonable job of approximating the substitutability between renewables and fossil fuels
 \end{itemize}
-\end{block}
-\end{frame}
-
-\begin{frame}
-\frametitle{Discussion -- Improving Models}
-
-\begin{block}{\centering VES approximation of the relationship between solar and coal}
-\end{block}
-
-\hspace*{-1.5em}
-\begin{overpic}[width=1.1\textwidth,tics=10]{../code/matlab/simulation_april/fig_ves_approx_x.png} 
-\end{overpic}
 
@@
 \begin{frame}
-\frametitle{Discussion -- Improving Models}
 
-\begin{block}{What exactly is the VES function?}
-	\begin{itemize}
-		\setlength\itemsep{0.5em}
-		\item Assumes that the elasticity of substitution between factors varies as a linear function of their quantities
-		\item Can be empirically estimated
-		\item Simpler to implement in a theoretical or numerical framework than our model
-	\end{itemize}
-	\begin{align*}
-	&Z = \gamma X_1^{\omega(1-\delta \rho)} \left( X_2 + (\rho - 1) X_1 \right)^{\omega \delta \rho} \\
-	&\highlight{e = 1 + \beta (X_1 / X_2)} \\
-	&\,\beta = (\rho - 1) / ( 1- \delta \rho ) 
-	\end{align*}
-	\vspace{-4ex}
-	$$\gamma > 0, \quad \omega > 0, \quad0 < \delta < 1, \quad 0 \leq \delta \rho \leq 1 , \quad (X_2/X_1) >  -\beta $$
+\begin{block}{\centering \large Questions?}
 \end{block}
 
-\end{frame}
-
-\begin{frame}
-\frametitle{Conclusion}
-
-\begin{itemize}
-	\setlength\itemsep{0.75em}
-	\item Welfare effects of carbon taxes and renewable subsidies depend on the intermittency of renewables and thus vary geographically
-	\item Intermittency can create a trade-off between efficiently and equitably preventing climate change
-	\item Subsidizing battery research can complement other policies by increasing the substitutability of renewable and fossil energy while mitigating their unintentional distributional consequences 
-	\item The VES function can do a reasonable job of approximating the substitutability between renewables and fossil fuels
-\end{itemize}
+\blfootnote{Saketh Aleti (saketh.aleti@rutgers.edu), Gal Hochman (gal.hochman@rutgers.edu)}
 
@@
 \begin{frame}
+\frametitle{Appendix -- VES}
+
+\begin{block}{How can future models of energy generation substitutability be improved?}
+	\begin{itemize}
+		\setlength\itemsep{0.5em}
+		\item <1-> Assuming a constant elasticity of substitution between renewables and fossil fuels does not accurately capture intermittency
+		\item <1-> Empirical estimates of the elasticity of substitution may be incorrect since the functional form (CES) does not seem to be appropriate 
+		\item <1-> Directly implementing our model may not allow for analytical tractability
+		\item <2-> Can try the variable elasticity of substitution (VES) form instead\footnote{The VES function was first defined in Revankar (1971).}
+	\end{itemize}
+\end{block}
+\end{frame}
+
+\begin{frame}
+\frametitle{Appendix -- VES}
+
+\begin{block}{\centering VES approximation of the relationship between solar and coal}
+\end{block}
+
+\hspace*{-1.5em}
+\begin{overpic}[width=1.1\textwidth,tics=10]{../code/matlab/simulation_april/fig_ves_approx_x.png} 
+\end{overpic}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Appendix -- VES}
+
+\begin{block}{What exactly is the VES function?}
+\begin{itemize}
+\setlength\itemsep{0.5em}
+\item Assumes that the elasticity of substitution between factors varies as a linear function of their quantities
+\item Can be empirically estimated
+\item Simpler to implement in a theoretical or numerical framework than our model
+\end{itemize}
+\begin{align*}
+&Z = \gamma X_1^{\omega(1-\delta \rho)} \left( X_2 + (\rho - 1) X_1 \right)^{\omega \delta \rho} \\
+&\highlight{e = 1 + \beta (X_1 / X_2)} \\
+&\,\beta = (\rho - 1) / ( 1- \delta \rho ) 
+\end{align*}
+\vspace{-4ex}
+$$\gamma > 0, \quad \omega > 0, \quad0 < \delta < 1, \quad 0 \leq \delta \rho \leq 1 , \quad (X_2/X_1) >  -\beta $$
+\end{block}
+
+\end{frame}
+
+%%%%%%remove
+\begin{frame}
+\frametitle{Appendix -- Literature}
+
+\begin{itemize}
+	\setlength\itemsep{0.2em}
+	\item Some literature approach the problem by numerically optimizing the capacity of intermittent renewables given reliability constraints \footnote{(Musgens \& Neuhoff, 2006), (Neuhoff et al., 2007)}
+	\item Other papers study how intermittent technologies affect the market itself \footnote{(Ambec \& Crampes, 2012), (Chao, 2011), (Borenstein, 2012)}	
+	\item A common top-down approach is to model intermittency through a CES function between different energy technologies \footnote{See Papageorgiou et al.
+(2017) for a survey of the literature taking this approach}
+	%\item Consumers prefer to smooth their electricity consumption\footnote{(Schwarz et al., 2002), (Herriges et al., 1993), (King \& Shatrawka, 2011).}
+	\item Our model is closest to Helm and Mier (2019)
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
 \frametitle{Appendix -- OLS Results}
@@
 \begin{table}[t] \centering 
-	\caption{OLS Regression Results}
-	\label{table:1} 
-	\footnotesize
+	%\label{table:1} 
+	\tiny
 	\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
-		\\[-5ex]\hline  
+		\\[-3ex]\hline  
 		\hline \\[-1.8ex] 
@@
 		$-\ln (P_{t,i} / P_{s,i})$ & 0.937$^{***}$ & 1.075$^{***}$ & 1.098$^{***}$ & 1.074$^{***}$ & 1.263$^{***}$ & 1.305$^{***}$ \\ 
-		& (0.030) & (0.026) & (0.026) & (0.224) & (0.172) & (0.169) \\  [0.9ex]
+		& (0.030) & (0.026) & (0.026) & (0.224) & (0.172) & (0.169) \\
+		%& & & & & & \\ 
+		$\Delta_{t,s}$ &  &  & 0.0005$^{***}$ &  &  & 0.0065$^{*}$ \\ 
+		&  &  & (0.0001) &  &  & (0.0003) \\ 
+		%& & & & & & \\ 
+		CDD$_t$ &  & 1.156$^{***}$ & 1.163$^{***}$ &  & 1.164$^{***}$ & 1.174$^{***}$ \\
+
+		$\quad(\times 1000^{-1})$ &  & (0.017) & (0.017) &  & (0.072) & (0.075) \\ 
+		%& & & & & & \\ 
+		CDD$_s$ &  & $-$1.143$^{***}$ & $-$1.158$^{***}$ &  & $-$1.200$^{***}$ & $-$1.224$^{***}$ \\ 
+		$\quad(\times 1000^{-1})$&  & (0.025) & (0.026) &  & (0.096) & (0.098) \\ 
+		%& & & & & & \\ 
+		HDD$_t$  &  & 0.246$^{***}$ & 0.245$^{***}$ &  & 0.237$^{***}$ & 0.236$^{***}$ \\ 
+		$\quad(\times 1000^{-1})$ &  & (0.007) & (0.007) &  & (0.031) & (0.031) \\ 
+		%& & & & & & \\ 
+		HDD$_s$ &  & $-$0.267$^{***}$ & $-$0.265$^{***}$ &  & $-$0.268$^{***}$ & $-$0.263$^{***}$ \\ 
+		$\quad(\times 1000^{-1})$ &  & (0.008) & (0.008) &  & (0.038) & (0.038) \\ 
+		%& & & & & & \\ 
+		Intercept & 0.028$^{***}$ & 0.012$^{*}$ & 0.026$^{***}$ &  &  &  \\ 
+		& (0.004) & (0.006) & (0.007) &  &  &  \\  [0.9ex]
 		\hline \\[-1.8ex] 
-		Time Control &   &   & Yes &   &   & Yes  \\ 
-		Degree Day Controls &   & Yes  & Yes &   & Yes  & Yes \\ 
 		State FEs &   &   &   & Yes & Yes & Yes \\ 
@@
 \begin{table}[h] \centering 
-	\caption{IV (2SLS) Regression Results}
+	%\caption{IV (2SLS) Regression Results}
 	\label{table:2} 
-	\scriptsize
+	\tiny
 	\begin{tabular}{@{\extracolsep{4pt}}lcccccc} 
-		\\[-6ex]\hline  
+		\\[-4ex]\hline  
 		\hline \\[-1.6ex] 
@@
 		$-\ln (P_{t,i} / P_{s,i})$ &  &  &  & 2.978$^{***}$ & 5.896$^{***}$ & 5.818$^{***}$ \\ 
-		&  &  &  & (0.180) & (0.548) & (0.524) \\   [0.9ex]
+		&  &  &  & (0.180) & (0.548) & (0.524) \\   
+		$\Delta_{t,s}$  &  &  & 0.001$^{***}$ &  &  & 0.003$^{***}$ \\ 
+		&  &  & (0.00004) &  &  & (0.0004) \\ 
+		%& & & & & & \\ 
+		CDD$_t$  &  & 0.100$^{***}$ & 0.105$^{***}$ &  & 1.637$^{***}$ & 1.657$^{***}$ \\ 
+		$\quad(\times 1000^{-1})$ &  & (0.006) & (0.006) &  & (0.068) & (0.067) \\ 
+		%& & & & & & \\ 
+		CDD$_s$ &  & $-$0.096$^{***}$ & $-$0.114$^{***}$ &  & $-$1.688$^{***}$ & $-$1.783$^{***}$ \\ 
+		$\quad(\times 1000^{-1})$  &  & (0.009) & (0.009) &  & (0.079) & (0.084) \\ 
+		%& & & & & & \\ 
+		HDD$_t$  &  & $-$0.048$^{***}$ & $-$0.048$^{***}$ &  & 0.001 & 0.007 \\ 
+		$\quad(\times 1000^{-1})$ &  & (0.003) & (0.003) &  & (0.031) & (0.030) \\ 
+		%& & & & & & \\ 
+		HDD$_s$  &  & 0.053$^{***}$ & 0.055$^{***}$ &  & 0.0001 & 0.007 \\ 
+		$\quad(\times 1000^{-1})$  &  & (0.003) & (0.003) &  & (0.035) & (0.034) \\   [0.9ex]
 		\hline \\[-1.8ex] 
-		Time Control &   &   & Yes &   &   & Yes  \\ 
-		Degree Day Controls &   & Yes  & Yes &   & Yes  & Yes \\ 
 		State FEs &  Yes & Yes  & Yes  & Yes & Yes & Yes \\ 

### 2019-06-13 code/R/workshop_graphs.R
Finalize workshop graphs
- also update gitignore

@@ -72,16 +72,20 @@ ggsave('../../documents/exhibits/rel_renew_map.pdf',
 
 # Ercot data
 
-ggplot(data = ercot_data) +
+ercot_plot <- ggplot(data = ercot_data) +
     geom_line(aes(x = Hour, y = Load, color = 'Load'), size = 1) +
     geom_line(aes(x = Hour, y = SolarGen*50, color = 'SolarGen'), size = 1) +
-    scale_y_continuous(expand = c(0, 100),
-        sec.axis = sec_axis(~./50, name = "Solar Generation (MW)")) +
-    scale_colour_manual(values = c("blue", "orange")) +
+    ylab('Load (MW)\n') +
+    scale_y_continuous(expand = c(0.01,0),
+        sec.axis = sec_axis(~./50, name = "Solar Generation (MW)\n"),
+        breaks = c(0,500,1000,1500)*50) +
+    scale_x_continuous(breaks = seq(0,25,2)) +
+    scale_colour_manual(values = c("#23373B", "#EB811B")) +
     expand_limits(x = 0, y = 0) +
+    labs(title = 'ERCOT Hourly Load and Solar Generation (6/1/2019)') +
     theme(legend.box = "vertical", legend.key.size = unit(0.5, "cm"),
           legend.key.width = unit(2, "cm"), legend.title = element_blank(),
-          legend.direction = "horizontal", legend.position = "bottom",
+          legend.direction = "vertical", legend.position = c(0.15, 0.9),
           legend.margin = margin(-0.25,0,0,0, unit="cm"),
           legend.background = element_rect(fill = '#FAFAFA', color = '#FAFAFA'),
           panel.background = element_rect(fill = '#FAFAFA', color = '#FAFAFA'),
@@ -90,6 +94,9 @@ ggplot(data = ercot_data) +
           axis.line.y.left = element_line(size = 0.5, colour = "grey50"),
           panel.grid.major = element_line(color = 'grey90'))
 
+print(ercot_plot)
+ggsave('../../documents/exhibits/ercot_load.pdf',
+       width = plot_width*1.25, height = plot_height*0.9, dpi = 600)
 
 
 

### 2019-06-18 documents/draft.tex
Update notebooks and draft

@@
 We collect monthly data from the \cite{EIANetgen} on retail electricity prices and consumption for each state in the US from 2011 to 2018.
-Additionally, also from the EIA, we obtain data on the average cost of coal for electricity generation for each state and month.\footnote{ The coal price data set contains a large number of missing values due to privacy concerns; however, we do not expect that these missing values are correlated with the data itself.} We deflated both electricity and coal prices over time using the PCECP Index provided by the  \cite{USBEA}.
+Additionally, also from the EIA, we obtain data on the average cost of coal for electricity generation for each state and month.\footnote{ The coal price data set contains a large number of missing values due to privacy concerns; however, we do not expect that these missing values are correlated with the data itself.} We deflated both electricity and coal prices over time using the PCEP Index provided by the  \cite{USBEA}.
 Finally, we collect data on HDDs and CDDs from the NOAA's \citet{CPC} for the same panel.
@@
 		\multicolumn{7}{@{}p{41.4em}@{}}{\textit{Note: } The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
-The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state; as discussed in the Data section, we take a random sample of 9000 observations from the data.
+The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state.
 The coefficient on $-\ln (P_{t,i} / P_{s,i})$ is the estimate of $\sigma$.
@@
 The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
-The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state; as discussed in the Data section, we take a random sample of 9000 observations from the data.
+The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state.
 The coefficient on $\ln (P_{t,i} / P_{s,i})$ is an estimate of $-\sigma$.
@@
 The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
-The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state; as discussed in the Data section, we take a random sample of 9000 observations from the data.
+The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state.
 The estimation procedure is described in the appendix.
@@
 
-	\bibitem[Newey(2007)]{Newey}
+	\bibitem[Newey(1990)]{Newey}
 	Newey, W. (1990). Efficient Instrumental Variables Estimation of Non-linear Models. Econometrica, 58(4), 809–837. https://doi.org/10.2307/2938351

### 2019-06-19 analysis/bioenergy/biomass_prod_graphs.R
Remove old analysis code

@@ -1,155 +1,0 @@
-library(tidyverse)
-library(readxl)
-library(ggplot2)
-library(ggmap)
-library(maps)
-library(mapdata)
-library(tools)
-
-setwd('C:/Users/saket/GitHub/BECCS-Case-Study/analysis/bioenergy/')
-fig_folder <- '../../documents/exhibits/bioenergy/'
-
-# import state map
-map_data <- map_data("county")
-
-# import bioenergy data
-bioenergy_data <- read_csv('../../data/bioenergy/bioenergy_county_clean.csv')
-fsprod_county_data <- read_csv('../../data/bioenergy/bioenergy_county_avgprod.csv')
-
-# clean data
-bioenergy_data <- filter(bioenergy_data, Year == 2016)
-#bioenergy_data$ResourceType <- bioenergy_data$ResourceType
-
-# get average production of each feedstock by state
-fsprod_county_data <- bioenergy_data %>%
-    group_by(State, County, ResourceType, Feedstock) %>%
-    summarize(Production = mean(Production)) %>%
-    ungroup
-
-
-## This merged data does not plot well!
-
-# merge map and bioenergy data
-fsprod_county_data$Feedstock <- toTitleCase(fsprod_county_data$Feedstock)
-fsprod_county_data$state <- tolower(fsprod_county_data$State)
-fsprod_county_data$subregion <- fsprod_county_data$County
-map_data$state           <- tolower(map_data$region)
-merged_fs_data <- full_join(map_data, fsprod_county_data,
-                        by = c('state', 'subregion')) %>%
-                  filter(is.na(Feedstock) == FALSE)
-
-# get total resource type production
-rtprod_county_data <- fsprod_county_data %>%
-    group_by(State, County, ResourceType) %>%
-    summarize(Production = sum(Production, na.rm = TRUE)) %>%
-    ungroup
-rtprod_county_data$state <- tolower(rtprod_county_data$State)
-rtprod_county_data$subregion <- rtprod_county_data$County
-merged_rt_data <- full_join(map_data, rtprod_county_data,
-                        by = c('state', 'subregion')) %>%
-                  filter(is.na(ResourceType) == FALSE)
-
-# get total production of every feedstock
-totprod_county_data <- fsprod_county_data %>%
-    group_by(State, County) %>%
-    summarize(Production = sum(Production, na.rm = TRUE)) %>%
-    ungroup
-totprod_county_data$state <- tolower(totprod_county_data$State)
[…]

### 2019-06-19 analysis/ces_regressions.R

@@ -1,162 +1,0 @@
-library(tidyverse)
-library(ggplot2)
-library(AER)
-library(stargazer)
-library(commarobust)
-library(ivpack)
-library(sandwich)
-library(plm)
-
-## Import DAta
-
-# Set working directory to script location
-setwd(dirname(rstudioapi::getSourceEditorContext()$path))
-reg_data <- read_csv('../data/processed/ces_monthly.csv')
-reg_data$state <- factor(reg_data$state_1)
-
-# Adjust degree day scale
-reg_data$CDD_1 = reg_data$CDD_1/1000
-reg_data$CDD_2 = reg_data$CDD_2/1000
-reg_data$HDD_1 = reg_data$HDD_1/1000
-reg_data$HDD_2 = reg_data$HDD_2/1000
-
-## Linear Models
-
-# Regressions
-
-reg_lm_1   = lm(paste0('ln_load_rel ~ ln_price_rel'),
-                data = reg_data)
-
-reg_lm_2   = lm(paste0('ln_load_rel ~ (CDD_1)',
-                       ' + (CDD_2) + (HDD_1) + (HDD_2)',
-                       ' + ln_price_rel'),
-                data = reg_data)
-
-reg_lm_3   = lm(paste0('ln_load_rel ~ time_diff + (CDD_1)',
-                       ' + (CDD_2) + (HDD_1) + (HDD_2)',
-                       ' + ln_price_rel'),
-                data = reg_data)
-
-reg_plm_1  = plm(as.formula(paste0('ln_load_rel ~ ln_price_rel')),
-                 index = 'state', model = 'within', data = reg_data)
-
-reg_plm_2  = plm(as.formula(paste0('ln_load_rel ~ ln_price_rel + (CDD_1)',
-                                   ' + (CDD_2) + (HDD_1) + (HDD_2)')),
-                 index = 'state', model = 'within', data = reg_data)
-
-reg_plm_3  = plm(as.formula(paste0('ln_load_rel ~ ln_price_rel + (CDD_1)',
-                                   ' + (CDD_2) + (HDD_1)',
-                                   ' + (HDD_2) + time_diff')),
-                 index = 'state', model = 'within', data = reg_data)
-
-# Stargazer
-
-fits       = list(reg_lm_1, reg_lm_2, reg_lm_3,
-                  reg_plm_1, reg_plm_2, reg_plm_3)
-
[…]

### 2019-06-19 analysis/cge/cge_graphs.R

@@ -1,251 +1,0 @@
-library(tidyverse)
-library(plyr)
-library(gdxrrw)
-library(ggplot2)
-library(scales)
-library(ggthemes)
-
-setwd('C:/Users/saket/GitHub/BECCS-Case-Study/analysis/cge')
-
-# Paths
-igdx(gamsSysDir = "C:/GAMS/win64/25.1")
-data_loc <- '../../data/cge/results_ne.gdx'
-
-# Folder to put graphs
-fig_folder <- '../../documents/exhibits/cge/ne/'
-
-# Params
-fig_scale  <- 1.1
-fig_width  <- 7
-fig_height <- 5
-
-#--------------
-## Load Data
-
-# Data
-data_Zpz    <- rgdx.param(data_loc, 'Res_Zpz')
-data_Z      <- rgdx.param(data_loc, 'Res_Z')
-data_pz     <- rgdx.param(data_loc, 'Res_pz')
-data_co2    <- rgdx.param(data_loc, 'Res_co2')
-data_tax    <- rgdx.param(data_loc, 'Res_tax')
-data_ler    <- rgdx.param(data_loc, 'L_mult')
-data_co2_rt <- rgdx.param(data_loc, 'co2_tax_rt')
-
-
-#--------------
-## Data Clean up
-
-# Merge some data
-data_merged <- merge(data_tax, data_Zpz, on = c('i', 't'))
-data_merged <- merge(data_merged, data_pz, on = c('i', 't'))
-data_merged <- merge(data_merged, data_Z, on = c('i', 't'))
-data_merged <- merge(data_merged, data_co2, on = c('i', 't'))
-
-# Clean column names
-data_merged$i <- mapvalues(data_merged$i,
-          from = c('ELC_BECCS', 'ELC_FF', 'ELC_RNW'),
-          to = c('BECCS', 'Fossil Fuels', 'Renewables'))
-
-data_merged$tax_revenue <- data_merged$Res_tax * data_merged$Res_Zpz
-
-data_merged <- ddply(data_merged, .(i, t))
-
-data_merged <- ddply(data_merged, .(i), transform,
-                     tax_rev_chg = (tax_revenue - tax_revenue[1]),
-                     tax_rev_chg_rel = (tax_revenue/tax_revenue[1]) - 1,
-                     zpz_pct_chg = Res_Zpz/Res_Zpz[1] - 1,
-                     zpz_chg = Res_Zpz - Res_Zpz[1]
[…]

### 2019-06-19 code/python/balance_sam.py
Remove old cge code

@@ -1,251 +1,0 @@
-import pandas as pd
-import os
-import numpy as np
-from scipy import optimize
-
-### Functions
-
-def RAS_step(row_totals, col_totals, seed_values, zero_cutoff = 1e-3):
-
-        # Initial conditions
-        assert type(row_totals)  == np.ndarray
-        assert type(col_totals)  == np.ndarray
-        assert sum(row_totals)   == sum(col_totals)
-
-        # Initialize the matrix
-        matrix = seed_values.copy()
-        assert type(matrix)    == np.ndarray
-        assert matrix.shape[0] == len(row_totals)
-        assert matrix.shape[1] == len(col_totals)
-        
-        # Row update
-        row_scalars = matrix.sum(axis=1) / row_totals
-        matrix = (matrix.T / row_scalars).T
-
-        # Column update
-        col_scalars = matrix.sum(axis=0) / col_totals
-        matrix = (matrix / col_scalars)
-
-        # Return
-        return matrix
-
-def vec_to_sam(B):
-    
-    n = len(sam_mat)
-    sam_B = np.zeros((n,n))
-    sam_B[sam_mat != 0] = B
-    
-    return np.matrix(sam_B)
-
-def kl_divergence(B):
-    
-    mat_a = sam_mat.copy()
-    mat_b = vec_to_sam(B)
-    
-    # Divide matrices where we don't have zeros
-    mat_div = np.divide(mat_b, mat_a, where = ((mat_a*100).astype(int) != 0))
-    
-    # Replace 0's with 1's which will become 0's when logged
-    mat_div[np.where((mat_a*100).astype(int) == 0)] = 1
-    mat_div[mat_div == 0] = 1
-    
-    return np.power(np.sum(np.multiply(mat_b, np.log(mat_div))), 2)
-
-def row_col_constraint(B):    
-    
-    sam = vec_to_sam(B)
-    
-    # Row and column totals
-    totals_0 = np.sum(sam, axis = 0).T
-    totals_1 = np.sum(sam, axis = 1)
-    
-    # Divide sums where we don't have zeros
-    sum_div = np.divide(totals_0, totals_1, where = totals_0 != 0)
-    
-    # Replace 0's with 1's
-    sum_div[np.where((sum_div*100).astype(int) == 0)] = 1
-    sum_div[sum_div == 0] = 1
-    
-    # Find total squared deviation from equality    
[…]

### 2019-06-19 code/python/construct_state_sams.py

@@ -1,325 +1,0 @@
-import pandas as pd
-import numpy as np
-import os
-
-
-### Functions
-
-def agg_beccs(index):
-    
-    index = int(index)
-    
-    if   index in range(1,11):
-        return 'AGR_CRP'
-    elif index in range(11,15):
-        return 'AGR_LIV'
-    elif (index in range(17,19) or (index in range(20,41)) or 
-         (index in range(50,146)) or (index in range(154,395))):
-        return 'MAN'
-    elif index in range(395,518):
-        return 'SER'
-    elif index == 49:
-        return 'ELC_DIST'
-    elif index == 48:
-        return 'ELC_OTHER'
-    elif index == 42:
-        return 'ELC_FF'
-    elif index == 41:
-        return 'ELC_HYDRO'
-    elif index == 43:
-        return 'ELC_NUC'
-    elif index == 44:
-        return 'ELC_SOLAR'
-    elif index == 45:
-        return 'ELC_WIND'
-    elif index == 46:
-        return 'ELC_GEO'
-    elif index == 47:
-        return 'ELC_BIOMASS'
-    elif index in [15,16,19]:
-        return 'FORE'
-    elif index in range(146,154):
-        return 'PAP'
-    elif index in range(518,521):
-        return 'GOV_FED_ENT'
-    elif index in range(521,527):
-        return 'GOV_STT_ENT'
-    elif index in [535, 536]:
-        return 'GOV_FED_EMP'
-    elif index in range(531, 535):
-        return 'GOV_STT_EMP'
-    elif index in range(527, 531):
-        return 'NonIndustry'
-    elif index == 5001:
-        return 'LAB'
-    elif index == 6001:
-        return 'PROF'
-    elif index == 7001:
-        return 'PROP'
-    elif index == 8001:
-        return 'TAX'
-    elif index in range(10000,11000):
-        return 'HOH'
-    elif index in range(11000,12000):
-        return 'GOV_FED'
-    elif index in range(12000,13000):
-        return 'GOV_STT'
-    elif index == 13001:
-        return 'CORP'
-    elif index in [14001, 14002]:
-        return 'CAP'
-    elif index in [25001, 28001]:
-        return 'TRD'
-    else:
[…]

### 2019-06-19 code/shell/run_cge_ne.sh

@@ -1,6 +1,0 @@
-scp ../model/stdcge_beccs_ne.gms TheWorkers@172.19.138.112:Documents/Saketh
-ssh TheWorkers@172.19.138.112 '
-export PATH=$PATH:"/Applications/GAMS25.1/GAMS Terminal.app/../sysdir" && cd ~/Documents/Saketh
-gams stdcge_beccs_ne.gms'
-scp TheWorkers@172.19.138.112:Documents/Saketh/stdcge_beccs_ne.lst ../model/stdcge_beccs_ne.lst 
-scp TheWorkers@172.19.138.112:Documents/Saketh/results.gdx ../../data/cge/results_ne.gdx 

### 2019-06-19 code/shell/run_cge_pgm.sh

@@ -1,6 +1,0 @@
-scp ../model/stdcge_beccs_pgm.gms TheWorkers@172.19.138.112:Documents/Saketh
-ssh TheWorkers@172.19.138.112 '
-export PATH=$PATH:"/Applications/GAMS25.1/GAMS Terminal.app/../sysdir" && cd ~/Documents/Saketh
-gams stdcge_beccs_pgm.gms'
-scp TheWorkers@172.19.138.112:Documents/Saketh/stdcge_beccs_pgm.lst ../model/stdcge_beccs_pgm.lst 
-scp TheWorkers@172.19.138.112:Documents/Saketh/results.gdx ../../data/cge/results_pgm.gdx 

### 2019-06-19 code/simulation/sim_adoption_curve.m
Update simulation code
- change figure output location
- rename workshop figures
- rename workshop scripts

@@ -93,7 +93,7 @@ legend('Location', 'southwest')
 title(hleg, '\sigma')
 
 % Save figure
-%print(gcf,'fig_adoption_c2.png','-dpng','-r300')
+%print(gcf,'../../figures/fig_adoption_c2.png','-dpng','-r300')
 
 
 %% Adoption with Respect to Price of Solar Sim
@@ -182,5 +182,5 @@ ylim([0 100])
 grid('on')
 
 % Save figure
-print(gcf,'fig_adoption_c1.png','-dpng','-r300')
+print(gcf,'../../figures/fig_adoption.png','-dpng','-r300')
 

### 2019-06-19 code/simulation/sim_batteries.m

@@ -108,5 +108,5 @@ ylim([0 25])
 grid('on')
 
 % Save figure
-print(gcf,'fig_batteries.png','-dpng','-r300')
+print(gcf,'../../figures/fig_batteries.png','-dpng','-r300')
 

### 2019-06-19 code/simulation/sim_batteries_workshop.m

@@ -114,5 +114,5 @@ set(gcf,'units','points','position',[100,100,1600,700]/2)
 set(gca,'color','none')
 set(gcf, 'InvertHardcopy', 'off')
 set(gcf,'color', [250 250 250]/255);
-print(gcf,'fig_batteries_x.png','-dpng','-r500')
+print(gcf,'../../figures/fig_batteries_workshop.png','-dpng','-r500')
 

### 2019-06-19 code/simulation/sim_elasticity.m

@@ -104,5 +104,5 @@ legend('Location', 'southwest')
 title(hleg, '\sigma')
 
 % Save figure
-print(gcf,'fig_coal_elas.png','-dpng','-r300')
+print(gcf,'../../figures/fig_coal_elas.png','-dpng','-r300')
 

### 2019-06-19 code/simulation/sim_elasticity_workshop.m

@@ -1,10 +1,10 @@
-%% Elasticity of Substitution Sim with error bars on sigma estimate
+%% Adoption with Respect to Price of Solar Sim
 
 close all; clear; clc;
 
 % Simulation params
-n = 5000;
-cost_multiplier = linspace(0.5,3,n);
+n = 500;
+cost_multiplier = linspace(1, 1.6, n);
 sigma_range = [0.8847 + 1.96*0.044, 0.8847, 0.8847 - 1.96*0.044];
 m = length(sigma_range);
 
@@ -17,7 +17,7 @@ xi_2  = [1, 0.1];
 budget = 1;
 
 
-figure('Renderer', 'painters', 'Position', [100 100 900 600])
+%figure('Renderer', 'painters', 'Position', [100 100 900 400])
 hold on;
 
 for j = 1:m
@@ -49,7 +49,7 @@ for j = 1:m
         
         % Quantities
         Y = ((alpha'./prices).^(sigma)) * (budget/P);
-           
+          
         X = (xi_mat')\Y;
 
         results(i,:) = X';
@@ -57,27 +57,29 @@ for j = 1:m
     end    
 
     output = [];
-    output(1,:) = c_1*cost_multiplier'./c_2;
-    output(2,:) = results(:,1)./results(:,2);
-
-    % subset to positive quantities
-    ind = ~any(output <= 0);
-    output = output(:,ind);
+    output(1,:) = results(:,1);
+    output(2,:) = results(:,2);
+    output(3,:) = cost_multiplier-1;
+    output(4,:) = c_1*cost_multiplier;
     
-    % relationship between e and log quantities
+    % subset to positive quantities
+    ind = ~any(output(1:2,:) <= 0);
+    output = output(:,ind);
+
+    % elasticity of coal versus price
     hold on;
     
     if sigma == 0.8847
-        plot(log(output(2,2:end)), ...
-            diff(log(output(2,:)))./diff(-log(output(1,:))), ...
+        plot(output(3,2:end)*100, ...
+            diff(log(output(1,:)))./diff(log(output(4,:))), ...
             'LineWidth', 1, 'Color', [207, 74, 48]/255);
 %     elseif sigma < 0.8846
-%         plot(log(output(2,2:end)), ...
-%             diff(log(output(2,:)))./diff(-log(output(1,:))), ...
+%         plot(output(3,2:end)*100, ...
[…]

### 2019-06-19 code/simulation/sim_eos.m

@@ -127,5 +127,5 @@ ylim([0 15])
 grid('on')
 
 % Save figure
-print(gcf,'fig_elasticity.png','-dpng','-r300')
+print(gcf,'../../figures/fig_elasticity.png','-dpng','-r300')
 

### 2019-06-19 code/simulation/sim_eos_range.m

@@ -109,5 +109,5 @@ grid('on')
 %legend([e_1_line], ' e = 1');
 
 % Save figure
-print(gcf,'fig_elasticity_range.png','-dpng','-r300')
+print(gcf,'../../figures/fig_elasticity_range.png','-dpng','-r300')
 

### 2019-06-19 code/simulation/sim_eos_workshop.m

@@ -1,10 +1,10 @@
-%% Adoption with Respect to Price of Solar Sim
+%% Elasticity of Substitution Sim with error bars on sigma estimate
 
 close all; clear; clc;
 
 % Simulation params
-n = 500;
-cost_multiplier = linspace(1, 1.6, n);
+n = 5000;
+cost_multiplier = linspace(0.5,3,n);
 sigma_range = [0.8847 + 1.96*0.044, 0.8847, 0.8847 - 1.96*0.044];
 m = length(sigma_range);
 
@@ -17,7 +17,7 @@ xi_2  = [1, 0.1];
 budget = 1;
 
 
-%figure('Renderer', 'painters', 'Position', [100 100 900 400])
+figure('Renderer', 'painters', 'Position', [100 100 900 600])
 hold on;
 
 for j = 1:m
@@ -49,7 +49,7 @@ for j = 1:m
         
         % Quantities
         Y = ((alpha'./prices).^(sigma)) * (budget/P);
-          
+           
         X = (xi_mat')\Y;
 
         results(i,:) = X';
@@ -57,29 +57,27 @@ for j = 1:m
     end    
 
     output = [];
-    output(1,:) = results(:,1);
-    output(2,:) = results(:,2);
-    output(3,:) = cost_multiplier-1;
-    output(4,:) = c_1*cost_multiplier;
-    
-    % subset to positive quantities
-    ind = ~any(output(1:2,:) <= 0);
-    output = output(:,ind);
+    output(1,:) = c_1*cost_multiplier'./c_2;
+    output(2,:) = results(:,1)./results(:,2);
 
-    % elasticity of coal versus price
+    % subset to positive quantities
+    ind = ~any(output <= 0);
+    output = output(:,ind);
+    
+    % relationship between e and log quantities
     hold on;
     
     if sigma == 0.8847
-        plot(output(3,2:end)*100, ...
-            diff(log(output(1,:)))./diff(log(output(4,:))), ...
+        plot(log(output(2,2:end)), ...
+            diff(log(output(2,:)))./diff(-log(output(1,:))), ...
             'LineWidth', 1, 'Color', [207, 74, 48]/255);
 %     elseif sigma < 0.8846
-%         plot(output(3,2:end)*100, ...
-%             diff(log(output(1,:)))./diff(log(output(4,:))), ...
+%         plot(log(output(2,2:end)), ...
[…]

### 2019-06-19 code/simulation/sim_tax_subsidy.m

@@ -172,6 +172,6 @@ xlim([0, 200])
 grid('on')
 
 % Save figure
-print(gcf,'fig_tax_subsidy.png','-dpng','-r300')
+print(gcf,'../../figures/fig_tax_subsidy.png','-dpng','-r300')
 
 

### 2019-06-19 code/simulation/sim_ves.m

@@ -132,5 +132,5 @@ grid('on')
 legend('Location', 'northwest')
 
 % Save figure
-print(gcf,'fig_ves_approx.png','-dpng','-r300')
+print(gcf,'../../figures/fig_ves_approx.png','-dpng','-r300')
 

### 2019-06-19 code/simulation/sim_ves_int.m

@@ -119,5 +119,5 @@ grid('on')
 legend('Location', 'northwest')
 
 % Save figure
-print(gcf,'fig_ves_approx_int.png','-dpng','-r300')
+print(gcf,'../../figures/fig_ves_approx_int.png','-dpng','-r300')
 

### 2019-06-19 code/simulation/sim_ves_workshop.m

@@ -138,5 +138,5 @@ set(gcf,'units','points','position',[100,100,1600,700]/2)
 set(gca,'color','none')
 set(gcf, 'InvertHardcopy', 'off')
 set(gcf,'color', [250 250 250]/255);
-print(gcf,'fig_ves_approx_x.png','-dpng','-r600')
+print(gcf,'../../figures/fig_ves_approx_workshop.png','-dpng','-r600')
 

### 2019-06-19 documents/draft.tex
Update draft
- draft now correctly references new figures' location

@@
 % images
-\graphicspath{ {D:/Users/saketh/Documents/GitHub/BECCS-Case-Study/documents/exhibits/} }
+%\graphicspath{ {D:/Users/saketh/Documents/GitHub/Energy-Intermittency-Paper/figures/} }
 
@@
 \captionsetup[table]{
+	font = {sc},
+	labelfont = {bf}
+}
+
+% caption set up
+\captionsetup[figure]{
 	font = {sc},
@@
 
+	\begin{table}[t] \centering 
+		\caption{Descriptive Statistics}
+		\label{table:stats} 
+		\begin{tabular}{@{\extracolsep{0pt}}lrrrrrrr@{}}
+			\\[-4ex]\hline  
+			\hline \\[-1.8ex] 
+			{} &     Mean &      StDev  &     Min &     25\% &      50\% &      75\% &       Max \\
+			\midrule
+			Electricity Price (\$/kWh)     &     0.12 &     0.03 &    0.08 &    0.10 &     0.11 &     0.13 &      0.21 \\
+			Electricity Load (GwH) & 2454.97 &  2380.24 &  144.00 &  790.50 &  1869.50 &  3315.00 &  18621.00 \\
+			Coal Price (\$/ton) &    46.00 &    17.68 &   24.04 &   33.43 &    41.40 &    51.83 &    107.49 \\
+			Cooling Degree Days      &    64.66 &   134.97 &    0.00 &    0.00 &     0.00 &    47.25 &    761.00 \\
+			Heating Degree Days       &   443.20 &   412.27 &    0.00 &   48.00 &   367.00 &   754.50 &   1794.00 \\ [0.5ex]
+			\hline 
+			\hline \\[-1.8ex] 
+			\multicolumn{8}{@{}p{41.5em}@{}}{\textit{Note: } The underlying data covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable.
+Each observation corresponds to a particular year, month, and state.
+}  \\
+		\end{tabular}
+	\end{table}
+
 	\section{Results}
@@
 		\caption{OLS Regression Results}
-	\label{table:1} 
+		\label{table:ols} 
 		\small
@@
 
-Based on the OLS results reported in \hyperref[table:1]{Table 1}, we estimate the intertemporal elasticity of substitution for electricity consumption $\hat{\sigma}  = 1.305$ ($|t| > 24$) when accounting for all degree day covariates and state fixed effects.
+	Based on the OLS results reported in \autoref{table:ols} we estimate the intertemporal elasticity of substitution for electricity consumption $\hat{\sigma}  = 1.305$ ($|t| > 24$) when accounting for all degree day covariates and state fixed effects.
 Additionally, we find that accounting for cooling and heating degree days captures a large amount of variation in demand for electricity; in the fixed effects regressions, adding these controls raises adjusted $R^2$ from 8.5\% to 51.8\%.
@@
 
-To account for endogeneity in the OLS results, we provide results for our IV specification in \hyperref[table:2]{Table 2}.
+	To account for endogeneity in the OLS results, we provide results for our IV specification in \autoref{table:iv}.
 Here, we find a much larger estimate of $\hat{\sigma}  = 5.818$ ($|t| > 11.1$) when considering all covariates and fixed effects.
@@
 
-Finally, we control for nonlinear effects using a partially linear IV regression reported in \hyperref[table:3]{Table 3}.
+	Finally, we control for nonlinear effects using a partially linear IV regression reported in \autoref{table:pariv}.
 Here, we find much smaller results than 2SLS when controlling for all possible covariates.
@@
 
-\begin{table}[h] \centering 
-	\vspace{-2em}
+	\begin{table}[h] 
+		\centering 
 		\caption{IV (2SLS) Regression Results}
-	\label{table:2} 
+		\label{table:iv} 
 		\small
@@
 		\end{tabular} 
-	%\end{table}
-	\\[4ex]
-
-	%\begin{table}[!t] \centering 
+	\end{table}
+
+	\begin{table}[!t] 
+		\centering 
 		\caption{Partially Linear IV Regression Results}
-	\label{table:3} 
+		\label{table:pariv} 
 		\small
@@
 
-\begin{table}[t]
-	\caption*{\textbf{Figure 1:} The Elasticity of Substition between Solar and Coal} 
+	\begin{figure}[t]
+		\caption{The Elasticity of Substitution between Solar and Coal} 
 		\label{fig:eosnum}
@@
 		\begin{tabular}{@{\extracolsep{0em}}c}
-		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_elasticity} \\
+			\includegraphics[width=1\linewidth]{../figures/fig_elasticity} \\
 			\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } Technology 1 is coal and technology 2 is solar.
@@
 		\end{tabular}
-\end{table}
-
-We plot our numerical estimates of $e_{1, 2}$, the elasticity of substitution between solar and coal power, in \hyperref[fig:eosnum]{Figure 1}.
+	\end{figure}
+
+	We plot our numerical estimates of $e_{1, 2}$, the elasticity of substitution between solar and coal power, in \autoref{fig:eosnum}.
 We generated these results by computing the optimal quantities of each technology given a range of relative prices $c_2/c_1$.
@@
 
-The first relationship we see in \hyperref[fig:eosnum]{Figure 1} is that $e_{1,2}$ varies non-linearly with the relative costs of each technology; in particular, it appears to take on a hockey stick shape.
+	The first relationship we see in \autoref{fig:eosnum} is that $e_{1,2}$ varies non-linearly with the relative costs of each technology; in particular, it appears to take on a hockey stick shape.
 This shape is a result of both intermittency and costs.
@@
 That is, we again consider a two-period, two-technology example, but assume that $\xi_1$ and $\xi_2$ are nearly constant over time.
-We plot our results in \hyperref[fig:eosrange]{Figure B.1} and find that the elasticity of substitution takes on a u-shape.
+We plot our results in \autoref{fig:eosrange} and find that the elasticity of substitution takes on a u-shape.
 } That is, $e_{1,2}$ rises when the relative prices of solar and coal are very different.
 When these two effects interact, we see the elasticity of substitution between solar and coal takes on a hockey stick shape.
-
-% Middle of paragraph (hard to understand?)
-% To understand why, let us consider three cases.
-For the first case, suppose coal is relatively far cheaper than solar ($\log(c_2/c_1)$ is large).
-This suggests producers will primarily employ coal for electricity.
-Because the output of coal does not vary with time, we will have a constant amount of electricity through the day.
-Consequently, the intermittency will not matter much on the margin since generation is already quite consistent.
-Instead, the cost of a competing generation technology will play a much bigger role.
-Consequently, solar and coal will be strong substitutes; this explains why $e_{1,2}$ is much larger when $\log(c_2/c_1)$ is large.
-On the other hand, for the second case, suppose that the price of solar and coal are such that we use about an equal amount of both.
-This corresponds to the point where $\log(c_2/c_1)  = -0.7$ in the \hyperref[fig:eosnum]{Figure 1}.
-In this case, output will not be constant through the day, since a large portion of electricity is coming from solar.
-As a result, consumers will care about intermittency on the margin; so, the  intermittency effect will matters in this case and will impede the adoption of solar.
-As a result, coal and solar will be relatively weaker substitutes; thus, we see $e_{1,2}$ is relatively lower when relative prices are not at extrema.
-Finally, consider the third case where solar is relatively much cheaper than coal.
-In this case, the quantity of solar is much larger than that of coal; this causes overall electricity output to be very intermittent.
-So, again, the intermittency effect matters.
-However, since the cost of each technology differs greatly, small changes in price could cause large changes in quantity.
-Accounting for both these factors, we see a moderately large elasticity of substitution $e_{1,2}$ when $\log(c_2/c_1)$ is small.
 
@@
 Consequently, this implies that the elasticity of substitution $e_{1, 2}$ will be larger.
-Hence, in the lower subplot of \hyperref[fig:eosnum]{Figure 1}, we see that $e_{1, 2}$ rises with $\sigma$ when holding the  relative prices of each technology constant.
+Hence, in the lower subplot of \autoref{fig:eosnum}, we see that $e_{1, 2}$ rises with $\sigma$ when holding the  relative prices of each technology constant.
 Secondly, we find that $e_{1,2}$ becomes more u-shaped as $\sigma$ rises.
@@
 As argued earlier, when costs differ greatly between technologies, the elasticity of substitution $e_{1,2}$ is higher.
-
-%Additionally, note that we assumed earlier that the estimates of $\sigma$ on a monthly basis would be fairly close to those on a daily or hourly basis.
-But, our results showed estimates of $\hat{\sigma} \approx 0.5$ which differs from the literatures' estimates which fall between $0.01$ and $0.25$.
-Does this impact our numerical results?
-Alternatively, if our estimates were closer to past estimates, would there be significantly different economic implications?
-Based on our numerical model, the answer seems to be no.
-That is, the relationship between $e$ and $\log(c_2/c_1)$ in \hyperref[fig:eosnum]{Figure 1} does not significantly differ when varying $\sigma$ in $\{0.05, 0.25, 0.5\}$.
-Hence, even if our assumption is incorrect or past estimates are biased, our model's results do not significantly differ within this range of estimates for $\sigma$.
-
-%\footnote{ Recall that $\sigma < 1$ implies that  electricity consumption in different periods are complements, $\sigma = 1$ implies to a Cobb-Douglas relationship, and $\sigma > 1$ implies that electricity consumption in different periods are substitutes.}
 
@@
 
-\begin{table}[!t]
-	\caption*{\textbf{Figure 2:} The Price Elasticity of Demand for Coal Power} 
+	\begin{figure}[!t]
+		\caption{The Price Elasticity of Demand for Coal Power} 
 		\label{fig:coalelas}
@@
 		\begin{tabular}{@{\extracolsep{0em}}c}
-		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_coal_elas} \\
+			\includegraphics[width=1\linewidth]{../figures/fig_coal_elas} \\
 			\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$, $\sigma = 0.5$.
@@
 		\end{tabular}
-\end{table}
+	\end{figure}
 
@@
 Specifically, the elasticity of demand for non-intermittent energy increases then decreases with respect to its own price.
-Using the earlier numerical example of solar and coal power, we show this explicitly in \hyperref[fig:coalelas]{Figure 2}.
+Using the earlier numerical example of solar and coal power, we show this explicitly in \autoref{fig:coalelas}.
 As the price of coal power rises significantly beyond its current price, demand gets more elastic because its price becomes the primary factor disincentivizing its use.
@@
 
-\begin{table}[t]
+	\begin{figure}[t]
 		\captionsetup{format=centerproper}
-	\caption*{\textbf{Figure 3:} The Effect of Battery Storage on the Elasticity\newline of Substitution between Solar and Coal} 
+		\caption{The Effect of Battery Storage on the Elasticity\newline of Substitution between Solar and Coal} 
 		\label{fig:battery}
@@
 		\begin{tabular}{@{\extracolsep{0em}}c}
-		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_batteries} \\
+			\includegraphics[width=1\linewidth]{../figures/fig_batteries} \\
 			\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } Technology 1 is coal and technology 2 is solar.
@@
 Furthermore, we set the parameter for the intertemporal elasticity of substitution for electricity consumption equal to our estimate $\hat{\sigma} = 0.8847$.
-We generated these numerical results with the same procedure used for \hyperref[fig:eosnum]{Figure 1}.
+We generated these numerical results with the same procedure used for \autoref{fig:eosnum}.
 We repeated this procedure with $\xi_2 = (0.95, 0.15)$ and $\xi_2 = (0.90, 0.20)$ to simulate the effects of shifting solar power output using batteries.
@@
 So, we represent solar output with batteries using $\xi_2 = (0.95, 0.15)$ and $\xi_2 = (0.90, 0.20)$; this is equivalent to transferring 5\% and 10\% of solar output.
-We plot our results in \hyperref[fig:battery]{Figure 3}.
+We plot our results in \autoref{fig:battery}.
 It is immediately clear that making solar output more consistent through the day results in a large increase in the elasticity of substitution $e_{1,2}$.
@@
 		\captionsetup{format=centerproper}
-	\caption*{\textbf{Table 4:} The Effect of Battery Storage on the   \newline Elasticity of Demand for Coal Power} 
-	\label{table:4} 
+		\caption{The Effect of Battery Storage on the   \newline Elasticity of Demand for Coal Power} 
+		\label{table:storelas} 
 		\small
@@
 	Consequently, batteries can complement reductions in the cost of intermittent renewables and mitigate the distributional side effects of a carbon tax.
-As shown in \hyperref[fig:battery]{Figure 3}, the elasticity of substitution between solar and coal rises significantly as solar becomes less intermittent; this implies that a change in the relative price of solar would have a far greater effect on solar adoption if batteries were employed with solar.
+As shown in \autoref{fig:battery}, the elasticity of substitution between solar and coal rises significantly as solar becomes less intermittent; this implies that a change in the relative price of solar would have a far greater effect on solar adoption if batteries were employed with solar.
 Hence, if policy makers aim to promote the use of renewables, they should subsidize research that reduces the cost of renewables as well as research that improves battery technology.
@@
 This is because, by reducing the intermittency of renewables, batteries make demand for fossil fuels less inelastic.
-We specifically show this elasticity would change with another numerical example in \hyperref[table:4]{Table 4}; like  \hyperref[fig:battery]{Figure 3}, we model batteries that shift solar output towards the off-peak.
+We specifically show this elasticity would change with another numerical example in \autoref{table:storelas}; like  \autoref{fig:battery}, we model batteries that shift solar output towards the off-peak.
 We then estimate the elasticity of demand for coal power around its initial price; this elasticity is decreasing at an increasing rate with the percent shift in solar output.
@@
 		\captionsetup{format=centerproper}
-	\caption*{\textbf{Figure 4:} The VES Approximation of the Elasticity of Substitution \\ between Solar and Coal } 
+		\caption{The VES Approximation of the Elasticity of Substitution \\ between Solar and Coal } 
 		\label{fig:ves}
@@
 		\begin{tabular}{@{\extracolsep{0em}}c}
-		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_ves_approx} \\
+			\includegraphics[width=1\linewidth]{../figures/fig_ves_approx} \\
 			\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } Technology 1 is coal and technology 2 is solar.
@@
 Note that $e$ is a linear function of $X_1/X_2$; this relationship allows a VES function to approximate the effects of intermittency.
-To show why, we plot $e$ against its VES approximation $\hat{e}$ for solar and coal in \hyperref[fig:ves]{Figure 4}.
+To show why, we plot $e$ against its VES approximation $\hat{e}$ for solar and coal in \autoref{fig:ves}.
 This approximation was fit by running OLS against the numerical results for $e$ while holding the intercept fixed at 1.\footnote{ There also exists a VES function described by \citet{VES} with the form $e = \beta_0 + \beta (X_1/X_2)$.
@@
 	One potential objection to using the VES function is that it assumes the elasticity of substitution $e$ approaches 1 when the majority of generation comes from renewables ($X_1/X_2 \to 0$).
-And, a VES structure assumes linear $e$ which does not seem to be the case in \hyperref[fig:ves]{Figure 4}.
+And, a VES structure assumes linear $e$ which does not seem to be the case in \autoref{fig:ves}.
 However, both these assumptions may still be fairly reasonable in the right context.
@@
 Hence, in these cases, a VES approximation  can perfectly match $e$.
-Additionally, even when consumer's elasticity of substitution is not $1$, $e$ may still be approximately linear; this is shown in \hyperref[fig:ves_int]{Figure B.2} where we consider our estimated $\hat{\sigma} = 0.8847$.
+Additionally, even when consumer's elasticity of substitution is not $1$, $e$ may still be approximately linear; this is shown in \autoref{fig:ves_int} where we consider our estimated $\hat{\sigma} = 0.8847$.
 In short, the assumptions made by a VES structure may nevertheless be accurate in certain cases.
-
-%Moreover, even if these assumptions were not true, our model implies that VES function would only underestimate the substitutability of clean and dirty energy in these edge cases.
-While \textit{overestimating} $e$ may result in policy failing to mitigate a preventable climate disaster, \textit{underestimating} $e$ would simply cause a policy overreaction.
-The former would likely  result in far more economic damage than the latter, hence a risk averse policymaker need not be too concerned with the error of a VES assumption for $e$.
 
@@
 Its structure is simple enough to be calibrated with a given set of data, while its implementation can produce simple but reasonably accurate models of energy sectors with intermittency.
-
-%\subsubsection{Technical Change and the Adoption of Renewable Energy}
-% 
-% \begin{table}[!t]
-% 	\caption*{\textbf{Figure 2:} The Market Share of Solar Energy versus Own Price} 
-% 	\label{fig:adoptc2}
-% 	\footnotesize
-% 	\vspace{-1em}
-% 	\begin{tabular}{@{\extracolsep{0em}}c}
-% 		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_adoption_c2} \\
-% 		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
-To generate these values, we first vary the price of solar relative to its original parametrized cost $c_2$.
-Then, we find the optimal capacity of solar as a fraction of the total optimal capacity of all technologies (solar and coal) for each set of prices.
-And, finally, we repeat this process and plot the results for different values of $\sigma$, the consumer's intertemporal elasticity of electricity consumption.
-}     \\
-% 	\end{tabular}
-% \end{table}
-% 
-% \begin{table}[!t]
-% 	\caption*{\textbf{Figure 3:} The Market Share of Solar Energy versus the Price of Coal} 
-% 	\label{fig:adoptc1}
-% 	\footnotesize
-% 	\vspace{-1em}
-% 	\begin{tabular}{@{\extracolsep{0em}}c}
-% 		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_adoption_c1} \\
-% 		\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
-To generate these values, we first vary the price of coal relative to its original parametrized cost $c_1$.
-Then, we find the optimal capacity of solar as a fraction of the total optimal capacity of all technologies (solar and coal) for each set of prices.
-And, finally, we repeat this process and plot the results for different values of $\sigma$, the consumer's intertemporal elasticity of electricity consumption.
-}     \\
-% 	\end{tabular}
-% \end{table}
-%
-%
-% 
-%We now do a similar exercise but instead study the adoption (or market share/diffusion) of renewables.
-Specifically, using the same technologies, solar and coal, along with the same parameters, we study how the cost of each technology affects the market share of solar.
-First, we study the market share of solar with respect to its own price.
-Our results are shown in \hyperref[fig:adoptc2]{Figure 2}.
-We find that, for values of $\sigma \geq 1$, the market share of solar energy appears to be convex with respect to increases in cost efficiency.
-This relationship somewhat persists through to $\sigma = 0.5$; here, the market share appears to follow an inverted S-shape that starts concave and becomes convex.
-But, overall, the curve for $\sigma = 0.5$ seems almost linear.
-On the other hand, when $\sigma$ is sufficiently low, this relationship is more consistently convex.
-Interestingly, these dynamics with respect to $\sigma$ seem to be a product of intermittency.
-That is, as we discussed earlier, when consumers have high $\sigma$, they are more willing to shift their electricity consumption and are thus relatively more sensitive to chances in price.
-Consequently, the rate of adoption (the slope of the market share curve) is larger for higher $\sigma$ around moderate changes in price; however, this relationship between adoption and $\sigma$ changes as price falls more drastically.
-To understand why, see \hyperref[fig:adoptc1]{Figure 3}, where we compare the market share of solar with respect to the price of coal.
-We find that solar market share is concave for all values of $\sigma$; consequently, the market share of coal must be convex with respect to its own price.
-Hence, it seems that market share with respect to own price is convex for non-intermittent technologies, but may be concave for intermittent ones.
-Furthermore, the importance of intermittency in this context is driven by $\sigma$; that is, intermittency plays a bigger role in determining market share when consumers prefer, on the margin, smoother electricity consumption than electricity cost savings.
-This result directly contrasts with \cite{HH} who find S-shaped market diffusion for renewable energy; this shape is a result of their representation of intermittency as unpredictable, stochastic variability in the output of renewable energy.
-On the other hand, because we represent intermittency in a different way, our market share curves differ significantly.
-In any case, these market share curves have important implications in the context of promoting renewable energy adoption.
-
-%
-%\subsubsection{Externalities}
-%
-%
-%
-%Suppose we are interested in handling externalities.
-We may assume that our first technology produces pollution according to the function $S(X) = \gamma X_1$ where $\gamma$ is the monetary damage per unit of $X_1$.
-A social planner then aims to balance the damages caused by pollution with the surplus of the private sector and the revenue from the tax.
-Hence, their objective function is given by
-%$$\max_{\tau} \; CS + PS - \gamma X_1 + \tau X_1$$
-%where $CS$ is consumer surplus, $PS$ is producer surplus, $\gamma$ is the marginal cost of pollution generated by $X_1$, $\gamma X_1$ is the cost of pollution, $\tau$ is the tax on $X_1$, and $\tau X_1$ is the tax revenue.
-As usual, the optimal tax is a Pigouvian tax; $\tau$ should be set equal to the marginal social cost of pollution $\gamma$.
-%
-%\textbf{More Here}
-
-%However, given the presence of intermittency, is there a better way to handle pollution?
-For example, \citet{Ace2012} model intermittency using a CES production function between clean and dirty energy.
-They find that both carbon taxes and research subsidies are necessary to promote long-run structural change in the energy production sector and avert a climate disaster.
-
-%The necessity of both instruments is a consequence of their model spanning multiple periods; that is, assuming we have CES production structure between clean and dirty energy in a one-period model, a single instrument is enough to optimally handle externalities.
-\footnote{ Recall that, with a CES production structure, the optimal quantity of technology $i$ is given by $X_i = \left( \frac{\xi_i}{c_i} \right)^\sigma  \frac{B}{P}$ where $\xi_i$ is its output per unit, $B$ is the budget, and $P$ is the price index.
-Neglecting effects on the price index, the own-price elasticity of any good is $-\sigma$.
-Furthermore, for the same structure,  we have the FOC: $X_i/X_j =  \left( \frac{\xi_i c_j}{\xi_j c_i} \right)^\sigma$.
-This implies that the cross elasticity of $X_i$ with respect to the output efficiency of technology $j$, $\xi_j$, is also $-\sigma$.
-Hence, a tax on the cost of $X_i$ or a subsidy that increases the efficiency $X_j$ can be used to deal with externalities; but, both are not necessary to do so.} However, while our model focuses on production on a shorter time scale, we find a similar result -- a combination of both taxes and subsidies may be more effective in promoting a shift towards clean energy.
-Moreover, the optimality of combining both instruments is a result of intermittency.
-
-%For clarity, let us first consider the cases in our framework where only one instrument is necessary.
-The first case is when no two technologies produce in the same period.
-That is, we can say that the output efficiency matrix, $\xi$, is diagonal without loss of generality; this further implies that we have a CES structure between technologies where the elasticity of substitution is same as that for consumers, $\sigma$.\footnote{ A proof is provided in \hyperref[sec:CESspecialcase]{Appendix A.C}} Consequently, if one of these technologies creates negative externalities, the optimal solution is simply use a single instrument such as a Pigouvian tax.
-On the other hand, the second case occurs when all technologies produce in every period but with time-invariant output.
-This results in an edge case where we only employ whichever technology has the highest cost efficiency (output per dollar).
-Consequently, we only need one or no instruments depending on whether the technology employed creates negative externalities.
-Essentially this latter case describes a situation where we have no intermittency at all.
-On the other hand, the former case describes a situation where we have, in a sense, maximized relative intermittency.
-But, with respect to both cases, we only need one instrument to handle externalities.
-
-%In all other situations, where we have a mix of intermittent and constant-output technologies, using multiple instruments can be more effective than just one.
-That is,  first suppose that research subsidies increase the output efficiency $\xi_i$ of some technology $i$.
-So, output efficiency is then given by $\xi_i \left( 1 + \beta_i \right)$ where $\beta_i$ is the percent increase in the output efficiency of technology $i$ as a result of research.
-Now, consider again a two-period setting with coal and solar with the same parameters as those given in \hyperref[Params: Example A]{Example A}.
-As discussed earlier, one solution to externalities is to set a Pigouvian tax on coal equal to its marginal social damage.
-However, we may be able to reduce our reliance on coal in a more effective (welfare-maximizing) way by subsidizing research in solar as well.
-
-%We can intuit this to be a potential solution based on \hyperref[fig:coaltech]{Figure 4}.
-In the first subplot, we show the effects of improving solar output efficiency on the use of coal; in the second subplot, we show how the use of coal varies with its own price.
-Essentially, with respect to reducing the use of coal power, there are diminishing returns to both carbon taxes and solar research subsidies.
-Consequently, there must the be diminishing returns to the pollution-reduction benefits of each, since pollution scales with the amount of coal power employed.
-But, we should also consider a secondary benefit of carbon taxes -- the revenue they generate.
-
-%It is also important to note that carbon taxes have an added benefit -- they generate revenue.
-
-%Hence, the pollution-reduction benefits of both instruments are convex.
-Additionally, even when \footnote{ To be more precise, we numerically compute the Hessian for $X_1$ with respect to $\beta_2$, the percent change in the output efficiency of solar from research, and the tax rate, $\tau$.
-We find that the Hessian is negative definite.
-Consequently, since reducing $X_1$ creates welfare by reducing the social cost of pollution $\gamma X_1$, the Hessian of the benefits, $-\gamma X_1$ is positive definite and thus convex.}
-
-%Additionally, the deadweight loss created by taxation is generally convex; since research subsidies must be funded by tax revenue, its costs must necessarily be convex as well.
-The remaining factors to consider are the secondary benefits to each instrument.
-Research subsidies increase consumer surplus by making energy cheaper; since producers have linear costs in our model, we can neglect the effect on producer surplus.
-Additionally,
-
-% CO2 emits 204 pounds of co2 per million btu
-% million btu = 0.29307107 mwh
-% ~700 pounds per Mwh
-
-% On the other hand, the deadweight loss created by taxation is generally convex; since research subsidies must be funded by tax revenue, its costs must necessarily be convex as well.
-In short, both instruments have convex benefits and costs.
-If we are not at an edge case, this implies that optimal policy is likely a combination of both.
-%\footnote{ To be more precise, we numerically compute the Hessian for $X_1$ with respect to $\beta_2$, the percent change in the output efficiency of solar from research, and the tax rate, $\tau$.
-We find that the Hessian is negative definite.
-Consequently, since reducing $X_1$ creates welfare by reducing the social cost of pollution $\gamma X_1$, the Hessian of the benefits, $-\gamma X_1$ is positive definite and thus convex.
-Note that we neglect here the change in surplus from the technological improvement $beta$ and the tax revenue from $\tau$.
-}
 
@@
 
-\begin{table}[h!]
+	\begin{figure}[h!]
 		\captionsetup{format=centerproper}
-	\caption*{\textbf{Figure B.1:} The Elasticity of Substitution Between Two \newline  Minimally Intermittent Technologies} 
+		\caption{The Elasticity of Substitution Between Two \newline  Minimally Intermittent Technologies} 
 		\label{fig:eosrange}
@@
 		\begin{tabular}{@{\extracolsep{0em}}c}
-		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_elasticity_range} \\
+			\includegraphics[width=1\linewidth]{../figures/fig_elasticity_range} \\
 			\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } The y-axis of the first plot is equivalent to $\log(X_1/X_2)$ and the x-axis of both plots is equivalent to  $\log(c_2/c_1)$.
@@
 
-\begin{table}[h!]
+	\begin{figure}[h!]
 		\captionsetup{format=centerproper}
-	\caption*{\textbf{Figure B.2:} The VES Approximation of the Elasticity of Substitution \\ between Highly Intermittent Solar and Coal} 
+		\caption{The VES Approximation of the Elasticity of Substitution \\ between Highly Intermittent Solar and Coal} 
 		\label{fig:ves_int}
@@
 		\begin{tabular}{@{\extracolsep{0em}}c}
-		\includegraphics[width=1\linewidth]{../code/matlab/simulation_april/fig_ves_approx_int} \\
+			\includegraphics[width=1\linewidth]{../figures/fig_ves_approx_int} \\
 			\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } Technology 1 is coal and technology 2 is solar.

### 2019-06-19 code/simulation/main.m
Remove unused matlab code

@@ -1,55 +1,0 @@
-%%% Model %%%
-% Linear cost
-% CES Utility
-% Two Periods
-
-
-%% CES Numerical Sim
-
-alpha = [0.6, 0.4];
-xi_1  = [1, 1];
-xi_2  = [1, 0.9]*1.00;
-
-sigma = 0.5;
-phi   = (sigma - 1)/sigma;
-budget = 1;
-
-x_1_cost_param = 104.3*1.00;
-x_2_cost_param = 100;
-
-% Prices
-xi_mat   = [xi_1; xi_2];
-cost_mat = [x_1_cost_param; x_2_cost_param];
-prices   = xi_mat\cost_mat;
-
-% Price Index
-P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
-
-% Quantities
-Y = ((alpha'./prices).^(sigma)) * (budget/P);
-X = (xi_mat')\Y
-
-
-%% Hessian
-
-f_ab = (sim_function([1.01,1.01]) - sim_function([1.01, 0.99])        ...
-    - sim_function([0.99, 1.01]) + sim_function([0.99, 0.99])) ...
-    / (4*0.02*0.02);
-
-f_aa = (-sim_function([0.99, 1.0]) + 2*sim_function([1, 1]) ...
-    - sim_function([1.01, 1]))/(0.01^2);
-
-
-f_bb = (-sim_function([1.0, 0.99]) + 2*sim_function([1, 1]) ...
-    - sim_function([1.0, 0.99]))/(0.01^2);
-
-% g = tax X1
-g_ab = f_ab(1);
-g_aa = f_aa(1);
-g_bb = f_bb(1);
-
-g_Hes = [g_aa, g_ab; g_ab, g_bb];
-
-eig(-g_Hes)
-
-

### 2019-06-19 code/simulation/sim_adoption_curve.m

@@ -1,186 +1,0 @@
-%% Adoption with Respect to Price of Solar Sim
-
-close all; clear; clc;
-
-% Simulation params
-n = 5000;
-cost_multiplier = linspace(0.01,2,n);
-sigma_range = [0.8847 + 1.96*0.044, 0.8847, 0.8847 - 1.96*0.044];
-m = length(sigma_range);
-
-% Exogenous params
-c_1 = 104.3;
-c_2 = 50;
-alpha = [0.6, 0.4];
-xi_1  = [1,   1];
-xi_2  = [1, 0.1];
-budget = 1;
-
-
-figure('Renderer', 'painters', 'Position', [100 100 900 600])
-hold on;
-
-for j = 1:m
-    
-    sigma = sigma_range(j);
-    results = zeros(n,2); 
-
-    for i = 1:n
-
-
-        phi   = (sigma - 1)/sigma;
-        x_1_cost_param = c_1;
-        x_2_cost_param = c_2*cost_multiplier(i);
-
-        % Prices
-        xi_mat   = [xi_1; xi_2];
-        cost_mat = [x_1_cost_param; x_2_cost_param];
-        prices   = xi_mat\cost_mat;
-
-        if any(prices<0)
-            continue
-        end
-
-        % Price Index
-        P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
-        if sigma == 1
-            P = 1;
-        end
-        
-        % Quantities
-        Y = ((alpha'./prices).^(sigma)) * (budget/P);
-          
-        X = (xi_mat')\Y;
-
-        results(i,:) = X';
-
-    end    
-
-    output = [];
-    output(1,:) = results(:,1);
-    output(2,:) = results(:,2);
-    output(3,:) = cost_multiplier-1;
-    
-    % subset to positive quantities
-    ind = ~any(output(1:2,:) <= 0);
-    output = output(:,ind);
-
-    % adoption curve for solar
-    hold on;
-    subplot(2,1,1);
-    plot(output(3,:)*100, ...
-         100*output(2,:)./(output(1,:) + output(2,:)), ...
-        'LineWidth', 1);
-    
-end
-
-%% Plot formatting
-
-% Format plot 1
-legend('0.9709 (Upper 95% Confidence Limit)', '0.8847', ...
-    '0.7985 (Lower 95% Confidence Limit)')
[…]

### 2019-06-19 code/simulation/sim_adoption_surface.m

@@ -1,63 +1,0 @@
-%% Adoption Curve with Respect to Both Prices Sim
-
-close all; clear; clc;
-
-% Simulation params
-[c_1_range, c_2_range] = meshgrid(0.5:0.05:2, 0.5:0.05:2);
-
-% Exogenous params
-c_1 = 104.3;
-c_2 = 50;
-alpha = [0.6, 0.4];
-xi_1  = [1,   1];
-xi_2  = [1, 0.1];
-budget = 1;
-sigma = 0.5;
-
-
-figure('Renderer', 'painters', 'Position', [100 100 900 600])
-hold on;
-
-results = ones(length(c_1_range), length(c_1_range)); 
-
-for i = 1:length(results)
-    for j = 1:length(results)
-
-        phi   = (sigma - 1)/sigma;
-        x_1_cost_param = c_1*c_1_range(i,j);
-        x_2_cost_param = c_2*c_2_range(i,j);
-
-        % Prices
-        xi_mat   = [xi_1; xi_2];
-        cost_mat = [x_1_cost_param; x_2_cost_param];
-        prices   = xi_mat\cost_mat;
-
-        % Price Index
-        P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
-
-        % Quantities
-        Y = ((alpha'./prices).^(sigma)) * (budget/P);
-
-        X = (xi_mat')\Y;
-
-        if all(X > 0)
-            results(i,j) = X(2)/(X(1) + X(2));
-        else
-            results(i,j) = nan;
-        end
-
-    end    
-end
-
-surf(100*(c_1_range-1), 100*(c_2_range-1), results)
-
-%% Plot formatting
-
-xlabel('Percent Change in the Cost of Coal')
-ylabel('Percent Change in the Cost of Solar')
-zlabel('Solar Capacity as a Fraction of All Capacity')
-xtickformat('percentage')
-ytickformat('percentage')
-
-
-

### 2019-06-19 code/simulation/sim_function.m

@@ -1,59 +1,0 @@
-function [ output ] = sim_function(v)
-% ========================================================================
-% SIM_FUNCTION finds the optimal X_1 given a multiplier 
-% for the output efficiency of solar and a tax rate on coal
-% ========================================================================
-% INPUT ARGUMENTS:
-%   v             (matrx)  the first entry is the multiplier on the output
-%                          efficiency of solar and the second entry is the 
-%                          tax rate
-% ========================================================================
-
-alpha = [0.6, 0.4];
-xi_1  = [1, 1];
-xi_2  = [1, 0.1]*v(1);
-
-sigma = 1;
-phi   = (sigma - 1)/sigma;
-budget = 1;
-gamma = 70;
-
-c_1 = 104.3;
-c_2 = 50;
-c_b = 0.75;
-
-x_1_cost_param = c_1+v(2);
-x_2_cost_param = c_2;
-
-% Prices
-xi_mat   = [xi_1; xi_2];
-cost_mat = [x_1_cost_param; x_2_cost_param];
-prices   = xi_mat\cost_mat;
-
-% Price Index
-P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
-
-if sigma == 1
-    P = 1;
-end
-        
-
-% Quantities
-Y = ((alpha'./prices).^(sigma)) * (budget/P);
-X = (xi_mat')\Y;
-
-% Tax revenue + Pollution costs 
-tax_revenue    = v(2) * X(1);
-pollution_dmg  = gamma*X(1);
-
-% Beta costs
-beta_cost = c_b*v(1);
-
-% Consumer surplus trim
-cons_surplus_trim = -alpha(1)*budget*log(prices(1)) + ...
-                    -alpha(2)*budget*log(prices(2));
-
-output = [X(1), X(2), ...
-    tax_revenue - pollution_dmg, cons_surplus_trim, -beta_cost];
-
-end

### 2019-06-19 code/simulation/sim_opt_policy.m

@@ -1,88 +1,0 @@
-%% Optimal policy with just tax
-
-beta = 0;
-n = 10000;
-tau_range = linspace(0,140,n);
-results = zeros(n,1);
-
-
-for i = 1:n
-
-    tau = tau_range(i);
-    output = sim_function([1+beta, tau]);
-    welfare = output(3) + output(4) + output(5);
-    results(i) = welfare;
-
-end
-
-plot(tau_range, results)
-[M, I] = max(results);
-tau_range(I)
-
-
-%% Optimal policy with just subsidy
-
-tau = 0;
-n = 1000;
-beta_range = linspace(0,4,n);
-results = zeros(n,1);
-
-
-for j = 1:n
-
-    beta = beta_range(j);
-    output = sim_function([1+beta, tau]);
-    welfare = output(3) + output(4) + output(5);
-    results(j) = welfare;
-
-    if (output(1) < 0) || (output(2) < 0)
-        results(j) = nan;
-    end
-    
-end
-
-plot(beta_range, results)
-[M, I] = max(results);
-beta_range(I)
-
-
-%% Optimal policy with both
-
-n = 500;
-[tau_range, beta_range] = meshgrid(linspace(60,80,n), linspace(0,1,n));
-results = zeros(n,n);
-
-
-for i = 1:n      % tau
-    for j = 1:n  % beta
-           
-        tau = tau_range(i,j);
-        beta = beta_range(i,j);
-        output = sim_function([1+beta, tau]);
-        welfare = output(3) + output(4) + output(5);
-        results(i,j) = welfare;
-
-        if ((output(1) < 0) || (output(2) < 0) ||  ~isreal(welfare))
-            results(i,j) = nan;
-        end
-
-    end
-end
-
-disp('Done')
-
-mesh(tau_range, beta_range, results)
-
-%%
-
-% beta = 0 case
-[M, I] = max(results(1,:));
-tau_range(I)
-
-% general case
-[M, I] = max(results(:));
-[beta_range(I) tau_range(I)]
-
-
-
-

### 2019-06-19 code/simulation/sim_tax_subsidy.m

@@ -1,177 +1,0 @@
-%% Optimal capacity of Coal with respect to solar price
-
-close all; clear; clc;
-
-% Simulation params
-n = 10000;
-research_multiplier = linspace(1,3,n);
-sigma_range = [0.8847 + 1.96*0.044, 0.8847, 0.8847 - 1.96*0.044];
-m = length(sigma_range);
-
-% Exogenous params
-c_1 = 104.3;
-c_2 = 50;
-alpha = [0.6, 0.4];
-xi_1  = [1,   1];
-xi_2  = [1, 0.1];
-budget = 1;
-
-
-figure('Renderer', 'painters', 'Position', [100 100 900 600])
-hold on;
-
-for j = 1:m
-    
-    sigma = sigma_range(j);
-    results = zeros(n,2); 
-
-    for i = 1:n
-
-        phi   = (sigma - 1)/sigma;
-        x_1_cost_param = c_1;
-        x_2_cost_param = c_2;
-
-        % Prices
-        xi_mat   = [xi_1; xi_2*(research_multiplier(i))];
-        cost_mat = [x_1_cost_param; x_2_cost_param];
-        prices   = xi_mat\cost_mat;
-
-        if any(prices<0)
-            continue
-        end
-
-        % Price Index
-        P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
-        if sigma == 1
-            P = 1;
-        end
-        
-        % Quantities
-        Y = ((alpha'./prices).^(sigma)) * (budget/P);
-           
-        X = (xi_mat')\Y;
-
-        results(i,:) = X';
-
-    end    
-
-    output = [];
-    output(1,:) = results(:,1);
-    output(2,:) = results(:,2);
-    output(3,:) = research_multiplier-1;
-    
-    % subset to positive quantities
-    ind = ~any(output(1:2,:) <= 0);
-    output = output(:,ind);
-
-    % quantity of solar
-    subplot(2,1,1);
-    hold on;
-    plot(output(3,:)*100, ...
-        100*output(2,:)./(output(1,:) + output(2,:)), ...
-        'LineWidth', 1);
-    
-end
-
-%% Plot formatting
-
-% Format subplot 1
-legend('0.9709 (Upper 95% Confidence Limit)', '0.8847', ...
-    '0.7985 (Lower 95% Confidence Limit)')
[…]

### 2019-06-19 code/matlab/confun.m
Remove old matlab code

@@ -1,44 +1,0 @@
-function [c, ceq] = confun(obj_vars, p_1, p_2, c_1, c_2, xi_1_d, xi_1_n, xi_2_d, ...
-    xi_2_n, alpha, beta, budget, eta_1, eta_2)
-
-% 
-x = obj_vars(1:2);
-p_d = obj_vars(3);
-p_n = obj_vars(4);
-
-% Output function
-output_d = @(x) xi_1_d.*x(1) + xi_2_d.*x(2);
-output_n = @(x) xi_1_n.*x(1) + xi_2_n.*x(2);
-
-% Input cost functions
-cost_x = @(x) (p_1*(x(1)-c_1)^eta_1 + p_2*(x(2)-c_1)^eta_2) + 1; %(p_1 + log(x(1)))*x(1) + (p_2 + log(x(2)))*x(2);
-
-% % Demand functions
-demand_d = @(x) (alpha*budget)/p_d;
-demand_n = @(x) (alpha*budget)/p_n;
-
-inv_demand_d = @(x) (alpha*budget)/output_d(x);   %15 - log(output_d(x)+1);
-inv_demand_n = @(x) (beta*budget)/output_n(x);   %15 - log(output_n(x)+1);
-
-% Profit
-revenue_d = @(x) min([output_d(x), demand_d(x)])*p_d;
-revenue_n = @(x) min([output_n(x), demand_n(x)])*p_n;
-profit = @(x) revenue_d(x) + revenue_n(x) - (cost_x(x));
-
-
-%% Nonlinear inequality constraints
-
-% %budget constraint
-con_budget_cons = p_d*output_d(x) + p_n*output_n(x) - budget;
-
-% firms making profit
-profit_cons = -profit(x);
- 
-c = [profit_cons, con_budget_cons];  
-
-%% Nonlinear equality constraints
-
-ceq = [];
-
-
-end

### 2019-06-19 code/matlab/consprofit.m

@@ -1,46 +1,0 @@
-function [c, ceq] = confun(vars)
-
-% 
-x = obj_vars(1:2);
-p_1 = obj_vars(3);
-p_2 = obj_vars(4);
-p_d = obj_vars(5);
-p_n = obj_vars(6);
-
-% Output function
-output_d = @(x) xi_1_d.*x(1) + xi_2_d.*x(2);
-output_n = @(x) xi_1_n.*x(1) + xi_2_n.*x(2);
-
-% Input cost functions
-cost_x = @(x) (p_1*x(1) + p_2*x(2)); %(p_1 + log(x(1)))*x(1) + (p_2 + log(x(2)))*x(2);
-
-% Demand functions
-inv_demand_d = @(x) (alpha*budget)/output_d(x);   %15 - log(output_d(x)+1);
-inv_demand_n = @(x) (beta*budget)/output_n(x);   %15 - log(output_n(x)+1);
-
-% Profit
-profit = @(x) max([output_d(x)*inv_demand_d(x) ...
-    + output_n(x)*inv_demand_n(x) - (cost_x(x)), 0]);
-
-
-%% Nonlinear inequality constraints
-
-% production >= consumption
-prod_d_cons = (alpha*budget)/p_d - output_d(x);
-prod_n_cons = (beta*budget)/p_n  - output_n(x);
-
-% budget constraint
-con_budget_cons = p_d*output_d(x) + p_n*output_n(x) - budget;
-prod_budget_cons =  cost_x(x) - (p_d*output_d(x) + p_n*output_n(x));
-
-% firms making profit
-profit_cons = -profit(x);
- 
-c = [prod_d_cons; prod_n_cons; con_budget_cons; prod_budget_cons; profit_cons];  
-
-%% Nonlinear equality constraints
-
-ceq = [];
-
-
-end

### 2019-06-19 code/matlab/intermit_2.m

@@ -1,140 +1,0 @@
-
-
-%% Params
-
-% Initial Prices
-p_1 = 10;
-p_2 = 10;
-c_1 = 0.5;
-c_2 = 0.5;
-xi_1_d = 5;
-xi_1_n = 5;
-xi_2_d = 20;
-xi_2_n = 1;
-
-% cobb-douglas utiltiy
-alpha = 0.3;
-beta = 0.7;
-budget = 50;
-
-% cost function
-eta_1 = 3;
-eta_2 = 3;
-
-n = 20;
-var_range = linspace(0.7*p_2, 1.3*p_2, n);    
-X = [];
-
-
-%% Main
-% d and n (day and night) are used instead of time t and s
-
-for i = 1:n
-    
-    % change price of second input
-    p_2 = var_range(i);
-
-%     % Output function
-%     output_d = @(x) xi_1_d.*x(1) + xi_2_d.*x(2);
-%     output_n = @(x) xi_1_n.*x(1) + xi_2_n.*x(2);
-% 
-%     % Input cost functions
-%     cost_x = @(x) (p_1*x(1)^2 + p_2*x(2)^2); 
-%     
-%     % Demand functions
-%     demand_d = @(x) (alpha*budget)/x(3);
-%     demand_n = @(x) (beta*budget)/x(4);
-%     
-%     % Profit
-%     revenue_d = @(x) min([output_d(x), demand_d(x)])*x(3);
-%     revenue_n = @(x) min([output_n(x), demand_n(x)])*x(4);
-%     profit = @(x) output_d(x)*inv_demand_d(x) + output_n(x)*inv_demand_n(x) ... 
-%         - (cost_x(x));
-    
-    % Utility
-    utility = @(x) output_d(x).^alpha * output_n(x).^beta;
-
-    % Objective
-    neg_profit = @(x) -profit(x)*1000;
-    neg_utility = @(x) -utility(x)*10000;
-    obj = @(x) neg_utility(x);
-    
-    % Optimize
-    options = optimoptions(@fmincon,'Algorithm','sqp');
-
-    % constraints are given in confun.m
-    constraints = @(obj_vars) confun(obj_vars, p_1, p_2, c_1, c_2, xi_1_d, ...
-        xi_1_n, xi_2_d, xi_2_n, alpha, beta, budget, eta_1, eta_2);
-
-    [result,fval] = ... 
[…]

### 2019-06-19 code/matlab/intermit_xi.m

@@ -1,104 +1,0 @@
-
-% Initial Prices
-p_1 = 10;
-p_2 = 10;
-c_1 = 0.5;
-c_2 = 0.5;
-xi_1_d = 5;
-xi_1_n = 5;
-xi_2_d = 10;
-xi_2_n = 4;
-
-% cobb-douglas utiltiy
-alpha = 0.3;
-beta = 0.7;
-budget = 50;
-
-% cost function
-eta_1 = 3;
-eta_2 = 3;
-
-
-n = 20;
-range_temp = linspace(0.7*xi_1_n, 1.3*xi_1_n, n);    
-X = [];
-    
-
-for i = 1:n
-    
-    xi_1_n = range_temp(i);
-
-    % Output function
-    output_d = @(x) xi_1_d.*x(1) + xi_2_d.*x(2);
-    output_n = @(x) xi_1_n.*x(1) + xi_2_n.*x(2);
-
-    % Input cost functions
-    cost_x = @(x) (p_1*x(1)^2 + p_2*x(2)^2); %(p_1 + log(x(1)))*x(1) + (p_2 + log(x(2)))*x(2);
-    
-    % Demand functions
-    demand_d = @(x) (alpha*budget)/x(3);
-    demand_n = @(x) (beta*budget)/x(4);
-    
-    inv_demand_d = @(x) (alpha*budget)/output_d(x);   %15 - log(output_d(x)+1);
-    inv_demand_n = @(x) (beta*budget)/output_n(x);   %15 - log(output_n(x)+1);
-    %inv_demand_d = @(x) 1500 - output_d(x)^2% log(output_d(x)+1);
-    %inv_demand_n = @(x) 1500 - output_n(x)^2% log(output_n(x)+1);
-    
-    % Profit
-    revenue_d = @(x) min([output_d(x), demand_d(x)])*x(3);
-    revenue_n = @(x) min([output_n(x), demand_n(x)])*x(4);
-    profit = @(x) output_d(x)*inv_demand_d(x) + output_n(x)*inv_demand_n(x) ... 
-        - (cost_x(x));
-    
-    % Utility
-    utility = @(x) output_d(x).^alpha * output_n(x).^beta;
-
-    % Objective
-    neg_profit = @(x) -profit(x)*1000;
-    neg_utility = @(x) -utility(x)*10000;
-    obj = @(x) neg_utility(x);
-    
-    
-    %% Run
[…]

### 2019-06-19 code/matlab/main.m

@@ -1,73 +1,0 @@
-
-%% Params
-
-% Initial Prices
-p_1 = 10;
-p_2 = 10;
-xi_1_d = 5;
-xi_1_n = 5;
-xi_2_d = 10;
-xi_2_n = 4;
-
-% cobb-douglas utiltiy
-alpha = 0.3;
-beta = 0.7;
-budget = 50;
-
-
-%% Objectives
-
-% Profit
-profit = @(x) max([output_d(x)*inv_demand_d(x) ...
-        + output_n(x)*inv_demand_n(x) - (cost_x(x)), 0]);
-
-output_d = @(x) xi_1_d.*x(1) + xi_2_d.*x(2);
-output_n = @(x) xi_1_n.*x(1) + xi_2_n.*x(2);
-    
-% Utility
-utility = @(x) output_d(x).^alpha * output_n(x).^beta;
-
-% Objective
-neg_profit = @(x) -profit(x)*1000;
-neg_utility = @(x) -utility(x)*1000;
-objfunc = @(obj_vars) neg_profit(obj_vars(1:2));
-
-
-%% Optimization
-
-% run
-x0 = ones(1,6);     % Make a starting guess at the solution
-options = optimoptions(@fmincon,'Algorithm','sqp');
-
-constraints = @(obj_vars) confun(obj_vars, p_1, p_2, xi_1_d, xi_1_n, xi_2_d, ...
-    xi_2_n, alpha, beta, budget);
-
-[x1,fval] = ... 
-fmincon(@(obj_vars) objfunc(obj_vars),x0,[],[],[],[],[],[],@(obj_vars) constraints(obj_vars),options);
-
-
-
-%%
-log_X_ratio = log(X(:,1)./X(:,2));
-log_P_ratio = log(p_1./range_temp);
-
-x = X(1,:);
-revenue = output_d(x)*inv_demand_d(x) + output_n(x)*inv_demand_n(x);
-costs   = x(1)*p_1 + x(2)*p_2;
-
-plot(-log_P_ratio', log_X_ratio)
-title('Log Input Differences versus (-1) * Log Price Differences')
-ylabel('Log(X_{constant}/X_{intermittent})')
-xlabel('-Log(P_{constant}/P_{intermittent})')
-
-[b,bint,r,rint,stats] = regress(log_X_ratio, [- log_P_ratio', ones(n,1)]);
[…]

### 2019-06-19 code/matlab/simulation_batteries/constraints.m

@@ -1,83 +1,0 @@
-function [ c, ceq ] = constraints( opt_coeffs, parameters )
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Unpack
-
-% funcs
-alpha = parameters.alpha;
-xi_1  = parameters.xi_1;
-xi_2  = parameters.xi_2;
-
-% prices
-price_coeffs = opt_coeffs(1:24);
-x_1_cost_param = parameters.x_1_cost_param;
-x_2_cost_param = parameters.x_2_cost_param;
-
-% constants
-phi   = parameters.phi;
-sigma = 1/(1-phi);
-budget = parameters.budget;
-
-% storage
-storage_coeffs = opt_coeffs(27:50);
-
-
-%% Condition
-
-% price
-price_coeffs_positive = sum(price_coeffs > 0) == length(price_coeffs);
-
-% Input
-X_1 = opt_coeffs(25);%(1/x_1_cost_param)*xi_1(linspace(0,1,24))*price_coeffs'/24;
-X_2 = opt_coeffs(26);%(1/x_2_cost_param)*xi_2(linspace(0,1,24))*price_coeffs'/24;
-
-% Output
-G = (1/24)*(xi_1(linspace(0,1,24))*X_1 + xi_2(linspace(0,1,24))*X_2);
-Z = storage_coeffs;
-
-Y = G + Z;
-I = price_coeffs*Y'/24;
-
-% price index
-P = ((1/24)*(price_coeffs.^(1-sigma))*(alpha(linspace(0,1,24))'.^sigma)).^(1/(1-sigma));
-Y_demand = ((price_coeffs./(alpha(linspace(0,1,24)))).^(-sigma)) .* (P.^(1-sigma));
-U = (1/24)*(alpha(linspace(0,1,24))*(Y.^phi)').^(1/phi);
-
-% quantity mismatch
-q_diff = (20.*(Y - Y_demand)./Y).^4;
-q_diff_total = sum(q_diff)/24;
-
-
-
-%% <= constraints
-
-budget_constraint = I - budget;
[…]

### 2019-06-19 code/matlab/simulation_batteries/main.m

@@ -1,149 +1,0 @@
-
-%%%%% Time period is from 0 to 1  %%%%%
-%%%%% Broken up into 24 hr chunks %%%%%
-
-
-%% Parameters
-
-parameters.alpha = @(t) 1.75-(2.*t-1).^2/2;
-parameters.xi_1  = @(t) cos(t.*3-2)/2 + 1.5;
-parameters.xi_2  = @(t) sin(t.*6-.5)/2 + 1.5;
-
-parameters.phi = 0.5;
-parameters.budget = 1;
-
-parameters.x_1_cost_param = 10;
-parameters.x_2_cost_param = 1;
-
-parameters.storage_decay = 0.00;
-
-% plots
-figure;
- 
-subplot(2,1,1); 
-fplot(parameters.alpha, [0 1])
-title('\alpha')
-
-subplot(2,1,2); hold on; 
-fplot(parameters.xi_1, [0 1])
-fplot(parameters.xi_2, [0 1])
-title('Conversion Rates')
-legend('\xi_1', '\xi_2')
-ylabel('Energy per Input Unit')
-xlabel('Time')
-
-
-
-%% Optimize
-
-disp('Optimizing...')
-[ optimal_vars, optimal_val, objfunc, objcons ] = optimize ( parameters );
-
-
-%% Get results
-
-% unpack params
-price_coeffs = optimal_vars(1:24);
-
-alpha = parameters.alpha;
-xi_1  = parameters.xi_1;
-xi_2  = parameters.xi_2;
-
-% 
-x_1_cost_param = parameters.x_1_cost_param;
-x_2_cost_param = parameters.x_2_cost_param;
-
-phi   = parameters.phi;
-sigma = 1 / (1-phi);
-
-% 
-price_coeffs_positive = sum(price_coeffs > 0) == length(price_coeffs);
-
-% Input
-X_1 = optimal_vars(25);%(1/x_1_cost_param)*xi_1(linspace(0,1,24))*price_coeffs'/24;
-X_2 = optimal_vars(26);%(1/x_2_cost_param)*xi_2(linspace(0,1,24))*price_coeffs'/24;
-
-% Output
-G = (1/24)*(xi_1(linspace(0,1,24))*X_1 + xi_2(linspace(0,1,24))*X_2);
-Z = optimal_vars(27:50);
-
-Y = G + Z;
-I = price_coeffs*Y'/24;
-
-% price index
[…]

### 2019-06-19 code/matlab/simulation_batteries/obj_f.m

@@ -1,52 +1,0 @@
-function [ obj_value ] = obj_f ( opt_coeffs, parameters )
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Unpack parameters
-
-% funcs
-alpha = parameters.alpha;
-xi_1  = parameters.xi_1;
-xi_2  = parameters.xi_2;
-
-% prices
-price_coeffs = opt_coeffs(1:24);
-x_1_cost_param = parameters.x_1_cost_param;
-x_2_cost_param = parameters.x_2_cost_param;
-
-% constants
-phi   = parameters.phi;
-sigma = 1/(1-phi);
-budget = parameters.budget;
-
-% storage
-storage_coeffs = opt_coeffs(27:50);
-
-%% Find utility
-
-% price
-price_coeffs_positive = sum(price_coeffs > 0) == length(price_coeffs);
-
-% Input
-X_1 = opt_coeffs(25);%(1/x_1_cost_param)*xi_1(linspace(0,1,24))*price_coeffs'/24;
-X_2 = opt_coeffs(26);%(1/x_2_cost_param)*xi_2(linspace(0,1,24))*price_coeffs'/24;
-
-% Output
-G = (1/24)*(xi_1(linspace(0,1,24))*X_1 + xi_2(linspace(0,1,24))*X_2);
-Z = storage_coeffs;
-
-Y = G + Z;
-I = price_coeffs*Y'/24;
-
-% price index
-P = ((1/24)*(price_coeffs.^(1-sigma))*(alpha(linspace(0,1,24))'.^sigma)).^(1/(1-sigma));
-Y_demand = ((price_coeffs./(alpha(linspace(0,1,24)))).^(-sigma)) .* (P.^(1-sigma));
-U = (1/24)*(alpha(linspace(0,1,24))*(Y.^phi)').^(1/phi);
-
-% quantity mismatch
-q_diff = (30.*(Y - Y_demand)).^4;
-q_diff_total = sum(q_diff)/24;
-
-obj_value = -U;%20*q_diff_total;
-
-
-end

### 2019-06-19 code/matlab/simulation_batteries/optimize.m

@@ -1,21 +1,0 @@
-function [ optimal_vars, optimal_val, objfunc, objcons ] = optimize ( parameters )
-
-%% Optimize
-
-% set up
-price_coeffs_est = [3.7*ones(1,26), -ones(1,24)*0.1];     % Make a starting guess at the solution
-options = optimoptions(@fmincon,'MaxFunctionEvaluations', 500000, ...
-    'MaxIterations', 2000, 'Algorithm', 'interior-point');
-
-objcons = @(obj_vars) constraints(obj_vars, parameters);
-
-objfunc = @(obj_vars) obj_f(obj_vars, parameters);
-
-
-[optimal_vars, optimal_val] = fmincon(@(obj_vars) objfunc(obj_vars), ...
-    price_coeffs_est, [],[],[],[],[zeros(1,26), ones(1,24)*-10],[], ...
-    @(obj_vars) objcons(obj_vars), options);
-
-
-
-end

### 2019-06-19 code/matlab/simulation_july10/constraints.m

@@ -1,47 +1,0 @@
-function [ c, ceq ] = constraints( x_1, x_2, parameters )
-
-xi_1   = parameters.xi_1; 
-xi_2_t = parameters.xi_2_t;
-xi_2_s = parameters.xi_2_s;
-alpha  = parameters.alpha;
-beta   = parameters.beta;
-budget = parameters.budget;
-p_1    = parameters.p_1;
-p_2    = parameters.p_2;
-
-% profit first-order max
-p_t = -(p_2*xi_1 - p_1*xi_2_s)/(xi_1*(xi_2_s - xi_2_t));
-p_s = (p_2*xi_1 - p_1*xi_2_t)/(xi_1*(xi_2_s - xi_2_t));
-
-% demand
-y_t_demand = alpha*budget/p_t;
-y_s_demand = beta*budget/p_s;
-
-% supply
-y_t_supply = xi_1*x_1 + xi_2_t*x_2;
-y_s_supply = xi_1*x_1 + xi_2_s*x_2;
-
-% output used
-y_t = min(y_t_supply, y_t_demand);
-y_s = min(y_s_supply, y_s_demand);
-
-cost_f = @(x_1, x_2) p_1*x_1 + p_2*x_2;
-
-
-%% <= constraints
-positive_output_y_t = -y_t;
-positive_output_y_s = -y_s;
-positive_profit = y_t*p_t + y_s*p_s - cost_f(x_1, x_2);
-c = [positive_output_y_t, positive_output_y_s, -positive_profit];
-
-
-%% == constraints
-budget_constraint = ((y_t*p_t + y_s*p_s) - budget).^2;
-eq_t = (y_t_demand - y_t_supply)^2;
-eq_s = (y_s_demand - y_s_supply)^2;
-
-ceq = [budget_constraint, eq_t, eq_s];
-
-
-end
-

### 2019-06-19 code/matlab/simulation_july10/main.m

@@ -1,155 +1,0 @@
-
-parameters.xi_1   = 4.00; 
-parameters.xi_2_t = 6;
-parameters.xi_2_s = 2;
-parameters.alpha  = 0.7;
-parameters.beta   = 0.3;
-parameters.budget = 100;
-parameters.p_1    = 0.5; 
-parameters.p_2    = 0.5; 
-
-debug = true;
-
-
-%% Optimize
-
-[ optimal_vars, optimal_val, objfunc, objcons, p_t, p_s, y_t, y_s ] = optimize ( parameters, debug );
-
-
-%% Load results
-
-% exog
-xi_1   = parameters.xi_1; 
-xi_2_t = parameters.xi_2_t;
-xi_2_s = parameters.xi_2_s;
-alpha  = parameters.alpha;
-beta   = parameters.beta;
-budget = parameters.budget;
-p_1    = parameters.p_1;
-p_2    = parameters.p_2;
-
-% endog
-x_1 = optimal_vars(1);
-x_2 = optimal_vars(2);
-
-
-%% Check results
-
-%%% objectives
-profit = (y_t*p_t + y_s*p_s) - (p_1*x_1 + p_2*x_2);
-utility = (y_t^alpha + y_s^beta);
-
-disp('')
-fprintf('\nProfit: %f\n', profit)
-fprintf('Utility: %f\n', utility)
-
-
-%% Parameter effects params
-
-delta = 0.001;
-xi_1_init = 4;
-xi_2_t_init = 6;
-xi_2_s_init = 2;
-
-
-%% Parameter effects: xi_1
-
-parameters.xi_1 = xi_1_init;
-
-[ optimal_vars, optimal_val, objfunc, objcons, p_t, p_s, y_t, y_s ] = ...
-    optimize ( parameters, debug );
-
-x_1_temp = optimal_vars(1);
-x_2_temp = optimal_vars(2);
-y_t_temp = y_t;
-y_s_temp = y_s;
-
-parameters.xi_1 = xi_1_init + delta;
-
-[ optimal_vars, optimal_val, objfunc, objcons, p_t, p_s, y_t, y_s ] = ...
-    optimize ( parameters, debug );
-
-x_1 = optimal_vars(2);
-x_2 = optimal_vars(2);
-
-disp('Derivatives of [x_1, x_2, y_t, y_s]')
-[(x_1 - x_1_temp)/delta (x_2 - x_2_temp)/delta ...
[…]

### 2019-06-19 code/matlab/simulation_july10/obj_f.m

@@ -1,51 +1,0 @@
-function [ obj_value ] = obj_f ( x_1, x_2, parameters )
-
-xi_1   = parameters.xi_1; 
-xi_2_t = parameters.xi_2_t;
-xi_2_s = parameters.xi_2_s;
-alpha  = parameters.alpha;
-beta   = parameters.beta;
-budget = parameters.budget;
-p_1    = parameters.p_1;
-p_2    = parameters.p_2;
-
-
-% profit first-order max
-p_t = -(p_2*xi_1 - p_1*xi_2_s)/(xi_1*(xi_2_s - xi_2_t));
-p_s = (p_2*xi_1 - p_1*xi_2_t)/(xi_1*(xi_2_s - xi_2_t));
-
-% demand
-y_t_demand = alpha*budget/p_t;
-y_s_demand = beta*budget/p_s;
-
-% supply
-y_t_supply = xi_1*x_1 + xi_2_t*x_2;
-y_s_supply = xi_1*x_1 + xi_2_s*x_2;
-
-% output used
-y_t = min(y_t_supply, y_t_demand);
-y_s = min(y_s_supply, y_s_demand);
-
-
-cost_f = @(x_1, x_2) p_1*x_1 + p_2*x_2;
-
-
-% utility max
-% umax_t = y_t - alpha*budget/p_t;
-% umax_s = y_s - beta*budget/p_s;
-
-profit = (y_t*p_t + y_s*p_s) - cost_f(x_1, x_2);
-utility = y_t^alpha * y_s*beta;
-
-output_diff_t = (y_t_supply - y_t_demand).^2;
-output_diff_s = (y_s_supply - y_s_demand).^2;
-
-%obj_value = pmax_1.^2 + pmax_2.^2 + umax_t.^2 + umax_s.^2;
-
-obj_value = -profit;
-
-
-
-
-
-end

### 2019-06-19 code/matlab/simulation_july10/optimize.m

@@ -1,63 +1,0 @@
-function [ optimal_vars, optimal_val, objfunc, objcons, ...
-    p_t, p_s, y_t, y_s ] = optimize ( parameters, debug )
-
-%% Optimize
-
-% set up
-x0 = [1 1];     % Make a starting guess at the solution
-options = optimoptions(@fmincon,'MaxFunctionEvaluations', 6000);
-
-objcons = @(obj_vars) constraints(obj_vars(1), obj_vars(2), parameters);
-
-objfunc = @(obj_vars) obj_f(obj_vars(1), obj_vars(2), parameters);
-
-if ~debug
-    [optimal_vars, optimal_val] = fmincon(@(obj_vars) objfunc(obj_vars), ...
-        x0,[],[],[],[],[0 0],[],@(obj_vars) objcons(obj_vars), options);
-else
-    
-    xi_1   = parameters.xi_1; 
-    xi_2_t = parameters.xi_2_t;
-    xi_2_s = parameters.xi_2_s;
-    alpha  = parameters.alpha;
-    beta   = parameters.beta;
-    budget = parameters.budget;
-    p_1    = parameters.p_1;
-    p_2    = parameters.p_2;
-    
-    % profit first-order max
-    p_t = -(p_2*xi_1 - p_1*xi_2_s)/(xi_1*(xi_2_s - xi_2_t));
-    p_s = (p_2*xi_1 - p_1*xi_2_t)/(xi_1*(xi_2_s - xi_2_t));
-    
-    % utility first-order max
-    y_t = alpha*budget/p_t;
-    y_s = beta*budget/p_s;
-    
-    % solutions for x
-    x_2 = (y_t - y_s)/(xi_2_t - xi_2_s);
-    x_1 = (y_t - xi_2_t*x_2)/xi_1;
-    
-    optimal_vars = [x_1, x_2];
-    optimal_val = 0;
-    
-end
-
-%% Info
-
-xi_1   = parameters.xi_1; 
-xi_2_t = parameters.xi_2_t;
-xi_2_s = parameters.xi_2_s;
-alpha  = parameters.alpha;
-beta   = parameters.beta;
-budget = parameters.budget;
-p_1    = parameters.p_1;
-p_2    = parameters.p_2;
-
-x_1 = optimal_vars(1);
-x_2 = optimal_vars(2);
[…]

### 2019-06-19 code/matlab/simulation_july21/constraints.m

@@ -1,53 +1,0 @@
-function [ c, ceq ] = constraints( price_coeffs, parameters )
-
-
-%% Unpack
-
-% funcs
-alpha = parameters.alpha;
-xi_1  = parameters.xi_1;
-xi_2  = parameters.xi_2;
-
-% constants
-phi   = parameters.phi;
-sigma = 1/(1-phi);
-budget = parameters.budget;
-
-
-%% Condition
-
-% price
-poly_coeffs = polyfit(linspace(0,1,7), price_coeffs, 6);
-p = @(t) poly_coeffs(1).*(t.^6) +  poly_coeffs(2).*(t.^5) + poly_coeffs(3).*(t.^4) + ...
-    poly_coeffs(4).*(t.^3) + poly_coeffs(5).*(t.^2) + ...
-    poly_coeffs(6).*(t.^1) + poly_coeffs(7).*(t.^0);
-price_positive = sum(p(linspace(0,1,100)) > 0) == 100;
-price_coeffs_positive = sum(price_coeffs > 0) == length(price_coeffs);
-
-% budget
-X_1 = integral(@(t) xi_1(t).*p(t), 0, 1);
-X_2 = integral(@(t) xi_2(t).*p(t), 0, 1);
-
-Y = @(t) xi_1(t).*X_1 + xi_2(t).*X_2;
-I = integral(@(t) p(t).*Y(t), 0, 1);
-
-% price index
-P = integral(@(t) p(t).^(1-sigma) .* alpha(t).^sigma, 0, 1).^(1/(1-sigma));
-Y_demand = @(t) ((p(t)./alpha(t)).^(-sigma)) .* (P.^(1-sigma));
-
-
-
-%% <= constraints
-
-budget_constraint = I - budget;
-
-c = [budget_constraint];
-
-
-%% == constraints
-
-ceq = [1 - price_positive, 1 - price_coeffs_positive];
-
-
-end
-

### 2019-06-19 code/matlab/simulation_july21/main.m

@@ -1,103 +1,0 @@
-
-%%%%%%% Doesn't work well %%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Parameters
-
-parameters.alpha = @(t) 1.75-(2.*t-1).^2/2;
-parameters.xi_1  = @(t) 1.5 + 0.*t;
-parameters.xi_2  = @(t) 1.9869 - 0.6816*(t-0.5) - 8.764*(t-.5).^2 + 4.089*(t-0.5).^2;
-
-figure; hold on;
-fplot(parameters.alpha, [0 1])
-fplot(parameters.xi_1, [0 1])
-fplot(parameters.xi_2, [0 1])
-hold off;
-
-parameters.phi =  2;
-parameters.budget = 100;
-
-
-%% Optimize
-
-disp('Optimizing...')
-[ optimal_vars, optimal_val, objfunc, objcons ] = optimize ( parameters )
-
-
-%% Get results
-
-price_coeffs = optimal_vars;
-
-alpha = parameters.alpha;
-xi_1  = parameters.xi_1;
-xi_2  = parameters.xi_2;
-
-phi   = parameters.phi;
-sigma = 1 / (1-phi);
-
-poly_coeffs = polyfit(linspace(0,1,7), price_coeffs, 6);
-p = @(t) poly_coeffs(1).*(t.^6) +  poly_coeffs(2).*(t.^5) + poly_coeffs(3).*(t.^4) + ...
-    poly_coeffs(4).*(t.^3) + poly_coeffs(5).*(t.^2) + ...
-    poly_coeffs(6).*(t.^1) + poly_coeffs(7).*(t.^0);
-X_1 = integral(@(t) xi_1(t).*p(t), 0, 1);
-X_2 = integral(@(t) xi_2(t).*p(t), 0, 1);
-
-Y = @(t) xi_1(t).*X_1 + xi_2(t).*X_2;
-U = (integral(@(t) alpha(t).*(Y(t).^phi), 0, 1).^(1/phi));
-I = integral(@(t) p(t).*Y(t), 0, 1);
-
-P = integral(@(t) p(t).^(1-sigma) .* alpha(t).^sigma, 0, 1).^(1/(1-sigma));
-Y_demand = @(t) ((p(t)./alpha(t)).^(-sigma)) .* (P.^(1-sigma));
-
-
-%%
-
-fplot(p, [0 1])
-
-
-%% Output
[…]

### 2019-06-19 code/matlab/simulation_july21/obj_f.m

@@ -1,37 +1,0 @@
-function [ obj_value ] = obj_f ( price_coeffs, parameters )
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Unpack parameters
-
-alpha = parameters.alpha;
-xi_1  = parameters.xi_1;
-xi_2  = parameters.xi_2;
-
-phi   = parameters.phi;
-sigma = 1 / (1-phi);
-
-%% Find utility
-
-poly_coeffs = polyfit(linspace(0,1,7), price_coeffs, 6);
-p = @(t) poly_coeffs(1).*(t.^6) +  poly_coeffs(2).*(t.^5) + poly_coeffs(3).*(t.^4) + ...
-    poly_coeffs(4).*(t.^3) + poly_coeffs(5).*(t.^2) + ...
-    poly_coeffs(6).*(t.^1) + poly_coeffs(7).*(t.^0);
-
-X_1 = integral(@(t) xi_1(t).*p(t), 0, 1);
-X_2 = integral(@(t) xi_2(t).*p(t), 0, 1);
-
-Y = @(t) xi_1(t).*X_1 + xi_2(t).*X_2;
-U = (integral(@(t) alpha(t).*(Y(t).^phi), 0, 1).^(1/phi));
-
-% price index
-P = integral(@(t) p(t).^(1-sigma) .* alpha(t).^sigma, 0, 1).^(1/(1-sigma));
-Y_demand = @(t) ((p(t)./alpha(t)).^(-sigma)) .* (P.^(1-sigma));
-
-% quantity mismatch
-q_diff = @(t) (3.*(Y(t) - Y_demand(t))).^4;
-q_diff_total = integral(q_diff, 0, 1);
-
-obj_value = 1*q_diff_total;
-
-
-end

### 2019-06-19 code/matlab/simulation_july21/optimize.m

@@ -1,20 +1,0 @@
-function [ optimal_vars, optimal_val, objfunc, objcons ] = optimize ( parameters )
-
-%% Optimize
-
-% set up
-price_coeffs_est = [1 1 1 1 1 1 1]/3;     % Make a starting guess at the solution
-options = optimoptions(@fmincon,'MaxFunctionEvaluations', 5000, 'Algorithm', 'interior-point');
-
-objcons = @(obj_vars) constraints(obj_vars, parameters);
-
-objfunc = @(obj_vars) obj_f(obj_vars, parameters);
-
-
-[optimal_vars, optimal_val] = fmincon(@(obj_vars) objfunc(obj_vars), ...
-    price_coeffs_est, [],[],[],[],[1 1 1 1 1 1 1]/100,[], ...
-    @(obj_vars) objcons(obj_vars), options);
-
-
-
-end

### 2019-06-19 code/matlab/simulation_july22/constraints.m

@@ -1,53 +1,0 @@
-function [ c, ceq ] = constraints( price_coeffs, parameters )
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Unpack
-
-% funcs
-alpha = parameters.alpha;
-xi_1  = parameters.xi_1;
-xi_2  = parameters.xi_2;
-
-% prices
-x_1_cost_param = parameters.x_1_cost_param;
-x_2_cost_param = parameters.x_2_cost_param;
-
-% constants
-phi   = parameters.phi;
-sigma = 1/(1-phi);
-budget = parameters.budget;
-
-
-%% Condition
-
-% price
-price_coeffs_positive = sum(price_coeffs > 0) == length(price_coeffs);
-
-% 
-X_1 = (1/x_1_cost_param)*xi_1(linspace(0,1,24))*price_coeffs'/24;
-X_2 = (1/x_2_cost_param)*xi_2(linspace(0,1,24))*price_coeffs'/24;
-
-Y = (1/24)*(xi_1(linspace(0,1,24))*X_1 + xi_2(linspace(0,1,24))*X_2);
-I = price_coeffs*Y'/24;
-
-% price index
-P = ((1/24)*(price_coeffs.^(1-sigma))*(alpha(linspace(0,1,24))'.^sigma)).^(1/(1-sigma));
-Y_demand = ((price_coeffs./(alpha(linspace(0,1,24)))).^(-sigma)) .* (P.^(1-sigma));
-
-
-
-%% <= constraints
-
-budget_constraint = I - budget;
-
-c = [budget_constraint];
-
-
-%% == constraints
-
-ceq = [1 - price_coeffs_positive];
-
-
-end
-

### 2019-06-19 code/matlab/simulation_july22/main.m

@@ -1,121 +1,0 @@
-
-%%%%% Time period is from 0 to 1  %%%%%
-%%%%% Broken up into 24 hr chunks %%%%%
-
-
-%% Parameters
-
-parameters.alpha = @(t) 1.75-(2.*t-1).^2/2;
-parameters.xi_1  = @(t) cos(t.*3-2)/2 + 1.5;
-parameters.xi_2  = @(t) sin(t.*6-.5)/2 + 1.5;
-
-parameters.phi =  2;
-parameters.budget = 1;
-
-parameters.x_1_cost_param = 0.6;
-parameters.x_2_cost_param = 1;
-
-% plots
-figure;
- 
-subplot(2,1,1); 
-fplot(parameters.alpha, [0 1])
-title('\alpha')
-
-subplot(2,1,2); hold on; 
-fplot(parameters.xi_1, [0 1])
-fplot(parameters.xi_2, [0 1])
-title('Conversion Rates')
-legend('\xi_1', '\xi_2')
-ylabel('Energy per Input Unit')
-xlabel('Time')
-
-
-
-%% Optimize
-
-disp('Optimizing...')
-[ optimal_vars, optimal_val, objfunc, objcons ] = optimize ( parameters );
-
-
-%% Get results
-
-% unpack params
-price_coeffs = optimal_vars;
-
-alpha = parameters.alpha;
-xi_1  = parameters.xi_1;
-xi_2  = parameters.xi_2;
-
-% 
-x_1_cost_param = parameters.x_1_cost_param;
-x_2_cost_param = parameters.x_2_cost_param;
-
-phi   = parameters.phi;
-sigma = 1 / (1-phi);
-
-% 
-price_coeffs_positive = sum(price_coeffs > 0) == length(price_coeffs);
-
-X_1 = (1/x_1_cost_param)*xi_1(linspace(0,1,24))*price_coeffs'/24;
-X_2 = (1/x_2_cost_param)*xi_2(linspace(0,1,24))*price_coeffs'/24;
-
-Y = (1/24)*(xi_1(linspace(0,1,24))*X_1 + xi_2(linspace(0,1,24))*X_2);
-I = price_coeffs*Y'/24;
-
-% price index
-P = ((1/24)*(price_coeffs.^(1-sigma))*(alpha(linspace(0,1,24))'.^sigma)).^(1/(1-sigma));
-
[…]

### 2019-06-19 code/matlab/simulation_july22/obj_f.m

@@ -1,45 +1,0 @@
-function [ obj_value ] = obj_f ( price_coeffs, parameters )
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Unpack parameters
-
-% funcs
-alpha = parameters.alpha;
-xi_1  = parameters.xi_1;
-xi_2  = parameters.xi_2;
-
-% prices
-x_1_cost_param = parameters.x_1_cost_param;
-x_2_cost_param = parameters.x_2_cost_param;
-
-% constants
-phi   = parameters.phi;
-sigma = 1/(1-phi);
-budget = parameters.budget;
-
-
-%% Find utility
-
-% price
-price_coeffs_positive = sum(price_coeffs > 0) == length(price_coeffs);
-
-% 
-X_1 = (1/x_1_cost_param)*xi_1(linspace(0,1,24))*price_coeffs'/24;
-X_2 = (1/x_2_cost_param)*xi_2(linspace(0,1,24))*price_coeffs'/24;
-
-Y = (1/24)*(xi_1(linspace(0,1,24))*X_1 + xi_2(linspace(0,1,24))*X_2);
-I = price_coeffs*Y'/24;
-
-% price index
-P = ((1/24)*(price_coeffs.^(1-sigma))*(alpha(linspace(0,1,24))'.^sigma)).^(1/(1-sigma));
-Y_demand = ((price_coeffs./(alpha(linspace(0,1,24)))).^(-sigma)) .* (P.^(1-sigma));
-U = (1/24)*(alpha(linspace(0,1,24))*(Y.^phi)').^(1/phi);
-
-% quantity mismatch
-q_diff = (7.*(Y - Y_demand)).^2;
-q_diff_total = sum(q_diff)/24;
-
-obj_value = 1*q_diff_total;
-
-
-end

### 2019-06-19 code/matlab/simulation_july22/optimize.m

@@ -1,20 +1,0 @@
-function [ optimal_vars, optimal_val, objfunc, objcons ] = optimize ( parameters )
-
-%% Optimize
-
-% set up
-price_coeffs_est = ones(1,24);     % Make a starting guess at the solution
-options = optimoptions(@fmincon,'MaxFunctionEvaluations', 5000, 'Algorithm', 'interior-point');
-
-objcons = @(obj_vars) constraints(obj_vars, parameters);
-
-objfunc = @(obj_vars) obj_f(obj_vars, parameters);
-
-
-[optimal_vars, optimal_val] = fmincon(@(obj_vars) objfunc(obj_vars), ...
-    price_coeffs_est, [],[],[],[],zeros(1,24),[], ...
-    @(obj_vars) objcons(obj_vars), options);
-
-
-
-end

### 2019-06-19 code/matlab/simulation_july31/constraints.m

@@ -1,55 +1,0 @@
-function [ c, ceq ] = constraints( opt_coeffs, parameters )
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Unpack
-
-% funcs
-alpha = parameters.alpha;
-xi_1  = parameters.xi_1;
-xi_2  = parameters.xi_2;
-
-% prices
-price_coeffs = opt_coeffs(1:24);
-x_1_cost_param = parameters.x_1_cost_param;
-x_2_cost_param = parameters.x_2_cost_param;
-
-% constants
-phi   = parameters.phi;
-sigma = 1/(1-phi);
-budget = parameters.budget;
-
-
-%% Condition
-
-% price
-price_coeffs_positive = sum(price_coeffs > 0) == length(price_coeffs);
-
-% 
-X_1 = opt_coeffs(25);%(1/x_1_cost_param)*xi_1(linspace(0,1,24))*price_coeffs'/24;
-X_2 = opt_coeffs(26);%(1/x_2_cost_param)*xi_2(linspace(0,1,24))*price_coeffs'/24;
-
-Y = (1/24)*(xi_1(linspace(0,1,24))*X_1 + xi_2(linspace(0,1,24))*X_2);
-I = price_coeffs*Y'/24;
-
-% price index
-P = ((1/24)*(price_coeffs.^(1-sigma))*(alpha(linspace(0,1,24))'.^sigma)).^(1/(1-sigma));
-Y_demand = ((price_coeffs./(alpha(linspace(0,1,24)))).^(-sigma)) .* (P.^(1-sigma));
-
-
-
-%% <= constraints
-
-budget_constraint = I - budget;
-budget_constraint2 = (x_1_cost_param*X_1 + x_2_cost_param*X_2) - budget;
-
-c = [budget_constraint, budget_constraint2, ];
-
-
-%% == constraints
-
-ceq = [1 - price_coeffs_positive];
-
-
-end
-

### 2019-06-19 code/matlab/simulation_july31/main.m

@@ -1,121 +1,0 @@
-
-%%%%% Time period is from 0 to 1  %%%%%
-%%%%% Broken up into 24 hr chunks %%%%%
-
-
-%% Parameters
-
-parameters.alpha = @(t) 1.75-(2.*t-1).^2/2;
-parameters.xi_1  = @(t) 0.*t+1;%sin(t.*6-.5)/2 + 1.5;
-parameters.xi_2  = @(t) cos(t.*3-2)/2 + 1.5;
-
-parameters.phi = 0.5;
-parameters.budget = 1;
-
-parameters.x_1_cost_param = 0.9;
-parameters.x_2_cost_param = 1;
-
-% plots
-figure;
- 
-subplot(2,1,1); 
-fplot(parameters.alpha, [0 1])
-title('\alpha')
-
-subplot(2,1,2); hold on; 
-fplot(parameters.xi_1, [0 1])
-fplot(parameters.xi_2, [0 1])
-title('Conversion Rates')
-legend('\xi_1', '\xi_2')
-ylabel('Energy per Input Unit')
-xlabel('Time')
-
-
-
-%% Optimize
-
-disp('Optimizing...')
-[ optimal_vars, optimal_val, objfunc, objcons ] = optimize ( parameters );
-
-
-%% Get results
-
-% unpack params
-price_coeffs = optimal_vars(1:24);
-
-alpha = parameters.alpha;
-xi_1  = parameters.xi_1;
-xi_2  = parameters.xi_2;
-
-% 
-x_1_cost_param = parameters.x_1_cost_param;
-x_2_cost_param = parameters.x_2_cost_param;
-
-phi   = parameters.phi;
-sigma = 1 / (1-phi);
-
-% 
-price_coeffs_positive = sum(price_coeffs > 0) == length(price_coeffs);
-
-X_1 = optimal_vars(25);
-X_2 = optimal_vars(26);
-
-Y = (1/24)*(xi_1(linspace(0,1,24))*X_1 + xi_2(linspace(0,1,24))*X_2);
-I = price_coeffs*Y'/24;
-
-% price index
-P = ((1/24)*(price_coeffs.^(1-sigma))*(alpha(linspace(0,1,24))'.^sigma)).^(1/(1-sigma));
-
-Y_demand = ((price_coeffs./(alpha(linspace(0,1,24)))).^(-sigma)) .* (P.^(1-sigma));
[…]

### 2019-06-19 code/matlab/simulation_july31/obj_f.m

@@ -1,47 +1,0 @@
-function [ obj_value ] = obj_f ( opt_coeffs, parameters )
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Unpack parameters
-
-% funcs
-alpha = parameters.alpha;
-xi_1  = parameters.xi_1;
-xi_2  = parameters.xi_2;
-
-% prices
-price_coeffs = opt_coeffs(1:24);
-x_1_cost_param = parameters.x_1_cost_param;
-x_2_cost_param = parameters.x_2_cost_param;
-
-% constants
-phi   = parameters.phi;
-sigma = 1/(1-phi);
-budget = parameters.budget;
-
-
-%% Find utility
-
-% price
-price_coeffs_positive = sum(price_coeffs > 0) == length(price_coeffs);
-
-% 
-X_1 = opt_coeffs(25);%(1/x_1_cost_param)*xi_1(linspace(0,1,24))*price_coeffs'/24;
-X_2 = opt_coeffs(26);%(1/x_2_cost_param)*xi_2(linspace(0,1,24))*price_coeffs'/24;
-
-Y = (1/24)*(xi_1(linspace(0,1,24))*X_1 + xi_2(linspace(0,1,24))*X_2);
-I = price_coeffs*Y'/24;
-
-% price index
-P = ((1/24)*(price_coeffs.^(1-sigma))*(alpha(linspace(0,1,24))'.^sigma)).^(1/(1-sigma));
-Y_demand = ((price_coeffs./(alpha(linspace(0,1,24)))).^(-sigma)) .* (P.^(1-sigma));
-U = (1/24)*(alpha(linspace(0,1,24))*(Y.^phi)').^(1/phi);
-
-% quantity mismatch
-q_diff = (20.*(Y - Y_demand)).^2;
-q_diff_total = sum(q_diff)/24;
-
-obj_value = 2*q_diff_total;
-
-
-end

### 2019-06-19 code/matlab/simulation_july31/optimize.m

@@ -1,21 +1,0 @@
-function [ optimal_vars, optimal_val, objfunc, objcons ] = optimize ( parameters )
-
-%% Optimize
-
-% set up
-price_coeffs_est = ones(1,26);     % Make a starting guess at the solution
-options = optimoptions(@fmincon,'MaxFunctionEvaluations', ...
-    5000, 'Algorithm', 'interior-point');
-
-objcons = @(obj_vars) constraints(obj_vars, parameters);
-
-objfunc = @(obj_vars) obj_f(obj_vars, parameters);
-
-
-[optimal_vars, optimal_val] = fmincon(@(obj_vars) objfunc(obj_vars), ...
-    price_coeffs_est, [],[],[],[],zeros(1,26),[], ...
-    @(obj_vars) objcons(obj_vars), options);
-
-
-
-end

### 2019-06-19 code/matlab/simulation_july31_c/constraints.m

@@ -1,55 +1,0 @@
-function [ c, ceq ] = constraints( opt_coeffs, parameters )
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Unpack
-
-% funcs
-alpha = parameters.alpha;
-xi_1  = parameters.xi_1;
-xi_2  = parameters.xi_2;
-
-% prices
-% price_coeffs = opt_coeffs(1:24);
-x_1_cost_param = parameters.x_1_cost_param;
-x_2_cost_param = parameters.x_2_cost_param;
-
-% constants
-phi   = parameters.phi;
-sigma = 1/(1-phi);
-budget = parameters.budget;
-
-
-%% Condition
-
-% price
-% price_coeffs_positive = sum(price_coeffs > 0) == length(price_coeffs);
-
-% 
-X_1 = opt_coeffs(1);%(1/x_1_cost_param)*xi_1(linspace(0,1,24))*price_coeffs'/24;
-X_2 = opt_coeffs(2);%(1/x_2_cost_param)*xi_2(linspace(0,1,24))*price_coeffs'/24;
-
-Y = (1/24)*(xi_1(linspace(0,1,24))*X_1 + xi_2(linspace(0,1,24))*X_1);
-% I = price_coeffs*Y'/24;
-
-% price index
-% P = ((1/24)*(price_coeffs.^(1-sigma))*(alpha(linspace(0,1,24))'.^sigma)).^(1/(1-sigma));
-% Y_demand = ((price_coeffs./(alpha(linspace(0,1,24)))).^(-sigma)) .* (P.^(1-sigma));
-
-
-
-%% <= constraints
-
-% budget_constraint = I - budget;
-budget_constraint2 = (x_1_cost_param*X_1 + x_2_cost_param*X_2) - budget;
-
-c = [budget_constraint2];
-
-
-%% == constraints
-
-ceq = [ ];
-
-
-end
-

### 2019-06-19 code/matlab/simulation_july31_c/main.m

@@ -1,121 +1,0 @@
-
-%%%%% Time period is from 0 to 1  %%%%%
-%%%%% Broken up into 24 hr chunks %%%%%
-
-
-%% Parameters
-
-parameters.alpha = @(t) 1.75-(2.*t-1).^2/2;
-parameters.xi_1  = @(t) 2*t.^1+2.5;% cos(t.*3-2)/2 + 1.5;
-parameters.xi_2  = @(t) 2-2*t.^1+3;%sin(t.*6-.5)/2 + 1.5;
-
-parameters.phi =  2;
-parameters.budget = 1;
-
-parameters.x_1_cost_param = 1;
-parameters.x_2_cost_param = 1.13934865804215;
-
-% plots
-figure;
- 
-subplot(2,1,1); 
-fplot(parameters.alpha, [0 1])
-title('\alpha')
-
-subplot(2,1,2); hold on; 
-fplot(parameters.xi_1, [0 1])
-fplot(parameters.xi_2, [0 1])
-title('Conversion Rates')
-legend('\xi_1', '\xi_2')
-ylabel('Energy per Input Unit')
-xlabel('Time')
-
-
-
-%% Optimize
-
-disp('Optimizing...')
-[ optimal_vars, optimal_val, objfunc, objcons ] = optimize ( parameters );
-
-
-%% Get results
-
-% unpack params
-% price_coeffs = optimal_vars(1:24);
-
-alpha = parameters.alpha;
-xi_1  = parameters.xi_1;
-xi_2  = parameters.xi_2;
-
-% 
-x_1_cost_param = parameters.x_1_cost_param;
-x_2_cost_param = parameters.x_2_cost_param;
-
-phi   = parameters.phi;
-sigma = 1 / (1-phi);
-
-% 
-%price_coeffs_positive = sum(price_coeffs > 0) == length(price_coeffs);
-
-X_1 = optimal_vars(1);
-X_2 = optimal_vars(2);
-
-Y = (1/24)*(xi_1(linspace(0,1,24))*X_1 + xi_2(linspace(0,1,24))*X_2);
-% I = price_coeffs*Y'/24;
-
-% price index
-% P = ((1/24)*(price_coeffs.^(1-sigma))*(alpha(linspace(0,1,24))'.^sigma)).^(1/(1-sigma));
-
-%Y_demand = ((price_coeffs./(alpha(linspace(0,1,24)))).^(-sigma)) .* (P.^(1-sigma));
[…]

### 2019-06-19 code/matlab/simulation_july31_c/obj_f.m

@@ -1,46 +1,0 @@
-function [ obj_value ] = obj_f ( opt_coeffs, parameters )
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Unpack parameters
-
-% funcs
-alpha = parameters.alpha;
-xi_1  = parameters.xi_1;
-xi_2  = parameters.xi_2;
-
-% prices
-% price_coeffs = opt_coeffs(1:24);
-x_1_cost_param = parameters.x_1_cost_param;
-x_2_cost_param = parameters.x_2_cost_param;
-
-% constants
-phi   = parameters.phi;
-sigma = 1/(1-phi);
-budget = parameters.budget;
-
-
-%% Find utility
-
-% price
-% price_coeffs_positive = sum(price_coeffs > 0) == length(price_coeffs);
-
-% 
-X_1 = opt_coeffs(1);%(1/x_1_cost_param)*xi_1(linspace(0,1,24))*price_coeffs'/24;
-X_2 = opt_coeffs(2);%(1/x_2_cost_param)*xi_2(linspace(0,1,24))*price_coeffs'/24;
-
-Y = (1/24)*(xi_1(linspace(0,1,24))*X_1 + xi_2(linspace(0,1,24))*X_2);
-% I = price_coeffs*Y'/24;
-% 
-% % price index
-% P = ((1/24)*(price_coeffs.^(1-sigma))*(alpha(linspace(0,1,24))'.^sigma)).^(1/(1-sigma));
-% Y_demand = ((price_coeffs./(alpha(linspace(0,1,24)))).^(-sigma)) .* (P.^(1-sigma));
-U = (1/24)*(alpha(linspace(0,1,24))*(Y.^phi)').^(1/phi);
-
-% quantity mismatch
-% q_diff = (100.*(Y - Y_demand)).^4;
-% q_diff_total = sum(q_diff)/24;
-
-obj_value = -U;%1*q_diff_total;
-
-
-end

### 2019-06-19 code/matlab/simulation_july31_c/optimize.m

@@ -1,20 +1,0 @@
-function [ optimal_vars, optimal_val, objfunc, objcons ] = optimize ( parameters )
-
-%% Optimize
-
-% set up
-price_coeffs_est = [1 1];     % Make a starting guess at the solution
-options = optimoptions(@fmincon,'MaxFunctionEvaluations', 5000, 'Algorithm', 'interior-point');
-
-objcons = @(obj_vars) constraints(obj_vars, parameters);
-
-objfunc = @(obj_vars) obj_f(obj_vars, parameters);
-
-
-[optimal_vars, optimal_val] = fmincon(@(obj_vars) objfunc(obj_vars), ...
-    price_coeffs_est, [],[],[],[],zeros(1,2),[], ...
-    @(obj_vars) objcons(obj_vars), options);
-
-
-
-end

### 2019-06-19 code/matlab/simulation_july7/constraints.m

@@ -1,43 +1,0 @@
-function [ c, ceq ] = constraints( p_t, p_s, parameters )
-
-xi_1   = parameters.xi_1; 
-xi_2_t = parameters.xi_2_t;
-xi_2_s = parameters.xi_2_s;
-alpha  = parameters.alpha;
-beta   = parameters.beta;
-budget = parameters.budget;
-p_1    = parameters.p_1;
-p_2    = parameters.p_2;
-
-% supply
-x_1 = (2*p_1)^(-1)*(p_t*xi_1 + p_s*xi_1);
-x_2 = (2*p_2)^(-1)*(p_t*xi_2_t + p_s*xi_2_s);
-y_t_supply = xi_1*x_1 + xi_2_t*x_2;
-y_s_supply = xi_1*x_1 + xi_2_s*x_2;
-
-% demand
-y_t_demand = alpha*budget/p_t;
-y_s_demand = beta*budget/p_s;
-
-% output used
-y_t = min(y_t_supply, y_t_demand);
-y_s = min(y_s_supply, y_s_demand);
-
-
-%% <= constraints
-positive_output_y_t = -y_t;
-positive_output_y_s = -y_s;
-positive_profit = y_t*p_t + y_s*p_s - (p_1*x_1^2 + p_2*x_2^2);
-c = [positive_output_y_t, positive_output_y_s, -positive_profit];
-
-
-%% == constraints
-budget_constraint = ((y_t*p_t + y_s*p_s) - budget).^2;
-sd_t = p_s*(xi_1^2 + xi_2_s*xi_2_t) + p_t*(xi_1^2 + xi_2_t^2) - alpha*budget/p_t;
-sd_s = p_t*(xi_1^2 + xi_2_s*xi_2_t) + p_s*(xi_1^2 + xi_2_s^2) - beta*budget/p_s;
-
-ceq = [budget_constraint, sd_t, sd_s];
-
-
-end
-

### 2019-06-19 code/matlab/simulation_july7/main.m

@@ -1,154 +1,0 @@
-
-parameters.xi_1   = 4.0001; 
-parameters.xi_2_t = 6;
-parameters.xi_2_s = 2;
-parameters.alpha  = 0.3;
-parameters.beta   = 0.7;
-parameters.budget = 100;
-parameters.p_1    = 0.5; % not used
-parameters.p_2    = 0.5; % not used
-
-
-%% Optimize
-
-[ optimal_vars, optimal_val, objfunc, objcons, x_1, x_2, y_t, y_s ] = optimize ( parameters );
-
-
-%% Load results
-
-% exog
-xi_1   = parameters.xi_1; 
-xi_2_t = parameters.xi_2_t;
-xi_2_s = parameters.xi_2_s;
-alpha  = parameters.alpha;
-beta   = parameters.beta;
-budget = parameters.budget;
-p_1    = parameters.p_1;
-p_2    = parameters.p_2;
-
-% endog
-p_t = optimal_vars(1);
-p_s = optimal_vars(2);
-x_1 = (2*p_1)^(-1)*(p_t*xi_1 + p_s*xi_1);
-x_2 = (2*p_2)^(-1)*(p_t*xi_2_t + p_s*xi_2_s);
-
-
-%% Check results
-
-%%% objectives
-profit = (y_t*p_t + y_s*p_s) - (p_1*x_1^2 + p_2*x_2^2);
-utility = (y_t^alpha + y_s^beta);
-
-disp('')
-fprintf('\nProfit: %f\n', profit)
-fprintf('Utility: %f\n', utility)
-
-
-%% Parameter effects params
-
-delta = 0.001;
-xi_1_init = 4;
-xi_2_t_init = 6;
-xi_2_s_init = 2;
-
-
-%% Parameter effects: xi_1
-
-parameters.xi_1 = xi_1_init;
-
-[ optimal_vars, optimal_val, objfunc, objcons, x_1, x_2, y_t, y_s ] = ...
-    optimize ( parameters );
-
-x_1_temp = x_1;
-x_2_temp = x_2;
-y_t_temp = y_t;
-y_s_temp = y_s;
-
-parameters.xi_1 = xi_1_init + delta;
-
-[ optimal_vars, optimal_val, objfunc, objcons, x_1, x_2, y_t, y_s ] = ...
-    optimize ( parameters );
-
-[(x_1 - x_1_temp)/delta (x_2 - x_2_temp)/delta ...
[…]

### 2019-06-19 code/matlab/simulation_july7/obj_f.m

@@ -1,46 +1,0 @@
-function [ obj_value ] = obj_f ( p_t, p_s, parameters )
-
-xi_1   = parameters.xi_1; 
-xi_2_t = parameters.xi_2_t;
-xi_2_s = parameters.xi_2_s;
-alpha  = parameters.alpha;
-beta   = parameters.beta;
-budget = parameters.budget;
-p_1    = parameters.p_1;
-p_2    = parameters.p_2;
-
-
-% supply
-x_1 = (2*p_1)^(-1)*(p_t*xi_1 + p_s*xi_1);
-x_2 = (2*p_2)^(-1)*(p_t*xi_2_t + p_s*xi_2_s);
-y_t_supply = xi_1*x_1 + xi_2_t*x_2;
-y_s_supply = xi_1*x_1 + xi_2_s*x_2;
-
-% demand
-y_t_demand = alpha*budget/p_t;
-y_s_demand = beta*budget/p_s;
-
-% output used
-y_t = min(y_t_supply, y_t_demand);
-y_s = min(y_s_supply, y_s_demand);
-
-
-% utility max
-% umax_t = y_t - alpha*budget/p_t;
-% umax_s = y_s - beta*budget/p_s;
-
-profit = (y_t*p_t + y_s*p_s) - (p_1*x_1^2 + p_2*x_2^2);
-utility = y_t^alpha * y_s*beta;
-
-output_diff_t = (y_t_supply - y_t_demand).^2;
-output_diff_s = (y_s_supply - y_s_demand).^2;
-
-%obj_value = pmax_1.^2 + pmax_2.^2 + umax_t.^2 + umax_s.^2;
-
-obj_value = -utility;
-
-
-
-
-
-end

### 2019-06-19 code/matlab/simulation_july7/optimize.m

@@ -1,38 +1,0 @@
-function [ optimal_vars, optimal_val, objfunc, objcons, ...
-    x_1, x_2, y_t, y_s ] = optimize ( parameters )
-
-%% Optimize
-
-% set up
-x0 = [1 1];     % Make a starting guess at the solution
-%options = optimoptions(@fmincon,'Algorithm','sqp');
-
-objcons = @(obj_vars) constraints(obj_vars(1), obj_vars(2), parameters);
-
-objfunc = @(obj_vars) obj_f(obj_vars(1), obj_vars(2), parameters);
-
-[optimal_vars, optimal_val] = ... 
-    fmincon(@(obj_vars) objfunc(obj_vars),x0,[],[],[],[],[0 0],[],@(obj_vars) objcons(obj_vars));
-
-
-%% Info
-
-xi_1   = parameters.xi_1; 
-xi_2_t = parameters.xi_2_t;
-xi_2_s = parameters.xi_2_s;
-alpha  = parameters.alpha;
-beta   = parameters.beta;
-budget = parameters.budget;
-p_1    = parameters.p_1;
-p_2    = parameters.p_2;
-
-p_t = optimal_vars(1);
-p_s = optimal_vars(2);
-x_1 = (2*p_1)^(-1)*(p_t*xi_1 + p_s*xi_1);
-x_2 = (2*p_2)^(-1)*(p_t*xi_2_t + p_s*xi_2_s);
-y_t = xi_1*x_1 + xi_2_t*x_2;
-y_s = xi_1*x_1 + xi_2_s*x_2;
-
-[x_1 x_2, y_t, y_s];
-
-end

### 2019-06-19 code/matlab/solutions.m

@@ -1,124 +1,0 @@
-%%% Algebraic Solutions 
-
-syms xi_1_t xi_1_s xi_2_t xi_2_s p_1 p_2 p_t p_s x_1 x_2
-syms alpha beta budget y_t y_s
-syms sigma p_t_opt
-
-
-assume([p_t > 0, p_s > 0, alpha + beta == 1, alpha > 0, beta > 0, ...
-    alpha < 1, beta < 1, budget > 0, p_1 > 0, p_2 > 0, ...
-    xi_1_s > 0, xi_2_s > 0, xi_1_t > 0, xi_2_t > 0, sigma > 0, x_1 >= 0, x_2 >= 0])
-
-
-%% Profit maximization
-
-[x_1_prof, x_2_prof] = solve(p_t*xi_1_t + p_s*xi_1_s - 2*p_1*x_1 == 0 ,...
-                           p_t*xi_2_t + p_s*xi_2_s - 2*p_2*x_2 == 0, x_1, x_2)
-                       
-
-%% Utility max
-
-[x_1_util, x_2_util] = solve( ...
-    p_t == (alpha*budget)/(xi_1_t*x_1 + xi_2_t*x_2), ...
-    p_s == (beta*budget)/(xi_1_s*x_1 + xi_2_s*x_2), ...
-    ...%(alpha*budget)*(xi_1_t./(xi_1_t*x_1 + xi_2_t*x_2)) + (beta*budget)*(xi_1_s./(xi_1_s*x_1 + xi_2_s*x_2)) == 0, ...
-    ...%(alpha*budget)*(xi_2_t./(xi_1_t*x_1 + xi_2_t*x_2)) + (beta*budget)*(xi_2_s./(xi_1_s*x_1 + xi_2_s*x_2)) == 0, ...
-    (xi_1_t*x_1 + xi_2_t*x_2)*p_t + (xi_1_s*x_1 + xi_2_s*x_2)*p_s == budget, x_1, x_2)
-    
-               
-%% Central Planner Welfare maximization
-
-[x_1_cent, x_2_cent] = solve(...
-    [(alpha*budget)*(xi_1_t/(xi_1_t*x_1 + xi_2_t*x_2)) + (beta*budget)*(xi_1_s/(xi_1_s*x_1 + xi_2_s*x_2)) + ...
[…]

### 2019-06-21 documents/draft.tex
Update draft
- add contact info
- fix abstract key words and jel
- move references
- move figures and tables
- minor fixes

@@
-\documentclass[11pt,a4paper]{extarticle}
+\documentclass[11pt,a4paper,leqno]{extarticle}
 \usepackage[margin=1in]{geometry}
@@
 \usepackage{gensymb}
-%\usepackage{showframe}
-%\usepackage{lipsum}
-
-% set space
-%\doublespacing
 
@@
 {\bf\centering\large}{\thesection}{1em}{}
-
 \titleformat{\subsection}
 {\itshape\centering}{\thesubsection}{1em}{}
-
 \titleformat{\subsubsection}
@@
 
-% unicode chars for plots
-\DeclareUnicodeCharacter{2212}{$-$}
-
-% booktabs
-\setlength\heavyrulewidth{0.06em} % 0.01em> midrule
+% section referencing
+\crefformat{section}{\S#2#1#3}
+\crefformat{subsection}{\S#2#1#3}
+\crefformat{subsubsection}{\S#2#1#3}
+\crefrangeformat{section}{\S\S#3#1#4 to~#5#2#6}
+\crefmultiformat{section}{\S\S#2#1#3}{ and~#2#1#3}{, #2#1#3}{ and~#2#1#3}
 
 % images
-%\graphicspath{ {D:/Users/saketh/Documents/GitHub/Energy-Intermittency-Paper/figures/} }
+\graphicspath{ {D:/Users/saketh/Documents/GitHub/Energy-Intermittency-Paper/figures/} }
 
@@
 
-% array
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
-
-% section referencing
-\crefformat{section}{\S#2#1#3}
-\crefformat{subsection}{\S#2#1#3}
-\crefformat{subsubsection}{\S#2#1#3}
-\crefrangeformat{section}{\S\S#3#1#4 to~#5#2#6}
-\crefmultiformat{section}{\S\S#2#1#3}{ and~#2#1#3}{, #2#1#3}{ and~#2#1#3}
-
 % caption set up
@@
 \newenvironment{proof}[1][Proof]{\noindent\textbf{#1:} }{\ \rule{0.5em}{0.5em}}
-
-% sig stars
-\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
 
@@
 
-	\title{\singlespacing{\textbf{Efficient Pollution Abatement in Electricity Markets with Intermittent Renewable Energy}}\thanks{We would like to thank Prof.
-Roger Klein for helpful comments and the Sun Grant (award number 122682) for funding this project.}}
-
-	\author[]{Saketh Aleti \, and Gal Hochman}
-
-	\affil[]{Rutgers University}
+	\title{\singlespacing{\textbf{Efficient Pollution Abatement in Electricity Markets with Intermittent Renewable Energy}}\thanks{Saketh Aleti: Graduate Student, Department of Economics, Duke University, 419 Chapel Drive, 213 Social Sciences Bldg., Durham, NC 27708-0097, USA (email: sa400@duke.edu).
+Gal Hochman: Associate Professor, Department of Agriculture, Food \& Resource Economics, Cook Office Building, 55 Dudley Road, Room 116, New Brunswick, NJ 08901, USA (email: gal.hochman@rutgers.edu).}}
+
+	\author[]{Saketh Aleti and Gal Hochman}
 
@@
 Subsidizing research into battery technology can mitigate this distributional side effect while complementing traditional policies used to promote renewable energy.
-(JEL Q28, Q41, Q48, Q52, Q55, Q58)
 		}
+		\\
+		\noindent\textbf{Key words:} renewable energy, intermittency, pollution, environment
+
+		\noindent\textbf{JEL Classifications:} Q28, Q41, Q48, Q52, Q55, Q58
 	\end{addmargin}
@@
 Our representative consumer maximizes utility against this budget constraint; the first order conditions of this problem imply:
-	\begin{align}
+	\begin{align}\label{eq:demand}
 	Z_t &= \left(\frac{\alpha_t}{p_t} \right)^\sigma \frac{I}{P} \\
@@
 	\end{equation}
-	Combining this FOC with the demand equation (Equation (3)) allows us to find the equilibrium.
+	Combining this FOC with the demand equation (\cref{eq:demand}) allows us to find the equilibrium.
 Generally, the equilibrium results for any number of technologies ($n$) are analytic, but they are difficult to interpret due to the number of parameters involved.
@@
 
-	Now, recall the demand equation from earlier (Equation 3)
+	Now, recall the demand equation from earlier
 	$$Z_t = \left(\frac{\alpha_t}{p_t} \right)^\sigma \frac{I}{P}$$
@@
 
-	Firstly, recall the demand equation (Equation 3) from our general model:
+	We begin with the demand equation from our general model:
 	\begin{align*}
@@
 Then, we merge these three data sets and trim 1\% of outliers for a total of $818$ observations for each month and state.
+We provide descriptive statistics for this data in \autoref{table:stats}.
 We use this preliminary data set to construct the data required for our regressions.
@@
 
-	\begin{table}[t] \centering 
+	\vspace{0.15in}
+	\begin{center}
+		[INSERT Table 1: Descriptive Statistics]
+	\end{center}
+	\vspace{0.15in}
+
+	\section{Results}
+	\label{sec:results}
+
+	Based on the OLS results reported in \autoref{table:ols} we estimate the intertemporal elasticity of substitution for electricity consumption $\hat{\sigma}  = 1.305$ ($|t| > 24$) when accounting for all degree day covariates and state fixed effects.
+Additionally, we find that accounting for cooling and heating degree days captures a large amount of variation in demand for electricity; in the fixed effects regressions, adding these controls raises adjusted $R^2$ from 8.5\% to 51.8\%.
+Also, as expected, the coefficients on the degree day covariates are symmetrical; that is, the coefficient on $CDD_{t}$ is approximately the same as the negative of that on $CDD_{s}$, and the same applies to $HDD_{t}$ and $HDD_{s}$.
+\footnote{It is important to note that the reason they are not perfectly equal is because our regression data consists of each unique \textit{combination} of $(t,s)$ for each $i$; that is, if we have an arbitrary observation $(t,s,i)$ in our data, then $(s,t,i)$ does not also appear.
+Including these observations would not affect $\sigma$ and they also don't add any further information to our regression.
+However, they would make the magnitude of the estimated coefficients for  CDD$_t$ and CDD$_s$ equivalent (and likewise for HDDs).
+}  Furthermore, we found that electricity consumption seems to rise more in response to CDDs rather than HDDs.
+Next, we find that the sign on $\Delta_{t,s}$ is positive in all regressions, so electricity consumption rises over time independent of price.
+Specifically, fit (6) finds a coefficient of $0.000655$ which implies that electricity consumption rises, on average, by $\approx 0.7\%$ per year.
+Finally, adding state fixed effects seems to raise the estimates of $\sigma$ for all fits.
+
+	\vspace{0.15in}
+	\begin{center}
+		[INSERT Table 2: OLS Regression Results]
+	\end{center}
+	\vspace{0.15in}
+
+	To account for endogeneity in the OLS results, we provide results for our IV specification in \autoref{table:iv}.
+Here, we find a much larger estimate of $\hat{\sigma}  = 5.818$ ($|t| > 11.1$) when considering all covariates and fixed effects.
+F-Statistics on all three specifications are significantly larger than 10, which suggests that the instruments are not weak \citep{SS1997}.
+These results greatly differ from the literature's estimates probably as a consequence of controlling for endogeneity.
+That is, ignoring variation on the supply side would bias OLS estimates for the effect of price on demand downwards; by controlling for this, we find larger estimates of $\sigma$ which is expected.
+Next, with respect to the demand controls, we find results similar to those of OLS.
+The magnitudes of the coefficients on DDs do not appear to be significantly different.
+Furthermore, we again find that CDDs affect electricity consumption more than HDDs.
+But, this time, the coefficients on heating degree days do not appear to be significant.
+Additionally, in contrast with the OLS results, we find a much larger estimate for the coefficient on $\Delta_{t,s}$ of $0.003$; this implies that electricity consumption seems to rise by about 3.65\% per year.
+So, overall, our IV results suggest much higher estimates of $\sigma$.
+
+	\vspace{0.15in}
+	\begin{center}
+		[INSERT Table 3: IV (2SLS) Regression Results]
+	\end{center}
+	\vspace{0.15in}
+
+	Finally, we control for nonlinear effects using a partially linear IV regression reported in \autoref{table:pariv}.
+Here, we find much smaller results than 2SLS when controlling for all possible covariates.
+Specifically, in fit (3), we have $\hat{\sigma} = 0.8847$ ($|t| > 20$).
+The estimates of $\sigma$ with fewer controls are much larger.
+However, based on the OLS and IV results, it seems that both the time control and degree day controls are significant.
+Hence, fit (3) is likely the most appropriate specification.
+Additionally, all of these estimates are significantly different from the 2SLS results which suggests that the 2SLS results are not robust.
+To be precise, our controls and instrument likely have non-linear effects on price and quantity which cannot be captured by linear models; this may explain why the 2SLS results differ significantly from these semiparametric results.
+Alternatively, this difference may also be because the errors in our regressions are not Gaussian.
+In any case, we  believe that our third semiparametric fit, $\hat{\sigma} = 0.8847$, is the most robust estimate of $\sigma$.
+We now discuss what this means for renewable energy policy in greater detail.
+
+	\vspace{0.15in}
+	\begin{center}
+		[INSERT Table 4: Partially Linear IV Regression Results]
+	\end{center}
+	\vspace{0.15in}
+
+	\clearpage
+	\section{Discussion}
+	\label{sec:Discussion}
+
+	\subsection{The Elasticity of Substitution between Renewable and Fossil Energy}
+
+	We are concerned with how $\sigma$ affects the substitutability of fossil and renewable energy.
+This is important, because sufficient substitutability between these two technologies is required to transition into greener economy in the future.
+For instance, \citet{Ace2012} provide a model where they argue that, ``When the two
+	sectors [clean and dirty energy] are substitutable but not sufficiently so, preventing an environmental disaster requires a permanent policy intervention.
+Finally, when the two sectors are complementary, the only way to stave off a disaster is to stop long-run growth." However, note that while our model sets the intertemporal elasticity of substitution for  electricity consumption $\sigma$ to a fixed value, we make no direct assumptions about the elasticity of substitution between different energy technologies.
+Instead, this latter elasticity is indirectly defined by the substitutability of electricity consumption between periods.
+To illustrate this, we parametrize and estimate our model numerically.
+
+	Firstly, let technology 1 be coal power and technology 2 be solar power.
+These two technologies exemplify consistent fossil energy and intermittent renewable energy.
+Furthermore,  let period $t$ represent peak hours and period $s$ represent off-peak hours.
+We assume that, holding prices equal, consumers prefer that approximately 60\% of their energy arrive in period $t$ and the remaining 40\% arrive in period $s$; that is, we have $\alpha_t = 0.6$ and $\alpha_s = 0.4$.
+Next, we normalize all quantity units to a MWh basis.
+Hence, we let $\xi$ represent the percent of capacity utilized in each period; we assume coal uses 100\% of its capacity in both periods, while solar can access 100\% during peak hours and only 10\% during the off-peak.
+Finally, we set the cost parameters, given in  \$ per MWh, equal to LCOE\footnote{ The LCOE for a generation technology is equal to the sum of its lifetime costs divided by its lifetime energy output.
+\citet{Joskow2011} explains the flaws of comparing generation technologies solely on the basis of LCOE; but,  our use of this measure is unrelated to his critique.
+That is, he argues that the economic value an intermittent technology should also account for when it produces electricity and the prices of electricity in those periods (see Table 2 of his paper).
+Our model does exactly this; but, we still need to  use LCOE to parametrize the cost of developing capacity.
+} estimates for 2023 from the \citet{EIALCOE}; specifically, we use estimates for "Solar PV" and "Coal with 30\% CCS" from Table 1b.
+In total, we have the following parameters.
+
+	\begin{center}
+		\noindent \textbf{Model Parameters:} $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$. 
+		\label{Params: Example A}
+	\end{center}
+
+	We begin by exploring the implied elasticity of substitution between these two technologies. Recall, for any two commodities $i$ and $j$,  the elasticity of substitution $e_{i,j}$ is given by:
+	$$e_{i,j} = \frac{\partial \log (X_i/ X_j)}{\partial \log (c_j/c_i)}$$
+	where $c$ is their prices.
+This relationship is of particular interest, because many applied and theoretical models studying renewable and fossil energy impose a CES production structure between the two (see \citet{Pap}).
+That is, they assume that $e$ is a fixed constant between renewable and fossil energy.
+In our model, this is not the case; while directly deriving the equation for $e_{1,2}$ in our model is analytically intractable, we numerically estimate how it varies with $\log (c_2/c_1)$ and $\sigma$.
+
+	\vspace{0.15in}
+	\begin{center}
+		[INSERT Figure 1: The Elasticity of Substitution between Solar and Coal]
+	\end{center}
+	\vspace{0.15in}
+
+	We plot our numerical estimates of $e_{1, 2}$, the elasticity of substitution between solar and coal power, in \autoref{fig:eosnum}.
+We generated these results by computing the optimal quantities of each technology given a range of relative prices $c_2/c_1$.
+Then, we numerically differentiated $\log(X_1/X_2)$ with respect to $\log(c_2/c_1)$ to estimate the elasticity of substitution between solar and coal.
+This numerically computed elasticity of substitution between solar and coal power, $e_{solar,coal}$, is shown in the lower subplot.
+We repeat this process with different values of $\sigma$, the elasticity of substitution in the consumer's utility function.
+Specifically, we use our estimate of $\hat{\sigma} = 0.8847\, (0.044)$ and its 95\%  confidence interval $(0.7985, 0.9709)$.
+Finally, after finding the optimal values of our quantities $X$, we filter all observations of our numerical simulation that correspond to edge cases -- solutions where $X, Z \leq  0$.
+
+	The first relationship we see in \autoref{fig:eosnum} is that $e_{1,2}$ varies non-linearly with the relative costs of each technology; in particular, it appears to take on a hockey stick shape.
+This shape is a result of both intermittency and costs.
+Intermittency reduces substitutability as overall energy generation becomes more intermittent.
+In other words, intermittency is a bigger issue for consumers when their energy supply is not consistent.
+This causes $e_{1,2}$ to fall when the majority of energy generated comes from solar; naturally, the latter occurs when $\log(c_2/c_1)$ is small (solar is relatively cheap).
+At the same time, quantities become more sensitive to costs when costs greatly differ.\footnote{We explore this point further in Appendix B in which we consider a numerical example where technologies are minimally intermittent.
+That is, we again consider a two-period, two-technology example, but assume that $\xi_1$ and $\xi_2$ are nearly constant over time.
+We plot our results in \autoref{fig:eosrange} and find that the elasticity of substitution takes on a u-shape.
+} That is, $e_{1,2}$ rises when the relative prices of solar and coal are very different.
+When these two effects interact, we see the elasticity of substitution between solar and coal takes on a hockey stick shape.
+
+	Additionally, note that the elasticity of substitution $e_{1,2}$ between solar and coal becomes larger and more non-linear as $\sigma$ rises.
+Firstly, the reason why  it becomes larger is fairly intuitive.
+When a consumer's intertemporal elasticity of substitution for electricity consumption $\sigma$ is large, they will be more sensitive to changes in the price of electricity and more willing to substitute their electricity consumption across periods.
+As a result, the intermittency of solar becomes less of an  issue for consumers, but its relative price with respect to coal will play a bigger role.
+Consequently, this implies that the elasticity of substitution $e_{1, 2}$ will be larger.
+Hence, in the lower subplot of \autoref{fig:eosnum}, we see that $e_{1, 2}$ rises with $\sigma$ when holding the  relative prices of each technology constant.
+Secondly, we find that $e_{1,2}$ becomes more u-shaped as $\sigma$ rises.
+This is because larger values of $\sigma$ weaken the disincentive created by intermittency.
+Consequently, the shape of the elasticity of substitution $e_{1,2}$ becomes more dependent on the relative costs.
+As argued earlier, when costs differ greatly between technologies, the elasticity of substitution $e_{1,2}$ is higher.
+
+	\subsection{Implications for Environmental Policy}
+
+	Overall, our results suggest that the elasticity of substitution between  renewable and fossil energy is not constant.
+Furthermore, it appears to fall with the level of intermittency.
+What implications does this result have?
+
+	\subsubsection{Revisiting Past Models}
+
+	To start, we consider how  a variable elasticity of substitution affects past models of the energy sector.
+As an example, consider the results of \citet{Ace2012}.
+Firstly, they find that the short-run cost of policy intervention is increasing with the elasticity of substitution between clean and dirty technologies.\footnote{ See Corollary 1 of their paper for a proof and intuitive explanation.} Additionally, their paper states that the cost of delaying intervention is increasing with the elasticity of substitution.
+Secondly, Acemoglu et al.
+argue that, when the discount rate and elasticity of substitution between clean and dirty energy ($e$) is sufficiently low, a disaster cannot be avoided under laissez-faire.\footnote{ See Proposition 9 of their paper.} And, finally, Acemoglu et al.
+find that, ``when the elasticity of substitution is high\dots\, a relatively small carbon tax is sufficient to redirect R\&D towards clean technologies."
+
+	Based on our results, each of these statements has a complementary interpretation in terms of intermittency.
+For instance, the first statement suggests that the cost of policy intervention is decreasing with the intermittency of clean technologies; the cost of delaying intervention is decreasing with intermittency as well.
+This is because the elasticity of substitution between renewables and fossil fuels becomes small when renewables are more intermittent.
+So, in other words, delaying policy intervention will be the most costly in regions with access to clean, non-intermittent energy (such as hydro and geothermal energy).
+Secondly,  when the discount rate is sufficiently low and the intermittency of clean energy is sufficiently high, a disaster cannot be avoided under laissez-faire.
+The intuition here is that, even if clean energy became relatively cheap, its intermittency would prevent it from adequately substituting for fossil energy.
+Finally, Acemoglu et al.
+argue that the size of a carbon tax should be inversely proportional to the elasticity of substitution and should decrease over time.
+Recall that, in our model, the elasticity of substitution $e$ changes with relative prices; when fossil fuels are relatively cheap, $e$ is large.
+Hence, this implies we need a relatively small carbon tax early on to spur research.
+As technological change makes renewables cheaper, fossil fuels will become relatively more expensive so $e$ will fall; thus, the carbon tax will need to increase over time.
+These dynamics (a rising carbon tax) contrast with the results of Acemoglu et al.
+who numerically show that an optimal carbon tax should decrease over time when $e$ is sufficiently large.
+A potential resolution to these contradictory solutions may be to take an intermediate route and maintain a constant carbon tax over time.
+
+	\vspace{0.15in}
+	\begin{center}
+		[INSERT Figure 2: The Price Elasticity of Demand for Coal Power]
+	\end{center}
+	\vspace{0.15in}
+
+	\subsubsection{Carbon Taxes and their Distributive Consequences}
+
+	Our results also suggest that carbon taxes can have important distributional consequences.
+Earlier, we showed that the elasticity of substitution between renewable and fossil fuels $(e)$ is non-constant and falls with the intermittency of present generation.
+This further implies that the elasticity of demand for generation technologies is non-constant as well.
+Specifically, the elasticity of demand for non-intermittent energy increases then decreases with respect to its own price.
+Using the earlier numerical example of solar and coal power, we show this explicitly in \autoref{fig:coalelas}.
+As the price of coal power rises significantly beyond its current price, demand gets more elastic because its price becomes the primary factor disincentivizing its use.
+But, initially, a rise in the cost of coal power causes its demand to become inelastic.
+This is because a rise in the price of coal shifts generation towards solar;  consequently, generation becomes more intermittent and demand for coal becomes less price sensitive since it is needed to help smooth electricity generation.
+This relationship should be of concern for policy makers considering a pollution tax.
+Consumers in regions without access to clean, non-intermittent energy will have the most inelastic demand for fossil fuels; hence, they will bear the greatest welfare losses from a tax on pollution/carbon.
+On the other hand, consumers in regions that have access to dispatchable, renewable energy such as hydropower will see smaller welfare losses; the demand for fossil fuels in these regions will not be as inelastic, because dirty generation can be replaced with non-intermittent, clean generation.
+All in all, if a carbon tax were implemented federally and its revenue were distributed equally, it may nevertheless function as an inequitable, between-state welfare transfer due to differences in the availability of renewable energy technology.
+This same argument would apply  to carbon quotas.
+
+	\vspace{0.15in}
+	\begin{center}
+		[INSERT Figure 3: The Effect of Battery Storage on the Elasticity of Substitution between Solar and Coal]
+	\end{center}
+	\vspace{0.15in}
+
+	\subsubsection{The Case for Subsidizing Battery Research}
+
+	However, there are alternative policies that can mitigate this distributional side effect.
+One such policy is a research subsidy for improving battery technologies.
+Reducing battery costs, improving their storage capacity, and reducing their  energy loss can allow intermittent renewables to far more easily substitute for traditional, fossil energy.
+To understand the magnitude of this effect, we again provide a numerical example using solar and coal.
+We aim to understand how batteries effect substitutability, so consider a parsimonious model where batteries are used to shift a portion of solar energy output from its high-output period to its low-output period.\footnote{Because we are only interested in the effects of batteries on $e$, we ignore the energy losses and costs of battery storage.
+Furthermore, if our goal instead was to economically optimize battery storage and deployment, we would have to   rewrite our model as a dynamic optimization problem and solve using optimal control theory.
+However, we set aside these complications and consider a second-best solution where batteries are used to shift a fraction of solar output from its low-output period to its high-output period.
+But, since we are shifting relatively marginal fractions of energy output, this is likely equivalent to the first-best solution.
+} Specifically, we initially parametrized solar with $\xi_{2} = (1, 0.1)$ implying that it functions at 100\% of its potential capacity during the peak and at 10\% of its potential capacity during the off-peak; this is far from matching consumer demand.
+So, we represent solar output with batteries using $\xi_2 = (0.95, 0.15)$ and $\xi_2 = (0.90, 0.20)$; this is equivalent to transferring 5\% and 10\% of solar output.
+We plot our results in \autoref{fig:battery}.
+It is immediately clear that making solar output more consistent through the day results in a large increase in the elasticity of substitution $e_{1,2}$.
+Moreover,  $e_{1,2}$ no longer tapers off around 4 as solar becomes the dominant source of electricity.
+Rather, with batteries, cost plays a much larger role in determining the optimal quantity of each technology even when solar is relatively cheap.
+Overall, shifting even a small fraction of solar output using batteries can significantly improve solar power's substitutability with coal.
+
+	\vspace{0.15in}
+	\begin{center}
+		[INSERT Figure 4: The Effect of Battery Storage on the  Elasticity of Demand for Coal Power]
+	\end{center}
+	\vspace{0.15in}
+
+	Consequently, batteries can complement reductions in the cost of intermittent renewables and mitigate the distributional side effects of a carbon tax.
+As shown in \autoref{fig:battery}, the elasticity of substitution between solar and coal rises significantly as solar becomes less intermittent; this implies that a change in the relative price of solar would have a far greater effect on solar adoption if batteries were employed with solar.
+Hence, if policy makers aim to promote the use of renewables, they should subsidize research that reduces the cost of renewables as well as research that improves battery technology.
+Using both policy instruments can be more effective than either alone.
+Additionally, the second benefit of batteries is that they mitigate the distributional problems of a carbon tax.
+This is because, by reducing the intermittency of renewables, batteries make demand for fossil fuels less inelastic.
+We specifically show this elasticity would change with another numerical example in \autoref{table:storelas}; like  \autoref{fig:battery}, we model batteries that shift solar output towards the off-peak.
+We then estimate the elasticity of demand for coal power around its initial price; this elasticity is decreasing at an increasing rate with the percent shift in solar output.
+The practical implications of this are straightforward.
+Researching and implementing battery technology can reduce the welfare losses from a carbon tax.
+Moreover, regions without clean, consistent renewables would benefit in particular, because they will be able to combine intermittent technologies with better energy storage to help transition away from fossil fuel energy.
+In short, subsidizing battery research can reduce some of the unintended distributional consequences of carbon taxes while mitigating environmental damage.
+
+	\subsubsection{Learning-by-Doing and Intermittency}
+
+	Lastly, our results suggest that renewable subsidies aimed at correcting the positive externalities of ``learning-by-doing" should also vary geographically.
+This is because the adoption rate of a renewable technology depends on its intermittency and the pre-existing technologies used for generation.
+For instance, hydropower plants can easily substitute for fossil fuel technologies, because hydropower is non-intermittent.
+Consequently, developing a larger initial capacity of hydropower to promote learning-by-doing can be done with a relatively small subsidy.
+On the other hand, suppose a region's only source of renewable energy is wind power.
+In this case, the intermittency of wind power reduces its elasticity of substitution with fossil fuel technologies.
+Thus, relatively larger subsidies are required to raise the capacity of wind power.
+Furthermore, the intermittency of renewable technologies (especially wind and solar) is linked to the weather which varies geographically.
+Hence, two regions with access to the same intermittent renewables at the same cost may still experience differing levels of intermittency based on their location.
+So, optimal renewable subsidies may also vary geographically simply due to differences in the weather.
+Thirdly, as discussed earlier, the elasticity of substitution between clean and dirty energy rises when prices differ greatly.
+This implies that regions with relatively expensive renewables (relatively cheap fossil energy) can benefit more from subsidies; again, this can vary geographically since the costs of both fossil fuels and renewables vary geographically.
+So, in total, correcting the externality from learning-by-doing should take into account the geographic differences in the availability of renewable technologies, weather conditions that may influence renewable output, and the relative prices of renewable and fossil energy.
+
+	This implies that optimal renewable subsidies should differ geographically but only to the extent that the spillovers of learning-by-doing balance out differences in welfare gains.
+That is, recall that subsidies for renewables have two benefits: promoting learning-by-doing and raising consumer and producer surplus.
+The first effect  can spur innovation that affects technology in all regions while the latter effect is mostly local.
+Now, consider two edge-case policy solutions targeting one benefit but ignoring the other.
+The first extreme solution may be to maximize learning by doing while ignoring the effects of subsidies on welfare.
+This solution would suggest that we subsidize renewables wherever they can best substitute for fossil fuels.
+The other extreme solution would be to distribute subsidies almost equally to ensure welfare gains are equitable; this assumes policymakers do not want to concentrate welfare gains for some regions but not others.
+Since we know the effect of subsidies on renewable adoption varies geographically, these two extreme solutions must differ; in other words, there's likely a trade-off between efficiently and equitably promoting renewables.
+Consequently, ignoring an edge case, an intermediate choice between these two approaches is a valid second-best solution for policymakers looking to balance efficiency and equity.
+Alternatively, a first-best solution would simply maximize efficiency with the first approach and then make welfare outcomes more equitable with direct monetary transfers.
+And finally, like before with carbon taxes, improving battery technology can also help mitigate the distributional side effects of efficient renewable subsidies.
+
+	\subsection{Adjusting Future Models}
+
+	Given that traditional assumption of a CES relationship between renewable and fossil energy appears to be inaccurate, we offer two alternative approaches for future models.
+The first approach is to directly integrate our model within a given framework.
+The second approach is to assume a variable elasticity of substitution (VES) structure\footnote{ The VES function was originally introduced by \citet{VES}.} between clean and dirty energy.
+These two approaches have their own advantages/disadvantages and serve different purposes.
+
+	\subsubsection{Direct Integration}
+
+	The first approach is better suited for numerical models.
+For example, our model of the energy sector can be embedded within a Computational General Equilibrium (CGE) model.
+CGEs, specifically ones designed to study energy and environmental policy, tend to assume a CES relationship between generation technologies and treat electricity as a homogeneous good.
+On the other hand, our representation of the energy sector makes more realistic assumptions and directly models the source of imperfect substitutability between generation technologies -- intermittency.
+Consequently, embedding our model within a CGE would improve its predictive accuracy by giving it more realistic microfoundations.
+
+	Furthermore, implementation can be done with relatively few modifications to standard CGE.
+To start, CGEs already use CES utility to model consumer preferences.
+In order to integrate our method of modeling electricity consumption, a CGE practitioner need only to rewrite preferences as:
+	\begin{equation}
+	U =   \left( \sum_{i \neq elc} \alpha_{i} Z_{i}^\eta +  \alpha_{elc} \left( \sum_{t=1}^T \alpha_{elc,t} Z_{elc, t}^\phi \right)^{\eta/\phi} \right)^{1/\eta}
+	\end{equation}
+	where the intertemporal elasticity of substitution for electricity consumption is given by $\sigma = 1/(1-\phi)$,  the elasticity of substitution between all consumer goods is given by $1/(1-\eta)$, the consumption of each good is given by $Z_{i}$, and the consumption of electricity in each period $t$ is given by $Z_{elc, t}$.
+This can be simplified to:
+	\begin{align}
+	U &= \left(  \left( \sum_{i \neq elc} \alpha_{i} Z_{i}^\eta \right) + \alpha_{elc} Z_{elc}^\eta \right)^{1/\eta} \\
+	Z_{elc} &= \left(  \sum_{t=1}^T \alpha_{elc,t} Z_{elc, t}^\phi \right)^{1/\phi}
+	\end{align}
+	where $Z_{elc}$ is an aggregate electricity good.
+Next, we consider the production functions for electricity production in each period.
+These are simply linear, since the total  electricity produced in a period is equal to the sum of electricity produced by each technology in that period.
+That is, we have
+	\begin{equation}
+	Z_{elc,t} = \sum_i \xi_{i,t} X_i 
+	\end{equation}
+	where $X_i$ is a generation technology and $\xi_{i,t}$ is its output in period $t$.
+The parameters for $\xi_{1,t}$ must be estimated using additional data.
+For fossil fuels, $\xi_i$ can remain constant over time.
+For intermittent renewables, $\xi_{i,t}$ may be set to empirical estimates of the average output per unit of $X_i$ in period $t$.\footnote{ It is important to note that each period $t$ should describe a short time frame.
+For instance, each period may represent an hour of a day, or, as in our examples, we may have two periods that represent peak and off-peak.
+If larger periods are chosen, the underlying assumptions behind our model are no longer relevant.
+That is, technologies like coal and nuclear can change their output over longer periods of time to respond to changes in price; on the other hand, as discussed earlier, we assume here that output in each period is exogenous.}  Additionally, the supply-side equations for building capacity in each technology can be modeled using the usual  CGE approach; total cost is given by the sum of costs for each input factor and total quantity is given by a CES of the input factors used to build capacity $(X_i)$.
+Finally, since these functional forms equivalent\footnote{ Linear production functions simply a special case of CES production functions where the elasticity of substitution is arbitrarily high.} to those used in standard CGEs, they can be calibrated using the usual procedures and a social accounting matrix.
+So, overall, implementing our model within a CGE can be done in a fairly simple way.
+
+	\subsubsection{VES Approximation}
+
+	\vspace{0.15in}
+	\begin{center}
+		[INSERT Figure 5: The VES Approximation of the Elasticity of Substitution between Solar and Coal]
+	\end{center}
+	\vspace{0.15in}
+
+	The second approach is to use a variable elasticity of substitution function to model the relationship between clean and dirty energy.
+A VES function would approximately capture the dynamics of $e$, the elasticity of substitution between clean and dirty technology,  while keeping a theoretical model relatively simple.
+The latter is because assuming a VES structure between clean and dirty energy only requires considering one more parameter than a traditional CES function.
+To be more precise, the VES function is defined in \citet{VES} as
+	\begin{align}
+	Z &= \gamma X_1^{\omega(1-\delta \rho)} \left( X_2 + (\rho - 1) X_1 \right)^{\omega \delta \rho} \\
+	e &= 1 + \beta (X_1 / X_2) \\
+	\beta &= (\rho - 1) / ( 1- \delta \rho ) 
+	\end{align}
+	\vspace{-4ex}
+	$$\gamma > 0, \quad \omega > 0, \quad0 < \delta < 1, \quad 0 \leq \delta \rho \leq 1 , \quad (X_2/X_1) >  -\beta $$
+	where $\omega, \delta, \rho$, and $\gamma$ are parameters.
+Additionally, $Z$ is the output, $X_1$ and $X_2$ are the inputs, and $e$ is the elasticity of substitution between $X_1$ and $X_2$.
+In our case, we can think of $Z$ as electricity output while $X_1$ and $X_2$ represent dirty and clean technology.
+Note that $e$ is a linear function of $X_1/X_2$; this relationship allows a VES function to approximate the effects of intermittency.
+To show why, we plot $e$ against its VES approximation $\hat{e}$ for solar and coal in \autoref{fig:ves}.
+This approximation was fit by running OLS against the numerical results for $e$ while holding the intercept fixed at 1.\footnote{ There also exists a VES function described by \citet{VES} with the form $e = \beta_0 + \beta (X_1/X_2)$.
+This function may provide a better approximation of $e$, but there is no tractable production function that underlies it for $\beta_0 \neq 1$.
+Hence, we only consider the case where $\beta_0 = 1$, since the entire point of taking a VES approximation, in this case, is for analytical tractability.
+} We can see that, as either the capacity of solar or coal dominates the market, the approximation becomes weaker.
+But, overall, it seems to mimic the shape of the true elasticity of substitution $e$ implied by our model of intermittency.
+Hence, a  VES function is a reasonable alternative to a CES function -- it better models intermittency while also maintaining parsimony.
+
+	One potential objection to using the VES function is that it assumes the elasticity of substitution $e$ approaches 1 when the majority of generation comes from renewables ($X_1/X_2 \to 0$).
+And, a VES structure assumes linear $e$ which does not seem to be the case in \autoref{fig:ves}.
+However, both these assumptions may still be fairly reasonable in the right context.
+That is, suppose renewable energy was highly intermittent and that the consumer's elasticity of substitution $\sigma = 1$.
+Firstly, this results in renewable  and fossil energy entering a Cobb-Douglas relationship ($e = 1$) as $X_1/X_2 \to 0$ which supports the VES assumption of an intercept of 1.
+Secondly, no matter the relative prices, whenever the renewable technology is highly intermittent, $e$ becomes perfectly linear with respect to $X_1/X_2$; this supports the VES assumption of linearity.
+The proofs for both are given in \hyperref[sec:asympeos]{Appendix A.C}.
+Hence, in these cases, a VES approximation  can perfectly match $e$.
+Additionally, even when consumer's elasticity of substitution is not $1$, $e$ may still be approximately linear; this is shown in \autoref{fig:ves_int} where we consider our estimated $\hat{\sigma} = 0.8847$.
+In short, the assumptions made by a VES structure may nevertheless be accurate in certain cases.
+
+	Overall, using a VES function is a reasonable alternative to directly modeling intermittency.
+It allows theorists to derive policy implications from intermittency without relying too heavily on numerical models.
+Furthermore, it keeps theory simple since the elasticity of substitution can be represented as a linear function of a single parameter $\beta$.
+And, this parameter can be estimated econometrically, so theoretical models assuming a VES structure can offer empirically-based results.
+Finally, it may even be of use for CGE modelers.
+Its structure is simple enough to be calibrated with a given set of data, while its implementation can produce simple but reasonably accurate models of energy sectors with intermittency.
+
+	\section{Conclusion}
+
+	In this paper, we have offered a framework for understanding the economics of intermittent renewable energy that bears in mind the critique offered by \citet{Joskow2011}.
+That is, our model evaluates the economic feasibility of a technology by integrating its production profile with the market value of electricity in equilibrium.
+Moreover, this equilibrium is reached using a fairly realistic model of consumer behavior.
+The empirical parameterization of our model and its numerical results suggest that the elasticity of substitution between renewable and fossil energy is non-constant.
+We have shown that this has important implications for policy and future models.
+
+	With respect to policy, we have shown (i) the welfare effects of carbon taxes and renewable subsidies depend on the intermittency of renewables and thus vary geographically; (ii) the effect that renewable subsidies have on promoting the adoption of renewables varies geographically; (iii) the combination of (i) and (ii) can create a trade-off between efficiently and equitably preventing climate change; (iv) subsidizing battery research can complement other policies by increasing the substitutability of renewable and fossil energy; (v) improving batteries can mitigate the unintentional distributional consequences of carbon taxes and research subsidies.
+Additionally, we have qualitatively evaluated the results of \citet{Ace2012} in a setting where renewables and fossil fuels have a non-linear elasticity of substitution.
+Based on their framework, we have further argued that: (vi) the short-run cost of policy intervention is decreasing with intermittency;  (vii) the cost of delaying intervention is decreasing with intermittency; (viii) when the discount rate is sufficiently low and the intermittency of renewables is sufficiently high, a laissez-faire equilibrium would require policy intervention to prevent disaster; (ix) when renewables are moderately intermittent, an optimal carbon tax should remain approximately constant over time.
+
+	Given how strongly the elasticity of substitution between renewable and fossil energy varies with relative price, future models of intermittency should not assume a CES structure.
+So, we have shown to integrate our framework within a numerical model, such as a CGE; this may improve predictive accuracy by providing more realistic microfoundations.
+On the other hand, theoretical models would be better served by more a analytically tractable alternative.
+Therefore, we suggest theoretical models use a VES production function to approximate the effect of intermittency on the elasticity of substitution between renewable and fossil energy.
+Under certain conditions, our own model simplifies to a VES case; hence, the VES production function can reasonably approximate for our full model in a more tractable way.
+
+	While constructing our model, we made several simplifications for tractability.
+For instance, we set aside modeling reliability -- stochastic or otherwise unpredictable variation in output.
+An aim for future research may be to develop a model of clean and dirty energy that incorporates both intermittency and reliability in a multi-period setting.
+This could involve integrating our framework with that of \citet{HH}.
+Additionally, another avenue for future research may be to explicitly model the effects of battery technology and how storage interacts with intermittency and reliability.
+Such models can offer more accurate predictions/suggestions for policymakers and bring theory closer to reality.
+
+	\section{Acknowledgments}
+
+	This research was funded by the Sun Grant (122682). We would also like to thank Prof. Roger Klein and the participants of the NAREA 2019 Workshop for helpful comments.
+
+	\begin{thebibliography}{9}
+
+		\bibitem[Acemoglu et al.(2012)]{Ace2012}
+		Acemoglu, D., Aghion, P., Bursztyn, L., \& Hemous, D. (2012). The Environment and Directed Technical Change. American Economic Review, 102(1), 131–166. https://doi.org/10.1257/aer.102.1.131
+
+		\bibitem[Adelman(1995)]{genie}
+		Adelman, M. A. (1995). The genie out of the bottle: World oil since 1970. MIT Press.
+
+		\bibitem[Ambec and Crampes(2012)]{AC2012}
+		Ambec, S., \& Crampes, C. (2012). Electricity provision with intermittent sources of energy. Resource and Energy Economics, 34(3), 319–336. https://doi.org/10.1016/j.reseneeco.2012.01.001
+
+		\bibitem[Aubin et al.(1995)]{Aubin}
+		Aubin, C., Fougere, D., Husson, E., \& Ivaldi, M.
+(1995).
+Real-time pricing of electricity for residential customers: Econometric analysis of an experiment.
+Journal Of Applied Econometrics, 10, S171–S191.
+
+		\bibitem[Borenstein(2012)]{Boren2012}
+		Borenstein, S. (2012). The Private and Public Economics of Renewable Electricity Generation. Journal of Economic Perspectives, 26(1), 67–92. https://doi.org/10.1257/jep.26.1.67
+
+		\bibitem[Chao(2011)]{Chao2011}
+		Chao, H. (2011). Efficient pricing and investment in electricity markets with intermittent resources. Energy Policy, 39(7), 3945–3953. https://doi.org/10.1016/j.enpol.2011.01.010
+
+		\bibitem[Climate Prediction Center(2019)]{CPC}
+		Climate Prediction Center (2019). Degree Days Statistics. National Oceanic and Atmospheric Administration. https://www.cpc.ncep.noaa.gov/products/analysis\_monitoring/cdus/degree\_days/
+
+		\bibitem[Delarue et al.(2010)]{Delarue}
+		Delarue, E., De Jonghe, C., Belmans, R., \& D’Haeseleer, W.
+(2010).
+Applying portfolio theory to the electricity sector: Energy versus power.
+Energy Economics, 33(1), 12–23.
+https://doi.org/10.1016/j.eneco.2010.05.003
+
+		\bibitem[Deryugina and Mackay(2017)]{Deryugina}
+		Deryugina, T., Mackay, A., \& Reif, J. (2017). The Long-Run Dynamics of Electricity Demand: Evidence from Municipal Aggregation. NBER Working Paper Series. https://doi.org/10.3386/w23483
+
+		\bibitem[EIA(2019a)]{EIANetgen}
+		Electricity Information Administration (2019a). Net generation, United States, all sectors, annual. Electricity Data Browser. https://www.eia.gov/electricity/data/browser
+
+		\bibitem[EIA(2019b)]{EIALCOE}
+		Electricity Information Administration (2019b).
+Levelized Cost and Levelized Avoided Cost of New Generation.
+Annual Energy Outlook 2019.
+https://www.eia.gov/outlooks/aeo/pdf/electricity\_generation.pdf
+
+		\bibitem[EIA(2019c)]{EIArenew}
+		Electricity Information Administration (2019c). U.S. renewable electricity generation has doubled since 2008. Today in Energy. https://www.eia.gov/todayinenergy/detail.php?id=38752
+
+		\bibitem[Fan and Hyndman(2011)]{Fan}
+		Fan, S., \& Hyndman, R. (2011). The price elasticity of electricity demand in South Australia. Energy Policy, 39(6), 3709–3719. https://doi.org/10.1016/j.enpol.2011.03.080
+
+		\bibitem[Foley et al.(2012)]{Foley2012}
+		Foley, A., Leahy, P., Marvuglia, A., \& Mckeogh, E.
+(2012).
+Current methods and advances in forecasting of wind power generation.
+Renewable Energy, 37(1), 1–8.
+https://doi.org/10.1016/j.renene.2011.05.033
+
+		\bibitem[Geroski(1957)]{Geroski2000}
+		Geroski, P. (2000). Models of technology diffusion. Research Policy. Elsevier B.V. https://doi.org/10.1016/S0048-7333(99)00092-X
+
+		\bibitem[Helm and Mier(2019)]{HH}
+		Helm, C., \& Mier, M. (2019). On the efficient market diffusion of intermittent renewable energies. Energy Economics, 80, 812–830. https://doi.org/10.1016/j.eneco.2019.01.017
+
+		\bibitem[Herriges et al.(1993)]{Herriges}
+		Herriges, J., Baladi, S., Caves, D., \& Neenan, B.
+(1993).
+The Response of Industrial Customers to Electric Rates Based Upon Dynamic Marginal Costs.
+The Review of Economics and Statistics, 75(3), 446.
+https://doi.org/10.2307/2109458
+
+		\bibitem[Joskow(2011)]{Joskow2011}
+		Joskow, P. (2011). Comparing the Costs of Intermittent and Dispatchable Electricity Generating Technologies. American Economic Review, 101(3), 238–241. https://doi.org/10.1257/aer.101.3.238
+
+		\bibitem[King and Shatrawka(2011)]{KS1994}
+		King, Kathleen, and Peter Shatrawka (1994). "Customer Response to a Permanent Time- Varying
+		Pricing Program in the United Kingdom." Laurits R. Christensen Associates, Madison,
+		Wisconsin.
+
+		\bibitem[Mohajeryami et al.(2016)]{Moha2016}
+		Mohajeryami, S., Moghaddam, I., Doostan, M., Vatani, B., \& Schwarz, P.
+(2016).
+A novel economic model for price-based demand response.
+Electric Power Systems Research, 135, 1–9.
+https://doi.org/10.1016/j.epsr.2016.03.026
+
+		\bibitem[Musgens and Neuhoff(2006)]{MN2006}
+		Musgens, F., \& Neuhoff, K. (2006). Modelling Dynamic Constraints in Electricity Markets and the Costs of Uncertain Wind Output. Faculty of Economics.
+
+		\bibitem[Neuhoff et al.(2007)]{NCK2007}
+		Neuhoff, K., Cust, J.
+\& Keats, K.
+(2007).
+Implications of intermittency and transmission constraints for renewables deployment.
+Cambridge Working Papers in Economics 0711, Faculty of Economics, University of Cambridge.
+
+		\bibitem[Newey(1990)]{Newey}
+		Newey, W. (1990). Efficient Instrumental Variables Estimation of Non-linear Models. Econometrica, 58(4), 809–837. https://doi.org/10.2307/2938351
+
+		\bibitem[ORNL(2004)]{ORNL}
+		ORNL (2004).
+Measurement practices for reliability and power quality.
+A toolkit of reliability measurement practices.
+U.S.
+Department of Energy.
+https://info.ornl.gov/sites/publications/Files/Pub57467.pdf
+
+		\bibitem[Papageorgiou et al.(2017)]{Pap}
+		Papageorgiou, C., Saarn, M., \& Schulte, P.
+(2017).
+Substitution between clean and dirty energy inputs: a macroeconomic perspective.(Author abstract).
+Review of Economics and Statistics, 99(2), 201–212.
+https://doi.org/10.1162/REST\_a\_00623
+
+		\bibitem[Reiss and White(2005)]{Reiss}
+		Reiss, P., \& White, M. (2005). Household Electricity Demand, Revisited. The Review of Economic Studies, 72(252), 853. Retrieved from http://search.proquest.com/docview/204335314/
+
+		\bibitem[Revankar(1971)]{VES}
+		Revankar, N. (1971). A Class of Variable Elasticity of Substitution Production Functions. Econometrica, 39(1), 61–71. https://doi.org/10.2307/1909140
+
+		\bibitem[Schwarz et al.(2002)]{Schwarz}
+		Schwarz, P., Taylor, T., Birmingham, M., \& Dardan, S.
+(2002).
+Industrial response to electricity real-time prices: short run and long run.
+Economic Inquiry, 40(4), 597–610.
+https://doi.org/10.1093/ei/40.4.597
+
+		\bibitem[Shahriari and Blumsack(2018)]{SB2018}
+		Shahriari, M., \& Blumsack, S. (2018). The capacity value of optimal wind and solar portfolios. Energy, 148, 992–1005. https://doi.org/10.1016/j.energy.2017.12.121
+
+		\bibitem[Silverman(1986)]{Silverman}
+		Silverman, B. (1986). Density estimation for statistics and data analysis. London; Chapman and Hall.
+
+		\bibitem[Zhou and Teng(2013)]{Zhou}
+		Zhou, S. \& Teng, F., (2013). Estimation of urban residential electricity demand in China using household survey data.(Statistical data). Energy Policy, 61, 394–402.
+
+		\bibitem[Staiger and Stock(1997)]{SS1997} 
+		Staiger, D., \& Stock, J. (1997). Instrumental Variables Regression with Weak Instruments. Econometrica, 65(3), 557–586. https://doi.org/10.2307/2171753
+
+		\bibitem[US BEA(2019)]{USBEA}
+		U.S. Bureau of Economic Analysis (2019). Personal consumption expenditures: chain-type price index. FRED, Federal Reserve Bank of St. Louis. https://fred.stlouisfed.org/series/PCEPI, April 27, 2019.
+
+		\bibitem[Wolak and Patrick(2001)]{Wolak}
+		Wolak, F., \& Patrick, R.
+(2001).
+The Impact of Market Rules and Market Structure on the Price Determination Process in the England and Wales Electricity Market.
+NBER Working Paper Series.
+https://doi.org/10.3386/w8248
+
+		\bibitem[Woo et al.(1996)]{Woo}
+		Woo, C., Chow, P., \& Horowitz, I. (1996). Optional real-time pricing of electricity for industrial firms. Pacific Economic Review, 1(1), 79–92. https://doi.org/10.1111/j.1468-0106.1996.tb00175.x
+
+		\bibitem[Zarnikau(1990)]{Zarnikau}
+		Zarnikau, J. (1990). Customer Responsiveness to Real-Time Pricing of Electricity. The Energy Journal, 11(4), 99. https://doi.org/10.5547/ISSN0195-6574-EJ-Vol11-No4-6
+
+	\end{thebibliography}
+
+	\clearpage
+
+	\section{Tables and Figures}
+
+	\begin{table}[!h] \centering 
 		\caption{Descriptive Statistics}
@@
 			Electricity Price (\$/kWh)     &     0.12 &     0.03 &    0.08 &    0.10 &     0.11 &     0.13 &      0.21 \\
-			Electricity Load (GwH) & 2454.97 &  2380.24 &  144.00 &  790.50 &  1869.50 &  3315.00 &  18621.00 \\
+			Electricity Load (gWh) & 2454.97 &  2380.24 &  144.00 &  790.50 &  1869.50 &  3315.00 &  18621.00 \\
 			Coal Price (\$/ton) &    46.00 &    17.68 &   24.04 &   33.43 &    41.40 &    51.83 &    107.49 \\
@@
 
-	\section{Results}
-	\label{sec:results}
-
-	\begin{table}[t] \centering 
+	\begin{table}[!h] \centering 
 		\caption{OLS Regression Results}
@@
 
-	Based on the OLS results reported in \autoref{table:ols} we estimate the intertemporal elasticity of substitution for electricity consumption $\hat{\sigma}  = 1.305$ ($|t| > 24$) when accounting for all degree day covariates and state fixed effects.
-Additionally, we find that accounting for cooling and heating degree days captures a large amount of variation in demand for electricity; in the fixed effects regressions, adding these controls raises adjusted $R^2$ from 8.5\% to 51.8\%.
-Also, as expected, the coefficients on the degree day covariates are symmetrical; that is, the coefficient on $CDD_{t}$ is approximately the same as the negative of that on $CDD_{s}$, and the same applies to $HDD_{t}$ and $HDD_{s}$.
-\footnote{It is important to note that the reason they are not perfectly equal is because our regression data consists of each unique \textit{combination} of $(t,s)$ for each $i$; that is, if we have an arbitrary observation $(t,s,i)$ in our data, then $(s,t,i)$ does not also appear.
-Including these observations would not affect $\sigma$ and they also don't add any further information to our regression.
-However, they would make the magnitude of the estimated coefficients for  CDD$_t$ and CDD$_s$ equivalent (and likewise for HDDs).
-}  Furthermore, we found that electricity consumption seems to rise more in response to CDDs rather than HDDs.
-Next, we find that the sign on $\Delta_{t,s}$ is positive in all regressions, so electricity consumption rises over time independent of price.
-Specifically, fit (6) finds a coefficient of $0.000655$ which implies that electricity consumption rises, on average, by $\approx 0.7\%$ per year.
-Finally, adding state fixed effects seems to raise the estimates of $\sigma$ for all fits.
-
-	To account for endogeneity in the OLS results, we provide results for our IV specification in \autoref{table:iv}.
-Here, we find a much larger estimate of $\hat{\sigma}  = 5.818$ ($|t| > 11.1$) when considering all covariates and fixed effects.
-F-Statistics on all three specifications are significantly larger than 10, which suggests that the instruments are not weak \citep{SS1997}.
-These results greatly differ from the literature's estimates probably as a consequence of controlling for endogeneity.
-That is, ignoring variation on the supply side would bias OLS estimates for the effect of price on demand downwards; by controlling for this, we find larger estimates of $\sigma$ which is expected.
-Next, with respect to the demand controls, we find results similar to those of OLS.
-The magnitudes of the coefficients on DDs do not appear to be significantly different.
-Furthermore, we again find that CDDs affect electricity consumption more than HDDs.
-But, this time, the coefficients on heating degree days do not appear to be significant.
-Additionally, in contrast with the OLS results, we find a much larger estimate for the coefficient on $\Delta_{t,s}$ of $0.003$; this implies that electricity consumption seems to rise by about 3.65\% per year.
-So, overall, our IV results suggest much higher estimates of $\sigma$.
-
-	Finally, we control for nonlinear effects using a partially linear IV regression reported in \autoref{table:pariv}.
-Here, we find much smaller results than 2SLS when controlling for all possible covariates.
-Specifically, in fit (3), we have $\hat{\sigma} = 0.8847$ ($|t| > 20$).
-The estimates of $\sigma$ with fewer controls are much larger.
-However, based on the OLS and IV results, it seems that both the time control and degree day controls are significant.
-Hence, fit (3) is likely the most appropriate specification.
-Additionally, all of these estimates are significantly different from the 2SLS results which suggests that the 2SLS results are not robust.
-To be precise, our controls and instrument likely have non-linear effects on price and quantity which cannot be captured by linear models; this may explain why the 2SLS results differ significantly from these semiparametric results.
-Alternatively, this difference may also be because the errors in our regressions are not Gaussian.
-In any case, we  believe that our third semiparametric fit, $\hat{\sigma} = 0.8847$, is the most robust estimate of $\sigma$.
-We now discuss what this means for renewable energy policy in greater detail.
-
-	\begin{table}[h] 
+	\begin{table}[!h] 
 		\centering 
@@
 
-	\begin{table}[!t] 
+	\begin{table}[!h] 
 		\centering 
@@
 
-	\clearpage
-	\section{Discussion}
-	\label{sec:Discussion}
-
-	\subsection{The Elasticity of Substitution between Renewable and Fossil Energy}
-
-	We are concerned with how $\sigma$ affects the substitutability of fossil and renewable energy.
-This is important, because sufficient substitutability between these two technologies is required to transition into greener economy in the future.
-For instance, \citet{Ace2012} provide a model where they argue that, ``When the two
-	sectors [clean and dirty energy] are substitutable but not sufficiently so, preventing an environmental disaster requires a permanent policy intervention.
-Finally, when the two sectors are complementary, the only way to stave off a disaster is to stop long-run growth." However, note that while our model sets the intertemporal elasticity of substitution for  electricity consumption $\sigma$ to a fixed value, we make no direct assumptions about the elasticity of substitution between different energy technologies.
-Instead, this latter elasticity is indirectly defined by the substitutability of electricity consumption between periods.
-To illustrate this, we parametrize and estimate our model numerically.
-
-	Firstly, let technology 1 be coal power and technology 2 be solar power.
-These two technologies exemplify consistent fossil energy and intermittent renewable energy.
-Furthermore,  let period $t$ represent peak hours and period $s$ represent off-peak hours.
-We assume that, holding prices equal, consumers prefer that approximately 60\% of their energy arrive in period $t$ and the remaining 40\% arrive in period $s$; that is, we have $\alpha_t = 0.6$ and $\alpha_s = 0.4$.
-Next, we normalize all quantity units to a MWh basis.
-Hence, we let $\xi$ represent the percent of capacity utilized in each period; we assume coal uses 100\% of its capacity in both periods, while solar can access 100\% during peak hours and only 10\% during the off-peak.
-Finally, we set the cost parameters, given in  \$ per MWh, equal to LCOE\footnote{ The LCOE for a generation technology is equal to the sum of its lifetime costs divided by its lifetime energy output.
-\citet{Joskow2011} explains the flaws of comparing generation technologies solely on the basis of LCOE; but,  our use of this measure is unrelated to his critique.
-That is, he argues that the economic value an intermittent technology should also account for when it produces electricity and the prices of electricity in those periods (see Table 2 of his paper).
-Our model does exactly this; but, we still need to  use LCOE to parametrize the cost of developing capacity.
-} estimates for 2023 from the \citet{EIALCOE}; specifically, we use estimates for "Solar PV" and "Coal with 30\% CCS" from Table 1b.
-In total, we have the following parameters.
-
-	\begin{center}
-		\noindent \textbf{Example  A:} $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$. 
-		\label{Params: Example A}
-	\end{center}
-
-	We begin by exploring the implied elasticity of substitution between these two technologies. Recall, for any two commodities $i$ and $j$,  the elasticity of substitution $e_{i,j}$ is given by:
-	$$e_{i,j} = \frac{\partial \log (X_i/ X_j)}{\partial \log (c_j/c_i)}$$
-	where $c$ is their prices.
-This relationship is of particular interest, because many applied and theoretical models studying renewable and fossil energy impose a CES production structure between the two (see \citet{Pap}).
-That is, they assume that $e$ is a fixed constant between renewable and fossil energy.
-In our model, this is not the case; while directly deriving the equation for $e_{1,2}$ in our model is analytically intractable, we numerically estimate how it varies with $\log (c_2/c_1)$ and $\sigma$.
-
-	\begin{figure}[t]
+	\begin{figure}[!h]
 		\caption{The Elasticity of Substitution between Solar and Coal} 
@@
 
-	We plot our numerical estimates of $e_{1, 2}$, the elasticity of substitution between solar and coal power, in \autoref{fig:eosnum}.
-We generated these results by computing the optimal quantities of each technology given a range of relative prices $c_2/c_1$.
-Then, we numerically differentiated $\log(X_1/X_2)$ with respect to $\log(c_2/c_1)$ to estimate the elasticity of substitution between solar and coal.
-This numerically computed elasticity of substitution between solar and coal power, $e_{solar,coal}$, is shown in the lower subplot.
-We repeat this process with different values of $\sigma$, the elasticity of substitution in the consumer's utility function.
-Specifically, we use our estimate of $\hat{\sigma} = 0.8847\, (0.044)$ and its 95\%  confidence interval $(0.7985, 0.9709)$.
-Finally, after finding the optimal values of our quantities $X$, we filter all observations of our numerical simulation that correspond to edge cases -- solutions where $X, Z \leq  0$.
-
-	The first relationship we see in \autoref{fig:eosnum} is that $e_{1,2}$ varies non-linearly with the relative costs of each technology; in particular, it appears to take on a hockey stick shape.
-This shape is a result of both intermittency and costs.
-Intermittency reduces substitutability as overall energy generation becomes more intermittent.
-In other words, intermittency is a bigger issue for consumers when their energy supply is not consistent.
-This causes $e_{1,2}$ to fall when the majority of energy generated comes from solar; naturally, the latter occurs when $\log(c_2/c_1)$ is small (solar is relatively cheap).
-At the same time, quantities become more sensitive to costs when costs greatly differ.\footnote{We explore this point further in Appendix B in which we consider a numerical example where technologies are minimally intermittent.
-That is, we again consider a two-period, two-technology example, but assume that $\xi_1$ and $\xi_2$ are nearly constant over time.
-We plot our results in \autoref{fig:eosrange} and find that the elasticity of substitution takes on a u-shape.
-} That is, $e_{1,2}$ rises when the relative prices of solar and coal are very different.
-When these two effects interact, we see the elasticity of substitution between solar and coal takes on a hockey stick shape.
-
-	Additionally, note that the elasticity of substitution $e_{1,2}$ between solar and coal becomes larger and more non-linear as $\sigma$ rises.
-Firstly, the reason why  it becomes larger is fairly intuitive.
-When a consumer's intertemporal elasticity of substitution for electricity consumption $\sigma$ is large, they will be more sensitive to changes in the price of electricity and more willing to substitute their electricity consumption across periods.
-As a result, the intermittency of solar becomes less of an  issue for consumers, but its relative price with respect to coal will play a bigger role.
-Consequently, this implies that the elasticity of substitution $e_{1, 2}$ will be larger.
-Hence, in the lower subplot of \autoref{fig:eosnum}, we see that $e_{1, 2}$ rises with $\sigma$ when holding the  relative prices of each technology constant.
-Secondly, we find that $e_{1,2}$ becomes more u-shaped as $\sigma$ rises.
-This is because larger values of $\sigma$ weaken the disincentive created by intermittency.
-Consequently, the shape of the elasticity of substitution $e_{1,2}$ becomes more dependent on the relative costs.
-As argued earlier, when costs differ greatly between technologies, the elasticity of substitution $e_{1,2}$ is higher.
-
-	\subsection{Implications for Environmental Policy}
-
-	Overall, our results suggest that the elasticity of substitution between  renewable and fossil energy is not constant.
-Furthermore, it appears to fall with the level of intermittency.
-What implications does this result have?
-
-	\subsubsection{Revisiting Past Models}
-
-	To start, we consider how  a variable elasticity of substitution affects past models of the energy sector.
-As an example, consider the results of \citet{Ace2012}.
-Firstly, they find that the short-run cost of policy intervention is increasing with the elasticity of substitution between clean and dirty technologies.\footnote{ See Corollary 1 of their paper for a proof and intuitive explanation.} Additionally, their paper states that the cost of delaying intervention is increasing with the elasticity of substitution.
-Secondly, Acemoglu et al.
-argue that, when the discount rate and elasticity of substitution between clean and dirty energy ($e$) is sufficiently low, a disaster cannot be avoided under laissez-faire.\footnote{ See Proposition 9 of their paper.} And, finally, Acemoglu et al.
-find that, ``when the elasticity of substitution is high\dots\, a relatively small carbon tax is sufficient to redirect R\&D towards clean technologies."
-
-	Based on our results, each of these statements has a complementary interpretation in terms of intermittency.
-For instance, the first statement suggests that the cost of policy intervention is decreasing with the intermittency of clean technologies; the cost of delaying intervention is decreasing with intermittency as well.
-This is because the elasticity of substitution between renewables and fossil fuels becomes small when renewables are more intermittent.
-So, in other words, delaying policy intervention will be the most costly in regions with access to clean, non-intermittent energy (such as hydro and geothermal energy).
-Secondly,  when the discount rate is sufficiently low and the intermittency of clean energy is sufficiently high, a disaster cannot be avoided under laissez-faire.
-The intuition here is that, even if clean energy became relatively cheap, its intermittency would prevent it from adequately substituting for fossil energy.
-Finally, Acemoglu et al.
-argue that the size of a carbon tax should be inversely proportional to the elasticity of substitution and should decrease over time.
-Recall that, in our model, the elasticity of substitution $e$ changes with relative prices; when fossil fuels are relatively cheap, $e$ is large.
-Hence, this implies we need a relatively small carbon tax early on to spur research.
-As technological change makes renewables cheaper, fossil fuels will become relatively more expensive so $e$ will fall; thus, the carbon tax will need to increase over time.
-These dynamics (a rising carbon tax) contrast with the results of Acemoglu et al.
-who numerically show that an optimal carbon tax should decrease over time when $e$ is sufficiently large.
-A potential resolution to these contradictory solutions may be to take an intermediate route and maintain a constant carbon tax over time.
-
-	\begin{figure}[!t]
+	\begin{figure}[!h]
 		\caption{The Price Elasticity of Demand for Coal Power} 
@@
 
-	\subsubsection{Carbon Taxes and their Distributive Consequences}
-
-	Our results also suggest that carbon taxes can have important distributional consequences.
-Earlier, we showed that the elasticity of substitution between renewable and fossil fuels $(e)$ is non-constant and falls with the intermittency of present generation.
-This further implies that the elasticity of demand for generation technologies is non-constant as well.
-Specifically, the elasticity of demand for non-intermittent energy increases then decreases with respect to its own price.
-Using the earlier numerical example of solar and coal power, we show this explicitly in \autoref{fig:coalelas}.
-As the price of coal power rises significantly beyond its current price, demand gets more elastic because its price becomes the primary factor disincentivizing its use.
-But, initially, a rise in the cost of coal power causes its demand to become inelastic.
-This is because a rise in the price of coal shifts generation towards solar;  consequently, generation becomes more intermittent and demand for coal becomes less price sensitive since it is needed to help smooth electricity generation.
-This relationship should be of concern for policy makers considering a pollution tax.
-Consumers in regions without access to clean, non-intermittent energy will have the most inelastic demand for fossil fuels; hence, they will bear the greatest welfare losses from a tax on pollution/carbon.
-On the other hand, consumers in regions that have access to dispatchable, renewable energy such as hydropower will see smaller welfare losses; the demand for fossil fuels in these regions will not be as inelastic, because dirty generation can be replaced with non-intermittent, clean generation.
-All in all, if a carbon tax were implemented federally and its revenue were distributed equally, it may nevertheless function as an inequitable, between-state welfare transfer due to differences in the availability of renewable energy technology.
-This same argument would apply  to carbon quotas.
-
-	\begin{figure}[t]
+	\begin{figure}[!h]
 		\captionsetup{format=centerproper}
@@
 
-	\subsubsection{The Case for Subsidizing Battery Research}
-
-	However, there are alternative policies that can mitigate this distributional side effect.
-One such policy is a research subsidy for improving battery technologies.
-Reducing battery costs, improving their storage capacity, and reducing their  energy loss can allow intermittent renewables to far more easily substitute for traditional, fossil energy.
-To understand the magnitude of this effect, we again provide a numerical example using solar and coal.
-We aim to understand how batteries effect substitutability, so consider a parsimonious model where batteries are used to shift a portion of solar energy output from its high-output period to its low-output period.\footnote{Because we are only interested in the effects of batteries on $e$, we ignore the energy losses and costs of battery storage.
-Furthermore, if our goal instead was to economically optimize battery storage and deployment, we would have to   rewrite our model as a dynamic optimization problem and solve using optimal control theory.
-However, we set aside these complications and consider a second-best solution where batteries are used to shift a fraction of solar output from its low-output period to its high-output period.
-But, since we are shifting relatively marginal fractions of energy output, this is likely equivalent to the first-best solution.
-} Specifically, we initially parametrized solar with $\xi_{2} = (1, 0.1)$ implying that it functions at 100\% of its potential capacity during the peak and at 10\% of its potential capacity during the off-peak; this is far from matching consumer demand.
-So, we represent solar output with batteries using $\xi_2 = (0.95, 0.15)$ and $\xi_2 = (0.90, 0.20)$; this is equivalent to transferring 5\% and 10\% of solar output.
-We plot our results in \autoref{fig:battery}.
-It is immediately clear that making solar output more consistent through the day results in a large increase in the elasticity of substitution $e_{1,2}$.
-Moreover,  $e_{1,2}$ no longer tapers off around 4 as solar becomes the dominant source of electricity.
-Rather, with batteries, cost plays a much larger role in determining the optimal quantity of each technology even when solar is relatively cheap.
-Overall, shifting even a small fraction of solar output using batteries can significantly improve solar power's substitutability with coal.
-
-	\begin{table}[!t] \centering 
+	\begin{table}[!h] \centering 
 		\captionsetup{format=centerproper}
@@
 
-	Consequently, batteries can complement reductions in the cost of intermittent renewables and mitigate the distributional side effects of a carbon tax.
-As shown in \autoref{fig:battery}, the elasticity of substitution between solar and coal rises significantly as solar becomes less intermittent; this implies that a change in the relative price of solar would have a far greater effect on solar adoption if batteries were employed with solar.
-Hence, if policy makers aim to promote the use of renewables, they should subsidize research that reduces the cost of renewables as well as research that improves battery technology.
-Using both policy instruments can be more effective than either alone.
-Additionally, the second benefit of batteries is that they mitigate the distributional problems of a carbon tax.
-This is because, by reducing the intermittency of renewables, batteries make demand for fossil fuels less inelastic.
-We specifically show this elasticity would change with another numerical example in \autoref{table:storelas}; like  \autoref{fig:battery}, we model batteries that shift solar output towards the off-peak.
-We then estimate the elasticity of demand for coal power around its initial price; this elasticity is decreasing at an increasing rate with the percent shift in solar output.
-The practical implications of this are straightforward.
-Researching and implementing battery technology can reduce the welfare losses from a carbon tax.
-Moreover, regions without clean, consistent renewables would benefit in particular, because they will be able to combine intermittent technologies with better energy storage to help transition away from fossil fuel energy.
-In short, subsidizing battery research can reduce some of the unintended distributional consequences of carbon taxes while mitigating environmental damage.
-
-	\subsubsection{Learning-by-Doing and Intermittency}
-
-	Lastly, our results suggest that renewable subsidies aimed at correcting the positive externalities of ``learning-by-doing" should also vary geographically.
-This is because the adoption rate of a renewable technology depends on its intermittency and the pre-existing technologies used for generation.
-For instance, hydropower plants can easily substitute for fossil fuel technologies, because hydropower is non-intermittent.
-Consequently, developing a larger initial capacity of hydropower to promote learning-by-doing can be done with a relatively small subsidy.
-On the other hand, suppose a region's only source of renewable energy is wind power.
-In this case, the intermittency of wind power reduces its elasticity of substitution with fossil fuel technologies.
-Thus, relatively larger subsidies are required to raise the capacity of wind power.
-Furthermore, the intermittency of renewable technologies (especially wind and solar) is linked to the weather which varies geographically.
-Hence, two regions with access to the same intermittent renewables at the same cost may still experience differing levels of intermittency based on their location.
-So, optimal renewable subsidies may also vary geographically simply due to differences in the weather.
-Thirdly, as discussed earlier, the elasticity of substitution between clean and dirty energy rises when prices differ greatly.
-This implies that regions with relatively expensive renewables (relatively cheap fossil energy) can benefit more from subsidies; again, this can vary geographically since the costs of both fossil fuels and renewables vary geographically.
-So, in total, correcting the externality from learning-by-doing should take into account the geographic differences in the availability of renewable technologies, weather conditions that may influence renewable output, and the relative prices of renewable and fossil energy.
-
-	This implies that optimal renewable subsidies should differ geographically but only to the extent that the spillovers of learning-by-doing balance out differences in welfare gains.
-That is, recall that subsidies for renewables have two benefits: promoting learning-by-doing and raising consumer and producer surplus.
-The first effect  can spur innovation that affects technology in all regions while the latter effect is mostly local.
-Now, consider two edge-case policy solutions targeting one benefit but ignoring the other.
-The first extreme solution may be to maximize learning by doing while ignoring the effects of subsidies on welfare.
-This solution would suggest that we subsidize renewables wherever they can best substitute for fossil fuels.
-The other extreme solution would be to distribute subsidies almost equally to ensure welfare gains are equitable; this assumes policymakers do not want to concentrate welfare gains for some regions but not others.
-Since we know the effect of subsidies on renewable adoption varies geographically, these two extreme solutions must differ; in other words, there's likely a trade-off between efficiently and equitably promoting renewables.
-Consequently, ignoring an edge case, an intermediate choice between these two approaches is a valid second-best solution for policymakers looking to balance efficiency and equity.
-Alternatively, a first-best solution would simply maximize efficiency with the first approach and then make welfare outcomes more equitable with direct monetary transfers.
-And finally, like before with carbon taxes, improving battery technology can also help mitigate the distributional side effects of efficient renewable subsidies.
-
-	\subsection{Adjusting Future Models}
-
-	Given that traditional assumption of a CES relationship between renewable and fossil energy appears to be inaccurate, we offer two alternative approaches for future models.
-The first approach is to directly integrate our model within a given framework.
-The second approach is to assume a variable elasticity of substitution (VES) structure\footnote{ The VES function was originally introduced by \citet{VES}.} between clean and dirty energy.
-These two approaches have their own advantages/disadvantages and serve different purposes.
-
-	\subsubsection{Direct Integration}
-
-	The first approach is better suited for numerical models.
-For example, our model of the energy sector can be embedded within a Computational General Equilibrium (CGE) model.
-CGEs, specifically ones designed to study energy and environmental policy, tend to assume a CES relationship between generation technologies and treat electricity as a homogeneous good.
-On the other hand, our representation of the energy sector makes more realistic assumptions and directly models the source of imperfect substitutability between generation technologies -- intermittency.
-Consequently, embedding our model within a CGE would improve its predictive accuracy by giving it more realistic microfoundations.
-
-	Furthermore, implementation can be done with relatively few modifications to standard CGE.
-To start, CGEs already use CES utility to model consumer preferences.
-In order to integrate our method of modeling electricity consumption, a CGE practitioner need only to rewrite preferences as:
-	\begin{equation}
-	U =   \left( \sum_{i \neq elc} \alpha_{i} Z_{i}^\eta +  \alpha_{elc} \left( \sum_{t=1}^T \alpha_{elc,t} Z_{elc, t}^\phi \right)^{\eta/\phi} \right)^{1/\eta}
-	\end{equation}
-	where the intertemporal elasticity of substitution for electricity consumption is given by $\sigma = 1/(1-\phi)$,  the elasticity of substitution between all consumer goods is given by $1/(1-\eta)$, the consumption of each good is given by $Z_{i}$, and the consumption of electricity in each period $t$ is given by $Z_{elc, t}$.
-This can be simplified to:
-	\begin{align}
-	U &= \left(  \left( \sum_{i \neq elc} \alpha_{i} Z_{i}^\eta \right) + \alpha_{elc} Z_{elc}^\eta \right)^{1/\eta} \\
-	Z_{elc} &= \left(  \sum_{t=1}^T \alpha_{elc,t} Z_{elc, t}^\phi \right)^{1/\phi}
-	\end{align}
-	where $Z_{elc}$ is an aggregate electricity good.
-Next, we consider the production functions for electricity production in each period.
-These are simply linear, since the total  electricity produced in a period is equal to the sum of electricity produced by each technology in that period.
-That is, we have
-	\begin{equation}
-	Z_{elc,t} = \sum_i \xi_{i,t} X_i 
-	\end{equation}
-	where $X_i$ is a generation technology and $\xi_{i,t}$ is its output in period $t$.
-The parameters for $\xi_{1,t}$ must be estimated using additional data.
-For fossil fuels, $\xi_i$ can remain constant over time.
-For intermittent renewables, $\xi_{i,t}$ may be set to empirical estimates of the average output per unit of $X_i$ in period $t$.\footnote{ It is important to note that each period $t$ should describe a short time frame.
-For instance, each period may represent an hour of a day, or, as in our examples, we may have two periods that represent peak and off-peak.
-If larger periods are chosen, the underlying assumptions behind our model are no longer relevant.
-That is, technologies like coal and nuclear can change their output over longer periods of time to respond to changes in price; on the other hand, as discussed earlier, we assume here that output in each period is exogenous.}  Additionally, the supply-side equations for building capacity in each technology can be modeled using the usual  CGE approach; total cost is given by the sum of costs for each input factor and total quantity is given by a CES of the input factors used to build capacity $(X_i)$.
-Finally, since these functional forms equivalent\footnote{ Linear production functions simply a special case of CES production functions where the elasticity of substitution is arbitrarily high.} to those used in standard CGEs, they can be calibrated using the usual procedures and a social accounting matrix.
-So, overall, implementing our model within a CGE can be done in a fairly simple way.
-
-	\subsubsection{VES Approximation}
-
-	\begin{table}[t]
+	\begin{figure}[!h]
 		\captionsetup{format=centerproper}
@@
 		\end{tabular}
-	\end{table}
-
-	The second approach is to use a variable elasticity of substitution function to model the relationship between clean and dirty energy.
-A VES function would approximately capture the dynamics of $e$, the elasticity of substitution between clean and dirty technology,  while keeping a theoretical model relatively simple.
-The latter is because assuming a VES structure between clean and dirty energy only requires considering one more parameter than a traditional CES function.
-To be more precise, the VES function is defined in \citet{VES} as
-	\begin{align}
-	Z &= \gamma X_1^{\omega(1-\delta \rho)} \left( X_2 + (\rho - 1) X_1 \right)^{\omega \delta \rho} \\
-	e &= 1 + \beta (X_1 / X_2) \\
-	\beta &= (\rho - 1) / ( 1- \delta \rho ) 
-	\end{align}
-	\vspace{-4ex}
-	$$\gamma > 0, \quad \omega > 0, \quad0 < \delta < 1, \quad 0 \leq \delta \rho \leq 1 , \quad (X_2/X_1) >  -\beta $$
-	where $\omega, \delta, \rho$, and $\gamma$ are parameters.
-Additionally, $Z$ is the output, $X_1$ and $X_2$ are the inputs, and $e$ is the elasticity of substitution between $X_1$ and $X_2$.
-In our case, we can think of $Z$ as electricity output while $X_1$ and $X_2$ represent dirty and clean technology.
-Note that $e$ is a linear function of $X_1/X_2$; this relationship allows a VES function to approximate the effects of intermittency.
-To show why, we plot $e$ against its VES approximation $\hat{e}$ for solar and coal in \autoref{fig:ves}.
-This approximation was fit by running OLS against the numerical results for $e$ while holding the intercept fixed at 1.\footnote{ There also exists a VES function described by \citet{VES} with the form $e = \beta_0 + \beta (X_1/X_2)$.
-This function may provide a better approximation of $e$, but there is no tractable production function that underlies it for $\beta_0 \neq 1$.
-Hence, we only consider the case where $\beta_0 = 1$, since the entire point of taking a VES approximation, in this case, is for analytical tractability.
-} We can see that, as either the capacity of solar or coal dominates the market, the approximation becomes weaker.
-But, overall, it seems to mimic the shape of the true elasticity of substitution $e$ implied by our model of intermittency.
-Hence, a  VES function is a reasonable alternative to a CES function -- it better models intermittency while also maintaining parsimony.
-
-	One potential objection to using the VES function is that it assumes the elasticity of substitution $e$ approaches 1 when the majority of generation comes from renewables ($X_1/X_2 \to 0$).
-And, a VES structure assumes linear $e$ which does not seem to be the case in \autoref{fig:ves}.
-However, both these assumptions may still be fairly reasonable in the right context.
-That is, suppose renewable energy was highly intermittent and that the consumer's elasticity of substitution $\sigma = 1$.
-Firstly, this results in renewable  and fossil energy entering a Cobb-Douglas relationship ($e = 1$) as $X_1/X_2 \to 0$ which supports the VES assumption of an intercept of 1.
-Secondly, no matter the relative prices, whenever the renewable technology is highly intermittent, $e$ becomes perfectly linear with respect to $X_1/X_2$; this supports the VES assumption of linearity.
-The proofs for both are given in \hyperref[sec:asympeos]{Appendix A.C}.
-Hence, in these cases, a VES approximation  can perfectly match $e$.
-Additionally, even when consumer's elasticity of substitution is not $1$, $e$ may still be approximately linear; this is shown in \autoref{fig:ves_int} where we consider our estimated $\hat{\sigma} = 0.8847$.
-In short, the assumptions made by a VES structure may nevertheless be accurate in certain cases.
-
-	Overall, using a VES function is a reasonable alternative to directly modeling intermittency.
-It allows theorists to derive policy implications from intermittency without relying too heavily on numerical models.
-Furthermore, it keeps theory simple since the elasticity of substitution can be represented as a linear function of a single parameter $\beta$.
-And, this parameter can be estimated econometrically, so theoretical models assuming a VES structure can offer empirically-based results.
-Finally, it may even be of use for CGE modelers.
-Its structure is simple enough to be calibrated with a given set of data, while its implementation can produce simple but reasonably accurate models of energy sectors with intermittency.
-
-	\section{Conclusion}
-
-	In this paper, we have offered a framework for understanding the economics of intermittent renewable energy that bears in mind the critique offered by \citet{Joskow2011}.
-That is, our model evaluates the economic feasibility of a technology by integrating its production profile with the market value of electricity in equilibrium.
-Moreover, this equilibrium is reached using a fairly realistic model of consumer behavior.
-The empirical parameterization of our model and its numerical results suggest that the elasticity of substitution between renewable and fossil energy is non-constant.
-We have shown that this has important implications for policy and future models.
-
-	With respect to policy, we have shown (i) the welfare effects of carbon taxes and renewable subsidies depend on the intermittency of renewables and thus vary geographically; (ii) the effect that renewable subsidies have on promoting the adoption of renewables varies geographically; (iii) the combination of (i) and (ii) can create a trade-off between efficiently and equitably preventing climate change; (iv) subsidizing battery research can complement other policies by increasing the substitutability of renewable and fossil energy; (v) improving batteries can mitigate the unintentional distributional consequences of carbon taxes and research subsidies.
-Additionally, we have qualitatively evaluated the results of \citet{Ace2012} in a setting where renewables and fossil fuels have a non-linear elasticity of substitution.
-Based on their framework, we have further argued that: (vi) the short-run cost of policy intervention is decreasing with intermittency;  (vii) the cost of delaying intervention is decreasing with intermittency; (viii) when the discount rate is sufficiently low and the intermittency of renewables is sufficiently high, a laissez-faire equilibrium would require policy intervention to prevent disaster; (ix) when renewables are moderately intermittent, an optimal carbon tax should remain approximately constant over time.
-
-	Given how strongly the elasticity of substitution between renewable and fossil energy varies with relative price, future models of intermittency should not assume a CES structure.
-So, we have shown to integrate our framework within a numerical model, such as a CGE; this may improve predictive accuracy by providing more realistic microfoundations.
-On the other hand, theoretical models would be better served by more a analytically tractable alternative.
-Therefore, we suggest theoretical models use a VES production function to approximate the effect of intermittency on the elasticity of substitution between renewable and fossil energy.
-Under certain conditions, our own model simplifies to a VES case; hence, the VES production function can reasonably approximate for our full model in a more tractable way.
-
-	While constructing our model, we made several simplifications for tractability.
-For instance, we set aside modeling reliability -- stochastic or otherwise unpredictable variation in output.
-An aim for future research may be to develop a model of clean and dirty energy that incorporates both intermittency and reliability in a multi-period setting.
-This could involve integrating our framework with that of \citet{HH}.
-Additionally, another avenue for future research may be to explicitly model the effects of battery technology and how storage interacts with intermittency and reliability.
-Such models can offer more accurate predictions/suggestions for policymakers and bring theory closer to reality.
-
-	\pagebreak
+	\end{figure}
+
+	\clearpage
 
@@
 	\begin{table}[h!]
-		\caption*{\textbf{Table A.1:} Parameter Restrictions for $Z, X > 0$} 
+		\caption{Parameter Restrictions for $Z, X > 0$} 
 		\label{tab:paramrest}
@@
 Additionally, we use the \citet{Silverman} rule-of-thumb to select bandwidths.
-
+After estimating $E(Q \,|\,T)), (E(P\,|\,T,W),$ and $E(P\,|\,T))$ through kernel regressions, we finally regress
+	$$(Q - \hat{E}(Q \,|\,T)) = (\hat{E}(P\,|\,T,W) - \hat{E}(P\,|\,T)) \beta_d + u_d $$
+	to obtain $\hat{\beta}_d$. When Q and P represent the log differences in quantities and prices, $-\beta_d$ to $\sigma$ the elasticity of substitution. 
 	\pagebreak
@@
 
-	\begin{thebibliography}{9}
-
-		\bibitem[Acemoglu et al.(2012)]{Ace2012}
-		Acemoglu, D., Aghion, P., Bursztyn, L., \& Hemous, D. (2012). The Environment and Directed Technical Change. American Economic Review, 102(1), 131–166. https://doi.org/10.1257/aer.102.1.131
-
-		\bibitem[Adelman(1995)]{genie}
-		Adelman, M. A. (1995). The genie out of the bottle: World oil since 1970. MIT Press.
-
-		\bibitem[Ambec and Crampes(2012)]{AC2012}
-		Ambec, S., \& Crampes, C. (2012). Electricity provision with intermittent sources of energy. Resource and Energy Economics, 34(3), 319–336. https://doi.org/10.1016/j.reseneeco.2012.01.001
-
-		\bibitem[Aubin et al.(1995)]{Aubin}
-		Aubin, C., Fougere, D., Husson, E., \& Ivaldi, M.
-(1995).
-Real-time pricing of electricity for residential customers: Econometric analysis of an experiment.
-Journal Of Applied Econometrics, 10, S171–S191.
-
-		\bibitem[Borenstein(2012)]{Boren2012}
-		Borenstein, S. (2012). The Private and Public Economics of Renewable Electricity Generation. Journal of Economic Perspectives, 26(1), 67–92. https://doi.org/10.1257/jep.26.1.67
-
-		\bibitem[Chao(2011)]{Chao2011}
-		Chao, H. (2011). Efficient pricing and investment in electricity markets with intermittent resources. Energy Policy, 39(7), 3945–3953. https://doi.org/10.1016/j.enpol.2011.01.010
-
-		\bibitem[Climate Prediction Center(2019)]{CPC}
-		Climate Prediction Center (2019). Degree Days Statistics. National Oceanic and Atmospheric Administration. https://www.cpc.ncep.noaa.gov/products/analysis\_monitoring/cdus/degree\_days/
-
-		\bibitem[Delarue et al.(2010)]{Delarue}
-		Delarue, E., De Jonghe, C., Belmans, R., \& D’Haeseleer, W.
-(2010).
-Applying portfolio theory to the electricity sector: Energy versus power.
-Energy Economics, 33(1), 12–23.
-https://doi.org/10.1016/j.eneco.2010.05.003
-
-		\bibitem[Deryugina and Mackay(2017)]{Deryugina}
-		Deryugina, T., Mackay, A., \& Reif, J. (2017). The Long-Run Dynamics of Electricity Demand: Evidence from Municipal Aggregation. NBER Working Paper Series. https://doi.org/10.3386/w23483
-
-		\bibitem[EIA(2019a)]{EIANetgen}
-		Electricity Information Administration (2019a). Net generation, United States, all sectors, annual. Electricity Data Browser. https://www.eia.gov/electricity/data/browser
-
-		\bibitem[EIA(2019b)]{EIALCOE}
-		Electricity Information Administration (2019b).
-Levelized Cost and Levelized Avoided Cost of New Generation.
-Annual Energy Outlook 2019.
-https://www.eia.gov/outlooks/aeo/pdf/electricity\_generation.pdf
-
-		\bibitem[EIA(2019c)]{EIArenew}
-		Electricity Information Administration (2019c). U.S. renewable electricity generation has doubled since 2008. Today in Energy. https://www.eia.gov/todayinenergy/detail.php?id=38752
-
-		\bibitem[Fan and Hyndman(2011)]{Fan}
-		Fan, S., \& Hyndman, R. (2011). The price elasticity of electricity demand in South Australia. Energy Policy, 39(6), 3709–3719. https://doi.org/10.1016/j.enpol.2011.03.080
-
-		\bibitem[Foley et al.(2012)]{Foley2012}
-		Foley, A., Leahy, P., Marvuglia, A., \& Mckeogh, E.
-(2012).
-Current methods and advances in forecasting of wind power generation.
-Renewable Energy, 37(1), 1–8.
-https://doi.org/10.1016/j.renene.2011.05.033
-
-		\bibitem[Geroski(1957)]{Geroski2000}
-		Geroski, P. (2000). Models of technology diffusion. Research Policy. Elsevier B.V. https://doi.org/10.1016/S0048-7333(99)00092-X
-
-		\bibitem[Helm and Mier(2019)]{HH}
-		Helm, C., \& Mier, M. (2019). On the efficient market diffusion of intermittent renewable energies. Energy Economics, 80, 812–830. https://doi.org/10.1016/j.eneco.2019.01.017
-
-		\bibitem[Herriges et al.(1993)]{Herriges}
-		Herriges, J., Baladi, S., Caves, D., \& Neenan, B.
-(1993).
-The Response of Industrial Customers to Electric Rates Based Upon Dynamic Marginal Costs.
-The Review of Economics and Statistics, 75(3), 446.
-https://doi.org/10.2307/2109458
-
-		\bibitem[Joskow(2011)]{Joskow2011}
-		Joskow, P. (2011). Comparing the Costs of Intermittent and Dispatchable Electricity Generating Technologies. American Economic Review, 101(3), 238–241. https://doi.org/10.1257/aer.101.3.238
-
-		\bibitem[King and Shatrawka(2011)]{KS1994}
-		King, Kathleen, and Peter Shatrawka (1994). "Customer Response to a Permanent Time- Varying
-		Pricing Program in the United Kingdom." Laurits R. Christensen Associates, Madison,
-		Wisconsin.
-
-		\bibitem[Mohajeryami et al.(2016)]{Moha2016}
-		Mohajeryami, S., Moghaddam, I., Doostan, M., Vatani, B., \& Schwarz, P.
-(2016).
-A novel economic model for price-based demand response.
-Electric Power Systems Research, 135, 1–9.
-https://doi.org/10.1016/j.epsr.2016.03.026
-
-		\bibitem[Musgens and Neuhoff(2006)]{MN2006}
-		Musgens, F., \& Neuhoff, K. (2006). Modelling Dynamic Constraints in Electricity Markets and the Costs of Uncertain Wind Output. Faculty of Economics.
-
-		\bibitem[Neuhoff et al.(2007)]{NCK2007}
-		Neuhoff, K., Cust, J.
-\& Keats, K.
-(2007).
-Implications of intermittency and transmission constraints for renewables deployment.
-Cambridge Working Papers in Economics 0711, Faculty of Economics, University of Cambridge.
-
-		\bibitem[Newey(1990)]{Newey}
-		Newey, W. (1990). Efficient Instrumental Variables Estimation of Non-linear Models. Econometrica, 58(4), 809–837. https://doi.org/10.2307/2938351
-
-		\bibitem[ORNL(2004)]{ORNL}
-		ORNL (2004).
-Measurement practices for reliability and power quality.
-A toolkit of reliability measurement practices.
-U.S.
-Department of Energy.
-https://info.ornl.gov/sites/publications/Files/Pub57467.pdf
-
-		\bibitem[Papageorgiou et al.(2017)]{Pap}
-		Papageorgiou, C., Saarn, M., \& Schulte, P.
-(2017).
-Substitution between clean and dirty energy inputs: a macroeconomic perspective.(Author abstract).
-Review of Economics and Statistics, 99(2), 201–212.
-https://doi.org/10.1162/REST\_a\_00623
-
-		\bibitem[Reiss and White(2005)]{Reiss}
-		Reiss, P., \& White, M. (2005). Household Electricity Demand, Revisited. The Review of Economic Studies, 72(252), 853. Retrieved from http://search.proquest.com/docview/204335314/
-
-		\bibitem[Revankar(1971)]{VES}
-		Revankar, N. (1971). A Class of Variable Elasticity of Substitution Production Functions. Econometrica, 39(1), 61–71. https://doi.org/10.2307/1909140
-
-		\bibitem[Schwarz et al.(2002)]{Schwarz}
-		Schwarz, P., Taylor, T., Birmingham, M., \& Dardan, S.
-(2002).
-Industrial response to electricity real-time prices: short run and long run.
-Economic Inquiry, 40(4), 597–610.
-https://doi.org/10.1093/ei/40.4.597
-
-		\bibitem[Shahriari and Blumsack(2018)]{SB2018}
-		Shahriari, M., \& Blumsack, S. (2018). The capacity value of optimal wind and solar portfolios. Energy, 148, 992–1005. https://doi.org/10.1016/j.energy.2017.12.121
-
-		\bibitem[Silverman(1986)]{Silverman}
-		Silverman, B. (1986). Density estimation for statistics and data analysis. London; Chapman and Hall.
-
-		\bibitem[Zhou and Teng(2013)]{Zhou}
-		Zhou, S. \& Teng, F., (2013). Estimation of urban residential electricity demand in China using household survey data.(Statistical data). Energy Policy, 61, 394–402.
-
-		\bibitem[Staiger and Stock(1997)]{SS1997} 
-		Staiger, D., \& Stock, J. (1997). Instrumental Variables Regression with Weak Instruments. Econometrica, 65(3), 557–586. https://doi.org/10.2307/2171753
-
-		\bibitem[US BEA(2019)]{USBEA}
-		U.S. Bureau of Economic Analysis (2019). Personal consumption expenditures: chain-type price index. FRED, Federal Reserve Bank of St. Louis. https://fred.stlouisfed.org/series/PCEPI, April 27, 2019.
-
-		\bibitem[Wolak and Patrick(2001)]{Wolak}
-		Wolak, F., \& Patrick, R.
-(2001).
-The Impact of Market Rules and Market Structure on the Price Determination Process in the England and Wales Electricity Market.
-NBER Working Paper Series.
-https://doi.org/10.3386/w8248
-
-		\bibitem[Woo et al.(1996)]{Woo}
-		Woo, C., Chow, P., \& Horowitz, I. (1996). Optional real-time pricing of electricity for industrial firms. Pacific Economic Review, 1(1), 79–92. https://doi.org/10.1111/j.1468-0106.1996.tb00175.x
-
-		\bibitem[Zarnikau(1990)]{Zarnikau}
-		Zarnikau, J. (1990). Customer Responsiveness to Real-Time Pricing of Electricity. The Energy Journal, 11(4), 99. https://doi.org/10.5547/ISSN0195-6574-EJ-Vol11-No4-6
-
-	\end{thebibliography}
-
 \end{document}

### 2019-06-21 documents/draft.tex
Update draft
- fix NOAA CDD HDD reference

@@
 Additionally, also from the EIA, we obtain data on the average cost of coal for electricity generation for each state and month.\footnote{ The coal price data set contains a large number of missing values due to privacy concerns; however, we do not expect that these missing values are correlated with the data itself.} We deflated both electricity and coal prices over time using the PCEP Index provided by the  \cite{USBEA}.
-Finally, we collect data on HDDs and CDDs from the NOAA's \citet{CPC} for the same panel.
+Finally, we collect data on HDDs and CDDs from the NOAA's Climate Divisional Database (\citeyear{nCLIMDIV}) for the same panel.
 Then, we merge these three data sets and trim 1\% of outliers for a total of $818$ observations for each month and state.
@@
 
-		\bibitem[Climate Prediction Center(2019)]{CPC}
-		Climate Prediction Center (2019). Degree Days Statistics. National Oceanic and Atmospheric Administration. https://www.cpc.ncep.noaa.gov/products/analysis\_monitoring/cdus/degree\_days/
+		\bibitem[Vos et al.(2019)]{nCLIMDIV}
+		[dataset] Vos, R.S., Applequist, S., Squires, M., Durre, I., Menne, M.J., Williams, C.N., Fenimore, C., Gleason, K., Arndt, D.
+2019.
+``NOAA's Gridded Climate Divisional Dataset (CLIMDIV)", NOAA National Climatic Data Center.
+doi:10.7289/V5M32STR
 

### 2019-06-23 documents/draft.tex
Update draft
- fix references
- fix author info
- add transparency statement

@@
 \renewenvironment{thebibliography}[1]
-{\section*{References}%
+{\section{References}%
 	\@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}%
@@
 
-	\title{\singlespacing{\textbf{Efficient Pollution Abatement in Electricity Markets with Intermittent Renewable Energy}}\thanks{Saketh Aleti: Graduate Student, Department of Economics, Duke University, 419 Chapel Drive, 213 Social Sciences Bldg., Durham, NC 27708-0097, USA (email: sa400@duke.edu).
-Gal Hochman: Associate Professor, Department of Agriculture, Food \& Resource Economics, Cook Office Building, 55 Dudley Road, Room 116, New Brunswick, NJ 08901, USA (email: gal.hochman@rutgers.edu).}}
-
-	\author[]{Saketh Aleti and Gal Hochman}
-
-	\date{\vspace{-1em}}
+	\title{\singlespacing{\textbf{Efficient Pollution Abatement in Electricity Markets with Intermittent Renewable Energy}}}
+
+	\author[]{Saketh Aleti\thanks{Saketh Aleti: Graduate Student, Department of Economics, Duke University, 419 Chapel Drive, 213 Social Sciences Bldg., Durham, NC 27708-0097, USA (email: sa400@duke.edu).}  \, and  Gal Hochman\thanks{ Gal Hochman: Associate Professor, Department of Agriculture, Food \& Resource Economics, Rutgers University, 116 Cook Office Building, 55 Dudley Road, New Brunswick, NJ 08901, USA (email: gal.hochman@rutgers.edu).}}
+
+%	\date{\vspace{-1em}}
 
@@
 
-	This research was funded by the Sun Grant (122682). We would also like to thank Prof. Roger Klein and the participants of the NAREA 2019 Workshop for helpful comments.
+	This research was funded by the Sun Grant (122682). We would also like to thank Prof. Roger Klein and the participants of the NAREA 2019 Workshop for helpful comments.\\\\
+	\noindent
+	\textbf{Transparency and Openness Promotion Statement}: The data and code for replication are available \href{https://github.com/SA3291/Energy-Intermittency-Paper.git}{here}.
 
@@
 		\bibitem[Acemoglu et al.(2012)]{Ace2012}
-		Acemoglu, D., Aghion, P., Bursztyn, L., \& Hemous, D. (2012). The Environment and Directed Technical Change. American Economic Review, 102(1), 131–166. https://doi.org/10.1257/aer.102.1.131
+		Acemoglu, D., Aghion, P., Bursztyn, L., \& Hemous, D. 2012. ``The Environment and Directed Technical Change." \textit{American Economic Review} 102(1): 131–166. https://doi.org/10.1257/aer.102.1.131
 
 		\bibitem[Adelman(1995)]{genie}
-		Adelman, M. A. (1995). The genie out of the bottle: World oil since 1970. MIT Press.
+		Adelman, M. A. 1995. \textit{The Genie Out of the Bottle: World Oil since 1970}. MIT Press.
 
 		\bibitem[Ambec and Crampes(2012)]{AC2012}
-		Ambec, S., \& Crampes, C. (2012). Electricity provision with intermittent sources of energy. Resource and Energy Economics, 34(3), 319–336. https://doi.org/10.1016/j.reseneeco.2012.01.001
+		Ambec, S., \& Crampes, C. 2012. ``Electricity provision with intermittent sources of energy." \textit{Resource and Energy Economics} 34(3): 319–336. https://doi.org/10.1016/j.reseneeco.2012.01.001
 
@@
 		Aubin, C., Fougere, D., Husson, E., \& Ivaldi, M.
-(1995).
-Real-time pricing of electricity for residential customers: Econometric analysis of an experiment.
-Journal Of Applied Econometrics, 10, S171–S191.
+1995.
+``Real-time Pricing of Electricity for Residential Customers: Econometric Analysis of an Experiment." \textit{Journal Of Applied Econometrics} 10(S1): S171-S191.
+doi:10.1002/jae.3950100510
 
 		\bibitem[Borenstein(2012)]{Boren2012}
-		Borenstein, S. (2012). The Private and Public Economics of Renewable Electricity Generation. Journal of Economic Perspectives, 26(1), 67–92. https://doi.org/10.1257/jep.26.1.67
+		Borenstein, S. 2012. ``The Private and Public Economics of Renewable Electricity Generation." \textit{Journal of Economic Perspectives} 26(1): 67–92. https://doi.org/10.1257/jep.26.1.67
 
 		\bibitem[Chao(2011)]{Chao2011}
-		Chao, H. (2011). Efficient pricing and investment in electricity markets with intermittent resources. Energy Policy, 39(7), 3945–3953. https://doi.org/10.1016/j.enpol.2011.01.010
+		Chao, H. 2011. ``Efficient Pricing and Investment in Electricity Markets with Intermittent Resources." \textit{Energy Policy} 39(7): 3945–3953. https://doi.org/10.1016/j.enpol.2011.01.010
+
+		\bibitem[Delarue et al.(2010)]{Delarue}
+		Delarue, E., De Jonghe, C., Belmans, R., and D’Haeseleer, W.
+2010.
+``Applying Portfolio Theory to the Electricity Sector: Energy versus Power." \textit{Energy Economics} 33(1): 12–23.
+https://doi.org/10.1016/j.eneco.2010.05.003
+
+		\bibitem[Deryugina and Mackay(2017)]{Deryugina}
+		Deryugina, T., Mackay, A., and Reif, J. 2017. ``The Long-Run Dynamics of Electricity Demand: Evidence from Municipal Aggregation." \textit{NBER Working Paper Series} https://doi.org/10.3386/w23483
+
+		\bibitem[EIA(2019a)]{EIANetgen}
+		[dataset] Electricity Information Administration. 2019a. ``Net generation, United States, all sectors, annual. Electricity Data Browser." https://www.eia.gov/electricity/data/browser
+
+		\bibitem[EIA(2019b)]{EIALCOE}
+		Electricity Information Administration.
+2019b.
+``Levelized Cost and Levelized Avoided Cost of New Generation." \textit{Annual Energy Outlook 2019} https://www.eia.gov/outlooks/aeo/pdf/electricity\_generation.pdf
+
+		\bibitem[EIA(2019c)]{EIArenew}
+		Electricity Information Administration. 2019c. ``U.S. Renewable Electricity Generation has Doubled since 2008." \textit{Today in Energy} https://www.eia.gov/todayinenergy/detail.php?id=38752
+
+		\bibitem[Fan and Hyndman(2011)]{Fan}
+		Fan, S., \& Hyndman, R. 2011. ``The price elasticity of electricity demand in South Australia." \textit{Energy Policy} 39(6): 3709–3719. https://doi.org/10.1016/j.enpol.2011.03.080
+
+		\bibitem[Foley et al.(2012)]{Foley2012}
+		Foley, A., Leahy, P., Marvuglia, A., and Mckeogh, E.
+2012.
+``Current methods and advances in forecasting of wind power generation." \textit{Renewable Energy} 37(1): 1–8.
+https://doi.org/10.1016/j.renene.2011.05.033
+
+		\bibitem[Geroski(1957)]{Geroski2000}
+		Geroski, P. 2000. ``Models of technology diffusion." \textit{Research Policy}. https://doi.org/10.1016/S0048-7333(99)00092-X
+
+		\bibitem[Helm and Mier(2019)]{HH}
+		Helm, C. and Mier, M. 2019. ``On the Efficient Market Diffusion of Intermittent Renewable Energies." \textit{Energy Economics} 80: 812–830. https://doi.org/10.1016/j.eneco.2019.01.017
+
+		\bibitem[Herriges et al.(1993)]{Herriges}
+		Herriges, J., Baladi, S., Caves, D., and Neenan, B.
+1993.
+``The Response of Industrial Customers to Electric Rates Based Upon Dynamic Marginal Costs." \textit{The Review of Economics and Statistics} 75(3): 446-454.
+https://doi.org/10.2307/2109458
+
+		\bibitem[Joskow(2011)]{Joskow2011}
+		Joskow, P. 2011. ``Comparing the Costs of Intermittent and Dispatchable Electricity Generating Technologies." \textit{American Economic Review} 101(3): 238–241. https://doi.org/10.1257/aer.101.3.238
+
+		\bibitem[King and Shatrawka(2011)]{KS1994}
+		King, K. and Shatrawka, P. 1994. "Customer Response to a Permanent Time- Varying
+		Pricing Program in the United Kingdom." Madison, WI: Laurits R. Christensen Associates.
+
+		\bibitem[Mohajeryami et al.(2016)]{Moha2016}
+		Mohajeryami, S., Moghaddam, I., Doostan, M., Vatani, B., and Schwarz, P.
+2016.
+``A Novel Economic Model for Price-Based Demand Response." \textit{Electric Power Systems Research} 135: 1–9.
+https://doi.org/10.1016/j.epsr.2016.03.026
+
+		\bibitem[Musgens and Neuhoff(2006)]{MN2006}
+		Musgens, F., and Neuhoff, K. 2006.`` Modelling Dynamic Constraints in Electricity Markets and the Costs of Uncertain Wind Output."
+
+		\bibitem[Neuhoff et al.(2007)]{NCK2007}
+		Neuhoff, K., Cust, J. and Keats, K. 2007. ``Implications of intermittency and transmission constraints for renewables deployment." \textit{Cambridge Working Papers in Economics 0711}.
+
+		\bibitem[Newey(1990)]{Newey}
+		Newey, W. 1990. ``Efficient Instrumental Variables Estimation of Non-linear Models." \textit{Econometrica} 58(4): 809–837. https://doi.org/10.2307/2938351
+
+		\bibitem[ORNL(2004)]{ORNL}
+		Oak Ridge National Laboratory 2004.
+``Measurement Practices for Reliability and Power Quality.
+a Toolkit of Reliability Measurement Practices." U.S.
+Department of Energy.
+https://info.ornl.gov/sites/publications/Files/Pub57467.pdf
+
+		\bibitem[Papageorgiou et al.(2017)]{Pap}
+		Papageorgiou, C., Saarn, M., and Schulte, P.
+2017.
+``Substitution Between Clean and Dirty Energy Inputs: A Macroeconomic Perspective." \textit{Review of Economics and Statistics} 99(2): 201–212.
+https://doi.org/10.1162/REST\_a\_00623
+
+		\bibitem[Reiss and White(2005)]{Reiss}
+		Reiss, P., and White, M. 2005. ``Household Electricity Demand, Revisited." \textit{The Review of Economic Studies} 72(3): 853-883. http://www.jstor.org/stable/3700676
+
+		\bibitem[Revankar(1971)]{VES}
+		Revankar, N. 1971. ``A Class of Variable Elasticity of Substitution Production Functions." \textit{Econometrica} 39(1): 61–71. https://doi.org/10.2307/1909140
+
+		\bibitem[Schwarz et al.(2002)]{Schwarz}
+		Schwarz, P., Taylor, T., Birmingham, M., and Dardan, S.
+2002.
+``Industrial Response to Electricity Real-Time Prices: Short Run and Long Run." \textit{Economic Inquiry} 40(4): 597–610.
+https://doi.org/10.1093/ei/40.4.597
+
+		\bibitem[Shahriari and Blumsack(2018)]{SB2018}
+		Shahriari, M., and Blumsack, S. 2018. ``The Capacity Value of Optimal Wind and Solar Portfolios." \textit{Energy} 148: 992–1005. https://doi.org/10.1016/j.energy.2017.12.121
+
+		\bibitem[Silverman(1986)]{Silverman}
+		Silverman, B. 1986. \textit{Density Estimation for Statistics and Data Analysis}. London: Chapman and Hall.
+
+		\bibitem[Zhou and Teng(2013)]{Zhou}
+		Zhou, S. and Teng, F., 2013. ``Estimation of urban residential electricity demand in China using household survey data." \textit{Energy Policy} 61: 394–402.
+
+		\bibitem[Staiger and Stock(1997)]{SS1997} 
+		Staiger, D. and Stock, J. 1997. Instrumental Variables Regression with Weak Instruments. \textit{Econometrica} 65(3): 557–586. https://doi.org/10.2307/2171753
+
+		\bibitem[US BEA(2019)]{USBEA}
+		U.S. Bureau of Economic Analysis. 2019. ``Personal consumption expenditures: chain-type price index." \textit{FRED, Federal Reserve Bank of St. Louis}. https://fred.stlouisfed.org/series/PCEPI
 
@@
 
-		\bibitem[Delarue et al.(2010)]{Delarue}
-		Delarue, E., De Jonghe, C., Belmans, R., \& D’Haeseleer, W.
-(2010).
-Applying portfolio theory to the electricity sector: Energy versus power.
-Energy Economics, 33(1), 12–23.
-https://doi.org/10.1016/j.eneco.2010.05.003
-
-		\bibitem[Deryugina and Mackay(2017)]{Deryugina}
-		Deryugina, T., Mackay, A., \& Reif, J. (2017). The Long-Run Dynamics of Electricity Demand: Evidence from Municipal Aggregation. NBER Working Paper Series. https://doi.org/10.3386/w23483
-
-		\bibitem[EIA(2019a)]{EIANetgen}
-		Electricity Information Administration (2019a). Net generation, United States, all sectors, annual. Electricity Data Browser. https://www.eia.gov/electricity/data/browser
-
-		\bibitem[EIA(2019b)]{EIALCOE}
-		Electricity Information Administration (2019b).
-Levelized Cost and Levelized Avoided Cost of New Generation.
-Annual Energy Outlook 2019.
-https://www.eia.gov/outlooks/aeo/pdf/electricity\_generation.pdf
-
-		\bibitem[EIA(2019c)]{EIArenew}
-		Electricity Information Administration (2019c). U.S. renewable electricity generation has doubled since 2008. Today in Energy. https://www.eia.gov/todayinenergy/detail.php?id=38752
-
-		\bibitem[Fan and Hyndman(2011)]{Fan}
-		Fan, S., \& Hyndman, R. (2011). The price elasticity of electricity demand in South Australia. Energy Policy, 39(6), 3709–3719. https://doi.org/10.1016/j.enpol.2011.03.080
-
-		\bibitem[Foley et al.(2012)]{Foley2012}
-		Foley, A., Leahy, P., Marvuglia, A., \& Mckeogh, E.
-(2012).
-Current methods and advances in forecasting of wind power generation.
-Renewable Energy, 37(1), 1–8.
-https://doi.org/10.1016/j.renene.2011.05.033
-
-		\bibitem[Geroski(1957)]{Geroski2000}
-		Geroski, P. (2000). Models of technology diffusion. Research Policy. Elsevier B.V. https://doi.org/10.1016/S0048-7333(99)00092-X
-
-		\bibitem[Helm and Mier(2019)]{HH}
-		Helm, C., \& Mier, M. (2019). On the efficient market diffusion of intermittent renewable energies. Energy Economics, 80, 812–830. https://doi.org/10.1016/j.eneco.2019.01.017
-
-		\bibitem[Herriges et al.(1993)]{Herriges}
-		Herriges, J., Baladi, S., Caves, D., \& Neenan, B.
-(1993).
-The Response of Industrial Customers to Electric Rates Based Upon Dynamic Marginal Costs.
-The Review of Economics and Statistics, 75(3), 446.
-https://doi.org/10.2307/2109458
-
-		\bibitem[Joskow(2011)]{Joskow2011}
-		Joskow, P. (2011). Comparing the Costs of Intermittent and Dispatchable Electricity Generating Technologies. American Economic Review, 101(3), 238–241. https://doi.org/10.1257/aer.101.3.238
-
-		\bibitem[King and Shatrawka(2011)]{KS1994}
-		King, Kathleen, and Peter Shatrawka (1994). "Customer Response to a Permanent Time- Varying
-		Pricing Program in the United Kingdom." Laurits R. Christensen Associates, Madison,
-		Wisconsin.
-
-		\bibitem[Mohajeryami et al.(2016)]{Moha2016}
-		Mohajeryami, S., Moghaddam, I., Doostan, M., Vatani, B., \& Schwarz, P.
-(2016).
-A novel economic model for price-based demand response.
-Electric Power Systems Research, 135, 1–9.
-https://doi.org/10.1016/j.epsr.2016.03.026
-
-		\bibitem[Musgens and Neuhoff(2006)]{MN2006}
-		Musgens, F., \& Neuhoff, K. (2006). Modelling Dynamic Constraints in Electricity Markets and the Costs of Uncertain Wind Output. Faculty of Economics.
-
-		\bibitem[Neuhoff et al.(2007)]{NCK2007}
-		Neuhoff, K., Cust, J.
-\& Keats, K.
-(2007).
-Implications of intermittency and transmission constraints for renewables deployment.
-Cambridge Working Papers in Economics 0711, Faculty of Economics, University of Cambridge.
-
-		\bibitem[Newey(1990)]{Newey}
-		Newey, W. (1990). Efficient Instrumental Variables Estimation of Non-linear Models. Econometrica, 58(4), 809–837. https://doi.org/10.2307/2938351
-
-		\bibitem[ORNL(2004)]{ORNL}
-		ORNL (2004).
-Measurement practices for reliability and power quality.
-A toolkit of reliability measurement practices.
-U.S.
-Department of Energy.
-https://info.ornl.gov/sites/publications/Files/Pub57467.pdf
-
-		\bibitem[Papageorgiou et al.(2017)]{Pap}
-		Papageorgiou, C., Saarn, M., \& Schulte, P.
-(2017).
-Substitution between clean and dirty energy inputs: a macroeconomic perspective.(Author abstract).
-Review of Economics and Statistics, 99(2), 201–212.
-https://doi.org/10.1162/REST\_a\_00623
-
-		\bibitem[Reiss and White(2005)]{Reiss}
-		Reiss, P., \& White, M. (2005). Household Electricity Demand, Revisited. The Review of Economic Studies, 72(252), 853. Retrieved from http://search.proquest.com/docview/204335314/
-
-		\bibitem[Revankar(1971)]{VES}
-		Revankar, N. (1971). A Class of Variable Elasticity of Substitution Production Functions. Econometrica, 39(1), 61–71. https://doi.org/10.2307/1909140
-
-		\bibitem[Schwarz et al.(2002)]{Schwarz}
-		Schwarz, P., Taylor, T., Birmingham, M., \& Dardan, S.
-(2002).
-Industrial response to electricity real-time prices: short run and long run.
-Economic Inquiry, 40(4), 597–610.
-https://doi.org/10.1093/ei/40.4.597
-
-		\bibitem[Shahriari and Blumsack(2018)]{SB2018}
-		Shahriari, M., \& Blumsack, S. (2018). The capacity value of optimal wind and solar portfolios. Energy, 148, 992–1005. https://doi.org/10.1016/j.energy.2017.12.121
-
-		\bibitem[Silverman(1986)]{Silverman}
-		Silverman, B. (1986). Density estimation for statistics and data analysis. London; Chapman and Hall.
-
-		\bibitem[Zhou and Teng(2013)]{Zhou}
-		Zhou, S. \& Teng, F., (2013). Estimation of urban residential electricity demand in China using household survey data.(Statistical data). Energy Policy, 61, 394–402.
-
-		\bibitem[Staiger and Stock(1997)]{SS1997} 
-		Staiger, D., \& Stock, J. (1997). Instrumental Variables Regression with Weak Instruments. Econometrica, 65(3), 557–586. https://doi.org/10.2307/2171753
-
-		\bibitem[US BEA(2019)]{USBEA}
-		U.S. Bureau of Economic Analysis (2019). Personal consumption expenditures: chain-type price index. FRED, Federal Reserve Bank of St. Louis. https://fred.stlouisfed.org/series/PCEPI, April 27, 2019.
-
 		\bibitem[Wolak and Patrick(2001)]{Wolak}
-		Wolak, F., \& Patrick, R.
-(2001).
-The Impact of Market Rules and Market Structure on the Price Determination Process in the England and Wales Electricity Market.
-NBER Working Paper Series.
+		Wolak, F.
+and Patrick, R.
+2001.
+``The Impact of Market Rules and Market Structure on the Price Determination Process in the England and Wales Electricity Market." \textit{NBER Working Paper Series}.
 https://doi.org/10.3386/w8248
@@
 		\bibitem[Woo et al.(1996)]{Woo}
-		Woo, C., Chow, P., \& Horowitz, I. (1996). Optional real-time pricing of electricity for industrial firms. Pacific Economic Review, 1(1), 79–92. https://doi.org/10.1111/j.1468-0106.1996.tb00175.x
+		Woo, C., Chow, P., and Horowitz, I.
+1996.
+``Optional Real-Time Pricing of Electricity for Industrial Firms." \textit{Pacific Economic Review} 1(1): 79–92.
+https://doi.org/10.1111/j.1468-0106.1996.tb00175.x
 
 		\bibitem[Zarnikau(1990)]{Zarnikau}
-		Zarnikau, J. (1990). Customer Responsiveness to Real-Time Pricing of Electricity. The Energy Journal, 11(4), 99. https://doi.org/10.5547/ISSN0195-6574-EJ-Vol11-No4-6
+		Zarnikau, J. 1990. ``Customer Responsiveness to Real-Time Pricing of Electricity." \textit{The Energy Journal} 11(4): 99. https://doi.org/10.5547/ISSN0195-6574-EJ-Vol11-No4-6
 

### 2019-06-25 documents/draft.tex
Update simulation code and figures
- change figures to black and white
- update draft with new figures
- move appendix tables and figures

@@
 
-	\author[]{Saketh Aleti\thanks{Saketh Aleti: Graduate Student, Department of Economics, Duke University, 419 Chapel Drive, 213 Social Sciences Bldg., Durham, NC 27708-0097, USA (email: sa400@duke.edu).}  \, and  Gal Hochman\thanks{ Gal Hochman: Associate Professor, Department of Agriculture, Food \& Resource Economics, Rutgers University, 116 Cook Office Building, 55 Dudley Road, New Brunswick, NJ 08901, USA (email: gal.hochman@rutgers.edu).}}
+	\author[]{Saketh Aleti\thanks{Saketh Aleti: Graduate Student, Department of Economics, Duke University, 419 Chapel Drive, 213 Social Sciences Bldg., Durham, NC 27708-0097, USA (email: sa400@duke.edu).}  \, and  Gal Hochman\thanks{ Gal Hochman: Professor, Department of Agriculture, Food \& Resource Economics, Rutgers University, 116 Cook Office Building, 55 Dudley Road, New Brunswick, NJ 08901, USA (email: gal.hochman@rutgers.edu).}}
 
@@
 
-	This research was funded by the Sun Grant (122682). We would also like to thank Prof. Roger Klein and the participants of the NAREA 2019 Workshop for helpful comments.\\\\
+	This work was supported by the Northeast Sun Grant \#5701-RU-SDSU-G640. We would also like to thank Prof. Roger Klein and the participants of the NAREA 2019 Workshop for helpful comments.\\\\
 	\noindent
@@
 	\clearpage
+
+	\section{Appendix A: Supplementary Proofs}
+
+	\subsection{Cobb-Douglas Case with Two Periods \& Two Technologies}
+	\label{sec:cobbdoug}
+
+	In this section, we consider a simpler case of our general model to better understand its implications.
+Firstly, we restrict the utility function to its Cobb-Douglas form which is simply the case where the elasticity of substitution $\sigma = 1$.
+Secondly, we limit the number of periods and technologies to 2.
+And, thirdly, we normalize the prices such that our representative consumer's income $I$ is $1$.
+
+	\subsubsection{Equilibrium Results}
+
+	Firstly, our demand equations simplify to:
+	\begin{align}
+	Z_t &= \alpha_t / p_t \\
+	Z_s &= \alpha_s / p_s
+	\end{align}
+	where $t$ and $s$ are our two periods. Next, solving for the FOC condition for profit maximization, we have:
+	\begin{align*}
+	p &=  \xi^{-1} c \\
+	p &= \begin{pmatrix}
+	-\dfrac{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}  \\[2ex]
+	\dfrac{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}} 
+	\end{pmatrix} 
+	\end{align*}
+	And, substituting back into our demand equations, we find the equilibrium quantities for $Z$ and $X$. 
+	$$
+	Z = \begin{pmatrix}
+	\dfrac{\alpha _{t}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{c_{2}\,\xi _{\mathrm{1s}} - c_{1}\,\xi _{\mathrm{2s}}} \\[2ex]
+	\dfrac{\alpha _{s}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} 
+	\end{pmatrix}
+	\implies 
+	X = \begin{pmatrix}
+	\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}+\dfrac{\alpha _{s}\,\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} \\[2ex] 
+	-\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}-\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}
+	\end{pmatrix}
+	$$
+
+	Furthermore, we derive restrictions on the parameters $\xi$ and $c$ by assuming $Z, X > 0$.
+These restrictions are detailed in \autoref{tab:paramrest}.
+There are two possible sets of symmetrical restrictions.
+The first set, Case 1, assumes that technology 2 is more cost effective in period $t$, while the second set, Case 2, assumes that technology 1 is more cost effective in period $t$.
+If a given set of parameters do not fall into either case, we are left with an edge case where one of the technologies is not used.
+Additionally, these inequalities compare two types of efficiency -- output efficiency and cost efficiency; we define output efficiency as electricity output per unit of input and cost efficiency in terms of electricity output per dollar of input.
+We refer to the last set of restrictions as mixed, because they relate both cost and output efficiency.
+
+	\vspace{0.15in}
+	\begin{center}
+		[INSERT Table 7: Parameter Restrictions for $Z, X > 0$]
+	\end{center}
+	\vspace{0.15in}
+
+	\hfill\\
+	\begin{proof}
+		We aim to derive conditions on $\xi$ and $c$ required to have positive $Z$ and $X$, so we begin by assuming $X, Z  > 0$.
+Second, since the equations so far are symmetrical, note that there be two symmetrical sets of potential restrictions we must impose on the parameters.
+Thus, we first assume the inequality $c_1 \xi_{2t} - c_2 \xi_{1t} > 0$ to restrict ourselves to one of the two cases.
+This assumption results in the denominator of $Z_s$ being positive.
+Hence, we must also have $\xi_{1s}\xi_{2t} - \xi_{2s}\xi_{1t} > 0 $ for $Z_s > 0$.
+This same term appears in the numerator for $Z_t$, hence its denominator must be positive: $c_2 \xi_{1s} - c_1 \xi_{2s} > 0$.
+Now, rewriting these inequalities, we have:
+		\begin{align*}
+		c_1 \xi_{2t} - c_2 \xi_{1t} > 0 &\implies \xi_{2t}/c_2 > \xi_{1t}/c_1 \\
+		c_2 \xi_{1s} - c_1 \xi_{2s} > 0 &\implies \xi_{1s}/c_1 > \xi_{2s}/c_2 \\
+		\xi_{1s}\xi_{2t} - \xi_{2s}\xi_{1t} > 0 &\implies \xi_{1s}/\xi_{1t} > \xi_{2s}/\xi_{2t} \\
+		&\implies \xi_{1t}/\xi_{1s} < \xi_{2t}/\xi_{2s} 
+		\end{align*}
+		Note that the latter two restrictions can be derived from the former two.
+Additionally, we implicitly assume that we have $\xi > 0$.
+However, this is not necessary assumption, since $\xi$ invertible only requires $\xi_{1t} \xi_{2s} > 0$ or $\xi_{1s} \xi_{2t} > 0$.
+Instead, we may leave the latter two inequalities in the form $ \xi_{1s}\xi_{2t} > \xi_{2s}\xi_{1t}$ which remains valid when values of $\xi$ are equal to $0$.
+Lastly, the mixed efficiency restrictions come from $X > 0$.
+To start, for $X_1$, we have:
+		\begin{align*}
+		X_1 > 0 &\implies (\alpha_t \xi_{2s})(c_1 \xi_2t - c_2\xi_1t) + (\alpha_s \xi_{2t})(c_1 \xi_{2s} - c_2 \xi_{1s}) < 0\\
+		&\implies (\alpha_t \xi_{2s})(c_1 \xi_2t - c_2\xi_1t) < (\alpha_s \xi_{2t})(c_2 \xi_{1s} - c_1 \xi_{2s}) \\
+		&\implies (\xi_{2s}/\xi_{2t}) < (\alpha_s (c_2 \xi_{1s} - c_1 \xi_{2s}))/(\alpha_t(c_1 \xi_{2t} - c_2\xi_{1t})) \\
+		&\implies (\xi_{2s}/\xi_{2t}) < (\alpha_s (\xi_{1s}/c_1 -  \xi_{2s}/c_2))/(\alpha_t(\xi_{2t}/c_2 - \xi_{1t}/c_1)) 
+		\end{align*}
+		Similarly, for $X_2$, note that only the numerators differ; $\xi_{2s}$ is replaced with $-\xi_{1s}$ and $\xi_{2t}$ is replaced with $-\xi_{1t}$. Hence, we have
+		\begin{align*}
+		X_2 > 0 &\implies (\alpha_t \xi_{1s})(c_1 \xi_2t - c_2\xi_1t) + (\alpha_s \xi_{1t})(c_1 \xi_{2s} - c_2 \xi_{1s}) > 0\\
+		&\implies (\xi_{1s}/\xi_{1t}) > (\alpha_s (\xi_{1s}/c_1 -  \xi_{2s}/c_2))/(\alpha_t(\xi_{2t}/c_2 - \xi_{1t}/c_1)) 
+		\end{align*}
+		To double check, note that combining the inequalities from $X_1>0$ and $X_2 > 0$ leads to $\xi_{2s}/\xi_{2t} < \xi_{1s}/\xi_{1t}$.
+This is precisely the earlier result obtained from $Z > 0$.
+Again, it is  important to note that we assume $\xi > 0$ for to simplify the inequalities of $X_1 > 0$ and $X_2 > 0$ .
+Otherwise, we may leave the inequalities in their original forms and they are still valid when  $\xi_{1t} \xi_{2s} > 0$ or $\xi_{1s} \xi_{2t} > 0$.
+\\ \hfill
+	\end{proof}
+
+	Let us consider the set of restrictions belonging to Case 1.
+The first inequality, our initial assumption, states that technology 2 is relatively more cost effective in period $t$.
+The second inequality claims technology 1 is relatively more cost effective in period $s$.
+The implications are fairly straightforward; if a technology is to be used, it must have an absolute advantage in cost efficiency in at least one period.
+The third condition states that the relative output efficiency of technology 2 is greater than that of the first technology in period $t$.
+And, the fourth condition makes a symmetrical claim but for the technology 1 and period $s$.
+These latter two restrictions regarding output efficiency enter $Z$ and $X$ through $p$; they're simply a restatement of the invertibility of $\xi$ and can also be derived through the cost efficiency restrictions.
+
+	The mixed efficiency restrictions are less intuitive.
+Firstly, note that $\left(\xi_{1s}/c_1 - \xi_{2s}/c_2\right)$ is the difference in cost efficiency for the two technologies in period $s$; this is equivalent to the increase in $Z_s$ caused by shifting a marginal dollar towards technology 1.
+Similarly, the bottom term $\left( \xi_{2t}/c_2 - \xi_{1t}/c_1 \right)$ represents the change in $Z_t$ caused by shifting a marginal dollar towards technology 1.
+Both these terms are then multiplied by the share parameter of the utility function for their respective time periods.
+Furthermore, note that $\alpha_t$ $(\alpha_s)$ is the elasticity of utility with respect to $Z_t$ $(Z_t)$.
+Hence, in total, the mixed efficiency restrictions relate the relative cost efficiencies of each technology with their output efficiency and the demand for energy.
+So, for example, suppose that consumers prefer, \textit{ceteris paribus}, that nearly all their electricity arrives in period $t$.
+This would imply $\alpha_t$ is arbitrarily large which results in the left-hand side of the fraction becoming arbitrarily small.
+This violates the first mixed efficiency restriction but not the second; consequently, use of the first technology, which is less cost effective in period $t$, approaches $0$.
+
+	In more practical terms, suppose that our first technology is coal power and the latter is solar power.
+Although coal power is dispatchable, it does not easily ramp up or down within a day; hence, it is reasonable to apply our model where capacities are fixed over time so long as our time frame is sufficiently short.
+Hence, we now assume periods $t$ and $s$ represent the peak and off-peak for a day.
+And, we expect that there is more available solar radiation during peak hours than off-peak hours, since peak hours are usually during the middle of the day.
+This implies that the output efficiency of solar power is higher in period $t$ due to more available solar radiation.
+Additionally, since the energy output of a unit of coal is independent of time, we know that the output efficiency of coal is constant.
+In total, this implies that we have met the output efficiency restrictions, since we have $\xi_{2t}/\xi_{2s} > \xi_{1t}/\xi_{1s}$.
+Next, we can reasonably assume that coal is more cost effective than solar in the off-peak period when there is less sun; hence, the second cost efficiency restriction is satisfied.
+Then, for there to be an incentive to use solar power, we must satisfy the first cost-efficiency condition; that is, solar needs be cost effective during peak hours otherwise we hit an edge case where no solar is employed.
+And, finally, solar must also satisfy the mixed efficiency condition, which essentially implies that there must be sufficient demand for electricity during period $t$, when solar is more effective, for it to be a feasible technology.
+So, overall, for a technology to be economical, it must meet three conditions: it must the most cost effective technology for a particular period, it must have a comparative advantage in output efficiency in the same period, and there must be a sufficient amount of demand in that period.
+
+	%\footnote{This same analysis can be further extended to any $n$ technologies.
+However, the number restrictions and different cases to ensure $X , Z > 0$ expands very quickly ($O(n!)$).
+For instance, if we had 3 technologies and 3 periods, we must first assume each technology is more cost effective than the other two in a unique period; this adds 3*2 restrictions.
+Then, we must make the output efficiency restrictions comparing each pair of technologies for each pair of periods.}
+
+	\subsubsection{Comparative Statics}
+
+	The comparative statics are similarly intuitive.
+The equilibrium quantity of a technology is increasing with its output efficiency and decreasing with its cost per unit.
+Additionally, the equilibrium quantities for a particular technology move in the opposite direction with respect to the output efficiency and cost of the other technologies.
+For a practical example, consider again coal and solar power from before.
+An increase in the output efficiency of solar or a decrease in solar power's cost will reduce the optimal quantity of coal power.
+Likewise, as coal power's efficiency improves, it's adoption rises.
+To find the effects of $\alpha$ on $X$, we must assume one of the cases of restrictions shown in  \autoref{tab:paramrest}.
+So, again, let us assume Case 1 is true; this implies that $X_2$ is the most cost effective technology in period $t$ and likewise for $X_1$ in period $s$.
+Firstly, note that $\alpha$ determines the demand for electricity in a period.
+Hence, when $\alpha_t$ rises, we see the optimal level of $X_2$ rise as well; likewise, $X_1$ rises with $\alpha_s$.
+In short, the optimal quantity of a technology rises linearly with the demand for electricity in the period it specializes in.
+Moreover, these relationships are reversed with respect to demand in each technology's suboptimal period.
+So, for example, we would expect the use of solar energy to rise when the demand for electricity during peak hours rises, and it would fall when demand for energy in the off-peak rises.
+On the other hand, use coal power would rise with off-peak demand and fall with peak demand.
+This concept carries through for the comparative statics of $Z$.
+When the output efficiency of technology 1 rises or its cost falls, we see output $Z_s$ rise and output $Z_t$ fall.
+This is because technology 1 is optimal in period $s$ given the Case 1 restrictions.
+Likewise, we see symmetrical results for the output with respect to the cost and output efficiency of technology 2; improvements in the efficiency of $X_2$ result in greater output in $Z_t$ and smaller output in $Z_s$.
+
+	\hfill \\
+	\begin{proof}
+		We begin by deriving the comparative statics of the cost and efficiency parameters with respect to $X$.   Firstly, we take derivatives with respect to the cost vectors:
+		\begin{align*}
+		\frac{\partial X_1}{\partial c} &= 
+		\begin{pmatrix}
+		\dfrac{-\alpha _{t}\,{\xi _{\mathrm{2s}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}-\dfrac{\alpha _{s}\,{\xi _{\mathrm{2t}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}<0 \\
+		\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}+\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}>0
+		\end{pmatrix}\\
+		\frac{\partial X_2}{\partial c} &= 
+		\begin{pmatrix}
+		\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}+\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}>0 \\
+		\dfrac{-\alpha _{t}\,{\xi _{\mathrm{1s}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}-\dfrac{\alpha _{s}\,{\xi _{\mathrm{1t}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}<0
+		\end{pmatrix}
+		\end{align*}
+		The first and second terms of $\partial X_1 / \partial c_1$ are clearly both negative independent of the restrictions on the parameters.
+Similarly, all terms of  $\partial X_1 / \partial c_2$ are positive independent of any restrictions.
+Since the structure of this problem is symmetrical with respect to $X_1$ and $X_2$, the same comparative statics apply but in reverse for $X_1$.
+Next, we derive comparative statics for each element of $\xi$.
+		\begin{alignat*}{1}
+		\frac{\partial X_1}{\partial \xi} &= 
+		\begin{pmatrix}
+		\dfrac{\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}>0 & \dfrac{\alpha _{t}\,c_{2}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}>0 \\
+		\dfrac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}<0 & \dfrac{-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}<0 \\
+		\end{pmatrix}\\
+		\frac{\partial X_2}{\partial \xi} &= 
+		\begin{pmatrix}
+		\dfrac{-\alpha _{s}\,c_{1}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} <0& \dfrac{-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} <0\\
+		\dfrac{\alpha _{s}\,c_{1}\,\xi _{\mathrm{1t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}>0& \dfrac{\alpha _{t}\,c_{1}\,\xi _{\mathrm{1s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} >0\\
+		\end{pmatrix}
+		\end{alignat*}
+		Again, the signs are fairly straightforward.
+The optimal quantity of $X_1$ increases with its output efficiency in both periods; however, it decreases with the output efficiency of $X_2$ in both periods.
+Similarly, symmetrical results are shown for $X_2$.
+Next, we study the effects of $\alpha$ on $X$; this requires us to place some restrictions on the parameters, so we use those belonging to Case 1 in \autoref{tab:paramrest}.
+With $\alpha \equiv \left( \alpha_t \;\; \alpha_s \right)^T$,
+		\begin{align*}
+		\frac{\partial X_1}{\partial \alpha} &= 
+		\begin{pmatrix}
+		\dfrac{\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}<0 \\
+		\dfrac{\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}>0
+		\end{pmatrix}\\
+		\frac{\partial X_2}{\partial \alpha} &= 
+		\begin{pmatrix}
+		\dfrac{-\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}>0 \\
+		\dfrac{-\xi _{\mathrm{1t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}<0
+		\end{pmatrix}
+		\end{align*}
+		Note that our restrictions imply that $c_1 \xi_{2t} - c_2 \xi_{1t} > 0$ and $c_2 \xi_{1s} - c_1 \xi_{2s} > 0$.
+From here, the intuition is clear; we assume that $X_2$ is more cost efficient in period $t$, so increases in demand during period $t$ (caused by increases in $\alpha_t$) will increase the optimal quantity of $X_2$.
+And, the same applies to $X_1$ with respect to period $s$ and $\alpha_s$.
+Again, due to symmetry, the statics are reversed when the technologies are flipped.
+Similarly, the signs would also be flipped if we used the restrictions given by Case 2 instead.
+
+		Next, we derive the comparative statics for $Z$.
+From our restrictions, we have $\xi_{1s}\xi_{2t} > \xi_{2s}\xi_{1t}$.
+All the results above follow from this inequality and the cost efficiency restrictions.
+		\begin{align*}
+		\frac{\partial Z_t}{\partial c} &= 
+		\begin{pmatrix}
+		\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}>0\\
+		\dfrac{-\alpha _{t}\,\xi _{\mathrm{1s}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}<0
+		\end{pmatrix}\\
+		\frac{\partial Z_s}{\partial c} &= 
+		\begin{pmatrix}
+		\dfrac{-\alpha _{s}\,\xi _{\mathrm{2t}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} <0\\
+		\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} >0
+		\end{pmatrix}\\
+		\frac{\partial Z_t}{\partial \xi} &= 
+		\begin{pmatrix}
+		\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} < 0& \dfrac{-\alpha _{t}\,\xi _{\mathrm{2s}}\,\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} <0 \\
+		\dfrac{-\alpha _{t}\,\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} >0& \dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} >0\\
+		\end{pmatrix}\\
+		\frac{\partial Z_s}{\partial \xi} &= 
+		\begin{pmatrix}
+		\dfrac{-\alpha _{s}\,\xi _{\mathrm{2t}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}> 0& \dfrac{\alpha _{s}\,\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} > 0\\
+		\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} < 0& \dfrac{-\alpha _{s}\,\xi _{\mathrm{1t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} <0\\
+		\end{pmatrix}
+		\end{align*}
+		Again, recall that we have $c_1 \xi_{2t} - c_2 \xi_{1t} > 0$ and $c_2 \xi_{1s} - c_1 \xi_{2s} > 0$; the rest follows. And finally, we have:
+		\begin{align*}
+		\frac{\partial Z_t}{\partial \alpha} &= 
+		\begin{pmatrix}
+		\dfrac{-\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} > 0  \\
+		0
+		\end{pmatrix} \\
+		\frac{\partial Z_s}{\partial \alpha} &= 
+		\begin{pmatrix}
+		0 \\
+		\dfrac{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} > 0
+		\end{pmatrix}
+		\end{align*}
+		These are fairly trivial, since $Z_t = \alpha_t / p_t$ (and $Z_s = \alpha_s/ p_s$) and prices are positive. \\
+		\hfill
+	\end{proof}
+
+	%\subsection{Optimal Taxation}
+	%
+	%The following proof is a derivation of the optimal tax $\tau$ on $X_1$ in the case where it produces externalities. The marginal cost of pollution is given by $\gamma$. 
+	%\hfill \\
+	%\begin{proof} We aim to maximize welfare with respect to the tax $\tau$, hence our first order condition is:
+	%	\begin{align*}
+	%	0 &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial \gamma X_1}{\partial \tau} + \frac{\partial \tau X_1}{\partial \tau} \\
+	%	&=  \left( \underbrace{\frac{\partial CS}{\partial p}  + \frac{\partial PS}{\partial p}}_{= 0} - \frac{ \partial  \gamma X_1}{\partial p} + \frac{\partial \tau X_1}{\partial p} \right) \frac{\partial p}{\partial \tau} \\
+	%	&=  \left( 0 - \frac{ \partial  \gamma X_1}{\partial p} + \frac{\partial \tau X_1}{\partial p} \right) \frac{\partial p}{\partial \tau} \\
+	%	&=  - \gamma \frac{\partial  X_1}{\partial \tau} + \tau \frac{\partial  X_1}{\partial \tau}
+	%	\end{align*}
+	%	where the derivatives of producer and consumer surplus are eliminated by the envelope theorem. Therefore, we must have $\tau = \gamma$. \\
+	%	\hfill
+	%\end{proof}
+
+	\subsection{CES Production as a Special Case}
+
+	\label{sec:CESspecialcase}
+
+	Our framework nests the case where there exists a CES production structure between each technology.
+This occurs when each technology can only produce in a single, unique period; note that this is not a realistic scenario.
+For instance, this would occur if we had one technology that can only output electricity during the day and another that only outputs electricity at night.
+Anyways, in this case, the CES production function's elasticity parameter  will be equivalent to that of the consumer's CES utility function -- the intertemporal elasticity of substitution for electricity consumption.
+
+	\begin{proof}
+		Firstly, note that we can reindex our technologies such that $\xi$ is diagonal, since each technology only produces in one period.
+Hence, without loss of generality, we have diagonal $\xi$.
+Next, we may say that the electricity output in period $i$ is given by $Z_i = \xi_{i,i} X_i$.
+Now, recall that the FOC for profit-maximization is given by $p = \xi^{-1} c$, hence we have $p_i = c_i / \xi_{i,i}$.
+Combining these equations with the FOC for utility maximization, we have:
+		\begin{align*}
+		\frac{Z_i}{Z_j} &= \left( \frac{\alpha_i p_j}{\alpha_j p_i} \right)^\sigma \\
+		\implies \frac{ X_i }{X_j} &= \left( \frac{ \alpha_i p_j \xi_{j,j}^{1/\sigma} }{ \alpha_j p_i \xi_{i,i}^{1/\sigma} } \right)^\sigma \\
+		\implies \frac{ X_i }{X_j} &= \left( \frac{ \alpha_i c_j \xi_{j,j}^{1/\sigma - 1} }{ \alpha_j c_i \xi_{i,i}^{1/\sigma - 1} } \right)^\sigma
+		\end{align*}
+		By definition, the elasticity of substitution between any two, arbitrary technologies $i$ and $j$ is constant.
+Moreover, it can be shown that this FOC can be rearranged to give the following demand equation for each technology $i$
+		\begin{align}
+		X_i &= \left(\frac{\beta_i}{c_i} \right)^\sigma \frac{I}{P} \\
+		P &= \sum_t \beta_i^\sigma p_i^{1-\sigma}
+		\end{align}
+		where $\beta_i = \alpha_i \xi_{i,i}^{-\phi}$, $\sigma = 1 / (1-\phi)$, and $I$ is the consumers income.	So, in total, accounting for both the producer and consumer's objectives, we are essentially solving for:
+		\begin{align*} 
+		V &= \left( \sum_i \beta_i X_i^\phi \right)^{(1/\phi)}  \\
+		\text{such that\quad} I &= \sum_i c_i X_i 
+		\end{align*}
+		This is a standard CES function.
+		\\ \hfill
+	\end{proof}
+
+	\subsection{Asymptotic Elasticity of Substitution}
+
+	\label{sec:asympeos}
+
+	Suppose we are in a two-period, two-technology setting with $\sigma = 1$.
+Furthermore, suppose that the output of our first technology is constant in both periods, $\xi_{1t} = \xi_{2t}$, but the output of our second technology is zero in the second period $\xi_{2s} = 0$.
+And, assume we have the parameter restrictions mentioned in earlier in \autoref{tab:paramrest} that ensure $X, Z > 0$.
+This is a simple case where we have (1) a constant output technology and (2) a highly intermittent technology.
+We now show that, in this case, the elasticity of substitution approaches $1$ as the relative cost of our second technology $c_2/c_1$ approaches $0$.
+Furthermore, we show that the elasticity of substitution between $X_1$ and $X_2$ is a linear function of $X_1/X_2$.
+
+	\begin{proof}
+		Firstly, note that from earlier we have:
+		$$
+		X = \begin{pmatrix}
+		\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}+\dfrac{\alpha _{s}\,\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} \\[2ex] 
+		-\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}-\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}
+		\end{pmatrix}
+		$$
+		Let $\xi_1 = \xi_{1t} = \xi_{2t}$ and note that $\xi_{2s} = 0$. Hence, we have:
+		$$
+		X = \begin{pmatrix}
+		\dfrac{\alpha _{s}\,\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1}}} \\
+		\dfrac{\alpha _{t}}{c_{2}}-\dfrac{\alpha _{s}\,\xi _{\mathrm{1}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1}}}
+		\end{pmatrix}
+		$$
+		Now, note that $X_1/X_2$ is given by:
+		\begin{align*}
+		\frac{X_1}{X_2} &= \frac{\alpha_s \xi_{2t} \left( c_2 ( c_1 \xi_{2t} - c_2 \xi_{1} ) \right)}{ \left( \alpha_t (c_1 \xi_{2t} - c_2 \xi_{1}) -  c_2 \alpha_s \xi_1 \right) (c_1 \xi_{2t} - c_2 \xi_{1t})}  \\
+		&= \frac{\alpha_s c_2 \xi_{2t}}{ \alpha_t (c_1 \xi_{2t} - c_2 \xi_{1}) -  c_2 \alpha_s \xi_1 }\\
+		&= \frac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{\xi _{1}\,\left(\alpha _{s}\,c_{2}+\alpha _{t}\,c_{2}\right)-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}} \\
+		&= \frac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}
+		\end{align*}
+		where $\alpha_t + \alpha_s = 1$ by definition (see \hyperref[sec:consumers]{Section II.A}).  Next, we can see that:
+		$$
+		\frac{\partial \log(X_1/X_2)}{c_1} = \frac{\alpha _{t}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}
+		$$
+		The elasticity of substitution $e_{1,2}$ is given by:
+		\begin{align*}
+		\frac{\partial \log(X_1/X_2)}{\partial \log(c_2/c_1)} &= \frac{\partial \log(X_1/X_2)}{\partial c_1}\frac{\partial c_1}{\partial \log(c_2/c_1)} \\
+		&= \left( \frac{\alpha _{t}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}} \right) \left( -c_1 \right)  \\
+		&= \frac{-c_1 \alpha _{t}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}\\
+		&= \left( \frac{c_2 \xi_1 }{-c_1 \alpha_t \xi_{2t}} + 1 \right)^{-1}
+		\end{align*}
+		Finally, it is simple to see that:
+		$$ \lim_{c_2/c_1 \to 0} \frac{\partial \log(X_1/X_2)}{\partial \log(c_2/c_1)} = 1$$
+		Additionally, we can see that the elasticity of substitution between $X_1$ and $X_2$ is linear with respect to $X_1/X_2$. That is, note that we may rewrite the elasticity above as:
+		\begin{align*}
+		\frac{\partial \log(X_1/X_2)}{\partial \log(c_2/c_1)} &= \frac{-c_1 \alpha _{t}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}} \\
+		&= \left( \frac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}} \right) \left( \frac{- \alpha_t c_1 \xi_{2t} }{- \alpha_s c_2 \xi_{2t}} \right)\\
+		&= \left( \frac{X_1}{X_2} \right) \left( \frac{ \alpha_t c_1  }{\alpha_s c_2 } \right)
+		\end{align*}
+		Hence, we have shown that $e$ can be written as a linear function of $X_1/X_2$. 
+		\\ \hfill
+	\end{proof}
+
+	\pagebreak
+
+	\section{Appendix B: Supplementary Figures}
+	\label{sec:AppendixB}
+
+	\autoref{fig:eosrange} below models the elasticity of substitution for two technologies that are close to being non-intermittent.
+That is, for technology 1, we have $\xi_1 = (0.95,\, 1)$, and, for technology 2, we have $\xi_2 = (1, \,0.95)$.
+We further set their costs, $c_1$ and $c_2$, to equal values and allow $\alpha_t = \alpha_s$.
+This example illustrates how the elasticity of substitution between technologies $e_{1,2}$ would appear with minimal intermittency.
+We can see that the $e_{1,2}$ takes on a u-shape.
+
+	\vspace{0.15in}
+	\begin{center}
+		[INSERT Figure 5: The Elasticity of Substitution Between Two  Minimally Intermittent Technologies]
+	\end{center}
+	\vspace{0.15in}
+
+	Additionally, we repeat the exercise done to produce \autoref{fig:ves} but with $\xi_2 = (1, 0.01)$.
+That is, we assume here that solar is far more intermittent.
+We plot our results below in 	\autoref{fig:ves_int}.
+
+	\vspace{0.15in}
+	\begin{center}
+		[INSERT Figure 6: The VES Approximation of the Elasticity of Substitution between Highly Intermittent Solar and Coal]
+	\end{center}
+	\vspace{0.15in}
+
+	\pagebreak
+
+	\section{Appendix C: Econometric Methodology}
+	\label{sec:AppendixC}
+
+	We aim to estimate $\sigma$ in the following set of equations:
+	\begin{align*}
+	\ln (Z_{ t, i} / Z_{ s, i}) &= -\sigma \ln (P_{t,i} / P_{s,i}) +  f \left( A_{t,i}, A_{s,i}, \Delta_{t,s} \right) + u_i \\
+	\ln (Z_{ t, i} / Z_{ s, i}) &= \beta \ln (P_{t,i} / P_{s,i}) + g \left( \ln (C_{t,i} / C_{s,i})  \right) + v_{i}
+	\end{align*}
+	We base our estimation procedure on \citet{Newey}. To start, for simplicity, let us rewrite the above set of equations as:
+	\begin{align*}
+	Q &= P \beta_d + f(T) + u \\
+	Q &= P \beta_s + g(W) + v 
+	\end{align*}
+	where $\beta_d$ is the parameter of interest. Furthermore, we assume that 
+	\begin{align*}
+	E(u \, | \, T, W) &= 0 \\
+	E(v \, | \, T, W) &= 0 
+	\end{align*}
+	Next, with $\alpha \equiv (\beta_d - \beta_s)^{-1}$ and assuming $\beta_d \neq \beta_s$, note that:
+	\begin{align*}
+	P &= (\beta_d - \beta_s)^{-1} \, \left(  g(W) - f(T) + u_s - u_d \right)  \\
+	E(P\,|\,T)   &= \alpha \left( E(g(W)|T) - f(T)  \right)\\
+	E(P\,|\,W)   &= \alpha \left( g(W) - E(f(T)|W)  \right) \\
+	E(P\,|\,T,W) &= \alpha \left( g(W) - f(T)     \right) 
+	\end{align*}
+	Now, differencing $Q$ with its conditional expectation, we have:
+	\begin{align*}
+	Q - E(Q \,|\,T) &= (P - E(P\,|\,T))\beta_d + (f(T) - E(f(T) \,|\,T)) + (u - E(u|T))\\
+	&= (\alpha(g(W) - E(g(W)|T)))\beta_d + 0 + u_d 
+	\end{align*}
+	Furthermore, it can be shown that:
+	$$E(P\,|\,T,W) - E(P\,|\,T) = \alpha (g(W) - E(g(W)|T))$$
+	Hence, we can regress 
+	$$(Q - E(Q \,|\,T)) = (E(P\,|\,T,W) - E(P\,|\,T)) \beta_d + u_d $$
+	to estimate $\beta_d$.
+But, we cannot know the true values of these expectations.
+Hence, we estimate each conditional expectation in this regression by using Nadaraya–Watson kernel regressions.
+This requires us to trim the data, so we drop 1\% of outliers of $Q, P, T$, and $W$.
+Additionally, we use the \citet{Silverman} rule-of-thumb to select bandwidths.
+After estimating $E(Q \,|\,T)), (E(P\,|\,T,W),$ and $E(P\,|\,T))$ through kernel regressions, we finally regress
+	$$(Q - \hat{E}(Q \,|\,T)) = (\hat{E}(P\,|\,T,W) - \hat{E}(P\,|\,T)) \beta_d + u_d $$
+	to obtain $\hat{\beta}_d$. When Q and P represent the log differences in quantities and prices, $-\beta_d$ to $\sigma$ the elasticity of substitution. 
+	\pagebreak
+	\pagebreak
 
@@
 	\end{table}
+	\clearpage
 
@@
 	\end{table} 
+	\clearpage
 
@@
 	\end{figure}
+	\clearpage
 
@@
 	\end{figure}
-
 	\clearpage
-
-	\section{Appendix A: Supplementary Proofs}
-
-	\subsection{Cobb-Douglas Case with Two Periods \& Two Technologies}
-	\label{sec:cobbdoug}
-
-	In this section, we consider a simpler case of our general model to better understand its implications.
-Firstly, we restrict the utility function to its Cobb-Douglas form which is simply the case where the elasticity of substitution $\sigma = 1$.
-Secondly, we limit the number of periods and technologies to 2.
-And, thirdly, we normalize the prices such that our representative consumer's income $I$ is $1$.
-
-	\subsubsection{Equilibrium Results}
-
-	Firstly, our demand equations simplify to:
-	\begin{align}
-	Z_t &= \alpha_t / p_t \\
-	Z_s &= \alpha_s / p_s
-	\end{align}
-	where $t$ and $s$ are our two periods. Next, solving for the FOC condition for profit maximization, we have:
-	\begin{align*}
-	p &=  \xi^{-1} c \\
-	p &= \begin{pmatrix}
-	-\dfrac{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}  \\[2ex]
-	\dfrac{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}} 
-	\end{pmatrix} 
-	\end{align*}
-	And, substituting back into our demand equations, we find the equilibrium quantities for $Z$ and $X$. 
-	$$
-	Z = \begin{pmatrix}
-	\dfrac{\alpha _{t}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{c_{2}\,\xi _{\mathrm{1s}} - c_{1}\,\xi _{\mathrm{2s}}} \\[2ex]
-	\dfrac{\alpha _{s}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} 
-	\end{pmatrix}
-	\implies 
-	X = \begin{pmatrix}
-	\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}+\dfrac{\alpha _{s}\,\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} \\[2ex] 
-	-\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}-\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}
-	\end{pmatrix}
-	$$
-
-	Furthermore, we derive restrictions on the parameters $\xi$ and $c$ by assuming $Z, X > 0$.
-These restrictions are detailed in \hyperref[tab:paramrest]{Table A.1}.
-There are two possible sets of symmetrical restrictions.
-The first set, Case 1, assumes that technology 2 is more cost effective in period $t$, while the second set, Case 2, assumes that technology 1 is more cost effective in period $t$.
-If a given set of parameters do not fall into either case, we are left with an edge case where one of the technologies is not used.
-Additionally, these inequalities compare two types of efficiency -- output efficiency and cost efficiency; we define output efficiency as electricity output per unit of input and cost efficiency in terms of electricity output per dollar of input.
-We refer to the last set of restrictions as mixed, because they relate both cost and output efficiency.
 
@@
 	\end{table}
-
-	\hfill\\
-	\begin{proof}
-		We aim to derive conditions on $\xi$ and $c$ required to have positive $Z$ and $X$, so we begin by assuming $X, Z  > 0$.
-Second, since the equations so far are symmetrical, note that there be two symmetrical sets of potential restrictions we must impose on the parameters.
-Thus, we first assume the inequality $c_1 \xi_{2t} - c_2 \xi_{1t} > 0$ to restrict ourselves to one of the two cases.
-This assumption results in the denominator of $Z_s$ being positive.
-Hence, we must also have $\xi_{1s}\xi_{2t} - \xi_{2s}\xi_{1t} > 0 $ for $Z_s > 0$.
-This same term appears in the numerator for $Z_t$, hence its denominator must be positive: $c_2 \xi_{1s} - c_1 \xi_{2s} > 0$.
-Now, rewriting these inequalities, we have:
-		\begin{align*}
-		c_1 \xi_{2t} - c_2 \xi_{1t} > 0 &\implies \xi_{2t}/c_2 > \xi_{1t}/c_1 \\
-		c_2 \xi_{1s} - c_1 \xi_{2s} > 0 &\implies \xi_{1s}/c_1 > \xi_{2s}/c_2 \\
-		\xi_{1s}\xi_{2t} - \xi_{2s}\xi_{1t} > 0 &\implies \xi_{1s}/\xi_{1t} > \xi_{2s}/\xi_{2t} \\
-		&\implies \xi_{1t}/\xi_{1s} < \xi_{2t}/\xi_{2s} 
-		\end{align*}
-		Note that the latter two restrictions can be derived from the former two.
-Additionally, we implicitly assume that we have $\xi > 0$.
-However, this is not necessary assumption, since $\xi$ invertible only requires $\xi_{1t} \xi_{2s} > 0$ or $\xi_{1s} \xi_{2t} > 0$.
-Instead, we may leave the latter two inequalities in the form $ \xi_{1s}\xi_{2t} > \xi_{2s}\xi_{1t}$ which remains valid when values of $\xi$ are equal to $0$.
-Lastly, the mixed efficiency restrictions come from $X > 0$.
-To start, for $X_1$, we have:
-		\begin{align*}
-		X_1 > 0 &\implies (\alpha_t \xi_{2s})(c_1 \xi_2t - c_2\xi_1t) + (\alpha_s \xi_{2t})(c_1 \xi_{2s} - c_2 \xi_{1s}) < 0\\
-		&\implies (\alpha_t \xi_{2s})(c_1 \xi_2t - c_2\xi_1t) < (\alpha_s \xi_{2t})(c_2 \xi_{1s} - c_1 \xi_{2s}) \\
-		&\implies (\xi_{2s}/\xi_{2t}) < (\alpha_s (c_2 \xi_{1s} - c_1 \xi_{2s}))/(\alpha_t(c_1 \xi_{2t} - c_2\xi_{1t})) \\
-		&\implies (\xi_{2s}/\xi_{2t}) < (\alpha_s (\xi_{1s}/c_1 -  \xi_{2s}/c_2))/(\alpha_t(\xi_{2t}/c_2 - \xi_{1t}/c_1)) 
-		\end{align*}
-		Similarly, for $X_2$, note that only the numerators differ; $\xi_{2s}$ is replaced with $-\xi_{1s}$ and $\xi_{2t}$ is replaced with $-\xi_{1t}$. Hence, we have
-		\begin{align*}
-		X_2 > 0 &\implies (\alpha_t \xi_{1s})(c_1 \xi_2t - c_2\xi_1t) + (\alpha_s \xi_{1t})(c_1 \xi_{2s} - c_2 \xi_{1s}) > 0\\
-		&\implies (\xi_{1s}/\xi_{1t}) > (\alpha_s (\xi_{1s}/c_1 -  \xi_{2s}/c_2))/(\alpha_t(\xi_{2t}/c_2 - \xi_{1t}/c_1)) 
-		\end{align*}
-		To double check, note that combining the inequalities from $X_1>0$ and $X_2 > 0$ leads to $\xi_{2s}/\xi_{2t} < \xi_{1s}/\xi_{1t}$.
-This is precisely the earlier result obtained from $Z > 0$.
-Again, it is  important to note that we assume $\xi > 0$ for to simplify the inequalities of $X_1 > 0$ and $X_2 > 0$ .
-Otherwise, we may leave the inequalities in their original forms and they are still valid when  $\xi_{1t} \xi_{2s} > 0$ or $\xi_{1s} \xi_{2t} > 0$.
-\\ \hfill
-	\end{proof}
-
-	Let us consider the set of restrictions belonging to Case 1.
-The first inequality, our initial assumption, states that technology 2 is relatively more cost effective in period $t$.
-The second inequality claims technology 1 is relatively more cost effective in period $s$.
-The implications are fairly straightforward; if a technology is to be used, it must have an absolute advantage in cost efficiency in at least one period.
-The third condition states that the relative output efficiency of technology 2 is greater than that of the first technology in period $t$.
-And, the fourth condition makes a symmetrical claim but for the technology 1 and period $s$.
-These latter two restrictions regarding output efficiency enter $Z$ and $X$ through $p$; they're simply a restatement of the invertibility of $\xi$ and can also be derived through the cost efficiency restrictions.
-
-	The mixed efficiency restrictions are less intuitive.
-Firstly, note that $\left(\xi_{1s}/c_1 - \xi_{2s}/c_2\right)$ is the difference in cost efficiency for the two technologies in period $s$; this is equivalent to the increase in $Z_s$ caused by shifting a marginal dollar towards technology 1.
-Similarly, the bottom term $\left( \xi_{2t}/c_2 - \xi_{1t}/c_1 \right)$ represents the change in $Z_t$ caused by shifting a marginal dollar towards technology 1.
-Both these terms are then multiplied by the share parameter of the utility function for their respective time periods.
-Furthermore, note that $\alpha_t$ $(\alpha_s)$ is the elasticity of utility with respect to $Z_t$ $(Z_t)$.
-Hence, in total, the mixed efficiency restrictions relate the relative cost efficiencies of each technology with their output efficiency and the demand for energy.
-So, for example, suppose that consumers prefer, \textit{ceteris paribus}, that nearly all their electricity arrives in period $t$.
-This would imply $\alpha_t$ is arbitrarily large which results in the left-hand side of the fraction becoming arbitrarily small.
-This violates the first mixed efficiency restriction but not the second; consequently, use of the first technology, which is less cost effective in period $t$, approaches $0$.
-
-	In more practical terms, suppose that our first technology is coal power and the latter is solar power.
-Although coal power is dispatchable, it does not easily ramp up or down within a day; hence, it is reasonable to apply our model where capacities are fixed over time so long as our time frame is sufficiently short.
-Hence, we now assume periods $t$ and $s$ represent the peak and off-peak for a day.
-And, we expect that there is more available solar radiation during peak hours than off-peak hours, since peak hours are usually during the middle of the day.
-This implies that the output efficiency of solar power is higher in period $t$ due to more available solar radiation.
-Additionally, since the energy output of a unit of coal is independent of time, we know that the output efficiency of coal is constant.
-In total, this implies that we have met the output efficiency restrictions, since we have $\xi_{2t}/\xi_{2s} > \xi_{1t}/\xi_{1s}$.
-Next, we can reasonably assume that coal is more cost effective than solar in the off-peak period when there is less sun; hence, the second cost efficiency restriction is satisfied.
-Then, for there to be an incentive to use solar power, we must satisfy the first cost-efficiency condition; that is, solar needs be cost effective during peak hours otherwise we hit an edge case where no solar is employed.
-And, finally, solar must also satisfy the mixed efficiency condition, which essentially implies that there must be sufficient demand for electricity during period $t$, when solar is more effective, for it to be a feasible technology.
-So, overall, for a technology to be economical, it must meet three conditions: it must the most cost effective technology for a particular period, it must have a comparative advantage in output efficiency in the same period, and there must be a sufficient amount of demand in that period.
-
-	%\footnote{This same analysis can be further extended to any $n$ technologies.
-However, the number restrictions and different cases to ensure $X , Z > 0$ expands very quickly ($O(n!)$).
-For instance, if we had 3 technologies and 3 periods, we must first assume each technology is more cost effective than the other two in a unique period; this adds 3*2 restrictions.
-Then, we must make the output efficiency restrictions comparing each pair of technologies for each pair of periods.}
-
-	\subsubsection{Comparative Statics}
-
-	The comparative statics are similarly intuitive.
-The equilibrium quantity of a technology is increasing with its output efficiency and decreasing with its cost per unit.
-Additionally, the equilibrium quantities for a particular technology move in the opposite direction with respect to the output efficiency and cost of the other technologies.
-For a practical example, consider again coal and solar power from before.
-An increase in the output efficiency of solar or a decrease in solar power's cost will reduce the optimal quantity of coal power.
-Likewise, as coal power's efficiency improves, it's adoption rises.
-To find the effects of $\alpha$ on $X$, we must assume one of the cases of restrictions shown in \hyperref[tab:paramrest]{Table A.1}.
-So, again, let us assume Case 1 is true; this implies that $X_2$ is the most cost effective technology in period $t$ and likewise for $X_1$ in period $s$.
-Firstly, note that $\alpha$ determines the demand for electricity in a period.
-Hence, when $\alpha_t$ rises, we see the optimal level of $X_2$ rise as well; likewise, $X_1$ rises with $\alpha_s$.
-In short, the optimal quantity of a technology rises linearly with the demand for electricity in the period it specializes in.
-Moreover, these relationships are reversed with respect to demand in each technology's suboptimal period.
-So, for example, we would expect the use of solar energy to rise when the demand for electricity during peak hours rises, and it would fall when demand for energy in the off-peak rises.
-On the other hand, use coal power would rise with off-peak demand and fall with peak demand.
-This concept carries through for the comparative statics of $Z$.
-When the output efficiency of technology 1 rises or its cost falls, we see output $Z_s$ rise and output $Z_t$ fall.
-This is because technology 1 is optimal in period $s$ given the Case 1 restrictions.
-Likewise, we see symmetrical results for the output with respect to the cost and output efficiency of technology 2; improvements in the efficiency of $X_2$ result in greater output in $Z_t$ and smaller output in $Z_s$.
-
-	\hfill \\
-	\begin{proof}
-		We begin by deriving the comparative statics of the cost and efficiency parameters with respect to $X$.   Firstly, we take derivatives with respect to the cost vectors:
-		\begin{align*}
-		\frac{\partial X_1}{\partial c} &= 
-		\begin{pmatrix}
-		\dfrac{-\alpha _{t}\,{\xi _{\mathrm{2s}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}-\dfrac{\alpha _{s}\,{\xi _{\mathrm{2t}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}<0 \\
-		\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}+\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}>0
-		\end{pmatrix}\\
-		\frac{\partial X_2}{\partial c} &= 
-		\begin{pmatrix}
-		\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}+\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}>0 \\
-		\dfrac{-\alpha _{t}\,{\xi _{\mathrm{1s}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}-\dfrac{\alpha _{s}\,{\xi _{\mathrm{1t}}}^2}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}<0
-		\end{pmatrix}
-		\end{align*}
-		The first and second terms of $\partial X_1 / \partial c_1$ are clearly both negative independent of the restrictions on the parameters.
-Similarly, all terms of  $\partial X_1 / \partial c_2$ are positive independent of any restrictions.
-Since the structure of this problem is symmetrical with respect to $X_1$ and $X_2$, the same comparative statics apply but in reverse for $X_1$.
-Next, we derive comparative statics for each element of $\xi$.
-		\begin{alignat*}{1}
-		\frac{\partial X_1}{\partial \xi} &= 
-		\begin{pmatrix}
-		\dfrac{\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}>0 & \dfrac{\alpha _{t}\,c_{2}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}>0 \\
-		\dfrac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}<0 & \dfrac{-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}<0 \\
-		\end{pmatrix}\\
-		\frac{\partial X_2}{\partial \xi} &= 
-		\begin{pmatrix}
-		\dfrac{-\alpha _{s}\,c_{1}\,\xi _{\mathrm{2t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} <0& \dfrac{-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} <0\\
-		\dfrac{\alpha _{s}\,c_{1}\,\xi _{\mathrm{1t}}}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}>0& \dfrac{\alpha _{t}\,c_{1}\,\xi _{\mathrm{1s}}}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} >0\\
-		\end{pmatrix}
-		\end{alignat*}
-		Again, the signs are fairly straightforward.
-The optimal quantity of $X_1$ increases with its output efficiency in both periods; however, it decreases with the output efficiency of $X_2$ in both periods.
-Similarly, symmetrical results are shown for $X_2$.
-Next, we study the effects of $\alpha$ on $X$; this requires us to place some restrictions on the parameters, so we use those belonging to Case 1 in \hyperref[tab:paramrest]{Table A.1}.
-With $\alpha \equiv \left( \alpha_t \;\; \alpha_s \right)^T$,
-		\begin{align*}
-		\frac{\partial X_1}{\partial \alpha} &= 
-		\begin{pmatrix}
-		\dfrac{\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}<0 \\
-		\dfrac{\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}>0
-		\end{pmatrix}\\
-		\frac{\partial X_2}{\partial \alpha} &= 
-		\begin{pmatrix}
-		\dfrac{-\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}>0 \\
-		\dfrac{-\xi _{\mathrm{1t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}<0
-		\end{pmatrix}
-		\end{align*}
-		Note that our restrictions imply that $c_1 \xi_{2t} - c_2 \xi_{1t} > 0$ and $c_2 \xi_{1s} - c_1 \xi_{2s} > 0$.
-From here, the intuition is clear; we assume that $X_2$ is more cost efficient in period $t$, so increases in demand during period $t$ (caused by increases in $\alpha_t$) will increase the optimal quantity of $X_2$.
-And, the same applies to $X_1$ with respect to period $s$ and $\alpha_s$.
-Again, due to symmetry, the statics are reversed when the technologies are flipped.
-Similarly, the signs would also be flipped if we used the restrictions given by Case 2 instead.
-
-		Next, we derive the comparative statics for $Z$.
-From our restrictions, we have $\xi_{1s}\xi_{2t} > \xi_{2s}\xi_{1t}$.
-All the results above follow from this inequality and the cost efficiency restrictions.
-		\begin{align*}
-		\frac{\partial Z_t}{\partial c} &= 
-		\begin{pmatrix}
-		\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}>0\\
-		\dfrac{-\alpha _{t}\,\xi _{\mathrm{1s}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2}<0
-		\end{pmatrix}\\
-		\frac{\partial Z_s}{\partial c} &= 
-		\begin{pmatrix}
-		\dfrac{-\alpha _{s}\,\xi _{\mathrm{2t}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} <0\\
-		\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} >0
-		\end{pmatrix}\\
-		\frac{\partial Z_t}{\partial \xi} &= 
-		\begin{pmatrix}
-		\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} < 0& \dfrac{-\alpha _{t}\,\xi _{\mathrm{2s}}\,\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} <0 \\
-		\dfrac{-\alpha _{t}\,\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} >0& \dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}\,\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}^2} >0\\
-		\end{pmatrix}\\
-		\frac{\partial Z_s}{\partial \xi} &= 
-		\begin{pmatrix}
-		\dfrac{-\alpha _{s}\,\xi _{\mathrm{2t}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2}> 0& \dfrac{\alpha _{s}\,\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} > 0\\
-		\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}\,\left(c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}\right)}{{\left(c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}\right)}^2} < 0& \dfrac{-\alpha _{s}\,\xi _{\mathrm{1t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} <0\\
-		\end{pmatrix}
-		\end{align*}
-		Again, recall that we have $c_1 \xi_{2t} - c_2 \xi_{1t} > 0$ and $c_2 \xi_{1s} - c_1 \xi_{2s} > 0$; the rest follows. And finally, we have:
-		\begin{align*}
-		\frac{\partial Z_t}{\partial \alpha} &= 
-		\begin{pmatrix}
-		\dfrac{-\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}} > 0  \\
-		0
-		\end{pmatrix} \\
-		\frac{\partial Z_s}{\partial \alpha} &= 
-		\begin{pmatrix}
-		0 \\
-		\dfrac{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} > 0
-		\end{pmatrix}
-		\end{align*}
-		These are fairly trivial, since $Z_t = \alpha_t / p_t$ (and $Z_s = \alpha_s/ p_s$) and prices are positive. \\
-		\hfill
-	\end{proof}
-
-	%\subsection{Optimal Taxation}
-	%
-	%The following proof is a derivation of the optimal tax $\tau$ on $X_1$ in the case where it produces externalities. The marginal cost of pollution is given by $\gamma$. 
-	%\hfill \\
-	%\begin{proof} We aim to maximize welfare with respect to the tax $\tau$, hence our first order condition is:
-	%	\begin{align*}
-	%	0 &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial \gamma X_1}{\partial \tau} + \frac{\partial \tau X_1}{\partial \tau} \\
-	%	&=  \left( \underbrace{\frac{\partial CS}{\partial p}  + \frac{\partial PS}{\partial p}}_{= 0} - \frac{ \partial  \gamma X_1}{\partial p} + \frac{\partial \tau X_1}{\partial p} \right) \frac{\partial p}{\partial \tau} \\
-	%	&=  \left( 0 - \frac{ \partial  \gamma X_1}{\partial p} + \frac{\partial \tau X_1}{\partial p} \right) \frac{\partial p}{\partial \tau} \\
-	%	&=  - \gamma \frac{\partial  X_1}{\partial \tau} + \tau \frac{\partial  X_1}{\partial \tau}
-	%	\end{align*}
-	%	where the derivatives of producer and consumer surplus are eliminated by the envelope theorem. Therefore, we must have $\tau = \gamma$. \\
-	%	\hfill
-	%\end{proof}
-
-	\subsection{CES Production as a Special Case}
-
-	\label{sec:CESspecialcase}
-
-	Our framework nests the case where there exists a CES production structure between each technology.
-This occurs when each technology can only produce in a single, unique period; note that this is not a realistic scenario.
-For instance, this would occur if we had one technology that can only output electricity during the day and another that only outputs electricity at night.
-Anyways, in this case, the CES production function's elasticity parameter  will be equivalent to that of the consumer's CES utility function -- the intertemporal elasticity of substitution for electricity consumption.
-
-	\begin{proof}
-		Firstly, note that we can reindex our technologies such that $\xi$ is diagonal, since each technology only produces in one period.
-Hence, without loss of generality, we have diagonal $\xi$.
-Next, we may say that the electricity output in period $i$ is given by $Z_i = \xi_{i,i} X_i$.
-Now, recall that the FOC for profit-maximization is given by $p = \xi^{-1} c$, hence we have $p_i = c_i / \xi_{i,i}$.
-Combining these equations with the FOC for utility maximization, we have:
-		\begin{align*}
-		\frac{Z_i}{Z_j} &= \left( \frac{\alpha_i p_j}{\alpha_j p_i} \right)^\sigma \\
-		\implies \frac{ X_i }{X_j} &= \left( \frac{ \alpha_i p_j \xi_{j,j}^{1/\sigma} }{ \alpha_j p_i \xi_{i,i}^{1/\sigma} } \right)^\sigma \\
-		\implies \frac{ X_i }{X_j} &= \left( \frac{ \alpha_i c_j \xi_{j,j}^{1/\sigma - 1} }{ \alpha_j c_i \xi_{i,i}^{1/\sigma - 1} } \right)^\sigma
-		\end{align*}
-		By definition, the elasticity of substitution between any two, arbitrary technologies $i$ and $j$ is constant.
-Moreover, it can be shown that this FOC can be rearranged to give the following demand equation for each technology $i$
-		\begin{align}
-		X_i &= \left(\frac{\beta_i}{c_i} \right)^\sigma \frac{I}{P} \\
-		P &= \sum_t \beta_i^\sigma p_i^{1-\sigma}
-		\end{align}
-		where $\beta_i = \alpha_i \xi_{i,i}^{-\phi}$, $\sigma = 1 / (1-\phi)$, and $I$ is the consumers income.	So, in total, accounting for both the producer and consumer's objectives, we are essentially solving for:
-		\begin{align*} 
-		V &= \left( \sum_i \beta_i X_i^\phi \right)^{(1/\phi)}  \\
-		\text{such that\quad} I &= \sum_i c_i X_i 
-		\end{align*}
-		This is a standard CES function.
-		\\ \hfill
-	\end{proof}
-
-	\subsection{Asymptotic Elasticity of Substitution}
-
-	\label{sec:asympeos}
-
-	Suppose we are in a two-period, two-technology setting with $\sigma = 1$.
-Furthermore, suppose that the output of our first technology is constant in both periods, $\xi_{1t} = \xi_{2t}$, but the output of our second technology is zero in the second period $\xi_{2s} = 0$.
-And, assume we have the parameter restrictions mentioned in earlier in \hyperref[sec:cobbdoug]{Section A} that ensure $X, Z > 0$.
-This is a simple case where we have (1) a constant output technology and (2) a highly intermittent technology.
-We now show that, in this case, the elasticity of substitution approaches $1$ as the relative cost of our second technology $c_2/c_1$ approaches $0$.
-Furthermore, we show that the elasticity of substitution between $X_1$ and $X_2$ is a linear function of $X_1/X_2$.
-
-	\begin{proof}
-		Firstly, note that from earlier we have:
-		$$
-		X = \begin{pmatrix}
-		\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}+\dfrac{\alpha _{s}\,\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} \\[2ex] 
-		-\dfrac{\alpha _{t}\,\xi _{\mathrm{1s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}-\dfrac{\alpha _{s}\,\xi _{\mathrm{1t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}}
-		\end{pmatrix}
-		$$
-		Let $\xi_1 = \xi_{1t} = \xi_{2t}$ and note that $\xi_{2s} = 0$. Hence, we have:
-		$$
-		X = \begin{pmatrix}
-		\dfrac{\alpha _{s}\,\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1}}} \\
-		\dfrac{\alpha _{t}}{c_{2}}-\dfrac{\alpha _{s}\,\xi _{\mathrm{1}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1}}}
-		\end{pmatrix}
-		$$
-		Now, note that $X_1/X_2$ is given by:
-		\begin{align*}
-		\frac{X_1}{X_2} &= \frac{\alpha_s \xi_{2t} \left( c_2 ( c_1 \xi_{2t} - c_2 \xi_{1} ) \right)}{ \left( \alpha_t (c_1 \xi_{2t} - c_2 \xi_{1}) -  c_2 \alpha_s \xi_1 \right) (c_1 \xi_{2t} - c_2 \xi_{1t})}  \\
-		&= \frac{\alpha_s c_2 \xi_{2t}}{ \alpha_t (c_1 \xi_{2t} - c_2 \xi_{1}) -  c_2 \alpha_s \xi_1 }\\
-		&= \frac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{\xi _{1}\,\left(\alpha _{s}\,c_{2}+\alpha _{t}\,c_{2}\right)-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}} \\
-		&= \frac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}
-		\end{align*}
-		where $\alpha_t + \alpha_s = 1$ by definition (see \hyperref[sec:consumers]{Section II.A}).  Next, we can see that:
-		$$
-		\frac{\partial \log(X_1/X_2)}{c_1} = \frac{\alpha _{t}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}
-		$$
-		The elasticity of substitution $e_{1,2}$ is given by:
-		\begin{align*}
-		\frac{\partial \log(X_1/X_2)}{\partial \log(c_2/c_1)} &= \frac{\partial \log(X_1/X_2)}{\partial c_1}\frac{\partial c_1}{\partial \log(c_2/c_1)} \\
-		&= \left( \frac{\alpha _{t}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}} \right) \left( -c_1 \right)  \\
-		&= \frac{-c_1 \alpha _{t}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}\\
-		&= \left( \frac{c_2 \xi_1 }{-c_1 \alpha_t \xi_{2t}} + 1 \right)^{-1}
-		\end{align*}
-		Finally, it is simple to see that:
-		$$ \lim_{c_2/c_1 \to 0} \frac{\partial \log(X_1/X_2)}{\partial \log(c_2/c_1)} = 1$$
-		Additionally, we can see that the elasticity of substitution between $X_1$ and $X_2$ is linear with respect to $X_1/X_2$. That is, note that we may rewrite the elasticity above as:
-		\begin{align*}
-		\frac{\partial \log(X_1/X_2)}{\partial \log(c_2/c_1)} &= \frac{-c_1 \alpha _{t}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}} \\
-		&= \left( \frac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}} \right) \left( \frac{- \alpha_t c_1 \xi_{2t} }{- \alpha_s c_2 \xi_{2t}} \right)\\
-		&= \left( \frac{X_1}{X_2} \right) \left( \frac{ \alpha_t c_1  }{\alpha_s c_2 } \right)
-		\end{align*}
-		Hence, we have shown that $e$ can be written as a linear function of $X_1/X_2$. 
-		\\ \hfill
-	\end{proof}
-
-	\pagebreak
-
-	\section{Appendix B: Supplementary Figures}
-	\label{sec:AppendixB}
-
-	\hyperref[fig:eosrange]{Figure B.1} below models the elasticity of substitution for two technologies that are close to being non-intermittent.
-That is, for technology 1, we have $\xi_1 = (0.95,\, 1)$, and, for technology 2, we have $\xi_2 = (1, \,0.95)$.
-We further set their costs, $c_1$ and $c_2$, to equal values and allow $\alpha_t = \alpha_s$.
-This example illustrates how the elasticity of substitution between technologies $e_{1,2}$ would appear with minimal intermittency.
-We can see that the $e_{1,2}$ takes on a u-shape.
+	\clearpage
 
@@
 	\end{figure}
-
-	\pagebreak
-
-	We repeat the exercise done to produce \hyperref[fig:ves]{Figure 4} but with $\xi_2 = (1, 0.01)$.
-That is, we assume here that solar is far more intermittent.
-We plot our results below in \hyperref[fig:ves_int]{Figure B.2}.
+	\clearpage
 
@@
 	\end{figure}
-
-	\pagebreak
-
-	\section{Appendix C: Econometric Methodology}
-	\label{sec:AppendixC}
-
-	We aim to estimate $\sigma$ in the following set of equations:
-	\begin{align*}
-	\ln (Z_{ t, i} / Z_{ s, i}) &= -\sigma \ln (P_{t,i} / P_{s,i}) +  f \left( A_{t,i}, A_{s,i}, \Delta_{t,s} \right) + u_i \\
-	\ln (Z_{ t, i} / Z_{ s, i}) &= \beta \ln (P_{t,i} / P_{s,i}) + g \left( \ln (C_{t,i} / C_{s,i})  \right) + v_{i}
-	\end{align*}
-	We base our estimation procedure on \citet{Newey}. To start, for simplicity, let us rewrite the above set of equations as:
-	\begin{align*}
-	Q &= P \beta_d + f(T) + u \\
-	Q &= P \beta_s + g(W) + v 
-	\end{align*}
-	where $\beta_d$ is the parameter of interest. Furthermore, we assume that 
-	\begin{align*}
-	E(u \, | \, T, W) &= 0 \\
-	E(v \, | \, T, W) &= 0 
-	\end{align*}
-	Next, with $\alpha \equiv (\beta_d - \beta_s)^{-1}$ and assuming $\beta_d \neq \beta_s$, note that:
-	\begin{align*}
-	P &= (\beta_d - \beta_s)^{-1} \, \left(  g(W) - f(T) + u_s - u_d \right)  \\
-	E(P\,|\,T)   &= \alpha \left( E(g(W)|T) - f(T)  \right)\\
-	E(P\,|\,W)   &= \alpha \left( g(W) - E(f(T)|W)  \right) \\
-	E(P\,|\,T,W) &= \alpha \left( g(W) - f(T)     \right) 
-	\end{align*}
-	Now, differencing $Q$ with its conditional expectation, we have:
-	\begin{align*}
-	Q - E(Q \,|\,T) &= (P - E(P\,|\,T))\beta_d + (f(T) - E(f(T) \,|\,T)) + (u - E(u|T))\\
-	&= (\alpha(g(W) - E(g(W)|T)))\beta_d + 0 + u_d 
-	\end{align*}
-	Furthermore, it can be shown that:
-	$$E(P\,|\,T,W) - E(P\,|\,T) = \alpha (g(W) - E(g(W)|T))$$
-	Hence, we can regress 
-	$$(Q - E(Q \,|\,T)) = (E(P\,|\,T,W) - E(P\,|\,T)) \beta_d + u_d $$
-	to estimate $\beta_d$.
-But, we cannot know the true values of these expectations.
-Hence, we estimate each conditional expectation in this regression by using Nadaraya–Watson kernel regressions.
-This requires us to trim the data, so we drop 1\% of outliers of $Q, P, T$, and $W$.
-Additionally, we use the \citet{Silverman} rule-of-thumb to select bandwidths.
-After estimating $E(Q \,|\,T)), (E(P\,|\,T,W),$ and $E(P\,|\,T))$ through kernel regressions, we finally regress
-	$$(Q - \hat{E}(Q \,|\,T)) = (\hat{E}(P\,|\,T,W) - \hat{E}(P\,|\,T)) \beta_d + u_d $$
-	to obtain $\hat{\beta}_d$. When Q and P represent the log differences in quantities and prices, $-\beta_d$ to $\sigma$ the elasticity of substitution. 
-	\pagebreak
-	\pagebreak
+	\clearpage
 

### 2019-06-25 code/simulation/sim_batteries.m

@@ -68,17 +68,35 @@ for j = 1:m
     subplot(2,1,1);
     hold on;
     
-    plot(-log(output(1,:)), log(output(2,:)), ...
-        'LineWidth', 1.5);
+    if j == 1
+        plot(-log(output(1,:)), log(output(2,:)), ...
+            'LineWidth', 1.5, 'LineStyle', '-',  'Color', [1 1 1]*0.0);
+    elseif j == 2
+        plot(-log(output(1,:)), log(output(2,:)), ...
+            'LineWidth', 1.5, 'LineStyle', '--', 'Color', [1 1 1]*0.2);
+    else
+        plot(-log(output(1,:)), log(output(2,:)), ...
+            'LineWidth', 1.5, 'LineStyle', '-.', 'Color', [1 1 1]*0.4);
+    end
     
     
     % relationship between log prices and quantities
     subplot(2,1,2);
     hold on;
-    plot(-log(output(1,2:end)), ...
-        diff(log(output(2,:)))./diff(-log(output(1,:))), ...
-        'LineWidth', 1.5);
     
+    if j == 1
+        plot(-log(output(1,2:end)), ...
+             diff(log(output(2,:)))./diff(-log(output(1,:))), ...
+            'LineWidth', 1.5, 'LineStyle', '-',  'Color', [1 1 1]*0.0);
+    elseif j == 2
+        plot(-log(output(1,2:end)), ...
+             diff(log(output(2,:)))./diff(-log(output(1,:))), ...
+            'LineWidth', 1.5, 'LineStyle', '--', 'Color', [1 1 1]*0.2);
+    else
+        plot(-log(output(1,2:end)), ...
+             diff(log(output(2,:)))./diff(-log(output(1,:))), ...
+            'LineWidth', 1.5, 'LineStyle', '-.', 'Color', [1 1 1]*0.4);
+    end
     
 end
 

### 2019-06-25 code/simulation/sim_elasticity.m

@@ -76,11 +76,11 @@ for j = 1:m
     elseif sigma < 0.8846
         plot(output(3,2:end)*100, ...
             diff(log(output(1,:)))./diff(log(output(4,:))), ...
-            'LineWidth', 1, 'LineStyle', '--', 'Color', [0 0 1]*0.8);
+            'LineWidth', 1, 'LineStyle', '--', 'Color', [1 1 1]*0.2);
     else
         plot(output(3,2:end)*100, ...
             diff(log(output(1,:)))./diff(log(output(4,:))), ...
-            'LineWidth', 1, 'LineStyle', '--', 'Color', [1 0 0]*0.8);
+            'LineWidth', 1, 'LineStyle', '-.', 'Color', [1 1 0]*0.4);
     end
     
 end

### 2019-06-25 code/simulation/sim_eos.m

@@ -70,13 +70,13 @@ for j = 1:m
     
     if sigma == 0.8847
         plot(-log(output(1,:)), log(output(2,:)), ...
-            'LineWidth', 1, 'Color', 'k');
+            'LineWidth', 1.25, 'Color', 'k');
     elseif sigma < 0.8846
         plot(-log(output(1,:)), log(output(2,:)), ...
-            'LineWidth', 1, 'LineStyle', '--', 'Color', [0 0 1]*0.8);
+            'LineWidth', 1, 'LineStyle', '--', 'Color', [1 1 1]*0.2);
     else
         plot(-log(output(1,:)), log(output(2,:)), ...
-            'LineWidth', 1, 'LineStyle', '--', 'Color', [1 0 0]*0.8);
+            'LineWidth', 1, 'LineStyle', '-.', 'Color', [1 1 1]*0.4);
     end
     
     
@@ -87,15 +87,15 @@ for j = 1:m
     if sigma == 0.8847
         plot(-log(output(1,2:end)), ...
             diff(log(output(2,:)))./diff(-log(output(1,:))), ...
-            'LineWidth', 1, 'Color', 'k');
+            'LineWidth', 1.25, 'Color', 'k');
     elseif sigma < 0.8846
         plot(-log(output(1,2:end)), ...
             diff(log(output(2,:)))./diff(-log(output(1,:))), ...
-            'LineWidth', 1, 'LineStyle', '--', 'Color', [0 0 1]*0.8);
+            'LineWidth', 1, 'LineStyle', '--', 'Color', [1 1 1]*0.2);
     else
         plot(-log(output(1,2:end)), ...
             diff(log(output(2,:)))./diff(-log(output(1,:))), ...
-            'LineWidth', 1, 'LineStyle', '--', 'Color', [1 0 0]*0.8);
+            'LineWidth', 1, 'LineStyle', '-.', 'Color', [1 1 1]*0.4);
     end
     
 end

### 2019-06-25 code/simulation/sim_eos_range.m

@@ -67,7 +67,9 @@ for j = 1:m
     % relationship between log prices and quantities
     subplot(2,1,1);
     hold on;
-    plot(-log(output(1,:)), log(output(2,:)), 'LineWidth', 1)
+    
+    plot(-log(output(1,:)), log(output(2,:)), 'LineWidth', 1, ...
+         'Color', [1, 1, 1]*((sigma-0.5)*1.5))
     
     
     % relationship between log prices and quantities
@@ -76,7 +78,7 @@ for j = 1:m
     
     plot(-log(output(1,2:end)), ...
         diff(log(output(2,:)))./diff(-log(output(1,:))), ...
-        'LineWidth', 1);
+        'LineWidth', 1, 'Color', [1, 1, 1]*((sigma-0.5)*2));
     
 end
 
@@ -84,7 +86,7 @@ end
 
 % Format subplot 1
 subplot(2,1,1);
-legend('0.5', '0.6', '0.7', '0.8', '9')
+legend('0.5', '0.6', '0.7', '0.8', '0.9')
 xlabel({'Negative Log Difference in Costs', 'log(c_2/c_1)'})
 ylabel({'Log Difference in Quantities', 'log(X_1/X_2)'})
 xlim([-2, 2]/500)

### 2019-06-25 code/simulation/sim_ves.m

@@ -66,19 +66,9 @@ for j = 1:m
     % relationship between e and the ratio of quantities
     hold on;
     
-    if sigma == 0.8847
-        plot(output(2,2:end), ...
-            diff(log(output(2,:)))./diff(-log(output(1,:))), ...
-            'LineWidth', 1.5, 'Color', 'k');
-    elseif sigma < 0.8846
-        plot(output(2,2:end), ...
-            diff(log(output(2,:)))./diff(-log(output(1,:))), ...
-            'LineWidth', 1, 'LineStyle', '--', 'Color', [0 0 1]*0.8);
-    else
-        plot(output(2,2:end), ...
-            diff(log(output(2,:)))./diff(-log(output(1,:))), ...
-            'LineWidth', 1, 'LineStyle', '--', 'Color', [1 0 0]*0.8);
-    end
+    plot(output(2,2:end), ...
+        diff(log(output(2,:)))./diff(-log(output(1,:))), ...
+        'LineWidth', 1.5, 'Color', 'k');
     
     % store data for average sigma assumption
     if sigma == 0.8847
@@ -108,7 +98,7 @@ beta = X'\(Y'-1);
 X_range = linspace(0, 50, 100);
 Y_hat = 1 + X_range.*beta;
 plot(X_range, Y_hat, 'LineStyle', '-.', 'LineWidth', 2.5, ...
-    'Color', [0.6, 0.1, 0.6]);
+    'Color', [1, 1, 1]*0.3);
 
 
 %% Plot formatting

### 2019-06-25 code/simulation/sim_ves_int.m

@@ -68,7 +68,7 @@ for j = 1:m
     
     plot(output(2,2:end), ...
         diff(log(output(2,:)))./diff(-log(output(1,:))), ...
-        'LineWidth', 1.5, 'Color', 'k');
+        'LineWidth', 2, 'Color', 'k');
     
     % store data for average sigma assumption
     mean_output = output;
@@ -95,7 +95,7 @@ beta = X'\(Y'-1);
 X_range = linspace(0, 50, 100);
 Y_hat = 1 + X_range.*beta;
 plot(X_range, Y_hat, 'LineStyle', '-.', 'LineWidth', 2.5, ...
-    'Color', [0.6, 0.1, 0.6]);
+    'Color', [1, 1, 1]*0.5);
 
 
 %% Plot formatting

### 2019-07-15 documents/draft.tex
Update draft
- remove unnecessary graphics path setting
Update draft and reg code
- add additional trimming option in regression
- update draft's econometrics discussion
- add figure for robustness check

@@
 
-% images
-\graphicspath{ {D:/Users/saketh/Documents/GitHub/Energy-Intermittency-Paper/figures/} }
-
 % multiline cells
@@
 
-	We collect monthly data from the \cite{EIANetgen} on retail electricity prices and consumption for each state in the US from 2011 to 2018.
-Additionally, also from the EIA, we obtain data on the average cost of coal for electricity generation for each state and month.\footnote{ The coal price data set contains a large number of missing values due to privacy concerns; however, we do not expect that these missing values are correlated with the data itself.} We deflated both electricity and coal prices over time using the PCEP Index provided by the  \cite{USBEA}.
+	We collect monthly data from the \cite{EIANetgen} on retail electricity prices and consumption for the 48 contiguous US states from 2010 to 2018.
+Also from the EIA, we obtain data on the average cost of coal for electricity generation for each state and month.\footnote{ The coal price data set contains a large number of missing values due to privacy concerns; however, we do not expect that these missing values are correlated with the data itself.} We deflated both electricity and coal prices over time using the PCEP Index provided by the  \cite{USBEA}.
 Finally, we collect data on HDDs and CDDs from the NOAA's Climate Divisional Database (\citeyear{nCLIMDIV}) for the same panel.
@@
 The estimates of $\sigma$ with fewer controls are much larger.
-However, based on the OLS and IV results, it seems that both the time control and degree day controls are significant.
-Hence, fit (3) is likely the most appropriate specification.
+However, both the time and degree day controls were highly significant in the OLS and IV results; thus, it seems appropriate to include both controls in this regression.
+That is, fit (3) is likely the most appropriate specification.
 Additionally, all of these estimates are significantly different from the 2SLS results which suggests that the 2SLS results are not robust.
-To be precise, our controls and instrument likely have non-linear effects on price and quantity which cannot be captured by linear models; this may explain why the 2SLS results differ significantly from these semiparametric results.
-Alternatively, this difference may also be because the errors in our regressions are not Gaussian.
+In other words, our controls and instrument likely have non-linear effects on price and quantity which cannot be captured by linear models.
+Alternatively, this difference may also be because the true error term is not Gaussian.
 In any case, we  believe that our third semiparametric fit, $\hat{\sigma} = 0.8847$, is the most robust estimate of $\sigma$.
-We now discuss what this means for renewable energy policy in greater detail.
 
@@
 	\vspace{0.15in}
+
+	We also consider additional robustness checks for the estimate in fit (3).
+Firstly, we check if outliers are affecting the results meaningfully.
+We run the fit (3) regression but trim a larger number of outliers.
+We find that trimming an additional 1\%, 5\%, or 10\% of outliers does not appear to significantly change the estimate of $\hat{\sigma}$ or meaningfully affect its standard error.
+Secondly, we test whether any particular states are driving the results.
+We run regress fit (3) on 48 subsamples; in each subsample, one of the 48 states in our data set is dropped out.
+We plot the results in the Appendix \autoref{fig:regstaterobust}.
+The mean and median of the estimates for $\sigma$ are  $0.8873$ and $0.8860$; additionally, 95\% of the estimates lie in $(0.8333, 0.9343)$.
+All of these estimates are highly significant -- the average $|t|$ value is $19.88$ and the smallest $|t|$ is $18.52$.
+Furthermore, it seems that most the drop out estimates do not differ significantly from the full sample estimate of $\hat{\sigma} = 0.8847$ (stdev = $0.044$).
+And, of the subsample estimates that do significantly differ, the magnitude of the difference does not appear to be economically meaningful.
+To elaborate on this and the practical meaning of $\sigma$, we now discuss what these estimates mean in the context of renewable energy policy.
 
@@
 
+	\autoref{fig:regstaterobust} is a robustness check for fit (3) of \autoref{table:pariv}.
+We regress fit (3) on subsamples where each state in our dataset is dropped out.
+In this figure, we plot the regression results; specifically, the estimated coefficients and the inverse of their standard error.
+
+	\vspace{0.15in}
+	\begin{center}
+		[INSERT Figure 5: Partially Linear IV Regression Estimates with State Drop Outs]
+	\end{center}
+	\vspace{0.15in}
+
 	\autoref{fig:eosrange} below models the elasticity of substitution for two technologies that are close to being non-intermittent.
@@
 	\begin{center}
-		[INSERT Figure 5: The Elasticity of Substitution Between Two  Minimally Intermittent Technologies]
+		[INSERT Figure 6: The Elasticity of Substitution Between Two  Minimally Intermittent Technologies]
 	\end{center}
@@
 	\begin{center}
-		[INSERT Figure 6: The VES Approximation of the Elasticity of Substitution between Highly Intermittent Solar and Coal]
+		[INSERT Figure 7: The VES Approximation of the Elasticity of Substitution between Highly Intermittent Solar and Coal]
 	\end{center}
@@
 			\hline \\[-1.8ex] 
-			\multicolumn{8}{@{}p{41.5em}@{}}{\textit{Note: } The underlying data covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable.
+			\multicolumn{8}{@{}p{41.5em}@{}}{\textit{Note: } The underlying data covers the 48 contiguous US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable.
 Each observation corresponds to a particular year, month, and state.
@@
 			\hline \\[-1.8ex] 
-			\multicolumn{7}{@{}p{41.4em}@{}}{\textit{Note: } The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
+			\multicolumn{7}{@{}p{41.4em}@{}}{\textit{Note: } The sample covers the 48 contiguous US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
 The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state.
@@
 			\multicolumn{7}{@{}p{41.5em}@{}}{\textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions.
-The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
+The sample covers the 48 contiguous US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
 The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state.
@@
 			\multicolumn{4}{@{}p{41.5em}@{}}{\textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions.
-The sample covers all 50 US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
+The sample covers the 48 contiguous US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
 The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state.
-The estimation procedure is described in the appendix.
+The estimation procedure is described \autoref{sec:AppendixC}.
+Conditional expectations are taken using a Gaussian Kernel with a bandwidth chosen according to \citet{Silverman}.
 Robust standard errors are reported in parentheses.
@@
 		\captionsetup{format=centerproper}
+		\caption{Partially Linear IV Regression Estimates with State Drop Outs} 
+		\label{fig:regstaterobust}
+		\footnotesize
+		\vspace{-1em}
+		\begin{tabular}{@{\extracolsep{0em}}c}
+			\includegraphics[width=0.75\linewidth]{../figures/regression_state_robustness_check.png} \\
+			\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } This is a joint plot of the IES  $\hat{\sigma}$ against the inverse of its estimated standard deviation from fit (3) of \autoref{table:pariv}.
+Each point represents an estimate obtained from regressing on a dataset that drops out one state from the full sample.
+Since the sample consists of the 48 contiguous US states, this regression is a decrease in sample size of 2.08\% relative to the full dataset.
+On the top and right side of the graph are histograms for the two variables.}     \\
+		\end{tabular}
+	\end{figure}
+	\clearpage
+
+	\begin{figure}[h!]
+		\captionsetup{format=centerproper}
 		\caption{The Elasticity of Substitution Between Two \newline  Minimally Intermittent Technologies} 

### 2019-07-16 documents/draft.tex
Update draft
- update semiparametric notebook robustness checks
- slight changes to results section

@@
 All of these estimates are highly significant -- the average $|t|$ value is $19.88$ and the smallest $|t|$ is $18.52$.
-Furthermore, it seems that most the drop out estimates do not differ significantly from the full sample estimate of $\hat{\sigma} = 0.8847$ (stdev = $0.044$).
-And, of the subsample estimates that do significantly differ, the magnitude of the difference does not appear to be economically meaningful.
-To elaborate on this and the practical meaning of $\sigma$, we now discuss what these estimates mean in the context of renewable energy policy.
+And, although, it seems that some of the estimates are (statistically) significantly  from the full sample estimate of $\hat{\sigma} = 0.8847$ (stdev = $0.044$), the magnitude of the difference does not appear to be economically meaningful.
+That is, the largest estimate of $\hat{\sigma}$ is 0.9793 which is only 0.0946 larger than the full sample estimate, while the smallest estimate is 0.8174 which is 0.0674 smaller than the full sample estimate.
+These differences are not meaningful in the practical application of our model.
+To elaborate on this and the full economic implications of $\sigma$, we now discuss what these estimates mean in the context of renewable energy policy.
 
@@
 
-	We are concerned with how $\sigma$ affects the substitutability of fossil and renewable energy.
+	To start, we consider how $\sigma$ affects the substitutability of fossil and renewable energy.
 This is important, because sufficient substitutability between these two technologies is required to transition into greener economy in the future.
-For instance, \citet{Ace2012} provide a model where they argue that, ``When the two
-	sectors [clean and dirty energy] are substitutable but not sufficiently so, preventing an environmental disaster requires a permanent policy intervention.
+For instance, \citet{Ace2012} provide a model where they argue that, ``When the two	sectors [clean and dirty energy] are substitutable but not sufficiently so, preventing an environmental disaster requires a permanent policy intervention.
 Finally, when the two sectors are complementary, the only way to stave off a disaster is to stop long-run growth." However, note that while our model sets the intertemporal elasticity of substitution for  electricity consumption $\sigma$ to a fixed value, we make no direct assumptions about the elasticity of substitution between different energy technologies.
@@
 We assume that, holding prices equal, consumers prefer that approximately 60\% of their energy arrive in period $t$ and the remaining 40\% arrive in period $s$; that is, we have $\alpha_t = 0.6$ and $\alpha_s = 0.4$.
+Since the union of both periods makes up only a single day, our model's assumption of an exogenous and constant $\xi$ is fairly reasonable in this context.
 Next, we normalize all quantity units to a MWh basis.

### 2019-10-12 documents/revision.tex
Create revision document

--- 2019-07-16 documents/draft.tex
@@
 	\begin{align*}
-	P &= (\beta_d - \beta_s)^{-1} \, \left(  g(W) - f(T) + u_s - u_d \right)  \\
+	P &= (\beta_d - \beta_s)^{-1} \, \left(  g(W) - f(T) + v - u \right)  \\
 	E(P\,|\,T)   &= \alpha \left( E(g(W)|T) - f(T)  \right)\\
@@
 	Q - E(Q \,|\,T) &= (P - E(P\,|\,T))\beta_d + (f(T) - E(f(T) \,|\,T)) + (u - E(u|T))\\
-	&= (\alpha(g(W) - E(g(W)|T)))\beta_d + 0 + u_d 
+	&= (\alpha(g(W) - E(g(W)|T)))\beta_d + 0 + u
 	\end{align*}
@@
 	$$(Q - \hat{E}(Q \,|\,T)) = (\hat{E}(P\,|\,T,W) - \hat{E}(P\,|\,T)) \beta_d + u_d $$
-	to obtain $\hat{\beta}_d$. When Q and P represent the log differences in quantities and prices, $-\beta_d$ to $\sigma$ the elasticity of substitution. 
+	to obtain $\hat{\beta}_d$.
+Recall the earlier substitution, $Q = \ln (Z_{ t, i} / Z_{ s, i})$ and $P = \ln (P_{t,i} / P_{s,i})$.
+So, we have  $-\beta_d$ being $\sigma$, the intertemporal elasticity of substitution.
 	\pagebreak
@@
 			\midrule
-			Electricity Price (\$/kWh)     &     0.12 &     0.03 &    0.08 &    0.10 &     0.11 &     0.13 &      0.21 \\
+			Electricity Price (\$/kWh)     &     0.1184 &     0.0279 &    0.0766 &    0.0987 &     0.1110 &     0.1287 &      0.2090 \\
 			Electricity Load (gWh) & 2454.97 &  2380.24 &  144.00 &  790.50 &  1869.50 &  3315.00 &  18621.00 \\

### 2019-12-21 documents/revision.tex
Revise paper
- revisions to introduction
- bolded matrices/vectors
- rewrote some of model equilibrium discussion
- fixed beginning of empirc method
- added motivation for nonlin iv
- clarified discussion sec A
- cleaned up appendix A.A
- added section on e derivation for special case
- updated e asymptotic case

@@
 
+%math shortcuts
+\DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator*{\argmin}{arg\,min}
+
 % hyperlinks
@@
 
+	% In this paper, we develop a model where consumers demand electricity over time
+
 	Renewable energy technologies have seen considerable adoption over the last few decades \citep{EIArenew}.
@@
 Moreover, traditional approaches such as the levelized cost of electricity (LCOE) fail to capture the true economic value of intermittent technologies, because they neglect to account for variation in output and prices over time \citep{Joskow2011}.
+
+	In this paper, we develop a model where we capture the effects of intermittency on the adoption of energy technologies.
+We do so through the demand-side of the market; specifically, we model consumers using a utility function that implies a preference for smoothing electricity consumption over time.
+We then parameterize our model empirically, implement our model numerically, and study the results.
 
@@
 Their papers empirically estimate the parameters for this function; we provide a more detailed discussion of the empirical literature in our \hyperref[sec:methodology]{Methodology}.} These two sides of the market reach an equilibrium through adjustments in prices of electricity in each period.
-Overall, we make many of the same assumptions that \citet{HH} do; we assume dynamic pricing,\footnote{ \citeauthor{HH} motivate models incorporating the dynamic pricing of electricity.
+Otherwise, we make many of the same assumptions that \citet{HH} do; we assume dynamic pricing,\footnote{ \citeauthor{HH} motivate models incorporating the dynamic pricing of electricity.
 They argue that such approaches to pricing will become the norm with further technological advances and coming regulatory changes.} no load rationing, and positive prices.
@@
 	Then, we parametrize our model empirically.
-We fit the parameters of the consumer's CES utility function using electricity consumption and price data for each US state.
-That is, we estimate the intertemporal elasticity of substitution for electricity consumption; this parameter plays a particularly important role in our model, since it captures the effects of intermittency on demand.
+We fit the parameters of the consumer's utility function using electricity consumption and price data for each US state.
+Since the consumer's CES utility function is composed of electricity consumption differentiated by time, the elasticity parameter represents the intertemporal elasticity of substitution for electricity consumption (IES); this parameter plays a particularly important role in our model, since it captures the effects of intermittency on demand.
 Next, to model the supply side, we narrow our framework to a two-period, two-technology setting to focus on the substitutability between renewable and fossil energy.
-We proxy for renewable and fossil energy using solar and coal; we parametrize each accordingly.
+We proxy for renewable and fossil energy using solar and coal, while parameterizing each accordingly.
 Finally, we implement our model numerically and provide suggestions for policy and future models.
 
-	Our results show that the elasticity of substitution between renewable and fossil energy is not constant.
+	Our results quantify the relationship between the intertemporal elasticity of substitution for electricity consumption  (IES) and the elasticity of substitution between renewable and fossil energy.
+The intuition behind the relationship is based on how the IES affects the desire for smoother consumption; when the IES is low, consumers want their electricity consumption to be smooth.
+Consequently, they disprefer intermittent sources of energy such as certain renewables.
+Consequently, the substitutability between renewables and fossils will be small.
+On the other hand, when the IES is high, consumers care less about smoothing their electricity consumption, so they are more willing to substitute between renewable and fossil energy.
+Furthermore, we find that the elasticity of substitution between renewable and fossil energy is not a simple, constant relationship.
 This is important because a significant amount of literature has assumed a CES structure between renewable and fossil energy (see \citet{Pap}); this assumption has been motivated, in part, by the need to capture imperfect substitutability between these two generation technologies as a result of intermittency.
-But, our model finds that the elasticity of substitution between renewable and fossil energy is far from constant as a \textit{consequence} of intermittency.
+But, our model finds that the elasticity of substitution between renewable and fossil energy is far from constant as a consequence of intermittency.
 Specifically, this elasticity appears to vary with the quantity of each energy technology.
 Hence, we argue against assuming a CES structure.
-Alternatively, we find that a VES production function can be used to approximate the relationship that our model finds between the elasticity of substitution and the quantities of each technology.
-That is, this relationship is roughly linear which is exactly what a VES function assumes.
+Alternatively, we find that a variable elasticity of substitution (VES) production function can be used to approximate the relationship that our model finds between the elasticity of substitution and the quantities of each technology.\footnote{ The VES production function was created by \citet{VES}; we describe it in further detail in the \hyperref[sec:VES]{discussion}.
+} That is, this relationship is roughly linear which is exactly what a VES function assumes.
 Moreover, a VES function is analytically tractable, so it can be implemented in other frameworks without making them overly complicated.
@@
 	Additionally, our results have multiple important implications for environmental/energy policy.
-Firstly, we find that the welfare burden of a carbon tax  and the effect of subsidies on renewable adoption both vary geographically.
+Firstly, show how the welfare burden of a carbon tax  and the effect of subsidies on renewable adoption both vary geographically.
 This variation is a consequence of differences in the intermittency and availability of renewable energy by location.
@@
 	\begin{equation}
-	U = \left( \sum_t \alpha_t Z_t^\phi  \right)^{1/\phi}
+	U = \left( \sum_t \alpha_t Z_t^\phi  \right)^{1/\phi} \quad \phi < 1
 	\end{equation}
 	where $\sigma = 1/(1-\phi)$ is the intertemporal elasticity of substitution for electricity consumption.
-To ensure that indifferences surfaces are convex, we have $\phi \in (0,1)$ or, equivalently,  $\sigma > 0$; additionally, since electricity consumption increases utility, we must have $\alpha_t > 0$ for all $t$.
+The restriction on $\phi$ implies we have  $\sigma > 0$; additionally, since electricity consumption increases utility, we must have $\alpha_t > 0$ for all $t$.
 For simplicity, we also define $\sum_t \alpha_t = 1$, so that a 1\% increase in electricity consumption in all periods increases utility by 1\%; consequently, we then have $\alpha_t \in (0,1)$.
@@
 	\begin{align*}
-	X \equiv \begin{pmatrix}
+	\mathbf{X} \equiv \begin{pmatrix}
 	X_1\\
@@
 	\end{pmatrix} ,\;
-	Z \equiv \begin{pmatrix}
+	\mathbf{Z} \equiv \begin{pmatrix}
 	Z_1\\
@@
 	\end{pmatrix} ,\;
-	p \equiv \begin{pmatrix}
+	\mathbf{p} \equiv \begin{pmatrix}
 	p_1\\
@@
 	\end{pmatrix} ,\;
-	\xi \equiv \begin{pmatrix}
+	\boldsymbol{\xi} \equiv \begin{pmatrix}
 	\xi_{1,1} & \dots & \xi_{1,m}\\
@@
 	\end{align*}
-	where we have $n$ technologies, $m$ periods, and $Z \equiv \xi^T X$.
-A key element of this model is that $X$ does not vary by time.
+	where we have $n$ technologies, $m$ periods, and $\mathbf{Z} \equiv \boldsymbol{\xi}^T \mathbf{X}$.
+A key element of this model is that $\mathbf{X}$ does not vary by time.
 This is important because the time scale of our model must be fairly granular to study the effects of intermittency.
@@
 Additionally, this allows us to assume that producers cannot modify the quantity of the technologies they deploy.
-And, thirdly, for certain technologies, this time frame is short enough to assume that $\xi$ is exogenous; that is, technologies like coal power cannot significantly modify their output within a day, so $\xi$ can be treated as a given set of constants.
-These latter two assumptions, that $X$ cannot change over time and that $\xi$ is exogenous, are important for parsimony, because they prevent more complicated dynamics for entering our model.
+And, thirdly, for certain technologies, this time frame is short enough to assume that $\xi$ is exogenous; that is, technologies like coal power cannot significantly modify their output within a day, so $\boldsymbol{\xi}$ can be treated as a given set of constants.
+These latter two assumptions, that $\mathbf{X}$ cannot change over time and that $\boldsymbol{\xi}$ is exogenous, are important for parsimony, because they prevent more complicated dynamics for entering our model.
 So, by assuming a sufficiently short time frame, we can continue our study of intermittency in a relatively simpler setting.
 
-	Next, our representative firm sets $X$ once to maximize total profit while facing the cost function $C(X_1, \dots, X_n)$.
+	Next, our representative firm sets $\mathbf{X}$ once to maximize total profit; it does so by setting marginal profit equal to marginal cost.
 \citet{HH} note that past literature has argued for concave cost functions in the energy market due to effects such as economies of scale and learning-by-doing; on the other hand, standard cost functions are generally convex.
 So, like Helm and Meir, we take an intermediate approach by using a linear cost function.
-Specifically, we have $C(X) \equiv \sum_i c_i X_i \equiv c^T X$ where $c_i$ is the cost per unit of $X_i$.
+Specifically, the total cost of input $\mathbf{X}$ is given by $\equiv \sum_i c_i X_i \equiv \mathbf{c}^T \mathbf{X}$ where $c_i$ is the cost per unit of $X_i$.
 Total profit is given by
 	\begin{equation}
-	\Pi = p^T Z - c^T X
+	\Pi = \mathbf{p}^T \mathbf{Z} - \mathbf{c}^T \mathbf{X}
 	\end{equation}
@@
 	\begin{equation}
-	\frac{\partial \Pi}{\partial X} = 0 \implies p = \xi^{-1} c
+	\frac{\partial \Pi}{\partial \mathbf{X}} = 0 \implies \mathbf{p} =  \boldsymbol{\xi}^{-1} \mathbf{c}
 	\end{equation}
 	Combining this FOC with the demand equation (\cref{eq:demand}) allows us to find the equilibrium.
-Generally, the equilibrium results for any number of technologies ($n$) are analytic, but they are difficult to interpret due to the number of parameters involved.
+Generally, the equilibrium results for any number of technologies ($n$) are analytic, but they are difficult to interpret algebraically due to the number of parameters involved.
 
@@
 For technology $j$ to be economical, it must meet three conditions with respect to some arbitrary period $s$.
-Firstly, it must be more cost effective than any of the other technologies in period $s$.
+Firstly, it must be more cost efficient than any of the other technologies in period $s$.
 Secondly, it must have  a relative advantage in output efficiency in the same period $s$.
@@
 	\end{proposition}
-	The first condition is on cost efficacy and is fairly intuitive.
-Consider its contrapositive: if a technology does not have an advantage is cost efficiency in any period, it will not be used; this is fairly obvious.
+	The first condition is on cost efficiency and is fairly intuitive.
+Consider its contrapositive: if a technology does not have an advantage in cost efficiency in any period, it will not be used; this is fairly obvious.
 Alternatively, if a technology is the most cost effective in every single period, it will be the only technology used.
-The second condition regarding output efficiency actually stems from the invertibility of $\xi$.
-If we did not have $\xi$ invertible, we either have at least one technology that does not produce in any period or we have at least one technology being a linear combination of the other technologies in terms of output.
+The second condition regarding output efficiency actually stems from the invertibility of $\boldsymbol{\xi}$.
+If we did not have $\boldsymbol{\xi}$ invertible, we either have at least one technology that does not produce in any period or we have at least one technology being a linear combination of the other technologies in terms of output.
 In the latter case, some technologies are not economical because their output can be replicated by the other technologies in a more cost effective way.
-That is, suppose $\xi$ consisted of 3 technologies but was of rank $2$.
+That is, suppose $\boldsymbol{\xi}$ consisted of 3 technologies but was of rank $2$.
 In this case, we may represent any of these technologies as a linear combination of the other two; call this combination the synthetic version of technology $i$.
@@
 In the latter case, we may still eliminate technology $i$ or not use the other two technologies depending on the demand.
-Overall, in any case, $\xi$ not invertible means that at least one technology is not used.
+Overall, in any case, $\boldsymbol{\xi}$ not invertible means that at least one technology is not used.
 Finally, the demand condition is straightforward; even if a technology is optimal in a certain period, if consumers do not sufficiently demand electricity during that period, then there is little reason to use that technology.
@@
 	\begin{proposition}
-		Suppose we are not in an edge case, so that the conditions of Proposition 1 hold for each technology.
+		Suppose that the conditions of Proposition 1 hold for each technology, so we are not in an edge case.
 The equilibrium quantity of a technology is increasing with its output efficiency and decreasing with its cost; at the same time, it is decreasing with the output efficiency of the other technologies and increasing with their cost.
@@
 	\end{proposition}	
-	The comparative statics with respect to $X$ and its output efficiency and cost are not surprising.
-On the other hand, the statics for $Z$ may not be immediately obvious.
-Instead, they follow from the fact that we have $Z \equiv \xi_T X$.
+	The comparative statics with respect to $X_i$ and output efficiency and cost of technology $i$ are not surprising.
+On the other hand, the statics for $Z_t$ may not be immediately obvious.
+Instead, they follow from the fact that we have $\mathbf{Z} \equiv \boldsymbol{\xi}^T \mathbf{X}$.
 That is, suppose we have an arbitrary technology $i$ that is the most cost effective source of electricity in period $t$.
@@
 This intuition just happens to apply even when other technologies are employed and there is demand in multiple periods.
-Similarly, the comparative statics for the share parameters of the utility function, $\alpha$, travel in the opposite direction.
+Similarly, the comparative statics for the share parameters of the utility function, $\boldsymbol{\alpha} \equiv \left( \alpha_t \;\; \alpha_s \right)^T$, travel in the opposite direction.
 A rise in $\alpha_t$ would directly raise the optimal quantity of $Z_t$; hence, whichever technology is most cost effective at producing in period $t$ would be used more.
@@
 
+	Furthermore, these theoretical results have assumed that $\sigma = 1$.
+This simplification was made for analytical tractability; specifically, it implies that the utility function is Cobb-Douglas which then results in the first order condition $Z_t = \alpha_t/p_t$.
+This condition is vital to facilitating the analysis of $\mathbf{X}$, since, by definition, we have $\mathbf{Z} \equiv \boldsymbol{\xi}^T \mathbf{X}$.	However, this simplifying assumption on $\sigma$ may not be realistic.
+Hence, in the following section, we empirically estimate $\sigma$ to parameterize the model.
+Since the empirical estimate is not exactly 1, this complicates the solution for $\mathbf{Z}$; consequently, the solution for $\mathbf{X}$ loses tractability.
+However, we can still study the model in a qualitative sense to see how values of $\sigma$ would affect the equilibrium.
+
+	\begin{proposition}
+		Suppose that we have $\sigma \to \infty$.
+Then, electricity consumption in each period $t$ is a perfect substitute for electricity consumption in period $s$ for all periods $t,s$.
+Secondly, the utility function takes on the linear form $U = \sum_t \alpha_t Z_t$.
+And, thirdly, the set of optimal bundles of inputs $\mathbf{X}$ is given by
+		$$
+		W =
+		\{ \mathbf{X} \, : \, \mathbf{c}^T \mathbf{X} = I \;,\;  \mathbf{X} \geq 0 \;,\; \text{and} \;\;  (x_i > 0 \implies i \in S) \;\; \forall i \}
+		$$
+		$$\text{where} \quad S = \argmax_i \, \sum_t \alpha_t \xi_{i,t}/c_i$$
+		where $S$ represents the set of indices for technologies that have maximimal cost-adjusted marginal utility.
+In other words, any vector of inputs $\mathbf{X}$ consisting of a combination of technologies in $S$ represent a valid equilibrium solution.
+Furthermore, the set $Y = \{ \mathbf{Z} \,: \, \mathbf{Z} = \boldsymbol{\xi}^T \mathbf{X}  \; \, \forall \, \mathbf{X} \in W \}$ contains all possible equilibrium values of electricity output.
+	\end{proposition}
+
+	If we have $\sigma \to \infty$, then electricity in each period becomes a perfect substitute for electricity in other periods.
+This then leads to multiple possible solutions.
+The mathematical reason is that , since the utility function becomes linear, the marginal utility of each input becomes $\sum_t \alpha_t \xi_{i,t}$; then, using only whatever input offers the highest cost-adjusted marginal utility $(1/c_i) \sum_t \alpha_t \xi_{i,t}$ will maximize utility.
+If there are multiple technologies that have the same cost-adjusted marginal utility, we may get multiple solutions.
+The intuition here is that the perfect substitutability of $Z_t$ implies that consumers do not care about smoothing their electricity consumption over time.
+But, they still value consumption in particular periods more than others through the $\boldsymbol{\alpha}$ parameter.
+Consequently, they simply use whatever technology gives them the most total electricity (weighted by $\boldsymbol{\alpha}$).
+Intermittency of output simply does not matter in this case.
+This is what we should expect given that $\sigma \to \infty$ implies perfect substitutability.
+A detailed proof is given in \hyperref[sec:cobbdoug]{Appendix A.A}.
+
+	On the other hand, suppose that $\sigma \to 0$.
+This is the standard case of perfect complements in which we would get $U = \min_t \, Z_t/\alpha_t$.
+Unlike the perfect substitute case, any analytic results would not be as clear.
+However, some of the intuition from before carries through.
+That is, when electricity consumption in each period is perfectly complementary with that in other periods, consumers care strongly about smoothing their consumption.
+For instance, consider again a two period, two technology case with solar (intermittent) and coal (constant-output); furthermore, suppose that $\alpha_t$ is constant.
+The utility function here implies that consumers only care about periods when they are getting the least electricity.
+Since solar performs worse during the off-peak, the implicit demand for each technology would solely be based on their off-peak performance.
+Interestingly, no matter how high solar's output efficiency is during peak hours, as measured by its output per unit, consumer's decisions would be unaffected.
+In other words, intermittency plays a much larger role in this case, since \textit{when} a technology produces
+
+	To summarize, the channel by which $\sigma$ affects the inputs $\mathbf{X}$ is through the demand for electricity.
+Specifically, $\sigma$ is inversely related to how much consumers value smoother electricity consumption $\mathbf{Z}$.
+When $\sigma$ is low, consumers care more about consumption smoothing.
+They are willing to reduce their total consumption of electricity if it means having more consistent electricity over time.
+In this case, intermittent energy technologies are less appealing because, by definition, they do not generate a consistent electricity output over time.
+On the other hand, suppose $\sigma$ is high.
+Then, consumers care less about consumption smoothing and are focused more on total consumption; in the extreme case above, when $\sigma \to \infty$, they only care about total consumption and not about when they get their electricity.
+In this case, the intermittency is relatively less of a concern; consequently, other factors like cost efficiency and output efficiency play a larger role.
+In short,  $\sigma$ is inversely related to how much the intermittency of an input matters.
+
 	\section{Empirical Methodology}
@@
 	In order to better understand the practical implications of our model, we empirically estimate its parameters and study its implications numerically.
-We are particularly interested in estimating $\sigma$, the intertemporal elasticity of substitution for electricity consumption.
-In our  \hyperref[sec:Discussion]{discussion}, we explain in detail why $\sigma$ is of interest; to summarize, $\sigma$ implicitly determines how well renewables can substitute for fossil energy.
-Specifically, if $\sigma > 1$, then electricity consumption in different periods are substitutes; consequently, fossil energy and renewable energy are highly substitutable.
-On the other hand, if $\sigma< 1$, electricity consumption in different periods are complements; so, fossil and renewable energy are far less substitutable due to the effects of intermittency.
-The other parameters in our model, $c$,  $\xi$, and $\alpha$, are of secondary interest, since they are easier to obtain directly.
-
-	Now, recall the demand equation from earlier
+We are particularly interested in estimating $\sigma$, since it determines the importance of intermittency.
+As shown earlier, when $\sigma$ is large, consumers care less about when they get their electricity and are thus more likely to adopt intermittent technologies.
+On the other hand, when $\sigma$ is small, consumers prefer to smooth their electricity consumption and therefore prefer less intermittent sources.
+Hence, ensuring that we have accurate estimates of $\sigma$ is important for understanding how consumers decide between fossil and renewable energy.
+The other parameters in our model, $c$,  $\xi$, and $\boldsymbol{\alpha}$, are of secondary interest, since they are easier to obtain directly.
+
+	Recall the demand equation from earlier
 	$$Z_t = \left(\frac{\alpha_t}{p_t} \right)^\sigma \frac{I}{P}$$
@@
 Retail customers pay fixed rates each month for electricity, hence $p_t$ is constant within each month; and, we expect that income $I$ does not vary significantly on a daily basis.
-Consequently, all variation in intramonthly demand is due to the share parameter $\alpha$ and the elasticity $\sigma$.
+Consequently, all variation in intramonthly demand is due to the share parameter $\boldsymbol{\alpha}$ and the elasticity $\sigma$.
 But, this creates a problem; since retail consumers do not face prices that vary each hour, we cannot estimate  $\sigma$ on an hourly basis.
@@
 	Overall, the past literature has estimated $\sigma$ by running regressions on the CES demand equation, however we are concerned that this approach suffers from endogeneity.
-That is, producers may intertemporally substitute electricity generation which essentially means that there is a supply equation affecting prices.
+That is, producers may intertemporally substitute electricity output which essentially means that there is a supply equation affecting prices.
 For instance, during the oil crisis of 1973, refineries increased gasoline stocks expecting future prices to be higher \citep{genie}.
@@
 	In order to estimate this $\sigma$, we further modify this equation. 
-	Firstly, note that we cannot observe the demand shifter $\alpha_{t,i}$ directly, so we must replace the $\alpha$ terms with a set of controls that may be responsible for shifts in demand.
+	Firstly, note that we cannot observe the demand shifter $\alpha_{t,i}$ directly, so we must replace the $\boldsymbol{\alpha}$ terms with a set of controls that may be responsible for shifts in demand.
 So, still in general terms, our regression equation is now
@@
 In other words, our controls and instrument likely have non-linear effects on price and quantity which cannot be captured by linear models.
-Alternatively, this difference may also be because the true error term is not Gaussian.
-In any case, we  believe that our third semiparametric fit, $\hat{\sigma} = 0.8847$, is the most robust estimate of $\sigma$.
+Specifically, we are likely to see nonlinear effects from to temperature which is proxied by CDDs and HDDs in our model.
+The intuition here is that the amount of electricity needed to maintain room temperature varies nonlinearly with the outside temperature, so the linear structure of our OLS regression would likely be invalid.
+Alternatively, there is also no reason to believe that logged electricity prices would vary linearly with logged coal prices.
+Either way, there would be a functional form problem with the standard linear regressions.
+So, we believe that our third semiparametric fit, $\hat{\sigma} = 0.8847$, is the most robust estimate of $\sigma$.
 
@@
 
-	To start, we consider how $\sigma$ affects the substitutability of fossil and renewable energy.
+	So far, we have primarily focused on the (demand-side) intertemporal elasticity of substitution for electricity consumption $\sigma$.
+In this subsection, we discuss what implications $\sigma$ has for the (supply-side) elasticity of substitution between energy inputs;\footnote{
+	For two commodities $\{W_i, W_j\}$ and their prices $\{p_i, p_j\}$, the elasticity of substitution between the two is given by $\partial \log (W_i/ W_j) / \partial \log (p_j/p_i)$. 
+	}  from here on, we will refer to this latter elasticity as $e$.
+This elasticity is important, because sufficient substitutability between these energy inputs  is required to transition into greener economy in the future.
+For instance, \citet{Ace2012} provide a model where they argue that, ``When the two	sectors [clean and dirty energy] are substitutable but not sufficiently so, preventing an environmental disaster requires a permanent policy intervention.
+Finally, when the two sectors are complementary, the only way to stave off a disaster is to stop long-run growth."
+
+	Now, to clarify our discussion, we first look at a general model of energy production common in the literature. Specifically, we have
+	\begin{equation}
+	\tilde{Z} = \left( \sum_i \beta_i \tilde{X}_i^\omega \right)^{1/\omega}
+	\end{equation} 
+	where   $\tilde{Z}$ is the electricity produced, $\tilde{X}_i$ is the quantity of electricity-producing input, $\beta_i$ is a share parameter, and $(\omega-1)^{-1} $ is the elasticity of substitution between the inputs.
+In other words, the literature often represents electricity production using a CES function and treats electricity as a single, homogeneous good.
+Furthermore, such models would generally have firms maximizing profit against a  demand function based on some utility-maximizing agent.
+Although this approach is not realistic in its assumptions, it captures the imperfect substitution between energy inputs in a tractable way.
+However, any results based on this model would be based on the assumption that the  elasticity of substitution between energy inputs, $e$, is constant.
+
+	On the other hand, our model is based on relatively more realistic assumptions but it implies that $e$ is non-constant.
+We arrive at this conclusion through the numerical results which will follow, although we can also see that $e$ is non-constant in a simpler setting.
+Specifically, when $\sigma = 1$ and we have two periods and two technologies, the elasticity of substitution is given by\footnote{The full derivation is given in  \hyperref[sec:EOS_derivation]{Appendix A.A}.}
+	\begin{equation}\label{eq:eosmath}
+	e = 
+	\frac{-\alpha _{s}\,\alpha _{t}\,c_{1}\,c_{2}\,{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2 \left(\alpha _{s}\,c_{1}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{1t}}+\alpha _{t}\,c_{1}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{1t}}\right)^{-1}}{
+		\,\left(\alpha _{s}\,c_{1}\,\xi _{\mathrm{2s}}\,\xi _{\mathrm{2t}}-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}+\alpha _{t}\,c_{1}\,\xi _{\mathrm{2s}}\,\xi _{\mathrm{2t}}-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)
+	}
+	\end{equation}
+	It is clear from the above equation that $e$ depends on $\mathbf{c}$.
+However, what is not clear is the extent to which $e$ varies with $\mathbf{c}$ whether it varies enough to make a CES production assumption problematic.
+Furthermore, the above mathematical expression is only valid for $\sigma = 1$ which is close to but not exactly our estimates for $\hat{\sigma}$.
+Whether or not $e$ becomes constant under different values of $\sigma$ is another question.
+Because $e$ does not have a tractable solution when $\sigma \neq 1$, we parameterize and implement our model numerically in order to better study this elasticity.
+
+%	%% OLD
+%	To start, we consider how $\sigma$ affects the substitutability of fossil and renewable energy.
 This is important, because sufficient substitutability between these two technologies is required to transition into greener economy in the future.
@@
 
-	Firstly, let technology 1 be coal power and technology 2 be solar power.
+	To start, let technology 1 be coal power and technology 2 be solar power.
 These two technologies exemplify consistent fossil energy and intermittent renewable energy.
@@
 Since the union of both periods makes up only a single day, our model's assumption of an exogenous and constant $\xi$ is fairly reasonable in this context.
-Next, we normalize all quantity units to a MWh basis.
-Hence, we let $\xi$ represent the percent of capacity utilized in each period; we assume coal uses 100\% of its capacity in both periods, while solar can access 100\% during peak hours and only 10\% during the off-peak.
-Finally, we set the cost parameters, given in  \$ per MWh, equal to LCOE\footnote{ The LCOE for a generation technology is equal to the sum of its lifetime costs divided by its lifetime energy output.
+
+	Next, we normalize the remaining parameters in our model to a MWh basis rather than a per unit basis.
+This is has no effect on the model on a theoretical level but makes it easier to empirically parametrize the cost of electricity production $\mathbf{c}$.
+This is because the cost of electricity generation is generally reported in terms of \$ per unit of electricity, while we originally set $\mathbf{c}$ to represent cost per unit of input.
+Here, we set the cost parameters for each input equal to their LCOE (\$/MWh).\footnote{ The LCOE for a generation technology is equal to the sum of its lifetime costs divided by its lifetime energy output.
 \citet{Joskow2011} explains the flaws of comparing generation technologies solely on the basis of LCOE; but,  our use of this measure is unrelated to his critique.
-That is, he argues that the economic value an intermittent technology should also account for when it produces electricity and the prices of electricity in those periods (see Table 2 of his paper).
+That is, he argues that the economic value of an intermittent technology should also account for when it produces electricity and the prices of electricity in those periods (see Table 2 of his paper).
 Our model does exactly this; but, we still need to  use LCOE to parametrize the cost of developing capacity.
-} estimates for 2023 from the \citet{EIALCOE}; specifically, we use estimates for "Solar PV" and "Coal with 30\% CCS" from Table 1b.
+	} In particular, we use estimates for 2023 for "Solar PV" and "Coal with 30\% CCS" from Table 1b in  \citet{EIALCOE}.
+Additionally, normalizing cost parameter requires us to normalize $\boldsymbol{\xi}$ as well; this ensures the rest of the model is unaffected.
+Consequently, $\boldsymbol{\xi}$  represents the percent of total capacity utilized in each period; we assume coal uses 100\% of its capacity in both periods, while solar can access 100\% during peak hours and only 10\% during the off-peak.
 In total, we have the following parameters.
@@
 	$$e_{i,j} = \frac{\partial \log (X_i/ X_j)}{\partial \log (c_j/c_i)}$$
-	where $c$ is their prices.
+	where the vector $\mathbf{c}$ captures the cost of electricity production for each technology.
 This relationship is of particular interest, because many applied and theoretical models studying renewable and fossil energy impose a CES production structure between the two (see \citet{Pap}).
@@
 We generated these results by computing the optimal quantities of each technology given a range of relative prices $c_2/c_1$.
-Then, we numerically differentiated $\log(X_1/X_2)$ with respect to $\log(c_2/c_1)$ to estimate the elasticity of substitution between solar and coal.
-This numerically computed elasticity of substitution between solar and coal power, $e_{solar,coal}$, is shown in the lower subplot.
-We repeat this process with different values of $\sigma$, the elasticity of substitution in the consumer's utility function.
+Then, we numerically differentiated $\log(X_1/X_2)$ with respect to $\log(c_2/c_1)$ to estimate the elasticity of substitution between solar and coal  $e$.
+This is done by computing the slope of the first subplot in \autoref{fig:eosnum} at each value for $\log(c_2/c_1)$.
+Since $\log(X_1/X_2)$ is rising at an increasing rate with respect to $\log(c_2/c_1)$, we see that $e$ is positive and increasing in the lower subplot.
+We repeat this process with different values of $\sigma$, the IES in the consumer's utility function.
 Specifically, we use our estimate of $\hat{\sigma} = 0.8847\, (0.044)$ and its 95\%  confidence interval $(0.7985, 0.9709)$.
-Finally, after finding the optimal values of our quantities $X$, we filter all observations of our numerical simulation that correspond to edge cases -- solutions where $X, Z \leq  0$.
+Finally, after finding the optimal values of our quantities $\mathbf{X}$, we only keep results in our numerical simulation that correspond to interior solutions; that is, we drop edge cases where optimal output or technology  is non-positive.
 
 	The first relationship we see in \autoref{fig:eosnum} is that $e_{1,2}$ varies non-linearly with the relative costs of each technology; in particular, it appears to take on a hockey stick shape.
-This shape is a result of both intermittency and costs.
-Intermittency reduces substitutability as overall energy generation becomes more intermittent.
-In other words, intermittency is a bigger issue for consumers when their energy supply is not consistent.
-This causes $e_{1,2}$ to fall when the majority of energy generated comes from solar; naturally, the latter occurs when $\log(c_2/c_1)$ is small (solar is relatively cheap).
-At the same time, quantities become more sensitive to costs when costs greatly differ.\footnote{We explore this point further in Appendix B in which we consider a numerical example where technologies are minimally intermittent.
+It is quite similar to the mathematical expression for $e$ when $\sigma = 1$ given in the earlier (\cref{eq:eosmath}).
+However, it is more easily understood intuitively.
+Specifically, this shape can be understood as the interaction of two effects: intermittency and costs.
+The \textit{intermittency effect} is that $e$ falls when our electricity output is highly intermittent.
+The \textit{cost effect} is that $e$ is high costs $(c_1, c_2)$ differ significantly while $e$ is low  when costs are closer together.
+
+	First, we qualify the intermittency effect.
+Suppose that a majority of our energy came from solar; this corresponds to the left side of the graph where $\log(c_2/c_1)$ is lower and, as shown in the  first subplot, $\log(X_1/X_2)$ is higher.
+In this case, the overall output of electricity is intermittent.
+Since most of the supply comes from solar, we have a majority of electricity arriving during peak hours and much less during the off-peak.
+The intermittency of the overall supply is high here, since consumers are being starved of electricity during the off-peak.
+So, it is difficult to replace even more of the coal input with solar.
+Therefore, $e$ is relatively low.
+On the other hand, suppose that a majority of our electricity supply comes from coal; this corresponds to the right side of \autoref{fig:eosnum}.
+In this case, the electricity output is quite consistent over time.
+Consequently, replacing a marginal amount of coal input with solar input is not an issue.
+That is, making the overall energy output slightly more intermittent when it is already stable does not create as much disutility.
+Hence, the elasticity $e$ is high, since it is easy to substitute between the energy inputs.
+In short, as the electricity output becomes less intermittent, $e$ should rise.
+
+	Next, we study the effects of costs on $e$.
+We see quantities become more sensitive to costs when costs greatly differ.\footnote{We explore this point further in Appendix B in which we consider a numerical example where technologies are minimally intermittent.
 That is, we again consider a two-period, two-technology example, but assume that $\xi_1$ and $\xi_2$ are nearly constant over time.
 We plot our results in \autoref{fig:eosrange} and find that the elasticity of substitution takes on a u-shape.
-} That is, $e_{1,2}$ rises when the relative prices of solar and coal are very different.
-When these two effects interact, we see the elasticity of substitution between solar and coal takes on a hockey stick shape.
-
-	Additionally, note that the elasticity of substitution $e_{1,2}$ between solar and coal becomes larger and more non-linear as $\sigma$ rises.
+In other words, when intermittency is not a concern as a result of the output parameters $\boldsymbol{\xi}$, we see the cost effect take over.
+	} To understand why, suppose that cost efficiencies of two inputs are drastically different.
+Then, independent their intermittency, it is likely that the equilibrium quantities of the inputs are primarily being driven by costs.
+For example, note that consumers want more electricity during peak hours compared to the off-peak.
+They can only achieve this by combining solar and coal, since the electricity output of coal is constant while solar can produce more during peak hours.
+Then, if solar is extremely expensive, this makes it expensive to get relatively more electricity during peak hours than off-peak hours.
+Consequently, it may actually be more economical for consumers rely primarily on coal.
+In other words, they would have to give up too much of their income to get more power during peak-hours than off-peak hours.
+Now, note that the elasticity $e$ refers to how log inputs change with respect to their costs.
+Consequently, when costs are very different, we would expect that small changes in costs would do much to change quantities, since costs (as opposed to other factors like intermittency) are primarily driving the market equilibrium.
+So, $e$ would be high when $\log(c_2/c_1)$ takes extreme values.
+On the other hand, when costs are similar, the cost of generation does not matter for consumers as much as intermittency and other effects; so, we would expect $e$ to be low when $\log(c_2/c_1)$ takes more intermediate values.
+
+	We can add up the intermittency and cost effects to understand the shape of $e$.
+This means looking at three cases.
+The first case is the left-hand side of the second subplot of \autoref{fig:eosnum} where solar is much cheaper.
+Here, the overall energy supply is highly intermittent so $e$ gets strongly pushed downwards; at the same time the cost effect pushes $e$ upwards.
+These two effects cancel out and we see $e$ take an intermediate value.
+The second case is near the middle of the subplot where we have more intermediate costs.
+Here, the intermittency effect moderately increases $e$ while the cost effect moderately decreases $e$.
+So, again, $e$ takes an intermediate value.
+Finally, the third case is the right-hand side of the subplot where the majority of the electricity comes from coal.
+The intermittency effect here pushes $e$ upwards, and, similarly, the cost effect raises $e$.
+So, in this case, we see $e$ being relatively high.
+
+	%% OLD
+	%Additionally, note that the elasticity of substitution $e_{1,2}$ between solar and coal becomes larger and more non-linear as $\sigma$ rises.
 Firstly, the reason why  it becomes larger is fairly intuitive.
@@
 
+	Additionally, note that the elasticity of substitution $e_{1,2}$ between solar and coal becomes larger and more non-linear as $\sigma$ rises.
+Firstly, the reason why  it becomes larger at all points is fairly intuitive.
+As discussed earlier, when $\sigma$ is higher, consumers care less about smoother consumption and intermittency is less of an issue.
+Consequently, consumers are more willing to accept intermittency in the electricity supply and thus the elasticity $e$ rises.
+Next, to understand the non-linear effect and change in shape, we can appeal to the intermittency effect and the cost effect.
+Note that $\sigma$ rising makes intermittency matter less; this diminishes the intermittency effect.
+As a result, we see the cost effect dominate.
+Recall that the cost effect creates a u-shape while the intermittency effect is what causes $e$ to fall when we rely heavily on solar.
+Now, note how when $\sigma$ rises, the shape of $e$ becomes more u-shaped.
+This is because the intermittency effect becomes more diminished and the cost effect takes over.
+By this logic, if we keep raising $\sigma$, the level of $e$ becomes increasingly larger; at the same time, we would also see it become more u-shaped as the cost effect takes over.
+
+	We can tie these results in with the more mathematical discussion of the model's equilibrium from earlier.
+Specifically, recall that when $\sigma \to \infty$, utility becomes linear and the equilibrium tends towards whatever inputs maximize total electricity output.
+On the other hand, when $\sigma \to 0$, utility becomes Leontiff and consumers want to completely smooth their electricity consumption.
+These two extreme cases can help us understand how $e$ changes with $\sigma$.
+
+	In the first case, when $\sigma \to \infty$, recall that the optimal solution was to only use whatever input had the highest cost-adjusted marginal utility $\sum_t \alpha_t \xi_{i,t} /c_i$.
+The intuition here is that a very high $\sigma$ causes electricity in each period to become a perfect substitute for electricity in other periods; this can be seen by the fact that utility becomes a linear function of electricity output $\mathbf{Z}$ in each period.
+So, consumers only care about their total electricity consumption rather than when they get their electricity.
+As a result, all solutions turn into edge cases.
+Consequently, small changes in the cost of input $i$ can cause its equilibrium value to go from its maximum level to zero.
+Since $e_{12} = \partial \log(X_1/X_2) / \partial \log(c_2/c_1)$, we expect $e$ to be extremely large in this case since quantities are very sensitive to prices.
+
+	In the second case, when $\sigma \to 0$, the optimal solution was to figure out some combination of resources that make consumption as smooth as possible.
+Specifically, the utility was given by $\min_t \, Z_t/\alpha_t$.
+Therefore, consumers want a relatively fixed ratio of peak and off-peak consumption.
+Here, we know that coal offers a strictly smooth output while solar offers more during peak hours.
+Hence, the equilibrium would be one which primarily uses coal and then a small amount of solar to account for the fact that consumers demand slightly more electricity during peak hours.
+Furthermore, even if costs change, the optimal solution would still require the consumer to maintain a relatively fixed ratio of peak and off-peak electricity cosnumption to maximize utility; this then requires maintaining a fixed ratio of solar and coal.
+Consequently, changes in the cost of solar and coal would do little to affect the equilibrium ratio of inputs.
+Thus, since $e$ measures how sensitive the two inputs are with respect to their costs, it would be extremely small in this case.
+
+	To summarize, $e$ depends on two factors, cost and intermittency, while $\sigma$ affects the importance of intermittency.
+When costs are highly different, $e$ rises -- this is the cost effect.
+When the output of electricity is highly intermittent, $e$ falls -- this is the intermittency effect.
+These two effects combine to give $e$ the shape we see in \autoref{fig:eosnum}.
+Furthermore, at lower levels of $\sigma$, consumers case more about smoother electricity consumption and thus intermittency matters more.
+So, lower $\sigma$ means the intermittency effect is larger and $e$ is smaller overall.
+Additionally, when the intermittency effect is large, we see $e$ become more linear, while, when the intermittency effect is small, $e$ becomes more u-shaped as the cost effect dominates.
+Overall, these numerical results for $e$ are consistent with the analytic results and intuition discussed earlier.
+
 	\subsection{Implications for Environmental Policy}
 
-	Overall, our results suggest that the elasticity of substitution between  renewable and fossil energy is not constant.
+	A simple but important finding here is that $e$, the elasticity of substitution between  renewable and fossil energy, is not constant.
 Furthermore, it appears to fall with the level of intermittency.
@@
 The first approach is to directly integrate our model within a given framework.
-The second approach is to assume a variable elasticity of substitution (VES) structure\footnote{ The VES function was originally introduced by \citet{VES}.} between clean and dirty energy.
+The second approach is to assume a variable elasticity of substitution (VES) structure\footnote{ The VES function was originally introduced by \citet{VES}; we detail its structure in  } between clean and dirty energy.
 These two approaches have their own advantages/disadvantages and serve different purposes.
@@
 	\subsubsection{VES Approximation}
+	\label{sec:VES}
 
@@
 	where $\omega, \delta, \rho$, and $\gamma$ are parameters.
-Additionally, $Z$ is the output, $X_1$ and $X_2$ are the inputs, and $e$ is the elasticity of substitution between $X_1$ and $X_2$.
-In our case, we can think of $Z$ as electricity output while $X_1$ and $X_2$ represent dirty and clean technology.
+Additionally, $\mathbf{Z}$ is the output, $X_1$ and $X_2$ are the inputs, and $e$ is the elasticity of substitution between $X_1$ and $X_2$.
+In our case, we can think of $\mathbf{Z}$ as electricity output while $X_1$ and $X_2$ represent dirty and clean technology.
 Note that $e$ is a linear function of $X_1/X_2$; this relationship allows a VES function to approximate the effects of intermittency.
@@
 
-	One potential objection to using the VES function is that it assumes the elasticity of substitution $e$ approaches 1 when the majority of generation comes from renewables ($X_1/X_2 \to 0$).
+	One potential objection to using the VES function is that it assumes the elasticity of substitution $e$ approaches 1 when the majority of electricity output comes from renewables ($X_1/X_2 \to 0$).
 And, a VES structure assumes linear $e$ which does not seem to be the case in \autoref{fig:ves}.
@@
 	where $t$ and $s$ are our two periods. Next, solving for the FOC condition for profit maximization, we have:
-	\begin{align*}
-	p &=  \xi^{-1} c \\
-	p &= \begin{pmatrix}
+	\begin{align}
+	\mathbf{p} &=  \boldsymbol{\xi}^{-1} \mathbf{c} = \begin{pmatrix}
 	-\dfrac{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}{\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}  \\[2ex]
@@
 	\end{pmatrix} 
-	\end{align*}
-	And, substituting back into our demand equations, we find the equilibrium quantities for $Z$ and $X$. 
-	$$
-	Z = \begin{pmatrix}
+	\end{align}
+	And, substituting back into our demand equations, we find the equilibrium quantities for $\mathbf{Z}$ and $\mathbf{X}$. 
+	\begin{align}
+	\mathbf{Z} &= \begin{pmatrix}
 	\dfrac{\alpha _{t}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{c_{2}\,\xi _{\mathrm{1s}} - c_{1}\,\xi _{\mathrm{2s}}} \\[2ex]
 	\dfrac{\alpha _{s}\,\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} 
-	\end{pmatrix}
+	\end{pmatrix}\\
 	\implies 
-	X = \begin{pmatrix}
+	\mathbf{X} &= \begin{pmatrix}
 	\dfrac{\alpha _{t}\,\xi _{\mathrm{2s}}}{c_{1}\,\xi _{\mathrm{2s}}-c_{2}\,\xi _{\mathrm{1s}}}+\dfrac{\alpha _{s}\,\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1t}}} \\[2ex] 
@@
 	\end{pmatrix}
-	$$
-
+	\end{align}
 	Furthermore, we derive restrictions on the parameters $\xi$ and $c$ by assuming $Z, X > 0$.
@@
 	\begin{center}
-		[INSERT Table 7: Parameter Restrictions for $Z, X > 0$]
+		[INSERT Table 6: Parameter Restrictions for $\mathbf{Z}, \mathbf{X} > 0$]
 	\end{center}
@@
 	\begin{proof}
-		We aim to derive conditions on $\xi$ and $c$ required to have positive $Z$ and $X$, so we begin by assuming $X, Z  > 0$.
+		We aim to derive conditions on $\xi$ and $c$ required to have positive $\mathbf{Z}$ and $\mathbf{X}$, so we begin by assuming $\mathbf{Z}, \mathbf{X} > 0$.
 Second, since the equations so far are symmetrical, note that there be two symmetrical sets of potential restrictions we must impose on the parameters.
@@
 And, the fourth condition makes a symmetrical claim but for the technology 1 and period $s$.
-These latter two restrictions regarding output efficiency enter $Z$ and $X$ through $p$; they're simply a restatement of the invertibility of $\xi$ and can also be derived through the cost efficiency restrictions.
+These latter two restrictions regarding output efficiency enter $\mathbf{Z}$ and $\mathbf{X}$ through $\mathbf{p}$; they're simply a restatement of the invertibility of $\xi$ and can also be derived through the cost efficiency restrictions.
 
@@
 Likewise, as coal power's efficiency improves, it's adoption rises.
-To find the effects of $\alpha$ on $X$, we must assume one of the cases of restrictions shown in  \autoref{tab:paramrest}.
+To find the effects of $\boldsymbol{\alpha}$ on $\mathbf{X}$, we must assume one of the cases of restrictions shown in  \autoref{tab:paramrest}.
 So, again, let us assume Case 1 is true; this implies that $X_2$ is the most cost effective technology in period $t$ and likewise for $X_1$ in period $s$.
-Firstly, note that $\alpha$ determines the demand for electricity in a period.
+Firstly, note that $\boldsymbol{\alpha}$ determines the demand for electricity in a period.
 Hence, when $\alpha_t$ rises, we see the optimal level of $X_2$ rise as well; likewise, $X_1$ rises with $\alpha_s$.
@@
 On the other hand, use coal power would rise with off-peak demand and fall with peak demand.
-This concept carries through for the comparative statics of $Z$.
+This concept carries through for the comparative statics of $\mathbf{Z}$.
 When the output efficiency of technology 1 rises or its cost falls, we see output $Z_s$ rise and output $Z_t$ fall.
@@
 	\begin{proof}
-		We begin by deriving the comparative statics of the cost and efficiency parameters with respect to $X$.   Firstly, we take derivatives with respect to the cost vectors:
-		\begin{align*}
-		\frac{\partial X_1}{\partial c} &= 
+		We begin by deriving the comparative statics of the cost and efficiency parameters with respect to $\mathbf{X}$.   Firstly, we take derivatives with respect to the cost vectors:
+		\begin{align*}
+		\frac{\partial X_1}{\partial \mathbf{c}} &= 
 		\begin{pmatrix}
@@
 		\end{pmatrix}\\
-		\frac{\partial X_2}{\partial c} &= 
+		\frac{\partial X_2}{\partial \mathbf{c}} &= 
 		\begin{pmatrix}
@@
 		\begin{alignat*}{1}
-		\frac{\partial X_1}{\partial \xi} &= 
+		\frac{\partial X_1}{\partial \boldsymbol{\xi}} &= 
 		\begin{pmatrix}
@@
 		\end{pmatrix}\\
-		\frac{\partial X_2}{\partial \xi} &= 
+		\frac{\partial X_2}{\partial \boldsymbol{\xi}} &= 
 		\begin{pmatrix}
@@
 Similarly, symmetrical results are shown for $X_2$.
-Next, we study the effects of $\alpha$ on $X$; this requires us to place some restrictions on the parameters, so we use those belonging to Case 1 in \autoref{tab:paramrest}.
-With $\alpha \equiv \left( \alpha_t \;\; \alpha_s \right)^T$,
-		\begin{align*}
-		\frac{\partial X_1}{\partial \alpha} &= 
+Next, we study the effects of $\boldsymbol{\alpha}$ on $\mathbf{X}$; this requires us to place some restrictions on the parameters, so we use those belonging to Case 1 in \autoref{tab:paramrest}.
+Then, we have
+		\begin{align*}
+		\frac{\partial X_1}{\partial \boldsymbol{\alpha}} &= 
 		\begin{pmatrix}
@@
 		\end{pmatrix}\\
-		\frac{\partial X_2}{\partial \alpha} &= 
+		\frac{\partial X_2}{\partial \boldsymbol{\alpha}} &= 
 		\begin{pmatrix}
@@
 
-		Next, we derive the comparative statics for $Z$.
+		Next, we derive the comparative statics for $\mathbf{Z}$.
 From our restrictions, we have $\xi_{1s}\xi_{2t} > \xi_{2s}\xi_{1t}$.
@@
 		\begin{align*}
-		\frac{\partial Z_t}{\partial c} &= 
+		\frac{\partial Z_t}{\partial \mathbf{c}} &= 
 		\begin{pmatrix}
@@
 		\end{pmatrix}\\
-		\frac{\partial Z_s}{\partial c} &= 
+		\frac{\partial Z_s}{\partial \mathbf{c}} &= 
 		\begin{pmatrix}
@@
 		\end{pmatrix}\\
-		\frac{\partial Z_t}{\partial \xi} &= 
+		\frac{\partial Z_t}{\partial \boldsymbol{\xi}} &= 
 		\begin{pmatrix}
@@
 		\end{pmatrix}\\
-		\frac{\partial Z_s}{\partial \xi} &= 
+		\frac{\partial Z_s}{\partial \boldsymbol{\xi}} &= 
 		\begin{pmatrix}
@@
 		\begin{align*}
-		\frac{\partial Z_t}{\partial \alpha} &= 
+		\frac{\partial Z_t}{\partial \boldsymbol{\alpha}} &= 
 		\begin{pmatrix}
@@
 		\end{pmatrix} \\
-		\frac{\partial Z_s}{\partial \alpha} &= 
+		\frac{\partial Z_s}{\partial \boldsymbol{\alpha}} &= 
 		\begin{pmatrix}
@@
 
-	%\subsection{Optimal Taxation}
-	%
-	%The following proof is a derivation of the optimal tax $\tau$ on $X_1$ in the case where it produces externalities. The marginal cost of pollution is given by $\gamma$. 
-	%\hfill \\
-	%\begin{proof} We aim to maximize welfare with respect to the tax $\tau$, hence our first order condition is:
-	%	\begin{align*}
-	%	0 &= \frac{\partial CS}{\partial \tau} + \frac{\partial PS}{\partial \tau} - \frac{\partial \gamma X_1}{\partial \tau} + \frac{\partial \tau X_1}{\partial \tau} \\
-	%	&=  \left( \underbrace{\frac{\partial CS}{\partial p}  + \frac{\partial PS}{\partial p}}_{= 0} - \frac{ \partial  \gamma X_1}{\partial p} + \frac{\partial \tau X_1}{\partial p} \right) \frac{\partial p}{\partial \tau} \\
-	%	&=  \left( 0 - \frac{ \partial  \gamma X_1}{\partial p} + \frac{\partial \tau X_1}{\partial p} \right) \frac{\partial p}{\partial \tau} \\
-	%	&=  - \gamma \frac{\partial  X_1}{\partial \tau} + \tau \frac{\partial  X_1}{\partial \tau}
-	%	\end{align*}
-	%	where the derivatives of producer and consumer surplus are eliminated by the envelope theorem. Therefore, we must have $\tau = \gamma$. \\
-	%	\hfill
-	%\end{proof}
+	\subsubsection{Elasticity of Substitution}
+	\label{sec:EOS_derivation}
+
+	We derive the elasticity of substitution in this two-period, two-technology setting. By definition, the elasticity of substitution is 
+	$$e_{12} \equiv \frac{\partial \log(X_1/X_2)}{\partial \log(c_2/c_1)} = \frac{\partial X_1/X_2 }{ \partial (c_2/c_1)} \cdot \frac{c_2/c_1}{X_1/X_2} = \frac{\partial X_1/X_2}{ \partial  c_2}  \cdot \frac{\partial c_2}{\partial (c_2/c_1)} \cdot \frac{c_2/c_1}{X_1/X_2} $$
+	Note that
+	\begin{align*}
+		X_1/X_2 &= -\frac{\alpha _{s}\,c_{1}\,\xi _{\mathrm{2s}}\,\xi _{\mathrm{2t}}-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}+\alpha _{t}\,c_{1}\,\xi _{\mathrm{2s}}\,\xi _{\mathrm{2t}}-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}{\alpha _{s}\,c_{1}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{1t}}+\alpha _{t}\,c_{1}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{1t}}} \\
+		\frac{\partial X_1/X_2}{\partial c_2} &= \frac{\alpha _{s}\,\alpha _{t}\,c_{1}\,{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2}{{\left(\alpha _{s}\,c_{1}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{1t}}+\alpha _{t}\,c_{1}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{1t}}\right)}^2}	 \\
+		\frac{\partial c_2}{\partial (c_2/c_1)} &= \left( \frac{\partial (c_2/c_1)}{\partial c_2} \right)^{-1} = c_1
+	\end{align*}
+	Thus, the elasticity of substitution is
+	$$
+	e_{12} = 
+	\frac{-\alpha _{s}\,\alpha _{t}\,c_{1}\,c_{2}\,{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2 \left(\alpha _{s}\,c_{1}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{1t}}+\alpha _{t}\,c_{1}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{1t}}\right)^{-1}}{
+		\,\left(\alpha _{s}\,c_{1}\,\xi _{\mathrm{2s}}\,\xi _{\mathrm{2t}}-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}+\alpha _{t}\,c_{1}\,\xi _{\mathrm{2s}}\,\xi _{\mathrm{2t}}-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)
+	}
+	$$
+	The mixed efficiency restrictions (either case) from \autoref{tab:paramrest} imply that $(\alpha _{s}\,c_{1}\,\xi _{\mathrm{2s}}\,\xi _{\mathrm{2t}}-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}+\alpha _{t}\,c_{1}\,\xi _{\mathrm{2s}}\,\xi _{\mathrm{2t}}-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}})$ and $(\alpha _{s}\,c_{1}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{1t}}+\alpha _{t}\,c_{1}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{1t}})$ have opposite signs.
+Then, including the negative sign on the first term, the elasticity of substitution is positive as expected.
+
+	At this point, we cannot further simplify the elasticity of substitution.
+Furthermore, this expression and how it changes with the given parameters is not intuitive.
+Hence, we primarily rely on numerical simulations in the main text.
+However, in the following two subsections, we look at two special cases for a better theoretical intuition of this elasticity.
+
+	\subsection{Equilibrium in the Case of $\sigma \to \infty $}
+
+	Here, we consider what the competitive equilibrium looks like when $\sigma \to \infty$.
+This corresponds to the case where electricity consumption in each period is a perfect substitute for electricity consumption in the other periods.
+
+	Since $\sigma = 1/(1-\phi)$, we have $\phi \to 1$ which implies
+	$$  U = \left( \sum_t \alpha_t Z_t^\phi  \right)^{1/\phi} \to  \sum_t \alpha_t Z_t = \boldsymbol{\alpha}^T \boldsymbol{\xi}^T \mathbf{X}$$
+	Utility  here is simply a weighted sum of total electricity consumption. In other words, $Z_T$ is a prefect substitute for $Z_s$ for all periods $t,s$.
+
+	In order to find the equilibrium solution, we can maximize utility directly with respect to $\mathbf{X}$.
+To see why, first note that we have assumed that markets are perfectly competitive with no frictions; also, the utility function satisfies local  nonsatiation.
+With these assumptions, we can apply the First Welfare Theorem which states that the market equilibrium will be equivalent to the social planner's solution.
+Consequently, we can abstract from the firm problem and set $\mathbf{X}$ directly in a way that maximizes consumer utility.
+
+	Firstly, we can see that the marginal utility of each technology is given by $\sum_t \alpha_t \xi_{i,t}$.
+This is simply the sum of electricity output of each input across periods, weighted by the share parameter.
+Next, the cost of each input $i$ is $c_i$ by definition.
+Therefore, the total utility from spending all of income $I$ into a particular input is given by $(I/c_i) \sum_t \alpha_t \xi_{i,t}$.
+Now, consider the set
+	$$S = \argmax_i \, \sum_t \alpha_t \xi_{i,t}/c_i$$
+	This set contains the indices of the inputs that have the maximal cost-adjusted marginal utility. 
+	The optimal solution for $\mathbf{X}$ is defined by the set 
+	$$
+	W =
+	\{ \mathbf{X} \, : \, \mathbf{c}^T \mathbf{X} = I \;,\;  \mathbf{X} \geq 0 \;,\; \text{and} \;\;  (x_i > 0 \implies i \in S) \;\; \forall i \}
+	$$
+	This set contains vectors that define bundles of inputs that maximize utility.
+The intuition behind this result is based on the linearity of utility.
+This causes the total utility offered by a particular input to be equal to its quantity multiplied by its marginal utility.
+Consequently, since each input's marginal utility is a constant, exogenous value, the optimal bundle of inputs consists of a convex combination of those inputs in $S$.
+Specifically, the indices in $S$ denote the technologies that have maximial cost-adjusted marginal utility, so these inputs  will individually and in combination maximize consumer utility against the budget constraint.
+
+	\begin{proof}
+
+		Consider $\mathbf{Y} \not\in W$ where $\mathbf{Y} \geq 0$ (feasible) and $\mathbf{c}^T  \mathbf{Y} \leq  I$ (affordable).	Note that $\mathbf{Y} \not\in W$ implies we have either $\mathbf{c}^T \mathbf{Y} < I$ or there exists some $i$ such that $y_i > 0$ but $i \not\in S$.
+
+		In the first case, $\mathbf{Y}$ does not satisfy the budget constraint with equality.
+Consequently, it is possible to raise some element of $\mathbf{Y}$ by $\epsilon$ while maintaining the budget constraint and achieving higher utility.
+Thus, $\mathbf{Y}$ cannot be optimal.
+That is, utility is strictly monotonic with respect to each input, so the budget constraint must be satisfied with equality at an optimal solution.
+
+		So, alternatively, that $\mathbf{Y}$ satisfies the budget constraint with equality but does not satisfy the second condition.
+Specifically, let $j$ be such an index where $y_j > 0$ but $j \not\in S$.
+Now, pick arbitrary $k \in S$, and define
+		$$ \mathbf{Y}^* =  \mathbf{Y} - e_j y_j  + e_k y_j (c_j/c_k)$$
+		where $e_j$ is a unit vector which contains 0 in all entries except the $j$'th where entry which is equal to 1.
+Note that subtracting   $e_j y_j$ reduces the cost by $c_j y_j$, while adding $ e_k y_j (c_j/c_k)$ increases the cost by $y_j c_j$.
+Consequently, we have $ \mathbf{c}^T \mathbf{Y}^* = I$.
+Furthermore, note that subtracting $e_j y_j$ still means that the $j$'th input is feasible since it will then be 0.
+And, the $k$'th input will still be feasible because adding $ e_k y_j (c_j/c_k)$ means it will remain non-negative.
+Next, in terms of utility, we have
+		\begin{align*}
+			U(\mathbf{Y}^*) &= \sum_t \alpha_t \left( \sum_i  \xi_{i,t} ( \mathbf{Y} - e_j y_j  + e_k y_j (c_j/c_k) )_i  \right) \\
+			&= \sum_t \alpha_t \left( \sum_i  \xi_{i,t} y_i \right) - \sum_t \alpha_t   \xi_{j,t} y_j   + \sum_t \alpha_t  \xi_{k,t} y_j (c_j/c_k)   
+		\end{align*}
+		Note that 
+		\begin{align*}
+			\sum_t \alpha_t  \xi_{k,t} y_j (c_j/c_k) &> \sum_t \alpha_t   \xi_{j,t} y_j \\
+			\iff 	\sum_t \alpha_t  \xi_{k,t} /c_k &> \sum_t \alpha_t   \xi_{j,t}  /c_j 
+		\end{align*}
+		The last inequality must be true given that $k \in S$ but $j \not\in S$. Therefore, we have 
+		\begin{align*}
+		- \sum_t \alpha_t   \xi_{j,t} y_j   + \sum_t \alpha_t  \xi_{k,t} y_j (c_j/c_k)  &> 0 \\
+		\implies 	U(\mathbf{Y}^*) > U(\mathbf{Y})
+		\end{align*}
+		Thus,  all feasible and affordable vectors of inputs $\mathbf{Y} \not\in W$ must be  suboptimal, since there exists another feasible and affordable vector of inputs that offers higher utility.
+
+		Now, we show that every element in $W$ gives the same amount of utility. 
+		Consider an arbitrary vector $\mathbf{Y} \in W$. Each input gives a constant marginal utility of $\sum_t \alpha_t \xi_{i,t}$. Since utility is linear, the total utility offered by $\mathbf{Y}$ is
+		\begin{align*}
+		U(\mathbf{Y}) &=  \sum_i \left(  \sum_t \alpha_t \xi_{i,t} \right) y_i \\
+		&= \sum_t \alpha_t \xi_{1,t} y_1 + \dots + \sum_t \alpha_t \xi_{n,t} y_n
+		\end{align*}
+		where $n$ is the number of inputs. By definition, we have $y_i > 0 \implies i \in S$, so we have $i \not\in S \implies y_i = 0$. Thus, we can simplify the utility to 
+		$$U(\mathbf{Y}) = \sum_t \alpha_t \xi_{s_1,t} y_{s_1} + \dots  + \sum_t \alpha_t \xi_{s_m,t} y_{s_m} $$
+		where $m$ is the number of elements in $S$.
+If $m = 1$, there is only one element in $S$, so there is only one element in $W$ and we are done; otherwise, assume that $m > 1$.
+Now, suppose that we reduce element $s_m$ of $\mathbf{Y}$ to 0 and shift the additional income left over to the first element $s_1$.
+This gives us
+		$$\mathbf{Y}^{(m)} =  \mathbf{Y} - e_{s_m} y_{s_m} + e_{s_1} y_{s_m} (c_{s_m}/c_{s_1})$$
+		Again, linear utility gives us 
+		\begin{align*}
+		U(\mathbf{Y}^{(m)}) &= U(\mathbf{Y}) - U(e_{s_m} y_{s_m}) + U(e_{s_1} y_{s_m} (c_{s_m}/c_{s_1})) 
+		\end{align*}
+		And, since $s_1, s_m \in S$, we have
+		\begin{align*}
+			\sum_t \alpha_t \xi_{s_1, t} /c_{s_1} &=	\sum_t \alpha_t \xi_{s_m, t} /c_{s_m}  \\
+			\sum_t \alpha_t \xi_{s_1, t} (c_{s_m}/c_{s_1}) &=	\sum_t \alpha_t \xi_{s_m, t}  \\
+			\sum_t \alpha_t \xi_{s_1, t} (c_{s_m}/c_{s_1}) y_{s_m} &=	\sum_t \alpha_t \xi_{s_m, t} y_{s_m} \\
+			U(e_{s_1} y_{s_m} (c_{s_m}/c_{s_1})) &=	U(e_{s_m} y_{s_m})\\
+		\end{align*}
+		Therefore, $U(\mathbf{Y}^{(m)}) = U(\mathbf{Y})$.
+Furthermore, it is easy to see that $\mathbf{Y}^{(m)}$ is feasible (elements non-negative) and satisfies the budget constraint by an argument similar to one used earlier.
+Next, if we repeat this procedure $m-1$ times, we arrive at $U(\mathbf{Y}^{(1)}) = U(\mathbf{Y})$ where $\mathbf{Y}^{(1)}$ is a bundle consisting only of the first input.
+Note that $\mathbf{Y}^{(1)}$ must satisfy the budget constraint with equality, so it must be equal to $e_{s_1} (I/c_{s_1})$.
+In short, we have shown that every vector in $W$ offers utility $U( e_{s_1} (I/c_{s_1})) = \sum_t \alpha_t \xi_{{s_1},t} (I/c_{s_1})$.
+
+		Overall, we have shown that all bundles in $W$ offer the same utility, and all feasible and affordable bundles not in $W$ offer strictly less utility than those in $W$. \\
+		\hfill
+	\end{proof}
+
+	%This further allows us to write the marginal utility of each input $i$ as $\sum_t \alpha_t \xi_{i,t}$ -- a weighted sum of the electricity produced by a marginal unit of that input.
+Since we have assumed that firms are competitive,
 
@@
 		X = \begin{pmatrix}
-		\dfrac{\alpha _{s}\,\xi _{\mathrm{2t}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1}}} \\
-		\dfrac{\alpha _{t}}{c_{2}}-\dfrac{\alpha _{s}\,\xi _{\mathrm{1}}}{c_{1}\,\xi _{\mathrm{2t}}-c_{2}\,\xi _{\mathrm{1}}}
+		\dfrac{\alpha_s}{c_1 - c_2} \\[2ex] 
+		\dfrac{\alpha_t}{c_2} - \dfrac{\alpha_s}{c_1 - c_2}
 		\end{pmatrix}
@@
 		\begin{align*}
-		\frac{X_1}{X_2} &= \frac{\alpha_s \xi_{2t} \left( c_2 ( c_1 \xi_{2t} - c_2 \xi_{1} ) \right)}{ \left( \alpha_t (c_1 \xi_{2t} - c_2 \xi_{1}) -  c_2 \alpha_s \xi_1 \right) (c_1 \xi_{2t} - c_2 \xi_{1t})}  \\
-		&= \frac{\alpha_s c_2 \xi_{2t}}{ \alpha_t (c_1 \xi_{2t} - c_2 \xi_{1}) -  c_2 \alpha_s \xi_1 }\\
-		&= \frac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{\xi _{1}\,\left(\alpha _{s}\,c_{2}+\alpha _{t}\,c_{2}\right)-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}} \\
-		&= \frac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}
-		\end{align*}
-		where $\alpha_t + \alpha_s = 1$ by definition (see \hyperref[sec:consumers]{Section II.A}).  Next, we can see that:
-		$$
-		\frac{\partial \log(X_1/X_2)}{c_1} = \frac{\alpha _{t}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}
-		$$
-		The elasticity of substitution $e_{1,2}$ is given by:
-		\begin{align*}
-		\frac{\partial \log(X_1/X_2)}{\partial \log(c_2/c_1)} &= \frac{\partial \log(X_1/X_2)}{\partial c_1}\frac{\partial c_1}{\partial \log(c_2/c_1)} \\
-		&= \left( \frac{\alpha _{t}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}} \right) \left( -c_1 \right)  \\
-		&= \frac{-c_1 \alpha _{t}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}}\\
-		&= \left( \frac{c_2 \xi_1 }{-c_1 \alpha_t \xi_{2t}} + 1 \right)^{-1}
+		\frac{X_1}{X_2} &= \frac{\alpha _{s}\,c_{2}}{\alpha _{t}\,c_{1} - c_2}
+		\end{align*}
+		where $\alpha_t + \alpha_s = 1$ by definition (see \hyperref[sec:consumers]{Section II.A}).  Next, using the earlier result, we have
+		\begin{align*}
+		e_{12} &= 
+		\frac{-\alpha _{s}\,\alpha _{t}\,c_{1}\,c_{2}\,{\left(\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)}^2 \left(\alpha _{s}\,c_{1}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{1t}}+\alpha _{t}\,c_{1}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{1t}}\right)^{-1}}{
+			\,\left(\alpha _{s}\,c_{1}\,\xi _{\mathrm{2s}}\,\xi _{\mathrm{2t}}-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}+\alpha _{t}\,c_{1}\,\xi _{\mathrm{2s}}\,\xi _{\mathrm{2t}}-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}\right)
+		}\\
+		&= \frac{-\alpha_s \, \alpha_t \, c_1 \, c_2 \, (\xi_{1s} \xi_{2t})^2 ( -\alpha_s c_2 \xi_{1s} \xi_{1t} + \alpha_t c_1 \xi_{1s} \xi_{2t} - \alpha_t c_2 \xi_{1s} \xi_{1t})^{-1}}{
+		( \alpha_s c_2 \xi_{1s} \xi_{2t})		
+		} \\
+		&= 
+		\frac{-\alpha _{t}\,c_{1}\,\xi _{\mathrm{1t}}}{\alpha _{s}\,c_{2}\,\xi _{\mathrm{1t}}-\alpha _{t}\,c_{1}\,\xi _{\mathrm{1t}}+\alpha _{t}\,c_{2}\,\xi _{\mathrm{1t}}} \\
+		&= 
+		\frac{\alpha _{t}\,c_{1} }{\alpha _{t}\,c_{1} - c_2}
 		\end{align*}
@@
 		\begin{align*}
-		\frac{\partial \log(X_1/X_2)}{\partial \log(c_2/c_1)} &= \frac{-c_1 \alpha _{t}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}} \\
-		&= \left( \frac{-\alpha _{s}\,c_{2}\,\xi _{\mathrm{2t}}}{c_2\,\xi_1-\alpha _{t}\,c_{1}\,\xi _{\mathrm{2t}}} \right) \left( \frac{- \alpha_t c_1 \xi_{2t} }{- \alpha_s c_2 \xi_{2t}} \right)\\
+		\frac{\partial \log(X_1/X_2)}{\partial \log(c_2/c_1)} &= \frac{\alpha _{t}\,c_{1} }{\alpha _{t}\,c_{1} - c_2}\\
+		&= \left( \frac{\alpha _{s}\,c_{2} }{\alpha _{t}\,c_{1} - c_2} \right) \left( \frac{ \alpha_t c_1 }{ \alpha_s c_2 } \right)\\
 		&= \left( \frac{X_1}{X_2} \right) \left( \frac{ \alpha_t c_1  }{\alpha_s c_2 } \right)
@@
 Furthermore, we set the parameter for the intertemporal elasticity of substitution for electricity consumption equal to our estimate $\hat{\sigma} = 0.8847$.
-In order to generate these numerical results, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.5\, c_1, 2 \,c_1)$.
+In order to generate these numerical results, we first found the optimal quantities of $\mathbf{X}$ over a range of prices $c_1^* \in (0.5\, c_1, 2 \,c_1)$.
 Then, we obtained estimates of the elasticity of substitution by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1/ c_2)$.
@@
 Furthermore, we set the parameter for the intertemporal elasticity of substitution for electricity consumption equal to our estimate $\hat{\sigma} = 0.8847$.
-In order to generate these numerical results, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.9\, c_1, 2 \,c_1)$.
+In order to generate these numerical results, we first found the optimal quantities of $\mathbf{X}$ over a range of prices $c_1^* \in (0.9\, c_1, 2 \,c_1)$.
 Then, we obtained estimates of the elasticity of substitution by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1, c_2)$.
@@
 These results were obtained using the following parameters: $\alpha_t = 0.5$, $\alpha_s = 0.5$, $\xi_1 = (0.95, \, 1)$, $\xi_2 = (1, \, 0.95)$, $c_1 = 100$, $c_2 = 100$.
-In order to generate these numerical results, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (0.5\, c_1, 1.5 \,c_1)$.
+In order to generate these numerical results, we first found the optimal quantities of $\mathbf{X}$ over a range of prices $c_1^* \in (0.5\, c_1, 1.5 \,c_1)$.
 Then, we obtained estimates of the elasticity of substitution by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1, c_2)$.
@@
 Furthermore, we set the parameter for the intertemporal elasticity of substitution for electricity consumption equal to our estimate $\hat{\sigma} = 0.8847$.
-In order to generate these numerical results, we first found the optimal quantities of $X$ over a range of prices $c_1^* \in (c_1, 2 \,c_1)$.
+In order to generate these numerical results, we first found the optimal quantities of $\mathbf{X}$ over a range of prices $c_1^* \in (c_1, 2 \,c_1)$.
 Then, we obtained estimates of the elasticity of substitution by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1, c_2)$.

### 2019-12-27 code/simulation/sim_eos_robust.m
Add code for robustness check
- generate and update figures

@@ -1,0 +1,108 @@
+%% Elasticity of Substitution Sim with error bars on sigma estimate
+
+close all; clear; clc;
+
+% Simulation params
+n = 5000;
+cost_multiplier = linspace(0.5,2,n);
+sigma_range = [1, 0.8847, 0.5, 0.25, 0.1,  0.01];
+m = length(sigma_range);
+
+% Exogenous params
+c_1 = 104.3;
+c_2 = 60;
+alpha = [0.6, 0.4];
+xi_1  = [1,   1];
+xi_2  = [1, 0.1];
+budget = 1;
+
+
+figure('Renderer', 'painters', 'Position', [100 100 900 400])
+hold on;
+
+for j = 1:m
+    
+    sigma = sigma_range(j);
+    results = zeros(n,2); 
+
+    for i = 1:n
+
+
+        phi   = (sigma - 1)/sigma;
+        x_1_cost_param = c_1*cost_multiplier(i);
+        x_2_cost_param = c_2;
+
+        % Prices
+        xi_mat   = [xi_1; xi_2];
+        cost_mat = [x_1_cost_param; x_2_cost_param];
+        prices   = xi_mat\cost_mat;
+
+        if any(prices<0)
+            continue
+        end
+
+        % Price Index
+        P = ((1/2) * (prices'.^(1-sigma))*(alpha'.^sigma)).^(1/(1-sigma));
+        if sigma == 1
+            P = 1;
+        end
+        
+        % Quantities
+        Y = ((alpha'./prices).^(sigma)) * (budget/P);
+           
+        X = (xi_mat')\Y;
+
+        results(i,:) = X';
+
+    end    
+
+    output = [];
+    output(1,:) = c_1*cost_multiplier'./c_2;
+    output(2,:) = results(:,1)./results(:,2);
+
+    % subset to positive quantities
+    ind = ~any(output <= 0);
+    output = output(:,ind);
+
+
+    % relationship between log prices and quantities
+%     subplot(2,1,1);
+%     hold on;
+%     
+%     plot(-log(output(1,:)), log(output(2,:)), 'LineWidth', 1, ...
+%          'Color', [1, 1, 1]*(sigma/2 + 0.1))
+  
+    
+    % relationship between log prices and quantities
+%     subplot(2,1,2);
+    hold on;
+    
+    plot(-log(output(1,2:end)), ...
[…]

### 2019-12-27 documents/revision.tex
Revise paper
- update equilibrium section
- update discussion
- add robustness check

@@
 \newtheorem{proposition}{Proposition}
+\newtheorem{lemma}{Lemma}
 \newenvironment{proof}[1][Proof]{\noindent\textbf{#1:} }{\ \rule{0.5em}{0.5em}}
@@
 
-	% In this paper, we develop a model where consumers demand electricity over time
-
 	Renewable energy technologies have seen considerable adoption over the last few decades \citep{EIArenew}.
-Unlike the alternatives, wind and solar power are particularly unique in that the amount of energy they supply is intermittent.
-Consequently, designing economically efficient policies to promote their adoption is not straightforward given that they cannot easily substitute for fossil fuel technologies such as coal power.
-Moreover, traditional approaches such as the levelized cost of electricity (LCOE) fail to capture the true economic value of intermittent technologies, because they neglect to account for variation in output and prices over time \citep{Joskow2011}.
-
-	In this paper, we develop a model where we capture the effects of intermittency on the adoption of energy technologies.
-We do so through the demand-side of the market; specifically, we model consumers using a utility function that implies a preference for smoothing electricity consumption over time.
-We then parameterize our model empirically, implement our model numerically, and study the results.
-
-	Some of the literature has approached this problem by constructing numerical models that find the cheapest renewable technology set while accounting for intermittent supply.
+Certain renewables, such as wind and solar power, are particularly unique technologies in that the amount of energy they supply is intermittent.
+Specifically, by intermittent, we mean that their output changes in predictable ways related to physical constraints.
+For example, wind turbine output varies with wind speed and direction which can be predicted ahead of time.
+On the other hand, traditional fossil fuel energy sources offer a constant amount of energy.
+Intermittency presents a challenge when evaluating the economic value of renewable energy.
+Traditional approaches such as the levelized cost of electricity (LCOE) fail to capture the true economic value of intermittent technologies, because they neglect to account for variation in output and prices over time \citep{Joskow2011}.
+Additionally, the intermittency of renewables complicates their ability to substitute for fossil energy, because consumers prefer to have more electricity at certain times than others, while the output of intermittent renewables varies exogenously with the weather.
+Consequently, modeling and better understanding the effects of intermittency  would help us design more effective policies to promote the adoption of renewable energy.
+
+	In this paper, we develop a partial equilibrium model of the electricity sector that takes into account intermittent generation.
+Specifically, the electricity sector consists of a representative firm that chooses and builds capacity from a set of electricity-generating technologies to maximize profit; some of these technologies are intermittent while others have constant output.
+Then, we consider a representative consumer who purchases varying quantities of electricity in each period in order to maximize utility.
+People prefer to smooth their electricity consumption over time, so we model our consumer's preferences using a CES function of electricity consumption differentiated by period.\footnote{ The use of a CES function in this way has been explored earlier by \citet{Schwarz}, \citet{Schwarz}, \citet{Herriges}, and \citet{KS1994}, \citet{Aubin}, and \citet{Moha2016}.
+Their papers empirically estimate the parameters for this function; we provide a more detailed discussion of the empirical literature in our \hyperref[sec:methodology]{Methodology}.} These two sides of the market reach an equilibrium through the prices of electricity in each period.
+
+	Our model has two important features that distinguish it from present approaches in the literature.
+Firstly, it accommodates the critique made by \citet{Joskow2011}.
+In our model, when firms maximize profit, they implicitly measure the economic value of each energy technology by integrating its production profile with electricity prices.
+That is, firms take into account how much a technology produces in each period and the price of electricity in those periods, as opposed to simply taking the product of the average electricity output of a technology with the average price of electricity.
+Secondly, our model captures the imperfect substitutability of intermittent and reliable energy technologies  by modeling consumers with a preference for smooth electricity consumption which they signal through prices.
+When firms respond to this signal and maximize profit, the equilibrium result  is that the intermittency of certain renewables interferes with their ability to perfectly substitute for reliable energy technologies.
+In other words, we directly link the substitutability of energy technologies with their intermittency.
+	This contrasts with alternative approaches that model electricity as a homogenous good produced according to  a CES function of electricity-generating technologies; such approaches model imperfect substitutability on the supply-side to implicitly capture the effects of intermittency.
+However, these approaches abstract from key features of intermittency and thus may reach incorrect conclusions.
+
+	Next, we parametrize our model empirically by fitting the parameters of the consumer's utility function using electricity consumption and price data for each US state.
+Since the consumer's CES utility function is composed of electricity consumption differentiated by time, the elasticity parameter represents the intertemporal elasticity of substitution for electricity consumption; this parameter plays a particularly important role in our model, since it captures the effects of intermittency on demand.
+Next, to model the supply side, we narrow our framework to a two-period, two-technology setting to focus on the substitutability between renewable and fossil energy.
+We proxy for renewable and fossil energy using solar and coal, respectively, while parameterizing each accordingly.
+Finally, we implement our model numerically and provide suggestions for policy and future models.
+
+	Our results quantify the relationship between the intertemporal elasticity of substitution for electricity consumption  (IES) and the elasticity of substitution between renewable and fossil energy.
+The intuition behind the relationship is based on how the IES affects the desire for smoother consumption.
+When the IES is low, consumers want their electricity consumption to be smooth; so, they prefer not to consume intermittent sources of energy such as solar.
+This means that the substitutability between renewables and fossils will be small.
+On the other hand, when the IES is high, consumers care less about smoothing their electricity consumption, so they are more willing to substitute between renewable and fossil energy.
+We also find that the elasticity of substitution between renewable and fossil energy is not a simple, constant relationship.
+This is important because a significant amount of literature has assumed a CES structure between renewable and fossil energy (see \citet{Pap}); this assumption has been motivated, in part, by the need to capture imperfect substitutability between these two generation technologies as a result of intermittency.
+But, our model finds that the elasticity of substitution between renewable and fossil energy is far from constant as a consequence of intermittency.
+This elasticity appears to vary with the quantity of each energy technology.
+Hence, we argue against assuming a CES structure.
+Alternatively, we find that a variable elasticity of substitution (VES) production function can be used to approximate the relationship that our model finds between the elasticity of substitution and the quantities of each technology.\footnote{ The VES production function was created by \citet{VES}; we describe it in further detail in the \hyperref[sec:VES]{discussion}.
+} The numerical results suggest this relationship is roughly linear which is exactly what a VES function assumes.
+Moreover, a VES function is analytically tractable, so it can be implemented in other frameworks without making them overly complicated.
+
+	These results have multiple important implications for environmental/energy policy.
+Firstly, the welfare burden of both a carbon tax and renewable subsidies vary geographically.
+This variation is a consequence of differences in the intermittency and availability of renewable energy by location.
+Moreover, this variability can create a trade-off between equity and efficiency when introducing policy to mitigate climate change.
+Secondly, we find strong motivation for research and development subsidies aimed at improving battery technology.
+Better energy storage can greatly increase the substitutability of renewable and fossil energy.
+Also, batteries can  lessen the distributional side effects of carbon taxes and renewable subsidies by  reducing intermittency.
+Thus, research into improving batteries can complement other policies by making them more equitable and by increasing their impact on the adoption of renewables.
+Finally, we revisit the results of \citet{Ace2012} and qualitatively discuss the implications of our model in their setting.
+
+	Some of the literature has approached the question of intermittency by constructing numerical models that find the cheapest renewable technology set while accounting for intermittent supply.
 For instance, \citet{MN2006} model uncertain renewable output with intertemporal generation constraints, while \citet{NCK2007} model the temporal and spatial characteristics of wind output to optimize its deployment in the UK.
@@
 Additionally, \citet{Boren2012} reviews the effects of present public policies used to promote renewables and the challenges posed by intermittency.
-
 Our model comes closest to that of \citet{HH} who build a peak-load pricing model where the availability of renewable capacity varies stochastically.
-This stochastic variability models intermittency and negatively affects the adoption of renewables.
-Furthermore, they simplify their analysis by setting aside complications such as  outage costs and rationing rules.
-Their model finds an S-shaped adoption curve for renewables as they get cheaper.
-In addition, they find that a Pigouvian tax can properly internalize the costs of fossil fuels in a setting with perfect competition.
-Like \citeauthor{HH}, we model the  equilibrium of a market with dynamic prices and access to both renewable and fossil energy.
-However, our results differ in key ways, because we take a different approach to modeling intermittency.
-
-	To highlight this difference, we must first contrast the terms  \textit{intermittency} and \textit{reliability}.
-By intermittency, we mean predictable changes in output related to physical constraints.
-For instance, while wind energy output varies over time, if  we know the wind speed and angle, we may precisely derive the quantity of energy that a wind farm generates.\footnote{ \citet{Foley2012} provide a review of the literature on the forecasting of wind power.
-Over time, forecasts have gotten much more accurate allowing electricity grids to manage wind power intermittency ahead of time.}  At the same time, forecasts can never be perfectly accurate, so we may see still unexpected variation in  electricity output.
-This unpredictability is better captured by the notion of reliability; specifically,  we refer to definition provided by the US Department of Energy's \citet{ORNL} -- ``Power reliability can be defined as the degree to which the performance of the elements in a bulk system results in electricity being delivered to customers within accepted standards and in the amount desired." This is more so related to the stochastic or unpredictable variation in the output of a technology.
+Like \citeauthor{HH}, we model the  equilibrium of a market with dynamic prices\footnote{ \citeauthor{HH} motivate models incorporating the dynamic pricing of electricity.
+They argue that such approaches to pricing will become the norm with further technological advances and coming regulatory changes.} and access to both renewable and fossil energy.
+However,  \citeauthor{HH}'s approach  is closer to one of reliability rather than intermittency.
+In accordance with US Department of Energy's \citet{ORNL}, we define reliability as stochastic variability while intermittency as deterministic variability.\footnote{
+		The \citeauthor{ORNL} states, ``Power reliability can be defined as the degree to which the performance of the elements in a bulk system results in electricity being delivered to customers within accepted standards and in the amount desired.'' Consequently, stochastic variance in output is better captured by the term  reliability.
 Unlike intermittency, this cannot be planned around with 100\% certainty.
 A practical example may be a wind turbine's systems failing.
-While we may know the chances of this occurring, it's not always possible to know when it will occur ahead of time; consequently, this may result in a temporary reduction in the quantity and quality of the electricity delivered --  a loss of reliability.
-In short, when \citeauthor{HH} model renewable output as equal to a base capacity multiplied by a uniform random variable, their treatment is closer to one of reliability rather than intermittency.
-
-	On the other hand,  we model intermittency as defined above by allowing the output of renewable energy to differ between periods according to known function.
-For parsimony, we assume that the output of each technology  does not vary stochastically; that is, we do not study reliability.
-Next, we model the electricity sector using a representative firm that chooses and builds capacity from a set of electricity-generating technologies to maximize profit; some of these technologies are intermittent while others have constant output.
-Then, we consider a representative consumer who purchases varying quantities of electricity in each period in order to maximize utility.
-People prefer to smooth their electricity consumption over time, so we model our consumer's preferences using a CES function of electricity consumption differentiated by period.\footnote{ The use of a CES function in this way has been explored earlier by \citet{Schwarz}, \citet{Schwarz}, \citet{Herriges}, and \citet{KS1994}, \citet{Aubin}, and \citet{Moha2016}.
-Their papers empirically estimate the parameters for this function; we provide a more detailed discussion of the empirical literature in our \hyperref[sec:methodology]{Methodology}.} These two sides of the market reach an equilibrium through adjustments in prices of electricity in each period.
-Otherwise, we make many of the same assumptions that \citet{HH} do; we assume dynamic pricing,\footnote{ \citeauthor{HH} motivate models incorporating the dynamic pricing of electricity.
-They argue that such approaches to pricing will become the norm with further technological advances and coming regulatory changes.} no load rationing, and positive prices.
-
-	Then, we parametrize our model empirically.
-We fit the parameters of the consumer's utility function using electricity consumption and price data for each US state.
-Since the consumer's CES utility function is composed of electricity consumption differentiated by time, the elasticity parameter represents the intertemporal elasticity of substitution for electricity consumption (IES); this parameter plays a particularly important role in our model, since it captures the effects of intermittency on demand.
-Next, to model the supply side, we narrow our framework to a two-period, two-technology setting to focus on the substitutability between renewable and fossil energy.
-We proxy for renewable and fossil energy using solar and coal, while parameterizing each accordingly.
-Finally, we implement our model numerically and provide suggestions for policy and future models.
-
-	Our results quantify the relationship between the intertemporal elasticity of substitution for electricity consumption  (IES) and the elasticity of substitution between renewable and fossil energy.
-The intuition behind the relationship is based on how the IES affects the desire for smoother consumption; when the IES is low, consumers want their electricity consumption to be smooth.
-Consequently, they disprefer intermittent sources of energy such as certain renewables.
-Consequently, the substitutability between renewables and fossils will be small.
-On the other hand, when the IES is high, consumers care less about smoothing their electricity consumption, so they are more willing to substitute between renewable and fossil energy.
-Furthermore, we find that the elasticity of substitution between renewable and fossil energy is not a simple, constant relationship.
-This is important because a significant amount of literature has assumed a CES structure between renewable and fossil energy (see \citet{Pap}); this assumption has been motivated, in part, by the need to capture imperfect substitutability between these two generation technologies as a result of intermittency.
-But, our model finds that the elasticity of substitution between renewable and fossil energy is far from constant as a consequence of intermittency.
-Specifically, this elasticity appears to vary with the quantity of each energy technology.
-Hence, we argue against assuming a CES structure.
-Alternatively, we find that a variable elasticity of substitution (VES) production function can be used to approximate the relationship that our model finds between the elasticity of substitution and the quantities of each technology.\footnote{ The VES production function was created by \citet{VES}; we describe it in further detail in the \hyperref[sec:VES]{discussion}.
-} That is, this relationship is roughly linear which is exactly what a VES function assumes.
-Moreover, a VES function is analytically tractable, so it can be implemented in other frameworks without making them overly complicated.
-
-	Additionally, our results have multiple important implications for environmental/energy policy.
-Firstly, show how the welfare burden of a carbon tax  and the effect of subsidies on renewable adoption both vary geographically.
-This variation is a consequence of differences in the intermittency and availability of renewable energy by location.
-Moreover, this can create a trade-off between equitably and efficiently mitigating climate change.
-Hence, policymakers should account for geographic variation in energy markets to ensure they handle this equity-efficiency trade-off appropriately.
-Secondly, we find strong motivation for research subsidies aimed at improving battery technology.
-That is, better energy storage can greatly increase the elasticity of substitution between renewable and fossil energy.
-Also, batteries can  lessen the distributional side effects of carbon taxes and renewable subsidies by  reducing intermittency.
-Hence, research into improving batteries can complement other policies by making them more equitable and by increasing their impact on the adoption of renewables.
-Finally, we revisit the results of \citet{Ace2012} and qualitatively discuss the implications of our model in their setting.
-We now discuss our model in greater detail.
+While we may know the chances of this occurring, it's not always possible to know when it will occur ahead of time; consequently, this may result in a temporary reduction in the quantity and quality of the electricity delivered.
+	} Consequently, since we model a different characteristic of renewable output, our model and results differ in a key way.
+
+	The remainder of the paper proceeds as follows.
+The Model section states our model and its equilibrium; we also provide a discussion of the (consumer side) IES parameter and how it relates to the substitutability of intermittent and reliable technologies on a theoretical level.
+The Empirical Methodology section details how we estimate the IES parameter along with a description of our data.
+This is followed by the Results section where we discuss our estimates.
+We then empirically parameterize, numerically implement, and study our model further in the Discussion.
+Finally, in the Conclusion, we summarize our model's policy implications and offer suggestions for future models of intermittency.
 
 	\section{Model}
+	\label{sec:Model}
 
@@
 	\begin{align}\label{eq:demand}
-	Z_t &= \left(\frac{\alpha_t}{p_t} \right)^\sigma \frac{I}{P} \\
+	Z_t &= \left(\frac{\alpha_t}{p_t} \right)^\sigma \frac{I}{P} \\\label{eq:priceindex}
 	P &= \sum_t \alpha_t^\sigma p_t^{1-\sigma}
@@
 And, thirdly, for certain technologies, this time frame is short enough to assume that $\xi$ is exogenous; that is, technologies like coal power cannot significantly modify their output within a day, so $\boldsymbol{\xi}$ can be treated as a given set of constants.
-These latter two assumptions, that $\mathbf{X}$ cannot change over time and that $\boldsymbol{\xi}$ is exogenous, are important for parsimony, because they prevent more complicated dynamics for entering our model.
+These latter two assumptions, that $\mathbf{X}$ cannot change over time and that $\boldsymbol{\xi}$ is exogenous, are important for parsimony, because they prevent more complicated dynamics from entering our model.
 So, by assuming a sufficiently short time frame, we can continue our study of intermittency in a relatively simpler setting.
+Furthermore, in this setting, we can use ``intermittent'' to refer to a technology where output per unit, $\xi_{i,t}$, varies over time (with $t$).
 
@@
 So, like Helm and Meir, we take an intermediate approach by using a linear cost function.
-Specifically, the total cost of input $\mathbf{X}$ is given by $\equiv \sum_i c_i X_i \equiv \mathbf{c}^T \mathbf{X}$ where $c_i$ is the cost per unit of $X_i$.
+Specifically, the total cost of the input bundle $\mathbf{X}$ is given by $ \sum_i c_i X_i \equiv \mathbf{c}^T \mathbf{X}$ where $c_i$ is the cost per unit of $X_i$.
 Total profit is given by
@@
 Now, maximizing profit, we find the first order condition:
-	\begin{equation}
+	\begin{equation}\label{eq:firm_foc}
 	\frac{\partial \Pi}{\partial \mathbf{X}} = 0 \implies \mathbf{p} =  \boldsymbol{\xi}^{-1} \mathbf{c}
 	\end{equation}
-	Combining this FOC with the demand equation (\cref{eq:demand}) allows us to find the equilibrium.
+	Combining this FOC with the demand equation (\autoref{eq:demand}) allows us to find the equilibrium.
 Generally, the equilibrium results for any number of technologies ($n$) are analytic, but they are difficult to interpret algebraically due to the number of parameters involved.
@@
 
-	For more tractable results, we consider a simpler scenario where $n = m = 2$ and $\sigma = 1$ (Cobb-Douglas); this particular case is described in greater  detail  in \hyperref[sec:cobbdoug]{Appendix A.A}.
-These parameters simplify the model enough to allow us to derive comparative statics and determine which sets of parameters lead to edge cases.
+	For more tractable results, we consider a simpler scenario where $n = m = 2$ and $\sigma = 1$ (Cobb-Douglas); this particular case is described in greater details in \hyperref[sec:cobbdoug]{Appendix A.A}.
+These assumptions simplify the discussion of intermittency.
+In a two-period, two-technology model, we can intuit that the magnitude of intermittency is given by how much $\xi_{i,t}/c_i$ (output per dollar) varies with $t$; this is useful for understanding the link between intermittency and other parameters like $\sigma$.
 Furthermore, as we will discuss in our \hyperref[sec:results]{results}, assuming $\sigma=1$ is not far from its empirical estimate.
 
-	To start, we discuss the conditions required on the exogenous parameters  to avoid edge-cases.
-But  first, we define two recurring terms in our analysis: cost efficiency and output efficiency.
-For some arbitrary period $t$ and technology $i$, we use cost efficiency to refer to $\xi_{i,t}/c_i$ and output efficiency to refer to $\xi_{i,t}$.
-So, for example, with two technologies $i$ and $j$ and an arbitrary period $t$, technology $i$ is more cost efficient than technology $j$ in period $t$ when $\xi_{i,t}/c_i > \xi_{j,t}/c_j$.
+	We define two recurring terms in our analysis: cost efficiency and output at period $t$.
+For period $t$ and technology $i$, we use cost efficiency to refer to $\xi_{i,t}/c_i$ and output to refer to $\xi_{i,t}$.
+So, for example, with two technologies $i$ and $j$ at period $t$, technology $i$ is more cost efficient than technology $j$ when $\xi_{i,t}/c_i > \xi_{j,t}/c_j$.
 Additionally, we say a technology is economical if its equilibrium quantity is above 0.
-In order to avoid an edge-case, we require both technologies to be economical; we give the conditions to ensure this for each technology in Proposition 1.
-	\begin{proposition}
+
+	In Lemma 1 we use these two terms to define conditions that avoid an edge-case solution.
+	\begin{lemma}
 		Assume that, for all technologies $i$ and periods $t$, we have $\xi_{i,t} > 0 \, , \alpha_t > 0 \, ,$ and $ c_i > 0$.
-For technology $j$ to be economical, it must meet three conditions with respect to some arbitrary period $s$.
-Firstly, it must be more cost efficient than any of the other technologies in period $s$.
-Secondly, it must have  a relative advantage in output efficiency in the same period $s$.
-And, thirdly, there must be sufficient amount of demand for energy in this period $s$.
-	\end{proposition}
-	The first condition is on cost efficiency and is fairly intuitive.
-Consider its contrapositive: if a technology does not have an advantage in cost efficiency in any period, it will not be used; this is fairly obvious.
+Then, for technology $j$ to be economical, there need to exist a period $s$ where the following three conditions are met:
+		\begin{itemize}
+			\item $\xi_{j,s}/c_j > \xi_{i,s}/c_i$ for all $i$
+			\item $\xi_{j,s}/\xi_{j,t} >  \xi_{i,s}/\xi_{i,t} $ where $i \neq j$ and $t \neq s$
+			\item Period $s$ demand needs to be sufficiently large, i.e., $\alpha_s$ is large enough
+		\end{itemize}
+	\end{lemma}
+	The first condition is on cost efficiency and is intuitive.
+Consider its contrapositive: if a technology does not have an advantage in cost efficiency in any period, it will not be used.
 Alternatively, if a technology is the most cost effective in every single period, it will be the only technology used.
-The second condition regarding output efficiency actually stems from the invertibility of $\boldsymbol{\xi}$.
-If we did not have $\boldsymbol{\xi}$ invertible, we either have at least one technology that does not produce in any period or we have at least one technology being a linear combination of the other technologies in terms of output.
-In the latter case, some technologies are not economical because their output can be replicated by the other technologies in a more cost effective way.
-That is, suppose $\boldsymbol{\xi}$ consisted of 3 technologies but was of rank $2$.
-In this case, we may represent any of these technologies as a linear combination of the other two; call this combination the synthetic version of technology $i$.
-It is not possible for every synthetic technology $i$ to be more expensive than its original; for at least one $i$, we must have a synthetic technology being cheaper or equal in price to the actual technology.
-In the first case, synthetic technology $i$ is cheaper so we do not use the actual technology $i$.
-In the latter case, we may still eliminate technology $i$ or not use the other two technologies depending on the demand.
-Overall, in any case, $\boldsymbol{\xi}$ not invertible means that at least one technology is not used.
-Finally, the demand condition is straightforward; even if a technology is optimal in a certain period, if consumers do not sufficiently demand electricity during that period, then there is little reason to use that technology.
+The second condition regarding output stems from the invertibility of $\boldsymbol{\xi}$.
+If we did not have $\boldsymbol{\xi}$ invertible, we either have at least one technology that does not produce in any period or we have at least one technology being a linear combination of the other technologies in terms of output and $\boldsymbol{\xi}$ is of row rank $n < m$ impling that at most $n$ technologies are used in equilibrium.
+Finally, the intuition behind the demand condition is straightforward; even if a technology is optimal in a certain period, if consumers do not sufficiently demand electricity during that period, then there is little reason to use that technology.
 
@@
 	\begin{proposition}
-		Suppose that the conditions of Proposition 1 hold for each technology, so we are not in an edge case.
-The equilibrium quantity of a technology is increasing with its output efficiency and decreasing with its cost; at the same time, it is decreasing with the output efficiency of the other technologies and increasing with their cost.
-Also, suppose that some technology $i$ is the most cost effective in period $t$.
-Then, its equilibrium quantity is increasing with respect to the demand parameter $\alpha_t$ and decreasing with respect to the demand parameters of the other periods.
-Furthermore, again assuming technology $i$ is the most cost effective in period $t$, the comparative statics of $Z_t$ and $X_i$ are equivalent.
+		Suppose that the conditions of Lemma 1 hold for each technology, so we are not in an edge case. Then, 
+		\begin{itemize}
+			\item The equilibrium quantity of a technology is increasing with its output and decreasing with its cost; at the same time, it is decreasing with the output of other technologies and increasing with the cost of other technologies.
+			\item Also, suppose that some technology $i$ is the most cost effective in period $t$.
+Then, its equilibrium quantity is increasing with respect to the demand parameter $\alpha_t$ and decreasing with respect to the demand parameters in other periods.
+			\item Furthermore, again assuming technology $i$ is the most cost effective in period $t$, the comparative statics of $Z_t$ and $X_i$ are equivalent. 
+		\end{itemize}
 	\end{proposition}		
-	The comparative statics with respect to $X_i$ and output efficiency and cost of technology $i$ are not surprising.
-On the other hand, the statics for $Z_t$ may not be immediately obvious.
-Instead, they follow from the fact that we have $\mathbf{Z} \equiv \boldsymbol{\xi}^T \mathbf{X}$.
-That is, suppose we have an arbitrary technology $i$ that is the most cost effective source of electricity in period $t$.
+	The comparative statics with respect to $X_i$ and output efficiency and cost of technology $i$ are straight forward.
+On the other hand, the statics for $Z_t$  follow from the fact that we have $\mathbf{Z} \equiv \boldsymbol{\xi}^T \mathbf{X}$.
+That is, suppose technology $i$ is the most cost effective source of electricity in period $t$.
 If consumers demanded that 100\% of their energy arrive in period $t$, then relying solely on technology $i$ for energy would be the most economical solution.
-Consequently, it seems intuitive that the comparative statics of $X_i$ follow through to $Z_t$.
-This intuition just happens to apply even when other technologies are employed and there is demand in multiple periods.
+Consequently, the comparative statics of $X_i$ follow through to $Z_t$.
+This intuition can then be generalized to when multiple technologies are employed and there is demand for electricity in multiple periods.
 Similarly, the comparative statics for the share parameters of the utility function, $\boldsymbol{\alpha} \equiv \left( \alpha_t \;\; \alpha_s \right)^T$, travel in the opposite direction.
 A rise in $\alpha_t$ would directly raise the optimal quantity of $Z_t$; hence, whichever technology is most cost effective at producing in period $t$ would be used more.
-We provide a more detailed and formal discussion of the comparative statics and edge cases in the appendix.
-
-	Furthermore, these theoretical results have assumed that $\sigma = 1$.
-This simplification was made for analytical tractability; specifically, it implies that the utility function is Cobb-Douglas which then results in the first order condition $Z_t = \alpha_t/p_t$.
-This condition is vital to facilitating the analysis of $\mathbf{X}$, since, by definition, we have $\mathbf{Z} \equiv \boldsymbol{\xi}^T \mathbf{X}$.	However, this simplifying assumption on $\sigma$ may not be realistic.
-Hence, in the following section, we empirically estimate $\sigma$ to parameterize the model.
+We provide a more detailed and formal discussion of the comparative statics and edge cases in \hyperref[sec:appendixa]{Appendix A}.
+
+	These theoretical results assumed $\sigma = 1$.
+This simplification implies that the utility function is Cobb-Douglas which then results in the first order condition $Z_t = \alpha_t/p_t$.
+This condition facilitates the analysis of $\mathbf{X}$.
+In the following section, we empirically estimate $\sigma$ to parameterize the model.
 Since the empirical estimate is not exactly 1, this complicates the solution for $\mathbf{Z}$; consequently, the solution for $\mathbf{X}$ loses tractability.
-However, we can still study the model in a qualitative sense to see how values of $\sigma$ would affect the equilibrium.
+However, we can study the model analytically when $\sigma$ is asymptotically large and small to see how it affects the equilibrium.
 
 	\begin{proposition}
-		Suppose that we have $\sigma \to \infty$.
-Then, electricity consumption in each period $t$ is a perfect substitute for electricity consumption in period $s$ for all periods $t,s$.
-Secondly, the utility function takes on the linear form $U = \sum_t \alpha_t Z_t$.
-And, thirdly, the set of optimal bundles of inputs $\mathbf{X}$ is given by
+		Suppose that we have $\sigma \to \infty$. Then, 
+		\begin{itemize}
+			\item Electricity consumption in each period $t$ is a perfect substitute for electricity consumption in period $s$ for all periods $t,s$; 
+			\item The utility function takes on the linear form $U = \sum_t \alpha_t Z_t$; and
+			\item The set of optimal bundles of inputs $\mathbf{X}$ is given by 
 			$$
 			W =
-		\{ \mathbf{X} \, : \, \mathbf{c}^T \mathbf{X} = I \;,\;  \mathbf{X} \geq 0 \;,\; \text{and} \;\;  (x_i > 0 \implies i \in S) \;\; \forall i \}
+			\{ \mathbf{X} \, : \, \mathbf{c}^T \mathbf{X} = I \,,\;  \mathbf{X} \text{ non-negative} \,,\; \text{and} \;\;  (x_i > 0 \implies i \in S) \;\; \forall i \}
 			$$
 			$$\text{where} \quad S = \argmax_i \, \sum_t \alpha_t \xi_{i,t}/c_i$$
-		where $S$ represents the set of indices for technologies that have maximimal cost-adjusted marginal utility.
-In other words, any vector of inputs $\mathbf{X}$ consisting of a combination of technologies in $S$ represent a valid equilibrium solution.
+		\end{itemize}
+		$S$ represents the set of indices for technologies that have maximal cost-adjusted marginal utility.
+In other words, any vector of inputs $\mathbf{X}$ consisting of a feasible (non-negative $\mathbf{X}$) and affordable $(\mathbf{c}^T \mathbf{X} = I$) combination of technologies in $S$ represent a valid equilibrium solution.
 Furthermore, the set $Y = \{ \mathbf{Z} \,: \, \mathbf{Z} = \boldsymbol{\xi}^T \mathbf{X}  \; \, \forall \, \mathbf{X} \in W \}$ contains all possible equilibrium values of electricity output.
@@
 
-	If we have $\sigma \to \infty$, then electricity in each period becomes a perfect substitute for electricity in other periods.
-This then leads to multiple possible solutions.
-The mathematical reason is that , since the utility function becomes linear, the marginal utility of each input becomes $\sum_t \alpha_t \xi_{i,t}$; then, using only whatever input offers the highest cost-adjusted marginal utility $(1/c_i) \sum_t \alpha_t \xi_{i,t}$ will maximize utility.
-If there are multiple technologies that have the same cost-adjusted marginal utility, we may get multiple solutions.
-The intuition here is that the perfect substitutability of $Z_t$ implies that consumers do not care about smoothing their electricity consumption over time.
+	If $\sigma \to \infty$, then electricity consumption in each period becomes a perfect substitute for electricity consumption in other periods.
+In this case, the marginal utility of each input is $\sum_t \alpha_t \xi_{i,t}$; hence, the input that offers highest cost-adjusted marginal utility $(1/c_i) \sum_t \alpha_t \xi_{i,t}$ will maximize utility.
+The perfect substitutability of $Z_t$ implies that consumers do not care about smoothing their electricity consumption over time.
 But, they still value consumption in particular periods more than others through the $\boldsymbol{\alpha}$ parameter.
 Consequently, they simply use whatever technology gives them the most total electricity (weighted by $\boldsymbol{\alpha}$).
-Intermittency of output simply does not matter in this case.
-This is what we should expect given that $\sigma \to \infty$ implies perfect substitutability.
-A detailed proof is given in \hyperref[sec:cobbdoug]{Appendix A.A}.
-
-	On the other hand, suppose that $\sigma \to 0$.
-This is the standard case of perfect complements in which we would get $U = \min_t \, Z_t/\alpha_t$.
-Unlike the perfect substitute case, any analytic results would not be as clear.
-However, some of the intuition from before carries through.
-That is, when electricity consumption in each period is perfectly complementary with that in other periods, consumers care strongly about smoothing their consumption.
-For instance, consider again a two period, two technology case with solar (intermittent) and coal (constant-output); furthermore, suppose that $\alpha_t$ is constant.
+And, there may be multiple technologies that maximize consumer utility in this way; so, any combination of these technologies, indexed by $S$ in Proposition 2, will be optimal.
+Also, since consumers do not care about smoothing their consumption , the intermittency of an input has no effect on its adoption.
+A detailed proof of Proposition 2 is given in \hyperref[sec:cobbdoug]{Appendix A.A}.
+
+	On the other hand, suppose that $\sigma \to 0$; here, electricity consumption in each period is perfectly complementary with that in other periods.
+Furthermore, the utility function becomes $U = \min_t \, Z_t/\alpha_t$.
+While the analytic solution is not as clear here, some of the intuition from before carries through.
+As a result of perfect complementarity, consumers care strongly about smoothing their consumption.
+For instance, consider again a two period, two technology case with solar (intermittent) and coal (constant-output).
+Also, suppose that $\alpha_t$ is constant.
 The utility function here implies that consumers only care about periods when they are getting the least electricity.
-Since solar performs worse during the off-peak, the implicit demand for each technology would solely be based on their off-peak performance.
-Interestingly, no matter how high solar's output efficiency is during peak hours, as measured by its output per unit, consumer's decisions would be unaffected.
-In other words, intermittency plays a much larger role in this case, since \textit{when} a technology produces
+Since solar performs worse during the off-peak, the implicit demand for solar would solely be based on its off-peak performance.
+Interestingly, no matter how high solar's output efficiency is during peak hours, the consumer's decisions and utility would be unaffected.
+On the other hand, when we had $\sigma \to \infty$, the reduced performance of solar in the off-peak could always be compensated for by increasing performance during peak hours.
+In other words, intermittency plays a much larger role when $\sigma \to 0$, since, in this case, a technology that with low output efficiency in certain periods cannot compensate by having higher output efficiency in other periods.
 
@@
 In this case, intermittent energy technologies are less appealing because, by definition, they do not generate a consistent electricity output over time.
-On the other hand, suppose $\sigma$ is high.
-Then, consumers care less about consumption smoothing and are focused more on total consumption; in the extreme case above, when $\sigma \to \infty$, they only care about total consumption and not about when they get their electricity.
-In this case, the intermittency is relatively less of a concern; consequently, other factors like cost efficiency and output efficiency play a larger role.
+On the other hand, when $\sigma$ is high, consumers care less about consumption smoothing and are focused more on total consumption.
+In the extreme case above, when $\sigma \to \infty$, they only care about total consumption and not about when they get their electricity.
+Intermittency becomes less of a concern, while other factors like cost efficiency and output play a larger role.
 In short, $\sigma$ is inversely related to how much the intermittency of an input matters.
@@
 Papers that use these experiments include \citet{Schwarz}, \citet{Herriges}, and \citet{KS1994}.
-	The latter two papers estimate $\sigma$ to be around $0.1$ while the paper by \citeauthor{Schwarz}  obtains estimates around $0.04$.
+	The latter two papers estimate $\sigma$ to be around $0.15$ while the paper by \citeauthor{Schwarz}  obtains estimates around $0.03$.
 All three papers study real-time electricity pricing programs for industrial consumers using similar methodologies.
@@
 	}  from here on, we will refer to this latter elasticity as $e$.
-This elasticity is important, because sufficient substitutability between these energy inputs  is required to transition into greener economy in the future.
+Understanding this elasticity is important, because the substitutability of energy inputs determines the trade-offs required to transition into greener economy in the future.
 For instance, \citet{Ace2012} provide a model where they argue that, ``When the two	sectors [clean and dirty energy] are substitutable but not sufficiently so, preventing an environmental disaster requires a permanent policy intervention.
@@
 
-	Now, to clarify our discussion, we first look at a general model of energy production common in the literature. Specifically, we have
+	The elasticity $e$ is often assumed to be a constant value in the literature \citep{Pap}. This is because existing models often represent the electricity sector using the production function
 	\begin{equation}
@@
 	\end{equation} 
-	where   $\tilde{Z}$ is the electricity produced, $\tilde{X}_i$ is the quantity of electricity-producing input, $\beta_i$ is a share parameter, and $(\omega-1)^{-1} $ is the elasticity of substitution between the inputs.
-In other words, the literature often represents electricity production using a CES function and treats electricity as a single, homogeneous good.
+	where   $\tilde{Z}$ is the quantity of electricity output, $\tilde{X}_i$ is the quantity of electricity-producing input, $\beta_i$ is a share parameter, and $(\omega-1)^{-1} $ is the elasticity of substitution between the inputs.
+Since $\omega$ is a fixed parameter, the implied elasticity of substitution is constant.
+The literature often represents electricity production using a CES function and treats electricity as a single, homogeneous good.
 Furthermore, such models would generally have firms maximizing profit against a  demand function based on some utility-maximizing agent.
-Although this approach is not realistic in its assumptions, it captures the imperfect substitution between energy inputs in a tractable way.
-However, any results based on this model would be based on the assumption that the  elasticity of substitution between energy inputs, $e$, is constant.
-
-	On the other hand, our model is based on relatively more realistic assumptions but it implies that $e$ is non-constant.
+This approach captures the imperfect substitution between energy inputs in a tractable way.
+However, any results based on this model may be driven by on the assumption that the  elasticity of substitution between energy inputs, $e$, is constant.
+
+	Different from the exiting literature, our model implies that $e$ is non-constant.
 We arrive at this conclusion through the numerical results which will follow, although we can also see that $e$ is non-constant in a simpler setting.
@@
 	\end{equation}
-	It is clear from the above equation that $e$ depends on $\mathbf{c}$.
-However, what is not clear is the extent to which $e$ varies with $\mathbf{c}$ whether it varies enough to make a CES production assumption problematic.
-Furthermore, the above mathematical expression is only valid for $\sigma = 1$ which is close to but not exactly our estimates for $\hat{\sigma}$.
-Whether or not $e$ becomes constant under different values of $\sigma$ is another question.
-Because $e$ does not have a tractable solution when $\sigma \neq 1$, we parameterize and implement our model numerically in order to better study this elasticity.
-
-%	%% OLD
-%	To start, we consider how $\sigma$ affects the substitutability of fossil and renewable energy.
-This is important, because sufficient substitutability between these two technologies is required to transition into greener economy in the future.
-For instance, \citet{Ace2012} provide a model where they argue that, ``When the two	sectors [clean and dirty energy] are substitutable but not sufficiently so, preventing an environmental disaster requires a permanent policy intervention.
-Finally, when the two sectors are complementary, the only way to stave off a disaster is to stop long-run growth." However, note that while our model sets the intertemporal elasticity of substitution for  electricity consumption $\sigma$ to a fixed value, we make no direct assumptions about the elasticity of substitution between different energy technologies.
-Instead, this latter elasticity is indirectly defined by the substitutability of electricity consumption between periods.
-To illustrate this, we parametrize and estimate our model numerically.
+	It is clear from the above equation that $e$ will vary with the cost of the inputs $\mathbf{c}$.
+However, what is not clear from this equation is the extent to which $e$ varies with $\mathbf{c}$ or the link between intermittency and the elasticity $\sigma$.
+Since $e$ does not have a tractable solution when $\sigma \neq 1$, we parameterize and implement our model numerically.
 
@@
 	Next, we normalize the remaining parameters in our model to a MWh basis rather than a per unit basis.
-This is has no effect on the model on a theoretical level but makes it easier to empirically parametrize the cost of electricity production $\mathbf{c}$.
+This is has no effect on the model at the theoretical level but makes it easier to empirically parametrize the cost of electricity production $\mathbf{c}$.
 This is because the cost of electricity generation is generally reported in terms of \$ per unit of electricity, while we originally set $\mathbf{c}$ to represent cost per unit of input.
@@
 
-	We begin by exploring the implied elasticity of substitution between these two technologies. Recall, for any two commodities $i$ and $j$,  the elasticity of substitution $e_{i,j}$ is given by:
+	We use these parameters with the theoretical results in the \hyperref[sec:Model]{Model} section to numerically compute the equilibrium.
+Specifically, given $\boldsymbol{\xi}$ and $\mathbf{c}$, we can compute the equilibrium prices using the firm FOC $\mathbf{p} = \boldsymbol{\xi}^{-1} \mathbf{c}$ (\autoref{eq:firm_foc}).
+Then, knowing the prices, we can compute the price index given by the solution to the consumer's utility maximization problem $P = \sum_t \alpha_t^\sigma p_t^{1-\sigma}$ (\autoref{eq:priceindex}).
+Next, using the consumer's demand function $Z_t = (\alpha_t / p_t)^{\sigma} (I/P)$, we are able to compute the solution for $\mathbf{Z}$ (\autoref{eq:demand}).\footnote{
+	The numerical solutions that will follow are invariant to the parametrization of I.
+This is because CES preferences are homothetic -- the utility function is homogeneous of degree 1.
+Consequently, the implied consumer preferences are invariant to income.
+	} Finally, by definition, we have $\mathbf{Z} \equiv \boldsymbol{\xi}^T \mathbf{X}$ which gives us the solution for $\mathbf{X}$.
+In total, we have the equilibrium quantities $\mathbf{X}, \mathbf{Z}$ and prices $\mathbf{p}$.
+
+	Now, we explore how the elasticity of substitution $e$ between these two technologies, solar and coal, changes with $\sigma$.
+Recall that, for any two technologies $i$ and $j$, the elasticity  of substitution $e_{i,j}$ is given by:
 	$$e_{i,j} = \frac{\partial \log (X_i/ X_j)}{\partial \log (c_j/c_i)}$$
-	where the vector $\mathbf{c}$ captures the cost of electricity production for each technology.
-This relationship is of particular interest, because many applied and theoretical models studying renewable and fossil energy impose a CES production structure between the two (see \citet{Pap}).
-That is, they assume that $e$ is a fixed constant between renewable and fossil energy.
-In our model, this is not the case; while directly deriving the equation for $e_{1,2}$ in our model is analytically intractable, we numerically estimate how it varies with $\log (c_2/c_1)$ and $\sigma$.
+	We compute and plot our numerical estimates of $e_{1, 2}$, the elasticity of substitution between solar and coal power, in \autoref{fig:eosnum}.
+To compute $e_{1,2}$, we numerically differentiate $\log(X_1/X_2)$ with respect to $\log(c_2/c_1)$.
+This is done by first computing the equilibrium quantities $\mathbf{X}$ across a range of cost vectors $\mathbf{c}$; the results, in terms of $\log(X_1/X_2)$ and $\log(c_2/c_1)$, are shown in the first subplot of \autoref{fig:eosnum}.
+We only keep the results for $\mathbf{X}$ that correspond to interior solutions.
+Then,  we numerically estimate $e$ by computing the slope of $\log(X_1/X_2)$ with respect to $\log(c_2/c_1)$; this result is plotted in the lower subplot.
+Since $\log(X_1/X_2)$ is rising at an increasing rate with respect to $\log(c_2/c_1)$, we see that $e$ is positive and increasing.
+We repeat this process with different values of $\sigma$, the IES in the consumer's utility function.
+Specifically, we use our estimate of $\hat{\sigma} = 0.8847\, (0.044)$ and its 95\%  confidence interval $(0.7985, 0.9709)$.
+Overall, this shows how elasticity of substitution between solar and coal, $e_{1,2}$, changes with costs $\mathbf{c}$ and the consumer-side elasticity $\sigma$.
 
@@
 
-	We plot our numerical estimates of $e_{1, 2}$, the elasticity of substitution between solar and coal power, in \autoref{fig:eosnum}.
-We generated these results by computing the optimal quantities of each technology given a range of relative prices $c_2/c_1$.
-Then, we numerically differentiated $\log(X_1/X_2)$ with respect to $\log(c_2/c_1)$ to estimate the elasticity of substitution between solar and coal  $e$.
-This is done by computing the slope of the first subplot in \autoref{fig:eosnum} at each value for $\log(c_2/c_1)$.
-Since $\log(X_1/X_2)$ is rising at an increasing rate with respect to $\log(c_2/c_1)$, we see that $e$ is positive and increasing in the lower subplot.
-We repeat this process with different values of $\sigma$, the IES in the consumer's utility function.
-Specifically, we use our estimate of $\hat{\sigma} = 0.8847\, (0.044)$ and its 95\%  confidence interval $(0.7985, 0.9709)$.
-Finally, after finding the optimal values of our quantities $\mathbf{X}$, we only keep results in our numerical simulation that correspond to interior solutions; that is, we drop edge cases where optimal output or technology  is non-positive.
-
-	The first relationship we see in \autoref{fig:eosnum} is that $e_{1,2}$ varies non-linearly with the relative costs of each technology; in particular, it appears to take on a hockey stick shape.
-It is quite similar to the mathematical expression for $e$ when $\sigma = 1$ given in the earlier (\cref{eq:eosmath}).
-However, it is more easily understood intuitively.
-Specifically, this shape can be understood as the interaction of two effects: intermittency and costs.
+	We see in \autoref{fig:eosnum} is that $e_{1,2}$ varies non-linearly with the relative costs of each technology; in particular, it appears to take on a hockey stick shape.
+This shape can be understood as the interaction of two effects: intermittency and costs.
 The \textit{intermittency effect} is that $e$ falls when our electricity output is highly intermittent.
-The \textit{cost effect} is that $e$ is high costs $(c_1, c_2)$ differ significantly while $e$ is low  when costs are closer together.
-
-	First, we qualify the intermittency effect.
+The \textit{cost effect} is that $e$ is high when costs $(c_1, c_2)$ differ significantly.
+
+	First, we explain the intermittency effect.
 Suppose that a majority of our energy came from solar; this corresponds to the left side of the graph where $\log(c_2/c_1)$ is lower and, as shown in the  first subplot, $\log(X_1/X_2)$ is higher.
@@
 So, it is difficult to replace even more of the coal input with solar.
-Therefore, $e$ is relatively low.
+This reduces the elasticity $e$.
 On the other hand, suppose that a majority of our electricity supply comes from coal; this corresponds to the right side of \autoref{fig:eosnum}.
@@
 That is, making the overall energy output slightly more intermittent when it is already stable does not create as much disutility.
-Hence, the elasticity $e$ is high, since it is easy to substitute between the energy inputs.
+Hence, when the intermittency of output is low, the elasticity $e$ is relatively higher, since it is easier to substitute between the energy inputs.
 In short, as the electricity output becomes less intermittent, $e$ should rise.
@@
 We plot our results in \autoref{fig:eosrange} and find that the elasticity of substitution takes on a u-shape.
-In other words, when intermittency is not a concern as a result of the output parameters $\boldsymbol{\xi}$, we see the cost effect take over.
+In other words, when intermittency is not a concern as a result of the output parameters $\boldsymbol{\xi}$, we see $e$ rise significantly whenever costs differ significantly.
 	} To understand why, suppose that cost efficiencies of two inputs are drastically different.
-Then, independent their intermittency, it is likely that the equilibrium quantities of the inputs are primarily being driven by costs.
-For example, note that consumers want more electricity during peak hours compared to the off-peak.
-They can only achieve this by combining solar and coal, since the electricity output of coal is constant while solar can produce more during peak hours.
-Then, if solar is extremely expensive, this makes it expensive to get relatively more electricity during peak hours than off-peak hours.
+And, note that consumers want more electricity during peak hours compared to the off-peak based on the parametrization of $\boldsymbol{alpha}$.
+This demand profile can only be achieved by combining solar and coal, since the electricity output of coal is constant while solar produces more during peak hours.
+But, if solar is extremely expensive, this makes it expensive to get relatively more electricity during peak hours than off-peak hours.
 Consequently, it may actually be more economical for consumers rely primarily on coal.
@@
 So, $e$ would be high when $\log(c_2/c_1)$ takes extreme values.
-On the other hand, when costs are similar, the cost of generation does not matter for consumers as much as intermittency and other effects; so, we would expect $e$ to be low when $\log(c_2/c_1)$ takes more intermediate values.
+On the other hand, when costs are similar, the cost of generation does not matter for consumers as much as intermittency; so, we would expect $e$ to be low when $\log(c_2/c_1)$ takes more intermediate values.
 
@@
 Finally, the third case is the right-hand side of the subplot where the majority of the electricity comes from coal.
-The intermittency effect here pushes $e$ upwards, and, similarly, the cost effect raises $e$.
+Both the intermittency and cost effect push $e$ upwards.
 So, in this case, we see $e$ being relatively high.
+In total, the two effects cause $e$ to stay flat when the cost ratio, $\log(c_2/c_1)$, is low and then rise sharply when the cost ratio is high.
 
@@
 
-	Additionally, note that the elasticity of substitution $e_{1,2}$ between solar and coal becomes larger and more non-linear as $\sigma$ rises.
-Firstly, the reason why  it becomes larger at all points is fairly intuitive.
-As discussed earlier, when $\sigma$ is higher, consumers care less about smoother consumption and intermittency is less of an issue.
-Consequently, consumers are more willing to accept intermittency in the electricity supply and thus the elasticity $e$ rises.
-Next, to understand the non-linear effect and change in shape, we can appeal to the intermittency effect and the cost effect.
+	Secondly, we can see that the elasticity of substitution $e_{1,2}$ between solar and coal becomes larger  as $\sigma$ rises.
+To  explain why, we first study the magnitude of $e$ in two extreme cases:  $\sigma \to 0$ and $\sigma \to \infty$.
+Specifically, we show that $e$ will be small when $\sigma \to 0$ and $e$ will be large when $\sigma \to \infty$.
+Understanding these two cases helps develop the intuition for why $e$ rises with $\sigma$.
+
+	To start, consider the case where $\sigma \to \infty$.
+Here, electricity consumption in each period is a perfect substitute for electricity consumption in other periods.
+Furthermore, from the equilibrium results, recall that the optimal solution was to only use whatever input had the highest cost-adjusted marginal utility $\sum_t \alpha_t \xi_{i,t} /c_i$.
+This is because $\sigma \to \infty$ causes utility becomes a linear function of electricity output in each period.
+So, consumers only care about their total electricity consumption rather than when they get their electricity.\footnote{ To be precise, they maximize $U = \boldsymbol{\alpha}^T \mathbf{Z}$ which is a weighted sum of electricity output in each period.
+	}  As a result, solutions generally turn into edge cases where we rely entirely on one input -- whichever has the highest cost-adjusted marginal utility.
+Small changes in the cost of input $i$ can cause it to become suboptimal.
+This means that the equilibrium quantity of the input may go from its maximum level to zero.
+Since $e_{12} = \partial \log(X_1/X_2) / \partial \log(c_2/c_1)$ measures the sensitivity of the quantities of each input with respect to prices, we expect $e$ to be extremely large in this case.
+
+	Next, consider the case where $\sigma \to 0$.
+Here, electricity consumption across periods becomes perfect complementary, so  the optimal solution was to use some combination of inputs that make electricity output as smooth as possible.
+This is because, when $\sigma \to 0$, utility takes on a Leontiff functional form: $\min_t \, Z_t/\alpha_t$.
+In the context of our parametrization, this would  imply that consumers want a relatively fixed ratio of peak and off-peak consumption.
+We know that coal offers a strictly smooth output while solar offers more during peak hours.
+Hence, the equilibrium would be one which primarily uses coal and then a small amount of solar to account for the fact that consumers demand slightly more electricity during peak hours.
+Furthermore, even if costs change, the optimal solution would still require the consumer to maintain a relatively fixed ratio of peak and off-peak electricity cosnumption to maximize utility; this then requires maintaining a fixed ratio of solar and coal.
+Consequently, changes in the cost of solar and coal would do little to affect the equilibrium ratio of inputs.
+Thus, since $e$ measures how sensitive the two inputs are with respect to their costs, it would be close to zero in this case.
+
+	These two extreme cases illustrate the link between $e$ and $\sigma$.
+When $\sigma$ rises, consumers care less about smoother consumption.
+Consequently, consumers are more willing to accept intermittency in the electricity supply.
+This causes the implicit demand for inputs to become relatively less sensitive to intermittency and relatively more sensitive to their costs.
+As a result, the substitutability of intermittent and consistent technologies rises; so, we see $e$ increase.
+
+	Thirdly, we can see that the higher levels of $\sigma$ cause $e$ to change shape.
+To understand why, we can appeal to the intermittency effect and the cost effect.
 Note that $\sigma$ rising makes intermittency matter less; this diminishes the intermittency effect.
@@
 
-	We can tie these results in with the more mathematical discussion of the model's equilibrium from earlier.
-Specifically, recall that when $\sigma \to \infty$, utility becomes linear and the equilibrium tends towards whatever inputs maximize total electricity output.
-On the other hand, when $\sigma \to 0$, utility becomes Leontiff and consumers want to completely smooth their electricity consumption.
-These two extreme cases can help us understand how $e$ changes with $\sigma$.
-
-	In the first case, when $\sigma \to \infty$, recall that the optimal solution was to only use whatever input had the highest cost-adjusted marginal utility $\sum_t \alpha_t \xi_{i,t} /c_i$.
-The intuition here is that a very high $\sigma$ causes electricity in each period to become a perfect substitute for electricity in other periods; this can be seen by the fact that utility becomes a linear function of electricity output $\mathbf{Z}$ in each period.
-So, consumers only care about their total electricity consumption rather than when they get their electricity.
-As a result, all solutions turn into edge cases.
-Consequently, small changes in the cost of input $i$ can cause its equilibrium value to go from its maximum level to zero.
-Since $e_{12} = \partial \log(X_1/X_2) / \partial \log(c_2/c_1)$, we expect $e$ to be extremely large in this case since quantities are very sensitive to prices.
-
-	In the second case, when $\sigma \to 0$, the optimal solution was to figure out some combination of resources that make consumption as smooth as possible.
-Specifically, the utility was given by $\min_t \, Z_t/\alpha_t$.
-Therefore, consumers want a relatively fixed ratio of peak and off-peak consumption.
-Here, we know that coal offers a strictly smooth output while solar offers more during peak hours.
-Hence, the equilibrium would be one which primarily uses coal and then a small amount of solar to account for the fact that consumers demand slightly more electricity during peak hours.
-Furthermore, even if costs change, the optimal solution would still require the consumer to maintain a relatively fixed ratio of peak and off-peak electricity cosnumption to maximize utility; this then requires maintaining a fixed ratio of solar and coal.
-Consequently, changes in the cost of solar and coal would do little to affect the equilibrium ratio of inputs.
-Thus, since $e$ measures how sensitive the two inputs are with respect to their costs, it would be extremely small in this case.
-
 	To summarize, $e$ depends on two factors, cost and intermittency, while $\sigma$ affects the importance of intermittency.
@@
 These two effects combine to give $e$ the shape we see in \autoref{fig:eosnum}.
-Furthermore, at lower levels of $\sigma$, consumers case more about smoother electricity consumption and thus intermittency matters more.
-So, lower $\sigma$ means the intermittency effect is larger and $e$ is smaller overall.
-Additionally, when the intermittency effect is large, we see $e$ become more linear, while, when the intermittency effect is small, $e$ becomes more u-shaped as the cost effect dominates.
-Overall, these numerical results for $e$ are consistent with the analytic results and intuition discussed earlier.
+Furthermore, at higher levels of $\sigma$, consumers care less about smoother electricity consumption and thus intermittency matters less.
+So, higher $\sigma$ diminishes the magnitude of the intermittency effect and makes  $e$ is larger overall.
+Additionally, a smaller intermittency effect causes  $e$ to take on more of a u-shape as the cost effect dominates.
+Overall, these numerical results for $e$ are consistent with the analytic results and intuition from earlier.
 
@@
 	\begin{center}
-		[INSERT Figure 5: The VES Approximation of the Elasticity of Substitution between Solar and Coal]
+		[INSERT Figure 4: The VES Approximation of the Elasticity of Substitution between Solar and Coal]
 	\end{center}
@@
 
+	\subsection{Robustness}
+
+	As a robustness check, we reproduce the estimates of $e$ shown in \autoref{fig:eosnum} across a larger range of values for $\sigma$.
+This allows us to  evaluate the extent to which our results for $e$ are driven by our estimate of $\sigma$.
+Specifically, we consider parametrizations of $\sigma$ closer to estimates from the literature.
+\citet{Herriges} and \citet{KS1994} estimated $\sigma$ to be between 0.1 and 0.3, while estimates by \citet{Schwarz} were between $0.02$ and $0.04$.
+We estimate $e$ using values of $\sigma$ around these values and plot our results in  \autoref{fig:eosrobust}.
+
+	\vspace{0.15in}
+	\begin{center}
+		[INSERT Figure 6: The Elasticity of Substitution Between between Solar and Coal \newline  (Robustness Check)]
+	\end{center}
+	\vspace{0.15in}
+
+	As expected, we find that lower values of $\sigma$ result in lower values of $e$.
+The estimate for $e$ near the parameterized value of $\mathbf{c}$ is  $10.29$ when $\sigma = 0.8847$ (our estimate) and $8.93$ when $\sigma = 0.1$.
+Furthermore, the difference between the implied elasticities $e$ when $\sigma = 0.1$ and when $\sigma = 0.01$ is fairly small.
+On the other hand, we see that the elasticity $e$ is larger when $\sigma$ is closer to our estimate.
+Furthermore, the difference between the results implied by our estimate of $\sigma$ and that of the literature gets  bigger when solar is relatively cheaper (left-hand side of the plot); this is because of the intermittency effect as discussed earlier.
+
+	Although these differences appear to be large, they do not negatively affect the implications of our results.
+Thus far, we have discussed how intermittency complicates environmental policy.
+If consumers did not care about intermittency, then these complications would be less relevant in terms of consumer welfare.
+However,  the literature's estimates of $\sigma$ are lower than our own; in other words, the literature finds that consumers care strongly about smoothing their electricity consumption.
+Consequently, if one puts more weight on the literature's estimates, then intermittency is even more significant than our results imply.
+That is, when $\sigma$ is lower, it is harder to substitute between intermittent renewable and reliable fossil energy; this is shown in \autoref{fig:eosrobust} where $e$ is lower at all relative prices $\log(c_2/c_1)$ when $\sigma$ is lower.
+As a result, the distributional consequences of energy policy to be more pronounced and makes research into batteries more important.
+Hence, our results are robust to the literature's estimates of $\sigma$ which increase the importance of intermittency.
+
 	\section{Conclusion}
@@
 	\section{Appendix A: Supplementary Proofs}
+	\label{sec:appendixa}
 
@@
 	\begin{center}
-		[INSERT Figure 6: The Elasticity of Substitution Between Two  Minimally Intermittent Technologies]
+		[INSERT Figure 7: The Elasticity of Substitution Between Two  Minimally Intermittent Technologies]
 	\end{center}
@@
 	\begin{center}
-		[INSERT Figure 7: The VES Approximation of the Elasticity of Substitution between Highly Intermittent Solar and Coal]
+		[INSERT Figure 8: The VES Approximation of the Elasticity of Substitution between Highly Intermittent Solar and Coal]
 	\end{center}
@@
 Furthermore, we set the parameter for the intertemporal elasticity of substitution for electricity consumption equal to our estimate $\hat{\sigma} = 0.8847$.
-In order to generate these numerical results, we first found the optimal quantities of $\mathbf{X}$ over a range of prices $c_1^* \in (0.9\, c_1, 2 \,c_1)$.
+In order to generate these numerical results, we first found the optimal quantities of $\mathbf{X}$ over a range of prices $c_1^* \in (0.5\, c_1, 2 \,c_1)$.
 Then, we obtained estimates of the elasticity of substitution by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1, c_2)$.
@@
 		\captionsetup{format=centerproper}
+		\caption{The Elasticity of Substitution Between between Solar and Coal \newline  (Robustness Check) } 
+		\label{fig:eosrobust}
+		\footnotesize
+		\vspace{-1em}
+		\begin{tabular}{@{\extracolsep{0em}}c}
+			\includegraphics[width=1\linewidth]{../figures/fig_elasticity_robust} \\
+			\multicolumn{1}{@{\hspace{0.2in}}p{5.9in}@{}}{ \textit{Note: } This figure is identical to \autoref{fig:eosnum}, but it considers a large range of values for $\sigma$.
+Technology 1 is coal and technology 2 is solar.
+The purple, dash-dots line represents a linear approximation of $e_{1,2}$ for $\sigma = 0.8847$ with a fixed intercept of 1.
+These results were obtained using the following parameters: $\alpha_t = 0.6$, $\alpha_s = 0.4$, $\xi_1 = (1, \, 1)$, $\xi_2 = (1, \, 0.1)$, $c_1 = 104.3$, $c_2 = 60$.
+Furthermore, we set the parameter for the intertemporal elasticity of substitution for electricity consumption equal to our estimate $\hat{\sigma} = 0.8847$.
+In order to generate these numerical results, we first found the optimal quantities of $\mathbf{X}$ over a range of prices $c_1^* \in (0.5\, c_1, 2 \,c_1)$.
+Then, we obtained estimates of the elasticity of substitution by numerically differentiating $\ln(X_1/X_2)$ with respect to $-\ln(c_1, c_2)$.
+}     \\
+		\end{tabular}
+	\end{figure}
+	\clearpage
+
+	\begin{figure}[h!]
+		\captionsetup{format=centerproper}
 		\caption{The Elasticity of Substitution Between Two \newline  Minimally Intermittent Technologies} 

### 2019-12-31 documents/revision.tex
Revise paper
- update abstract
- clean up intro
- add equation numbers and appendix equation numbering
- update robustness section
- fix results discussion
- merge results tables
- minor changes to appendix

@@
 \newtheorem{lemma}{Lemma}
+
 \newenvironment{proof}[1][Proof]{\noindent\textbf{#1:} }{\ \rule{0.5em}{0.5em}}
@@
 The economic value of a electricity generation technology is given by integrating its production profile with the market price of electricity.
-We parametrize this model empirically and generate numerical results.
+We estimate the intertemporal elasticity of substitution for electricity consumption,  parameterize the model empirically, and generate numerical results.
 The introduction of intermittency results in a non-constant elasticity of substitution between renewable and fossil energy.
@@
 	In this paper, we develop a partial equilibrium model of the electricity sector that takes into account intermittent generation.
-Specifically, the electricity sector consists of a representative firm that chooses and builds capacity from a set of electricity-generating technologies to maximize profit; some of these technologies are intermittent while others have constant output.
+Specifically, the electricity sector consists of a representative firm that chooses and builds capacity from a set of electricity-generating technologies to maximize profit; some of these technologies are intermittent while others are consistent.
 Then, we consider a representative consumer who purchases varying quantities of electricity in each period in order to maximize utility.
@@
 Secondly, our model captures the imperfect substitutability of intermittent and reliable energy technologies  by modeling consumers with a preference for smooth electricity consumption which they signal through prices.
-When firms respond to this signal and maximize profit, the equilibrium result  is that the intermittency of certain renewables interferes with their ability to perfectly substitute for reliable energy technologies.
-In other words, we directly link the substitutability of energy technologies with their intermittency.
+When firms respond to this signal and maximize profit, the equilibrium result  is that the intermittency of certain renewables interferes with their ability to perfectly substitute for reliable energy technologies; that is, the substitutability of energy technologies is directly linked with their intermittency.
 	This contrasts with alternative approaches that model electricity as a homogenous good produced according to  a CES function of electricity-generating technologies; such approaches model imperfect substitutability on the supply-side to implicitly capture the effects of intermittency.
@@
 	The remainder of the paper proceeds as follows.
-The Model section states our model and its equilibrium; we also provide a discussion of the (consumer side) IES parameter and how it relates to the substitutability of intermittent and reliable technologies on a theoretical level.
-The Empirical Methodology section details how we estimate the IES parameter along with a description of our data.
-This is followed by the Results section where we discuss our estimates.
-We then empirically parameterize, numerically implement, and study our model further in the Discussion.
+The Model section states the consumer and firm problems and the resulting equilibrium.
+We also provide a discussion of the (consumer side) IES parameter and how it affects the optimal choice of electricity-generating inputs.
+Then, using the analytic results from the market equilibrium, we derive estimable equations for the IES parameter in the Empirical Methodology section.
+We estimate these equations using 2SLS in the Results section.
+In the Discussion, we use our estimate for the IES parameter to empirically parameterize and numerically implement our model; we also elaborate on the link between the IES parameter, intermittency, and the substitutability of renewable and fossil energy.
 Finally, in the Conclusion, we summarize our model's policy implications and offer suggestions for future models of intermittency.
@@
 	\begin{equation}
-	U = \left( \sum_t \alpha_t Z_t^\phi  \right)^{1/\phi} \quad \phi < 1
+	U = \left( \sum_t \alpha_t Z_t^\phi  \right)^{1/\phi} \qquad \phi < 1
 	\end{equation}
@@
 To simplify notation, we have
-	\begin{align*}
+	\begin{align}
 	\mathbf{X} \equiv \begin{pmatrix}
@@
 	\end{pmatrix} 
-	\end{align*}
+	\end{align}
 	where we have $n$ technologies, $m$ periods, and $\mathbf{Z} \equiv \boldsymbol{\xi}^T \mathbf{X}$.
@@
 Additionally, this allows us to assume that producers cannot modify the quantity of the technologies they deploy.
-And, thirdly, for certain technologies, this time frame is short enough to assume that $\xi$ is exogenous; that is, technologies like coal power cannot significantly modify their output within a day, so $\boldsymbol{\xi}$ can be treated as a given set of constants.
+And, thirdly, for certain technologies, this time frame is short enough to assume that $\boldsymbol{\xi}$ is exogenous; that is, technologies like coal power cannot significantly modify their output within a day, so $\boldsymbol{\xi}$ can be treated as a given set of constants.
 These latter two assumptions, that $\mathbf{X}$ cannot change over time and that $\boldsymbol{\xi}$ is exogenous, are important for parsimony, because they prevent more complicated dynamics from entering our model.
@@
 Additionally, we further require that the output per unit of each technology is unique and non-negative in each period; in other words, the output per unit of one technology is not a linear combination of those of the other technologies in our set.
-This then implies that $\xi$ is of full rank and therefore invertible.
+This then implies that $\boldsymbol{\xi}$ is of full rank and therefore invertible.
 Now, maximizing profit, we find the first order condition:
@@
 	\end{lemma}
+
 	The first condition is on cost efficiency and is intuitive.
@@
 Hence, ensuring that we have accurate estimates of $\sigma$ is important for understanding how consumers decide between fossil and renewable energy.
-The other parameters in our model, $c$,  $\xi$, and $\boldsymbol{\alpha}$, are of secondary interest, since they are easier to obtain directly.
+The other parameters in our model, $\mathbf{c}$,  $\boldsymbol{\xi}$, and $\boldsymbol{\alpha}$, are of secondary interest, since they are easier to obtain directly.
 
 	Recall the demand equation from earlier
-	$$Z_t = \left(\frac{\alpha_t}{p_t} \right)^\sigma \frac{I}{P}$$
+	\begin{equation}
+	Z_t = \left(\frac{\alpha_t}{p_t} \right)^\sigma \frac{I}{P}
+	\end{equation}
 	where $P$ is the price index and $I$ is income.
@@
 	In order to estimate this $\sigma$, we further modify this equation. 
-	Firstly, note that we cannot observe the demand shifter $\alpha_{t,i}$ directly, so we must replace the $\boldsymbol{\alpha}$ terms with a set of controls that may be responsible for shifts in demand.
+	Firstly, note that we cannot observe the demand shifter $\alpha_{t,i}$ directly, so we must replace the $\alpha$ terms with a set of controls that may be responsible for shifts in demand.
 So, still in general terms, our regression equation is now
@@
 	\begin{align*}
-	\ln (Z_{ t, i} / Z_{ s, i}) &= \beta \ln (P_{t,i} / P_{s,i}) + \xi \ln (C_{t,i} / C_{s,i}) + v_{i}
+	\ln (Z_{ t, i} / Z_{ s, i}) &= \beta \ln (P_{t,i} / P_{s,i}) + \zeta \ln (C_{t,i} / C_{s,i}) + v_{i}
 	\end{align*}
@@
 	\begin{equation}
-	\ln (P_{t,i} / P_{s,i}) = \left( \beta + \sigma \right)^{-1} \left( \gamma_{t,i} A_{t,i} + \gamma_{s,i} A_{s,i} + \eta \Delta_{t,s} - \xi \ln (C_{t,i} / C_{s,i}) + u_{i} - v_i \right)  
+	\ln (P_{t,i} / P_{s,i}) = \left( \beta + \sigma \right)^{-1} \left( \gamma_{t,i} A_{t,i} + \gamma_{s,i} A_{s,i} + \eta \Delta_{t,s} - \zeta \ln (C_{t,i} / C_{s,i}) + u_{i} - v_i \right)  
 	\end{equation}
@@
 So, overall, we have:
-	\begin{align}
+	\begin{align} \label{eq:pariv1}
 	\ln (Z_{ t, i} / Z_{ s, i}) &= -\sigma \ln (P_{t,i} / P_{s,i}) +  f \left( A_{t,i}, A_{s,i}, \Delta_{t,s} \right) + u_i \\
-	\ln (Z_{ t, i} / Z_{ s, i}) &= \beta \ln (P_{t,i} / P_{s,i}) + g \left( \ln (C_{t,i} / C_{s,i})  \right) + v_{i}
+	\ln (Z_{ t, i} / Z_{ s, i}) &= \beta \ln (P_{t,i} / P_{s,i}) + g \left( \ln (C_{t,i} / C_{s,i})  \right) + v_{i} \label{eq:pariv2}
 	\end{align}
@@
 
-	Based on the OLS results reported in \autoref{table:ols} we estimate the intertemporal elasticity of substitution for electricity consumption $\hat{\sigma}  = 1.305$ ($|t| > 24$) when accounting for all degree day covariates and state fixed effects.
+	Based on the OLS results reported in \autoref{table:regresults}, we find that the intertemporal elasticity of substitution for electricity consumption is $\hat{\sigma}  = 1.305$ ($|t| > 24$) when accounting for all degree day covariates and state fixed effects.
 Additionally, we find that accounting for cooling and heating degree days captures a large amount of variation in demand for electricity; in the fixed effects regressions, adding these controls raises adjusted $R^2$ from 8.5\% to 51.8\%.
@@
 	\begin{center}
-		[INSERT Table 2: OLS Regression Results]
+		[INSERT Table 2: OLS and 2SLS Regression Results]
 	\end{center}
@@
 
-	To account for endogeneity in the OLS results, we provide results for our IV specification in \autoref{table:iv}.
+	To account for endogeneity in the OLS results, we also provide results for our IV specification in \autoref{table:regresults}.
 Here, we find a much larger estimate of $\hat{\sigma}  = 5.818$ ($|t| > 11.1$) when considering all covariates and fixed effects.
@@
 Additionally, in contrast with the OLS results, we find a much larger estimate for the coefficient on $\Delta_{t,s}$ of $0.003$; this implies that electricity consumption seems to rise by about 3.65\% per year.
-So, overall, our IV results suggest much higher estimates of $\sigma$.
+Overall, our IV results suggest much higher estimates of $\sigma$.
 
@@
 	\begin{center}
-		[INSERT Table 3: IV (2SLS) Regression Results]
+		[INSERT Table 3: Partially Linear IV Regression Results]
 	\end{center}
@@
 
-	Finally, we control for nonlinear effects using a partially linear IV regression reported in \autoref{table:pariv}.
+	In \autoref{table:pariv}, we report the results for our partially linear IV regression  which controls for non-linear effects.
 Here, we find much smaller results than 2SLS when controlling for all possible covariates.
@@
 That is, fit (3) is likely the most appropriate specification.
-Additionally, all of these estimates are significantly different from the 2SLS results which suggests that the 2SLS results are not robust.
-In other words, our controls and instrument likely have non-linear effects on price and quantity which cannot be captured by linear models.
-Specifically, we are likely to see nonlinear effects from to temperature which is proxied by CDDs and HDDs in our model.
-The intuition here is that the amount of electricity needed to maintain room temperature varies nonlinearly with the outside temperature, so the linear structure of our OLS regression would likely be invalid.
-Alternatively, there is also no reason to believe that logged electricity prices would vary linearly with logged coal prices.
-Either way, there would be a functional form problem with the standard linear regressions.
+
+	Additionally, all of the partially linear IV estimates are significantly different from the 2SLS results which suggests that the 2SLS results are inconsistent.
+This may be because our controls and instrument have non-linear effects on price and quantity which cannot be captured by linear models.
+Specifically, we are likely to see  temperature, which is proxied by CDDs and HDDs, to have non-linear effects on electricity demand.
+The intuition here is that the amount of electricity needed to maintain room temperature varies nonlinearly with the outside temperature.
+So, using a linear functional form in the OLS and 2SLS regressions would produce inconsistent estimates.
+Alternatively, it may also be possible that the instrument, coal prices, affects electricity prices  non-linearly; this would also result in the 2SLS regression being inconsistent.
+On the other hand, the partially linear regression allows the control and instrumental  variables to have non-linear effects in both the supply and demand equation; this is shown \autoref{eq:pariv1} and \autoref{eq:pariv2}.
+If the true functional form was linear for both the controls and instruments, we would expect the partially linear results to be closer to the 2SLS results.
+However, because the two types of regressions give significantly different results, the partially linear regression is more reliable since it is robust to non-linearities that 2SLS cannot capture.
 So, we believe that our third semiparametric fit, $\hat{\sigma} = 0.8847$, is the most robust estimate of $\sigma$.
-
-	\vspace{0.15in}
-	\begin{center}
-		[INSERT Table 4: Partially Linear IV Regression Results]
-	\end{center}
-	\vspace{0.15in}
 
@@
 	} To understand why, suppose that cost efficiencies of two inputs are drastically different.
-And, note that consumers want more electricity during peak hours compared to the off-peak based on the parametrization of $\boldsymbol{alpha}$.
+And, note that consumers want more electricity during peak hours compared to the off-peak based on the parametrization of $\boldsymbol{\alpha}$.
 This demand profile can only be achieved by combining solar and coal, since the electricity output of coal is constant while solar produces more during peak hours.
@@
 CGEs, specifically ones designed to study energy and environmental policy, tend to assume a CES relationship between generation technologies and treat electricity as a homogeneous good.
-On the other hand, our representation of the energy sector makes more realistic assumptions and directly models the source of imperfect substitutability between generation technologies -- intermittency.
+On the other hand, our representation of the energy sector directly models the source of imperfect substitutability between generation technologies -- intermittency.
 Consequently, embedding our model within a CGE would improve its predictive accuracy by giving it more realistic microfoundations.
@@
 	$$\gamma > 0, \quad \omega > 0, \quad0 < \delta < 1, \quad 0 \leq \delta \rho \leq 1 , \quad (X_2/X_1) >  -\beta $$
-	where $\omega, \delta, \rho$, and $\gamma$ are parameters.
-Additionally, $\mathbf{Z}$ is the output, $X_1$ and $X_2$ are the inputs, and $e$ is the elasticity of substitution between $X_1$ and $X_2$.
-In our case, we can think of $\mathbf{Z}$ as electricity output while $X_1$ and $X_2$ represent dirty and clean technology.
+	where $\omega, \delta, \rho$, and $\gamma$ are parameters, $Z$ is the output, $X_1$ and $X_2$ are the inputs, and $e$ is the elasticity of substitution between $X_1$ and $X_2$.
+In the context of an electricity sector, we can think of $Z$ as electricity output while $X_1$ and $X_2$ represent dirty and clean inputs.
 Note that $e$ is a linear function of $X_1/X_2$; this relationship allows a VES function to approximate the effects of intermittency.
@@
 \citet{Herriges} and \citet{KS1994} estimated $\sigma$ to be between 0.1 and 0.3, while estimates by \citet{Schwarz} were between $0.02$ and $0.04$.
+Additionally, we consider $\sigma = 1$ and $\sigma = 2$ which is closer to our OLS and 2SLS estimates.
 We estimate $e$ using values of $\sigma$ around these values and plot our results in  \autoref{fig:eosrobust}.
@@
 
-	As expected, we find that lower values of $\sigma$ result in lower values of $e$.
+	Using values of $\sigma$ closer to our OLS and 2SLS estimates cause $e$ to be much higher.
+This is because the OLS and 2SLS results have $\sigma$ higher than our partially linear specification.
+This suggests that intermittency is much less of a problem for substitutability if we parameterize our model using the 2SLS results.
+However, as argued in the Results section, the partially linear model is robust to functional form misspecifications and non-linearities while 2SLS is not.
+
+	When using the literature's estimates of $\sigma$, which are much lower than ours, we find  lower values of  $e$.
 The estimate for $e$ near the parameterized value of $\mathbf{c}$ is  $10.29$ when $\sigma = 0.8847$ (our estimate) and $8.93$ when $\sigma = 0.1$.
-Furthermore, the difference between the implied elasticities $e$ when $\sigma = 0.1$ and when $\sigma = 0.01$ is fairly small.
-On the other hand, we see that the elasticity $e$ is larger when $\sigma$ is closer to our estimate.
+Furthermore, the difference between the implied elasticity $e$ when $\sigma = 0.1$ and when $\sigma = 0.01$ is fairly small.
 Furthermore, the difference between the results implied by our estimate of $\sigma$ and that of the literature gets  bigger when solar is relatively cheaper (left-hand side of the plot); this is because of the intermittency effect as discussed earlier.
 
-	Although these differences appear to be large, they do not negatively affect the implications of our results.
+	Although these differences from using the literature's estimates appear to be large, they do not negatively affect the implications of our results.
 Thus far, we have discussed how intermittency complicates environmental policy.
-If consumers did not care about intermittency, then these complications would be less relevant in terms of consumer welfare.
-However,  the literature's estimates of $\sigma$ are lower than our own; in other words, the literature finds that consumers care strongly about smoothing their electricity consumption.
-Consequently, if one puts more weight on the literature's estimates, then intermittency is even more significant than our results imply.
-That is, when $\sigma$ is lower, it is harder to substitute between intermittent renewable and reliable fossil energy; this is shown in \autoref{fig:eosrobust} where $e$ is lower at all relative prices $\log(c_2/c_1)$ when $\sigma$ is lower.
-As a result, the distributional consequences of energy policy to be more pronounced and makes research into batteries more important.
-Hence, our results are robust to the literature's estimates of $\sigma$ which increase the importance of intermittency.
+The literature's estimates of $\sigma$ are lower than our own; in other words, the literature finds that consumers care strongly about smoothing their electricity consumption.
+Consequently, if one puts more weight on the literature's estimates, then intermittency is more important than we have argued with our results.
+That is, when $\sigma$ is lower, it is harder to substitute between intermittent renewable and reliable fossil energy; this is shown in \autoref{fig:eosrobust} where $e$ is lower at all relative prices $\log(c_2/c_1)$.
+As a result, using the literature's estimates of $\sigma$ makes the distributional consequences of energy policy more pronounced and research into batteries more important.
+Hence, the policy implications from our paper are strengthened when using the literature's estimates of $\sigma$.
 
@@
 	In this paper, we have offered a framework for understanding the economics of intermittent renewable energy that bears in mind the critique offered by \citet{Joskow2011}.
-That is, our model evaluates the economic feasibility of a technology by integrating its production profile with the market value of electricity in equilibrium.
-Moreover, this equilibrium is reached using a fairly realistic model of consumer behavior.
+That is, our model evaluates the economic value of a generation technology by integrating its production profile with the market value of electricity.
+Moreover, consumers in our model treat electricity as a heterogeneous good differentiated by time.
 The empirical parameterization of our model and its numerical results suggest that the elasticity of substitution between renewable and fossil energy is non-constant.
@@
 	\label{sec:appendixa}
+
+	\renewcommand{\theequation}{\arabic{equation}a}
 
@@
 	\end{align}
-	Furthermore, we derive restrictions on the parameters $\xi$ and $c$ by assuming $Z, X > 0$.
-These restrictions are detailed in \autoref{tab:paramrest}.
-There are two possible sets of symmetrical restrictions.
+	We now derive the restrictions on the parameters $\boldsymbol{\xi}$ and $\mathbf{c}$ that ensure $\mathbf{Z}, \mathbf{X} > 0$.
+These restrictions are given by Lemma 1 from the Model Equilibrium section:
+
+	\hfill
+
+	\noindent	\textbf{Lemma 1A:} \textit{ Assume that, for all technologies $i$ and periods $t$, we have $\xi_{i,t} > 0 \, , \alpha_t > 0 \, ,$ and $ c_i > 0$.
+Then, for technology $j$ to be economical, there need to exist a period $s$ where the following three conditions are met:
+		\begin{itemize}
+			\item $\xi_{j,s}/c_j > \xi_{i,s}/c_i$ for all $i$
+			\item $\xi_{j,s}/\xi_{j,t} >  \xi_{i,s}/\xi_{i,t} $ where $i \neq j$ and $t \neq s$
+			\item Period $s$ demand needs to be sufficiently large, i.e., $\alpha_s$ is large enough
+		\end{itemize}
+	}
+
+	In order to have $X_1, X_2 > 0$, we need to have the conditions of this lemma hold for both technologies.
+This is equivalent to  requiring one of two possible sets of symmetrical restrictions on $\boldsymbol{\xi}$ and $\mathbf{c}$ which are detailed in \autoref{tab:paramrest}.
 The first set, Case 1, assumes that technology 2 is more cost effective in period $t$, while the second set, Case 2, assumes that technology 1 is more cost effective in period $t$.
@@
 
-	\hfill\\
 	\begin{proof}
@@
 		Note that the latter two restrictions can be derived from the former two.
-Additionally, we implicitly assume that we have $\xi > 0$.
-However, this is not necessary assumption, since $\xi$ invertible only requires $\xi_{1t} \xi_{2s} > 0$ or $\xi_{1s} \xi_{2t} > 0$.
+Additionally, we implicitly assume that we have $\boldsymbol{\xi} > 0$.
+However, this is not necessary assumption, since $\boldsymbol{\xi}$ invertible only requires $\xi_{1t} \xi_{2s} > 0$ or $\xi_{1s} \xi_{2t} > 0$.
 Instead, we may leave the latter two inequalities in the form $ \xi_{1s}\xi_{2t} > \xi_{2s}\xi_{1t}$ which remains valid when values of $\xi$ are equal to $0$.
@@
 		To double check, note that combining the inequalities from $X_1>0$ and $X_2 > 0$ leads to $\xi_{2s}/\xi_{2t} < \xi_{1s}/\xi_{1t}$.
-This is precisely the earlier result obtained from $Z > 0$.
-Again, it is  important to note that we assume $\xi > 0$ for to simplify the inequalities of $X_1 > 0$ and $X_2 > 0$ .
+This is precisely the earlier result obtained from $\mathbf{Z} > 0$.
+Again, it is  important to note that we assume $\boldsymbol{\xi} > 0$ for to simplify the inequalities of $X_1 > 0$ and $X_2 > 0$ .
 Otherwise, we may leave the inequalities in their original forms and they are still valid when  $\xi_{1t} \xi_{2s} > 0$ or $\xi_{1s} \xi_{2t} > 0$.
@@
 Both these terms are then multiplied by the share parameter of the utility function for their respective time periods.
-Furthermore, note that $\alpha_t$ $(\alpha_s)$ is the elasticity of utility with respect to $Z_t$ $(Z_t)$.
+Furthermore, note that $\alpha_t$ $(\alpha_s)$ is the elasticity of utility with respect to $Z_t$ $(Z_s)$.
 Hence, in total, the mixed efficiency restrictions relate the relative cost efficiencies of each technology with their output efficiency and the demand for energy.
@@
 Likewise, we see symmetrical results for the output with respect to the cost and output efficiency of technology 2; improvements in the efficiency of $X_2$ result in greater output in $Z_t$ and smaller output in $Z_s$.
-
-	\hfill \\
+In total, we have Proposition 1:
+
+	\hfill
+
+	\noindent	\textbf{Proposition 1A:} \textit{Suppose that the conditions of Lemma 1 hold for each technology, so we are not in an edge case. Then, 
+		\begin{itemize}
+			\item The equilibrium quantity of a technology is increasing with its output and decreasing with its cost; at the same time, it is decreasing with the output of other technologies and increasing with the cost of other technologies.
+			\item Also, suppose that some technology $i$ is the most cost effective in period $t$.
+Then, its equilibrium quantity is increasing with respect to the demand parameter $\alpha_t$ and decreasing with respect to the demand parameters in other periods.
+			\item Furthermore, again assuming technology $i$ is the most cost effective in period $t$, the comparative statics of $Z_t$ and $X_i$ are equivalent. 
+	\end{itemize}}
+
+	\hfill
+
 	\begin{proof}
@@
 
-	We derive the elasticity of substitution in this two-period, two-technology setting. By definition, the elasticity of substitution is 
-	$$e_{12} \equiv \frac{\partial \log(X_1/X_2)}{\partial \log(c_2/c_1)} = \frac{\partial X_1/X_2 }{ \partial (c_2/c_1)} \cdot \frac{c_2/c_1}{X_1/X_2} = \frac{\partial X_1/X_2}{ \partial  c_2}  \cdot \frac{\partial c_2}{\partial (c_2/c_1)} \cdot \frac{c_2/c_1}{X_1/X_2} $$
+	We derive the elasticity of substitution between technologies in this two-period, two-technology setting. By definition, the elasticity of substitution is 
+	\begin{equation}
+	e_{12} \equiv \frac{\partial \log(X_1/X_2)}{\partial \log(c_2/c_1)} = \frac{\partial X_1/X_2 }{ \partial (c_2/c_1)} \cdot \frac{c_2/c_1}{X_1/X_2} = \frac{\partial X_1/X_2}{ \partial  c_2}  \cdot \frac{\partial c_2}{\partial (c_2/c_1)} \cdot \frac{c_2/c_1}{X_1/X_2}
+	\end{equation}
 	Note that
-	\begin{align*}
+	\begin{align}
 		X_1/X_2 &= -\frac{\alpha _{s}\,c_{1}\,\xi _{\mathrm{2s}}\,\xi _{\mathrm{2t}}-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}+\alpha _{t}\,c_{1}\,\xi _{\mathrm{2s}}\,\xi _{\mathrm{2t}}-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}}{\alpha _{s}\,c_{1}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{1t}}+\alpha _{t}\,c_{1}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{1t}}} \\
@@
 		\frac{\partial c_2}{\partial (c_2/c_1)} &= \left( \frac{\partial (c_2/c_1)}{\partial c_2} \right)^{-1} = c_1
-	\end{align*}
+	\end{align}
 	Thus, the elasticity of substitution is
-	$$
+	\begin{equation}
 	e_{12} = 
@@
 	}
-	$$
+	\end{equation}
 	The mixed efficiency restrictions (either case) from \autoref{tab:paramrest} imply that $(\alpha _{s}\,c_{1}\,\xi _{\mathrm{2s}}\,\xi _{\mathrm{2t}}-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}+\alpha _{t}\,c_{1}\,\xi _{\mathrm{2s}}\,\xi _{\mathrm{2t}}-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}})$ and $(\alpha _{s}\,c_{1}\,\xi _{\mathrm{1t}}\,\xi _{\mathrm{2s}}-\alpha _{s}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{1t}}+\alpha _{t}\,c_{1}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{2t}}-\alpha _{t}\,c_{2}\,\xi _{\mathrm{1s}}\,\xi _{\mathrm{1t}})$ have opposite signs.
@@
 
-	Since $\sigma = 1/(1-\phi)$, we have $\phi \to 1$ which implies
-	$$  U = \left( \sum_t \alpha_t Z_t^\phi  \right)^{1/\phi} \to  \sum_t \alpha_t Z_t = \boldsymbol{\alpha}^T \boldsymbol{\xi}^T \mathbf{X}$$
+	Recall that utility is given by 
+	\begin{equation}
+	U = \left( \sum_t \alpha_t Z_t^\phi  \right)^{1/\phi}
+	\end{equation}
+	Since $\sigma = 1/(1-\phi)$, we have $\phi \to 1$ which implies that the utility function becomes
+	\begin{equation}
+	U= \sum_t \alpha_t Z_t = \boldsymbol{\alpha}^T \boldsymbol{\xi}^T \mathbf{X}
+	\end{equation}
 	Utility  here is simply a weighted sum of total electricity consumption. In other words, $Z_T$ is a prefect substitute for $Z_s$ for all periods $t,s$.
@@
 Now, consider the set
-	$$S = \argmax_i \, \sum_t \alpha_t \xi_{i,t}/c_i$$
+	\begin{equation}
+	S = \argmax_i \, \sum_t \alpha_t \xi_{i,t}/c_i
+	\end{equation}
 	This set contains the indices of the inputs that have the maximal cost-adjusted marginal utility. 
 	The optimal solution for $\mathbf{X}$ is defined by the set 
-	$$
+	\begin{equation}
 	W =
 	\{ \mathbf{X} \, : \, \mathbf{c}^T \mathbf{X} = I \;,\;  \mathbf{X} \geq 0 \;,\; \text{and} \;\;  (x_i > 0 \implies i \in S) \;\; \forall i \}
-	$$
+	\end{equation}
 	This set contains vectors that define bundles of inputs that maximize utility.
@@
 Specifically, the indices in $S$ denote the technologies that have maximial cost-adjusted marginal utility, so these inputs  will individually and in combination maximize consumer utility against the budget constraint.
+	This gives us the last proposition:
+
+	\hfill
+
+	\noindent \textbf{Proposition 2A:} \textit{Suppose that we have $\sigma \to \infty$. Then, 
+		\begin{itemize}
+			\item Electricity consumption in each period $t$ is a perfect substitute for electricity consumption in period $s$ for all periods $t,s$; 
+			\item The utility function takes on the linear form $U = \sum_t \alpha_t Z_t$; and
+			\item The set of optimal bundles of inputs $\mathbf{X}$ is given by 
+			$$
+			W =
+			\{ \mathbf{X} \, : \, \mathbf{c}^T \mathbf{X} = I \,,\;  \mathbf{X} \text{ non-negative} \,,\; \text{and} \;\;  (x_i > 0 \implies i \in S) \;\; \forall i \}
+			$$
+			$$\text{where} \quad S = \argmax_i \, \sum_t \alpha_t \xi_{i,t}/c_i$$
+		\end{itemize}
+		$S$ represents the set of indices for technologies that have maximal cost-adjusted marginal utility.
+In other words, any vector of inputs $\mathbf{X}$ consisting of a feasible (non-negative $\mathbf{X}$) and affordable $(\mathbf{c}^T \mathbf{X} = I$) combination of technologies in $S$ represent a valid equilibrium solution.
+Furthermore, the set $Y = \{ \mathbf{Z} \,: \, \mathbf{Z} = \boldsymbol{\xi}^T \mathbf{X}  \; \, \forall \, \mathbf{X} \in W \}$ contains all possible equilibrium values of electricity output.
+}
+
+	\hfill
 
 	\begin{proof}
-
-		Consider $\mathbf{Y} \not\in W$ where $\mathbf{Y} \geq 0$ (feasible) and $\mathbf{c}^T  \mathbf{Y} \leq  I$ (affordable).	Note that $\mathbf{Y} \not\in W$ implies we have either $\mathbf{c}^T \mathbf{Y} < I$ or there exists some $i$ such that $y_i > 0$ but $i \not\in S$.
+		Consider an arbitrary input bundle $\mathbf{Y} \not\in W$ where $\mathbf{Y} \geq 0$ (feasible) and $\mathbf{c}^T  \mathbf{Y} \leq  I$ (affordable).	Note that $\mathbf{Y} \not\in W$ implies we have either $\mathbf{c}^T \mathbf{Y} < I$ or there exists some $i$ such that $y_i > 0$ but $i \not\in S$.
 
@@
 Moreover, it can be shown that this FOC can be rearranged to give the following demand equation for each technology $i$
-		\begin{align}
+		\begin{align*}
 		X_i &= \left(\frac{\beta_i}{c_i} \right)^\sigma \frac{I}{P} \\
 		P &= \sum_t \beta_i^\sigma p_i^{1-\sigma}
-		\end{align}
+		\end{align*}
 		where $\beta_i = \alpha_i \xi_{i,i}^{-\phi}$, $\sigma = 1 / (1-\phi)$, and $I$ is the consumers income.	So, in total, accounting for both the producer and consumer's objectives, we are essentially solving for:
@@
 Furthermore, suppose that the output of our first technology is constant in both periods, $\xi_{1t} = \xi_{2t}$, but the output of our second technology is zero in the second period $\xi_{2s} = 0$.
-And, assume we have the parameter restrictions mentioned in earlier in \autoref{tab:paramrest} that ensure $X, Z > 0$.
+And, assume we have the parameter restrictions mentioned in earlier in \autoref{tab:paramrest} that ensure $\mathbf{X}, \mathbf{Z} > 0$.
 This is a simple case where we have (1) a constant output technology and (2) a highly intermittent technology.
@@
 
-	\begin{table}[!h] \centering 
-		\caption{OLS Regression Results}
-		\label{table:ols} 
-		\small
-		\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
-			\\[-4ex]\hline  
-			\hline \\[-1.8ex] 
-			& \multicolumn{6}{c}{\textit{Dependent variable:} $\ln (Z_{ t, i} / Z_{ s, i})$} \\ [0.5ex]
-			\cline{2-7} 
-			\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ [0.5ex]
-			\hline \\[-1.8ex] 
-			$-\ln (P_{t,i} / P_{s,i})$ & 0.937$^{***}$ & 1.075$^{***}$ & 1.098$^{***}$ & 1.074$^{***}$ & 1.263$^{***}$ & 1.305$^{***}$ \\ 
-			& (0.030) & (0.026) & (0.026) & (0.224) & (0.172) & (0.169) \\ 
-			& & & & & & \\ 
-			$\Delta_{t,s}$ &  &  & 0.0005$^{***}$ &  &  & 0.0065$^{*}$ \\ 
-			&  &  & (0.0001) &  &  & (0.0003) \\ 
-			& & & & & & \\ 
-			CDD$_t$ &  & 1.156$^{***}$ & 1.163$^{***}$ &  & 1.164$^{***}$ & 1.174$^{***}$ \\
-
-			$\quad(\times 1000^{-1})$ &  & (0.017) & (0.017) &  & (0.072) & (0.075) \\ 
-			& & & & & & \\ 
-			CDD$_s$ &  & $-$1.143$^{***}$ & $-$1.158$^{***}$ &  & $-$1.200$^{***}$ & $-$1.224$^{***}$ \\ 
-			$\quad(\times 1000^{-1})$&  & (0.025) & (0.026) &  & (0.096) & (0.098) \\ 
-			& & & & & & \\ 
-			HDD$_t$  &  & 0.246$^{***}$ & 0.245$^{***}$ &  & 0.237$^{***}$ & 0.236$^{***}$ \\ 
-			$\quad(\times 1000^{-1})$ &  & (0.007) & (0.007) &  & (0.031) & (0.031) \\ 
-			& & & & & & \\ 
-			HDD$_s$ &  & $-$0.267$^{***}$ & $-$0.265$^{***}$ &  & $-$0.268$^{***}$ & $-$0.263$^{***}$ \\ 
-			$\quad(\times 1000^{-1})$ &  & (0.008) & (0.008) &  & (0.038) & (0.038) \\ 
-			& & & & & & \\ 
-			Intercept & 0.028$^{***}$ & 0.012$^{*}$ & 0.026$^{***}$ &  &  &  \\ 
-			& (0.004) & (0.006) & (0.007) &  &  &  \\  [0.9ex]
-			\hline \\[-1.8ex] 
-			State FEs &   &   &   & Yes & Yes & Yes \\ 
-			Observations & 6,817 & 6,817 & 6,817 & 6,817 & 6,817 & 6,817 \\ 
-			R$^{2}$ & 0.079 & 0.507 & 0.508 & 0.092 & 0.521 & 0.524 \\ 
-			Adjusted R$^{2}$ & 0.079 & 0.506 & 0.508 & 0.085 & 0.518 & 0.520 \\  
-			F Statistic & 582$^{***}$  & 1399$^{***}$  & 1172$^{***}$ & 685$^{***}$  & 1474$^{***}$  & 1241$^{***}$  \\ [0.5ex]
-			\hline 
-			\hline \\[-1.8ex] 
-			\multicolumn{7}{@{}p{41.4em}@{}}{\textit{Note: } The sample covers the 48 contiguous US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
+%	
+%	\begin{table}[!h] \centering 
+%		\caption{OLS Regression Results}
+%		\label{table:ols} 
+%		\small
+%		\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
+%			\\[-4ex]\hline  
+%			\hline \\[-1.8ex] 
+%			& \multicolumn{6}{c}{\textit{Dependent variable:} $\ln (Z_{ t, i} / Z_{ s, i})$} \\ [0.5ex]
+%			\cline{2-7} 
+%			\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ [0.5ex]
+%			\hline \\[-1.8ex] 
+%			$-\ln (P_{t,i} / P_{s,i})$ & 0.937$^{***}$ & 1.075$^{***}$ & 1.098$^{***}$ & 1.074$^{***}$ & 1.263$^{***}$ & 1.305$^{***}$ \\ 
+%			& (0.030) & (0.026) & (0.026) & (0.224) & (0.172) & (0.169) \\ 
+%			& & & & & & \\ 
+%			$\Delta_{t,s}$ &  &  & 0.0005$^{***}$ &  &  & 0.0065$^{*}$ \\ 
+%			&  &  & (0.0001) &  &  & (0.0003) \\ 
+%			& & & & & & \\ 
+%			CDD$_t$ &  & 1.156$^{***}$ & 1.163$^{***}$ &  & 1.164$^{***}$ & 1.174$^{***}$ \\ 
+%			
+%			$\quad(\times 1000^{-1})$ &  & (0.017) & (0.017) &  & (0.072) & (0.075) \\ 
+%			& & & & & & \\ 
+%			CDD$_s$ &  & $-$1.143$^{***}$ & $-$1.158$^{***}$ &  & $-$1.200$^{***}$ & $-$1.224$^{***}$ \\ 
+%			$\quad(\times 1000^{-1})$&  & (0.025) & (0.026) &  & (0.096) & (0.098) \\ 
+%			& & & & & & \\ 
+%			HDD$_t$  &  & 0.246$^{***}$ & 0.245$^{***}$ &  & 0.237$^{***}$ & 0.236$^{***}$ \\ 
+%			$\quad(\times 1000^{-1})$ &  & (0.007) & (0.007) &  & (0.031) & (0.031) \\ 
+%			& & & & & & \\ 
+%			HDD$_s$ &  & $-$0.267$^{***}$ & $-$0.265$^{***}$ &  & $-$0.268$^{***}$ & $-$0.263$^{***}$ \\ 
+%			$\quad(\times 1000^{-1})$ &  & (0.008) & (0.008) &  & (0.038) & (0.038) \\ 
+%			& & & & & & \\ 
+%			Intercept & 0.028$^{***}$ & 0.012$^{*}$ & 0.026$^{***}$ &  &  &  \\ 
+%			& (0.004) & (0.006) & (0.007) &  &  &  \\  [0.9ex]
+%			\hline \\[-1.8ex] 
+%			State FEs &   &   &   & Yes & Yes & Yes \\ 
+%			Observations & 6,817 & 6,817 & 6,817 & 6,817 & 6,817 & 6,817 \\ 
+%			R$^{2}$ & 0.079 & 0.507 & 0.508 & 0.092 & 0.521 & 0.524 \\ 
+%			Adjusted R$^{2}$ & 0.079 & 0.506 & 0.508 & 0.085 & 0.518 & 0.520 \\  
+%			F Statistic & 582$^{***}$  & 1399$^{***}$  & 1172$^{***}$ & 685$^{***}$  & 1474$^{***}$  & 1241$^{***}$  \\ [0.5ex]
+%			\hline 
+%			\hline \\[-1.8ex] 
+%			\multicolumn{7}{@{}p{41.4em}@{}}{\textit{Note: } The sample covers the 48 contiguous US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
 The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state.
@@
 *p$\textless$0.05, **p$\textless$0.01, ***p$\textless$0.001}  \\
-		\end{tabular} 
-	\end{table}
-	\clearpage
-
-	\begin{table}[!h] 
-		\centering 
-		\caption{IV (2SLS) Regression Results}
-		\label{table:iv} 
-		\small
-		\begin{tabular}{@{\extracolsep{4pt}}lcccccc} 
-			\\[-4ex]\hline  
-			\hline \\[-1.6ex] 
-			& \multicolumn{3}{c}{First-Stage} & \multicolumn{3}{c}{Second-Stage} \\ [0.5ex]
-			& \multicolumn{3}{c}{\textit{Dep. Variable:} $\ln (P_{t,i} / P_{s,i})$ } & \multicolumn{3}{c}{\textit{Dep. Variable:}  $\ln (Z_{ t, i} / Z_{ s, i})$}\\ [0.5ex]
-			\cmidrule(lr){2-4} \cmidrule(lr){5-7}\\[-2.2ex] 
-			& (A.1) & (B.1) & (C.1) & (A.2) & (B.2) & (C.2)\\ [0.5ex]
-			\hline \\[-1.8ex] 
-			$ \ln (C_{t,i} / C_{s,i})$ & $-$0.042$^{***}$ & $-$0.018$^{***}$ & $-$0.018$^{***}$ &  &  &  \\ 
-			& (0.002) & (0.002) & (0.002) &  &  &  \\ 
-			& & & & & & \\ 
-			$-\ln (P_{t,i} / P_{s,i})$ &  &  &  & 2.978$^{***}$ & 5.896$^{***}$ & 5.818$^{***}$ \\ 
-			&  &  &  & (0.180) & (0.548) & (0.524) \\ 
-			& & & & & & \\ 
-			$\Delta_{t,s}$  &  &  & 0.001$^{***}$ &  &  & 0.003$^{***}$ \\ 
-			&  &  & (0.00004) &  &  & (0.0004) \\ 
-			& & & & & & \\ 
-			CDD$_t$  &  & 0.100$^{***}$ & 0.105$^{***}$ &  & 1.637$^{***}$ & 1.657$^{***}$ \\ 
-			$\quad(\times 1000^{-1})$ &  & (0.006) & (0.006) &  & (0.068) & (0.067) \\ 
-			& & & & & & \\ 
-			CDD$_s$ &  & $-$0.096$^{***}$ & $-$0.114$^{***}$ &  & $-$1.688$^{***}$ & $-$1.783$^{***}$ \\ 
-			$\quad(\times 1000^{-1})$  &  & (0.009) & (0.009) &  & (0.079) & (0.084) \\ 
-			& & & & & & \\ 
-			HDD$_t$  &  & $-$0.048$^{***}$ & $-$0.048$^{***}$ &  & 0.001 & 0.007 \\ 
-			$\quad(\times 1000^{-1})$ &  & (0.003) & (0.003) &  & (0.031) & (0.030) \\ 
-			& & & & & & \\ 
-			HDD$_s$  &  & 0.053$^{***}$ & 0.055$^{***}$ &  & 0.0001 & 0.007 \\ 
-			$\quad(\times 1000^{-1})$  &  & (0.003) & (0.003) &  & (0.035) & (0.034) \\   [0.9ex]
-			\hline \\[-1.8ex] 
-			State FEs &  Yes & Yes  & Yes  & Yes & Yes & Yes \\ 
-			Observations & 6817 & 6817 & 6817 & 6817 & 6817 & 6817 \\ 
-			R$^{2}$ & 0.061 & 0.264 & 0.294 &  &  & \\ 
-			Adjusted R$^{2}$ & 0.061 & 0.264 & 0.293 & &  &  \\ 
-			F Statistic & 443$^{***}$  & 489$^{***}$ & 472$^{***}$  &  &  &  \\ 
-			\hline 
-			\hline \\[-1.8ex] 
-			\multicolumn{7}{@{}p{41.5em}@{}}{\textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions.
+%		\end{tabular} 
+%	\end{table}
+%	\clearpage
+%	
+%	
+%	
+%	\begin{table}[!h] 
+%		\centering 
+%		\caption{IV (2SLS) Regression Results}
+%		\label{table:iv} 
+%		\small
+%		\begin{tabular}{@{\extracolsep{4pt}}lcccccc} 
+%			\\[-4ex]\hline  
+%			\hline \\[-1.6ex] 
+%			& \multicolumn{3}{c}{First-Stage} & \multicolumn{3}{c}{Second-Stage} \\ [0.5ex]
+%			& \multicolumn{3}{c}{\textit{Dep. Variable:} $\ln (P_{t,i} / P_{s,i})$ } & \multicolumn{3}{c}{\textit{Dep. Variable:}  $\ln (Z_{ t, i} / Z_{ s, i})$}\\ [0.5ex]
+%			\cmidrule(lr){2-4} \cmidrule(lr){5-7}\\[-2.2ex] 
+%			& (A.1) & (B.1) & (C.1) & (A.2) & (B.2) & (C.2)\\ [0.5ex]
+%			\hline \\[-1.8ex] 
+%			$ \ln (C_{t,i} / C_{s,i})$ & $-$0.042$^{***}$ & $-$0.018$^{***}$ & $-$0.018$^{***}$ &  &  &  \\ 
+%			& (0.002) & (0.002) & (0.002) &  &  &  \\ 
+%			& & & & & & \\ 
+%			$-\ln (P_{t,i} / P_{s,i})$ &  &  &  & 2.978$^{***}$ & 5.896$^{***}$ & 5.818$^{***}$ \\ 
+%			&  &  &  & (0.180) & (0.548) & (0.524) \\ 
+%			& & & & & & \\ 
+%			$\Delta_{t,s}$  &  &  & 0.001$^{***}$ &  &  & 0.003$^{***}$ \\ 
+%			&  &  & (0.00004) &  &  & (0.0004) \\ 
+%			& & & & & & \\ 
+%			CDD$_t$  &  & 0.100$^{***}$ & 0.105$^{***}$ &  & 1.637$^{***}$ & 1.657$^{***}$ \\ 
+%			$\quad(\times 1000^{-1})$ &  & (0.006) & (0.006) &  & (0.068) & (0.067) \\ 
+%			& & & & & & \\ 
+%			CDD$_s$ &  & $-$0.096$^{***}$ & $-$0.114$^{***}$ &  & $-$1.688$^{***}$ & $-$1.783$^{***}$ \\ 
+%			$\quad(\times 1000^{-1})$  &  & (0.009) & (0.009) &  & (0.079) & (0.084) \\ 
+%			& & & & & & \\ 
+%			HDD$_t$  &  & $-$0.048$^{***}$ & $-$0.048$^{***}$ &  & 0.001 & 0.007 \\ 
+%			$\quad(\times 1000^{-1})$ &  & (0.003) & (0.003) &  & (0.031) & (0.030) \\ 
+%			& & & & & & \\ 
+%			HDD$_s$  &  & 0.053$^{***}$ & 0.055$^{***}$ &  & 0.0001 & 0.007 \\ 
+%			$\quad(\times 1000^{-1})$  &  & (0.003) & (0.003) &  & (0.035) & (0.034) \\   [0.9ex]
+%			\hline \\[-1.8ex] 
+%			State FEs &  Yes & Yes  & Yes  & Yes & Yes & Yes \\ 
+%			Observations & 6817 & 6817 & 6817 & 6817 & 6817 & 6817 \\ 
+%			R$^{2}$ & 0.061 & 0.264 & 0.294 &  &  & \\ 
+%			Adjusted R$^{2}$ & 0.061 & 0.264 & 0.293 & &  &  \\ 
+%			F Statistic & 443$^{***}$  & 489$^{***}$ & 472$^{***}$  &  &  &  \\ 
+%			\hline 
+%			\hline \\[-1.8ex] 
+%			\multicolumn{7}{@{}p{41.5em}@{}}{\textit{Note: } The log difference in coal price between period $t$ and $s$, $ \ln (C_{t,i} / C_{s,i})$, is used as an instrument in these regressions.
 The sample covers the 48 contiguous US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
@@
 *p$\textless$0.05, **p$\textless$0.01, ***p$\textless$0.001}  \\
+%		\end{tabular} 
+%	\end{table}
+%	\clearpage
+
+	\begin{landscape}
+
+		\begin{table}[!h] \centering 
+			\caption{OLS and 2SLS Regression Results}
+			\label{table:regresults} 
+			\small
+			\begin{tabular}{@{\extracolsep{5pt}}lccccccccc} 
+				\\[-4ex]\hline  
+				\hline \\[-1.8ex] 
+				& \multicolumn{9}{c}{\textit{Dependent variable:} $\ln (Z_{ t, i} / Z_{ s, i})$} \\ [0.5ex]
+				\cline{2-10} \\ [-1.5ex]
+				& \multicolumn{6}{c}{ OLS}   & \multicolumn{3}{c}{ 2SLS} \\ [0.5ex]
+				\cline{2-7} \cline{8-10} 
+				\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) \\ [0.5ex]
+				\hline \\[-1.8ex] 
+				$-\ln (P_{t,i} / P_{s,i})$ & 0.937$^{***}$ & 1.075$^{***}$ & 1.098$^{***}$ & 1.074$^{***}$ & 1.263$^{***}$ & 1.305$^{***}$  & 2.978$^{***}$ & 5.896$^{***}$ & 5.818$^{***}$ \\ 
+				& (0.030) & (0.026) & (0.026) & (0.224) & (0.172) & (0.169) & (0.180) & (0.548) & (0.524) \\ 
+				& & & & & & \\ 
+				$\Delta_{t,s}$ &  &  & 0.0005$^{***}$ &  &  & 0.0065$^{*}$ &  &  & 0.003$^{***}$ \\ 
+				&  &  & (0.0001) &  &  & (0.0003)  &  &  & (0.0004) \\ 
+				& & & & & & \\ 
+				CDD$_t$ &  & 1.156$^{***}$ & 1.163$^{***}$ &  & 1.164$^{***}$ & 1.174$^{***}$  &  & 1.637$^{***}$ & 1.657$^{***}$ \\
+
+				$\quad(\times 1000^{-1})$ &  & (0.017) & (0.017) &  & (0.072) & (0.075) &  & (0.068) & (0.067) \\ 
+				& & & & & & \\ 
+				CDD$_s$ &  & $-$1.143$^{***}$ & $-$1.158$^{***}$ &  & $-$1.200$^{***}$ & $-$1.224$^{***}$ &  & $-$1.688$^{***}$ & $-$1.783$^{***}$ \\ 
+				$\quad(\times 1000^{-1})$&  & (0.025) & (0.026) &  & (0.096) & (0.098)  &  & (0.079) & (0.084) \\ 
+				& & & & & & \\ 
+				HDD$_t$  &  & 0.246$^{***}$ & 0.245$^{***}$ &  & 0.237$^{***}$ & 0.236$^{***}$  &  & 0.001 & 0.007 \\ 
+				$\quad(\times 1000^{-1})$ &  & (0.007) & (0.007) &  & (0.031) & (0.031) &  & (0.031) & (0.030) \\ 
+				& & & & & & \\ 
+				HDD$_s$ &  & $-$0.267$^{***}$ & $-$0.265$^{***}$ &  & $-$0.268$^{***}$ & $-$0.263$^{***}$ &  & 0.0001 & 0.007 \\ 
+				$\quad(\times 1000^{-1})$ &  & (0.008) & (0.008) &  & (0.038) & (0.038) &  & (0.035) & (0.034) \\
+				& & & & & & \\ 
+				Intercept & 0.028$^{***}$ & 0.012$^{*}$ & 0.026$^{***}$ &  &  &  &  &  &  \\ 
+				& (0.004) & (0.006) & (0.007) &  &  &   &  &  &  \\   [0.9ex]
+				\hline \\[-1.8ex] 
+				State FEs &   &   &   & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+				R$^{2}$ & 0.079 & 0.507 & 0.508 & 0.092 & 0.521 & 0.524 &  &  & \\ 
+				Adjusted R$^{2}$ & 0.079 & 0.506 & 0.508 & 0.085 & 0.518 & &  &  \\  
+				F Statistic & 582$^{***}$  & 1399$^{***}$  & 1172$^{***}$ & 685$^{***}$  & 1474$^{***}$  & 1241$^{***}$  & 443$^{***}$  & 489$^{***}$ & 472$^{***}$  \\ [0.5ex]
+				\hline 
+				\hline \\[-1.8ex] 
+				\multicolumn{10}{@{}p{58.6em}@{}}{\textit{Note: } The sample contains 6,817 observations and covers the 48 contiguous US states from 2011 to 2018; outliers are removed by trimming 1\% of each variable except $\Delta_{t,s}$.
+The unit of observation is a set $(t,s,i)$ where $t \neq s$ are months and $i$ is a state.
+The coefficient on $-\ln (P_{t,i} / P_{s,i})$ is the estimate of $\sigma$.
+The variable $\Delta_{t,s}$ is the difference in months between periods $t$ and $s$.
+CDD$_t$ and HDD$_t$ refer to the total number of heating and cooling degree days in month $t$.
+We scale the coefficients on degree days for clarity.
+The firs-stage F Statistic is reported for the 2SLS results.
+Robust standard errors are reported in parentheses.
+*p$\textless$0.05, **p$\textless$0.01, ***p$\textless$0.001}  \\
 			\end{tabular} 
 		\end{table}
+
+	\end{landscape}
+
 	\clearpage

### 2019-12-31 code/simulation/sim_eos_robust.m

@@ -5,7 +5,7 @@ close all; clear; clc;
 % Simulation params
 n = 5000;
 cost_multiplier = linspace(0.5,2,n);
-sigma_range = [1, 0.8847, 0.5, 0.25, 0.1,  0.01];
+sigma_range = [2, 1, 0.8847, 0.5, 0.25, 0.1,  0.01];
 m = length(sigma_range);
 
 % Exogenous params
@@ -77,9 +77,16 @@ for j = 1:m
 %     subplot(2,1,2);
     hold on;
     
-    plot(-log(output(1,2:end)), ...
-        diff(log(output(2,:)))./diff(-log(output(1,:))), ...
-        'LineWidth', 1, 'Color', [1, 1, 1]*(sigma/2 + 0.2));
+    if sigma ~= 0.8847
+        plot(-log(output(1,2:end)), ...
+            diff(log(output(2,:)))./diff(-log(output(1,:))), ...
+            'LineWidth', 1, 'Color', [1, 1, 1]*(sigma/3.5 + 0.2));
+    else
+        plot(-log(output(1,2:end)), ...
+            diff(log(output(2,:)))./diff(-log(output(1,:))), ...
+            'LineWidth', 1, 'Color', [1, 1, 1]*(sigma/4 + 0.2), ...
+            'LineStyle', '--');
+    end
     
     temp = diff(log(output(2,:)))./diff(-log(output(1,:)));
     [sigma, temp(587)]
@@ -88,7 +95,7 @@ end
 
 %% Plot formatting
 
-legend('1', '0.8847', '0.5', '0.25', '0.1', '0.01')
+legend('2', '1', '0.8847', '0.5', '0.25', '0.1', '0.01')
 xlabel({'Negative Log Difference in Costs', 'log(c_2/c_1)'})
 ylabel({'Elasticity of Substitution', ...
     'between Technologies', 'e_{1, 2}',})

### 2020-01-01 documents/revision.tex
Revise paper
- add additional explanation to model equilibrium

@@
 On the other hand, when the IES is high, consumers care less about smoothing their electricity consumption, so they are more willing to substitute between renewable and fossil energy.
+In short, the elasticity of substitution between renewable and fossil energy increases with the IES.
 We also find that the elasticity of substitution between renewable and fossil energy is not a simple, constant relationship.
@@
 	\end{proposition}
+	A detailed proof of Proposition 2 is given in \hyperref[sec:cobbdoug]{Appendix A.A}.
 
@@
 And, there may be multiple technologies that maximize consumer utility in this way; so, any combination of these technologies, indexed by $S$ in Proposition 2, will be optimal.
-Also, since consumers do not care about smoothing their consumption , the intermittency of an input has no effect on its adoption.
-A detailed proof of Proposition 2 is given in \hyperref[sec:cobbdoug]{Appendix A.A}.
+
+	Furthermore, since only total electricity output weighted by $\boldsymbol{\alpha}$ matters when choosing the optimal set of inputs, there is no preference for smoothing electricity consumption over time; again, this is because $\sigma \to \infty$ corresponds to the case of perfect substitutes.
+Consequently, the intermittency of an input has no effect on its adoption.
+This makes different inputs stronger substitutes for one another.
+To better understand why, suppose we have two technologies that cost the same per unit and produce the same total amount of electricity; one technology only produces during peak hours and the other producers only during the off-peak.
+If we have $\alpha_{peak} = \alpha_{off-peak}$, both technologies are perfect substitutes for one another when $\sigma \to \infty$.
+This is because any feasible combination of the technologies would give the same utility to the representative consumer.
+For instance, using the first technology and only getting electricity during peak hours would offer the same amount of utility as using a mix of both technologies and getting electricity during both periods.
+On the other hand, if we had finite $\sigma$, consumers would care about having electricity during both periods.
+This would cause the equilibrium solution to involve using both inputs.
+So, in general, when $\sigma \to \infty$, intermittency does not matter and inputs are more substitutable.
 
@@
 In other words, intermittency plays a much larger role when $\sigma \to 0$, since, in this case, a technology that with low output efficiency in certain periods cannot compensate by having higher output efficiency in other periods.
+This makes intermittent and consistent technologies weaker substitutes.
 
@@
 	We begin with the demand equation from our general model:
-	\begin{align*}
+	\begin{align}
 	Z_t &= \left(\frac{\alpha_t}{p_t} \right)^\sigma \frac{I}{P} \\
 	P &= \sum_t \alpha_t^\sigma p_t^{1-\sigma}
-	\end{align*}
+	\end{align}
 	For any pair of electricity outputs $Z_t$ and $Z_s$, we have:
@@
 	Taking logs on both sides and letting $i$ represent different observations, we may rewrite this in a form more suitable for estimation. 
-	\begin{align*}
+	\begin{align}
 	\ln (Z_{t, i} / Z_{ s, i}) &= -\sigma \ln (P_{t,i} / P_{s,i}) + \sigma \ln (\alpha_{t,i} / \alpha_{s,i}) 
-	\end{align*}
+	\end{align}
 	Our data differentiates consumption for each state in the US, so we let $i$ refer to a particular state.
@@
 So, still in general terms, our regression equation is now
-	\begin{align*}
+	\begin{align}
 	\ln (Z_{t, i} / Z_{ s, i}) &= -\sigma \ln (P_{t,i} / P_{s,i}) +  \gamma_{t,i} A_{t,i} + \gamma_{s,i} A_{s,i} + u_i
-	\end{align*}
+	\end{align}
 	where $A$ represents set of controls for changes in demand while $u_i$ is a normal error term.
@@
 In total, the demand equation is:
-	\begin{align*}
+	\begin{equation}
+	\begin{split}
 	\ln (Z_{ t, i} / Z_{ s, i}) &= -\sigma \ln (P_{t,i} / P_{s,i}) +  \gamma_{t,i} A_{t,i} + \gamma_{s,i} A_{s,i} + \eta \Delta_{t,s} + u_i \\
@@
 	&\qquad + \gamma_{s,i} \left( CDD_{s,i} + HDD{s,i} \right)  + \eta \Delta_{t,s} + u_i
-	\end{align*}
+	\end{split}
+	\end{equation}
 
 	Still, this equation may suffer from bias, since producers can also substitute production over time. To address endogeneity concerns, we define the following supply equation
-	\begin{align*}
+	\begin{align}
 	\ln (Z_{ t, i} / Z_{ s, i}) &= \beta \ln (P_{t,i} / P_{s,i}) + \zeta \ln (C_{t,i} / C_{s,i}) + v_{i}
-	\end{align*}
+	\end{align}
 	where $C_{t,i}$ is the average cost of coal used for electricity generation in state $i$ at time $t$ and $v_i$ is a normal error term.

### 2020-01-02 documents/revision.tex
Update revision
- add difference file
- minor changes to introduction, model, and formatting

@@
 \usepackage{gensymb}
+\usepackage{lineno}
 
@@
 
+% line numbers
+\linenumbers
+
 \begin{document}
@@
 In short, the elasticity of substitution between renewable and fossil energy increases with the IES.
-We also find that the elasticity of substitution between renewable and fossil energy is not a simple, constant relationship.
-This is important because a significant amount of literature has assumed a CES structure between renewable and fossil energy (see \citet{Pap}); this assumption has been motivated, in part, by the need to capture imperfect substitutability between these two generation technologies as a result of intermittency.
-But, our model finds that the elasticity of substitution between renewable and fossil energy is far from constant as a consequence of intermittency.
-This elasticity appears to vary with the quantity of each energy technology.
+
+	Furthermore, our numerical results show that the elasticity of substitution between renewable and fossil energy is non-constant and rises with the intermittency of present electricity generation.
+This occurs because consumers prefer to smooth their electricity consumption; so, when electricity output varies more over time, it becomes harder to replace consistent technologies with intermittent technologies.
+The result that the elasticity of substitution between technologies is non-constant is important because a significant amount of literature has assumed a CES structure between renewable and fossil energy (see \citet{Pap}); this assumption has been motivated, in part, by the need to capture imperfect substitutability between these two generation technologies as a result of intermittency.
+But, our model finds that intermittency itself causes a non-constant elasticity between technologies.
+This elasticity appears to vary with the cost of each energy technology.
 Hence, we argue against assuming a CES structure.
@@
 Overall, these characteristics can be captured using a standard CES utility function.
-Furthermore, since CES preferences are homothetic, we may aggregate the consumers into a single representative consumer.
-This consumer has the utility function
+Hence, we consider a representative consumer with the utility function
 	\begin{equation}
@@
 	where we have $n$ technologies, $m$ periods, and $\mathbf{Z} \equiv \boldsymbol{\xi}^T \mathbf{X}$.
-A key element of this model is that $\mathbf{X}$ does not vary by time.
+
+	A key assumption of our model is that the time scale is short enough such that the input vector $\mathbf{X}$ does not vary with time and the output per unit matrix $\boldsymbol{\xi}$ is exogenous.
 This is important because the time scale of our model must be fairly granular to study the effects of intermittency.
-So, for instance, we may have $t \in \{ 1, \dots, 24\}$ representing each hour of the day.
-Over such short time scales, the intermittency of renewables like solar and wind can significantly affect their economic value.
-Additionally, this allows us to assume that producers cannot modify the quantity of the technologies they deploy.
-And, thirdly, for certain technologies, this time frame is short enough to assume that $\boldsymbol{\xi}$ is exogenous; that is, technologies like coal power cannot significantly modify their output within a day, so $\boldsymbol{\xi}$ can be treated as a given set of constants.
-These latter two assumptions, that $\mathbf{X}$ cannot change over time and that $\boldsymbol{\xi}$ is exogenous, are important for parsimony, because they prevent more complicated dynamics from entering our model.
-So, by assuming a sufficiently short time frame, we can continue our study of intermittency in a relatively simpler setting.
-Furthermore, in this setting, we can use ``intermittent'' to refer to a technology where output per unit, $\xi_{i,t}$, varies over time (with $t$).
-
-	Next, our representative firm sets $\mathbf{X}$ once to maximize total profit; it does so by setting marginal profit equal to marginal cost.
+So, for instance, a reasonably short two-period setting would be $t \in$ \{peak, off-peak\}.
+Since the overall time frame is a single day, producers cannot modify the quantity of the technologies they deploy, so $\mathbf{X}$ must be fixed.
+Furthermore, this time frame is short enough to assume that $\boldsymbol{\xi}$ is exogenous; that is, technologies like coal power cannot significantly modify their output within a day, so $\boldsymbol{\xi}$ can be treated as a given set of constants.
+These two implications, that $\mathbf{X}$ cannot change over time and that $\boldsymbol{\xi}$ is exogenous, are important for parsimony, because they prevent more complicated dynamics from entering our model.
+And, they also make intermittency economically relevant, because having $\mathbf{X}$ fixed and $\boldsymbol{\xi}$ exogenous means that producers have no way of compensating for intermittent output; therefore, they must view the intermittency of technologies like solar and wind as a trade-off.
+
+	Furthermore, assuming a short time scale makes it simple to differentiate intermittent technologies.
+In this setting, we can use ``intermittent'' to refer to a technology where  output per unit, $\xi_{i,t}$, varies over time (with $t$).
+This is because we define intermittency as variation in electricity output over time due to physical constraints.
+Based on our assumptions, the only source of variation in output over time comes from $\boldsymbol{\xi}$.
+Hence, we only need to consider $\boldsymbol{\xi}$ to determine which inputs are intermittent.
+
+	Now, we consider the firm's problem.
+Our representative firm chooses $\mathbf{X}$ to maximize total profit; it does so by setting marginal profit equal to marginal cost.
 \citet{HH} note that past literature has argued for concave cost functions in the energy market due to effects such as economies of scale and learning-by-doing; on the other hand, standard cost functions are generally convex.
@@
 Specifically, the total cost of the input bundle $\mathbf{X}$ is given by $ \sum_i c_i X_i \equiv \mathbf{c}^T \mathbf{X}$ where $c_i$ is the cost per unit of $X_i$.
-Total profit is given by
+Then, total profit is given by
 	\begin{equation}
@@
 
-	For more tractable results, we consider a simpler scenario where $n = m = 2$ and $\sigma = 1$ (Cobb-Douglas); this particular case is described in greater details in \hyperref[sec:cobbdoug]{Appendix A.A}.
+	For more tractable results, we consider a simpler scenario where $n = m = 2$ and $\sigma = 1$ (Cobb-Douglas); this particular case is described in greater detail in \hyperref[sec:cobbdoug]{Appendix A.A}.
 These assumptions simplify the discussion of intermittency.
@@
 To better understand why, suppose we have two technologies that cost the same per unit and produce the same total amount of electricity; one technology only produces during peak hours and the other producers only during the off-peak.
-If we have $\alpha_{peak} = \alpha_{off-peak}$, both technologies are perfect substitutes for one another when $\sigma \to \infty$.
+If we have $\alpha_{\text{peak}} = \alpha_{\text{off-peak}}$, both technologies are perfect substitutes for one another when $\sigma \to \infty$.
 This is because any feasible combination of the technologies would give the same utility to the representative consumer.
@@
 	\end{align}
-	\vspace{-4ex}
 	$$\gamma > 0, \quad \omega > 0, \quad0 < \delta < 1, \quad 0 \leq \delta \rho \leq 1 , \quad (X_2/X_1) >  -\beta $$
